### 2022-06-03 reports/ACIC (2022)/poster/nhl-ice-poster.tex
Upload work

%------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------

\documentclass[final]{beamer}
% Default size: ARCH E1 30 x 42
\definecolor{darkblue}{HTML}{102451}

\usepackage[orientation=landscape,size=a0,scale=1]{beamerposter} % Use the beamerposter package for laying out the poster
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=darkblue,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{42in} % A0 width: 46.8in
\setlength{\paperheight}{32in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.295\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
\setlength\labelsep{\dimexpr\labelsep + 1em\relax}
\setlength{\parskip}{0.5\baselineskip}
\setlength{\parindent}{0em}

%-----------------------------------------------------------
% \renewcommand{\figurename}{Fig.}

\usepackage{caption}
\captionsetup{labelformat=simple, labelsep=colon}

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables

\usepackage{bbm} % more BB
\input{\string~/HeadRs/common_supplement.tex}

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

\usepackage{multicol}

\usepackage{adjustbox}
\usepackage{pgf}
\usepackage{pgfplots}
\usepackage{cmbright}
\pgfplotsset{compat=1.17}
\usepackage{tikz}
\usetikzlibrary{graphs, arrows.meta, automata, positioning, decorations}

\usepackage[sorting=none]{biblatex}
\renewcommand*{\bibfont}{\footnotesize}
\addbibresource{ser_poster.bib}

% -----------------------------------------------------------
\setbeamertemplate{headline}{
 \leavevmode
  \begin{columns}
   \begin{column}{\linewidth} % line
    \vskip1cm
    \centering
    \usebeamercolor{title in headline}{\color{jblue}
        \Huge % CHANGE this line for the size of the title
        {\textbf{\inserttitle}}\\[0.5ex]}
    \usebeamercolor{author in headline}{\color{fg}
        \Large % CHANGE this line for the size of the author
        {\insertauthor}\\[1ex]}
    \usebeamercolor{institute in headline}{\color{fg}
        \large % CHANGE this line for the size of the institut
        {\insertinstitute}\\[1ex]}
    \vskip1cm
   \end{column}
   \vspace{1cm}
  \end{columns}
 \vspace{0.5in} % CHANGE this line for the space between your title and the horizontal rule
 \begin{beamercolorbox}[wd=46in,colsep=0.1cm]{cboxb}\end{beamercolorbox}
 \vspace{0.1in} % CHANGE this line for the space between your horizontal rule and your main body
}

%------------------------------------------------------------------
%	TITLE SECTION
%------------------------------------------------------------------
\title{\huge Evaluating Exposure Limits for Reducing Non-Hodgkin Lymphoma Incidence\\[-0.25\baselineskip]{\Large An Application of the Hazard-Extended Iterative Conditional Expectation G-formula}} % Poster title
\author{Kevin T. Chen\textsuperscript{\small 1,2}, Ellen A. Eisen\textsuperscript{\small 1}} % Author(s)
\institute{
	University of California, Berkeley School of Public Health\\
	\normalsize
	\textsuperscript{1} Division of Environmental Health Sciences
	\hspace{1em}
	\textsuperscript{2} Division of Epidemiology \& Biostatistics
} % Institution(s)
%------------------------------------------------------------------

\begin{document}

% add logo
\addtobeamertemplate{headline}{}
{\begin{tikzpicture}[remember picture, overlay]
			\node [anchor=north west, inner sep=2.25cm]  at (current page.north west)
			{\includegraphics[height=10cm]{ucberkeleyseal_139_540.eps}};
  \end{tikzpicture}}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\setlength{\leftmargini}{\baselineskip}
\setlength{\leftmarginii}{\baselineskip}

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t,onlytextwidth,totalwidth=\onecolwid]

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The first column

%------------------------------------------------------------------
%	Introduction
%------------------------------------------------------------------

\begin{block}{Introduction}

\begin{minipage}{\linewidth}\begin{itemize}\setlength{\itemsep}{7pt}
\item Non-Hodgkin lymphoma (NHL) incidence increased 4-fold since 1960 \nocite{Ekstrom-Smedby_2006}
\item Rise in NHL followed growing use of industrial chemicals
\item Past occupational studies of NHL were limited
 	\begin{itemize}\setlength{\itemsep}{7pt}\normalsize
	\item Crude exposure assessment
	\item Conditional estimates of association
	\item Unrealistic static interventions
	\item Potential bias due to the healthy worker survivor effect (HWSE) \nocite{Arrighi_1994}
	\end{itemize}
\item \bfseries We estimate counterfactual cumulative incidence of NHL from 1985 to 2004 under hypothetical limits on average annual occupational exposure to metalworking fluid (MWF)
\end{itemize}
\end{minipage}

\end{block}

%------------------------------------------------------------------
%	Methods
%------------------------------------------------------------------

\begin{block}{Methods}

\textbf{Interventions:} $g_a$ on average exposure $A_k$ in year $k$:

$$g_a:\ A_k \longrightarrow
\begin{cases}
A_k & \text{if } A_k \le a \\
a & \text{if } A_k > a \\
\end{cases}$$

\begin{itemize}\setlength{\itemsep}{7pt}
\item Hypothetical limits: $a = 0.5,\ 0.25,\ 0.05$ mg/m\textsuperscript{3}
\item $g_a$ is a longitudinal stochastic intervention
\item No censoring by death
\end{itemize}

\vspace{0.5\baselineskip}\textbf{Data: United Auto Workers-General Motors Cohort Study}

\vspace{0.5\baselineskip}
\begin{minipage}{\linewidth}
\begin{itemize}\setlength{\itemsep}{7pt}
\item \textit{Quantitative exposure} for each person-year of employment from hire to 1995 based on several hundred samples
\item \textit{NHL outcome} from 1985 to 2005 via linkage to the Michican Cancer Registry (MCR) and the Surveillance, Epidemiology, and End Results (SEER) Program
\item \textit{Covariates} are age, calendar year, employment status, cumulative time off, year of hire, sex, race, and plant
\end{itemize}
\end{minipage}\vspace{0.25\baselineskip}

\vspace{0.5\baselineskip}\textbf{Estimation: Hazard-extended parametric G-formula \nocite{Wen_2020}}

\begin{itemize}\setlength{\itemsep}{7pt}
\item Pooling exposure history over $K = 8$ time periods
\item Exposure history at each time summmarized as cumulative exposure
\end{itemize}

\vspace{0.5\baselineskip}\textbf{Assumptions for causal inference}
\vspace{0.5\baselineskip}

\begin{minipage}{\linewidth}
\begin{itemize}\setlength{\itemsep}{7pt}
\item \textit{Conditional exchangeability}
\item \textit{Positivity (overlap)}
\item \textit{Consistency}
\item \textit{Correct model specification}
\end{itemize}
\end{minipage}\vspace{0.25\baselineskip}

\end{block}

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % Begin a column which is two columns wide (column 2)

%------------------------------------------------------------------
%	Results
%------------------------------------------------------------------
\begin{block}{Results}

\begin{table}\renewcommand{\arraystretch}{1.1}
\caption{\bfseries Population and non-Hodgkin lymphoma (NHL) case characteristics.}
\small
\begin{tabular}{p{0.4\linewidth}rlcrl}
  \toprule
 & \multicolumn{2}{c}{Study population} 	&  & \multicolumn{2}{c}{NHL cases} \\
  \midrule
	$N$ (person-years) & 34,734 & (596,698) &  & 231 & (2,777) \\
  Race &  &  &  &  &  \\
  \hspace{1em}White & 22,789 & (66\%) 		&  & 173 & (75\%) \\
  \hspace{1em}Black & 6,304 & (18\%) 			&  & 21 & (9\%) \\
  \hspace{1em}Unknown & 5,641 & (16\%) 		&  & 37 & (16\%) \\
  Sex &  &  &  &  &  \\
  \hspace{1em}Male & 30,235 & (87\%)		 	&  & 206 & (89\%) \\
  \hspace{1em}Female & 4,499 & (13\%) 		&  & 25 & (11\%) \\
  Plant &  &  &  &  &  \\
  \hspace{1em}Plant 1 & 8,721 & (25\%) 		&  & 68 & (29\%) \\
  \hspace{1em}Plant 2 & 14,258 & (41\%) 	&  & 90 & (39\%) \\
  \hspace{1em}Plant 3 & 11,755 & (34\%) 	&  & 73 & (32\%) \\
  Ever exposed$^1$
											& 31,044 & (89\%) 	&  & 210 & (91\%) \\
	Deceased by end of follow-up
																					& 10,384 & (30\%) 	&  & 33 & (14\%) \\
  \hline
  Year of birth & 1940 & (1925, 1950) 		&  & 1929 & (1919, 1940) \\
  Year of hire & 1967 & (1953, 1976) 			&  & 1959 & (1951, 1969) \\
  Age at hire (years) & 23.6 & (20.0, 30.1)					 		&  & 25.4 & (21.1, 33.6) \\
	Cumulative time off (years)$^1$ & 1.05 & (0.30, 1.80) &  & 0.71 & (0.14, 1.40) \\
  Years at work$^2$ & 15.3 & (7.3, 27.1) 								&  & 19.2 & (8.0, 29.9) \\
  Cumulative exposure (mg/m$^2\cdot$yr)$^{1,3}$
							& 4.65 & (1.85, 12.13) 					&  & 7.16 & (2.86, 20.91) \\
	\midrule
	\multicolumn{6}{p{0.85\linewidth}}{
	$^1$ Lagged 10 years; $^2$ Among those who left work before 1995;}\\
	\multicolumn{6}{p{0.85\linewidth}}{
	$^3$ Among ever-exposed indidivuals.}\\
   \bottomrule
	\end{tabular}
\end{table}

\vspace{1em}

% \begin{figure}
% \caption{foo.}
% \begin{center}
% \begin{tikzpicture}[>={Stealth[scale=1.3]}, auto,
% semithick, scale=6,
% thick, fill=white, inner sep=0pt, minimum size=0pt]
% \tikzstyle{every state}=[
% shape = rectangle, align = center, draw = none
% ]
% %
% \node[state] at (0, 2.5) (L0) {$L_{k-1}$};
% \node[state] at (1.5, 2.5) (L1) {$L_{k}$};
% \node[state] at (3, 2.5) (L2) {$L_{k + 1}$};
% \node[state] at (0.6, 1.66) (A0) {$A_{k-1}$};
% \node[state] at (2.1, 1.66) (A1) {$A_{k}$};
% \node[state] at (3.6, 1.66) (A2) {$A_{k + 1}$};
% \node[state] at (1.2, 0.833) (C0) {$C_{k-1}$};
% \node[state] at (2.7, 0.833) (C1) {$C_{k}$};
% \node[state] at (4.2, 0.833) (C2) {$C_{k + 1}$};
% \node[state] at (1.8, 0) (Y0) {$Y_{k-1}$};
% \node[state] at (3.3, 0) (Y1) {$Y_{k}$};
% \node[state] at (4.8, 0) (Y2) {$Y_{k + 1}$};
% %
% \path[->] (L0) edge (A0);
% \path[->] (L0) edge [bend right=40] (C0);
% \path[->] (L0) edge [bend right=40] (Y0);
% \path[->] (L0) edge (L1);
% \path[->] (A0) edge (C0);
% \path[->] (A0) edge [bend right=40] (Y0);
% \path[->] (A0) edge (L1);
% \path[->] (A0) edge (A1);
% \path[->] (A0) edge (C1);
% \path[->] (C0) edge (Y0);
% \path[->] (C0) edge (L1);
% \path[->] (C0) edge (A1);
% \path[->] (C0) edge (C1);
% \path[->] (Y0) edge (L1);
% \path[->] (Y0) edge (A1);
% \path[->] (Y0) edge (C1);
% \path[->] (Y0) edge (Y1);
% %
% \path[->] (L1) edge (A1);
% \path[->] (L1) edge [bend right=40] (C1);
% \path[->] (L1) edge [bend right=40] (Y1);
% \path[->] (L1) edge (L2);
% \path[->] (A1) edge (C1);
% \path[->] (A1) edge [bend right=40] (Y1);
% \path[->] (A1) edge (L2);
% \path[->] (A1) edge (A2);
% \path[->] (A1) edge (C2);
% \path[->] (C1) edge (Y1);
% \path[->] (C1) edge (L2);
% \path[->] (C1) edge (A2);
% \path[->] (C1) edge (C2);
% \path[->] (Y1) edge (L2);
% \path[->] (Y1) edge (A2);
% \path[->] (Y1) edge (C2);
% \path[->] (Y1) edge (Y2);
% %
% %
% \path[->] (L2) edge (A2);
% \path[->] (L2) edge [bend right=40] (C2);
% \path[->] (L2) edge [bend right=40] (Y2);
% \path[->] (A2) edge (C2);
% \path[->] (A2) edge [bend right=40] (Y2);
% \path[->] (C2) edge (Y2);
% \end{tikzpicture}
% \end{center}
% \end{figure}

\begin{figure}
\caption{\bfseries Cumulative exposure at end of follow-up under hypothetical limits on average annual exposure. Rug plots mark cumulative exposure accrued by NHL cases at end of follow-up.}
\includegraphics[width=0.87\linewidth]{../../../resources/shift-soluble.pdf}
\end{figure}

\end{block}

\end{column} % End of column 2

\begin{column}{\sepwid}\end{column}

\begin{column}{\onecolwid}

\begin{figure}
\caption{\bfseries Counterfactual cumulative incidence ratio estimates comparing hypothetical limits on average annual exposure to no limit.}
\includegraphics[width=0.87\linewidth]{resources/rr.pdf}
\end{figure}

\begin{table}\renewcommand{\arraystretch}{1.1}
\caption{\bfseries Counterfactual cumulative incidence estimates under hypothetical limits on average annual exposure and no censoring.}
\small
\begin{tabular}{p{0.17\linewidth}C{0.2\linewidth}cC{0.11\linewidth}C{0.2\linewidth}}
\toprule
Exposure limit
	& \thead{Person-years\\intervened (\%)}
	&& \thead{Cases\\expected}
	& (95\% BS CI)
	%& RR & (95\% BS CI)
	 \\ \midrule
None & 0 && 332 & (283, 378) %& 1.00 &
 \\
 0.5\phantom{0} mg/m\textsuperscript{3} & 23.8 && 288 & (226, 354)
 % & 0.87 & (0.72, 1.02)
  \\
0.25 mg/m\textsuperscript{3} & 36.2 && 280 & (214, 353)
 % & 0.84 & (0.68, 1.01)
 \\
0.05 mg/m\textsuperscript{3} & 43.9 && 261 & (199, 330)
 % & 0.79 & (0.62, 0.97)
\\
\bottomrule
\end{tabular}
\end{table}

\vspace{0.5em}

%------------------------------------------------------------------
%	Discussion
%------------------------------------------------------------------

\begin{block}{Discussion and Conclusions}

\begin{itemize}\setlength{\itemsep}{7pt}
\item Limiting average annual MWF exposure reduces NHL incidence
\item Longitudinal stochastic interventions represent realistic policies
	\begin{itemize}\setlength{\itemsep}{7pt}\normalsize
	\item NIOSH Recommended Exposure Limit is 0.5 mg/m\textsuperscript{3} \nocite{NIOSH_1998}
	\end{itemize}
\item Our method reduced potential bias due to HWSE
\item Outcome models were logistic regressions; assumption of correct model specification may be more plausible under machine learning approaches with cross-validation
\end{itemize}

\end{block}

\vspace*{-0.5\baselineskip}

%------------------------------------------------------------------
%	References
%------------------------------------------------------------------

\begin{block}{References}
		\setlength{\bibitemsep}{0pt}
    \printbibliography
\end{block}

\vspace*{-0.5\baselineskip}

%------------------------------------------------------------------
%	Acknowledgement of support
%------------------------------------------------------------------

\begin{block}{Acknowledgement of support}
This poster was supported by Training Grant T42OH008429, funded by the National Institute for Occupational Safety and Health (NIOSH) / Centers for Disease Control and Prevention (CDC)
\end{block}

\vspace*{-1\baselineskip}

\end{column} % End of column 3

\begin{column}{\sepwid}\end{column}% Empty spacer column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2022-06-03 reports/ACIC (2022)/poster/resources/rr.tex
Upload work

% Created by tikzDevice version 0.12.3.1 on 2022-05-20 15:39:29
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,126.47);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,126.47);
\end{scope}
\begin{scope}
\path[clip] ( 35.37, 28.21) rectangle (283.58,120.97);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 35.37, 28.21) rectangle (283.58,120.97);
\definecolor{drawColor}{RGB}{16,36,81}

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.11,101.41) --
	(213.11,105.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.11,103.58) --
	(118.54,103.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (118.54,101.41) --
	(118.54,105.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.44, 43.43) --
	(197.44, 47.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.44, 45.61) --
	( 86.05, 45.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.05, 43.43) --
	( 86.05, 47.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.09, 72.42) --
	(212.09, 76.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.09, 74.59) --
	(104.01, 74.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.01, 72.42) --
	(104.01, 76.77);
\definecolor{fillColor}{RGB}{16,36,81}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.35,103.58) circle (  1.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.20, 45.61) circle (  1.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.25, 74.59) circle (  1.32);
\definecolor{drawColor}{RGB}{16,36,81}

\path[draw=drawColor,draw opacity=0.70,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (207.83, 28.21) -- (207.83,120.97);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37, 28.21) rectangle (283.58,120.97);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 42.85) {0.05};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 71.84) {0.25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,100.83) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 45.61) --
	( 35.37, 45.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 74.59) --
	( 35.37, 74.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,103.58) --
	( 35.37,103.58);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.88, 25.46) --
	( 78.88, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.36, 25.46) --
	(143.36, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.83, 25.46) --
	(207.83, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (272.30, 25.46) --
	(272.30, 28.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 78.88, 17.75) {0.6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (143.36, 17.75) {0.8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (207.83, 17.75) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (272.30, 17.75) {1.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (159.47,  7.25) {Risk ratio};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70, 74.59) {Hypothetical limit (mg/m$^3$)};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-06-03 reports/paper/01-introduction.rmd
Upload work

---
output:
  word_document:
    reference_docx: "~/HeadRs/rmd_templates/style-guide-arial-11.docx"
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
csl: "`r path.expand('~/HeadRs/csl/asa.csl')`"
---

```{r, include=FALSE, eval=F}
knitr::opts_chunk$set(echo=F, results = 'asis')
library(bibtex)
biblio <- bibtex::read.bib('~/Box Sync/papers/EnvEpi.bib')
```

Metalworking fluids (MWF) are complex chemical mixtures used to lubricate and cool machinery during manufacturing processes. Straight MWF are the oldest class of MWF, comprising of simple oils or combinations of oils. By the mid 20th century, straight MWF waned in popularity and ceded market share to soluble MWF. Soluble MWF are water-oil mixtures with diverse additives for improving performance and durability. By the 1970s, semisynthetic and synthetic MWF, which contain little to no oil, overtook straight oils in market share. Nonetheless, at the turn of the millennium, soluble MWFs still retained the largest share of the MWF market [@Childers_2005]. Carcinogenicity of MWFs has been of concern since as early as the 1970s, when the International Agency for Research on Cancer (IARC) classified mineral oils as carcinogenic, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973]. Concerns over the health effects of straight MWF hastened the adoption of soluble MWF, which contain less oil per volume, but a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrosamines, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987;@IARC_2014;@IARC_2017]. Health and environmental considerations led to substantial variation in MWF composition over time, but the elimination of particular etiologic agents often leads to their replacement with other potentially hazardous chemical compounds. Exposure limits for MWF as a mixture encourage limiting occupational exposure to multiple agents simultaneously.

Here, we assess the effect of hypothetical exposure limits on non-Hodgkin lymphoma (NHL) cumulative incidence (risk) from 1985 to 2005 in the United Auto Workers-General Motors (UAW-GM) Occupational Cohort Study. The large size of the study population and rich time-varying, quantitative MWF exposure data provide an opportunity to study this relatively rare cancer while contrasting realistic interventions on MWF exposure in a longitudinal cohort setting. Though NHL accounts for a small proportion of cancer incidence of all sites, it has garnered intense research attention because its incidence nearly quadrupled since 1960 [@Ekstrom-Smedby_2006]. Immune modulation due to immunosuppressive therapy and infection by human immunodeficiency virus (HIV) are the most prominent risk factors of NHL, but they cannot fully explain this rise in NHL incidence [@Shiels_2013;@Chiu_2015]. Epidemiologic investigations of environmental and occupational exposures have yielded varied results [@Ekstrom-Smedby_2006;@Alexander_2007]. This variation in epidemiologic findings may reflect the substantial etiologic heterogeneity of NHL, but studies of specific NHL subtypes are limited by the lack of quantitative exposure information and the lack of control for the healthy worker survivor effect (HWSE) or other forms of time-varying confounding affected by prior exposure [@Evens_2008;@Morton_2014]. The HWSE, a key concern in occupational epidemiology, is the dynamic selection process by which healthier individuals remain at work, where they accumulate more occupational exposure, and less healthy individuals leave work [@Arrighi_1994]. Standard analyses of occupational cohorts affected by the HWSE result in a downward bias on the exposure-outcome associations of interest.

In the present analysis of the UAW-GM Cohort Study, we estimated NHL risk from 1985 to 2005 under hypothetical limits on average annual soluble MWF by applying the novel hazard-extended iterative conditional expectation (ICE) parametric g-formula estimator [@Wen_2020]. We leveraged time-varying quantitative MWF exposure data in tandem with employment data to adjust for the HWSE. In particular, we estimated the expected number of NHL cases we would observe if the hypothetical limits of 0.5, 0.25, and 0.05 mg/m^3^ were enforced for soluble MWF over workers' entire working lifetimes. Since workers were exposed to MWF of other types as well, we also evaluated the effect of dynamically reducing soluble MWF exposure with the goal of limiting total MWF exposure to 0.5 and 0.25 mg/m^3^.

### 2022-06-03 reports/paper/02-methods.rmd
Upload work

---
output:
  word_document:
    reference_docx: "~/HeadRs/rmd_templates/style-guide-arial-11.docx"
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
csl: "`r path.expand('~/HeadRs/csl/asa.csl')`"
---

```{r, include=FALSE, eval=F}
knitr::opts_chunk$set(echo=F, results = 'asis')
library(bibtex)
biblio <- bibtex::read.bib('~/Box Sync/papers/EnvEpi.bib')
```

# Methods

## Study population

The UAW-GM Cohort includes hourly workers at three automobile manufacturing plants in Michigan who had worked at least 3 years by 1985. Past papers provide detailed descriptions of the cohort [@Eisen_1992;@Eisen_2001]. The present study population (N = 34,738) was restricted to the autoworkers who were at work in 1941 or not yet hired, alive at the start of follow-up, and missing no more than half of their employment history. Autoworkers in the study population were followed for NHL incidence from January 1, 1995 until NHL diagnosis, death, December 31, 2004, or upon reaching the oldest observed age at death, whichever came earlier.

## Outcome and covariates

We identified incident cancers in the UAW-GM Cohort that occurred between 1985 and 2004 by linkage to the Michigan Cancer Registry (MCR). Workers at Plants 1 and 2, located in the greater Detroit metropolitan area, were also linked to the Detroit Regional Registry of the Surveillance, Epidemiology, and End Results (SEER) Program. Cancer types were distinguished using site and histology codes conforming to the International classification of Diseases for Oncology, 3^rd^ edition (ICD-O-3). Non-Hodgkin lymphoma was defined by cancers with any of the following ICD-O-3 Histology codes: 9590-9597, 9670-9671, 9673, 9675, 9678-9680, 9684, 9687-9691, 9695, 9698-9702, 9705, 9708-9709, 9712, 9714-9719, 9724-9729, 9735, 9737-9738, 9811-9818, 9823, 9827, 9837. Details regarding cancer incidence follow-up are described elsewhere [@Colbeth_2022]. Vital status was ascertained by company records and by linkage to Social Security Administration, National Death Index, death certificate, and state mortality files.

Covariates including year of hire, sex, race, and plant location were obtained from company records. Race data were missing for about 16% of the workers. In analyses, missing race was considered a distinct category of race.

## Exposure

For each combination of job type, department, and plant industrial hygienists collected several hundred personal and area samples for particulate matter (mg/m^3^) over the course of three decades to derive quantitative 8-hour time-weighted average exposure estimates to soluble, straight, and synthetic MWFs. Workers' time-weighted average annual exposure to each MWF type was determined according to employment records, which recorded time-varying job type, department, and plant. For employment records that were no less than half complete, gaps in the record were interpolated by carrying forward the last known job type. In each year, cumulative exposures to soluble, straight, and synthetic MWFs (mg/m^3^-years) were calculated by taking cumulative sums of average annual exposures. In analyses, MWF exposure was lagged 10 years. Exposure assessment is described in detail elsewhere [@Hallock_1994;@Woskie_1994;@Woskie_2003].

## Statistical methods

We applied the hazard-extended ICE parametric g-formula with pooling over treatment history [@Wen_2020] to estimate 20-year counterfactual risk of non-Hodgkin lymphoma under five hypothetical stochastic interventions on exposure to soluble MWFs with the elimination of censoring/competing risks. The first three interventions were static interventions that limited average annual exposure to soluble MWF to 0.5, 0.25, and 0.05 mg/m^3^. The remaining two were dynamic interventions that reduced average annual exposure to soluble MWF so that exposure to all MWF types was capped at 0.5 and 0.25 mg/m^3^, if possible. If those limits on total average annual exposure were not possible by intervention on soluble MWF alone, average annual exposure to soluble MWF was reduced to 0. Interventions were applied at hire, before the start of follow-up, through the end of follow-up. Person-years in which average annual exposure was below the hypothetical limits were not intervened upon. These hypothetical exposure limits reflect the Recommended Exposure Limit (REL) of the National Institute for Occupational Safety and Health (NIOSH) for total particulate mass from MWFs (0.5 mg/m^3^), half the REL (0.25 mg/m^3^), and a tenth of the REL (0.05 mg/m^3^) [@niosh_1998].

The hazard-extended ICE parametric g-formula estimator is an ICE expression of the parametric g-formula estimator, further extended to incorporate the predicted hazard of past outcomes. This differs from the classical ICE estimator, which incorporates past outcome data as indicators [@Wen_2020]. Under the assumptions of conditional exchangeability at all time points, positivity, counterfactual consistency, and correct model specification, the hazard-extended parametric g-formula yields unbiased estimates of counterfactual risk with greater statistical efficiency than both propensity-score based estimators and the classical ICE g-formula.

Our implementation of the hazard-extended ICE parametric g-formula involved a series of model-based standardization steps using logistic regression. Post-intervention estimates of the discrete hazard of NHL given all exposures and covariates were combined iteratively from the end of follow-up to the start. In each iteration, predicted discrete hazards were standardized over post-intervention exposure and covariate histories before combining with discrete hazards from the previous iteration. The result of this iterative process was sequentially-standardized estimates of the NHL risk over the entire follow-up period. Averaging over the baseline distribution of covariates yielded the counterfactual risk estimate of NHL when the intervention of interest was enforced for the entire study population.

We split the 20-year follow-up period into eight periods; the first two periods spanned four years each, and the remaining six periods spanned two years each. Post-intervention exposure and exposure history were summarized as cumulative exposure. We modeled discrete hazards by fitting a pooled logistic regression for NHL over at-risk person-periods given cumulative exposure to straight, soluble, and synthetic MWFs, employment status, cumulative time off, year of hire, sex (male/female), race (Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3). Cumulative exposure to MWFs, employment status, and cumulative time off were lagged 10 years. All continuous variables were represented as categorical variables with cut points determined by the tertiles of nonzero values among NHL cases. During the iterative combination of discrete hazards, we performed model-based standardization over baseline covariates and the complete set time-varying covariate histories.

We estimated risk under the observed distribution of soluble MWF exposure (natural course) and under the five interventions. We contrasted the risk under intervention to that under the natural course by computing relative risks. Confidence intervals were computed using the nonparametric bootstrap with 1000 samples and centering on the estimate computed from observed data. In secondary analyses (Appendix), we repeated the analysis to evaluate interventions on exposure to straight and synthetic MWFs.

<!-- GITHUB? -->

### 2022-06-03 reports/paper/03-results.rmd
Upload work

---
output:
  bookdown::word_document2:
    number_sections: false
    global_numbering: true
    reference_docx: "~/HeadRs/rmd_templates/style-guide-arial-11.docx"
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
csl: "`r path.expand('~/HeadRs/csl/asa.csl')`"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, results = 'asis',
											tab.cap.tnd = 1)
if (!'tidyr' %in% loadedNamespaces()) {library(tidyverse)}
library(flextable)
library(data.table)
```

# Results

```{r}
source(here::here("../gm-wrangling/wrangling/table1.R"))
clean.tab1 <- function(tab1) {
	# hspace.which <- grepl("\\\\hspace\\{.*\\}", rownames(tab1))
	rownames(tab1) <- gsub("\\\\hspace\\{.*\\}|\\\\hline |\\$.*\\$| among deceased", "", rownames(tab1))

	tab1[!grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2]  <-  paste0(
		"(",
		tab1[!grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2],
		")"
	)

	tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2] <- paste0(
		"(", tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2], ", ",
		tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 3],
		")"
	)

	return(tab1[,1:2])
}
full.tab1 <- readRDS(here::here("resources", "tab1.rds"))
nhl.tab1 <- readRDS(here::here("resources", "nhl.tab1.rds"))

tab1.clean <- clean.tab1(full.tab1)
nhl.tab1.clean <- clean.tab1(nhl.tab1)

tab1 <- cbind(hspace.logical = grepl("\\\\hspace\\{.*\\}", rownames(full.tab1)),
							variable = rownames(tab1.clean), tab1.clean, NA, nhl.tab1.clean)

tab1 <- tab1[!grepl("Years of follow-up", rownames(tab1)),]
tab1$variable[1] <- "N (person-years)"
```

Table 1 presents summary statistics of exposure and covariates for the full study population and for those diagnosed with NHL between 1985 and 2004. The cohort is predominantly white (66%) and male (87%). Plant 2 employed the largest number of workers while Plant 1 employed the fewest. The median year of hire among those diagnosed with NHL was 1959 whereas the median year of hire in the full study population was 1967. Age at hire was approximately the same among those with NHL and the full study population. Median lagged cumulative exposure to all three MWF types was higher among NHL cases. Soluble MWFs were the most widely used MWF type, with approximately 90% of workers ever exposed. Median cumulative exposure among exposed was 6.5 times higher for soluble than for straight MWFs. Figure 1 shows median average annual exposure to the three MWF types among exposed workers over calendar time. Exposure to MWF generally followed a downward trend over time. Figure 2 shows the post-intervention distribution of the logarithm of cumulative exposure to soluble MWF at end of follow-up if hypothetical limits on average annual exposure were enforced for all workers starting at hire. The interventions shifted the distribution of cumulative exposure rather than deterministically assigning exposure to a particular value.

```{r}
# tab1 <- tab1[tab1.which,]
tab1[,-grep("hspace.logical", colnames(tab1))] %>% 
	data.frame %>% flextable() %>%
	delete_part(part = "header") %>%
	add_header_row(values = c("", "Study population", "", "NHL cases"),
								 colwidths = c(1, 2, 1, 2)) %>%
	hline_top(part = "header") %>%
	hline_top() %>% hline_bottom() %>%
	hline(which((grepl("[0-9]\\)", tab1$spread))[-1])[1]) %>% width(4, 0.1) %>%
	width(1, 2.2) %>% width(c(3, 6), 1.1) %>% width(c(2, 5), 0.65) %>%
	flextable::compose(
		i = grep("Cumulative exposure", rownames(tab1)), j = 1,
		value = as_paragraph("Cumulative exposure to MWFs (mg/m",
												 as_sup("3"), "-years)")) %>%
	flextable::align(j = 2:6, align = "center", part = "all") %>%
	footnote(i = grep("Plant$", rownames(tab1)), j = 1, value = as_paragraph(
		" Plant of longest employment duration among those who worked at multiple plants"),
		ref_symbols = "a", inline = T) %>%
	footnote(i = grep("Ever exposed|time off", rownames(tab1)), j = 1, value = as_paragraph(
		" Lagged 10 years"),
		ref_symbols = "b", inline = T) %>%
	footnote(i = grep("work", rownames(tab1)), j = 1, value = as_paragraph(
		" Among those who left work by December 31, 1994"),
		ref_symbols = "c", inline = T) %>%
	# footnote(i = grep("death", rownames(tab1)), j = 1, value = as_paragraph(
	# 	" Among deceased"),
	# 	ref_symbols = "d", inline = T) %>%
	footnote(i = grep("Cumulative exposure", rownames(tab1)), j = 1, value = as_paragraph(
		" Among ever-exposed individuals, lagged 10 years."),
		ref_symbols = "d", inline = T) %>%
	add_footer_row(values = "NHL: non-Hodgkin lymphoma.", colwidths = 6) %>%
	padding(padding = 1.5, part = "all") %>%
	padding(
		i = which(tab1$hspace.logical),
		j = 1,
		padding.left = 20
	) %>%
	merge_at(i = grep("Cumulative exposure", rownames(tab1))) %>%
	hline_bottom(part = "footer") %>% font(fontname = 'arial') %>%
	set_caption(caption = "Summary of population characteristics. Statistics shown above the horizontal line are count (%). Those shown below are median (quartile 1, quartile 3).")
```
\

![Figure 1. Median average annual exposure to straight, soluble, and synthetic metalworking fluids among exposed workers over time.](`r here::here("resources/images", "exposure.png")`){width=6.5in}

\

![Figure 2. Post-intervention distribution of cumulative exposure to soluble metalworking fluids at end of follow-up under hypothetical limits on average annual exposure (mg/m^3^). The rugplot shows maximum cumulative exposure accrued by non-Hodgkin lymphoma cases.](`r here::here("resources/images", "shift-soluble.png")`){width=4in}

```{r}
intervened_py <- readRDS(here::here("resources", "percent-py-intervened.rds"))
# paste(paste0("\"", intervened_py$dt.name, "\""), collapse = ",\n") %>% clipr::write_clip()
dat.names <- data.table(
	dt.name = c(
		"dat.sol.reduced", "dat.sol.reduced2", "dat.sol.reduced10",
		"dat.sol_total.reduced", "dat.sol_total.reduced2",
		"dat.str.reduced", "dat.str.reduced2", "dat.str.reduced10",
		"dat.str_total.reduced", "dat.str_total.reduced2",
		"dat.syn.reduced", "dat.syn.reduced2", "dat.syn.reduced10",
		"dat.syn_total.reduced", "dat.syn_total.reduced2"),
	variable.dat = c(
		"soluble", "soluble2", "soluble10",
		"total by soluble", "total by soluble2",
		"straight", "straight2", "straight10",
		"total by straight", "total by straight2",
		"synthetic", "synthetic2", "synthetic10",
		"total by synthetic", "total by synthetic2"
	)
)
intervened_py <- as.data.table(merge(
	intervened_py, dat.names,
	by = "dt.name"))
intervened_py <- rbindlist(list(
	data.table(dt.name = NA,
						 mwf = NA, percent_py_intervened = 0,
						 variable.dat = "natural"),
	intervened_py
))
```

```{r}
load(here::here("resources", paste0("h.estimates.rdata")))
estimates.bs <- readRDS(here::here("resources", paste0("estimates.bs.rds")))
```

```{r}
do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
	x/estimates.bs[,2]
})) %>% melt(measure.vars = names(.)) -> rr.bs

estimates.bs[,-1] %>% melt(measure.vars = names(.)) -> risk.bs

# Collect point estimates
point_estimates <- data.table(
	variable = c(
		"straight", "total by straight", "straight2", "total by straight2",
		"straight10",
		"soluble", "total by soluble", "soluble2", "total by soluble2",
		"soluble10",
		"synthetic", "total by synthetic", "synthetic2", "total by synthetic2",
		"synthetic10",
		"scale all", "scale all2", "natural"),
	estimate = c(
		h.reduction.str, h.reduction.str_total, h.reduction.str2, h.reduction.str_total2,
		h.reduction.str10,
		h.reduction.sol, h.reduction.sol_total, h.reduction.sol2, h.reduction.sol_total2,
		h.reduction.sol10,
		h.reduction.syn, h.reduction.syn_total, h.reduction.syn2, h.reduction.syn_total2,
		h.reduction.syn10,
		h.reduction.total, h.reduction.total, h.baseline)
)

# Calculate risk ratios for each bootstrap sample
rr <- merge(
	rr.bs,
	point_estimates[,.(
		variable = paste0(variable, ".natural"),
		estimate = estimate/estimate[variable == "natural"]
	)],
	all = T,
	by = "variable")

# Get lower and upper 2.5th %tiles
rr <- rr[,.(estimate = estimate[1],
			lower = {
				x <- value
				x[!is.na(x)] <- quantile(x[!is.na(x)], 0.025) - mean(x[!is.na(x)]) + estimate[1]},
			upper = {
				x <- value
				x[!is.na(x)] <- quantile(x[!is.na(x)], 1 - 0.025) - mean(x[!is.na(x)]) + estimate[1]}
			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
			# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
			),
	 variable]

# Colleect risks
risks <- merge(
	risk.bs,
	point_estimates,
	all = T,
	by = "variable")

# Get lower and upper 2.5th %tiles
risks <- risks[,.(estimate = estimate[1],
			lower = {
				x <- value
				x[!is.na(x)] <- quantile(x[!is.na(x)], 0.025) - mean(x[!is.na(x)]) + estimate[1]},
			upper = {
				x <- value
				x[!is.na(x)] <- quantile(x[!is.na(x)], 1 - 0.025) - mean(x[!is.na(x)]) + estimate[1]}
			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
			# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
			),
	 .(variable.risks = variable)]
```

```{r}
intervention.labels <- data.table(
	variable = c(
		"natural", "straight", "soluble", "synthetic",
		"straight2", "soluble2", "synthetic2",
		"straight10", "soluble10", "synthetic10",
		"total by straight", "total by soluble", "total by synthetic",
		"total by straight2", "total by soluble2", "total by synthetic2",
		"scale all", "scale all2"
	),
	label = c(
		"None", rep("0.5", 3), rep("0.25", 3), rep("0.05", 3),
		"max(0, 0.5 - sol - syn)", "max(0, 0.5 - str - syn)", "max(0, 0.5 - str - sol)",
		"max(0, 0.25 - sol - syn)", "max(0, 0.25 - str - syn)", "max(0, 0.25 - str - sol)",
		"scale all to 0.5", "scale all to 0.25"
	)
)
# Add intervention labels
rr <- merge(
	rr, intervention.labels[,.(variable = paste0(variable, ".natural"), label)],
	all.x = T,
	by = "variable"
)
```

```{r}
clean_percent_py <- function(variable, digits = 1, scale = 100) {
	sprintf(paste0("%.", digits, "f"), round(
		intervened_py[match(
	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
	 		variable.dat
	), percent_py_intervened] * scale,
	digits))
}

clean_risk <- function(variable, digits = 2, scale = 1000) {
	sprintf(paste0("%.", digits, "f"), round(risks[match(
	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
	 		variable.risks
	), estimate] * scale, digits))
}

clean_risk.ci <- function(variable, digits = 2, scale = 1000) {
	 		x <- risks[match(
	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
	 		variable.risks
	 		),.(lower, upper)]
	 		ifelse(!is.na(x$lower), paste0(
	 			"(",
	 			sprintf(paste0("%.", digits, "f"), round(x$lower * scale, 2)),
	 			", ", 
	 			sprintf(paste0("%.", digits, "f"), round(x$upper * scale, 2)),
	 			")"), NA)
}

clean_rr.ci <- function(estimate, lower, upper, digits = 2) {
	ifelse(!is.na(lower), paste0(
		"(",
		sprintf(paste0("%.", digits, "f"), round(lower, digits)),
		", ",
		sprintf(paste0("%.", digits, "f"), round(upper, digits)),
		")"), NA)
}

mwf.flextable <- function(x) {
	flextable::compose(x, j = c(4, 6), value = as_paragraph(rep("(95% CI)", 2)),
		part = "header"
	) %>%
	border_remove() %>%
	hline_top(part = "header") %>%
	hline_top() %>% hline_bottom() %>%
	flextable::align(j = 2:6, align = "center", part = "all") %>%
	width(width = c(1.7, 1.1, 0.7, 1, 0.5, 1)) %>%
	padding(padding = 1.5, part = "all")
}
```

The observed risk of NHL over the 20-year follow-up period was 6.65 per 1000. Table 2 presents the hazard-extended ICE parametric g-formula estimates of the risk and risk ratios contrasting hypothetical limits on exposure to soluble MWF to no limit, with elimination of competing risks throughout. The estimated risk under no limit on MWF exposure was 9.56 (8.15, 10.89) per 1000. Stronger limits on average annual exposure to soluble MWFs resulted in monotonically stronger reductions in the risk of NHL. Capping average annual exposure to soluble MWFs at the NIOSH REL of 0.5 mg/m^3^ and a tenth of the REL resulted in a risk of 8.30 (6.52, 10.19) and 7.52 (5.73, 9.51) per 1000, respectively. The risk ratios contrasting these hypothetical limits to no limit were 0.87 (0.72, 1.02) and 0.79 (0.62, 0.97). Dynamic reductions in soluble exposure with the aim of limiting total MWF exposure to the REL and half the REL also yielded protective risk ratios: 0.84 (0.69, 0.99) and 0.80 (0.64, 0.98). These dynamic interventions attain risk reductions of similar magnitude as the static interventions enforcing exposure limits at 0.25 and 0.05 mg/m^3^, but do so while intervening on a smaller proportion of person-years.

Results for interventions on straight and synthetic MWF are presented in Tables S1 and S2 in the Appendix. The relative risks contrasting interventions on straight and synthetic MWF exposure to the natural course were much smaller in magnitude than those for soluble; none were statistically significant. Since exposure to soluble MWF was greatest in prevalence and magnitude, limits on soluble MWF would result in interventions on a greater percentage of person-years than limits on straight or synthetic MWF. The intervention capping average annual exposure to soluble MWF at the REL affected 23.8% of the person-years in the follow-up period. Limiting straight and synthetic MWF exposure to the REL affected 3.2% and 1.1% of the person-years under follow-up, respectively.

```{r, eval=F}
tikzDevice::tikz(here::here("reports/ACIC (2022)/poster/resources/rr.tex"),
								 width = 4, height = 1.75,
								 standAlone = T)
rr[grepl("sol|natural\\.natural", variable) & !grepl(
	"[a-z]", label),] %>% ggplot(
	aes(x = factor(label,
								 rev(c("0.5", "0.25", "0.05"))), y = estimate,
			ymin = lower, ymax = upper)
) +
	geom_errorbar(size = 0.5, width = 0.15, color = '#102451') +
	geom_point(size = 0.9, color = '#102451') + 
	geom_hline(yintercept = 1, lty = 2, color = '#102451', alpha = 0.7) + mytheme + labs(
	y = "Risk ratio",
	x = "Hypothetical limit (mg/m$^3$)"
) +
	coord_flip(ylim = c(0.5, 1.2)) +
	theme(panel.grid = element_blank())
dev.off()

lualatex(directory = here::here("reports/ACIC (2022)/poster/resources"))
```

```{r}
rr[grepl("sol|natural\\.natural", variable),.(
	 	label,
	 	`Person-years intervened (%)` = clean_percent_py(variable),
	 	`Risk per 1000` = clean_risk(variable, scale = 1000), # 34737),
	 	`(risk 95% CI)` = clean_risk.ci(variable, scale = 1000), # 34737),
	 	RR              = sprintf("%.2f", round(estimate, 2)),
	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
	 )][c(1, 2, 4, 3, 5, 6),] -> sol.tab

sol.tab %>% flextable %>%
	flextable::compose(j = 1, value = as_paragraph(
				"Exposure limit on soluble MWF (mg/m", as_sup("3"), ")"),
		part = "header"
	) %>% mwf.flextable %>%
	width(width = c(1.7, 1.1, 0.65, 1.1, 0.65, 0.9)) %>%
	add_footer_row(values = paste(
		"MWF: metalworking fluid;",
		"str: exposure to straight metalworking fluids;",
		"syn: exposure to synthetic metalworking fluids.",
		sep = "\n"), colwidths = 6) %>%
	hline_bottom(part = "footer") %>%
	set_caption(caption = "Counterfactual risks (per 1000)  and risk ratios contrasting interventions on soluble MWF to the observed course.")

```
\

```{r}
rr[grepl("str|natural\\.natural", variable),.(
	 	label,
	 	`Person-years intervened (%)` = clean_percent_py(variable),
	 	`Risk per 1000` = clean_risk(variable),
	 	`(risk 95% CI)` = clean_risk.ci(variable),
	 	RR              = sprintf("%.2f", round(estimate, 2)),
	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
	 )][c(1, 2, 4, 3, 5, 6),] -> str.tab

str.tab %>% flextable %>%
	flextable::compose(j = 1, value = as_paragraph(
				"Exposure limit on straight MWF (mg/m", as_sup("3"), ")"),
		part = "header"
	) %>% mwf.flextable %>%
	add_footer_row(values = paste(
		"MWF: metalworking fluid;",
		"sol: exposure to soluble metalworking fluids;",
		"syn: exposure to synthetic metalworking fluids.",
		sep = "\n"), colwidths = 6) %>%
	hline_bottom(part = "footer") %>%
	set_caption(caption = "Counterfactual risks (per 1000)  and risk ratios contrasting interventions on straight MWF to the observed course.") -> str.flextab
saveRDS(str.flextab, "str.flextab.rds")
```
\

```{r}
rr[grepl("syn|natural\\.natural", variable),.(
	 	label,
	 	`Person-years intervened (%)` = clean_percent_py(variable),
	 	`Risk per 1000` = clean_risk(variable),
	 	`(risk 95% CI)` = clean_risk.ci(variable),
	 	RR              = sprintf("%.2f", round(estimate, 2)),
	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
	 )][c(1, 2, 4, 3, 5, 6),] -> syn.tab

syn.tab %>% flextable %>%
	flextable::compose(j = 1, value = as_paragraph(
				"Exposure limit on synthetic MWF (mg/m", as_sup("3"), ")"),
		part = "header"
	) %>% mwf.flextable %>%
	add_footer_row(values = paste(
		"MWF: metalworking fluid;",
		"str: exposure to straight metalworking fluids;",
		"sol: exposure to soluble metalworking fluids.",
		sep = "\n"), colwidths = 6) %>%
	hline_bottom(part = "footer") %>%
	set_caption(caption = "Counterfactual risks (per 1000)  and risk ratios contrasting interventions on synthetic MWF to the observed course.") -> syn.flextab
saveRDS(syn.flextab, "syn.flextab.rds")
```

### 2022-06-03 reports/paper/04-discussion.rmd
Upload work

---
output:
  word_document:
    reference_docx: "~/HeadRs/rmd_templates/style-guide-arial-11.docx"
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
---

```{r, include=FALSE, eval=F}
knitr::opts_chunk$set(echo = F, results = 'asis',
											tab.cap.tnd = 1)
if (!'tidyr' %in% loadedNamespaces()) {library(tidyverse)}
library(flextable)
```

# Discussion

We estimated counterfactual 20-year risks of NHL from 1985 to 2005 in the UAW-GM  Cohort Study under different hypothetical interventions targeting exposure to soluble MWFs using the hazard-extended ICE parametric g-formula. We found a monotonic dose-dependent relationship with lower risk estimates arising from stronger limits. Contrasts in estimated NHL risk were statistically significant under the strongest static intervention, which limited soluble MWF exposure to 0.05 mg/m^3^, and the two dynamic interventions, which reduced exposure so that total MWF exposure would be capped at 0.5 or 0.25 mg/m^3^, if possible. The dynamic interventions, which take into consideration exposure to the other MWF types, may be more efficient at reducing risk of NHL than the static interventions, which ignore exposure to the other MWF types.

Colbeth et al. first reported an association between NHL and MWF exposure in this cohort in their standard survival analyses, which investigated associations between MWF exposure and several cancer incidence outcomes [@Colbeth_2022]. We verified and further examined this association in an approach capable of adjusting for time-varying confounding possibly affected by past exposure. The present approach also yielded marginal rather than conditional estimates of effect while evaluating realistic interventions, and is thus more compatible with a population health framework. Under the assumptions of conditional exchangeability, positivity, consistency, and correct model specification, our estimates are unbiased for the true counterfactual risk under the hypothetical interventions.

Conditional exchangeability means that for all time points, there is no confounding of the relationship between exposure/censoring and NHL status at all future time points given the observed past, including past exposure and covariates. A major threat to conditional exchangeability in longitudinal occupational studies is the HWSE. We limit potential bias due to the HWSE by conditioning on all past cumulative exposure, employment status, and cumulative time off at each time point. Cumulative time off and employment status are reasonable mediators of the causal paths linking past health to future exposure and health, but may not be sufficient to fully adjust for the HWSE. Declines in a worker's health may lead to reductions in work-related exposure without affecting employment status or time off work [@Garcia_2017]. We expect the absence of good time-varying measures of worker health over the life course to result in bias toward the null.

Positivity refers to the need for adequate variation in future exposure among strata formed by observed covariate and intervention-compliant exposure histories. Even under conditional exchangeability, where exposures within these strata may be considered the result of experimental assignment, expected counterfactual outcomes under different exposures may not be estimable if there is sparsity in the observed distribution of exposures [@Maldonado_2002]. We investigated static and dynamic stochastic interventions on soluble MWF exposure which intervened only when average annual exposure exceeded the hypothetical limit under consideration. Hence, our parameters of interest achieve positivity more easily than those for deterministic interventions e.g. setting all to exposed versus unexposed. Nonetheless, violations in positivity were still of concern due to the high dimensionality of covariates, as in common in longitudinal settings. We addressed sparsity by summarizing the 20 years of follow-up over a coarser timescale with only 8 follow-up periods and by representing covariates using fewer categories. Coarsening limits the comprehensiveness of confounding control, but improves positivity. In practice, causal inference using observational data must always balance positivity, covariate adjustment, and model specification [@Petersen_2012]. When estimating causal effects using estimators that do not require exposure modeling, as is the case with g-formula methods, concerns over potential bias due to practical violations in positivity may be relaxed if correct model specification is attained.

The consistency assumption, also known as the no-multiple-versions-of-treatment or stable unit treatment value assumption, is that counterfactual outcomes under each possible exposure value take on a unique value [@Cole_2009;@VanderWeele_2013]. This assumption would be violated if there were multiple versions of treatment causally associated with different outcomes. This basic notion of consistency is violated in our analysis because our exposure of interest is a complex mixture of diverse components with substantial variation over time due to changes in formulation and due to the natural physical, chemical, and biological changes in the MWF over the course of its use [@Howell_2006]. However, causal effects estimates under violations in the consistency assumption are still valid and unbiased if there is adequate adjustment for confounders of the exposure-version relationship [@VanderWeele_2013]. This may be thought of as conditional consistency within strata, in which there is only one version of treatment. Our analysis indexed time periods over calendar time and adjusted for age, year of hire, and plant. In this way, we limited potential for bias due to variation in MWF composition.

Correct model specification is a standard assumption in all analyses. The estimator we applied offers greater statistical efficiency than the classical ICE parametric g-formula estimator because it leverages greater parametric smoothing. In causal analyses of longitudinal cohort studies, both the hazard-extended and classical ICE parametric g-formula estimators are less common than the non-iterative expression (NICE) of the parametric g-formula [@Keil_2014]. However, a major limitation of the NICE g-formula is the g-null paradox: the guaranteed misspecification of parametric models resulting in the false rejection of the null hypothesis when the null is true and there is time-varying confounding affected by past exposure [@Naimi_2015;@McGrath_2022]. As with all ICE g-formula estimators, the estimator we applied is not subject to the g-null paradox. Furthermore, simulation studies show that the variance of the hazard-extended ICE parametric g-formula is similar to that of the NICE parametric g-formula, so we expect the former to be no less conservative than the latter [@Wen_2020].

<!-- In the last several decades, there have been substantial changes in the formulation of MWF, including the exclusion of nitrogenous compounds and the use of highly-refined mineral oils. The recent establishment of the Ecolabel for lubricants in the European Union reflects the shift toward prioritizing sustainability and health in the design and production of MWF and other lubricants [@EU_2018;@Skerlos_2008]. However, water-based MWF that satisfy Ecolabel criteria are nonetheless susceptible to the accumulation of dirt, metals, microbes, products of microbial metabolism, and unemulsified oil. These contaminants and their control strategies may also induce risks to human health. Furthermore, adoption of this new class of MWF remains limited, as is evidence of their safety. Considering the evolving complexity in MWF composition, epidemiologic investigations remain an invaluable approach for developing evidence-based occupational health policy and estimating their causal effect. -->

Much of the existing epidemiologic literature linking occupational and environmental exposures to NHL risk report findings from case-control studies where exposures are measured crudely as binary indicators of exposure or membership in a particular occupational group [@Cano_2001;@Costantini_2001;@Karunanayake_2008;@t-Mannetje_2016]. Associations between occupations and NHL risk vary considerably, but one study of working men in Kansas and Nebraska found strong associations between NHL risk and occupations involving metalworking and motor vehicles [@Zheng_2002]. Both of these occupations may entail exposure to soluble MWFs, which contain a number of additives of concern for human health and NHL risk in particular. Organic compounds containing phosphorous, chlorine, sulfur, nitrogen, and boron are commonly added to soluble MWF to control microbial growth, improve performance under high heat/pressure, and inhibit corrosion [@Evans_2020]. Organophosphorous compounds include organophosphate pesticides, which have been linked to cancer risk in epidemiologic and animal studies. Some were classified as possibly carcinogenic by the IARC [@IARC_2017]. Studies of occupational exposure to chlorinated solvents and pesticides have also been linked to NHL risk [@Cocco_2008;@Purdue_2011;@Cocco_2013;@Vlaanderen_2013;@Callahan_2018]. In 2014, the International Agency for Research on Cancer classified trichloroethylene, tetrachloroethylene, and other chlorinated agents as Group 1 carcinogens [@IARC_2014]. Chlorinated solvents are commonly used as degreasers in industrial settings, but their use in the plants under study here was uncommon and limited to particular operations [@Shrestha_2016]. The structural characteristics shared by MWF additives and known/suspected carcinogens suggest similarities in molecular function and carcinogenesis.

This study investigated the effect of hypothetical limits on average annual exposure to MWF by comparing the standardized distribution of NHL under various distributions of cumulative exposure induced by applying upper bounds to annual exposure. When average annual exposure did not exceed the hypothetical limit, it was left at the observed level of exposure. We selected these hypothetical limits based on the NIOSH REL of 0.5 mg/m^3^ [@niosh_1998]. Without enforcement of the REL, we still observed average annual exposures below the REL for many person-years. If the REL were enforced in the real world, we would not expect reductions in exposure for these low-exposure person-years. Hence, contrasting the counterfactual scenario where all workers experienced annual exposure at the REL to one where all workers experienced annual exposure at some higher level would result in an overestimate of the expected real-world benefit of REL enforcement. By considering stochastic interventions that result in exposure distributions more similar to what we would expect in the real world, our analysis yielded results that more realistically quantify the effects of policy than those investigating deterministic interventions [@Bembom_2007;@Munoz_2012].

<!-- The interventions we considered are stochastic interventions resulting in post-intervention distributions of exposure that better reflect what we would expect if exposure limits were enforced in the real world. The interventions which ignore exposure to straight and synthetic MWFs are static. The interventions which reduce exposure to soluble MWF by a quantity determined by exposure to other MWF are dynamic. The dynamic stochastic interventions respect the fact that the REL is for total MWF, not just soluble MWF. If an individual experienced a large amount of exposure to straight and synthetic MWF in one year, then their exposure to soluble MWF should be bounded at a lower level so that the sum of their exposure to soluble, straight, and synthetic MWFs is no greater than the hypothetical limit.  -->

Associations between several occupations and risk of NHL have been reported previously, but none evaluated the potential effect of hypothetical limits on occupational exposures [@Ekstrom-Smedby_2006;@Chiu_2015;@t-Mannetje_2016;@Callahan_2018]. We found evidence that exposure to soluble MWF was associated with NHL incidence after adjustment for time-varying confounding affected by prior exposure using the hazard-extended ICE parametric g-formula. Shifting the distribution of cumulative exposure to soluble MWF by limiting average annual exposure resulted in reductions in NHL incidence. Limits on exposure to soluble MWF that take into consideration exposure to straight and synthetic MWFs led to greater reductions NHL incidence while intervening on fewer person-years.

### 2022-06-03 reports/paper/05-appendix.rmd
Upload work

---
output:
  pdf_document:
    keep_tex: true
header-includes:
- \usepackage{longtable}
- \usepackage{setspace}\onehalfspacing
- \usepackage{verbatim}
- \usepackage{framed}
- \usepackage{pgf}
- \usepackage{pgfplots}
- \pgfplotsset{compat=1.17}
- \usepackage{tikz}
- \usetikzlibrary{graphs, arrows, automata, positioning, decorations}
- \tikzset{invisible/.style={opacity=0}, visible on/.style={alt={#1{}{invisible}}}, alt/.code args={<#1>#2#3}{\alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}}},}
- \usepackage{textgreek}
- \usepackage{framed}
- \usepackage{xcolor}
- \renewenvironment{quote}{\begin{minipage}{\linewidth}\colorlet{shadecolor}{orange!15}\begin{snugshade}}{\end{snugshade}\end{minipage}}
- \usepackage{booktabs}
- \usepackage{adjustbox}
- \newcommand{\ind}{\perp\mkern-10mu\perp}
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
csl: "`r path.expand('~/HeadRs/csl/asa.csl')`"
---

```{=tex}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\arraystretch}{1}
```

```{r, include=FALSE}
knitr::opts_chunk$set(
	echo = F, results = 'asis',
	warning = F,
	tab.cap.tnd = 1,
	ft.arraystretch = 1.15)
if (!'tidyr' %in% loadedNamespaces()) {library(tidyverse)}
library(flextable)
```

# Appendix

```{r, tab.cap.pre="Table A"}
str.flextab <- readRDS("str.flextab.rds")
str.flextab
```

```{r}
syn.flextab <- readRDS("syn.flextab.rds")
syn.flextab
```

### 2022-06-03 reports/paper/05-appendix.tex
Upload work

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{longtable}
\usepackage{setspace}\onehalfspacing
\usepackage{verbatim}
\usepackage{framed}
\usepackage{pgf}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}
\usepackage{tikz}
\usetikzlibrary{graphs, arrows, automata, positioning, decorations}
\tikzset{invisible/.style={opacity=0}, visible on/.style={alt={#1{}{invisible}}}, alt/.code args={<#1>#2#3}{\alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}}},}
\usepackage{textgreek}
\usepackage{framed}
\usepackage{xcolor}
\renewenvironment{quote}{\begin{minipage}{\linewidth}\colorlet{shadecolor}{orange!15}\begin{snugshade}}{\end{snugshade}\end{minipage}}
\usepackage{booktabs}
\usepackage{adjustbox}
\newcommand{\ind}{\perp\mkern-10mu\perp}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\arraystretch}{1}

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{1.15}

\begin{longtable}[c]{|p{1.70in}|p{1.10in}|p{0.70in}|p{1.00in}|p{0.50in}|p{1.00in}}

\caption{Counterfactual risks (per 1000)  and risk ratios contrasting interventions on straight MWF to the observed course.
}\\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exposure\ limit\ on\ straight\ MWF\ (mg/m}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{3}}}\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Person-years\ intervened\ (\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Risk\ per\ 1000}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(95\%\ CI)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{RR}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(95\%\ CI)}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exposure\ limit\ on\ straight\ MWF\ (mg/m}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{3}}}\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Person-years\ intervened\ (\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Risk\ per\ 1000}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(95\%\ CI)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{RR}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(95\%\ CI)}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}\endhead

\multicolumn{6}{!{\color[HTML]{FFFFFF}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+10\tabcolsep+5\arrayrulewidth}!{\color[HTML]{FFFFFF}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{MWF:\ metalworking\ fluid;\linebreak sol:\ exposure\ to\ soluble\ metalworking\ fluids;\linebreak syn:\ exposure\ to\ synthetic\ metalworking\ fluids.}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}\endfoot

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{None}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.56}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(8.15,\ 10.89)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.00}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.5}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3.2}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.63}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(8.16,\ 10.99)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.01}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.96,\ 1.06)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.25}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{8.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.84}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(8.27,\ 11.33)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.03}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.96,\ 1.10)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.05}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{26.3}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{10.12}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(8.00,\ 12.19)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.06}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.91,\ 1.21)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{max(0,\ 0.5\ -\ sol\ -\ syn)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{19.1}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.69}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(7.90,\ 11.51)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.01}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.90,\ 1.14)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{max(0,\ 0.25\ -\ sol\ -\ syn)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{32.5}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.62}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(7.73,\ 11.61)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.01}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.87,\ 1.15)}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\end{longtable}

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{1.15}

\begin{longtable}[c]{|p{1.70in}|p{1.10in}|p{0.70in}|p{1.00in}|p{0.50in}|p{1.00in}}

\caption{Counterfactual risks (per 1000)  and risk ratios contrasting interventions on synthetic MWF to the observed course.
}\\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exposure\ limit\ on\ synthetic\ MWF\ (mg/m}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{3}}}\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Person-years\ intervened\ (\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Risk\ per\ 1000}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(95\%\ CI)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{RR}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(95\%\ CI)}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exposure\ limit\ on\ synthetic\ MWF\ (mg/m}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{3}}}\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Person-years\ intervened\ (\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Risk\ per\ 1000}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(95\%\ CI)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{RR}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(95\%\ CI)}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}\endhead

\multicolumn{6}{!{\color[HTML]{FFFFFF}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+10\tabcolsep+5\arrayrulewidth}!{\color[HTML]{FFFFFF}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{MWF:\ metalworking\ fluid;\linebreak str:\ exposure\ to\ straight\ metalworking\ fluids;\linebreak sol:\ exposure\ to\ soluble\ metalworking\ fluids.}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}\endfoot

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{None}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.56}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(8.15,\ 10.89)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.00}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.5}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.1}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.73}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(8.30,\ 11.11)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.02}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.99,\ 1.05)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.25}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3.9}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.52}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(8.11,\ 10.90)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.00}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.96,\ 1.03)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.05}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{12.7}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{8.95}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(7.46,\ 10.39)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.94}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.87,\ 1.01)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{max(0,\ 0.5\ -\ str\ -\ sol)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.9}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(7.96,\ 10.95)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0.99}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.93,\ 1.06)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{max(0,\ 0.25\ -\ str\ -\ sol)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{17.1}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.7in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9.60}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(8.01,\ 11.15)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1.00}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{(0.92,\ 1.09)}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\end{longtable}

\end{document}

### 2022-06-03 reports/paper/paper.Rmd
Upload work

---
# fontsize: 11pt
# mainfont: arial
output:
  # pdf_document:
  #   fig_caption: true
  #   latex_engine: lualatex
  #   includes:
  #     in_header: "~/HeadRs/Stathead.sty"
  #   keep_tex: true
  bookdown::word_document2:
    number_sections: false
    global_numbering: true
    reference_docx: "~/HeadRs/rmd_templates/style-guide-arial-11.docx"
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
---

\fancyhead[R]{}
\fancyhead[L]{}
\renewcommand{\headrulewidth}{0pt}
\singlespacing

\thispagestyle{empty}

\setlength{\columnseprule}{0pt}

```{r, include=FALSE}
knitr::opts_chunk$set(echo=F, results = 'asis')
library(bibtex)
biblio <- bibtex::read.bib('~/Box Sync/papers/EnvEpi.bib')
```

**Type of manuscript:** Original Research Article

**Manuscript title:** Evaluating hypothetical limits on metalworking fluid exposure for reducing non-Hodgkin lymphoma incidence: An application of the hazard-extended iterative conditional expectation parametric g-formula

**Authors:** Kevin T. Chen,^a,b^, Sally Picciotto^b^, Ellen A. Eisen^b^

^a^ University of California, Berkeley School of Public Health, Division of Epidemiology \& Biostatistics

^b^ University of California, Berkeley School of Public Health, Division of Environmental Health Sciences

**Corresponding author:**\
Kevin T. Chen\
2121 Berkeley Way\
Room 5302, Desk 5305-1\
Berkeley, CA 94720-7360\
kevchen@berkeley.edu\
(510) 387-3327

**Running head suggestion:** Limits on metalworking fluid for preventing NHL

**Conflicts of interests:** Authors declare no conflicts of interest

**Sources of financial support:** Supported by Training Grant T42OH008429, funded by the National Institute for Occupational Safety and Health (NIOSH) / Centers for Disease Control and Prevention (CDC)

**Data and computing code:**

\newpage

# Abstract (250 words)

**Background:** The second half of the 20th century saw a fourfold rise in non-Hodgkin lymphoma (NHL) incidence. Over the same period, concerns about the carcinogenicity of oil-based metalworking fluids (MWF) in automobile manufacturing fueled a transition to water-based soluble MWF. Soluble MWF, a complex mixture of diverse chemical additives, has become the most widely used class of MWF in the industry. We estimated the effect of limiting annual exposure to soluble MWF on NHL incidence in the United Auto Workers-General Motors (UAW-GM) Cohort Study (n = 33,138). We based our hypothetical interventions on the NIOSH recommended exposure limit (REL) of 0.5 mg/m3 for total MWF particulate mass.

**Methods:** We estimated counterfactual cumulative incidence of NHL from 1985 to 2004 in the UAW-GM cohort of hourly autoworkers ever employed at 3 Michigan plants for at least 3 years. Using the hazard-extended iterative conditional expectation g-computation, we adjusted for time-varying confounding and censoring affected by prior exposure. We contrasted counterfactual cumulative incidence under no intervention on exposure to when annual soluble exposure was capped at the REL, half the REL, and a tenth of the REL. Confidence intervals were computed using the nonparametric bootstrap.

Results: There were 211 NHL cases during the follow-up period. Lower annual soluble exposure resulted in lower cumulative incidence of NHL. The risk ratio when capping soluble exposure at the REL compared to no intervention was 0.90 (95% CI: 0.78, 1.03). The corresponding difference in cumulative incidence was -28 cases (95%CI: -63, 8 cases). Capping soluble exposure at a tenth of the REL resulted in a risk ratio of 0.84 (95% CI: 0.68, 1.00) and a difference in cumulative incidence of -45 cases (95%CI: -88, 1 case).
Conclusion: The current REL was based on evidence linking MWF exposure to respiratory and skin diseases, rather than cancer, and may not be adequate to prevent NHL in exposed autoworkers.

# What this study adds (100 words)

\newpage

```{r child = '01-introduction.rmd'}
```

```{r child = '02-methods.rmd'}
```

```{r child = '03-results.rmd'}
```

```{r child = '04-discussion.rmd'}
```

\newpage

# Citations

<div id="refs"></div>

### 2022-06-03 resources/exposure.tex
Upload work

% Created by tikzDevice version 0.12.3.1 on 2022-04-22 17:18:12
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,180.67);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 25.15, 28.21) rectangle (155.80,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.15, 28.21) rectangle (155.80,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15, 56.10) --
	(155.80, 56.10);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,101.47) --
	(155.80,101.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,146.83) --
	(155.80,146.83);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.63, 28.21) --
	( 48.63,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 75.63, 28.21) --
	( 75.63,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (102.62, 28.21) --
	(102.62,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.62, 28.21) --
	(129.62,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 33.42) --
	(155.80, 33.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 78.78) --
	(155.80, 78.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,124.15) --
	(155.80,124.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14, 28.21) --
	( 35.14,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.13, 28.21) --
	( 62.13,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.13, 28.21) --
	( 89.13,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.12, 28.21) --
	(116.12,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.12, 28.21) --
	(143.12,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14,116.20) --
	( 36.49,154.33) --
	( 37.83,144.98) --
	( 39.18,118.42) --
	( 40.53,121.74) --
	( 41.88,121.74) --
	( 43.23,122.07) --
	( 44.58,133.91) --
	( 45.93,153.22) --
	( 47.28,154.33) --
	( 48.63,154.33) --
	( 49.98,156.14) --
	( 51.33,154.33) --
	( 52.68,133.91) --
	( 54.03,154.33) --
	( 55.38,156.14) --
	( 56.73,156.14) --
	( 58.08,156.14) --
	( 59.43,133.91) --
	( 60.78,154.33) --
	( 62.13,145.58) --
	( 63.48,141.88) --
	( 64.83,120.02) --
	( 66.18,133.91) --
	( 67.53,134.46) --
	( 68.88,122.01) --
	( 70.23, 94.47) --
	( 71.58,103.66) --
	( 72.93, 95.01) --
	( 74.28, 94.47) --
	( 75.63, 92.26) --
	( 76.98, 92.10) --
	( 78.33, 83.33) --
	( 79.68, 83.33) --
	( 81.03, 85.43) --
	( 82.38, 85.43) --
	( 83.73, 83.33) --
	( 85.08, 85.43) --
	( 86.43, 80.26) --
	( 87.78, 83.77) --
	( 89.13, 87.97) --
	( 90.48, 84.75) --
	( 91.83, 90.01) --
	( 93.18, 90.64) --
	( 94.53, 87.88) --
	( 95.87, 86.46) --
	( 97.22, 85.35) --
	( 98.57, 83.33) --
	( 99.92, 83.33) --
	(101.27, 85.19) --
	(102.62, 52.02) --
	(103.97, 52.30) --
	(105.32, 50.60) --
	(106.67, 50.94) --
	(108.02, 47.63) --
	(109.37, 48.18) --
	(110.72, 49.42) --
	(112.07, 49.79) --
	(113.42, 49.46) --
	(114.77, 49.79) --
	(116.12, 44.84) --
	(117.47, 46.82) --
	(118.82, 43.96) --
	(120.17, 44.33) --
	(121.52, 48.46) --
	(122.87, 46.75) --
	(124.22, 44.89) --
	(125.57, 44.67) --
	(126.92, 43.52) --
	(128.27, 43.38) --
	(129.62, 43.35) --
	(130.97, 42.97) --
	(132.32, 42.70) --
	(133.67, 41.95) --
	(135.02, 39.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15, 28.21) rectangle (155.80,162.23);
\end{scope}
\begin{scope}
\path[clip] (161.30, 28.21) rectangle (291.96,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (161.30, 28.21) rectangle (291.96,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30, 56.10) --
	(291.96, 56.10);

\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30,101.47) --
	(291.96,101.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30,146.83) --
	(291.96,146.83);

\path[draw=drawColor,line width= 0.3pt,line join=round] (184.79, 28.21) --
	(184.79,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (211.79, 28.21) --
	(211.79,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (238.78, 28.21) --
	(238.78,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (265.78, 28.21) --
	(265.78,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30, 33.42) --
	(291.96, 33.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30, 78.78) --
	(291.96, 78.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30,124.15) --
	(291.96,124.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] (171.29, 28.21) --
	(171.29,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.29, 28.21) --
	(198.29,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.28, 28.21) --
	(225.28,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.28, 28.21) --
	(252.28,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (279.27, 28.21) --
	(279.27,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (171.29, 38.43) --
	(172.64, 41.00) --
	(173.99, 44.55) --
	(175.34, 41.44) --
	(176.69, 41.41) --
	(178.04, 43.59) --
	(179.39, 39.58) --
	(180.74, 45.48) --
	(182.09, 46.31) --
	(183.44, 48.44) --
	(184.79, 44.69) --
	(186.14, 48.44) --
	(187.49, 48.44) --
	(188.84, 40.74) --
	(190.19, 43.24) --
	(191.54, 44.57) --
	(192.89, 44.87) --
	(194.24, 48.44) --
	(195.59, 39.48) --
	(196.94, 48.44) --
	(198.29, 42.04) --
	(199.64, 51.78) --
	(200.99, 48.44) --
	(202.34, 51.09) --
	(203.69, 51.78) --
	(205.04, 47.41) --
	(206.39, 54.88) --
	(207.74, 57.99) --
	(209.09, 52.89) --
	(210.44, 53.09) --
	(211.79, 51.22) --
	(213.14, 43.75) --
	(214.49, 39.34) --
	(215.84, 38.74) --
	(217.19, 39.51) --
	(218.53, 39.79) --
	(219.88, 39.48) --
	(221.23, 39.48) --
	(222.58, 38.45) --
	(223.93, 40.70) --
	(225.28, 40.77) --
	(226.63, 39.48) --
	(227.98, 43.17) --
	(229.33, 43.78) --
	(230.68, 43.24) --
	(232.03, 43.81) --
	(233.38, 43.81) --
	(234.73, 43.81) --
	(236.08, 43.81) --
	(237.43, 43.81) --
	(238.78, 39.57) --
	(240.13, 40.14) --
	(241.48, 40.57) --
	(242.83, 39.42) --
	(244.18, 37.52) --
	(245.53, 37.52) --
	(246.88, 36.98) --
	(248.23, 36.49) --
	(249.58, 36.49) --
	(250.93, 36.49) --
	(252.28, 36.49) --
	(253.63, 36.49) --
	(254.98, 36.07) --
	(256.33, 36.38) --
	(257.68, 36.49) --
	(259.03, 36.49) --
	(260.38, 37.34) --
	(261.73, 37.85) --
	(263.08, 37.83) --
	(264.43, 37.00) --
	(265.78, 37.55) --
	(267.13, 37.79) --
	(268.48, 37.52) --
	(269.83, 37.68) --
	(271.18, 36.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (161.30, 28.21) rectangle (291.96,162.23);
\end{scope}
\begin{scope}
\path[clip] (297.46, 28.21) rectangle (428.12,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (297.46, 28.21) rectangle (428.12,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46, 56.10) --
	(428.12, 56.10);

\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46,101.47) --
	(428.12,101.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46,146.83) --
	(428.12,146.83);

\path[draw=drawColor,line width= 0.3pt,line join=round] (320.95, 28.21) --
	(320.95,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (347.94, 28.21) --
	(347.94,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (374.94, 28.21) --
	(374.94,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (401.93, 28.21) --
	(401.93,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46, 33.42) --
	(428.12, 33.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46, 78.78) --
	(428.12, 78.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46,124.15) --
	(428.12,124.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] (307.45, 28.21) --
	(307.45,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (334.45, 28.21) --
	(334.45,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.44, 28.21) --
	(361.44,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (388.44, 28.21) --
	(388.44,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (415.43, 28.21) --
	(415.43,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (308.80, 44.87) --
	(310.15, 44.87) --
	(311.50, 44.87) --
	(312.85, 42.13) --
	(314.20, 42.13) --
	(315.55, 44.87) --
	(316.90, 44.87) --
	(318.25, 44.27) --
	(319.60, 42.32) --
	(320.95, 48.60) --
	(322.30, 50.46) --
	(323.65, 69.90) --
	(325.00, 69.90) --
	(326.35, 69.90) --
	(327.70, 42.93) --
	(329.05, 42.93) --
	(330.40, 50.03) --
	(331.75,116.91) --
	(333.10,120.23) --
	(334.45, 42.93) --
	(335.80, 42.93) --
	(337.15, 64.53) --
	(338.50, 76.72) --
	(339.85, 64.53) --
	(341.19, 53.70) --
	(342.54, 64.53) --
	(343.89, 53.70) --
	(345.24, 43.76) --
	(346.59, 43.30) --
	(347.94, 40.78) --
	(349.29, 50.31) --
	(350.64, 51.13) --
	(351.99, 38.87) --
	(353.34, 38.87) --
	(354.69, 39.55) --
	(356.04, 38.90) --
	(357.39, 40.47) --
	(358.74, 38.87) --
	(360.09, 38.87) --
	(361.44, 38.93) --
	(362.79, 38.87) --
	(364.14, 38.87) --
	(365.49, 38.88) --
	(366.84, 39.40) --
	(368.19, 40.34) --
	(369.54, 39.02) --
	(370.89, 40.49) --
	(372.24, 40.05) --
	(373.59, 41.08) --
	(374.94, 35.04) --
	(376.29, 35.19) --
	(377.64, 35.19) --
	(378.99, 35.03) --
	(380.34, 34.30) --
	(381.69, 34.31) --
	(383.04, 34.53) --
	(384.39, 34.50) --
	(385.74, 34.43) --
	(387.09, 34.76) --
	(388.44, 34.80) --
	(389.79, 34.95) --
	(391.14, 34.71) --
	(392.49, 34.93) --
	(393.84, 35.19) --
	(395.19, 35.19) --
	(396.54, 36.02) --
	(397.89, 36.03) --
	(399.23, 36.02) --
	(400.58, 35.81) --
	(401.93, 36.04) --
	(403.28, 35.88) --
	(404.63, 35.23) --
	(405.98, 36.84) --
	(407.33, 35.58);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.46, 28.21) rectangle (428.12,162.23);
\end{scope}
\begin{scope}
\path[clip] ( 25.15,162.23) rectangle (155.80,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,162.23) rectangle (155.80,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 90.48,165.60) {Soluble};
\end{scope}
\begin{scope}
\path[clip] (161.30,162.23) rectangle (291.96,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (161.30,162.23) rectangle (291.96,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (226.63,165.60) {Straight};
\end{scope}
\begin{scope}
\path[clip] (297.46,162.23) rectangle (428.12,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (297.46,162.23) rectangle (428.12,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (362.79,165.60) {Synthetic};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14, 25.46) --
	( 35.14, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.13, 25.46) --
	( 62.13, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.13, 25.46) --
	( 89.13, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.12, 25.46) --
	(116.12, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.12, 25.46) --
	(143.12, 28.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 35.14, 17.75) {1920};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 62.13, 17.75) {1940};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 89.13, 17.75) {1960};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (116.12, 17.75) {1980};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (143.12, 17.75) {2000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (171.29, 25.46) --
	(171.29, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.29, 25.46) --
	(198.29, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.28, 25.46) --
	(225.28, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.28, 25.46) --
	(252.28, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (279.27, 25.46) --
	(279.27, 28.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (171.29, 17.75) {1920};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (198.29, 17.75) {1940};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (225.28, 17.75) {1960};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (252.28, 17.75) {1980};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (279.27, 17.75) {2000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (307.45, 25.46) --
	(307.45, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (334.45, 25.46) --
	(334.45, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.44, 25.46) --
	(361.44, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (388.44, 25.46) --
	(388.44, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (415.43, 25.46) --
	(415.43, 28.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (307.45, 17.75) {1920};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (334.45, 17.75) {1940};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (361.44, 17.75) {1960};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (388.44, 17.75) {1980};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (415.43, 17.75) {2000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 30.66) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 76.03) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,121.39) {2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 33.42) --
	( 25.15, 33.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 78.78) --
	( 25.15, 78.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,124.15) --
	( 25.15,124.15);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (226.63,  7.25) {Calendar year};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70, 95.22) {Median exposure (mg/m$^3$) among exposed};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-06-03 resources/exposure_long.tex
Upload work

% Created by tikzDevice version 0.12.3.1 on 2022-05-11 14:49:57
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (216.81,397.48);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (216.81,397.48);
\end{scope}
\begin{scope}
\path[clip] ( 25.15,274.39) rectangle (211.31,379.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.15,274.39) rectangle (211.31,379.04);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,296.17) --
	(211.31,296.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,331.59) --
	(211.31,331.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,367.02) --
	(211.31,367.02);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 58.61,274.39) --
	( 58.61,379.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 97.07,274.39) --
	( 97.07,379.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (135.54,274.39) --
	(135.54,379.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (174.00,274.39) --
	(174.00,379.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,278.46) --
	(211.31,278.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,313.88) --
	(211.31,313.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,349.30) --
	(211.31,349.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38,274.39) --
	( 39.38,379.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.84,274.39) --
	( 77.84,379.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.31,274.39) --
	(116.31,379.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.77,274.39) --
	(154.77,379.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.23,274.39) --
	(193.23,379.04);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38,343.10) --
	( 41.30,372.87) --
	( 43.22,365.57) --
	( 45.15,344.83) --
	( 47.07,347.42) --
	( 48.99,347.42) --
	( 50.92,347.68) --
	( 52.84,356.93) --
	( 54.76,372.01) --
	( 56.69,372.87) --
	( 58.61,372.87) --
	( 60.53,374.28) --
	( 62.46,372.87) --
	( 64.38,356.93) --
	( 66.30,372.87) --
	( 68.23,374.28) --
	( 70.15,374.28) --
	( 72.07,374.28) --
	( 74.00,356.93) --
	( 75.92,372.87) --
	( 77.84,366.04) --
	( 79.77,363.15) --
	( 81.69,346.08) --
	( 83.61,356.93) --
	( 85.53,357.36) --
	( 87.46,347.63) --
	( 89.38,326.13) --
	( 91.30,333.31) --
	( 93.23,326.55) --
	( 95.15,326.13) --
	( 97.07,324.41) --
	( 99.00,324.28) --
	(100.92,317.43) --
	(102.84,317.43) --
	(104.77,319.07) --
	(106.69,319.07) --
	(108.61,317.43) --
	(110.54,319.07) --
	(112.46,315.04) --
	(114.38,317.78) --
	(116.31,321.06) --
	(118.23,318.54) --
	(120.15,322.65) --
	(122.07,323.14) --
	(124.00,320.99) --
	(125.92,319.88) --
	(127.84,319.01) --
	(129.77,317.43) --
	(131.69,317.43) --
	(133.61,318.88) --
	(135.54,292.99) --
	(137.46,293.20) --
	(139.38,291.87) --
	(141.31,292.14) --
	(143.23,289.56) --
	(145.15,289.99) --
	(147.08,290.95) --
	(149.00,291.24) --
	(150.92,290.98) --
	(152.85,291.24) --
	(154.77,287.38) --
	(156.69,288.92) --
	(158.62,286.69) --
	(160.54,286.98) --
	(162.46,290.20) --
	(164.38,288.87) --
	(166.31,287.41) --
	(168.23,287.24) --
	(170.15,286.34) --
	(172.08,286.23) --
	(174.00,286.21) --
	(175.92,285.91) --
	(177.85,285.70) --
	(179.77,285.12) --
	(181.69,282.88);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15,274.39) rectangle (211.31,379.04);
\end{scope}
\begin{scope}
\path[clip] ( 25.15,151.30) rectangle (211.31,255.95);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.15,151.30) rectangle (211.31,255.95);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,173.08) --
	(211.31,173.08);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,208.50) --
	(211.31,208.50);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,243.93) --
	(211.31,243.93);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 58.61,151.30) --
	( 58.61,255.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 97.07,151.30) --
	( 97.07,255.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] (135.54,151.30) --
	(135.54,255.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] (174.00,151.30) --
	(174.00,255.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,155.37) --
	(211.31,155.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,190.79) --
	(211.31,190.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,226.21) --
	(211.31,226.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38,151.30) --
	( 39.38,255.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.84,151.30) --
	( 77.84,255.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.31,151.30) --
	(116.31,255.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.77,151.30) --
	(154.77,255.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.23,151.30) --
	(193.23,255.95);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38,159.28) --
	( 41.30,161.29) --
	( 43.22,164.06) --
	( 45.15,161.63) --
	( 47.07,161.61) --
	( 48.99,163.31) --
	( 50.92,160.18) --
	( 52.84,164.79) --
	( 54.76,165.43) --
	( 56.69,167.10) --
	( 58.61,164.17) --
	( 60.53,167.10) --
	( 62.46,167.10) --
	( 64.38,161.09) --
	( 66.30,163.03) --
	( 68.23,164.08) --
	( 70.15,164.31) --
	( 72.07,167.10) --
	( 74.00,160.10) --
	( 75.92,167.10) --
	( 77.84,162.10) --
	( 79.77,169.71) --
	( 81.69,167.10) --
	( 83.61,169.16) --
	( 85.53,169.71) --
	( 87.46,166.30) --
	( 89.38,172.13) --
	( 91.30,174.56) --
	( 93.23,170.57) --
	( 95.15,170.73) --
	( 97.07,169.26) --
	( 99.00,163.43) --
	(100.92,159.99) --
	(102.84,159.53) --
	(104.77,160.13) --
	(106.69,160.34) --
	(108.61,160.10) --
	(110.54,160.10) --
	(112.46,159.30) --
	(114.38,161.05) --
	(116.31,161.11) --
	(118.23,160.10) --
	(120.15,162.98) --
	(122.07,163.46) --
	(124.00,163.03) --
	(125.92,163.48) --
	(127.84,163.48) --
	(129.77,163.48) --
	(131.69,163.48) --
	(133.61,163.48) --
	(135.54,160.17) --
	(137.46,160.62) --
	(139.38,160.95) --
	(141.31,160.05) --
	(143.23,158.57) --
	(145.15,158.57) --
	(147.08,158.15) --
	(149.00,157.76) --
	(150.92,157.76) --
	(152.85,157.76) --
	(154.77,157.76) --
	(156.69,157.76) --
	(158.62,157.44) --
	(160.54,157.68) --
	(162.46,157.76) --
	(164.38,157.76) --
	(166.31,158.43) --
	(168.23,158.83) --
	(170.15,158.81) --
	(172.08,158.16) --
	(174.00,158.59) --
	(175.92,158.78) --
	(177.85,158.57) --
	(179.77,158.70) --
	(181.69,158.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15,151.30) rectangle (211.31,255.95);
\end{scope}
\begin{scope}
\path[clip] ( 25.15, 28.21) rectangle (211.31,132.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.15, 28.21) rectangle (211.31,132.86);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15, 49.99) --
	(211.31, 49.99);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15, 85.41) --
	(211.31, 85.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,120.84) --
	(211.31,120.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 58.61, 28.21) --
	( 58.61,132.86);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 97.07, 28.21) --
	( 97.07,132.86);

\path[draw=drawColor,line width= 0.3pt,line join=round] (135.54, 28.21) --
	(135.54,132.86);

\path[draw=drawColor,line width= 0.3pt,line join=round] (174.00, 28.21) --
	(174.00,132.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 32.28) --
	(211.31, 32.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 67.70) --
	(211.31, 67.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,103.12) --
	(211.31,103.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38, 28.21) --
	( 39.38,132.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.84, 28.21) --
	( 77.84,132.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.31, 28.21) --
	(116.31,132.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.77, 28.21) --
	(154.77,132.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.23, 28.21) --
	(193.23,132.86);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.30, 41.22) --
	( 43.22, 41.22) --
	( 45.15, 41.22) --
	( 47.07, 39.08) --
	( 48.99, 39.08) --
	( 50.92, 41.22) --
	( 52.84, 41.22) --
	( 54.76, 40.75) --
	( 56.69, 39.23) --
	( 58.61, 44.13) --
	( 60.53, 45.59) --
	( 62.46, 60.76) --
	( 64.38, 60.76) --
	( 66.30, 60.76) --
	( 68.23, 39.70) --
	( 70.15, 39.70) --
	( 72.07, 45.25) --
	( 74.00, 97.47) --
	( 75.92,100.06) --
	( 77.84, 39.70) --
	( 79.77, 39.70) --
	( 81.69, 56.57) --
	( 83.61, 66.09) --
	( 85.53, 56.57) --
	( 87.46, 48.11) --
	( 89.38, 56.57) --
	( 91.30, 48.11) --
	( 93.23, 40.35) --
	( 95.15, 39.99) --
	( 97.07, 38.02) --
	( 99.00, 45.46) --
	(100.92, 46.11) --
	(102.84, 36.53) --
	(104.77, 36.53) --
	(106.69, 37.07) --
	(108.61, 36.56) --
	(110.54, 37.79) --
	(112.46, 36.53) --
	(114.38, 36.53) --
	(116.31, 36.58) --
	(118.23, 36.53) --
	(120.15, 36.53) --
	(122.07, 36.54) --
	(124.00, 36.95) --
	(125.92, 37.68) --
	(127.84, 36.65) --
	(129.77, 37.80) --
	(131.69, 37.46) --
	(133.61, 38.26) --
	(135.54, 33.55) --
	(137.46, 33.66) --
	(139.38, 33.66) --
	(141.31, 33.53) --
	(143.23, 32.97) --
	(145.15, 32.97) --
	(147.08, 33.14) --
	(149.00, 33.12) --
	(150.92, 33.07) --
	(152.85, 33.33) --
	(154.77, 33.36) --
	(156.69, 33.47) --
	(158.62, 33.29) --
	(160.54, 33.46) --
	(162.46, 33.66) --
	(164.38, 33.66) --
	(166.31, 34.31) --
	(168.23, 34.31) --
	(170.15, 34.31) --
	(172.08, 34.14) --
	(174.00, 34.32) --
	(175.92, 34.20) --
	(177.85, 33.69) --
	(179.77, 34.95) --
	(181.69, 33.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15, 28.21) rectangle (211.31,132.86);
\end{scope}
\begin{scope}
\path[clip] ( 25.15,132.86) rectangle (211.31,145.80);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,132.86) rectangle (211.31,145.80);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (118.23,136.23) {Synthetic};
\end{scope}
\begin{scope}
\path[clip] ( 25.15,255.95) rectangle (211.31,268.89);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,255.95) rectangle (211.31,268.89);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (118.23,259.32) {Straight};
\end{scope}
\begin{scope}
\path[clip] ( 25.15,379.04) rectangle (211.31,391.99);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,379.04) rectangle (211.31,391.98);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (118.23,382.41) {Soluble};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38, 25.46) --
	( 39.38, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.84, 25.46) --
	( 77.84, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.31, 25.46) --
	(116.31, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.77, 25.46) --
	(154.77, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.23, 25.46) --
	(193.23, 28.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 39.38, 17.75) {1920};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 77.84, 17.75) {1940};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (116.31, 17.75) {1960};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (154.77, 17.75) {1980};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (193.23, 17.75) {2000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,275.70) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,311.13) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,346.55) {2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,278.46) --
	( 25.15,278.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,313.88) --
	( 25.15,313.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,349.30) --
	( 25.15,349.30);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,152.61) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,188.04) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,223.46) {2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,155.37) --
	( 25.15,155.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,190.79) --
	( 25.15,190.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,226.21) --
	( 25.15,226.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 29.52) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 64.94) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,100.37) {2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 32.28) --
	( 25.15, 32.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 67.70) --
	( 25.15, 67.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,103.12) --
	( 25.15,103.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (118.23,  7.25) {Calendar year};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,397.48);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,203.62) {Median exposure (mg/m$^3$) among exposed};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-06-03 resources/shift-soluble-dynamic.tex
Upload work

% Created by tikzDevice version 0.12.3.1 on 2022-06-01 15:12:18
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,198.74);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,198.74);
\end{scope}
\begin{scope}
\path[clip] ( 31.37, 51.21) rectangle (283.58,193.24);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37, 51.21) rectangle (283.58,193.24);

\path[] ( 42.83, 57.70) --
	( 43.28, 57.69) --
	( 43.73, 57.69) --
	( 44.18, 57.69) --
	( 44.63, 57.68) --
	( 45.08, 57.68) --
	( 45.52, 57.67) --
	( 45.97, 57.67) --
	( 46.42, 57.67) --
	( 46.87, 57.67) --
	( 47.32, 57.67) --
	( 47.77, 57.67) --
	( 48.22, 57.67) --
	( 48.67, 57.67) --
	( 49.11, 57.67) --
	( 49.56, 57.67) --
	( 50.01, 57.67) --
	( 50.46, 57.67) --
	( 50.91, 57.67) --
	( 51.36, 57.67) --
	( 51.81, 57.67) --
	( 52.25, 57.67) --
	( 52.70, 57.67) --
	( 53.15, 57.67) --
	( 53.60, 57.67) --
	( 54.05, 57.67) --
	( 54.50, 57.67) --
	( 54.95, 57.67) --
	( 55.40, 57.67) --
	( 55.84, 57.67) --
	( 56.29, 57.67) --
	( 56.74, 57.67) --
	( 57.19, 57.67) --
	( 57.64, 57.67) --
	( 58.09, 57.67) --
	( 58.54, 57.67) --
	( 58.99, 57.67) --
	( 59.43, 57.67) --
	( 59.88, 57.67) --
	( 60.33, 57.67) --
	( 60.78, 57.67) --
	( 61.23, 57.67) --
	( 61.68, 57.67) --
	( 62.13, 57.67) --
	( 62.57, 57.67) --
	( 63.02, 57.67) --
	( 63.47, 57.67) --
	( 63.92, 57.67) --
	( 64.37, 57.67) --
	( 64.82, 57.67) --
	( 65.27, 57.67) --
	( 65.72, 57.67) --
	( 66.16, 57.67) --
	( 66.61, 57.67) --
	( 67.06, 57.67) --
	( 67.51, 57.67) --
	( 67.96, 57.67) --
	( 68.41, 57.67) --
	( 68.86, 57.67) --
	( 69.31, 57.67) --
	( 69.75, 57.67) --
	( 70.20, 57.67) --
	( 70.65, 57.67) --
	( 71.10, 57.67) --
	( 71.55, 57.67) --
	( 72.00, 57.67) --
	( 72.45, 57.67) --
	( 72.89, 57.67) --
	( 73.34, 57.67) --
	( 73.79, 57.67) --
	( 74.24, 57.67) --
	( 74.69, 57.67) --
	( 75.14, 57.67) --
	( 75.59, 57.67) --
	( 76.04, 57.67) --
	( 76.48, 57.67) --
	( 76.93, 57.67) --
	( 77.38, 57.67) --
	( 77.83, 57.67) --
	( 78.28, 57.67) --
	( 78.73, 57.67) --
	( 79.18, 57.67) --
	( 79.63, 57.67) --
	( 80.07, 57.67) --
	( 80.52, 57.67) --
	( 80.97, 57.67) --
	( 81.42, 57.67) --
	( 81.87, 57.67) --
	( 82.32, 57.67) --
	( 82.77, 57.67) --
	( 83.21, 57.67) --
	( 83.66, 57.67) --
	( 84.11, 57.67) --
	( 84.56, 57.67) --
	( 85.01, 57.67) --
	( 85.46, 57.67) --
	( 85.91, 57.67) --
	( 86.36, 57.67) --
	( 86.80, 57.67) --
	( 87.25, 57.67) --
	( 87.70, 57.67) --
	( 88.15, 57.67) --
	( 88.60, 57.67) --
	( 89.05, 57.67) --
	( 89.50, 57.67) --
	( 89.95, 57.67) --
	( 90.39, 57.67) --
	( 90.84, 57.67) --
	( 91.29, 57.67) --
	( 91.74, 57.67) --
	( 92.19, 57.67) --
	( 92.64, 57.67) --
	( 93.09, 57.67) --
	( 93.53, 57.67) --
	( 93.98, 57.67) --
	( 94.43, 57.67) --
	( 94.88, 57.67) --
	( 95.33, 57.67) --
	( 95.78, 57.67) --
	( 96.23, 57.67) --
	( 96.68, 57.67) --
	( 97.12, 57.67) --
	( 97.57, 57.67) --
	( 98.02, 57.67) --
	( 98.47, 57.67) --
	( 98.92, 57.68) --
	( 99.37, 57.68) --
	( 99.82, 57.69) --
	(100.27, 57.69) --
	(100.71, 57.69) --
	(101.16, 57.69) --
	(101.61, 57.69) --
	(102.06, 57.69) --
	(102.51, 57.69) --
	(102.96, 57.68) --
	(103.41, 57.68) --
	(103.85, 57.68) --
	(104.30, 57.67) --
	(104.75, 57.67) --
	(105.20, 57.67) --
	(105.65, 57.68) --
	(106.10, 57.68) --
	(106.55, 57.69) --
	(107.00, 57.69) --
	(107.44, 57.70) --
	(107.89, 57.70) --
	(108.34, 57.71) --
	(108.79, 57.71) --
	(109.24, 57.71) --
	(109.69, 57.71) --
	(110.14, 57.71) --
	(110.59, 57.71) --
	(111.03, 57.72) --
	(111.48, 57.72) --
	(111.93, 57.73) --
	(112.38, 57.74) --
	(112.83, 57.75) --
	(113.28, 57.76) --
	(113.73, 57.76) --
	(114.17, 57.77) --
	(114.62, 57.78) --
	(115.07, 57.78) --
	(115.52, 57.78) --
	(115.97, 57.79) --
	(116.42, 57.79) --
	(116.87, 57.79) --
	(117.32, 57.80) --
	(117.76, 57.81) --
	(118.21, 57.82) --
	(118.66, 57.83) --
	(119.11, 57.85) --
	(119.56, 57.86) --
	(120.01, 57.87) --
	(120.46, 57.88) --
	(120.91, 57.88) --
	(121.35, 57.88) --
	(121.80, 57.87) --
	(122.25, 57.87) --
	(122.70, 57.87) --
	(123.15, 57.87) --
	(123.60, 57.88) --
	(124.05, 57.89) --
	(124.49, 57.91) --
	(124.94, 57.92) --
	(125.39, 57.92) --
	(125.84, 57.93) --
	(126.29, 57.93) --
	(126.74, 57.94) --
	(127.19, 57.95) --
	(127.64, 57.96) --
	(128.08, 57.97) --
	(128.53, 57.98) --
	(128.98, 58.00) --
	(129.43, 58.01) --
	(129.88, 58.03) --
	(130.33, 58.05) --
	(130.78, 58.08) --
	(131.23, 58.11) --
	(131.67, 58.15) --
	(132.12, 58.19) --
	(132.57, 58.23) --
	(133.02, 58.27) --
	(133.47, 58.30) --
	(133.92, 58.33) --
	(134.37, 58.35) --
	(134.81, 58.36) --
	(135.26, 58.37) --
	(135.71, 58.39) --
	(136.16, 58.40) --
	(136.61, 58.42) --
	(137.06, 58.45) --
	(137.51, 58.50) --
	(137.96, 58.56) --
	(138.40, 58.62) --
	(138.85, 58.70) --
	(139.30, 58.78) --
	(139.75, 58.87) --
	(140.20, 58.94) --
	(140.65, 59.00) --
	(141.10, 59.03) --
	(141.55, 59.03) --
	(141.99, 59.01) --
	(142.44, 58.98) --
	(142.89, 58.94) --
	(143.34, 58.92) --
	(143.79, 58.93) --
	(144.24, 58.97) --
	(144.69, 59.04) --
	(145.13, 59.13) --
	(145.58, 59.24) --
	(146.03, 59.36) --
	(146.48, 59.46) --
	(146.93, 59.56) --
	(147.38, 59.65) --
	(147.83, 59.73) --
	(148.28, 59.80) --
	(148.72, 59.88) --
	(149.17, 59.97) --
	(149.62, 60.07) --
	(150.07, 60.17) --
	(150.52, 60.28) --
	(150.97, 60.39) --
	(151.42, 60.51) --
	(151.87, 60.62) --
	(152.31, 60.74) --
	(152.76, 60.84) --
	(153.21, 60.93) --
	(153.66, 61.00) --
	(154.11, 61.03) --
	(154.56, 61.04) --
	(155.01, 61.01) --
	(155.45, 60.97) --
	(155.90, 60.93) --
	(156.35, 60.91) --
	(156.80, 60.94) --
	(157.25, 61.02) --
	(157.70, 61.15) --
	(158.15, 61.31) --
	(158.60, 61.49) --
	(159.04, 61.66) --
	(159.49, 61.80) --
	(159.94, 61.91) --
	(160.39, 61.99) --
	(160.84, 62.04) --
	(161.29, 62.09) --
	(161.74, 62.14) --
	(162.19, 62.21) --
	(162.63, 62.33) --
	(163.08, 62.48) --
	(163.53, 62.66) --
	(163.98, 62.86) --
	(164.43, 63.07) --
	(164.88, 63.27) --
	(165.33, 63.47) --
	(165.77, 63.65) --
	(166.22, 63.83) --
	(166.67, 64.01) --
	(167.12, 64.20) --
	(167.57, 64.40) --
	(168.02, 64.62) --
	(168.47, 64.84) --
	(168.92, 65.06) --
	(169.36, 65.29) --
	(169.81, 65.51) --
	(170.26, 65.72) --
	(170.71, 65.91) --
	(171.16, 66.07) --
	(171.61, 66.20) --
	(172.06, 66.29) --
	(172.51, 66.34) --
	(172.95, 66.37) --
	(173.40, 66.40) --
	(173.85, 66.44) --
	(174.30, 66.53) --
	(174.75, 66.68) --
	(175.20, 66.91) --
	(175.65, 67.22) --
	(176.09, 67.58) --
	(176.54, 67.99) --
	(176.99, 68.40) --
	(177.44, 68.83) --
	(177.89, 69.26) --
	(178.34, 69.71) --
	(178.79, 70.20) --
	(179.24, 70.76) --
	(179.68, 71.47) --
	(180.13, 72.40) --
	(180.58, 73.62) --
	(181.03, 75.20) --
	(181.48, 77.17) --
	(181.93, 79.44) --
	(182.38, 81.84) --
	(182.83, 84.13) --
	(183.27, 86.00) --
	(183.72, 87.21) --
	(184.17, 87.63) --
	(184.62, 87.40) --
	(185.07, 86.74) --
	(185.52, 85.93) --
	(185.97, 85.22) --
	(186.41, 84.76) --
	(186.86, 84.61) --
	(187.31, 84.77) --
	(187.76, 85.24) --
	(188.21, 86.01) --
	(188.66, 87.13) --
	(189.11, 88.65) --
	(189.56, 90.65) --
	(190.00, 93.13) --
	(190.45, 96.00) --
	(190.90, 99.05) --
	(191.35,101.96) --
	(191.80,104.39) --
	(192.25,106.10) --
	(192.70,106.97) --
	(193.15,107.20) --
	(193.59,107.13) --
	(194.04,107.15) --
	(194.49,107.59) --
	(194.94,108.62) --
	(195.39,110.24) --
	(195.84,112.29) --
	(196.29,114.53) --
	(196.73,116.73) --
	(197.18,118.74) --
	(197.63,120.57) --
	(198.08,122.36) --
	(198.53,124.29) --
	(198.98,126.50) --
	(199.43,128.98) --
	(199.88,131.59) --
	(200.32,134.10) --
	(200.77,136.29) --
	(201.22,138.06) --
	(201.67,139.44) --
	(202.12,140.59) --
	(202.57,141.61) --
	(203.02,142.55) --
	(203.47,143.40) --
	(203.91,144.16) --
	(204.36,144.83) --
	(204.81,145.43) --
	(205.26,146.01) --
	(205.71,146.57) --
	(206.16,147.10) --
	(206.61,147.59) --
	(207.05,148.05) --
	(207.50,148.47) --
	(207.95,148.88) --
	(208.40,149.30) --
	(208.85,149.72) --
	(209.30,150.15) --
	(209.75,150.55) --
	(210.20,150.92) --
	(210.64,151.26) --
	(211.09,151.62) --
	(211.54,152.06) --
	(211.99,152.66) --
	(212.44,153.43) --
	(212.89,154.35) --
	(213.34,155.30) --
	(213.79,156.12) --
	(214.23,156.59) --
	(214.68,156.52) --
	(215.13,155.77) --
	(215.58,154.29) --
	(216.03,152.16) --
	(216.48,149.49) --
	(216.93,146.47) --
	(217.37,143.23) --
	(217.82,139.88) --
	(218.27,136.49) --
	(218.72,133.09) --
	(219.17,129.74) --
	(219.62,126.52) --
	(220.07,123.54) --
	(220.52,120.89) --
	(220.96,118.60) --
	(221.41,116.64) --
	(221.86,114.91) --
	(222.31,113.25) --
	(222.76,111.46) --
	(223.21,109.40) --
	(223.66,106.93) --
	(224.11,103.99) --
	(224.55,100.54) --
	(225.00, 96.66) --
	(225.45, 92.45) --
	(225.90, 88.06) --
	(226.35, 83.70) --
	(226.80, 79.52) --
	(227.25, 75.68) --
	(227.69, 72.29) --
	(228.14, 69.34) --
	(228.59, 66.83) --
	(229.04, 64.72) --
	(229.49, 62.97) --
	(229.94, 61.55) --
	(230.39, 60.41) --
	(230.84, 59.53) --
	(231.28, 58.88) --
	(231.73, 58.42) --
	(232.18, 58.11) --
	(232.63, 57.92) --
	(233.08, 57.80) --
	(233.53, 57.73) --
	(233.98, 57.70) --
	(234.43, 57.68) --
	(234.87, 57.67) --
	(235.32, 57.67) --
	(235.77, 57.67) --
	(236.22, 57.67) --
	(236.67, 57.67) --
	(237.12, 57.67) --
	(237.57, 57.67) --
	(238.01, 57.67) --
	(238.46, 57.67) --
	(238.91, 57.67) --
	(239.36, 57.67) --
	(239.81, 57.67) --
	(240.26, 57.67) --
	(240.71, 57.67) --
	(241.16, 57.67) --
	(241.60, 57.67) --
	(242.05, 57.67) --
	(242.50, 57.67) --
	(242.95, 57.67) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67) --
	(272.12, 57.67) --
	(271.67, 57.67) --
	(271.22, 57.67) --
	(270.77, 57.67) --
	(270.32, 57.67) --
	(269.87, 57.67) --
	(269.42, 57.67) --
	(268.97, 57.67) --
	(268.53, 57.67) --
	(268.08, 57.67) --
	(267.63, 57.67) --
	(267.18, 57.67) --
	(266.73, 57.67) --
	(266.28, 57.67) --
	(265.83, 57.67) --
	(265.39, 57.67) --
	(264.94, 57.67) --
	(264.49, 57.67) --
	(264.04, 57.67) --
	(263.59, 57.67) --
	(263.14, 57.67) --
	(262.69, 57.67) --
	(262.24, 57.67) --
	(261.80, 57.67) --
	(261.35, 57.67) --
	(260.90, 57.67) --
	(260.45, 57.67) --
	(260.00, 57.67) --
	(259.55, 57.67) --
	(259.10, 57.67) --
	(258.65, 57.67) --
	(258.21, 57.67) --
	(257.76, 57.67) --
	(257.31, 57.67) --
	(256.86, 57.67) --
	(256.41, 57.67) --
	(255.96, 57.67) --
	(255.51, 57.67) --
	(255.07, 57.67) --
	(254.62, 57.67) --
	(254.17, 57.67) --
	(253.72, 57.67) --
	(253.27, 57.67) --
	(252.82, 57.67) --
	(252.37, 57.67) --
	(251.92, 57.67) --
	(251.48, 57.67) --
	(251.03, 57.67) --
	(250.58, 57.67) --
	(250.13, 57.67) --
	(249.68, 57.67) --
	(249.23, 57.67) --
	(248.78, 57.67) --
	(248.33, 57.67) --
	(247.89, 57.67) --
	(247.44, 57.67) --
	(246.99, 57.67) --
	(246.54, 57.67) --
	(246.09, 57.67) --
	(245.64, 57.67) --
	(245.19, 57.67) --
	(244.75, 57.67) --
	(244.30, 57.67) --
	(243.85, 57.67) --
	(243.40, 57.67) --
	(242.95, 57.67) --
	(242.50, 57.67) --
	(242.05, 57.67) --
	(241.60, 57.67) --
	(241.16, 57.67) --
	(240.71, 57.67) --
	(240.26, 57.67) --
	(239.81, 57.67) --
	(239.36, 57.67) --
	(238.91, 57.67) --
	(238.46, 57.67) --
	(238.01, 57.67) --
	(237.57, 57.67) --
	(237.12, 57.67) --
	(236.67, 57.67) --
	(236.22, 57.67) --
	(235.77, 57.67) --
	(235.32, 57.67) --
	(234.87, 57.67) --
	(234.43, 57.67) --
	(233.98, 57.67) --
	(233.53, 57.67) --
	(233.08, 57.67) --
	(232.63, 57.67) --
	(232.18, 57.67) --
	(231.73, 57.67) --
	(231.28, 57.67) --
	(230.84, 57.67) --
	(230.39, 57.67) --
	(229.94, 57.67) --
	(229.49, 57.67) --
	(229.04, 57.67) --
	(228.59, 57.67) --
	(228.14, 57.67) --
	(227.69, 57.67) --
	(227.25, 57.67) --
	(226.80, 57.67) --
	(226.35, 57.67) --
	(225.90, 57.67) --
	(225.45, 57.67) --
	(225.00, 57.67) --
	(224.55, 57.67) --
	(224.11, 57.67) --
	(223.66, 57.67) --
	(223.21, 57.67) --
	(222.76, 57.67) --
	(222.31, 57.67) --
	(221.86, 57.67) --
	(221.41, 57.67) --
	(220.96, 57.67) --
	(220.52, 57.67) --
	(220.07, 57.67) --
	(219.62, 57.67) --
	(219.17, 57.67) --
	(218.72, 57.67) --
	(218.27, 57.67) --
	(217.82, 57.67) --
	(217.37, 57.67) --
	(216.93, 57.67) --
	(216.48, 57.67) --
	(216.03, 57.67) --
	(215.58, 57.67) --
	(215.13, 57.67) --
	(214.68, 57.67) --
	(214.23, 57.67) --
	(213.79, 57.67) --
	(213.34, 57.67) --
	(212.89, 57.67) --
	(212.44, 57.67) --
	(211.99, 57.67) --
	(211.54, 57.67) --
	(211.09, 57.67) --
	(210.64, 57.67) --
	(210.20, 57.67) --
	(209.75, 57.67) --
	(209.30, 57.67) --
	(208.85, 57.67) --
	(208.40, 57.67) --
	(207.95, 57.67) --
	(207.50, 57.67) --
	(207.05, 57.67) --
	(206.61, 57.67) --
	(206.16, 57.67) --
	(205.71, 57.67) --
	(205.26, 57.67) --
	(204.81, 57.67) --
	(204.36, 57.67) --
	(203.91, 57.67) --
	(203.47, 57.67) --
	(203.02, 57.67) --
	(202.57, 57.67) --
	(202.12, 57.67) --
	(201.67, 57.67) --
	(201.22, 57.67) --
	(200.77, 57.67) --
	(200.32, 57.67) --
	(199.88, 57.67) --
	(199.43, 57.67) --
	(198.98, 57.67) --
	(198.53, 57.67) --
	(198.08, 57.67) --
	(197.63, 57.67) --
	(197.18, 57.67) --
	(196.73, 57.67) --
	(196.29, 57.67) --
	(195.84, 57.67) --
	(195.39, 57.67) --
	(194.94, 57.67) --
	(194.49, 57.67) --
	(194.04, 57.67) --
	(193.59, 57.67) --
	(193.15, 57.67) --
	(192.70, 57.67) --
	(192.25, 57.67) --
	(191.80, 57.67) --
	(191.35, 57.67) --
	(190.90, 57.67) --
	(190.45, 57.67) --
	(190.00, 57.67) --
	(189.56, 57.67) --
	(189.11, 57.67) --
	(188.66, 57.67) --
	(188.21, 57.67) --
	(187.76, 57.67) --
	(187.31, 57.67) --
	(186.86, 57.67) --
	(186.41, 57.67) --
	(185.97, 57.67) --
	(185.52, 57.67) --
	(185.07, 57.67) --
	(184.62, 57.67) --
	(184.17, 57.67) --
	(183.72, 57.67) --
	(183.27, 57.67) --
	(182.83, 57.67) --
	(182.38, 57.67) --
	(181.93, 57.67) --
	(181.48, 57.67) --
	(181.03, 57.67) --
	(180.58, 57.67) --
	(180.13, 57.67) --
	(179.68, 57.67) --
	(179.24, 57.67) --
	(178.79, 57.67) --
	(178.34, 57.67) --
	(177.89, 57.67) --
	(177.44, 57.67) --
	(176.99, 57.67) --
	(176.54, 57.67) --
	(176.09, 57.67) --
	(175.65, 57.67) --
	(175.20, 57.67) --
	(174.75, 57.67) --
	(174.30, 57.67) --
	(173.85, 57.67) --
	(173.40, 57.67) --
	(172.95, 57.67) --
	(172.51, 57.67) --
	(172.06, 57.67) --
	(171.61, 57.67) --
	(171.16, 57.67) --
	(170.71, 57.67) --
	(170.26, 57.67) --
	(169.81, 57.67) --
	(169.36, 57.67) --
	(168.92, 57.67) --
	(168.47, 57.67) --
	(168.02, 57.67) --
	(167.57, 57.67) --
	(167.12, 57.67) --
	(166.67, 57.67) --
	(166.22, 57.67) --
	(165.77, 57.67) --
	(165.33, 57.67) --
	(164.88, 57.67) --
	(164.43, 57.67) --
	(163.98, 57.67) --
	(163.53, 57.67) --
	(163.08, 57.67) --
	(162.63, 57.67) --
	(162.19, 57.67) --
	(161.74, 57.67) --
	(161.29, 57.67) --
	(160.84, 57.67) --
	(160.39, 57.67) --
	(159.94, 57.67) --
	(159.49, 57.67) --
	(159.04, 57.67) --
	(158.60, 57.67) --
	(158.15, 57.67) --
	(157.70, 57.67) --
	(157.25, 57.67) --
	(156.80, 57.67) --
	(156.35, 57.67) --
	(155.90, 57.67) --
	(155.45, 57.67) --
	(155.01, 57.67) --
	(154.56, 57.67) --
	(154.11, 57.67) --
	(153.66, 57.67) --
	(153.21, 57.67) --
	(152.76, 57.67) --
	(152.31, 57.67) --
	(151.87, 57.67) --
	(151.42, 57.67) --
	(150.97, 57.67) --
	(150.52, 57.67) --
	(150.07, 57.67) --
	(149.62, 57.67) --
	(149.17, 57.67) --
	(148.72, 57.67) --
	(148.28, 57.67) --
	(147.83, 57.67) --
	(147.38, 57.67) --
	(146.93, 57.67) --
	(146.48, 57.67) --
	(146.03, 57.67) --
	(145.58, 57.67) --
	(145.13, 57.67) --
	(144.69, 57.67) --
	(144.24, 57.67) --
	(143.79, 57.67) --
	(143.34, 57.67) --
	(142.89, 57.67) --
	(142.44, 57.67) --
	(141.99, 57.67) --
	(141.55, 57.67) --
	(141.10, 57.67) --
	(140.65, 57.67) --
	(140.20, 57.67) --
	(139.75, 57.67) --
	(139.30, 57.67) --
	(138.85, 57.67) --
	(138.40, 57.67) --
	(137.96, 57.67) --
	(137.51, 57.67) --
	(137.06, 57.67) --
	(136.61, 57.67) --
	(136.16, 57.67) --
	(135.71, 57.67) --
	(135.26, 57.67) --
	(134.81, 57.67) --
	(134.37, 57.67) --
	(133.92, 57.67) --
	(133.47, 57.67) --
	(133.02, 57.67) --
	(132.57, 57.67) --
	(132.12, 57.67) --
	(131.67, 57.67) --
	(131.23, 57.67) --
	(130.78, 57.67) --
	(130.33, 57.67) --
	(129.88, 57.67) --
	(129.43, 57.67) --
	(128.98, 57.67) --
	(128.53, 57.67) --
	(128.08, 57.67) --
	(127.64, 57.67) --
	(127.19, 57.67) --
	(126.74, 57.67) --
	(126.29, 57.67) --
	(125.84, 57.67) --
	(125.39, 57.67) --
	(124.94, 57.67) --
	(124.49, 57.67) --
	(124.05, 57.67) --
	(123.60, 57.67) --
	(123.15, 57.67) --
	(122.70, 57.67) --
	(122.25, 57.67) --
	(121.80, 57.67) --
	(121.35, 57.67) --
	(120.91, 57.67) --
	(120.46, 57.67) --
	(120.01, 57.67) --
	(119.56, 57.67) --
	(119.11, 57.67) --
	(118.66, 57.67) --
	(118.21, 57.67) --
	(117.76, 57.67) --
	(117.32, 57.67) --
	(116.87, 57.67) --
	(116.42, 57.67) --
	(115.97, 57.67) --
	(115.52, 57.67) --
	(115.07, 57.67) --
	(114.62, 57.67) --
	(114.17, 57.67) --
	(113.73, 57.67) --
	(113.28, 57.67) --
	(112.83, 57.67) --
	(112.38, 57.67) --
	(111.93, 57.67) --
	(111.48, 57.67) --
	(111.03, 57.67) --
	(110.59, 57.67) --
	(110.14, 57.67) --
	(109.69, 57.67) --
	(109.24, 57.67) --
	(108.79, 57.67) --
	(108.34, 57.67) --
	(107.89, 57.67) --
	(107.44, 57.67) --
	(107.00, 57.67) --
	(106.55, 57.67) --
	(106.10, 57.67) --
	(105.65, 57.67) --
	(105.20, 57.67) --
	(104.75, 57.67) --
	(104.30, 57.67) --
	(103.85, 57.67) --
	(103.41, 57.67) --
	(102.96, 57.67) --
	(102.51, 57.67) --
	(102.06, 57.67) --
	(101.61, 57.67) --
	(101.16, 57.67) --
	(100.71, 57.67) --
	(100.27, 57.67) --
	( 99.82, 57.67) --
	( 99.37, 57.67) --
	( 98.92, 57.67) --
	( 98.47, 57.67) --
	( 98.02, 57.67) --
	( 97.57, 57.67) --
	( 97.12, 57.67) --
	( 96.68, 57.67) --
	( 96.23, 57.67) --
	( 95.78, 57.67) --
	( 95.33, 57.67) --
	( 94.88, 57.67) --
	( 94.43, 57.67) --
	( 93.98, 57.67) --
	( 93.53, 57.67) --
	( 93.09, 57.67) --
	( 92.64, 57.67) --
	( 92.19, 57.67) --
	( 91.74, 57.67) --
	( 91.29, 57.67) --
	( 90.84, 57.67) --
	( 90.39, 57.67) --
	( 89.95, 57.67) --
	( 89.50, 57.67) --
	( 89.05, 57.67) --
	( 88.60, 57.67) --
	( 88.15, 57.67) --
	( 87.70, 57.67) --
	( 87.25, 57.67) --
	( 86.80, 57.67) --
	( 86.36, 57.67) --
	( 85.91, 57.67) --
	( 85.46, 57.67) --
	( 85.01, 57.67) --
	( 84.56, 57.67) --
	( 84.11, 57.67) --
	( 83.66, 57.67) --
	( 83.21, 57.67) --
	( 82.77, 57.67) --
	( 82.32, 57.67) --
	( 81.87, 57.67) --
	( 81.42, 57.67) --
	( 80.97, 57.67) --
	( 80.52, 57.67) --
	( 80.07, 57.67) --
	( 79.63, 57.67) --
	( 79.18, 57.67) --
	( 78.73, 57.67) --
	( 78.28, 57.67) --
	( 77.83, 57.67) --
	( 77.38, 57.67) --
	( 76.93, 57.67) --
	( 76.48, 57.67) --
	( 76.04, 57.67) --
	( 75.59, 57.67) --
	( 75.14, 57.67) --
	( 74.69, 57.67) --
	( 74.24, 57.67) --
	( 73.79, 57.67) --
	( 73.34, 57.67) --
	( 72.89, 57.67) --
	( 72.45, 57.67) --
	( 72.00, 57.67) --
	( 71.55, 57.67) --
	( 71.10, 57.67) --
	( 70.65, 57.67) --
	( 70.20, 57.67) --
	( 69.75, 57.67) --
	( 69.31, 57.67) --
	( 68.86, 57.67) --
	( 68.41, 57.67) --
	( 67.96, 57.67) --
	( 67.51, 57.67) --
	( 67.06, 57.67) --
	( 66.61, 57.67) --
	( 66.16, 57.67) --
	( 65.72, 57.67) --
	( 65.27, 57.67) --
	( 64.82, 57.67) --
	( 64.37, 57.67) --
	( 63.92, 57.67) --
	( 63.47, 57.67) --
	( 63.02, 57.67) --
	( 62.57, 57.67) --
	( 62.13, 57.67) --
	( 61.68, 57.67) --
	( 61.23, 57.67) --
	( 60.78, 57.67) --
	( 60.33, 57.67) --
	( 59.88, 57.67) --
	( 59.43, 57.67) --
	( 58.99, 57.67) --
	( 58.54, 57.67) --
	( 58.09, 57.67) --
	( 57.64, 57.67) --
	( 57.19, 57.67) --
	( 56.74, 57.67) --
	( 56.29, 57.67) --
	( 55.84, 57.67) --
	( 55.40, 57.67) --
	( 54.95, 57.67) --
	( 54.50, 57.67) --
	( 54.05, 57.67) --
	( 53.60, 57.67) --
	( 53.15, 57.67) --
	( 52.70, 57.67) --
	( 52.25, 57.67) --
	( 51.81, 57.67) --
	( 51.36, 57.67) --
	( 50.91, 57.67) --
	( 50.46, 57.67) --
	( 50.01, 57.67) --
	( 49.56, 57.67) --
	( 49.11, 57.67) --
	( 48.67, 57.67) --
	( 48.22, 57.67) --
	( 47.77, 57.67) --
	( 47.32, 57.67) --
	( 46.87, 57.67) --
	( 46.42, 57.67) --
	( 45.97, 57.67) --
	( 45.52, 57.67) --
	( 45.08, 57.67) --
	( 44.63, 57.67) --
	( 44.18, 57.67) --
	( 43.73, 57.67) --
	( 43.28, 57.67) --
	( 42.83, 57.67) --
	cycle;
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 42.83, 57.70) --
	( 43.28, 57.69) --
	( 43.73, 57.69) --
	( 44.18, 57.69) --
	( 44.63, 57.68) --
	( 45.08, 57.68) --
	( 45.52, 57.67) --
	( 45.97, 57.67) --
	( 46.42, 57.67) --
	( 46.87, 57.67) --
	( 47.32, 57.67) --
	( 47.77, 57.67) --
	( 48.22, 57.67) --
	( 48.67, 57.67) --
	( 49.11, 57.67) --
	( 49.56, 57.67) --
	( 50.01, 57.67) --
	( 50.46, 57.67) --
	( 50.91, 57.67) --
	( 51.36, 57.67) --
	( 51.81, 57.67) --
	( 52.25, 57.67) --
	( 52.70, 57.67) --
	( 53.15, 57.67) --
	( 53.60, 57.67) --
	( 54.05, 57.67) --
	( 54.50, 57.67) --
	( 54.95, 57.67) --
	( 55.40, 57.67) --
	( 55.84, 57.67) --
	( 56.29, 57.67) --
	( 56.74, 57.67) --
	( 57.19, 57.67) --
	( 57.64, 57.67) --
	( 58.09, 57.67) --
	( 58.54, 57.67) --
	( 58.99, 57.67) --
	( 59.43, 57.67) --
	( 59.88, 57.67) --
	( 60.33, 57.67) --
	( 60.78, 57.67) --
	( 61.23, 57.67) --
	( 61.68, 57.67) --
	( 62.13, 57.67) --
	( 62.57, 57.67) --
	( 63.02, 57.67) --
	( 63.47, 57.67) --
	( 63.92, 57.67) --
	( 64.37, 57.67) --
	( 64.82, 57.67) --
	( 65.27, 57.67) --
	( 65.72, 57.67) --
	( 66.16, 57.67) --
	( 66.61, 57.67) --
	( 67.06, 57.67) --
	( 67.51, 57.67) --
	( 67.96, 57.67) --
	( 68.41, 57.67) --
	( 68.86, 57.67) --
	( 69.31, 57.67) --
	( 69.75, 57.67) --
	( 70.20, 57.67) --
	( 70.65, 57.67) --
	( 71.10, 57.67) --
	( 71.55, 57.67) --
	( 72.00, 57.67) --
	( 72.45, 57.67) --
	( 72.89, 57.67) --
	( 73.34, 57.67) --
	( 73.79, 57.67) --
	( 74.24, 57.67) --
	( 74.69, 57.67) --
	( 75.14, 57.67) --
	( 75.59, 57.67) --
	( 76.04, 57.67) --
	( 76.48, 57.67) --
	( 76.93, 57.67) --
	( 77.38, 57.67) --
	( 77.83, 57.67) --
	( 78.28, 57.67) --
	( 78.73, 57.67) --
	( 79.18, 57.67) --
	( 79.63, 57.67) --
	( 80.07, 57.67) --
	( 80.52, 57.67) --
	( 80.97, 57.67) --
	( 81.42, 57.67) --
	( 81.87, 57.67) --
	( 82.32, 57.67) --
	( 82.77, 57.67) --
	( 83.21, 57.67) --
	( 83.66, 57.67) --
	( 84.11, 57.67) --
	( 84.56, 57.67) --
	( 85.01, 57.67) --
	( 85.46, 57.67) --
	( 85.91, 57.67) --
	( 86.36, 57.67) --
	( 86.80, 57.67) --
	( 87.25, 57.67) --
	( 87.70, 57.67) --
	( 88.15, 57.67) --
	( 88.60, 57.67) --
	( 89.05, 57.67) --
	( 89.50, 57.67) --
	( 89.95, 57.67) --
	( 90.39, 57.67) --
	( 90.84, 57.67) --
	( 91.29, 57.67) --
	( 91.74, 57.67) --
	( 92.19, 57.67) --
	( 92.64, 57.67) --
	( 93.09, 57.67) --
	( 93.53, 57.67) --
	( 93.98, 57.67) --
	( 94.43, 57.67) --
	( 94.88, 57.67) --
	( 95.33, 57.67) --
	( 95.78, 57.67) --
	( 96.23, 57.67) --
	( 96.68, 57.67) --
	( 97.12, 57.67) --
	( 97.57, 57.67) --
	( 98.02, 57.67) --
	( 98.47, 57.67) --
	( 98.92, 57.68) --
	( 99.37, 57.68) --
	( 99.82, 57.69) --
	(100.27, 57.69) --
	(100.71, 57.69) --
	(101.16, 57.69) --
	(101.61, 57.69) --
	(102.06, 57.69) --
	(102.51, 57.69) --
	(102.96, 57.68) --
	(103.41, 57.68) --
	(103.85, 57.68) --
	(104.30, 57.67) --
	(104.75, 57.67) --
	(105.20, 57.67) --
	(105.65, 57.68) --
	(106.10, 57.68) --
	(106.55, 57.69) --
	(107.00, 57.69) --
	(107.44, 57.70) --
	(107.89, 57.70) --
	(108.34, 57.71) --
	(108.79, 57.71) --
	(109.24, 57.71) --
	(109.69, 57.71) --
	(110.14, 57.71) --
	(110.59, 57.71) --
	(111.03, 57.72) --
	(111.48, 57.72) --
	(111.93, 57.73) --
	(112.38, 57.74) --
	(112.83, 57.75) --
	(113.28, 57.76) --
	(113.73, 57.76) --
	(114.17, 57.77) --
	(114.62, 57.78) --
	(115.07, 57.78) --
	(115.52, 57.78) --
	(115.97, 57.79) --
	(116.42, 57.79) --
	(116.87, 57.79) --
	(117.32, 57.80) --
	(117.76, 57.81) --
	(118.21, 57.82) --
	(118.66, 57.83) --
	(119.11, 57.85) --
	(119.56, 57.86) --
	(120.01, 57.87) --
	(120.46, 57.88) --
	(120.91, 57.88) --
	(121.35, 57.88) --
	(121.80, 57.87) --
	(122.25, 57.87) --
	(122.70, 57.87) --
	(123.15, 57.87) --
	(123.60, 57.88) --
	(124.05, 57.89) --
	(124.49, 57.91) --
	(124.94, 57.92) --
	(125.39, 57.92) --
	(125.84, 57.93) --
	(126.29, 57.93) --
	(126.74, 57.94) --
	(127.19, 57.95) --
	(127.64, 57.96) --
	(128.08, 57.97) --
	(128.53, 57.98) --
	(128.98, 58.00) --
	(129.43, 58.01) --
	(129.88, 58.03) --
	(130.33, 58.05) --
	(130.78, 58.08) --
	(131.23, 58.11) --
	(131.67, 58.15) --
	(132.12, 58.19) --
	(132.57, 58.23) --
	(133.02, 58.27) --
	(133.47, 58.30) --
	(133.92, 58.33) --
	(134.37, 58.35) --
	(134.81, 58.36) --
	(135.26, 58.37) --
	(135.71, 58.39) --
	(136.16, 58.40) --
	(136.61, 58.42) --
	(137.06, 58.45) --
	(137.51, 58.50) --
	(137.96, 58.56) --
	(138.40, 58.62) --
	(138.85, 58.70) --
	(139.30, 58.78) --
	(139.75, 58.87) --
	(140.20, 58.94) --
	(140.65, 59.00) --
	(141.10, 59.03) --
	(141.55, 59.03) --
	(141.99, 59.01) --
	(142.44, 58.98) --
	(142.89, 58.94) --
	(143.34, 58.92) --
	(143.79, 58.93) --
	(144.24, 58.97) --
	(144.69, 59.04) --
	(145.13, 59.13) --
	(145.58, 59.24) --
	(146.03, 59.36) --
	(146.48, 59.46) --
	(146.93, 59.56) --
	(147.38, 59.65) --
	(147.83, 59.73) --
	(148.28, 59.80) --
	(148.72, 59.88) --
	(149.17, 59.97) --
	(149.62, 60.07) --
	(150.07, 60.17) --
	(150.52, 60.28) --
	(150.97, 60.39) --
	(151.42, 60.51) --
	(151.87, 60.62) --
	(152.31, 60.74) --
	(152.76, 60.84) --
	(153.21, 60.93) --
	(153.66, 61.00) --
	(154.11, 61.03) --
	(154.56, 61.04) --
	(155.01, 61.01) --
	(155.45, 60.97) --
	(155.90, 60.93) --
	(156.35, 60.91) --
	(156.80, 60.94) --
	(157.25, 61.02) --
	(157.70, 61.15) --
	(158.15, 61.31) --
	(158.60, 61.49) --
	(159.04, 61.66) --
	(159.49, 61.80) --
	(159.94, 61.91) --
	(160.39, 61.99) --
	(160.84, 62.04) --
	(161.29, 62.09) --
	(161.74, 62.14) --
	(162.19, 62.21) --
	(162.63, 62.33) --
	(163.08, 62.48) --
	(163.53, 62.66) --
	(163.98, 62.86) --
	(164.43, 63.07) --
	(164.88, 63.27) --
	(165.33, 63.47) --
	(165.77, 63.65) --
	(166.22, 63.83) --
	(166.67, 64.01) --
	(167.12, 64.20) --
	(167.57, 64.40) --
	(168.02, 64.62) --
	(168.47, 64.84) --
	(168.92, 65.06) --
	(169.36, 65.29) --
	(169.81, 65.51) --
	(170.26, 65.72) --
	(170.71, 65.91) --
	(171.16, 66.07) --
	(171.61, 66.20) --
	(172.06, 66.29) --
	(172.51, 66.34) --
	(172.95, 66.37) --
	(173.40, 66.40) --
	(173.85, 66.44) --
	(174.30, 66.53) --
	(174.75, 66.68) --
	(175.20, 66.91) --
	(175.65, 67.22) --
	(176.09, 67.58) --
	(176.54, 67.99) --
	(176.99, 68.40) --
	(177.44, 68.83) --
	(177.89, 69.26) --
	(178.34, 69.71) --
	(178.79, 70.20) --
	(179.24, 70.76) --
	(179.68, 71.47) --
	(180.13, 72.40) --
	(180.58, 73.62) --
	(181.03, 75.20) --
	(181.48, 77.17) --
	(181.93, 79.44) --
	(182.38, 81.84) --
	(182.83, 84.13) --
	(183.27, 86.00) --
	(183.72, 87.21) --
	(184.17, 87.63) --
	(184.62, 87.40) --
	(185.07, 86.74) --
	(185.52, 85.93) --
	(185.97, 85.22) --
	(186.41, 84.76) --
	(186.86, 84.61) --
	(187.31, 84.77) --
	(187.76, 85.24) --
	(188.21, 86.01) --
	(188.66, 87.13) --
	(189.11, 88.65) --
	(189.56, 90.65) --
	(190.00, 93.13) --
	(190.45, 96.00) --
	(190.90, 99.05) --
	(191.35,101.96) --
	(191.80,104.39) --
	(192.25,106.10) --
	(192.70,106.97) --
	(193.15,107.20) --
	(193.59,107.13) --
	(194.04,107.15) --
	(194.49,107.59) --
	(194.94,108.62) --
	(195.39,110.24) --
	(195.84,112.29) --
	(196.29,114.53) --
	(196.73,116.73) --
	(197.18,118.74) --
	(197.63,120.57) --
	(198.08,122.36) --
	(198.53,124.29) --
	(198.98,126.50) --
	(199.43,128.98) --
	(199.88,131.59) --
	(200.32,134.10) --
	(200.77,136.29) --
	(201.22,138.06) --
	(201.67,139.44) --
	(202.12,140.59) --
	(202.57,141.61) --
	(203.02,142.55) --
	(203.47,143.40) --
	(203.91,144.16) --
	(204.36,144.83) --
	(204.81,145.43) --
	(205.26,146.01) --
	(205.71,146.57) --
	(206.16,147.10) --
	(206.61,147.59) --
	(207.05,148.05) --
	(207.50,148.47) --
	(207.95,148.88) --
	(208.40,149.30) --
	(208.85,149.72) --
	(209.30,150.15) --
	(209.75,150.55) --
	(210.20,150.92) --
	(210.64,151.26) --
	(211.09,151.62) --
	(211.54,152.06) --
	(211.99,152.66) --
	(212.44,153.43) --
	(212.89,154.35) --
	(213.34,155.30) --
	(213.79,156.12) --
	(214.23,156.59) --
	(214.68,156.52) --
	(215.13,155.77) --
	(215.58,154.29) --
	(216.03,152.16) --
	(216.48,149.49) --
	(216.93,146.47) --
	(217.37,143.23) --
	(217.82,139.88) --
	(218.27,136.49) --
	(218.72,133.09) --
	(219.17,129.74) --
	(219.62,126.52) --
	(220.07,123.54) --
	(220.52,120.89) --
	(220.96,118.60) --
	(221.41,116.64) --
	(221.86,114.91) --
	(222.31,113.25) --
	(222.76,111.46) --
	(223.21,109.40) --
	(223.66,106.93) --
	(224.11,103.99) --
	(224.55,100.54) --
	(225.00, 96.66) --
	(225.45, 92.45) --
	(225.90, 88.06) --
	(226.35, 83.70) --
	(226.80, 79.52) --
	(227.25, 75.68) --
	(227.69, 72.29) --
	(228.14, 69.34) --
	(228.59, 66.83) --
	(229.04, 64.72) --
	(229.49, 62.97) --
	(229.94, 61.55) --
	(230.39, 60.41) --
	(230.84, 59.53) --
	(231.28, 58.88) --
	(231.73, 58.42) --
	(232.18, 58.11) --
	(232.63, 57.92) --
	(233.08, 57.80) --
	(233.53, 57.73) --
	(233.98, 57.70) --
	(234.43, 57.68) --
	(234.87, 57.67) --
	(235.32, 57.67) --
	(235.77, 57.67) --
	(236.22, 57.67) --
	(236.67, 57.67) --
	(237.12, 57.67) --
	(237.57, 57.67) --
	(238.01, 57.67) --
	(238.46, 57.67) --
	(238.91, 57.67) --
	(239.36, 57.67) --
	(239.81, 57.67) --
	(240.26, 57.67) --
	(240.71, 57.67) --
	(241.16, 57.67) --
	(241.60, 57.67) --
	(242.05, 57.67) --
	(242.50, 57.67) --
	(242.95, 57.67) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67);

\path[] ( 42.83, 57.67) --
	( 43.28, 57.67) --
	( 43.73, 57.67) --
	( 44.18, 57.67) --
	( 44.63, 57.67) --
	( 45.08, 57.67) --
	( 45.52, 57.67) --
	( 45.97, 57.67) --
	( 46.42, 57.67) --
	( 46.87, 57.67) --
	( 47.32, 57.67) --
	( 47.77, 57.67) --
	( 48.22, 57.67) --
	( 48.67, 57.67) --
	( 49.11, 57.67) --
	( 49.56, 57.67) --
	( 50.01, 57.67) --
	( 50.46, 57.67) --
	( 50.91, 57.67) --
	( 51.36, 57.67) --
	( 51.81, 57.67) --
	( 52.25, 57.67) --
	( 52.70, 57.67) --
	( 53.15, 57.67) --
	( 53.60, 57.67) --
	( 54.05, 57.67) --
	( 54.50, 57.67) --
	( 54.95, 57.67) --
	( 55.40, 57.67) --
	( 55.84, 57.67) --
	( 56.29, 57.67) --
	( 56.74, 57.67) --
	( 57.19, 57.67) --
	( 57.64, 57.67) --
	( 58.09, 57.67) --
	( 58.54, 57.67) --
	( 58.99, 57.67) --
	( 59.43, 57.67) --
	( 59.88, 57.67) --
	( 60.33, 57.67) --
	( 60.78, 57.67) --
	( 61.23, 57.67) --
	( 61.68, 57.67) --
	( 62.13, 57.67) --
	( 62.57, 57.67) --
	( 63.02, 57.67) --
	( 63.47, 57.67) --
	( 63.92, 57.67) --
	( 64.37, 57.67) --
	( 64.82, 57.67) --
	( 65.27, 57.67) --
	( 65.72, 57.67) --
	( 66.16, 57.67) --
	( 66.61, 57.67) --
	( 67.06, 57.67) --
	( 67.51, 57.67) --
	( 67.96, 57.67) --
	( 68.41, 57.67) --
	( 68.86, 57.67) --
	( 69.31, 57.67) --
	( 69.75, 57.67) --
	( 70.20, 57.67) --
	( 70.65, 57.67) --
	( 71.10, 57.67) --
	( 71.55, 57.67) --
	( 72.00, 57.67) --
	( 72.45, 57.67) --
	( 72.89, 57.67) --
	( 73.34, 57.67) --
	( 73.79, 57.67) --
	( 74.24, 57.67) --
	( 74.69, 57.67) --
	( 75.14, 57.67) --
	( 75.59, 57.67) --
	( 76.04, 57.67) --
	( 76.48, 57.67) --
	( 76.93, 57.67) --
	( 77.38, 57.67) --
	( 77.83, 57.67) --
	( 78.28, 57.67) --
	( 78.73, 57.67) --
	( 79.18, 57.67) --
	( 79.63, 57.67) --
	( 80.07, 57.67) --
	( 80.52, 57.67) --
	( 80.97, 57.67) --
	( 81.42, 57.67) --
	( 81.87, 57.67) --
	( 82.32, 57.67) --
	( 82.77, 57.67) --
	( 83.21, 57.67) --
	( 83.66, 57.67) --
	( 84.11, 57.67) --
	( 84.56, 57.67) --
	( 85.01, 57.67) --
	( 85.46, 57.67) --
	( 85.91, 57.67) --
	( 86.36, 57.67) --
	( 86.80, 57.67) --
	( 87.25, 57.67) --
	( 87.70, 57.67) --
	( 88.15, 57.67) --
	( 88.60, 57.67) --
	( 89.05, 57.67) --
	( 89.50, 57.67) --
	( 89.95, 57.67) --
	( 90.39, 57.67) --
	( 90.84, 57.67) --
	( 91.29, 57.67) --
	( 91.74, 57.67) --
	( 92.19, 57.67) --
	( 92.64, 57.67) --
	( 93.09, 57.67) --
	( 93.53, 57.67) --
	( 93.98, 57.68) --
	( 94.43, 57.68) --
	( 94.88, 57.68) --
	( 95.33, 57.69) --
	( 95.78, 57.69) --
	( 96.23, 57.69) --
	( 96.68, 57.69) --
	( 97.12, 57.69) --
	( 97.57, 57.69) --
	( 98.02, 57.69) --
	( 98.47, 57.68) --
	( 98.92, 57.68) --
	( 99.37, 57.67) --
	( 99.82, 57.67) --
	(100.27, 57.67) --
	(100.71, 57.67) --
	(101.16, 57.67) --
	(101.61, 57.67) --
	(102.06, 57.67) --
	(102.51, 57.67) --
	(102.96, 57.67) --
	(103.41, 57.67) --
	(103.85, 57.67) --
	(104.30, 57.67) --
	(104.75, 57.67) --
	(105.20, 57.67) --
	(105.65, 57.68) --
	(106.10, 57.68) --
	(106.55, 57.69) --
	(107.00, 57.69) --
	(107.44, 57.70) --
	(107.89, 57.70) --
	(108.34, 57.70) --
	(108.79, 57.71) --
	(109.24, 57.71) --
	(109.69, 57.71) --
	(110.14, 57.71) --
	(110.59, 57.71) --
	(111.03, 57.72) --
	(111.48, 57.72) --
	(111.93, 57.73) --
	(112.38, 57.74) --
	(112.83, 57.74) --
	(113.28, 57.75) --
	(113.73, 57.76) --
	(114.17, 57.77) --
	(114.62, 57.77) --
	(115.07, 57.77) --
	(115.52, 57.77) --
	(115.97, 57.77) --
	(116.42, 57.77) --
	(116.87, 57.77) --
	(117.32, 57.77) --
	(117.76, 57.78) --
	(118.21, 57.78) --
	(118.66, 57.79) --
	(119.11, 57.81) --
	(119.56, 57.82) --
	(120.01, 57.83) --
	(120.46, 57.84) --
	(120.91, 57.85) --
	(121.35, 57.85) --
	(121.80, 57.85) --
	(122.25, 57.85) --
	(122.70, 57.85) --
	(123.15, 57.85) --
	(123.60, 57.86) --
	(124.05, 57.86) --
	(124.49, 57.87) --
	(124.94, 57.88) --
	(125.39, 57.89) --
	(125.84, 57.89) --
	(126.29, 57.90) --
	(126.74, 57.92) --
	(127.19, 57.94) --
	(127.64, 57.97) --
	(128.08, 58.01) --
	(128.53, 58.05) --
	(128.98, 58.09) --
	(129.43, 58.13) --
	(129.88, 58.15) --
	(130.33, 58.17) --
	(130.78, 58.18) --
	(131.23, 58.19) --
	(131.67, 58.20) --
	(132.12, 58.21) --
	(132.57, 58.23) --
	(133.02, 58.25) --
	(133.47, 58.28) --
	(133.92, 58.30) --
	(134.37, 58.33) --
	(134.81, 58.36) --
	(135.26, 58.38) --
	(135.71, 58.41) --
	(136.16, 58.43) --
	(136.61, 58.44) --
	(137.06, 58.45) --
	(137.51, 58.47) --
	(137.96, 58.49) --
	(138.40, 58.52) --
	(138.85, 58.57) --
	(139.30, 58.64) --
	(139.75, 58.73) --
	(140.20, 58.82) --
	(140.65, 58.90) --
	(141.10, 58.95) --
	(141.55, 58.97) --
	(141.99, 58.97) --
	(142.44, 58.94) --
	(142.89, 58.91) --
	(143.34, 58.89) --
	(143.79, 58.88) --
	(144.24, 58.90) --
	(144.69, 58.95) --
	(145.13, 59.01) --
	(145.58, 59.08) --
	(146.03, 59.16) --
	(146.48, 59.24) --
	(146.93, 59.33) --
	(147.38, 59.42) --
	(147.83, 59.53) --
	(148.28, 59.63) --
	(148.72, 59.73) --
	(149.17, 59.82) --
	(149.62, 59.90) --
	(150.07, 59.97) --
	(150.52, 60.03) --
	(150.97, 60.10) --
	(151.42, 60.18) --
	(151.87, 60.27) --
	(152.31, 60.36) --
	(152.76, 60.46) --
	(153.21, 60.54) --
	(153.66, 60.59) --
	(154.11, 60.60) --
	(154.56, 60.58) --
	(155.01, 60.53) --
	(155.45, 60.46) --
	(155.90, 60.40) --
	(156.35, 60.36) --
	(156.80, 60.36) --
	(157.25, 60.40) --
	(157.70, 60.48) --
	(158.15, 60.59) --
	(158.60, 60.72) --
	(159.04, 60.85) --
	(159.49, 60.98) --
	(159.94, 61.09) --
	(160.39, 61.18) --
	(160.84, 61.26) --
	(161.29, 61.34) --
	(161.74, 61.42) --
	(162.19, 61.51) --
	(162.63, 61.62) --
	(163.08, 61.76) --
	(163.53, 61.92) --
	(163.98, 62.09) --
	(164.43, 62.25) --
	(164.88, 62.38) --
	(165.33, 62.49) --
	(165.77, 62.55) --
	(166.22, 62.59) --
	(166.67, 62.60) --
	(167.12, 62.62) --
	(167.57, 62.66) --
	(168.02, 62.71) --
	(168.47, 62.80) --
	(168.92, 62.91) --
	(169.36, 63.03) --
	(169.81, 63.17) --
	(170.26, 63.32) --
	(170.71, 63.48) --
	(171.16, 63.64) --
	(171.61, 63.80) --
	(172.06, 63.95) --
	(172.51, 64.10) --
	(172.95, 64.23) --
	(173.40, 64.33) --
	(173.85, 64.42) --
	(174.30, 64.52) --
	(174.75, 64.63) --
	(175.20, 64.77) --
	(175.65, 64.98) --
	(176.09, 65.23) --
	(176.54, 65.54) --
	(176.99, 65.87) --
	(177.44, 66.22) --
	(177.89, 66.55) --
	(178.34, 66.86) --
	(178.79, 67.12) --
	(179.24, 67.36) --
	(179.68, 67.57) --
	(180.13, 67.79) --
	(180.58, 68.05) --
	(181.03, 68.36) --
	(181.48, 68.73) --
	(181.93, 69.16) --
	(182.38, 69.63) --
	(182.83, 70.13) --
	(183.27, 70.62) --
	(183.72, 71.07) --
	(184.17, 71.46) --
	(184.62, 71.77) --
	(185.07, 72.00) --
	(185.52, 72.16) --
	(185.97, 72.27) --
	(186.41, 72.38) --
	(186.86, 72.51) --
	(187.31, 72.72) --
	(187.76, 73.06) --
	(188.21, 73.59) --
	(188.66, 74.34) --
	(189.11, 75.38) --
	(189.56, 76.73) --
	(190.00, 78.37) --
	(190.45, 80.24) --
	(190.90, 82.21) --
	(191.35, 84.10) --
	(191.80, 85.72) --
	(192.25, 86.91) --
	(192.70, 87.61) --
	(193.15, 87.88) --
	(193.59, 87.88) --
	(194.04, 87.79) --
	(194.49, 87.74) --
	(194.94, 87.84) --
	(195.39, 88.13) --
	(195.84, 88.59) --
	(196.29, 89.21) --
	(196.73, 89.97) --
	(197.18, 90.90) --
	(197.63, 92.03) --
	(198.08, 93.42) --
	(198.53, 95.10) --
	(198.98, 97.07) --
	(199.43, 99.25) --
	(199.88,101.51) --
	(200.32,103.68) --
	(200.77,105.60) --
	(201.22,107.22) --
	(201.67,108.57) --
	(202.12,109.78) --
	(202.57,111.05) --
	(203.02,112.51) --
	(203.47,114.27) --
	(203.91,116.32) --
	(204.36,118.62) --
	(204.81,121.05) --
	(205.26,123.48) --
	(205.71,125.84) --
	(206.16,128.09) --
	(206.61,130.27) --
	(207.05,132.48) --
	(207.50,134.74) --
	(207.95,137.07) --
	(208.40,139.36) --
	(208.85,141.51) --
	(209.30,143.40) --
	(209.75,145.01) --
	(210.20,146.39) --
	(210.64,147.64) --
	(211.09,148.86) --
	(211.54,150.09) --
	(211.99,151.28) --
	(212.44,152.40) --
	(212.89,153.38) --
	(213.34,154.16) --
	(213.79,154.72) --
	(214.23,155.06) --
	(214.68,155.21) --
	(215.13,155.24) --
	(215.58,155.20) --
	(216.03,155.11) --
	(216.48,154.98) --
	(216.93,154.77) --
	(217.37,154.41) --
	(217.82,153.86) --
	(218.27,153.09) --
	(218.72,152.08) --
	(219.17,150.85) --
	(219.62,149.46) --
	(220.07,147.95) --
	(220.52,146.36) --
	(220.96,144.71) --
	(221.41,143.03) --
	(221.86,141.30) --
	(222.31,139.53) --
	(222.76,137.70) --
	(223.21,135.84) --
	(223.66,133.95) --
	(224.11,132.04) --
	(224.55,130.11) --
	(225.00,128.15) --
	(225.45,126.16) --
	(225.90,124.13) --
	(226.35,122.06) --
	(226.80,119.97) --
	(227.25,117.88) --
	(227.69,115.85) --
	(228.14,113.92) --
	(228.59,112.14) --
	(229.04,110.54) --
	(229.49,109.08) --
	(229.94,107.70) --
	(230.39,106.31) --
	(230.84,104.79) --
	(231.28,103.03) --
	(231.73,100.95) --
	(232.18, 98.50) --
	(232.63, 95.66) --
	(233.08, 92.47) --
	(233.53, 89.01) --
	(233.98, 85.40) --
	(234.43, 81.77) --
	(234.87, 78.25) --
	(235.32, 74.97) --
	(235.77, 72.00) --
	(236.22, 69.38) --
	(236.67, 67.11) --
	(237.12, 65.15) --
	(237.57, 63.48) --
	(238.01, 62.06) --
	(238.46, 60.89) --
	(238.91, 59.94) --
	(239.36, 59.21) --
	(239.81, 58.66) --
	(240.26, 58.28) --
	(240.71, 58.02) --
	(241.16, 57.86) --
	(241.60, 57.77) --
	(242.05, 57.72) --
	(242.50, 57.69) --
	(242.95, 57.68) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67) --
	(272.12, 57.67) --
	(271.67, 57.67) --
	(271.22, 57.67) --
	(270.77, 57.67) --
	(270.32, 57.67) --
	(269.87, 57.67) --
	(269.42, 57.67) --
	(268.97, 57.67) --
	(268.53, 57.67) --
	(268.08, 57.67) --
	(267.63, 57.67) --
	(267.18, 57.67) --
	(266.73, 57.67) --
	(266.28, 57.67) --
	(265.83, 57.67) --
	(265.39, 57.67) --
	(264.94, 57.67) --
	(264.49, 57.67) --
	(264.04, 57.67) --
	(263.59, 57.67) --
	(263.14, 57.67) --
	(262.69, 57.67) --
	(262.24, 57.67) --
	(261.80, 57.67) --
	(261.35, 57.67) --
	(260.90, 57.67) --
	(260.45, 57.67) --
	(260.00, 57.67) --
	(259.55, 57.67) --
	(259.10, 57.67) --
	(258.65, 57.67) --
	(258.21, 57.67) --
	(257.76, 57.67) --
	(257.31, 57.67) --
	(256.86, 57.67) --
	(256.41, 57.67) --
	(255.96, 57.67) --
	(255.51, 57.67) --
	(255.07, 57.67) --
	(254.62, 57.67) --
	(254.17, 57.67) --
	(253.72, 57.67) --
	(253.27, 57.67) --
	(252.82, 57.67) --
	(252.37, 57.67) --
	(251.92, 57.67) --
	(251.48, 57.67) --
	(251.03, 57.67) --
	(250.58, 57.67) --
	(250.13, 57.67) --
	(249.68, 57.67) --
	(249.23, 57.67) --
	(248.78, 57.67) --
	(248.33, 57.67) --
	(247.89, 57.67) --
	(247.44, 57.67) --
	(246.99, 57.67) --
	(246.54, 57.67) --
	(246.09, 57.67) --
	(245.64, 57.67) --
	(245.19, 57.67) --
	(244.75, 57.67) --
	(244.30, 57.67) --
	(243.85, 57.67) --
	(243.40, 57.67) --
	(242.95, 57.67) --
	(242.50, 57.67) --
	(242.05, 57.67) --
	(241.60, 57.67) --
	(241.16, 57.67) --
	(240.71, 57.67) --
	(240.26, 57.67) --
	(239.81, 57.67) --
	(239.36, 57.67) --
	(238.91, 57.67) --
	(238.46, 57.67) --
	(238.01, 57.67) --
	(237.57, 57.67) --
	(237.12, 57.67) --
	(236.67, 57.67) --
	(236.22, 57.67) --
	(235.77, 57.67) --
	(235.32, 57.67) --
	(234.87, 57.67) --
	(234.43, 57.67) --
	(233.98, 57.67) --
	(233.53, 57.67) --
	(233.08, 57.67) --
	(232.63, 57.67) --
	(232.18, 57.67) --
	(231.73, 57.67) --
	(231.28, 57.67) --
	(230.84, 57.67) --
	(230.39, 57.67) --
	(229.94, 57.67) --
	(229.49, 57.67) --
	(229.04, 57.67) --
	(228.59, 57.67) --
	(228.14, 57.67) --
	(227.69, 57.67) --
	(227.25, 57.67) --
	(226.80, 57.67) --
	(226.35, 57.67) --
	(225.90, 57.67) --
	(225.45, 57.67) --
	(225.00, 57.67) --
	(224.55, 57.67) --
	(224.11, 57.67) --
	(223.66, 57.67) --
	(223.21, 57.67) --
	(222.76, 57.67) --
	(222.31, 57.67) --
	(221.86, 57.67) --
	(221.41, 57.67) --
	(220.96, 57.67) --
	(220.52, 57.67) --
	(220.07, 57.67) --
	(219.62, 57.67) --
	(219.17, 57.67) --
	(218.72, 57.67) --
	(218.27, 57.67) --
	(217.82, 57.67) --
	(217.37, 57.67) --
	(216.93, 57.67) --
	(216.48, 57.67) --
	(216.03, 57.67) --
	(215.58, 57.67) --
	(215.13, 57.67) --
	(214.68, 57.67) --
	(214.23, 57.67) --
	(213.79, 57.67) --
	(213.34, 57.67) --
	(212.89, 57.67) --
	(212.44, 57.67) --
	(211.99, 57.67) --
	(211.54, 57.67) --
	(211.09, 57.67) --
	(210.64, 57.67) --
	(210.20, 57.67) --
	(209.75, 57.67) --
	(209.30, 57.67) --
	(208.85, 57.67) --
	(208.40, 57.67) --
	(207.95, 57.67) --
	(207.50, 57.67) --
	(207.05, 57.67) --
	(206.61, 57.67) --
	(206.16, 57.67) --
	(205.71, 57.67) --
	(205.26, 57.67) --
	(204.81, 57.67) --
	(204.36, 57.67) --
	(203.91, 57.67) --
	(203.47, 57.67) --
	(203.02, 57.67) --
	(202.57, 57.67) --
	(202.12, 57.67) --
	(201.67, 57.67) --
	(201.22, 57.67) --
	(200.77, 57.67) --
	(200.32, 57.67) --
	(199.88, 57.67) --
	(199.43, 57.67) --
	(198.98, 57.67) --
	(198.53, 57.67) --
	(198.08, 57.67) --
	(197.63, 57.67) --
	(197.18, 57.67) --
	(196.73, 57.67) --
	(196.29, 57.67) --
	(195.84, 57.67) --
	(195.39, 57.67) --
	(194.94, 57.67) --
	(194.49, 57.67) --
	(194.04, 57.67) --
	(193.59, 57.67) --
	(193.15, 57.67) --
	(192.70, 57.67) --
	(192.25, 57.67) --
	(191.80, 57.67) --
	(191.35, 57.67) --
	(190.90, 57.67) --
	(190.45, 57.67) --
	(190.00, 57.67) --
	(189.56, 57.67) --
	(189.11, 57.67) --
	(188.66, 57.67) --
	(188.21, 57.67) --
	(187.76, 57.67) --
	(187.31, 57.67) --
	(186.86, 57.67) --
	(186.41, 57.67) --
	(185.97, 57.67) --
	(185.52, 57.67) --
	(185.07, 57.67) --
	(184.62, 57.67) --
	(184.17, 57.67) --
	(183.72, 57.67) --
	(183.27, 57.67) --
	(182.83, 57.67) --
	(182.38, 57.67) --
	(181.93, 57.67) --
	(181.48, 57.67) --
	(181.03, 57.67) --
	(180.58, 57.67) --
	(180.13, 57.67) --
	(179.68, 57.67) --
	(179.24, 57.67) --
	(178.79, 57.67) --
	(178.34, 57.67) --
	(177.89, 57.67) --
	(177.44, 57.67) --
	(176.99, 57.67) --
	(176.54, 57.67) --
	(176.09, 57.67) --
	(175.65, 57.67) --
	(175.20, 57.67) --
	(174.75, 57.67) --
	(174.30, 57.67) --
	(173.85, 57.67) --
	(173.40, 57.67) --
	(172.95, 57.67) --
	(172.51, 57.67) --
	(172.06, 57.67) --
	(171.61, 57.67) --
	(171.16, 57.67) --
	(170.71, 57.67) --
	(170.26, 57.67) --
	(169.81, 57.67) --
	(169.36, 57.67) --
	(168.92, 57.67) --
	(168.47, 57.67) --
	(168.02, 57.67) --
	(167.57, 57.67) --
	(167.12, 57.67) --
	(166.67, 57.67) --
	(166.22, 57.67) --
	(165.77, 57.67) --
	(165.33, 57.67) --
	(164.88, 57.67) --
	(164.43, 57.67) --
	(163.98, 57.67) --
	(163.53, 57.67) --
	(163.08, 57.67) --
	(162.63, 57.67) --
	(162.19, 57.67) --
	(161.74, 57.67) --
	(161.29, 57.67) --
	(160.84, 57.67) --
	(160.39, 57.67) --
	(159.94, 57.67) --
	(159.49, 57.67) --
	(159.04, 57.67) --
	(158.60, 57.67) --
	(158.15, 57.67) --
	(157.70, 57.67) --
	(157.25, 57.67) --
	(156.80, 57.67) --
	(156.35, 57.67) --
	(155.90, 57.67) --
	(155.45, 57.67) --
	(155.01, 57.67) --
	(154.56, 57.67) --
	(154.11, 57.67) --
	(153.66, 57.67) --
	(153.21, 57.67) --
	(152.76, 57.67) --
	(152.31, 57.67) --
	(151.87, 57.67) --
	(151.42, 57.67) --
	(150.97, 57.67) --
	(150.52, 57.67) --
	(150.07, 57.67) --
	(149.62, 57.67) --
	(149.17, 57.67) --
	(148.72, 57.67) --
	(148.28, 57.67) --
	(147.83, 57.67) --
	(147.38, 57.67) --
	(146.93, 57.67) --
	(146.48, 57.67) --
	(146.03, 57.67) --
	(145.58, 57.67) --
	(145.13, 57.67) --
	(144.69, 57.67) --
	(144.24, 57.67) --
	(143.79, 57.67) --
	(143.34, 57.67) --
	(142.89, 57.67) --
	(142.44, 57.67) --
	(141.99, 57.67) --
	(141.55, 57.67) --
	(141.10, 57.67) --
	(140.65, 57.67) --
	(140.20, 57.67) --
	(139.75, 57.67) --
	(139.30, 57.67) --
	(138.85, 57.67) --
	(138.40, 57.67) --
	(137.96, 57.67) --
	(137.51, 57.67) --
	(137.06, 57.67) --
	(136.61, 57.67) --
	(136.16, 57.67) --
	(135.71, 57.67) --
	(135.26, 57.67) --
	(134.81, 57.67) --
	(134.37, 57.67) --
	(133.92, 57.67) --
	(133.47, 57.67) --
	(133.02, 57.67) --
	(132.57, 57.67) --
	(132.12, 57.67) --
	(131.67, 57.67) --
	(131.23, 57.67) --
	(130.78, 57.67) --
	(130.33, 57.67) --
	(129.88, 57.67) --
	(129.43, 57.67) --
	(128.98, 57.67) --
	(128.53, 57.67) --
	(128.08, 57.67) --
	(127.64, 57.67) --
	(127.19, 57.67) --
	(126.74, 57.67) --
	(126.29, 57.67) --
	(125.84, 57.67) --
	(125.39, 57.67) --
	(124.94, 57.67) --
	(124.49, 57.67) --
	(124.05, 57.67) --
	(123.60, 57.67) --
	(123.15, 57.67) --
	(122.70, 57.67) --
	(122.25, 57.67) --
	(121.80, 57.67) --
	(121.35, 57.67) --
	(120.91, 57.67) --
	(120.46, 57.67) --
	(120.01, 57.67) --
	(119.56, 57.67) --
	(119.11, 57.67) --
	(118.66, 57.67) --
	(118.21, 57.67) --
	(117.76, 57.67) --
	(117.32, 57.67) --
	(116.87, 57.67) --
	(116.42, 57.67) --
	(115.97, 57.67) --
	(115.52, 57.67) --
	(115.07, 57.67) --
	(114.62, 57.67) --
	(114.17, 57.67) --
	(113.73, 57.67) --
	(113.28, 57.67) --
	(112.83, 57.67) --
	(112.38, 57.67) --
	(111.93, 57.67) --
	(111.48, 57.67) --
	(111.03, 57.67) --
	(110.59, 57.67) --
	(110.14, 57.67) --
	(109.69, 57.67) --
	(109.24, 57.67) --
	(108.79, 57.67) --
	(108.34, 57.67) --
	(107.89, 57.67) --
	(107.44, 57.67) --
	(107.00, 57.67) --
	(106.55, 57.67) --
	(106.10, 57.67) --
	(105.65, 57.67) --
	(105.20, 57.67) --
	(104.75, 57.67) --
	(104.30, 57.67) --
	(103.85, 57.67) --
	(103.41, 57.67) --
	(102.96, 57.67) --
	(102.51, 57.67) --
	(102.06, 57.67) --
	(101.61, 57.67) --
	(101.16, 57.67) --
	(100.71, 57.67) --
	(100.27, 57.67) --
	( 99.82, 57.67) --
	( 99.37, 57.67) --
	( 98.92, 57.67) --
	( 98.47, 57.67) --
	( 98.02, 57.67) --
	( 97.57, 57.67) --
	( 97.12, 57.67) --
	( 96.68, 57.67) --
	( 96.23, 57.67) --
	( 95.78, 57.67) --
	( 95.33, 57.67) --
	( 94.88, 57.67) --
	( 94.43, 57.67) --
	( 93.98, 57.67) --
	( 93.53, 57.67) --
	( 93.09, 57.67) --
	( 92.64, 57.67) --
	( 92.19, 57.67) --
	( 91.74, 57.67) --
	( 91.29, 57.67) --
	( 90.84, 57.67) --
	( 90.39, 57.67) --
	( 89.95, 57.67) --
	( 89.50, 57.67) --
	( 89.05, 57.67) --
	( 88.60, 57.67) --
	( 88.15, 57.67) --
	( 87.70, 57.67) --
	( 87.25, 57.67) --
	( 86.80, 57.67) --
	( 86.36, 57.67) --
	( 85.91, 57.67) --
	( 85.46, 57.67) --
	( 85.01, 57.67) --
	( 84.56, 57.67) --
	( 84.11, 57.67) --
	( 83.66, 57.67) --
	( 83.21, 57.67) --
	( 82.77, 57.67) --
	( 82.32, 57.67) --
	( 81.87, 57.67) --
	( 81.42, 57.67) --
	( 80.97, 57.67) --
	( 80.52, 57.67) --
	( 80.07, 57.67) --
	( 79.63, 57.67) --
	( 79.18, 57.67) --
	( 78.73, 57.67) --
	( 78.28, 57.67) --
	( 77.83, 57.67) --
	( 77.38, 57.67) --
	( 76.93, 57.67) --
	( 76.48, 57.67) --
	( 76.04, 57.67) --
	( 75.59, 57.67) --
	( 75.14, 57.67) --
	( 74.69, 57.67) --
	( 74.24, 57.67) --
	( 73.79, 57.67) --
	( 73.34, 57.67) --
	( 72.89, 57.67) --
	( 72.45, 57.67) --
	( 72.00, 57.67) --
	( 71.55, 57.67) --
	( 71.10, 57.67) --
	( 70.65, 57.67) --
	( 70.20, 57.67) --
	( 69.75, 57.67) --
	( 69.31, 57.67) --
	( 68.86, 57.67) --
	( 68.41, 57.67) --
	( 67.96, 57.67) --
	( 67.51, 57.67) --
	( 67.06, 57.67) --
	( 66.61, 57.67) --
	( 66.16, 57.67) --
	( 65.72, 57.67) --
	( 65.27, 57.67) --
	( 64.82, 57.67) --
	( 64.37, 57.67) --
	( 63.92, 57.67) --
	( 63.47, 57.67) --
	( 63.02, 57.67) --
	( 62.57, 57.67) --
	( 62.13, 57.67) --
	( 61.68, 57.67) --
	( 61.23, 57.67) --
	( 60.78, 57.67) --
	( 60.33, 57.67) --
	( 59.88, 57.67) --
	( 59.43, 57.67) --
	( 58.99, 57.67) --
	( 58.54, 57.67) --
	( 58.09, 57.67) --
	( 57.64, 57.67) --
	( 57.19, 57.67) --
	( 56.74, 57.67) --
	( 56.29, 57.67) --
	( 55.84, 57.67) --
	( 55.40, 57.67) --
	( 54.95, 57.67) --
	( 54.50, 57.67) --
	( 54.05, 57.67) --
	( 53.60, 57.67) --
	( 53.15, 57.67) --
	( 52.70, 57.67) --
	( 52.25, 57.67) --
	( 51.81, 57.67) --
	( 51.36, 57.67) --
	( 50.91, 57.67) --
	( 50.46, 57.67) --
	( 50.01, 57.67) --
	( 49.56, 57.67) --
	( 49.11, 57.67) --
	( 48.67, 57.67) --
	( 48.22, 57.67) --
	( 47.77, 57.67) --
	( 47.32, 57.67) --
	( 46.87, 57.67) --
	( 46.42, 57.67) --
	( 45.97, 57.67) --
	( 45.52, 57.67) --
	( 45.08, 57.67) --
	( 44.63, 57.67) --
	( 44.18, 57.67) --
	( 43.73, 57.67) --
	( 43.28, 57.67) --
	( 42.83, 57.67) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round,line cap=round] ( 42.83, 57.67) --
	( 43.28, 57.67) --
	( 43.73, 57.67) --
	( 44.18, 57.67) --
	( 44.63, 57.67) --
	( 45.08, 57.67) --
	( 45.52, 57.67) --
	( 45.97, 57.67) --
	( 46.42, 57.67) --
	( 46.87, 57.67) --
	( 47.32, 57.67) --
	( 47.77, 57.67) --
	( 48.22, 57.67) --
	( 48.67, 57.67) --
	( 49.11, 57.67) --
	( 49.56, 57.67) --
	( 50.01, 57.67) --
	( 50.46, 57.67) --
	( 50.91, 57.67) --
	( 51.36, 57.67) --
	( 51.81, 57.67) --
	( 52.25, 57.67) --
	( 52.70, 57.67) --
	( 53.15, 57.67) --
	( 53.60, 57.67) --
	( 54.05, 57.67) --
	( 54.50, 57.67) --
	( 54.95, 57.67) --
	( 55.40, 57.67) --
	( 55.84, 57.67) --
	( 56.29, 57.67) --
	( 56.74, 57.67) --
	( 57.19, 57.67) --
	( 57.64, 57.67) --
	( 58.09, 57.67) --
	( 58.54, 57.67) --
	( 58.99, 57.67) --
	( 59.43, 57.67) --
	( 59.88, 57.67) --
	( 60.33, 57.67) --
	( 60.78, 57.67) --
	( 61.23, 57.67) --
	( 61.68, 57.67) --
	( 62.13, 57.67) --
	( 62.57, 57.67) --
	( 63.02, 57.67) --
	( 63.47, 57.67) --
	( 63.92, 57.67) --
	( 64.37, 57.67) --
	( 64.82, 57.67) --
	( 65.27, 57.67) --
	( 65.72, 57.67) --
	( 66.16, 57.67) --
	( 66.61, 57.67) --
	( 67.06, 57.67) --
	( 67.51, 57.67) --
	( 67.96, 57.67) --
	( 68.41, 57.67) --
	( 68.86, 57.67) --
	( 69.31, 57.67) --
	( 69.75, 57.67) --
	( 70.20, 57.67) --
	( 70.65, 57.67) --
	( 71.10, 57.67) --
	( 71.55, 57.67) --
	( 72.00, 57.67) --
	( 72.45, 57.67) --
	( 72.89, 57.67) --
	( 73.34, 57.67) --
	( 73.79, 57.67) --
	( 74.24, 57.67) --
	( 74.69, 57.67) --
	( 75.14, 57.67) --
	( 75.59, 57.67) --
	( 76.04, 57.67) --
	( 76.48, 57.67) --
	( 76.93, 57.67) --
	( 77.38, 57.67) --
	( 77.83, 57.67) --
	( 78.28, 57.67) --
	( 78.73, 57.67) --
	( 79.18, 57.67) --
	( 79.63, 57.67) --
	( 80.07, 57.67) --
	( 80.52, 57.67) --
	( 80.97, 57.67) --
	( 81.42, 57.67) --
	( 81.87, 57.67) --
	( 82.32, 57.67) --
	( 82.77, 57.67) --
	( 83.21, 57.67) --
	( 83.66, 57.67) --
	( 84.11, 57.67) --
	( 84.56, 57.67) --
	( 85.01, 57.67) --
	( 85.46, 57.67) --
	( 85.91, 57.67) --
	( 86.36, 57.67) --
	( 86.80, 57.67) --
	( 87.25, 57.67) --
	( 87.70, 57.67) --
	( 88.15, 57.67) --
	( 88.60, 57.67) --
	( 89.05, 57.67) --
	( 89.50, 57.67) --
	( 89.95, 57.67) --
	( 90.39, 57.67) --
	( 90.84, 57.67) --
	( 91.29, 57.67) --
	( 91.74, 57.67) --
	( 92.19, 57.67) --
	( 92.64, 57.67) --
	( 93.09, 57.67) --
	( 93.53, 57.67) --
	( 93.98, 57.68) --
	( 94.43, 57.68) --
	( 94.88, 57.68) --
	( 95.33, 57.69) --
	( 95.78, 57.69) --
	( 96.23, 57.69) --
	( 96.68, 57.69) --
	( 97.12, 57.69) --
	( 97.57, 57.69) --
	( 98.02, 57.69) --
	( 98.47, 57.68) --
	( 98.92, 57.68) --
	( 99.37, 57.67) --
	( 99.82, 57.67) --
	(100.27, 57.67) --
	(100.71, 57.67) --
	(101.16, 57.67) --
	(101.61, 57.67) --
	(102.06, 57.67) --
	(102.51, 57.67) --
	(102.96, 57.67) --
	(103.41, 57.67) --
	(103.85, 57.67) --
	(104.30, 57.67) --
	(104.75, 57.67) --
	(105.20, 57.67) --
	(105.65, 57.68) --
	(106.10, 57.68) --
	(106.55, 57.69) --
	(107.00, 57.69) --
	(107.44, 57.70) --
	(107.89, 57.70) --
	(108.34, 57.70) --
	(108.79, 57.71) --
	(109.24, 57.71) --
	(109.69, 57.71) --
	(110.14, 57.71) --
	(110.59, 57.71) --
	(111.03, 57.72) --
	(111.48, 57.72) --
	(111.93, 57.73) --
	(112.38, 57.74) --
	(112.83, 57.74) --
	(113.28, 57.75) --
	(113.73, 57.76) --
	(114.17, 57.77) --
	(114.62, 57.77) --
	(115.07, 57.77) --
	(115.52, 57.77) --
	(115.97, 57.77) --
	(116.42, 57.77) --
	(116.87, 57.77) --
	(117.32, 57.77) --
	(117.76, 57.78) --
	(118.21, 57.78) --
	(118.66, 57.79) --
	(119.11, 57.81) --
	(119.56, 57.82) --
	(120.01, 57.83) --
	(120.46, 57.84) --
	(120.91, 57.85) --
	(121.35, 57.85) --
	(121.80, 57.85) --
	(122.25, 57.85) --
	(122.70, 57.85) --
	(123.15, 57.85) --
	(123.60, 57.86) --
	(124.05, 57.86) --
	(124.49, 57.87) --
	(124.94, 57.88) --
	(125.39, 57.89) --
	(125.84, 57.89) --
	(126.29, 57.90) --
	(126.74, 57.92) --
	(127.19, 57.94) --
	(127.64, 57.97) --
	(128.08, 58.01) --
	(128.53, 58.05) --
	(128.98, 58.09) --
	(129.43, 58.13) --
	(129.88, 58.15) --
	(130.33, 58.17) --
	(130.78, 58.18) --
	(131.23, 58.19) --
	(131.67, 58.20) --
	(132.12, 58.21) --
	(132.57, 58.23) --
	(133.02, 58.25) --
	(133.47, 58.28) --
	(133.92, 58.30) --
	(134.37, 58.33) --
	(134.81, 58.36) --
	(135.26, 58.38) --
	(135.71, 58.41) --
	(136.16, 58.43) --
	(136.61, 58.44) --
	(137.06, 58.45) --
	(137.51, 58.47) --
	(137.96, 58.49) --
	(138.40, 58.52) --
	(138.85, 58.57) --
	(139.30, 58.64) --
	(139.75, 58.73) --
	(140.20, 58.82) --
	(140.65, 58.90) --
	(141.10, 58.95) --
	(141.55, 58.97) --
	(141.99, 58.97) --
	(142.44, 58.94) --
	(142.89, 58.91) --
	(143.34, 58.89) --
	(143.79, 58.88) --
	(144.24, 58.90) --
	(144.69, 58.95) --
	(145.13, 59.01) --
	(145.58, 59.08) --
	(146.03, 59.16) --
	(146.48, 59.24) --
	(146.93, 59.33) --
	(147.38, 59.42) --
	(147.83, 59.53) --
	(148.28, 59.63) --
	(148.72, 59.73) --
	(149.17, 59.82) --
	(149.62, 59.90) --
	(150.07, 59.97) --
	(150.52, 60.03) --
	(150.97, 60.10) --
	(151.42, 60.18) --
	(151.87, 60.27) --
	(152.31, 60.36) --
	(152.76, 60.46) --
	(153.21, 60.54) --
	(153.66, 60.59) --
	(154.11, 60.60) --
	(154.56, 60.58) --
	(155.01, 60.53) --
	(155.45, 60.46) --
	(155.90, 60.40) --
	(156.35, 60.36) --
	(156.80, 60.36) --
	(157.25, 60.40) --
	(157.70, 60.48) --
	(158.15, 60.59) --
	(158.60, 60.72) --
	(159.04, 60.85) --
	(159.49, 60.98) --
	(159.94, 61.09) --
	(160.39, 61.18) --
	(160.84, 61.26) --
	(161.29, 61.34) --
	(161.74, 61.42) --
	(162.19, 61.51) --
	(162.63, 61.62) --
	(163.08, 61.76) --
	(163.53, 61.92) --
	(163.98, 62.09) --
	(164.43, 62.25) --
	(164.88, 62.38) --
	(165.33, 62.49) --
	(165.77, 62.55) --
	(166.22, 62.59) --
	(166.67, 62.60) --
	(167.12, 62.62) --
	(167.57, 62.66) --
	(168.02, 62.71) --
	(168.47, 62.80) --
	(168.92, 62.91) --
	(169.36, 63.03) --
	(169.81, 63.17) --
	(170.26, 63.32) --
	(170.71, 63.48) --
	(171.16, 63.64) --
	(171.61, 63.80) --
	(172.06, 63.95) --
	(172.51, 64.10) --
	(172.95, 64.23) --
	(173.40, 64.33) --
	(173.85, 64.42) --
	(174.30, 64.52) --
	(174.75, 64.63) --
	(175.20, 64.77) --
	(175.65, 64.98) --
	(176.09, 65.23) --
	(176.54, 65.54) --
	(176.99, 65.87) --
	(177.44, 66.22) --
	(177.89, 66.55) --
	(178.34, 66.86) --
	(178.79, 67.12) --
	(179.24, 67.36) --
	(179.68, 67.57) --
	(180.13, 67.79) --
	(180.58, 68.05) --
	(181.03, 68.36) --
	(181.48, 68.73) --
	(181.93, 69.16) --
	(182.38, 69.63) --
	(182.83, 70.13) --
	(183.27, 70.62) --
	(183.72, 71.07) --
	(184.17, 71.46) --
	(184.62, 71.77) --
	(185.07, 72.00) --
	(185.52, 72.16) --
	(185.97, 72.27) --
	(186.41, 72.38) --
	(186.86, 72.51) --
	(187.31, 72.72) --
	(187.76, 73.06) --
	(188.21, 73.59) --
	(188.66, 74.34) --
	(189.11, 75.38) --
	(189.56, 76.73) --
	(190.00, 78.37) --
	(190.45, 80.24) --
	(190.90, 82.21) --
	(191.35, 84.10) --
	(191.80, 85.72) --
	(192.25, 86.91) --
	(192.70, 87.61) --
	(193.15, 87.88) --
	(193.59, 87.88) --
	(194.04, 87.79) --
	(194.49, 87.74) --
	(194.94, 87.84) --
	(195.39, 88.13) --
	(195.84, 88.59) --
	(196.29, 89.21) --
	(196.73, 89.97) --
	(197.18, 90.90) --
	(197.63, 92.03) --
	(198.08, 93.42) --
	(198.53, 95.10) --
	(198.98, 97.07) --
	(199.43, 99.25) --
	(199.88,101.51) --
	(200.32,103.68) --
	(200.77,105.60) --
	(201.22,107.22) --
	(201.67,108.57) --
	(202.12,109.78) --
	(202.57,111.05) --
	(203.02,112.51) --
	(203.47,114.27) --
	(203.91,116.32) --
	(204.36,118.62) --
	(204.81,121.05) --
	(205.26,123.48) --
	(205.71,125.84) --
	(206.16,128.09) --
	(206.61,130.27) --
	(207.05,132.48) --
	(207.50,134.74) --
	(207.95,137.07) --
	(208.40,139.36) --
	(208.85,141.51) --
	(209.30,143.40) --
	(209.75,145.01) --
	(210.20,146.39) --
	(210.64,147.64) --
	(211.09,148.86) --
	(211.54,150.09) --
	(211.99,151.28) --
	(212.44,152.40) --
	(212.89,153.38) --
	(213.34,154.16) --
	(213.79,154.72) --
	(214.23,155.06) --
	(214.68,155.21) --
	(215.13,155.24) --
	(215.58,155.20) --
	(216.03,155.11) --
	(216.48,154.98) --
	(216.93,154.77) --
	(217.37,154.41) --
	(217.82,153.86) --
	(218.27,153.09) --
	(218.72,152.08) --
	(219.17,150.85) --
	(219.62,149.46) --
	(220.07,147.95) --
	(220.52,146.36) --
	(220.96,144.71) --
	(221.41,143.03) --
	(221.86,141.30) --
	(222.31,139.53) --
	(222.76,137.70) --
	(223.21,135.84) --
	(223.66,133.95) --
	(224.11,132.04) --
	(224.55,130.11) --
	(225.00,128.15) --
	(225.45,126.16) --
	(225.90,124.13) --
	(226.35,122.06) --
	(226.80,119.97) --
	(227.25,117.88) --
	(227.69,115.85) --
	(228.14,113.92) --
	(228.59,112.14) --
	(229.04,110.54) --
	(229.49,109.08) --
	(229.94,107.70) --
	(230.39,106.31) --
	(230.84,104.79) --
	(231.28,103.03) --
	(231.73,100.95) --
	(232.18, 98.50) --
	(232.63, 95.66) --
	(233.08, 92.47) --
	(233.53, 89.01) --
	(233.98, 85.40) --
	(234.43, 81.77) --
	(234.87, 78.25) --
	(235.32, 74.97) --
	(235.77, 72.00) --
	(236.22, 69.38) --
	(236.67, 67.11) --
	(237.12, 65.15) --
	(237.57, 63.48) --
	(238.01, 62.06) --
	(238.46, 60.89) --
	(238.91, 59.94) --
	(239.36, 59.21) --
	(239.81, 58.66) --
	(240.26, 58.28) --
	(240.71, 58.02) --
	(241.16, 57.86) --
	(241.60, 57.77) --
	(242.05, 57.72) --
	(242.50, 57.69) --
	(242.95, 57.68) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67);

\path[] ( 42.83, 57.67) --
	( 43.28, 57.67) --
	( 43.73, 57.67) --
	( 44.18, 57.67) --
	( 44.63, 57.67) --
	( 45.08, 57.67) --
	( 45.52, 57.67) --
	( 45.97, 57.67) --
	( 46.42, 57.67) --
	( 46.87, 57.67) --
	( 47.32, 57.67) --
	( 47.77, 57.67) --
	( 48.22, 57.67) --
	( 48.67, 57.67) --
	( 49.11, 57.67) --
	( 49.56, 57.67) --
	( 50.01, 57.67) --
	( 50.46, 57.67) --
	( 50.91, 57.67) --
	( 51.36, 57.67) --
	( 51.81, 57.67) --
	( 52.25, 57.67) --
	( 52.70, 57.67) --
	( 53.15, 57.67) --
	( 53.60, 57.67) --
	( 54.05, 57.67) --
	( 54.50, 57.67) --
	( 54.95, 57.67) --
	( 55.40, 57.67) --
	( 55.84, 57.67) --
	( 56.29, 57.67) --
	( 56.74, 57.67) --
	( 57.19, 57.67) --
	( 57.64, 57.67) --
	( 58.09, 57.67) --
	( 58.54, 57.67) --
	( 58.99, 57.67) --
	( 59.43, 57.67) --
	( 59.88, 57.67) --
	( 60.33, 57.67) --
	( 60.78, 57.67) --
	( 61.23, 57.67) --
	( 61.68, 57.67) --
	( 62.13, 57.67) --
	( 62.57, 57.67) --
	( 63.02, 57.67) --
	( 63.47, 57.67) --
	( 63.92, 57.67) --
	( 64.37, 57.67) --
	( 64.82, 57.67) --
	( 65.27, 57.67) --
	( 65.72, 57.67) --
	( 66.16, 57.67) --
	( 66.61, 57.67) --
	( 67.06, 57.67) --
	( 67.51, 57.67) --
	( 67.96, 57.67) --
	( 68.41, 57.67) --
	( 68.86, 57.67) --
	( 69.31, 57.67) --
	( 69.75, 57.67) --
	( 70.20, 57.67) --
	( 70.65, 57.67) --
	( 71.10, 57.67) --
	( 71.55, 57.67) --
	( 72.00, 57.67) --
	( 72.45, 57.67) --
	( 72.89, 57.67) --
	( 73.34, 57.67) --
	( 73.79, 57.67) --
	( 74.24, 57.67) --
	( 74.69, 57.67) --
	( 75.14, 57.67) --
	( 75.59, 57.67) --
	( 76.04, 57.67) --
	( 76.48, 57.67) --
	( 76.93, 57.67) --
	( 77.38, 57.67) --
	( 77.83, 57.67) --
	( 78.28, 57.67) --
	( 78.73, 57.67) --
	( 79.18, 57.67) --
	( 79.63, 57.67) --
	( 80.07, 57.67) --
	( 80.52, 57.67) --
	( 80.97, 57.67) --
	( 81.42, 57.67) --
	( 81.87, 57.67) --
	( 82.32, 57.67) --
	( 82.77, 57.67) --
	( 83.21, 57.67) --
	( 83.66, 57.67) --
	( 84.11, 57.67) --
	( 84.56, 57.67) --
	( 85.01, 57.67) --
	( 85.46, 57.67) --
	( 85.91, 57.67) --
	( 86.36, 57.67) --
	( 86.80, 57.67) --
	( 87.25, 57.67) --
	( 87.70, 57.67) --
	( 88.15, 57.67) --
	( 88.60, 57.67) --
	( 89.05, 57.67) --
	( 89.50, 57.67) --
	( 89.95, 57.67) --
	( 90.39, 57.67) --
	( 90.84, 57.67) --
	( 91.29, 57.67) --
	( 91.74, 57.67) --
	( 92.19, 57.67) --
	( 92.64, 57.67) --
	( 93.09, 57.67) --
	( 93.53, 57.67) --
	( 93.98, 57.67) --
	( 94.43, 57.67) --
	( 94.88, 57.67) --
	( 95.33, 57.67) --
	( 95.78, 57.67) --
	( 96.23, 57.67) --
	( 96.68, 57.67) --
	( 97.12, 57.67) --
	( 97.57, 57.67) --
	( 98.02, 57.67) --
	( 98.47, 57.67) --
	( 98.92, 57.67) --
	( 99.37, 57.67) --
	( 99.82, 57.67) --
	(100.27, 57.67) --
	(100.71, 57.67) --
	(101.16, 57.67) --
	(101.61, 57.67) --
	(102.06, 57.67) --
	(102.51, 57.67) --
	(102.96, 57.67) --
	(103.41, 57.67) --
	(103.85, 57.67) --
	(104.30, 57.67) --
	(104.75, 57.67) --
	(105.20, 57.68) --
	(105.65, 57.68) --
	(106.10, 57.68) --
	(106.55, 57.69) --
	(107.00, 57.69) --
	(107.44, 57.69) --
	(107.89, 57.70) --
	(108.34, 57.70) --
	(108.79, 57.71) --
	(109.24, 57.71) --
	(109.69, 57.71) --
	(110.14, 57.72) --
	(110.59, 57.72) --
	(111.03, 57.72) --
	(111.48, 57.73) --
	(111.93, 57.74) --
	(112.38, 57.75) --
	(112.83, 57.75) --
	(113.28, 57.76) --
	(113.73, 57.76) --
	(114.17, 57.77) --
	(114.62, 57.77) --
	(115.07, 57.77) --
	(115.52, 57.77) --
	(115.97, 57.76) --
	(116.42, 57.76) --
	(116.87, 57.76) --
	(117.32, 57.77) --
	(117.76, 57.77) --
	(118.21, 57.78) --
	(118.66, 57.78) --
	(119.11, 57.79) --
	(119.56, 57.80) --
	(120.01, 57.81) --
	(120.46, 57.82) --
	(120.91, 57.83) --
	(121.35, 57.83) --
	(121.80, 57.84) --
	(122.25, 57.85) --
	(122.70, 57.86) --
	(123.15, 57.87) --
	(123.60, 57.87) --
	(124.05, 57.88) --
	(124.49, 57.89) --
	(124.94, 57.89) --
	(125.39, 57.90) --
	(125.84, 57.90) --
	(126.29, 57.90) --
	(126.74, 57.90) --
	(127.19, 57.91) --
	(127.64, 57.91) --
	(128.08, 57.92) --
	(128.53, 57.93) --
	(128.98, 57.95) --
	(129.43, 57.97) --
	(129.88, 57.99) --
	(130.33, 58.02) --
	(130.78, 58.05) --
	(131.23, 58.08) --
	(131.67, 58.11) --
	(132.12, 58.14) --
	(132.57, 58.17) --
	(133.02, 58.20) --
	(133.47, 58.22) --
	(133.92, 58.23) --
	(134.37, 58.24) --
	(134.81, 58.24) --
	(135.26, 58.24) --
	(135.71, 58.25) --
	(136.16, 58.25) --
	(136.61, 58.25) --
	(137.06, 58.26) --
	(137.51, 58.28) --
	(137.96, 58.31) --
	(138.40, 58.35) --
	(138.85, 58.40) --
	(139.30, 58.45) --
	(139.75, 58.51) --
	(140.20, 58.56) --
	(140.65, 58.61) --
	(141.10, 58.65) --
	(141.55, 58.68) --
	(141.99, 58.70) --
	(142.44, 58.72) --
	(142.89, 58.73) --
	(143.34, 58.75) --
	(143.79, 58.77) --
	(144.24, 58.80) --
	(144.69, 58.84) --
	(145.13, 58.89) --
	(145.58, 58.94) --
	(146.03, 59.00) --
	(146.48, 59.06) --
	(146.93, 59.12) --
	(147.38, 59.18) --
	(147.83, 59.24) --
	(148.28, 59.30) --
	(148.72, 59.36) --
	(149.17, 59.42) --
	(149.62, 59.48) --
	(150.07, 59.55) --
	(150.52, 59.62) --
	(150.97, 59.70) --
	(151.42, 59.78) --
	(151.87, 59.87) --
	(152.31, 59.95) --
	(152.76, 60.03) --
	(153.21, 60.09) --
	(153.66, 60.14) --
	(154.11, 60.18) --
	(154.56, 60.19) --
	(155.01, 60.19) --
	(155.45, 60.18) --
	(155.90, 60.18) --
	(156.35, 60.18) --
	(156.80, 60.20) --
	(157.25, 60.24) --
	(157.70, 60.30) --
	(158.15, 60.38) --
	(158.60, 60.47) --
	(159.04, 60.57) --
	(159.49, 60.66) --
	(159.94, 60.74) --
	(160.39, 60.81) --
	(160.84, 60.87) --
	(161.29, 60.92) --
	(161.74, 60.96) --
	(162.19, 61.01) --
	(162.63, 61.07) --
	(163.08, 61.14) --
	(163.53, 61.23) --
	(163.98, 61.33) --
	(164.43, 61.44) --
	(164.88, 61.55) --
	(165.33, 61.67) --
	(165.77, 61.78) --
	(166.22, 61.88) --
	(166.67, 61.97) --
	(167.12, 62.06) --
	(167.57, 62.15) --
	(168.02, 62.24) --
	(168.47, 62.33) --
	(168.92, 62.42) --
	(169.36, 62.52) --
	(169.81, 62.61) --
	(170.26, 62.71) --
	(170.71, 62.82) --
	(171.16, 62.92) --
	(171.61, 63.03) --
	(172.06, 63.13) --
	(172.51, 63.23) --
	(172.95, 63.32) --
	(173.40, 63.41) --
	(173.85, 63.49) --
	(174.30, 63.57) --
	(174.75, 63.67) --
	(175.20, 63.77) --
	(175.65, 63.90) --
	(176.09, 64.04) --
	(176.54, 64.21) --
	(176.99, 64.39) --
	(177.44, 64.58) --
	(177.89, 64.78) --
	(178.34, 64.98) --
	(178.79, 65.19) --
	(179.24, 65.40) --
	(179.68, 65.61) --
	(180.13, 65.83) --
	(180.58, 66.06) --
	(181.03, 66.30) --
	(181.48, 66.56) --
	(181.93, 66.82) --
	(182.38, 67.10) --
	(182.83, 67.38) --
	(183.27, 67.66) --
	(183.72, 67.95) --
	(184.17, 68.23) --
	(184.62, 68.50) --
	(185.07, 68.75) --
	(185.52, 69.00) --
	(185.97, 69.24) --
	(186.41, 69.48) --
	(186.86, 69.74) --
	(187.31, 70.03) --
	(187.76, 70.38) --
	(188.21, 70.80) --
	(188.66, 71.30) --
	(189.11, 71.87) --
	(189.56, 72.52) --
	(190.00, 73.22) --
	(190.45, 73.96) --
	(190.90, 74.71) --
	(191.35, 75.45) --
	(191.80, 76.14) --
	(192.25, 76.78) --
	(192.70, 77.35) --
	(193.15, 77.85) --
	(193.59, 78.28) --
	(194.04, 78.66) --
	(194.49, 79.02) --
	(194.94, 79.38) --
	(195.39, 79.75) --
	(195.84, 80.16) --
	(196.29, 80.61) --
	(196.73, 81.10) --
	(197.18, 81.65) --
	(197.63, 82.25) --
	(198.08, 82.90) --
	(198.53, 83.59) --
	(198.98, 84.33) --
	(199.43, 85.11) --
	(199.88, 85.93) --
	(200.32, 86.80) --
	(200.77, 87.70) --
	(201.22, 88.64) --
	(201.67, 89.62) --
	(202.12, 90.64) --
	(202.57, 91.70) --
	(203.02, 92.81) --
	(203.47, 93.99) --
	(203.91, 95.23) --
	(204.36, 96.53) --
	(204.81, 97.88) --
	(205.26, 99.26) --
	(205.71,100.65) --
	(206.16,102.02) --
	(206.61,103.34) --
	(207.05,104.59) --
	(207.50,105.79) --
	(207.95,106.95) --
	(208.40,108.12) --
	(208.85,109.33) --
	(209.30,110.64) --
	(209.75,112.07) --
	(210.20,113.65) --
	(210.64,115.38) --
	(211.09,117.25) --
	(211.54,119.23) --
	(211.99,121.28) --
	(212.44,123.37) --
	(212.89,125.45) --
	(213.34,127.51) --
	(213.79,129.49) --
	(214.23,131.38) --
	(214.68,133.14) --
	(215.13,134.75) --
	(215.58,136.17) --
	(216.03,137.38) --
	(216.48,138.36) --
	(216.93,139.09) --
	(217.37,139.59) --
	(217.82,139.86) --
	(218.27,139.93) --
	(218.72,139.81) --
	(219.17,139.53) --
	(219.62,139.11) --
	(220.07,138.54) --
	(220.52,137.83) --
	(220.96,136.99) --
	(221.41,136.02) --
	(221.86,134.93) --
	(222.31,133.73) --
	(222.76,132.45) --
	(223.21,131.09) --
	(223.66,129.68) --
	(224.11,128.22) --
	(224.55,126.72) --
	(225.00,125.21) --
	(225.45,123.69) --
	(225.90,122.20) --
	(226.35,120.74) --
	(226.80,119.37) --
	(227.25,118.09) --
	(227.69,116.95) --
	(228.14,115.97) --
	(228.59,115.14) --
	(229.04,114.44) --
	(229.49,113.84) --
	(229.94,113.31) --
	(230.39,112.81) --
	(230.84,112.29) --
	(231.28,111.73) --
	(231.73,111.12) --
	(232.18,110.45) --
	(232.63,109.73) --
	(233.08,108.98) --
	(233.53,108.23) --
	(233.98,107.49) --
	(234.43,106.78) --
	(234.87,106.11) --
	(235.32,105.45) --
	(235.77,104.81) --
	(236.22,104.15) --
	(236.67,103.46) --
	(237.12,102.73) --
	(237.57,101.95) --
	(238.01,101.11) --
	(238.46,100.21) --
	(238.91, 99.24) --
	(239.36, 98.22) --
	(239.81, 97.15) --
	(240.26, 96.04) --
	(240.71, 94.90) --
	(241.16, 93.74) --
	(241.60, 92.57) --
	(242.05, 91.39) --
	(242.50, 90.22) --
	(242.95, 89.06) --
	(243.40, 87.91) --
	(243.85, 86.78) --
	(244.30, 85.67) --
	(244.75, 84.57) --
	(245.19, 83.50) --
	(245.64, 82.44) --
	(246.09, 81.39) --
	(246.54, 80.35) --
	(246.99, 79.31) --
	(247.44, 78.29) --
	(247.89, 77.29) --
	(248.33, 76.32) --
	(248.78, 75.38) --
	(249.23, 74.49) --
	(249.68, 73.65) --
	(250.13, 72.86) --
	(250.58, 72.10) --
	(251.03, 71.40) --
	(251.48, 70.73) --
	(251.92, 70.10) --
	(252.37, 69.50) --
	(252.82, 68.94) --
	(253.27, 68.40) --
	(253.72, 67.90) --
	(254.17, 67.43) --
	(254.62, 66.98) --
	(255.07, 66.56) --
	(255.51, 66.16) --
	(255.96, 65.77) --
	(256.41, 65.41) --
	(256.86, 65.04) --
	(257.31, 64.68) --
	(257.76, 64.29) --
	(258.21, 63.89) --
	(258.65, 63.46) --
	(259.10, 63.01) --
	(259.55, 62.54) --
	(260.00, 62.07) --
	(260.45, 61.60) --
	(260.90, 61.15) --
	(261.35, 60.73) --
	(261.80, 60.34) --
	(262.24, 59.99) --
	(262.69, 59.67) --
	(263.14, 59.40) --
	(263.59, 59.16) --
	(264.04, 58.96) --
	(264.49, 58.79) --
	(264.94, 58.65) --
	(265.39, 58.53) --
	(265.83, 58.44) --
	(266.28, 58.38) --
	(266.73, 58.33) --
	(267.18, 58.30) --
	(267.63, 58.28) --
	(268.08, 58.27) --
	(268.53, 58.27) --
	(268.97, 58.26) --
	(269.42, 58.24) --
	(269.87, 58.22) --
	(270.32, 58.19) --
	(270.77, 58.14) --
	(271.22, 58.09) --
	(271.67, 58.03) --
	(272.12, 57.97) --
	(272.12, 57.67) --
	(271.67, 57.67) --
	(271.22, 57.67) --
	(270.77, 57.67) --
	(270.32, 57.67) --
	(269.87, 57.67) --
	(269.42, 57.67) --
	(268.97, 57.67) --
	(268.53, 57.67) --
	(268.08, 57.67) --
	(267.63, 57.67) --
	(267.18, 57.67) --
	(266.73, 57.67) --
	(266.28, 57.67) --
	(265.83, 57.67) --
	(265.39, 57.67) --
	(264.94, 57.67) --
	(264.49, 57.67) --
	(264.04, 57.67) --
	(263.59, 57.67) --
	(263.14, 57.67) --
	(262.69, 57.67) --
	(262.24, 57.67) --
	(261.80, 57.67) --
	(261.35, 57.67) --
	(260.90, 57.67) --
	(260.45, 57.67) --
	(260.00, 57.67) --
	(259.55, 57.67) --
	(259.10, 57.67) --
	(258.65, 57.67) --
	(258.21, 57.67) --
	(257.76, 57.67) --
	(257.31, 57.67) --
	(256.86, 57.67) --
	(256.41, 57.67) --
	(255.96, 57.67) --
	(255.51, 57.67) --
	(255.07, 57.67) --
	(254.62, 57.67) --
	(254.17, 57.67) --
	(253.72, 57.67) --
	(253.27, 57.67) --
	(252.82, 57.67) --
	(252.37, 57.67) --
	(251.92, 57.67) --
	(251.48, 57.67) --
	(251.03, 57.67) --
	(250.58, 57.67) --
	(250.13, 57.67) --
	(249.68, 57.67) --
	(249.23, 57.67) --
	(248.78, 57.67) --
	(248.33, 57.67) --
	(247.89, 57.67) --
	(247.44, 57.67) --
	(246.99, 57.67) --
	(246.54, 57.67) --
	(246.09, 57.67) --
	(245.64, 57.67) --
	(245.19, 57.67) --
	(244.75, 57.67) --
	(244.30, 57.67) --
	(243.85, 57.67) --
	(243.40, 57.67) --
	(242.95, 57.67) --
	(242.50, 57.67) --
	(242.05, 57.67) --
	(241.60, 57.67) --
	(241.16, 57.67) --
	(240.71, 57.67) --
	(240.26, 57.67) --
	(239.81, 57.67) --
	(239.36, 57.67) --
	(238.91, 57.67) --
	(238.46, 57.67) --
	(238.01, 57.67) --
	(237.57, 57.67) --
	(237.12, 57.67) --
	(236.67, 57.67) --
	(236.22, 57.67) --
	(235.77, 57.67) --
	(235.32, 57.67) --
	(234.87, 57.67) --
	(234.43, 57.67) --
	(233.98, 57.67) --
	(233.53, 57.67) --
	(233.08, 57.67) --
	(232.63, 57.67) --
	(232.18, 57.67) --
	(231.73, 57.67) --
	(231.28, 57.67) --
	(230.84, 57.67) --
	(230.39, 57.67) --
	(229.94, 57.67) --
	(229.49, 57.67) --
	(229.04, 57.67) --
	(228.59, 57.67) --
	(228.14, 57.67) --
	(227.69, 57.67) --
	(227.25, 57.67) --
	(226.80, 57.67) --
	(226.35, 57.67) --
	(225.90, 57.67) --
	(225.45, 57.67) --
	(225.00, 57.67) --
	(224.55, 57.67) --
	(224.11, 57.67) --
	(223.66, 57.67) --
	(223.21, 57.67) --
	(222.76, 57.67) --
	(222.31, 57.67) --
	(221.86, 57.67) --
	(221.41, 57.67) --
	(220.96, 57.67) --
	(220.52, 57.67) --
	(220.07, 57.67) --
	(219.62, 57.67) --
	(219.17, 57.67) --
	(218.72, 57.67) --
	(218.27, 57.67) --
	(217.82, 57.67) --
	(217.37, 57.67) --
	(216.93, 57.67) --
	(216.48, 57.67) --
	(216.03, 57.67) --
	(215.58, 57.67) --
	(215.13, 57.67) --
	(214.68, 57.67) --
	(214.23, 57.67) --
	(213.79, 57.67) --
	(213.34, 57.67) --
	(212.89, 57.67) --
	(212.44, 57.67) --
	(211.99, 57.67) --
	(211.54, 57.67) --
	(211.09, 57.67) --
	(210.64, 57.67) --
	(210.20, 57.67) --
	(209.75, 57.67) --
	(209.30, 57.67) --
	(208.85, 57.67) --
	(208.40, 57.67) --
	(207.95, 57.67) --
	(207.50, 57.67) --
	(207.05, 57.67) --
	(206.61, 57.67) --
	(206.16, 57.67) --
	(205.71, 57.67) --
	(205.26, 57.67) --
	(204.81, 57.67) --
	(204.36, 57.67) --
	(203.91, 57.67) --
	(203.47, 57.67) --
	(203.02, 57.67) --
	(202.57, 57.67) --
	(202.12, 57.67) --
	(201.67, 57.67) --
	(201.22, 57.67) --
	(200.77, 57.67) --
	(200.32, 57.67) --
	(199.88, 57.67) --
	(199.43, 57.67) --
	(198.98, 57.67) --
	(198.53, 57.67) --
	(198.08, 57.67) --
	(197.63, 57.67) --
	(197.18, 57.67) --
	(196.73, 57.67) --
	(196.29, 57.67) --
	(195.84, 57.67) --
	(195.39, 57.67) --
	(194.94, 57.67) --
	(194.49, 57.67) --
	(194.04, 57.67) --
	(193.59, 57.67) --
	(193.15, 57.67) --
	(192.70, 57.67) --
	(192.25, 57.67) --
	(191.80, 57.67) --
	(191.35, 57.67) --
	(190.90, 57.67) --
	(190.45, 57.67) --
	(190.00, 57.67) --
	(189.56, 57.67) --
	(189.11, 57.67) --
	(188.66, 57.67) --
	(188.21, 57.67) --
	(187.76, 57.67) --
	(187.31, 57.67) --
	(186.86, 57.67) --
	(186.41, 57.67) --
	(185.97, 57.67) --
	(185.52, 57.67) --
	(185.07, 57.67) --
	(184.62, 57.67) --
	(184.17, 57.67) --
	(183.72, 57.67) --
	(183.27, 57.67) --
	(182.83, 57.67) --
	(182.38, 57.67) --
	(181.93, 57.67) --
	(181.48, 57.67) --
	(181.03, 57.67) --
	(180.58, 57.67) --
	(180.13, 57.67) --
	(179.68, 57.67) --
	(179.24, 57.67) --
	(178.79, 57.67) --
	(178.34, 57.67) --
	(177.89, 57.67) --
	(177.44, 57.67) --
	(176.99, 57.67) --
	(176.54, 57.67) --
	(176.09, 57.67) --
	(175.65, 57.67) --
	(175.20, 57.67) --
	(174.75, 57.67) --
	(174.30, 57.67) --
	(173.85, 57.67) --
	(173.40, 57.67) --
	(172.95, 57.67) --
	(172.51, 57.67) --
	(172.06, 57.67) --
	(171.61, 57.67) --
	(171.16, 57.67) --
	(170.71, 57.67) --
	(170.26, 57.67) --
	(169.81, 57.67) --
	(169.36, 57.67) --
	(168.92, 57.67) --
	(168.47, 57.67) --
	(168.02, 57.67) --
	(167.57, 57.67) --
	(167.12, 57.67) --
	(166.67, 57.67) --
	(166.22, 57.67) --
	(165.77, 57.67) --
	(165.33, 57.67) --
	(164.88, 57.67) --
	(164.43, 57.67) --
	(163.98, 57.67) --
	(163.53, 57.67) --
	(163.08, 57.67) --
	(162.63, 57.67) --
	(162.19, 57.67) --
	(161.74, 57.67) --
	(161.29, 57.67) --
	(160.84, 57.67) --
	(160.39, 57.67) --
	(159.94, 57.67) --
	(159.49, 57.67) --
	(159.04, 57.67) --
	(158.60, 57.67) --
	(158.15, 57.67) --
	(157.70, 57.67) --
	(157.25, 57.67) --
	(156.80, 57.67) --
	(156.35, 57.67) --
	(155.90, 57.67) --
	(155.45, 57.67) --
	(155.01, 57.67) --
	(154.56, 57.67) --
	(154.11, 57.67) --
	(153.66, 57.67) --
	(153.21, 57.67) --
	(152.76, 57.67) --
	(152.31, 57.67) --
	(151.87, 57.67) --
	(151.42, 57.67) --
	(150.97, 57.67) --
	(150.52, 57.67) --
	(150.07, 57.67) --
	(149.62, 57.67) --
	(149.17, 57.67) --
	(148.72, 57.67) --
	(148.28, 57.67) --
	(147.83, 57.67) --
	(147.38, 57.67) --
	(146.93, 57.67) --
	(146.48, 57.67) --
	(146.03, 57.67) --
	(145.58, 57.67) --
	(145.13, 57.67) --
	(144.69, 57.67) --
	(144.24, 57.67) --
	(143.79, 57.67) --
	(143.34, 57.67) --
	(142.89, 57.67) --
	(142.44, 57.67) --
	(141.99, 57.67) --
	(141.55, 57.67) --
	(141.10, 57.67) --
	(140.65, 57.67) --
	(140.20, 57.67) --
	(139.75, 57.67) --
	(139.30, 57.67) --
	(138.85, 57.67) --
	(138.40, 57.67) --
	(137.96, 57.67) --
	(137.51, 57.67) --
	(137.06, 57.67) --
	(136.61, 57.67) --
	(136.16, 57.67) --
	(135.71, 57.67) --
	(135.26, 57.67) --
	(134.81, 57.67) --
	(134.37, 57.67) --
	(133.92, 57.67) --
	(133.47, 57.67) --
	(133.02, 57.67) --
	(132.57, 57.67) --
	(132.12, 57.67) --
	(131.67, 57.67) --
	(131.23, 57.67) --
	(130.78, 57.67) --
	(130.33, 57.67) --
	(129.88, 57.67) --
	(129.43, 57.67) --
	(128.98, 57.67) --
	(128.53, 57.67) --
	(128.08, 57.67) --
	(127.64, 57.67) --
	(127.19, 57.67) --
	(126.74, 57.67) --
	(126.29, 57.67) --
	(125.84, 57.67) --
	(125.39, 57.67) --
	(124.94, 57.67) --
	(124.49, 57.67) --
	(124.05, 57.67) --
	(123.60, 57.67) --
	(123.15, 57.67) --
	(122.70, 57.67) --
	(122.25, 57.67) --
	(121.80, 57.67) --
	(121.35, 57.67) --
	(120.91, 57.67) --
	(120.46, 57.67) --
	(120.01, 57.67) --
	(119.56, 57.67) --
	(119.11, 57.67) --
	(118.66, 57.67) --
	(118.21, 57.67) --
	(117.76, 57.67) --
	(117.32, 57.67) --
	(116.87, 57.67) --
	(116.42, 57.67) --
	(115.97, 57.67) --
	(115.52, 57.67) --
	(115.07, 57.67) --
	(114.62, 57.67) --
	(114.17, 57.67) --
	(113.73, 57.67) --
	(113.28, 57.67) --
	(112.83, 57.67) --
	(112.38, 57.67) --
	(111.93, 57.67) --
	(111.48, 57.67) --
	(111.03, 57.67) --
	(110.59, 57.67) --
	(110.14, 57.67) --
	(109.69, 57.67) --
	(109.24, 57.67) --
	(108.79, 57.67) --
	(108.34, 57.67) --
	(107.89, 57.67) --
	(107.44, 57.67) --
	(107.00, 57.67) --
	(106.55, 57.67) --
	(106.10, 57.67) --
	(105.65, 57.67) --
	(105.20, 57.67) --
	(104.75, 57.67) --
	(104.30, 57.67) --
	(103.85, 57.67) --
	(103.41, 57.67) --
	(102.96, 57.67) --
	(102.51, 57.67) --
	(102.06, 57.67) --
	(101.61, 57.67) --
	(101.16, 57.67) --
	(100.71, 57.67) --
	(100.27, 57.67) --
	( 99.82, 57.67) --
	( 99.37, 57.67) --
	( 98.92, 57.67) --
	( 98.47, 57.67) --
	( 98.02, 57.67) --
	( 97.57, 57.67) --
	( 97.12, 57.67) --
	( 96.68, 57.67) --
	( 96.23, 57.67) --
	( 95.78, 57.67) --
	( 95.33, 57.67) --
	( 94.88, 57.67) --
	( 94.43, 57.67) --
	( 93.98, 57.67) --
	( 93.53, 57.67) --
	( 93.09, 57.67) --
	( 92.64, 57.67) --
	( 92.19, 57.67) --
	( 91.74, 57.67) --
	( 91.29, 57.67) --
	( 90.84, 57.67) --
	( 90.39, 57.67) --
	( 89.95, 57.67) --
	( 89.50, 57.67) --
	( 89.05, 57.67) --
	( 88.60, 57.67) --
	( 88.15, 57.67) --
	( 87.70, 57.67) --
	( 87.25, 57.67) --
	( 86.80, 57.67) --
	( 86.36, 57.67) --
	( 85.91, 57.67) --
	( 85.46, 57.67) --
	( 85.01, 57.67) --
	( 84.56, 57.67) --
	( 84.11, 57.67) --
	( 83.66, 57.67) --
	( 83.21, 57.67) --
	( 82.77, 57.67) --
	( 82.32, 57.67) --
	( 81.87, 57.67) --
	( 81.42, 57.67) --
	( 80.97, 57.67) --
	( 80.52, 57.67) --
	( 80.07, 57.67) --
	( 79.63, 57.67) --
	( 79.18, 57.67) --
	( 78.73, 57.67) --
	( 78.28, 57.67) --
	( 77.83, 57.67) --
	( 77.38, 57.67) --
	( 76.93, 57.67) --
	( 76.48, 57.67) --
	( 76.04, 57.67) --
	( 75.59, 57.67) --
	( 75.14, 57.67) --
	( 74.69, 57.67) --
	( 74.24, 57.67) --
	( 73.79, 57.67) --
	( 73.34, 57.67) --
	( 72.89, 57.67) --
	( 72.45, 57.67) --
	( 72.00, 57.67) --
	( 71.55, 57.67) --
	( 71.10, 57.67) --
	( 70.65, 57.67) --
	( 70.20, 57.67) --
	( 69.75, 57.67) --
	( 69.31, 57.67) --
	( 68.86, 57.67) --
	( 68.41, 57.67) --
	( 67.96, 57.67) --
	( 67.51, 57.67) --
	( 67.06, 57.67) --
	( 66.61, 57.67) --
	( 66.16, 57.67) --
	( 65.72, 57.67) --
	( 65.27, 57.67) --
	( 64.82, 57.67) --
	( 64.37, 57.67) --
	( 63.92, 57.67) --
	( 63.47, 57.67) --
	( 63.02, 57.67) --
	( 62.57, 57.67) --
	( 62.13, 57.67) --
	( 61.68, 57.67) --
	( 61.23, 57.67) --
	( 60.78, 57.67) --
	( 60.33, 57.67) --
	( 59.88, 57.67) --
	( 59.43, 57.67) --
	( 58.99, 57.67) --
	( 58.54, 57.67) --
	( 58.09, 57.67) --
	( 57.64, 57.67) --
	( 57.19, 57.67) --
	( 56.74, 57.67) --
	( 56.29, 57.67) --
	( 55.84, 57.67) --
	( 55.40, 57.67) --
	( 54.95, 57.67) --
	( 54.50, 57.67) --
	( 54.05, 57.67) --
	( 53.60, 57.67) --
	( 53.15, 57.67) --
	( 52.70, 57.67) --
	( 52.25, 57.67) --
	( 51.81, 57.67) --
	( 51.36, 57.67) --
	( 50.91, 57.67) --
	( 50.46, 57.67) --
	( 50.01, 57.67) --
	( 49.56, 57.67) --
	( 49.11, 57.67) --
	( 48.67, 57.67) --
	( 48.22, 57.67) --
	( 47.77, 57.67) --
	( 47.32, 57.67) --
	( 46.87, 57.67) --
	( 46.42, 57.67) --
	( 45.97, 57.67) --
	( 45.52, 57.67) --
	( 45.08, 57.67) --
	( 44.63, 57.67) --
	( 44.18, 57.67) --
	( 43.73, 57.67) --
	( 43.28, 57.67) --
	( 42.83, 57.67) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 42.83, 57.67) --
	( 43.28, 57.67) --
	( 43.73, 57.67) --
	( 44.18, 57.67) --
	( 44.63, 57.67) --
	( 45.08, 57.67) --
	( 45.52, 57.67) --
	( 45.97, 57.67) --
	( 46.42, 57.67) --
	( 46.87, 57.67) --
	( 47.32, 57.67) --
	( 47.77, 57.67) --
	( 48.22, 57.67) --
	( 48.67, 57.67) --
	( 49.11, 57.67) --
	( 49.56, 57.67) --
	( 50.01, 57.67) --
	( 50.46, 57.67) --
	( 50.91, 57.67) --
	( 51.36, 57.67) --
	( 51.81, 57.67) --
	( 52.25, 57.67) --
	( 52.70, 57.67) --
	( 53.15, 57.67) --
	( 53.60, 57.67) --
	( 54.05, 57.67) --
	( 54.50, 57.67) --
	( 54.95, 57.67) --
	( 55.40, 57.67) --
	( 55.84, 57.67) --
	( 56.29, 57.67) --
	( 56.74, 57.67) --
	( 57.19, 57.67) --
	( 57.64, 57.67) --
	( 58.09, 57.67) --
	( 58.54, 57.67) --
	( 58.99, 57.67) --
	( 59.43, 57.67) --
	( 59.88, 57.67) --
	( 60.33, 57.67) --
	( 60.78, 57.67) --
	( 61.23, 57.67) --
	( 61.68, 57.67) --
	( 62.13, 57.67) --
	( 62.57, 57.67) --
	( 63.02, 57.67) --
	( 63.47, 57.67) --
	( 63.92, 57.67) --
	( 64.37, 57.67) --
	( 64.82, 57.67) --
	( 65.27, 57.67) --
	( 65.72, 57.67) --
	( 66.16, 57.67) --
	( 66.61, 57.67) --
	( 67.06, 57.67) --
	( 67.51, 57.67) --
	( 67.96, 57.67) --
	( 68.41, 57.67) --
	( 68.86, 57.67) --
	( 69.31, 57.67) --
	( 69.75, 57.67) --
	( 70.20, 57.67) --
	( 70.65, 57.67) --
	( 71.10, 57.67) --
	( 71.55, 57.67) --
	( 72.00, 57.67) --
	( 72.45, 57.67) --
	( 72.89, 57.67) --
	( 73.34, 57.67) --
	( 73.79, 57.67) --
	( 74.24, 57.67) --
	( 74.69, 57.67) --
	( 75.14, 57.67) --
	( 75.59, 57.67) --
	( 76.04, 57.67) --
	( 76.48, 57.67) --
	( 76.93, 57.67) --
	( 77.38, 57.67) --
	( 77.83, 57.67) --
	( 78.28, 57.67) --
	( 78.73, 57.67) --
	( 79.18, 57.67) --
	( 79.63, 57.67) --
	( 80.07, 57.67) --
	( 80.52, 57.67) --
	( 80.97, 57.67) --
	( 81.42, 57.67) --
	( 81.87, 57.67) --
	( 82.32, 57.67) --
	( 82.77, 57.67) --
	( 83.21, 57.67) --
	( 83.66, 57.67) --
	( 84.11, 57.67) --
	( 84.56, 57.67) --
	( 85.01, 57.67) --
	( 85.46, 57.67) --
	( 85.91, 57.67) --
	( 86.36, 57.67) --
	( 86.80, 57.67) --
	( 87.25, 57.67) --
	( 87.70, 57.67) --
	( 88.15, 57.67) --
	( 88.60, 57.67) --
	( 89.05, 57.67) --
	( 89.50, 57.67) --
	( 89.95, 57.67) --
	( 90.39, 57.67) --
	( 90.84, 57.67) --
	( 91.29, 57.67) --
	( 91.74, 57.67) --
	( 92.19, 57.67) --
	( 92.64, 57.67) --
	( 93.09, 57.67) --
	( 93.53, 57.67) --
	( 93.98, 57.67) --
	( 94.43, 57.67) --
	( 94.88, 57.67) --
	( 95.33, 57.67) --
	( 95.78, 57.67) --
	( 96.23, 57.67) --
	( 96.68, 57.67) --
	( 97.12, 57.67) --
	( 97.57, 57.67) --
	( 98.02, 57.67) --
	( 98.47, 57.67) --
	( 98.92, 57.67) --
	( 99.37, 57.67) --
	( 99.82, 57.67) --
	(100.27, 57.67) --
	(100.71, 57.67) --
	(101.16, 57.67) --
	(101.61, 57.67) --
	(102.06, 57.67) --
	(102.51, 57.67) --
	(102.96, 57.67) --
	(103.41, 57.67) --
	(103.85, 57.67) --
	(104.30, 57.67) --
	(104.75, 57.67) --
	(105.20, 57.68) --
	(105.65, 57.68) --
	(106.10, 57.68) --
	(106.55, 57.69) --
	(107.00, 57.69) --
	(107.44, 57.69) --
	(107.89, 57.70) --
	(108.34, 57.70) --
	(108.79, 57.71) --
	(109.24, 57.71) --
	(109.69, 57.71) --
	(110.14, 57.72) --
	(110.59, 57.72) --
	(111.03, 57.72) --
	(111.48, 57.73) --
	(111.93, 57.74) --
	(112.38, 57.75) --
	(112.83, 57.75) --
	(113.28, 57.76) --
	(113.73, 57.76) --
	(114.17, 57.77) --
	(114.62, 57.77) --
	(115.07, 57.77) --
	(115.52, 57.77) --
	(115.97, 57.76) --
	(116.42, 57.76) --
	(116.87, 57.76) --
	(117.32, 57.77) --
	(117.76, 57.77) --
	(118.21, 57.78) --
	(118.66, 57.78) --
	(119.11, 57.79) --
	(119.56, 57.80) --
	(120.01, 57.81) --
	(120.46, 57.82) --
	(120.91, 57.83) --
	(121.35, 57.83) --
	(121.80, 57.84) --
	(122.25, 57.85) --
	(122.70, 57.86) --
	(123.15, 57.87) --
	(123.60, 57.87) --
	(124.05, 57.88) --
	(124.49, 57.89) --
	(124.94, 57.89) --
	(125.39, 57.90) --
	(125.84, 57.90) --
	(126.29, 57.90) --
	(126.74, 57.90) --
	(127.19, 57.91) --
	(127.64, 57.91) --
	(128.08, 57.92) --
	(128.53, 57.93) --
	(128.98, 57.95) --
	(129.43, 57.97) --
	(129.88, 57.99) --
	(130.33, 58.02) --
	(130.78, 58.05) --
	(131.23, 58.08) --
	(131.67, 58.11) --
	(132.12, 58.14) --
	(132.57, 58.17) --
	(133.02, 58.20) --
	(133.47, 58.22) --
	(133.92, 58.23) --
	(134.37, 58.24) --
	(134.81, 58.24) --
	(135.26, 58.24) --
	(135.71, 58.25) --
	(136.16, 58.25) --
	(136.61, 58.25) --
	(137.06, 58.26) --
	(137.51, 58.28) --
	(137.96, 58.31) --
	(138.40, 58.35) --
	(138.85, 58.40) --
	(139.30, 58.45) --
	(139.75, 58.51) --
	(140.20, 58.56) --
	(140.65, 58.61) --
	(141.10, 58.65) --
	(141.55, 58.68) --
	(141.99, 58.70) --
	(142.44, 58.72) --
	(142.89, 58.73) --
	(143.34, 58.75) --
	(143.79, 58.77) --
	(144.24, 58.80) --
	(144.69, 58.84) --
	(145.13, 58.89) --
	(145.58, 58.94) --
	(146.03, 59.00) --
	(146.48, 59.06) --
	(146.93, 59.12) --
	(147.38, 59.18) --
	(147.83, 59.24) --
	(148.28, 59.30) --
	(148.72, 59.36) --
	(149.17, 59.42) --
	(149.62, 59.48) --
	(150.07, 59.55) --
	(150.52, 59.62) --
	(150.97, 59.70) --
	(151.42, 59.78) --
	(151.87, 59.87) --
	(152.31, 59.95) --
	(152.76, 60.03) --
	(153.21, 60.09) --
	(153.66, 60.14) --
	(154.11, 60.18) --
	(154.56, 60.19) --
	(155.01, 60.19) --
	(155.45, 60.18) --
	(155.90, 60.18) --
	(156.35, 60.18) --
	(156.80, 60.20) --
	(157.25, 60.24) --
	(157.70, 60.30) --
	(158.15, 60.38) --
	(158.60, 60.47) --
	(159.04, 60.57) --
	(159.49, 60.66) --
	(159.94, 60.74) --
	(160.39, 60.81) --
	(160.84, 60.87) --
	(161.29, 60.92) --
	(161.74, 60.96) --
	(162.19, 61.01) --
	(162.63, 61.07) --
	(163.08, 61.14) --
	(163.53, 61.23) --
	(163.98, 61.33) --
	(164.43, 61.44) --
	(164.88, 61.55) --
	(165.33, 61.67) --
	(165.77, 61.78) --
	(166.22, 61.88) --
	(166.67, 61.97) --
	(167.12, 62.06) --
	(167.57, 62.15) --
	(168.02, 62.24) --
	(168.47, 62.33) --
	(168.92, 62.42) --
	(169.36, 62.52) --
	(169.81, 62.61) --
	(170.26, 62.71) --
	(170.71, 62.82) --
	(171.16, 62.92) --
	(171.61, 63.03) --
	(172.06, 63.13) --
	(172.51, 63.23) --
	(172.95, 63.32) --
	(173.40, 63.41) --
	(173.85, 63.49) --
	(174.30, 63.57) --
	(174.75, 63.67) --
	(175.20, 63.77) --
	(175.65, 63.90) --
	(176.09, 64.04) --
	(176.54, 64.21) --
	(176.99, 64.39) --
	(177.44, 64.58) --
	(177.89, 64.78) --
	(178.34, 64.98) --
	(178.79, 65.19) --
	(179.24, 65.40) --
	(179.68, 65.61) --
	(180.13, 65.83) --
	(180.58, 66.06) --
	(181.03, 66.30) --
	(181.48, 66.56) --
	(181.93, 66.82) --
	(182.38, 67.10) --
	(182.83, 67.38) --
	(183.27, 67.66) --
	(183.72, 67.95) --
	(184.17, 68.23) --
	(184.62, 68.50) --
	(185.07, 68.75) --
	(185.52, 69.00) --
	(185.97, 69.24) --
	(186.41, 69.48) --
	(186.86, 69.74) --
	(187.31, 70.03) --
	(187.76, 70.38) --
	(188.21, 70.80) --
	(188.66, 71.30) --
	(189.11, 71.87) --
	(189.56, 72.52) --
	(190.00, 73.22) --
	(190.45, 73.96) --
	(190.90, 74.71) --
	(191.35, 75.45) --
	(191.80, 76.14) --
	(192.25, 76.78) --
	(192.70, 77.35) --
	(193.15, 77.85) --
	(193.59, 78.28) --
	(194.04, 78.66) --
	(194.49, 79.02) --
	(194.94, 79.38) --
	(195.39, 79.75) --
	(195.84, 80.16) --
	(196.29, 80.61) --
	(196.73, 81.10) --
	(197.18, 81.65) --
	(197.63, 82.25) --
	(198.08, 82.90) --
	(198.53, 83.59) --
	(198.98, 84.33) --
	(199.43, 85.11) --
	(199.88, 85.93) --
	(200.32, 86.80) --
	(200.77, 87.70) --
	(201.22, 88.64) --
	(201.67, 89.62) --
	(202.12, 90.64) --
	(202.57, 91.70) --
	(203.02, 92.81) --
	(203.47, 93.99) --
	(203.91, 95.23) --
	(204.36, 96.53) --
	(204.81, 97.88) --
	(205.26, 99.26) --
	(205.71,100.65) --
	(206.16,102.02) --
	(206.61,103.34) --
	(207.05,104.59) --
	(207.50,105.79) --
	(207.95,106.95) --
	(208.40,108.12) --
	(208.85,109.33) --
	(209.30,110.64) --
	(209.75,112.07) --
	(210.20,113.65) --
	(210.64,115.38) --
	(211.09,117.25) --
	(211.54,119.23) --
	(211.99,121.28) --
	(212.44,123.37) --
	(212.89,125.45) --
	(213.34,127.51) --
	(213.79,129.49) --
	(214.23,131.38) --
	(214.68,133.14) --
	(215.13,134.75) --
	(215.58,136.17) --
	(216.03,137.38) --
	(216.48,138.36) --
	(216.93,139.09) --
	(217.37,139.59) --
	(217.82,139.86) --
	(218.27,139.93) --
	(218.72,139.81) --
	(219.17,139.53) --
	(219.62,139.11) --
	(220.07,138.54) --
	(220.52,137.83) --
	(220.96,136.99) --
	(221.41,136.02) --
	(221.86,134.93) --
	(222.31,133.73) --
	(222.76,132.45) --
	(223.21,131.09) --
	(223.66,129.68) --
	(224.11,128.22) --
	(224.55,126.72) --
	(225.00,125.21) --
	(225.45,123.69) --
	(225.90,122.20) --
	(226.35,120.74) --
	(226.80,119.37) --
	(227.25,118.09) --
	(227.69,116.95) --
	(228.14,115.97) --
	(228.59,115.14) --
	(229.04,114.44) --
	(229.49,113.84) --
	(229.94,113.31) --
	(230.39,112.81) --
	(230.84,112.29) --
	(231.28,111.73) --
	(231.73,111.12) --
	(232.18,110.45) --
	(232.63,109.73) --
	(233.08,108.98) --
	(233.53,108.23) --
	(233.98,107.49) --
	(234.43,106.78) --
	(234.87,106.11) --
	(235.32,105.45) --
	(235.77,104.81) --
	(236.22,104.15) --
	(236.67,103.46) --
	(237.12,102.73) --
	(237.57,101.95) --
	(238.01,101.11) --
	(238.46,100.21) --
	(238.91, 99.24) --
	(239.36, 98.22) --
	(239.81, 97.15) --
	(240.26, 96.04) --
	(240.71, 94.90) --
	(241.16, 93.74) --
	(241.60, 92.57) --
	(242.05, 91.39) --
	(242.50, 90.22) --
	(242.95, 89.06) --
	(243.40, 87.91) --
	(243.85, 86.78) --
	(244.30, 85.67) --
	(244.75, 84.57) --
	(245.19, 83.50) --
	(245.64, 82.44) --
	(246.09, 81.39) --
	(246.54, 80.35) --
	(246.99, 79.31) --
	(247.44, 78.29) --
	(247.89, 77.29) --
	(248.33, 76.32) --
	(248.78, 75.38) --
	(249.23, 74.49) --
	(249.68, 73.65) --
	(250.13, 72.86) --
	(250.58, 72.10) --
	(251.03, 71.40) --
	(251.48, 70.73) --
	(251.92, 70.10) --
	(252.37, 69.50) --
	(252.82, 68.94) --
	(253.27, 68.40) --
	(253.72, 67.90) --
	(254.17, 67.43) --
	(254.62, 66.98) --
	(255.07, 66.56) --
	(255.51, 66.16) --
	(255.96, 65.77) --
	(256.41, 65.41) --
	(256.86, 65.04) --
	(257.31, 64.68) --
	(257.76, 64.29) --
	(258.21, 63.89) --
	(258.65, 63.46) --
	(259.10, 63.01) --
	(259.55, 62.54) --
	(260.00, 62.07) --
	(260.45, 61.60) --
	(260.90, 61.15) --
	(261.35, 60.73) --
	(261.80, 60.34) --
	(262.24, 59.99) --
	(262.69, 59.67) --
	(263.14, 59.40) --
	(263.59, 59.16) --
	(264.04, 58.96) --
	(264.49, 58.79) --
	(264.94, 58.65) --
	(265.39, 58.53) --
	(265.83, 58.44) --
	(266.28, 58.38) --
	(266.73, 58.33) --
	(267.18, 58.30) --
	(267.63, 58.28) --
	(268.08, 58.27) --
	(268.53, 58.27) --
	(268.97, 58.26) --
	(269.42, 58.24) --
	(269.87, 58.22) --
	(270.32, 58.19) --
	(270.77, 58.14) --
	(271.22, 58.09) --
	(271.67, 58.03) --
	(272.12, 57.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.62, 51.21) -- (234.62, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.46, 51.21) -- (211.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (238.29, 51.21) -- (238.29, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.27, 51.21) -- (218.27, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.56, 51.21) -- (216.56, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.20, 51.21) -- (231.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.58, 51.21) -- (225.58, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (250.36, 51.21) -- (250.36, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (239.90, 51.21) -- (239.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.10, 51.21) -- (234.10, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (255.24, 51.21) -- (255.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (239.30, 51.21) -- (239.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.51, 51.21) -- (202.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (255.32, 51.21) -- (255.32, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (249.26, 51.21) -- (249.26, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.87, 51.21) -- (221.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.16, 51.21) -- (231.16, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.87, 51.21) -- (236.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (240.60, 51.21) -- (240.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.64, 51.21) -- (212.64, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.50, 51.21) -- (206.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.52, 51.21) -- (219.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.30, 51.21) -- (232.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.96, 51.21) -- (222.96, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.65, 51.21) -- (220.65, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.75, 51.21) -- (229.75, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.17, 51.21) -- (226.17, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.33, 51.21) -- (221.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.12, 51.21) -- (216.12, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.09, 51.21) -- (218.09, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.64, 51.21) -- (199.64, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.60, 51.21) -- (203.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.46, 51.21) -- (201.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (245.61, 51.21) -- (245.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (242.81, 51.21) -- (242.81, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.51, 51.21) -- (232.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (235.83, 51.21) -- (235.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (246.43, 51.21) -- (246.43, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.14, 51.21) -- (205.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (244.87, 51.21) -- (244.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.05, 51.21) -- (210.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (242.98, 51.21) -- (242.98, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.52, 51.21) -- (189.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.89, 51.21) -- (184.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.35, 51.21) -- (224.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.48, 51.21) -- (215.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.03, 51.21) -- (224.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (255.79, 51.21) -- (255.79, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (251.38, 51.21) -- (251.38, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.02, 51.21) -- (208.02, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.72, 51.21) -- (211.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (260.05, 51.21) -- (260.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.50, 51.21) -- (210.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.46, 51.21) -- (169.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (239.18, 51.21) -- (239.18, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.99, 51.21) -- (219.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.91, 51.21) -- (223.91, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.77, 51.21) -- (218.77, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.63, 51.21) -- (217.63, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.85, 51.21) -- (203.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.86, 51.21) -- (225.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.98, 51.21) -- (172.98, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.95, 51.21) -- (226.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.97, 51.21) -- (234.97, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.29, 51.21) -- (194.29, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (255.49, 51.21) -- (255.49, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (239.09, 51.21) -- (239.09, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.28, 51.21) -- (191.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (246.42, 51.21) -- (246.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.34, 51.21) -- (221.34, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.40, 51.21) -- (216.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.72, 51.21) -- (226.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (237.10, 51.21) -- (237.10, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.89, 51.21) -- (194.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (248.46, 51.21) -- (248.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.29, 51.21) -- (236.29, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.76, 51.21) -- (216.76, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.68, 51.21) -- (232.68, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (243.97, 51.21) -- (243.97, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.44, 51.21) -- (224.44, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (253.54, 51.21) -- (253.54, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (238.66, 51.21) -- (238.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.99, 51.21) -- (231.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.80, 51.21) -- (181.80, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.20, 51.21) -- (222.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.15, 51.21) -- (225.15, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.28, 51.21) -- (229.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.94, 51.21) -- (213.94, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (261.40, 51.21) -- (261.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (240.29, 51.21) -- (240.29, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (256.86, 51.21) -- (256.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.22, 51.21) -- (217.22, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (157.46, 51.21) -- (157.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (250.66, 51.21) -- (250.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.20, 51.21) -- (189.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (245.15, 51.21) -- (245.15, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.28, 51.21) -- (221.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (235.97, 51.21) -- (235.97, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.30, 51.21) -- (222.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.85, 51.21) -- (201.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (255.81, 51.21) -- (255.81, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.70, 51.21) -- (230.70, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.82, 51.21) -- (233.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.31, 51.21) -- (195.31, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (245.41, 51.21) -- (245.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.96, 51.21) -- (227.96, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.85, 51.21) -- (199.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.86, 51.21) -- (227.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.40, 51.21) -- (212.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.66, 51.21) -- (216.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.51, 51.21) -- (231.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.48, 51.21) -- (218.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (239.24, 51.21) -- (239.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (243.78, 51.21) -- (243.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.30, 51.21) -- (224.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.23, 51.21) -- (217.23, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.45, 51.21) -- (205.45, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.47, 51.21) -- (232.47, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (242.88, 51.21) -- (242.88, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.79, 51.21) -- (236.79, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.10, 51.21) -- (229.10, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.50, 51.21) -- (202.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.43, 51.21) -- (223.43, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.08, 51.21) -- (185.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.12, 51.21) -- (236.12, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.62, 51.21) -- (202.62, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.41, 51.21) -- (217.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (238.50, 51.21) -- (238.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (237.28, 51.21) -- (237.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.66, 51.21) -- (214.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.23, 51.21) -- (211.23, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.48, 51.21) -- (219.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.98, 51.21) -- (196.98, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.93, 51.21) -- (220.93, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.52, 51.21) -- (223.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (241.68, 51.21) -- (241.68, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.41, 51.21) -- (222.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.14, 51.21) -- (210.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.60, 51.21) -- (219.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (240.87, 51.21) -- (240.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.46, 51.21) -- (225.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.53, 51.21) -- (189.53, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.78, 51.21) -- (209.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.58, 51.21) -- (217.58, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.84, 51.21) -- (202.84, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.28, 51.21) -- (231.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.55, 51.21) -- (224.55, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.69, 51.21) -- (204.69, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.73, 51.21) -- (221.73, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.92, 51.21) -- (224.92, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (238.10, 51.21) -- (238.10, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.19, 51.21) -- (218.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.03, 51.21) -- (213.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (165.24, 51.21) -- (165.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.35, 51.21) -- (218.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.40, 51.21) -- (207.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (249.49, 51.21) -- (249.49, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.55, 51.21) -- (229.55, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.02, 51.21) -- (211.02, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.21, 51.21) -- (218.21, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.69, 51.21) -- (219.69, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (238.48, 51.21) -- (238.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.66, 51.21) -- (208.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (247.82, 51.21) -- (247.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.61, 51.21) -- (225.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.90, 51.21) -- (203.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.66, 51.21) -- (228.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.74, 51.21) -- (231.74, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.47, 51.21) -- (191.47, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.26, 51.21) -- (236.26, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.41, 51.21) -- (230.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (247.22, 51.21) -- (247.22, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.12, 51.21) -- (218.12, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (242.19, 51.21) -- (242.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.95, 51.21) -- (223.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.72, 51.21) -- (207.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (237.66, 51.21) -- (237.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.34, 51.21) -- (227.34, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (247.59, 51.21) -- (247.59, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.82, 51.21) -- (220.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.25, 51.21) -- (220.25, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.48, 51.21) -- (195.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.10, 51.21) -- (214.10, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.63, 51.21) -- (212.63, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.30, 51.21) -- (226.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.45, 51.21) -- (231.45, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (237.91, 51.21) -- (237.91, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (244.73, 51.21) -- (244.73, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (254.53, 51.21) -- (254.53, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.32, 51.21) -- (187.32, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.53, 51.21) -- (221.53, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.20, 51.21) -- (216.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.38, 51.21) -- (213.38, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (246.95, 51.21) -- (246.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.66, 51.21) -- (210.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (237.86, 51.21) -- (237.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (240.92, 51.21) -- (240.92, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (243.62, 51.21) -- (243.62, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.08, 51.21) -- (182.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.31, 51.21) -- (226.31, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.68, 51.21) -- (236.68, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.87, 51.21) -- (224.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.18, 51.21) -- (220.18, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (238.49, 51.21) -- (238.49, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.02, 51.21) -- (227.02, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.43, 51.21) -- (230.43, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (244.37, 51.21) -- (244.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.79, 51.21) -- (232.79, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.57, 51.21) -- (202.57, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (235.34, 51.21) -- (235.34, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.65, 51.21) -- (217.65, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.14, 51.21) -- (203.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.00, 51.21) -- (217.00, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.54, 51.21) -- (208.54, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.20, 51.21) -- (208.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.64, 51.21) -- (225.64, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.88, 51.21) -- (219.88, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.17, 51.21) -- (228.17, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.05, 51.21) -- (229.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.81, 51.21) -- (226.81, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.15, 51.21) -- (224.15, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.51, 51.21) -- (229.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.83, 51.21) -- (201.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.15, 51.21) -- (234.15, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.75, 51.21) -- (219.75, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.22, 51.21) -- (210.22, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.59, 51.21) -- (227.59, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.69, 51.21) -- (229.69, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.29, 51.21) -- (231.29, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.86, 51.21) -- (211.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.91, 51.21) -- (200.91, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.15, 51.21) -- (212.15, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.58, 51.21) -- (229.58, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.73, 51.21) -- (211.73, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.12, 51.21) -- (218.12, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.79, 51.21) -- (225.79, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.52, 51.21) -- (223.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.17, 51.21) -- (213.17, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.64, 51.21) -- (210.64, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.03, 51.21) -- (216.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.63, 51.21) -- (197.63, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.60, 51.21) -- (203.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.32, 51.21) -- (197.32, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.67, 51.21) -- (227.67, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.03, 51.21) -- (223.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.86, 51.21) -- (225.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.54, 51.21) -- (226.54, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.65, 51.21) -- (231.65, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.14, 51.21) -- (205.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.01, 51.21) -- (229.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.78, 51.21) -- (208.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (235.04, 51.21) -- (235.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.52, 51.21) -- (189.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.89, 51.21) -- (184.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.70, 51.21) -- (215.70, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.13, 51.21) -- (209.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.69, 51.21) -- (213.69, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.71, 51.21) -- (228.71, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.67, 51.21) -- (229.67, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.54, 51.21) -- (205.54, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.72, 51.21) -- (211.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.64, 51.21) -- (236.64, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.50, 51.21) -- (210.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.46, 51.21) -- (169.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.80, 51.21) -- (233.80, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.59, 51.21) -- (214.59, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.54, 51.21) -- (221.54, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.41, 51.21) -- (213.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.46, 51.21) -- (217.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.85, 51.21) -- (203.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.35, 51.21) -- (208.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.98, 51.21) -- (172.98, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.97, 51.21) -- (221.97, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.72, 51.21) -- (229.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.15, 51.21) -- (234.15, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.59, 51.21) -- (217.59, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.28, 51.21) -- (191.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.19, 51.21) -- (234.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.85, 51.21) -- (216.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.40, 51.21) -- (216.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.78, 51.21) -- (221.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.58, 51.21) -- (230.58, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.42, 51.21) -- (232.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.43, 51.21) -- (228.43, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.13, 51.21) -- (209.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.92, 51.21) -- (222.92, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.49, 51.21) -- (231.49, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.87, 51.21) -- (218.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.33, 51.21) -- (226.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.04, 51.21) -- (219.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.56, 51.21) -- (231.56, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.80, 51.21) -- (181.80, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.95, 51.21) -- (217.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.66, 51.21) -- (210.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.11, 51.21) -- (211.11, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.89, 51.21) -- (207.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (238.15, 51.21) -- (238.15, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.82, 51.21) -- (230.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.06, 51.21) -- (233.06, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.66, 51.21) -- (215.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (157.46, 51.21) -- (157.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.61, 51.21) -- (233.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.20, 51.21) -- (189.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.60, 51.21) -- (234.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.56, 51.21) -- (220.56, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.54, 51.21) -- (215.54, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.95, 51.21) -- (213.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.85, 51.21) -- (201.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.75, 51.21) -- (233.75, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.95, 51.21) -- (228.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.48, 51.21) -- (230.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.31, 51.21) -- (195.31, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.24, 51.21) -- (233.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.66, 51.21) -- (220.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.85, 51.21) -- (199.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.45, 51.21) -- (225.45, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.40, 51.21) -- (212.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.66, 51.21) -- (216.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.04, 51.21) -- (219.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.50, 51.21) -- (211.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.88, 51.21) -- (225.88, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.33, 51.21) -- (232.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.36, 51.21) -- (221.36, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.91, 51.21) -- (214.91, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.45, 51.21) -- (205.45, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.26, 51.21) -- (228.26, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.81, 51.21) -- (231.81, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.20, 51.21) -- (229.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.70, 51.21) -- (208.70, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.04, 51.21) -- (202.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.77, 51.21) -- (221.77, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.08, 51.21) -- (185.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.38, 51.21) -- (225.38, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.58, 51.21) -- (199.58, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.99, 51.21) -- (216.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.51, 51.21) -- (232.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.43, 51.21) -- (228.43, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.66, 51.21) -- (214.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.62, 51.21) -- (208.62, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.48, 51.21) -- (219.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.88, 51.21) -- (194.88, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.19, 51.21) -- (208.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.31, 51.21) -- (219.31, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.91, 51.21) -- (232.91, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.41, 51.21) -- (222.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.14, 51.21) -- (210.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.18, 51.21) -- (207.18, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.58, 51.21) -- (230.58, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.03, 51.21) -- (220.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.53, 51.21) -- (189.53, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.78, 51.21) -- (209.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.14, 51.21) -- (210.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.84, 51.21) -- (202.84, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.68, 51.21) -- (222.68, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.90, 51.21) -- (215.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.69, 51.21) -- (204.69, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.78, 51.21) -- (219.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.46, 51.21) -- (219.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.12, 51.21) -- (222.12, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.68, 51.21) -- (202.68, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.72, 51.21) -- (212.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (165.24, 51.21) -- (165.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.35, 51.21) -- (218.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.84, 51.21) -- (233.84, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.13, 51.21) -- (209.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.77, 51.21) -- (207.77, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.21, 51.21) -- (218.21, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.29, 51.21) -- (213.29, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.60, 51.21) -- (217.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.07, 51.21) -- (201.07, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.44, 51.21) -- (228.44, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.18, 51.21) -- (223.18, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.48, 51.21) -- (194.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.00, 51.21) -- (217.00, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.50, 51.21) -- (223.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.47, 51.21) -- (191.47, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.80, 51.21) -- (228.80, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.59, 51.21) -- (223.59, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.43, 51.21) -- (233.43, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.13, 51.21) -- (209.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.35, 51.21) -- (227.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.13, 51.21) -- (209.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.72, 51.21) -- (207.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.55, 51.21) -- (222.55, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.60, 51.21) -- (225.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.41, 51.21) -- (229.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.86, 51.21) -- (211.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.65, 51.21) -- (209.65, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.48, 51.21) -- (195.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.13, 51.21) -- (208.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.27, 51.21) -- (210.27, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.42, 51.21) -- (217.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.42, 51.21) -- (220.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.87, 51.21) -- (230.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.98, 51.21) -- (232.98, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.91, 51.21) -- (230.91, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.32, 51.21) -- (187.32, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.24, 51.21) -- (221.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.50, 51.21) -- (211.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.38, 51.21) -- (213.38, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.51, 51.21) -- (227.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.66, 51.21) -- (210.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.27, 51.21) -- (229.27, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.49, 51.21) -- (231.49, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.48, 51.21) -- (225.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.08, 51.21) -- (182.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.86, 51.21) -- (220.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.95, 51.21) -- (231.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.51, 51.21) -- (222.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.99, 51.21) -- (218.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.06, 51.21) -- (232.06, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.96, 51.21) -- (223.96, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.22, 51.21) -- (224.22, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.19, 51.21) -- (225.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.51, 51.21) -- (221.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.57, 51.21) -- (202.57, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.06, 51.21) -- (227.06, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.24, 51.21) -- (209.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.73, 51.21) -- (196.73, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.13, 51.21) -- (209.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.46, 51.21) -- (201.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.34, 51.21) -- (218.34, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.86, 51.21) -- (211.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.70, 51.21) -- (219.70, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.69, 51.21) -- (224.69, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.63, 51.21) -- (219.63, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.97, 51.21) -- (215.97, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.16, 51.21) -- (221.16, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.60, 51.21) -- (195.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.68, 51.21) -- (225.68, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.86, 51.21) -- (211.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.76, 51.21) -- (202.76, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.87, 51.21) -- (220.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.14, 51.21) -- (222.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.05, 51.21) -- (223.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.81, 51.21) -- (206.81, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.74, 51.21) -- (195.74, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.97, 51.21) -- (203.97, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.58, 51.21) -- (222.58, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.33, 51.21) -- (204.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.18, 51.21) -- (213.18, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.30, 51.21) -- (220.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.08, 51.21) -- (219.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.61, 51.21) -- (205.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.39, 51.21) -- (203.39, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.02, 51.21) -- (209.02, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.27, 51.21) -- (203.27, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.45, 51.21) -- (192.45, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.36, 51.21) -- (219.36, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.11, 51.21) -- (215.11, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.58, 51.21) -- (222.58, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.10, 51.21) -- (221.10, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.80, 51.21) -- (223.80, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.30, 51.21) -- (200.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.16, 51.21) -- (221.16, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.71, 51.21) -- (205.71, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.51, 51.21) -- (227.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.52, 51.21) -- (189.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.89, 51.21) -- (184.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.50, 51.21) -- (207.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.61, 51.21) -- (205.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.33, 51.21) -- (220.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.47, 51.21) -- (221.47, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.14, 51.21) -- (197.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.52, 51.21) -- (211.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.17, 51.21) -- (228.17, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.50, 51.21) -- (210.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.46, 51.21) -- (169.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.38, 51.21) -- (225.38, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.42, 51.21) -- (207.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.42, 51.21) -- (216.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.70, 51.21) -- (207.70, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.36, 51.21) -- (212.36, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.08, 51.21) -- (202.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.98, 51.21) -- (172.98, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.52, 51.21) -- (215.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.78, 51.21) -- (221.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.68, 51.21) -- (225.68, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.13, 51.21) -- (209.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.07, 51.21) -- (226.07, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.63, 51.21) -- (210.63, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.86, 51.21) -- (210.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.61, 51.21) -- (214.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.01, 51.21) -- (224.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.99, 51.21) -- (223.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.21, 51.21) -- (222.21, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.94, 51.21) -- (214.94, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.85, 51.21) -- (223.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.26, 51.21) -- (212.26, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.14, 51.21) -- (220.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.57, 51.21) -- (210.57, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.16, 51.21) -- (227.16, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.80, 51.21) -- (181.80, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.19, 51.21) -- (210.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.55, 51.21) -- (203.55, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.39, 51.21) -- (203.39, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.68, 51.21) -- (229.68, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.41, 51.21) -- (223.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.73, 51.21) -- (224.73, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.30, 51.21) -- (209.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (157.46, 51.21) -- (157.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.28, 51.21) -- (225.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.20, 51.21) -- (189.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.30, 51.21) -- (227.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.28, 51.21) -- (219.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.50, 51.21) -- (207.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.61, 51.21) -- (205.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.85, 51.21) -- (201.85, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.28, 51.21) -- (225.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.48, 51.21) -- (223.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.87, 51.21) -- (223.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.77, 51.21) -- (193.77, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.87, 51.21) -- (224.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.41, 51.21) -- (219.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.10, 51.21) -- (198.10, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.04, 51.21) -- (219.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.21, 51.21) -- (209.21, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.70, 51.21) -- (215.70, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.57, 51.21) -- (210.57, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.37, 51.21) -- (206.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.60, 51.21) -- (217.60, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.35, 51.21) -- (226.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.13, 51.21) -- (215.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.65, 51.21) -- (211.65, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.55, 51.21) -- (198.55, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.87, 51.21) -- (219.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.62, 51.21) -- (223.62, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.92, 51.21) -- (220.92, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.66, 51.21) -- (201.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.77, 51.21) -- (197.77, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.26, 51.21) -- (214.26, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.08, 51.21) -- (185.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.71, 51.21) -- (220.71, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.03, 51.21) -- (193.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.82, 51.21) -- (210.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.79, 51.21) -- (224.79, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.39, 51.21) -- (221.39, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.66, 51.21) -- (214.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.05, 51.21) -- (219.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.62, 51.21) -- (188.62, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.52, 51.21) -- (212.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.44, 51.21) -- (224.44, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.65, 51.21) -- (218.65, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.56, 51.21) -- (209.56, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.10, 51.21) -- (200.10, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.55, 51.21) -- (222.55, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.95, 51.21) -- (213.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.53, 51.21) -- (189.53, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.78, 51.21) -- (209.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.87, 51.21) -- (202.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.84, 51.21) -- (202.84, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.18, 51.21) -- (216.18, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.92, 51.21) -- (208.92, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.29, 51.21) -- (202.29, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.63, 51.21) -- (212.63, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.86, 51.21) -- (211.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.08, 51.21) -- (214.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.94, 51.21) -- (195.94, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.61, 51.21) -- (205.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (165.24, 51.21) -- (165.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.32, 51.21) -- (216.32, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.45, 51.21) -- (225.45, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.16, 51.21) -- (203.16, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.38, 51.21) -- (215.38, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.62, 51.21) -- (206.62, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.13, 51.21) -- (209.13, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.42, 51.21) -- (197.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.24, 51.21) -- (220.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.96, 51.21) -- (220.96, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.94, 51.21) -- (187.94, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.95, 51.21) -- (211.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.55, 51.21) -- (219.55, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.22, 51.21) -- (184.22, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.41, 51.21) -- (221.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.45, 51.21) -- (215.45, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.97, 51.21) -- (225.97, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.04, 51.21) -- (219.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.72, 51.21) -- (207.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.08, 51.21) -- (214.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.45, 51.21) -- (218.45, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.56, 51.21) -- (221.56, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.40, 51.21) -- (203.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.52, 51.21) -- (205.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.37, 51.21) -- (203.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.52, 51.21) -- (205.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.18, 51.21) -- (210.18, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.04, 51.21) -- (212.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.90, 51.21) -- (223.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.73, 51.21) -- (224.73, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.01, 51.21) -- (223.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.17, 51.21) -- (217.17, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.39, 51.21) -- (203.39, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.21, 51.21) -- (210.21, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.04, 51.21) -- (219.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.41, 51.21) -- (210.41, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.33, 51.21) -- (221.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.56, 51.21) -- (224.56, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.83, 51.21) -- (217.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.08, 51.21) -- (182.08, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.65, 51.21) -- (214.65, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.91, 51.21) -- (223.91, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.75, 51.21) -- (214.75, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.14, 51.21) -- (217.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.28, 51.21) -- (225.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.76, 51.21) -- (218.76, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.40, 51.21) -- (216.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.89, 51.21) -- (216.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.76, 51.21) -- (213.76, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.92, 51.21) -- (197.92, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.89, 51.21) -- (219.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.00, 51.21) -- (190.00, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.48, 51.21) -- (177.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.46, 51.21) -- (189.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.67, 51.21) -- (198.67, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.03, 51.21) -- (200.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.40, 51.21) -- (206.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.03, 51.21) -- (200.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.30, 51.21) -- (196.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.82, 51.21) -- (201.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.48, 51.21) -- (177.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.01, 51.21) -- (206.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.95, 51.21) -- (184.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.87, 51.21) -- (203.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.89, 51.21) -- (202.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.39, 51.21) -- (203.39, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.83, 51.21) -- (187.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.48, 51.21) -- (177.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.28, 51.21) -- (204.28, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.37, 51.21) -- (202.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.46, 51.21) -- (189.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.52, 51.21) -- (172.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.67, 51.21) -- (190.67, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.30, 51.21) -- (176.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.03, 51.21) -- (200.03, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.30, 51.21) -- (196.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.77, 51.21) -- (204.77, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.89, 51.21) -- (202.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.33, 51.21) -- (204.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.24, 51.21) -- (184.24, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.82, 51.21) -- (201.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.30, 51.21) -- (198.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.84, 51.21) -- (207.84, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.52, 51.21) -- (172.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.48, 51.21) -- (177.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.83, 51.21) -- (187.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.37, 51.21) -- (202.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.48, 51.21) -- (177.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.51, 51.21) -- (196.51, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.50, 51.21) -- (208.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.93, 51.21) -- (195.93, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.05, 51.21) -- (164.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.01, 51.21) -- (206.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.83, 51.21) -- (187.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.67, 51.21) -- (198.67, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.42, 51.21) -- (189.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.82, 51.21) -- (196.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.05, 51.21) -- (164.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.30, 51.21) -- (196.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.37, 51.21) -- (202.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.05, 51.21) -- (164.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.01, 51.21) -- (206.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.46, 51.21) -- (189.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.05, 51.21) -- (164.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.40, 51.21) -- (206.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.35, 51.21) -- (193.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.30, 51.21) -- (196.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.86, 51.21) -- (204.86, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.05, 51.21) -- (164.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.33, 51.21) -- (204.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.82, 51.21) -- (203.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.30, 51.21) -- (196.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.33, 51.21) -- (204.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.35, 51.21) -- (193.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.05, 51.21) -- (207.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.90, 51.21) -- (190.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.50, 51.21) -- (207.50, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.52, 51.21) -- (172.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.90, 51.21) -- (190.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.88, 51.21) -- (185.88, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.01, 51.21) -- (210.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.61, 51.21) -- (204.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.20, 51.21) -- (205.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.31, 51.21) -- (190.31, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (157.46, 51.21) -- (157.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.61, 51.21) -- (205.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.32, 51.21) -- (180.32, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.84, 51.21) -- (207.84, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.37, 51.21) -- (202.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.83, 51.21) -- (187.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.19, 51.21) -- (192.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.61, 51.21) -- (205.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.01, 51.21) -- (206.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.54, 51.21) -- (204.54, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.93, 51.21) -- (178.93, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.20, 51.21) -- (205.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.89, 51.21) -- (202.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.23, 51.21) -- (182.23, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.37, 51.21) -- (199.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.90, 51.21) -- (190.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.19, 51.21) -- (199.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.90, 51.21) -- (190.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.57, 51.21) -- (190.57, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.93, 51.21) -- (197.93, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.14, 51.21) -- (207.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.80, 51.21) -- (196.80, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.19, 51.21) -- (183.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.33, 51.21) -- (204.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.26, 51.21) -- (201.26, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.31, 51.21) -- (180.31, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.19, 51.21) -- (196.19, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.52, 51.21) -- (172.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.47, 51.21) -- (203.47, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.25, 51.21) -- (176.25, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.35, 51.21) -- (193.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.20, 51.21) -- (205.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.37, 51.21) -- (202.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.67, 51.21) -- (198.67, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.37, 51.21) -- (202.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.25, 51.21) -- (177.25, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.82, 51.21) -- (194.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.77, 51.21) -- (204.77, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.37, 51.21) -- (199.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.89, 51.21) -- (202.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.18, 51.21) -- (195.18, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.78, 51.21) -- (178.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.67, 51.21) -- (198.67, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.46, 51.21) -- (189.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.04, 51.21) -- (194.04, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.35, 51.21) -- (193.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.48, 51.21) -- (177.48, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.05, 51.21) -- (164.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.57, 51.21) -- (199.57, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.52, 51.21) -- (172.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.01, 51.21) -- (206.01, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.70, 51.21) -- (201.70, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.83, 51.21) -- (187.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.46, 51.21) -- (189.46, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.66, 51.21) -- (200.66, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.87, 51.21) -- (203.87, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.52, 51.21) -- (172.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.14, 51.21) -- (197.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.82, 51.21) -- (201.82, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.36, 51.21) -- (166.36, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.25, 51.21) -- (202.25, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.30, 51.21) -- (196.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.40, 51.21) -- (206.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.37, 51.21) -- (199.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.99, 51.21) -- (180.99, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.35, 51.21) -- (193.35, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.65, 51.21) -- (199.65, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.89, 51.21) -- (202.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.78, 51.21) -- (183.78, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.95, 51.21) -- (185.95, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.52, 51.21) -- (172.52, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.40, 51.21) -- (186.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.83, 51.21) -- (187.83, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.90, 51.21) -- (190.90, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.07, 51.21) -- (193.07, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.71, 51.21) -- (204.71, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.20, 51.21) -- (205.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.39, 51.21) -- (203.39, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.05, 51.21) -- (164.05, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.21, 51.21) -- (200.21, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.72, 51.21) -- (183.72, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.92, 51.21) -- (192.92, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.37, 51.21) -- (199.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.37, 51.21) -- (202.37, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.20, 51.21) -- (205.20, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.67, 51.21) -- (198.67, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.07, 51.21) -- (177.07, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.30, 51.21) -- (196.30, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.33, 51.21) -- (204.33, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.40, 51.21) -- (195.40, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.89, 51.21) -- (200.89, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.61, 51.21) -- (205.61, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.92, 51.21) -- (201.92, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.14, 51.21) -- (197.14, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.53, 51.21) -- (197.53, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.42, 51.21) -- (194.42, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.93, 51.21) -- (180.93, 57.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.82, 51.21) -- (201.82, 57.71);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 51.21) rectangle (283.58,193.24);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 54.91) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 80.74) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,106.56) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,132.38) {0.3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,158.21) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,184.03) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 57.67) --
	( 31.37, 57.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 83.49) --
	( 31.37, 83.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,109.32) --
	( 31.37,109.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,135.14) --
	( 31.37,135.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,160.96) --
	( 31.37,160.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,186.79) --
	( 31.37,186.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.46, 48.46) --
	( 78.46, 51.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (127.34, 48.46) --
	(127.34, 51.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (176.22, 48.46) --
	(176.22, 51.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.10, 48.46) --
	(225.10, 51.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (273.98, 48.46) --
	(273.98, 51.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 78.46, 40.75) {0.000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (127.34, 40.75) {0.002};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (176.22, 40.75) {0.135};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (225.10, 40.75) {7.389};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (273.98, 40.75) {403.429};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (157.47, 30.25) {Cumulative exposure (mg/m$^3\cdot\,$years)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,122.23) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 90.36,  5.50) rectangle (224.59, 26.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (101.36, 11.00) rectangle (111.36, 21.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect] (102.07, 11.71) rectangle (110.65, 20.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (138.35, 11.00) rectangle (148.35, 21.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line cap=rect] (139.06, 11.71) rectangle (147.64, 20.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (170.85, 11.00) rectangle (180.85, 21.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line cap=rect] (171.56, 11.71) rectangle (180.14, 20.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (116.86, 12.90) {0.25};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (153.85, 12.90) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (186.35, 12.90) {No limit};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-06-03 resources/shift-soluble.tex
Upload work

% Created by tikzDevice version 0.12.3.1 on 2022-06-02 13:14:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,198.74);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,198.74);
\end{scope}
\begin{scope}
\path[clip] ( 31.37, 51.21) rectangle (283.58,193.24);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37, 51.21) rectangle (283.58,193.24);

\path[] ( 42.83, 57.70) --
	( 43.28, 57.71) --
	( 43.73, 57.71) --
	( 44.18, 57.71) --
	( 44.63, 57.71) --
	( 45.08, 57.71) --
	( 45.52, 57.71) --
	( 45.97, 57.71) --
	( 46.42, 57.71) --
	( 46.87, 57.72) --
	( 47.32, 57.72) --
	( 47.77, 57.72) --
	( 48.22, 57.73) --
	( 48.67, 57.74) --
	( 49.11, 57.75) --
	( 49.56, 57.76) --
	( 50.01, 57.77) --
	( 50.46, 57.78) --
	( 50.91, 57.78) --
	( 51.36, 57.79) --
	( 51.81, 57.78) --
	( 52.25, 57.78) --
	( 52.70, 57.77) --
	( 53.15, 57.77) --
	( 53.60, 57.76) --
	( 54.05, 57.75) --
	( 54.50, 57.75) --
	( 54.95, 57.75) --
	( 55.40, 57.75) --
	( 55.84, 57.75) --
	( 56.29, 57.76) --
	( 56.74, 57.77) --
	( 57.19, 57.77) --
	( 57.64, 57.78) --
	( 58.09, 57.79) --
	( 58.54, 57.80) --
	( 58.99, 57.81) --
	( 59.43, 57.81) --
	( 59.88, 57.82) --
	( 60.33, 57.83) --
	( 60.78, 57.83) --
	( 61.23, 57.84) --
	( 61.68, 57.84) --
	( 62.13, 57.84) --
	( 62.57, 57.84) --
	( 63.02, 57.85) --
	( 63.47, 57.85) --
	( 63.92, 57.86) --
	( 64.37, 57.87) --
	( 64.82, 57.88) --
	( 65.27, 57.89) --
	( 65.72, 57.90) --
	( 66.16, 57.91) --
	( 66.61, 57.91) --
	( 67.06, 57.91) --
	( 67.51, 57.91) --
	( 67.96, 57.91) --
	( 68.41, 57.90) --
	( 68.86, 57.90) --
	( 69.31, 57.90) --
	( 69.75, 57.90) --
	( 70.20, 57.90) --
	( 70.65, 57.90) --
	( 71.10, 57.90) --
	( 71.55, 57.91) --
	( 72.00, 57.92) --
	( 72.45, 57.94) --
	( 72.89, 57.95) --
	( 73.34, 57.97) --
	( 73.79, 58.00) --
	( 74.24, 58.02) --
	( 74.69, 58.05) --
	( 75.14, 58.07) --
	( 75.59, 58.10) --
	( 76.04, 58.13) --
	( 76.48, 58.16) --
	( 76.93, 58.19) --
	( 77.38, 58.22) --
	( 77.83, 58.24) --
	( 78.28, 58.25) --
	( 78.73, 58.26) --
	( 79.18, 58.27) --
	( 79.63, 58.27) --
	( 80.07, 58.26) --
	( 80.52, 58.26) --
	( 80.97, 58.25) --
	( 81.42, 58.24) --
	( 81.87, 58.23) --
	( 82.32, 58.22) --
	( 82.77, 58.22) --
	( 83.21, 58.22) --
	( 83.66, 58.22) --
	( 84.11, 58.24) --
	( 84.56, 58.25) --
	( 85.01, 58.28) --
	( 85.46, 58.31) --
	( 85.91, 58.35) --
	( 86.36, 58.40) --
	( 86.80, 58.46) --
	( 87.25, 58.52) --
	( 87.70, 58.59) --
	( 88.15, 58.65) --
	( 88.60, 58.71) --
	( 89.05, 58.75) --
	( 89.50, 58.77) --
	( 89.95, 58.78) --
	( 90.39, 58.76) --
	( 90.84, 58.74) --
	( 91.29, 58.71) --
	( 91.74, 58.69) --
	( 92.19, 58.68) --
	( 92.64, 58.68) --
	( 93.09, 58.70) --
	( 93.53, 58.73) --
	( 93.98, 58.78) --
	( 94.43, 58.84) --
	( 94.88, 58.89) --
	( 95.33, 58.95) --
	( 95.78, 59.00) --
	( 96.23, 59.04) --
	( 96.68, 59.09) --
	( 97.12, 59.12) --
	( 97.57, 59.16) --
	( 98.02, 59.20) --
	( 98.47, 59.24) --
	( 98.92, 59.29) --
	( 99.37, 59.33) --
	( 99.82, 59.38) --
	(100.27, 59.42) --
	(100.71, 59.46) --
	(101.16, 59.49) --
	(101.61, 59.53) --
	(102.06, 59.57) --
	(102.51, 59.62) --
	(102.96, 59.68) --
	(103.41, 59.74) --
	(103.85, 59.82) --
	(104.30, 59.90) --
	(104.75, 59.98) --
	(105.20, 60.07) --
	(105.65, 60.16) --
	(106.10, 60.23) --
	(106.55, 60.29) --
	(107.00, 60.33) --
	(107.44, 60.33) --
	(107.89, 60.32) --
	(108.34, 60.27) --
	(108.79, 60.21) --
	(109.24, 60.15) --
	(109.69, 60.09) --
	(110.14, 60.05) --
	(110.59, 60.03) --
	(111.03, 60.04) --
	(111.48, 60.07) --
	(111.93, 60.13) --
	(112.38, 60.21) --
	(112.83, 60.31) --
	(113.28, 60.42) --
	(113.73, 60.54) --
	(114.17, 60.68) --
	(114.62, 60.83) --
	(115.07, 61.03) --
	(115.52, 61.32) --
	(115.97, 61.75) --
	(116.42, 62.41) --
	(116.87, 63.41) --
	(117.32, 64.87) --
	(117.76, 66.87) --
	(118.21, 69.43) --
	(118.66, 72.50) --
	(119.11, 75.89) --
	(119.56, 79.33) --
	(120.01, 82.43) --
	(120.46, 84.82) --
	(120.91, 86.17) --
	(121.35, 86.30) --
	(121.80, 85.21) --
	(122.25, 83.04) --
	(122.70, 80.20) --
	(123.15, 77.10) --
	(123.60, 74.08) --
	(124.05, 71.39) --
	(124.49, 69.17) --
	(124.94, 67.48) --
	(125.39, 66.29) --
	(125.84, 65.51) --
	(126.29, 65.07) --
	(126.74, 64.91) --
	(127.19, 64.99) --
	(127.64, 65.33) --
	(128.08, 65.97) --
	(128.53, 67.02) --
	(128.98, 68.59) --
	(129.43, 70.86) --
	(129.88, 73.86) --
	(130.33, 77.54) --
	(130.78, 81.72) --
	(131.23, 86.09) --
	(131.67, 90.19) --
	(132.12, 93.54) --
	(132.57, 95.71) --
	(133.02, 96.43) --
	(133.47, 95.65) --
	(133.92, 93.57) --
	(134.37, 90.61) --
	(134.81, 87.32) --
	(135.26, 84.28) --
	(135.71, 82.02) --
	(136.16, 80.96) --
	(136.61, 81.39) --
	(137.06, 83.20) --
	(137.51, 86.19) --
	(137.96, 89.97) --
	(138.40, 94.06) --
	(138.85, 97.92) --
	(139.30,101.10) --
	(139.75,103.30) --
	(140.20,104.46) --
	(140.65,104.81) --
	(141.10,104.78) --
	(141.55,104.91) --
	(141.99,105.73) --
	(142.44,107.60) --
	(142.89,110.57) --
	(143.34,114.42) --
	(143.79,118.64) --
	(144.24,122.65) --
	(144.69,126.06) --
	(145.13,128.71) --
	(145.58,130.72) --
	(146.03,132.38) --
	(146.48,134.01) --
	(146.93,135.86) --
	(147.38,137.97) --
	(147.83,140.22) --
	(148.28,142.36) --
	(148.72,144.16) --
	(149.17,145.46) --
	(149.62,146.24) --
	(150.07,146.61) --
	(150.52,146.73) --
	(150.97,146.72) --
	(151.42,146.65) --
	(151.87,146.50) --
	(152.31,146.24) --
	(152.76,145.86) --
	(153.21,145.36) --
	(153.66,144.76) --
	(154.11,144.13) --
	(154.56,143.52) --
	(155.01,143.00) --
	(155.45,142.61) --
	(155.90,142.39) --
	(156.35,142.38) --
	(156.80,142.59) --
	(157.25,142.99) --
	(157.70,143.56) --
	(158.15,144.27) --
	(158.60,145.06) --
	(159.04,145.91) --
	(159.49,146.80) --
	(159.94,147.73) --
	(160.39,148.67) --
	(160.84,149.62) --
	(161.29,150.54) --
	(161.74,151.39) --
	(162.19,152.14) --
	(162.63,152.78) --
	(163.08,153.32) --
	(163.53,153.81) --
	(163.98,154.31) --
	(164.43,154.92) --
	(164.88,155.75) --
	(165.33,156.89) --
	(165.77,158.39) --
	(166.22,160.28) --
	(166.67,162.54) --
	(167.12,165.11) --
	(167.57,167.88) --
	(168.02,170.70) --
	(168.47,173.39) --
	(168.92,175.76) --
	(169.36,177.63) --
	(169.81,178.86) --
	(170.26,179.34) --
	(170.71,179.06) --
	(171.16,178.08) --
	(171.61,176.54) --
	(172.06,174.61) --
	(172.51,172.54) --
	(172.95,170.52) --
	(173.40,168.69) --
	(173.85,167.12) --
	(174.30,165.82) --
	(174.75,164.74) --
	(175.20,163.78) --
	(175.65,162.80) --
	(176.09,161.68) --
	(176.54,160.26) --
	(176.99,158.41) --
	(177.44,156.03) --
	(177.89,153.00) --
	(178.34,149.26) --
	(178.79,144.76) --
	(179.24,139.49) --
	(179.68,133.57) --
	(180.13,127.15) --
	(180.58,120.44) --
	(181.03,113.65) --
	(181.48,107.01) --
	(181.93,100.68) --
	(182.38, 94.80) --
	(182.83, 89.43) --
	(183.27, 84.61) --
	(183.72, 80.31) --
	(184.17, 76.50) --
	(184.62, 73.14) --
	(185.07, 70.18) --
	(185.52, 67.62) --
	(185.97, 65.41) --
	(186.41, 63.58) --
	(186.86, 62.07) --
	(187.31, 60.87) --
	(187.76, 59.93) --
	(188.21, 59.22) --
	(188.66, 58.71) --
	(189.11, 58.34) --
	(189.56, 58.09) --
	(190.00, 57.92) --
	(190.45, 57.82) --
	(190.90, 57.75) --
	(191.35, 57.72) --
	(191.80, 57.69) --
	(192.25, 57.68) --
	(192.70, 57.67) --
	(193.15, 57.67) --
	(193.59, 57.67) --
	(194.04, 57.67) --
	(194.49, 57.67) --
	(194.94, 57.67) --
	(195.39, 57.67) --
	(195.84, 57.67) --
	(196.29, 57.67) --
	(196.73, 57.67) --
	(197.18, 57.67) --
	(197.63, 57.67) --
	(198.08, 57.67) --
	(198.53, 57.67) --
	(198.98, 57.67) --
	(199.43, 57.67) --
	(199.88, 57.67) --
	(200.32, 57.67) --
	(200.77, 57.67) --
	(201.22, 57.67) --
	(201.67, 57.67) --
	(202.12, 57.67) --
	(202.57, 57.67) --
	(203.02, 57.67) --
	(203.47, 57.67) --
	(203.91, 57.67) --
	(204.36, 57.67) --
	(204.81, 57.67) --
	(205.26, 57.67) --
	(205.71, 57.67) --
	(206.16, 57.67) --
	(206.61, 57.67) --
	(207.05, 57.67) --
	(207.50, 57.67) --
	(207.95, 57.67) --
	(208.40, 57.67) --
	(208.85, 57.67) --
	(209.30, 57.67) --
	(209.75, 57.67) --
	(210.20, 57.67) --
	(210.64, 57.67) --
	(211.09, 57.67) --
	(211.54, 57.67) --
	(211.99, 57.67) --
	(212.44, 57.67) --
	(212.89, 57.67) --
	(213.34, 57.67) --
	(213.79, 57.67) --
	(214.23, 57.67) --
	(214.68, 57.67) --
	(215.13, 57.67) --
	(215.58, 57.67) --
	(216.03, 57.67) --
	(216.48, 57.67) --
	(216.93, 57.67) --
	(217.37, 57.67) --
	(217.82, 57.67) --
	(218.27, 57.67) --
	(218.72, 57.67) --
	(219.17, 57.67) --
	(219.62, 57.67) --
	(220.07, 57.67) --
	(220.52, 57.67) --
	(220.96, 57.67) --
	(221.41, 57.67) --
	(221.86, 57.67) --
	(222.31, 57.67) --
	(222.76, 57.67) --
	(223.21, 57.67) --
	(223.66, 57.67) --
	(224.11, 57.67) --
	(224.55, 57.67) --
	(225.00, 57.67) --
	(225.45, 57.67) --
	(225.90, 57.67) --
	(226.35, 57.67) --
	(226.80, 57.67) --
	(227.25, 57.67) --
	(227.69, 57.67) --
	(228.14, 57.67) --
	(228.59, 57.67) --
	(229.04, 57.67) --
	(229.49, 57.67) --
	(229.94, 57.67) --
	(230.39, 57.67) --
	(230.84, 57.67) --
	(231.28, 57.67) --
	(231.73, 57.67) --
	(232.18, 57.67) --
	(232.63, 57.67) --
	(233.08, 57.67) --
	(233.53, 57.67) --
	(233.98, 57.67) --
	(234.43, 57.67) --
	(234.87, 57.67) --
	(235.32, 57.67) --
	(235.77, 57.67) --
	(236.22, 57.67) --
	(236.67, 57.67) --
	(237.12, 57.67) --
	(237.57, 57.67) --
	(238.01, 57.67) --
	(238.46, 57.67) --
	(238.91, 57.67) --
	(239.36, 57.67) --
	(239.81, 57.67) --
	(240.26, 57.67) --
	(240.71, 57.67) --
	(241.16, 57.67) --
	(241.60, 57.67) --
	(242.05, 57.67) --
	(242.50, 57.67) --
	(242.95, 57.67) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67) --
	(272.12, 57.67) --
	(271.67, 57.67) --
	(271.22, 57.67) --
	(270.77, 57.67) --
	(270.32, 57.67) --
	(269.87, 57.67) --
	(269.42, 57.67) --
	(268.97, 57.67) --
	(268.53, 57.67) --
	(268.08, 57.67) --
	(267.63, 57.67) --
	(267.18, 57.67) --
	(266.73, 57.67) --
	(266.28, 57.67) --
	(265.83, 57.67) --
	(265.39, 57.67) --
	(264.94, 57.67) --
	(264.49, 57.67) --
	(264.04, 57.67) --
	(263.59, 57.67) --
	(263.14, 57.67) --
	(262.69, 57.67) --
	(262.24, 57.67) --
	(261.80, 57.67) --
	(261.35, 57.67) --
	(260.90, 57.67) --
	(260.45, 57.67) --
	(260.00, 57.67) --
	(259.55, 57.67) --
	(259.10, 57.67) --
	(258.65, 57.67) --
	(258.21, 57.67) --
	(257.76, 57.67) --
	(257.31, 57.67) --
	(256.86, 57.67) --
	(256.41, 57.67) --
	(255.96, 57.67) --
	(255.51, 57.67) --
	(255.07, 57.67) --
	(254.62, 57.67) --
	(254.17, 57.67) --
	(253.72, 57.67) --
	(253.27, 57.67) --
	(252.82, 57.67) --
	(252.37, 57.67) --
	(251.92, 57.67) --
	(251.48, 57.67) --
	(251.03, 57.67) --
	(250.58, 57.67) --
	(250.13, 57.67) --
	(249.68, 57.67) --
	(249.23, 57.67) --
	(248.78, 57.67) --
	(248.33, 57.67) --
	(247.89, 57.67) --
	(247.44, 57.67) --
	(246.99, 57.67) --
	(246.54, 57.67) --
	(246.09, 57.67) --
	(245.64, 57.67) --
	(245.19, 57.67) --
	(244.75, 57.67) --
	(244.30, 57.67) --
	(243.85, 57.67) --
	(243.40, 57.67) --
	(242.95, 57.67) --
	(242.50, 57.67) --
	(242.05, 57.67) --
	(241.60, 57.67) --
	(241.16, 57.67) --
	(240.71, 57.67) --
	(240.26, 57.67) --
	(239.81, 57.67) --
	(239.36, 57.67) --
	(238.91, 57.67) --
	(238.46, 57.67) --
	(238.01, 57.67) --
	(237.57, 57.67) --
	(237.12, 57.67) --
	(236.67, 57.67) --
	(236.22, 57.67) --
	(235.77, 57.67) --
	(235.32, 57.67) --
	(234.87, 57.67) --
	(234.43, 57.67) --
	(233.98, 57.67) --
	(233.53, 57.67) --
	(233.08, 57.67) --
	(232.63, 57.67) --
	(232.18, 57.67) --
	(231.73, 57.67) --
	(231.28, 57.67) --
	(230.84, 57.67) --
	(230.39, 57.67) --
	(229.94, 57.67) --
	(229.49, 57.67) --
	(229.04, 57.67) --
	(228.59, 57.67) --
	(228.14, 57.67) --
	(227.69, 57.67) --
	(227.25, 57.67) --
	(226.80, 57.67) --
	(226.35, 57.67) --
	(225.90, 57.67) --
	(225.45, 57.67) --
	(225.00, 57.67) --
	(224.55, 57.67) --
	(224.11, 57.67) --
	(223.66, 57.67) --
	(223.21, 57.67) --
	(222.76, 57.67) --
	(222.31, 57.67) --
	(221.86, 57.67) --
	(221.41, 57.67) --
	(220.96, 57.67) --
	(220.52, 57.67) --
	(220.07, 57.67) --
	(219.62, 57.67) --
	(219.17, 57.67) --
	(218.72, 57.67) --
	(218.27, 57.67) --
	(217.82, 57.67) --
	(217.37, 57.67) --
	(216.93, 57.67) --
	(216.48, 57.67) --
	(216.03, 57.67) --
	(215.58, 57.67) --
	(215.13, 57.67) --
	(214.68, 57.67) --
	(214.23, 57.67) --
	(213.79, 57.67) --
	(213.34, 57.67) --
	(212.89, 57.67) --
	(212.44, 57.67) --
	(211.99, 57.67) --
	(211.54, 57.67) --
	(211.09, 57.67) --
	(210.64, 57.67) --
	(210.20, 57.67) --
	(209.75, 57.67) --
	(209.30, 57.67) --
	(208.85, 57.67) --
	(208.40, 57.67) --
	(207.95, 57.67) --
	(207.50, 57.67) --
	(207.05, 57.67) --
	(206.61, 57.67) --
	(206.16, 57.67) --
	(205.71, 57.67) --
	(205.26, 57.67) --
	(204.81, 57.67) --
	(204.36, 57.67) --
	(203.91, 57.67) --
	(203.47, 57.67) --
	(203.02, 57.67) --
	(202.57, 57.67) --
	(202.12, 57.67) --
	(201.67, 57.67) --
	(201.22, 57.67) --
	(200.77, 57.67) --
	(200.32, 57.67) --
	(199.88, 57.67) --
	(199.43, 57.67) --
	(198.98, 57.67) --
	(198.53, 57.67) --
	(198.08, 57.67) --
	(197.63, 57.67) --
	(197.18, 57.67) --
	(196.73, 57.67) --
	(196.29, 57.67) --
	(195.84, 57.67) --
	(195.39, 57.67) --
	(194.94, 57.67) --
	(194.49, 57.67) --
	(194.04, 57.67) --
	(193.59, 57.67) --
	(193.15, 57.67) --
	(192.70, 57.67) --
	(192.25, 57.67) --
	(191.80, 57.67) --
	(191.35, 57.67) --
	(190.90, 57.67) --
	(190.45, 57.67) --
	(190.00, 57.67) --
	(189.56, 57.67) --
	(189.11, 57.67) --
	(188.66, 57.67) --
	(188.21, 57.67) --
	(187.76, 57.67) --
	(187.31, 57.67) --
	(186.86, 57.67) --
	(186.41, 57.67) --
	(185.97, 57.67) --
	(185.52, 57.67) --
	(185.07, 57.67) --
	(184.62, 57.67) --
	(184.17, 57.67) --
	(183.72, 57.67) --
	(183.27, 57.67) --
	(182.83, 57.67) --
	(182.38, 57.67) --
	(181.93, 57.67) --
	(181.48, 57.67) --
	(181.03, 57.67) --
	(180.58, 57.67) --
	(180.13, 57.67) --
	(179.68, 57.67) --
	(179.24, 57.67) --
	(178.79, 57.67) --
	(178.34, 57.67) --
	(177.89, 57.67) --
	(177.44, 57.67) --
	(176.99, 57.67) --
	(176.54, 57.67) --
	(176.09, 57.67) --
	(175.65, 57.67) --
	(175.20, 57.67) --
	(174.75, 57.67) --
	(174.30, 57.67) --
	(173.85, 57.67) --
	(173.40, 57.67) --
	(172.95, 57.67) --
	(172.51, 57.67) --
	(172.06, 57.67) --
	(171.61, 57.67) --
	(171.16, 57.67) --
	(170.71, 57.67) --
	(170.26, 57.67) --
	(169.81, 57.67) --
	(169.36, 57.67) --
	(168.92, 57.67) --
	(168.47, 57.67) --
	(168.02, 57.67) --
	(167.57, 57.67) --
	(167.12, 57.67) --
	(166.67, 57.67) --
	(166.22, 57.67) --
	(165.77, 57.67) --
	(165.33, 57.67) --
	(164.88, 57.67) --
	(164.43, 57.67) --
	(163.98, 57.67) --
	(163.53, 57.67) --
	(163.08, 57.67) --
	(162.63, 57.67) --
	(162.19, 57.67) --
	(161.74, 57.67) --
	(161.29, 57.67) --
	(160.84, 57.67) --
	(160.39, 57.67) --
	(159.94, 57.67) --
	(159.49, 57.67) --
	(159.04, 57.67) --
	(158.60, 57.67) --
	(158.15, 57.67) --
	(157.70, 57.67) --
	(157.25, 57.67) --
	(156.80, 57.67) --
	(156.35, 57.67) --
	(155.90, 57.67) --
	(155.45, 57.67) --
	(155.01, 57.67) --
	(154.56, 57.67) --
	(154.11, 57.67) --
	(153.66, 57.67) --
	(153.21, 57.67) --
	(152.76, 57.67) --
	(152.31, 57.67) --
	(151.87, 57.67) --
	(151.42, 57.67) --
	(150.97, 57.67) --
	(150.52, 57.67) --
	(150.07, 57.67) --
	(149.62, 57.67) --
	(149.17, 57.67) --
	(148.72, 57.67) --
	(148.28, 57.67) --
	(147.83, 57.67) --
	(147.38, 57.67) --
	(146.93, 57.67) --
	(146.48, 57.67) --
	(146.03, 57.67) --
	(145.58, 57.67) --
	(145.13, 57.67) --
	(144.69, 57.67) --
	(144.24, 57.67) --
	(143.79, 57.67) --
	(143.34, 57.67) --
	(142.89, 57.67) --
	(142.44, 57.67) --
	(141.99, 57.67) --
	(141.55, 57.67) --
	(141.10, 57.67) --
	(140.65, 57.67) --
	(140.20, 57.67) --
	(139.75, 57.67) --
	(139.30, 57.67) --
	(138.85, 57.67) --
	(138.40, 57.67) --
	(137.96, 57.67) --
	(137.51, 57.67) --
	(137.06, 57.67) --
	(136.61, 57.67) --
	(136.16, 57.67) --
	(135.71, 57.67) --
	(135.26, 57.67) --
	(134.81, 57.67) --
	(134.37, 57.67) --
	(133.92, 57.67) --
	(133.47, 57.67) --
	(133.02, 57.67) --
	(132.57, 57.67) --
	(132.12, 57.67) --
	(131.67, 57.67) --
	(131.23, 57.67) --
	(130.78, 57.67) --
	(130.33, 57.67) --
	(129.88, 57.67) --
	(129.43, 57.67) --
	(128.98, 57.67) --
	(128.53, 57.67) --
	(128.08, 57.67) --
	(127.64, 57.67) --
	(127.19, 57.67) --
	(126.74, 57.67) --
	(126.29, 57.67) --
	(125.84, 57.67) --
	(125.39, 57.67) --
	(124.94, 57.67) --
	(124.49, 57.67) --
	(124.05, 57.67) --
	(123.60, 57.67) --
	(123.15, 57.67) --
	(122.70, 57.67) --
	(122.25, 57.67) --
	(121.80, 57.67) --
	(121.35, 57.67) --
	(120.91, 57.67) --
	(120.46, 57.67) --
	(120.01, 57.67) --
	(119.56, 57.67) --
	(119.11, 57.67) --
	(118.66, 57.67) --
	(118.21, 57.67) --
	(117.76, 57.67) --
	(117.32, 57.67) --
	(116.87, 57.67) --
	(116.42, 57.67) --
	(115.97, 57.67) --
	(115.52, 57.67) --
	(115.07, 57.67) --
	(114.62, 57.67) --
	(114.17, 57.67) --
	(113.73, 57.67) --
	(113.28, 57.67) --
	(112.83, 57.67) --
	(112.38, 57.67) --
	(111.93, 57.67) --
	(111.48, 57.67) --
	(111.03, 57.67) --
	(110.59, 57.67) --
	(110.14, 57.67) --
	(109.69, 57.67) --
	(109.24, 57.67) --
	(108.79, 57.67) --
	(108.34, 57.67) --
	(107.89, 57.67) --
	(107.44, 57.67) --
	(107.00, 57.67) --
	(106.55, 57.67) --
	(106.10, 57.67) --
	(105.65, 57.67) --
	(105.20, 57.67) --
	(104.75, 57.67) --
	(104.30, 57.67) --
	(103.85, 57.67) --
	(103.41, 57.67) --
	(102.96, 57.67) --
	(102.51, 57.67) --
	(102.06, 57.67) --
	(101.61, 57.67) --
	(101.16, 57.67) --
	(100.71, 57.67) --
	(100.27, 57.67) --
	( 99.82, 57.67) --
	( 99.37, 57.67) --
	( 98.92, 57.67) --
	( 98.47, 57.67) --
	( 98.02, 57.67) --
	( 97.57, 57.67) --
	( 97.12, 57.67) --
	( 96.68, 57.67) --
	( 96.23, 57.67) --
	( 95.78, 57.67) --
	( 95.33, 57.67) --
	( 94.88, 57.67) --
	( 94.43, 57.67) --
	( 93.98, 57.67) --
	( 93.53, 57.67) --
	( 93.09, 57.67) --
	( 92.64, 57.67) --
	( 92.19, 57.67) --
	( 91.74, 57.67) --
	( 91.29, 57.67) --
	( 90.84, 57.67) --
	( 90.39, 57.67) --
	( 89.95, 57.67) --
	( 89.50, 57.67) --
	( 89.05, 57.67) --
	( 88.60, 57.67) --
	( 88.15, 57.67) --
	( 87.70, 57.67) --
	( 87.25, 57.67) --
	( 86.80, 57.67) --
	( 86.36, 57.67) --
	( 85.91, 57.67) --
	( 85.46, 57.67) --
	( 85.01, 57.67) --
	( 84.56, 57.67) --
	( 84.11, 57.67) --
	( 83.66, 57.67) --
	( 83.21, 57.67) --
	( 82.77, 57.67) --
	( 82.32, 57.67) --
	( 81.87, 57.67) --
	( 81.42, 57.67) --
	( 80.97, 57.67) --
	( 80.52, 57.67) --
	( 80.07, 57.67) --
	( 79.63, 57.67) --
	( 79.18, 57.67) --
	( 78.73, 57.67) --
	( 78.28, 57.67) --
	( 77.83, 57.67) --
	( 77.38, 57.67) --
	( 76.93, 57.67) --
	( 76.48, 57.67) --
	( 76.04, 57.67) --
	( 75.59, 57.67) --
	( 75.14, 57.67) --
	( 74.69, 57.67) --
	( 74.24, 57.67) --
	( 73.79, 57.67) --
	( 73.34, 57.67) --
	( 72.89, 57.67) --
	( 72.45, 57.67) --
	( 72.00, 57.67) --
	( 71.55, 57.67) --
	( 71.10, 57.67) --
	( 70.65, 57.67) --
	( 70.20, 57.67) --
	( 69.75, 57.67) --
	( 69.31, 57.67) --
	( 68.86, 57.67) --
	( 68.41, 57.67) --
	( 67.96, 57.67) --
	( 67.51, 57.67) --
	( 67.06, 57.67) --
	( 66.61, 57.67) --
	( 66.16, 57.67) --
	( 65.72, 57.67) --
	( 65.27, 57.67) --
	( 64.82, 57.67) --
	( 64.37, 57.67) --
	( 63.92, 57.67) --
	( 63.47, 57.67) --
	( 63.02, 57.67) --
	( 62.57, 57.67) --
	( 62.13, 57.67) --
	( 61.68, 57.67) --
	( 61.23, 57.67) --
	( 60.78, 57.67) --
	( 60.33, 57.67) --
	( 59.88, 57.67) --
	( 59.43, 57.67) --
	( 58.99, 57.67) --
	( 58.54, 57.67) --
	( 58.09, 57.67) --
	( 57.64, 57.67) --
	( 57.19, 57.67) --
	( 56.74, 57.67) --
	( 56.29, 57.67) --
	( 55.84, 57.67) --
	( 55.40, 57.67) --
	( 54.95, 57.67) --
	( 54.50, 57.67) --
	( 54.05, 57.67) --
	( 53.60, 57.67) --
	( 53.15, 57.67) --
	( 52.70, 57.67) --
	( 52.25, 57.67) --
	( 51.81, 57.67) --
	( 51.36, 57.67) --
	( 50.91, 57.67) --
	( 50.46, 57.67) --
	( 50.01, 57.67) --
	( 49.56, 57.67) --
	( 49.11, 57.67) --
	( 48.67, 57.67) --
	( 48.22, 57.67) --
	( 47.77, 57.67) --
	( 47.32, 57.67) --
	( 46.87, 57.67) --
	( 46.42, 57.67) --
	( 45.97, 57.67) --
	( 45.52, 57.67) --
	( 45.08, 57.67) --
	( 44.63, 57.67) --
	( 44.18, 57.67) --
	( 43.73, 57.67) --
	( 43.28, 57.67) --
	( 42.83, 57.67) --
	cycle;
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 42.83, 57.70) --
	( 43.28, 57.71) --
	( 43.73, 57.71) --
	( 44.18, 57.71) --
	( 44.63, 57.71) --
	( 45.08, 57.71) --
	( 45.52, 57.71) --
	( 45.97, 57.71) --
	( 46.42, 57.71) --
	( 46.87, 57.72) --
	( 47.32, 57.72) --
	( 47.77, 57.72) --
	( 48.22, 57.73) --
	( 48.67, 57.74) --
	( 49.11, 57.75) --
	( 49.56, 57.76) --
	( 50.01, 57.77) --
	( 50.46, 57.78) --
	( 50.91, 57.78) --
	( 51.36, 57.79) --
	( 51.81, 57.78) --
	( 52.25, 57.78) --
	( 52.70, 57.77) --
	( 53.15, 57.77) --
	( 53.60, 57.76) --
	( 54.05, 57.75) --
	( 54.50, 57.75) --
	( 54.95, 57.75) --
	( 55.40, 57.75) --
	( 55.84, 57.75) --
	( 56.29, 57.76) --
	( 56.74, 57.77) --
	( 57.19, 57.77) --
	( 57.64, 57.78) --
	( 58.09, 57.79) --
	( 58.54, 57.80) --
	( 58.99, 57.81) --
	( 59.43, 57.81) --
	( 59.88, 57.82) --
	( 60.33, 57.83) --
	( 60.78, 57.83) --
	( 61.23, 57.84) --
	( 61.68, 57.84) --
	( 62.13, 57.84) --
	( 62.57, 57.84) --
	( 63.02, 57.85) --
	( 63.47, 57.85) --
	( 63.92, 57.86) --
	( 64.37, 57.87) --
	( 64.82, 57.88) --
	( 65.27, 57.89) --
	( 65.72, 57.90) --
	( 66.16, 57.91) --
	( 66.61, 57.91) --
	( 67.06, 57.91) --
	( 67.51, 57.91) --
	( 67.96, 57.91) --
	( 68.41, 57.90) --
	( 68.86, 57.90) --
	( 69.31, 57.90) --
	( 69.75, 57.90) --
	( 70.20, 57.90) --
	( 70.65, 57.90) --
	( 71.10, 57.90) --
	( 71.55, 57.91) --
	( 72.00, 57.92) --
	( 72.45, 57.94) --
	( 72.89, 57.95) --
	( 73.34, 57.97) --
	( 73.79, 58.00) --
	( 74.24, 58.02) --
	( 74.69, 58.05) --
	( 75.14, 58.07) --
	( 75.59, 58.10) --
	( 76.04, 58.13) --
	( 76.48, 58.16) --
	( 76.93, 58.19) --
	( 77.38, 58.22) --
	( 77.83, 58.24) --
	( 78.28, 58.25) --
	( 78.73, 58.26) --
	( 79.18, 58.27) --
	( 79.63, 58.27) --
	( 80.07, 58.26) --
	( 80.52, 58.26) --
	( 80.97, 58.25) --
	( 81.42, 58.24) --
	( 81.87, 58.23) --
	( 82.32, 58.22) --
	( 82.77, 58.22) --
	( 83.21, 58.22) --
	( 83.66, 58.22) --
	( 84.11, 58.24) --
	( 84.56, 58.25) --
	( 85.01, 58.28) --
	( 85.46, 58.31) --
	( 85.91, 58.35) --
	( 86.36, 58.40) --
	( 86.80, 58.46) --
	( 87.25, 58.52) --
	( 87.70, 58.59) --
	( 88.15, 58.65) --
	( 88.60, 58.71) --
	( 89.05, 58.75) --
	( 89.50, 58.77) --
	( 89.95, 58.78) --
	( 90.39, 58.76) --
	( 90.84, 58.74) --
	( 91.29, 58.71) --
	( 91.74, 58.69) --
	( 92.19, 58.68) --
	( 92.64, 58.68) --
	( 93.09, 58.70) --
	( 93.53, 58.73) --
	( 93.98, 58.78) --
	( 94.43, 58.84) --
	( 94.88, 58.89) --
	( 95.33, 58.95) --
	( 95.78, 59.00) --
	( 96.23, 59.04) --
	( 96.68, 59.09) --
	( 97.12, 59.12) --
	( 97.57, 59.16) --
	( 98.02, 59.20) --
	( 98.47, 59.24) --
	( 98.92, 59.29) --
	( 99.37, 59.33) --
	( 99.82, 59.38) --
	(100.27, 59.42) --
	(100.71, 59.46) --
	(101.16, 59.49) --
	(101.61, 59.53) --
	(102.06, 59.57) --
	(102.51, 59.62) --
	(102.96, 59.68) --
	(103.41, 59.74) --
	(103.85, 59.82) --
	(104.30, 59.90) --
	(104.75, 59.98) --
	(105.20, 60.07) --
	(105.65, 60.16) --
	(106.10, 60.23) --
	(106.55, 60.29) --
	(107.00, 60.33) --
	(107.44, 60.33) --
	(107.89, 60.32) --
	(108.34, 60.27) --
	(108.79, 60.21) --
	(109.24, 60.15) --
	(109.69, 60.09) --
	(110.14, 60.05) --
	(110.59, 60.03) --
	(111.03, 60.04) --
	(111.48, 60.07) --
	(111.93, 60.13) --
	(112.38, 60.21) --
	(112.83, 60.31) --
	(113.28, 60.42) --
	(113.73, 60.54) --
	(114.17, 60.68) --
	(114.62, 60.83) --
	(115.07, 61.03) --
	(115.52, 61.32) --
	(115.97, 61.75) --
	(116.42, 62.41) --
	(116.87, 63.41) --
	(117.32, 64.87) --
	(117.76, 66.87) --
	(118.21, 69.43) --
	(118.66, 72.50) --
	(119.11, 75.89) --
	(119.56, 79.33) --
	(120.01, 82.43) --
	(120.46, 84.82) --
	(120.91, 86.17) --
	(121.35, 86.30) --
	(121.80, 85.21) --
	(122.25, 83.04) --
	(122.70, 80.20) --
	(123.15, 77.10) --
	(123.60, 74.08) --
	(124.05, 71.39) --
	(124.49, 69.17) --
	(124.94, 67.48) --
	(125.39, 66.29) --
	(125.84, 65.51) --
	(126.29, 65.07) --
	(126.74, 64.91) --
	(127.19, 64.99) --
	(127.64, 65.33) --
	(128.08, 65.97) --
	(128.53, 67.02) --
	(128.98, 68.59) --
	(129.43, 70.86) --
	(129.88, 73.86) --
	(130.33, 77.54) --
	(130.78, 81.72) --
	(131.23, 86.09) --
	(131.67, 90.19) --
	(132.12, 93.54) --
	(132.57, 95.71) --
	(133.02, 96.43) --
	(133.47, 95.65) --
	(133.92, 93.57) --
	(134.37, 90.61) --
	(134.81, 87.32) --
	(135.26, 84.28) --
	(135.71, 82.02) --
	(136.16, 80.96) --
	(136.61, 81.39) --
	(137.06, 83.20) --
	(137.51, 86.19) --
	(137.96, 89.97) --
	(138.40, 94.06) --
	(138.85, 97.92) --
	(139.30,101.10) --
	(139.75,103.30) --
	(140.20,104.46) --
	(140.65,104.81) --
	(141.10,104.78) --
	(141.55,104.91) --
	(141.99,105.73) --
	(142.44,107.60) --
	(142.89,110.57) --
	(143.34,114.42) --
	(143.79,118.64) --
	(144.24,122.65) --
	(144.69,126.06) --
	(145.13,128.71) --
	(145.58,130.72) --
	(146.03,132.38) --
	(146.48,134.01) --
	(146.93,135.86) --
	(147.38,137.97) --
	(147.83,140.22) --
	(148.28,142.36) --
	(148.72,144.16) --
	(149.17,145.46) --
	(149.62,146.24) --
	(150.07,146.61) --
	(150.52,146.73) --
	(150.97,146.72) --
	(151.42,146.65) --
	(151.87,146.50) --
	(152.31,146.24) --
	(152.76,145.86) --
	(153.21,145.36) --
	(153.66,144.76) --
	(154.11,144.13) --
	(154.56,143.52) --
	(155.01,143.00) --
	(155.45,142.61) --
	(155.90,142.39) --
	(156.35,142.38) --
	(156.80,142.59) --
	(157.25,142.99) --
	(157.70,143.56) --
	(158.15,144.27) --
	(158.60,145.06) --
	(159.04,145.91) --
	(159.49,146.80) --
	(159.94,147.73) --
	(160.39,148.67) --
	(160.84,149.62) --
	(161.29,150.54) --
	(161.74,151.39) --
	(162.19,152.14) --
	(162.63,152.78) --
	(163.08,153.32) --
	(163.53,153.81) --
	(163.98,154.31) --
	(164.43,154.92) --
	(164.88,155.75) --
	(165.33,156.89) --
	(165.77,158.39) --
	(166.22,160.28) --
	(166.67,162.54) --
	(167.12,165.11) --
	(167.57,167.88) --
	(168.02,170.70) --
	(168.47,173.39) --
	(168.92,175.76) --
	(169.36,177.63) --
	(169.81,178.86) --
	(170.26,179.34) --
	(170.71,179.06) --
	(171.16,178.08) --
	(171.61,176.54) --
	(172.06,174.61) --
	(172.51,172.54) --
	(172.95,170.52) --
	(173.40,168.69) --
	(173.85,167.12) --
	(174.30,165.82) --
	(174.75,164.74) --
	(175.20,163.78) --
	(175.65,162.80) --
	(176.09,161.68) --
	(176.54,160.26) --
	(176.99,158.41) --
	(177.44,156.03) --
	(177.89,153.00) --
	(178.34,149.26) --
	(178.79,144.76) --
	(179.24,139.49) --
	(179.68,133.57) --
	(180.13,127.15) --
	(180.58,120.44) --
	(181.03,113.65) --
	(181.48,107.01) --
	(181.93,100.68) --
	(182.38, 94.80) --
	(182.83, 89.43) --
	(183.27, 84.61) --
	(183.72, 80.31) --
	(184.17, 76.50) --
	(184.62, 73.14) --
	(185.07, 70.18) --
	(185.52, 67.62) --
	(185.97, 65.41) --
	(186.41, 63.58) --
	(186.86, 62.07) --
	(187.31, 60.87) --
	(187.76, 59.93) --
	(188.21, 59.22) --
	(188.66, 58.71) --
	(189.11, 58.34) --
	(189.56, 58.09) --
	(190.00, 57.92) --
	(190.45, 57.82) --
	(190.90, 57.75) --
	(191.35, 57.72) --
	(191.80, 57.69) --
	(192.25, 57.68) --
	(192.70, 57.67) --
	(193.15, 57.67) --
	(193.59, 57.67) --
	(194.04, 57.67) --
	(194.49, 57.67) --
	(194.94, 57.67) --
	(195.39, 57.67) --
	(195.84, 57.67) --
	(196.29, 57.67) --
	(196.73, 57.67) --
	(197.18, 57.67) --
	(197.63, 57.67) --
	(198.08, 57.67) --
	(198.53, 57.67) --
	(198.98, 57.67) --
	(199.43, 57.67) --
	(199.88, 57.67) --
	(200.32, 57.67) --
	(200.77, 57.67) --
	(201.22, 57.67) --
	(201.67, 57.67) --
	(202.12, 57.67) --
	(202.57, 57.67) --
	(203.02, 57.67) --
	(203.47, 57.67) --
	(203.91, 57.67) --
	(204.36, 57.67) --
	(204.81, 57.67) --
	(205.26, 57.67) --
	(205.71, 57.67) --
	(206.16, 57.67) --
	(206.61, 57.67) --
	(207.05, 57.67) --
	(207.50, 57.67) --
	(207.95, 57.67) --
	(208.40, 57.67) --
	(208.85, 57.67) --
	(209.30, 57.67) --
	(209.75, 57.67) --
	(210.20, 57.67) --
	(210.64, 57.67) --
	(211.09, 57.67) --
	(211.54, 57.67) --
	(211.99, 57.67) --
	(212.44, 57.67) --
	(212.89, 57.67) --
	(213.34, 57.67) --
	(213.79, 57.67) --
	(214.23, 57.67) --
	(214.68, 57.67) --
	(215.13, 57.67) --
	(215.58, 57.67) --
	(216.03, 57.67) --
	(216.48, 57.67) --
	(216.93, 57.67) --
	(217.37, 57.67) --
	(217.82, 57.67) --
	(218.27, 57.67) --
	(218.72, 57.67) --
	(219.17, 57.67) --
	(219.62, 57.67) --
	(220.07, 57.67) --
	(220.52, 57.67) --
	(220.96, 57.67) --
	(221.41, 57.67) --
	(221.86, 57.67) --
	(222.31, 57.67) --
	(222.76, 57.67) --
	(223.21, 57.67) --
	(223.66, 57.67) --
	(224.11, 57.67) --
	(224.55, 57.67) --
	(225.00, 57.67) --
	(225.45, 57.67) --
	(225.90, 57.67) --
	(226.35, 57.67) --
	(226.80, 57.67) --
	(227.25, 57.67) --
	(227.69, 57.67) --
	(228.14, 57.67) --
	(228.59, 57.67) --
	(229.04, 57.67) --
	(229.49, 57.67) --
	(229.94, 57.67) --
	(230.39, 57.67) --
	(230.84, 57.67) --
	(231.28, 57.67) --
	(231.73, 57.67) --
	(232.18, 57.67) --
	(232.63, 57.67) --
	(233.08, 57.67) --
	(233.53, 57.67) --
	(233.98, 57.67) --
	(234.43, 57.67) --
	(234.87, 57.67) --
	(235.32, 57.67) --
	(235.77, 57.67) --
	(236.22, 57.67) --
	(236.67, 57.67) --
	(237.12, 57.67) --
	(237.57, 57.67) --
	(238.01, 57.67) --
	(238.46, 57.67) --
	(238.91, 57.67) --
	(239.36, 57.67) --
	(239.81, 57.67) --
	(240.26, 57.67) --
	(240.71, 57.67) --
	(241.16, 57.67) --
	(241.60, 57.67) --
	(242.05, 57.67) --
	(242.50, 57.67) --
	(242.95, 57.67) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67);

\path[] ( 42.83, 57.70) --
	( 43.28, 57.71) --
	( 43.73, 57.71) --
	( 44.18, 57.71) --
	( 44.63, 57.71) --
	( 45.08, 57.71) --
	( 45.52, 57.71) --
	( 45.97, 57.71) --
	( 46.42, 57.71) --
	( 46.87, 57.72) --
	( 47.32, 57.72) --
	( 47.77, 57.73) --
	( 48.22, 57.73) --
	( 48.67, 57.74) --
	( 49.11, 57.75) --
	( 49.56, 57.76) --
	( 50.01, 57.77) --
	( 50.46, 57.77) --
	( 50.91, 57.78) --
	( 51.36, 57.78) --
	( 51.81, 57.78) --
	( 52.25, 57.78) --
	( 52.70, 57.77) --
	( 53.15, 57.77) --
	( 53.60, 57.76) --
	( 54.05, 57.76) --
	( 54.50, 57.75) --
	( 54.95, 57.75) --
	( 55.40, 57.75) --
	( 55.84, 57.76) --
	( 56.29, 57.76) --
	( 56.74, 57.77) --
	( 57.19, 57.77) --
	( 57.64, 57.78) --
	( 58.09, 57.79) --
	( 58.54, 57.80) --
	( 58.99, 57.80) --
	( 59.43, 57.81) --
	( 59.88, 57.82) --
	( 60.33, 57.82) --
	( 60.78, 57.83) --
	( 61.23, 57.83) --
	( 61.68, 57.84) --
	( 62.13, 57.84) --
	( 62.57, 57.84) --
	( 63.02, 57.85) --
	( 63.47, 57.85) --
	( 63.92, 57.86) --
	( 64.37, 57.87) --
	( 64.82, 57.88) --
	( 65.27, 57.89) --
	( 65.72, 57.90) --
	( 66.16, 57.90) --
	( 66.61, 57.91) --
	( 67.06, 57.91) --
	( 67.51, 57.91) --
	( 67.96, 57.91) --
	( 68.41, 57.90) --
	( 68.86, 57.90) --
	( 69.31, 57.90) --
	( 69.75, 57.90) --
	( 70.20, 57.90) --
	( 70.65, 57.90) --
	( 71.10, 57.91) --
	( 71.55, 57.92) --
	( 72.00, 57.93) --
	( 72.45, 57.94) --
	( 72.89, 57.96) --
	( 73.34, 57.98) --
	( 73.79, 58.00) --
	( 74.24, 58.02) --
	( 74.69, 58.05) --
	( 75.14, 58.07) --
	( 75.59, 58.10) --
	( 76.04, 58.13) --
	( 76.48, 58.16) --
	( 76.93, 58.19) --
	( 77.38, 58.21) --
	( 77.83, 58.23) --
	( 78.28, 58.25) --
	( 78.73, 58.26) --
	( 79.18, 58.26) --
	( 79.63, 58.26) --
	( 80.07, 58.26) --
	( 80.52, 58.26) --
	( 80.97, 58.25) --
	( 81.42, 58.24) --
	( 81.87, 58.23) --
	( 82.32, 58.23) --
	( 82.77, 58.22) --
	( 83.21, 58.22) --
	( 83.66, 58.23) --
	( 84.11, 58.24) --
	( 84.56, 58.26) --
	( 85.01, 58.29) --
	( 85.46, 58.32) --
	( 85.91, 58.36) --
	( 86.36, 58.41) --
	( 86.80, 58.47) --
	( 87.25, 58.52) --
	( 87.70, 58.58) --
	( 88.15, 58.64) --
	( 88.60, 58.69) --
	( 89.05, 58.73) --
	( 89.50, 58.75) --
	( 89.95, 58.76) --
	( 90.39, 58.75) --
	( 90.84, 58.74) --
	( 91.29, 58.72) --
	( 91.74, 58.70) --
	( 92.19, 58.69) --
	( 92.64, 58.70) --
	( 93.09, 58.72) --
	( 93.53, 58.75) --
	( 93.98, 58.79) --
	( 94.43, 58.84) --
	( 94.88, 58.89) --
	( 95.33, 58.94) --
	( 95.78, 58.99) --
	( 96.23, 59.04) --
	( 96.68, 59.08) --
	( 97.12, 59.12) --
	( 97.57, 59.16) --
	( 98.02, 59.20) --
	( 98.47, 59.25) --
	( 98.92, 59.29) --
	( 99.37, 59.33) --
	( 99.82, 59.37) --
	(100.27, 59.41) --
	(100.71, 59.45) --
	(101.16, 59.50) --
	(101.61, 59.54) --
	(102.06, 59.58) --
	(102.51, 59.63) --
	(102.96, 59.69) --
	(103.41, 59.75) --
	(103.85, 59.82) --
	(104.30, 59.90) --
	(104.75, 59.99) --
	(105.20, 60.07) --
	(105.65, 60.14) --
	(106.10, 60.21) --
	(106.55, 60.26) --
	(107.00, 60.29) --
	(107.44, 60.30) --
	(107.89, 60.29) --
	(108.34, 60.25) --
	(108.79, 60.21) --
	(109.24, 60.16) --
	(109.69, 60.11) --
	(110.14, 60.07) --
	(110.59, 60.06) --
	(111.03, 60.07) --
	(111.48, 60.10) --
	(111.93, 60.15) --
	(112.38, 60.23) --
	(112.83, 60.32) --
	(113.28, 60.41) --
	(113.73, 60.52) --
	(114.17, 60.62) --
	(114.62, 60.71) --
	(115.07, 60.80) --
	(115.52, 60.86) --
	(115.97, 60.91) --
	(116.42, 60.94) --
	(116.87, 60.96) --
	(117.32, 60.96) --
	(117.76, 60.95) --
	(118.21, 60.94) --
	(118.66, 60.95) --
	(119.11, 60.97) --
	(119.56, 61.01) --
	(120.01, 61.07) --
	(120.46, 61.16) --
	(120.91, 61.26) --
	(121.35, 61.37) --
	(121.80, 61.49) --
	(122.25, 61.60) --
	(122.70, 61.70) --
	(123.15, 61.78) --
	(123.60, 61.86) --
	(124.05, 61.92) --
	(124.49, 61.97) --
	(124.94, 62.02) --
	(125.39, 62.07) --
	(125.84, 62.12) --
	(126.29, 62.18) --
	(126.74, 62.24) --
	(127.19, 62.31) --
	(127.64, 62.38) --
	(128.08, 62.45) --
	(128.53, 62.52) --
	(128.98, 62.58) --
	(129.43, 62.65) --
	(129.88, 62.72) --
	(130.33, 62.79) --
	(130.78, 62.87) --
	(131.23, 62.95) --
	(131.67, 63.04) --
	(132.12, 63.13) --
	(132.57, 63.22) --
	(133.02, 63.31) --
	(133.47, 63.38) --
	(133.92, 63.44) --
	(134.37, 63.48) --
	(134.81, 63.51) --
	(135.26, 63.53) --
	(135.71, 63.55) --
	(136.16, 63.59) --
	(136.61, 63.64) --
	(137.06, 63.72) --
	(137.51, 63.82) --
	(137.96, 63.95) --
	(138.40, 64.09) --
	(138.85, 64.24) --
	(139.30, 64.40) --
	(139.75, 64.56) --
	(140.20, 64.72) --
	(140.65, 64.88) --
	(141.10, 65.03) --
	(141.55, 65.19) --
	(141.99, 65.36) --
	(142.44, 65.56) --
	(142.89, 65.80) --
	(143.34, 66.12) --
	(143.79, 66.54) --
	(144.24, 67.13) --
	(144.69, 67.91) --
	(145.13, 68.93) --
	(145.58, 70.17) --
	(146.03, 71.63) --
	(146.48, 73.22) --
	(146.93, 74.86) --
	(147.38, 76.42) --
	(147.83, 77.77) --
	(148.28, 78.79) --
	(148.72, 79.40) --
	(149.17, 79.57) --
	(149.62, 79.33) --
	(150.07, 78.77) --
	(150.52, 77.99) --
	(150.97, 77.11) --
	(151.42, 76.28) --
	(151.87, 75.57) --
	(152.31, 75.03) --
	(152.76, 74.67) --
	(153.21, 74.51) --
	(153.66, 74.52) --
	(154.11, 74.68) --
	(154.56, 75.00) --
	(155.01, 75.48) --
	(155.45, 76.14) --
	(155.90, 77.03) --
	(156.35, 78.18) --
	(156.80, 79.65) --
	(157.25, 81.43) --
	(157.70, 83.53) --
	(158.15, 85.86) --
	(158.60, 88.28) --
	(159.04, 90.62) --
	(159.49, 92.70) --
	(159.94, 94.36) --
	(160.39, 95.47) --
	(160.84, 96.01) --
	(161.29, 96.02) --
	(161.74, 95.62) --
	(162.19, 94.99) --
	(162.63, 94.32) --
	(163.08, 93.84) --
	(163.53, 93.70) --
	(163.98, 94.03) --
	(164.43, 94.90) --
	(164.88, 96.25) --
	(165.33, 97.99) --
	(165.77, 99.96) --
	(166.22,102.01) --
	(166.67,104.00) --
	(167.12,105.84) --
	(167.57,107.52) --
	(168.02,109.08) --
	(168.47,110.65) --
	(168.92,112.37) --
	(169.36,114.38) --
	(169.81,116.76) --
	(170.26,119.52) --
	(170.71,122.57) --
	(171.16,125.76) --
	(171.61,128.87) --
	(172.06,131.72) --
	(172.51,134.22) --
	(172.95,136.36) --
	(173.40,138.16) --
	(173.85,139.72) --
	(174.30,141.10) --
	(174.75,142.33) --
	(175.20,143.42) --
	(175.65,144.33) --
	(176.09,145.02) --
	(176.54,145.44) --
	(176.99,145.63) --
	(177.44,145.61) --
	(177.89,145.48) --
	(178.34,145.30) --
	(178.79,145.15) --
	(179.24,145.07) --
	(179.68,145.04) --
	(180.13,145.08) --
	(180.58,145.16) --
	(181.03,145.27) --
	(181.48,145.40) --
	(181.93,145.54) --
	(182.38,145.69) --
	(182.83,145.85) --
	(183.27,146.02) --
	(183.72,146.20) --
	(184.17,146.41) --
	(184.62,146.64) --
	(185.07,146.91) --
	(185.52,147.23) --
	(185.97,147.60) --
	(186.41,148.03) --
	(186.86,148.51) --
	(187.31,149.05) --
	(187.76,149.62) --
	(188.21,150.21) --
	(188.66,150.81) --
	(189.11,151.41) --
	(189.56,151.99) --
	(190.00,152.57) --
	(190.45,153.13) --
	(190.90,153.68) --
	(191.35,154.23) --
	(191.80,154.80) --
	(192.25,155.41) --
	(192.70,156.06) --
	(193.15,156.76) --
	(193.59,157.50) --
	(194.04,158.24) --
	(194.49,158.94) --
	(194.94,159.54) --
	(195.39,159.95) --
	(195.84,160.10) --
	(196.29,159.92) --
	(196.73,159.37) --
	(197.18,158.45) --
	(197.63,157.17) --
	(198.08,155.62) --
	(198.53,153.90) --
	(198.98,152.15) --
	(199.43,150.47) --
	(199.88,148.96) --
	(200.32,147.67) --
	(200.77,146.61) --
	(201.22,145.75) --
	(201.67,145.01) --
	(202.12,144.31) --
	(202.57,143.54) --
	(203.02,142.61) --
	(203.47,141.43) --
	(203.91,139.92) --
	(204.36,138.00) --
	(204.81,135.62) --
	(205.26,132.72) --
	(205.71,129.32) --
	(206.16,125.43) --
	(206.61,121.08) --
	(207.05,116.37) --
	(207.50,111.40) --
	(207.95,106.30) --
	(208.40,101.20) --
	(208.85, 96.24) --
	(209.30, 91.51) --
	(209.75, 87.10) --
	(210.20, 83.04) --
	(210.64, 79.35) --
	(211.09, 76.03) --
	(211.54, 73.07) --
	(211.99, 70.44) --
	(212.44, 68.11) --
	(212.89, 66.07) --
	(213.34, 64.30) --
	(213.79, 62.80) --
	(214.23, 61.55) --
	(214.68, 60.54) --
	(215.13, 59.73) --
	(215.58, 59.12) --
	(216.03, 58.65) --
	(216.48, 58.32) --
	(216.93, 58.09) --
	(217.37, 57.93) --
	(217.82, 57.82) --
	(218.27, 57.76) --
	(218.72, 57.72) --
	(219.17, 57.70) --
	(219.62, 57.68) --
	(220.07, 57.68) --
	(220.52, 57.67) --
	(220.96, 57.67) --
	(221.41, 57.67) --
	(221.86, 57.67) --
	(222.31, 57.67) --
	(222.76, 57.67) --
	(223.21, 57.67) --
	(223.66, 57.67) --
	(224.11, 57.67) --
	(224.55, 57.67) --
	(225.00, 57.67) --
	(225.45, 57.67) --
	(225.90, 57.67) --
	(226.35, 57.67) --
	(226.80, 57.67) --
	(227.25, 57.67) --
	(227.69, 57.67) --
	(228.14, 57.67) --
	(228.59, 57.67) --
	(229.04, 57.67) --
	(229.49, 57.67) --
	(229.94, 57.67) --
	(230.39, 57.67) --
	(230.84, 57.67) --
	(231.28, 57.67) --
	(231.73, 57.67) --
	(232.18, 57.67) --
	(232.63, 57.67) --
	(233.08, 57.67) --
	(233.53, 57.67) --
	(233.98, 57.67) --
	(234.43, 57.67) --
	(234.87, 57.67) --
	(235.32, 57.67) --
	(235.77, 57.67) --
	(236.22, 57.67) --
	(236.67, 57.67) --
	(237.12, 57.67) --
	(237.57, 57.67) --
	(238.01, 57.67) --
	(238.46, 57.67) --
	(238.91, 57.67) --
	(239.36, 57.67) --
	(239.81, 57.67) --
	(240.26, 57.67) --
	(240.71, 57.67) --
	(241.16, 57.67) --
	(241.60, 57.67) --
	(242.05, 57.67) --
	(242.50, 57.67) --
	(242.95, 57.67) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67) --
	(272.12, 57.67) --
	(271.67, 57.67) --
	(271.22, 57.67) --
	(270.77, 57.67) --
	(270.32, 57.67) --
	(269.87, 57.67) --
	(269.42, 57.67) --
	(268.97, 57.67) --
	(268.53, 57.67) --
	(268.08, 57.67) --
	(267.63, 57.67) --
	(267.18, 57.67) --
	(266.73, 57.67) --
	(266.28, 57.67) --
	(265.83, 57.67) --
	(265.39, 57.67) --
	(264.94, 57.67) --
	(264.49, 57.67) --
	(264.04, 57.67) --
	(263.59, 57.67) --
	(263.14, 57.67) --
	(262.69, 57.67) --
	(262.24, 57.67) --
	(261.80, 57.67) --
	(261.35, 57.67) --
	(260.90, 57.67) --
	(260.45, 57.67) --
	(260.00, 57.67) --
	(259.55, 57.67) --
	(259.10, 57.67) --
	(258.65, 57.67) --
	(258.21, 57.67) --
	(257.76, 57.67) --
	(257.31, 57.67) --
	(256.86, 57.67) --
	(256.41, 57.67) --
	(255.96, 57.67) --
	(255.51, 57.67) --
	(255.07, 57.67) --
	(254.62, 57.67) --
	(254.17, 57.67) --
	(253.72, 57.67) --
	(253.27, 57.67) --
	(252.82, 57.67) --
	(252.37, 57.67) --
	(251.92, 57.67) --
	(251.48, 57.67) --
	(251.03, 57.67) --
	(250.58, 57.67) --
	(250.13, 57.67) --
	(249.68, 57.67) --
	(249.23, 57.67) --
	(248.78, 57.67) --
	(248.33, 57.67) --
	(247.89, 57.67) --
	(247.44, 57.67) --
	(246.99, 57.67) --
	(246.54, 57.67) --
	(246.09, 57.67) --
	(245.64, 57.67) --
	(245.19, 57.67) --
	(244.75, 57.67) --
	(244.30, 57.67) --
	(243.85, 57.67) --
	(243.40, 57.67) --
	(242.95, 57.67) --
	(242.50, 57.67) --
	(242.05, 57.67) --
	(241.60, 57.67) --
	(241.16, 57.67) --
	(240.71, 57.67) --
	(240.26, 57.67) --
	(239.81, 57.67) --
	(239.36, 57.67) --
	(238.91, 57.67) --
	(238.46, 57.67) --
	(238.01, 57.67) --
	(237.57, 57.67) --
	(237.12, 57.67) --
	(236.67, 57.67) --
	(236.22, 57.67) --
	(235.77, 57.67) --
	(235.32, 57.67) --
	(234.87, 57.67) --
	(234.43, 57.67) --
	(233.98, 57.67) --
	(233.53, 57.67) --
	(233.08, 57.67) --
	(232.63, 57.67) --
	(232.18, 57.67) --
	(231.73, 57.67) --
	(231.28, 57.67) --
	(230.84, 57.67) --
	(230.39, 57.67) --
	(229.94, 57.67) --
	(229.49, 57.67) --
	(229.04, 57.67) --
	(228.59, 57.67) --
	(228.14, 57.67) --
	(227.69, 57.67) --
	(227.25, 57.67) --
	(226.80, 57.67) --
	(226.35, 57.67) --
	(225.90, 57.67) --
	(225.45, 57.67) --
	(225.00, 57.67) --
	(224.55, 57.67) --
	(224.11, 57.67) --
	(223.66, 57.67) --
	(223.21, 57.67) --
	(222.76, 57.67) --
	(222.31, 57.67) --
	(221.86, 57.67) --
	(221.41, 57.67) --
	(220.96, 57.67) --
	(220.52, 57.67) --
	(220.07, 57.67) --
	(219.62, 57.67) --
	(219.17, 57.67) --
	(218.72, 57.67) --
	(218.27, 57.67) --
	(217.82, 57.67) --
	(217.37, 57.67) --
	(216.93, 57.67) --
	(216.48, 57.67) --
	(216.03, 57.67) --
	(215.58, 57.67) --
	(215.13, 57.67) --
	(214.68, 57.67) --
	(214.23, 57.67) --
	(213.79, 57.67) --
	(213.34, 57.67) --
	(212.89, 57.67) --
	(212.44, 57.67) --
	(211.99, 57.67) --
	(211.54, 57.67) --
	(211.09, 57.67) --
	(210.64, 57.67) --
	(210.20, 57.67) --
	(209.75, 57.67) --
	(209.30, 57.67) --
	(208.85, 57.67) --
	(208.40, 57.67) --
	(207.95, 57.67) --
	(207.50, 57.67) --
	(207.05, 57.67) --
	(206.61, 57.67) --
	(206.16, 57.67) --
	(205.71, 57.67) --
	(205.26, 57.67) --
	(204.81, 57.67) --
	(204.36, 57.67) --
	(203.91, 57.67) --
	(203.47, 57.67) --
	(203.02, 57.67) --
	(202.57, 57.67) --
	(202.12, 57.67) --
	(201.67, 57.67) --
	(201.22, 57.67) --
	(200.77, 57.67) --
	(200.32, 57.67) --
	(199.88, 57.67) --
	(199.43, 57.67) --
	(198.98, 57.67) --
	(198.53, 57.67) --
	(198.08, 57.67) --
	(197.63, 57.67) --
	(197.18, 57.67) --
	(196.73, 57.67) --
	(196.29, 57.67) --
	(195.84, 57.67) --
	(195.39, 57.67) --
	(194.94, 57.67) --
	(194.49, 57.67) --
	(194.04, 57.67) --
	(193.59, 57.67) --
	(193.15, 57.67) --
	(192.70, 57.67) --
	(192.25, 57.67) --
	(191.80, 57.67) --
	(191.35, 57.67) --
	(190.90, 57.67) --
	(190.45, 57.67) --
	(190.00, 57.67) --
	(189.56, 57.67) --
	(189.11, 57.67) --
	(188.66, 57.67) --
	(188.21, 57.67) --
	(187.76, 57.67) --
	(187.31, 57.67) --
	(186.86, 57.67) --
	(186.41, 57.67) --
	(185.97, 57.67) --
	(185.52, 57.67) --
	(185.07, 57.67) --
	(184.62, 57.67) --
	(184.17, 57.67) --
	(183.72, 57.67) --
	(183.27, 57.67) --
	(182.83, 57.67) --
	(182.38, 57.67) --
	(181.93, 57.67) --
	(181.48, 57.67) --
	(181.03, 57.67) --
	(180.58, 57.67) --
	(180.13, 57.67) --
	(179.68, 57.67) --
	(179.24, 57.67) --
	(178.79, 57.67) --
	(178.34, 57.67) --
	(177.89, 57.67) --
	(177.44, 57.67) --
	(176.99, 57.67) --
	(176.54, 57.67) --
	(176.09, 57.67) --
	(175.65, 57.67) --
	(175.20, 57.67) --
	(174.75, 57.67) --
	(174.30, 57.67) --
	(173.85, 57.67) --
	(173.40, 57.67) --
	(172.95, 57.67) --
	(172.51, 57.67) --
	(172.06, 57.67) --
	(171.61, 57.67) --
	(171.16, 57.67) --
	(170.71, 57.67) --
	(170.26, 57.67) --
	(169.81, 57.67) --
	(169.36, 57.67) --
	(168.92, 57.67) --
	(168.47, 57.67) --
	(168.02, 57.67) --
	(167.57, 57.67) --
	(167.12, 57.67) --
	(166.67, 57.67) --
	(166.22, 57.67) --
	(165.77, 57.67) --
	(165.33, 57.67) --
	(164.88, 57.67) --
	(164.43, 57.67) --
	(163.98, 57.67) --
	(163.53, 57.67) --
	(163.08, 57.67) --
	(162.63, 57.67) --
	(162.19, 57.67) --
	(161.74, 57.67) --
	(161.29, 57.67) --
	(160.84, 57.67) --
	(160.39, 57.67) --
	(159.94, 57.67) --
	(159.49, 57.67) --
	(159.04, 57.67) --
	(158.60, 57.67) --
	(158.15, 57.67) --
	(157.70, 57.67) --
	(157.25, 57.67) --
	(156.80, 57.67) --
	(156.35, 57.67) --
	(155.90, 57.67) --
	(155.45, 57.67) --
	(155.01, 57.67) --
	(154.56, 57.67) --
	(154.11, 57.67) --
	(153.66, 57.67) --
	(153.21, 57.67) --
	(152.76, 57.67) --
	(152.31, 57.67) --
	(151.87, 57.67) --
	(151.42, 57.67) --
	(150.97, 57.67) --
	(150.52, 57.67) --
	(150.07, 57.67) --
	(149.62, 57.67) --
	(149.17, 57.67) --
	(148.72, 57.67) --
	(148.28, 57.67) --
	(147.83, 57.67) --
	(147.38, 57.67) --
	(146.93, 57.67) --
	(146.48, 57.67) --
	(146.03, 57.67) --
	(145.58, 57.67) --
	(145.13, 57.67) --
	(144.69, 57.67) --
	(144.24, 57.67) --
	(143.79, 57.67) --
	(143.34, 57.67) --
	(142.89, 57.67) --
	(142.44, 57.67) --
	(141.99, 57.67) --
	(141.55, 57.67) --
	(141.10, 57.67) --
	(140.65, 57.67) --
	(140.20, 57.67) --
	(139.75, 57.67) --
	(139.30, 57.67) --
	(138.85, 57.67) --
	(138.40, 57.67) --
	(137.96, 57.67) --
	(137.51, 57.67) --
	(137.06, 57.67) --
	(136.61, 57.67) --
	(136.16, 57.67) --
	(135.71, 57.67) --
	(135.26, 57.67) --
	(134.81, 57.67) --
	(134.37, 57.67) --
	(133.92, 57.67) --
	(133.47, 57.67) --
	(133.02, 57.67) --
	(132.57, 57.67) --
	(132.12, 57.67) --
	(131.67, 57.67) --
	(131.23, 57.67) --
	(130.78, 57.67) --
	(130.33, 57.67) --
	(129.88, 57.67) --
	(129.43, 57.67) --
	(128.98, 57.67) --
	(128.53, 57.67) --
	(128.08, 57.67) --
	(127.64, 57.67) --
	(127.19, 57.67) --
	(126.74, 57.67) --
	(126.29, 57.67) --
	(125.84, 57.67) --
	(125.39, 57.67) --
	(124.94, 57.67) --
	(124.49, 57.67) --
	(124.05, 57.67) --
	(123.60, 57.67) --
	(123.15, 57.67) --
	(122.70, 57.67) --
	(122.25, 57.67) --
	(121.80, 57.67) --
	(121.35, 57.67) --
	(120.91, 57.67) --
	(120.46, 57.67) --
	(120.01, 57.67) --
	(119.56, 57.67) --
	(119.11, 57.67) --
	(118.66, 57.67) --
	(118.21, 57.67) --
	(117.76, 57.67) --
	(117.32, 57.67) --
	(116.87, 57.67) --
	(116.42, 57.67) --
	(115.97, 57.67) --
	(115.52, 57.67) --
	(115.07, 57.67) --
	(114.62, 57.67) --
	(114.17, 57.67) --
	(113.73, 57.67) --
	(113.28, 57.67) --
	(112.83, 57.67) --
	(112.38, 57.67) --
	(111.93, 57.67) --
	(111.48, 57.67) --
	(111.03, 57.67) --
	(110.59, 57.67) --
	(110.14, 57.67) --
	(109.69, 57.67) --
	(109.24, 57.67) --
	(108.79, 57.67) --
	(108.34, 57.67) --
	(107.89, 57.67) --
	(107.44, 57.67) --
	(107.00, 57.67) --
	(106.55, 57.67) --
	(106.10, 57.67) --
	(105.65, 57.67) --
	(105.20, 57.67) --
	(104.75, 57.67) --
	(104.30, 57.67) --
	(103.85, 57.67) --
	(103.41, 57.67) --
	(102.96, 57.67) --
	(102.51, 57.67) --
	(102.06, 57.67) --
	(101.61, 57.67) --
	(101.16, 57.67) --
	(100.71, 57.67) --
	(100.27, 57.67) --
	( 99.82, 57.67) --
	( 99.37, 57.67) --
	( 98.92, 57.67) --
	( 98.47, 57.67) --
	( 98.02, 57.67) --
	( 97.57, 57.67) --
	( 97.12, 57.67) --
	( 96.68, 57.67) --
	( 96.23, 57.67) --
	( 95.78, 57.67) --
	( 95.33, 57.67) --
	( 94.88, 57.67) --
	( 94.43, 57.67) --
	( 93.98, 57.67) --
	( 93.53, 57.67) --
	( 93.09, 57.67) --
	( 92.64, 57.67) --
	( 92.19, 57.67) --
	( 91.74, 57.67) --
	( 91.29, 57.67) --
	( 90.84, 57.67) --
	( 90.39, 57.67) --
	( 89.95, 57.67) --
	( 89.50, 57.67) --
	( 89.05, 57.67) --
	( 88.60, 57.67) --
	( 88.15, 57.67) --
	( 87.70, 57.67) --
	( 87.25, 57.67) --
	( 86.80, 57.67) --
	( 86.36, 57.67) --
	( 85.91, 57.67) --
	( 85.46, 57.67) --
	( 85.01, 57.67) --
	( 84.56, 57.67) --
	( 84.11, 57.67) --
	( 83.66, 57.67) --
	( 83.21, 57.67) --
	( 82.77, 57.67) --
	( 82.32, 57.67) --
	( 81.87, 57.67) --
	( 81.42, 57.67) --
	( 80.97, 57.67) --
	( 80.52, 57.67) --
	( 80.07, 57.67) --
	( 79.63, 57.67) --
	( 79.18, 57.67) --
	( 78.73, 57.67) --
	( 78.28, 57.67) --
	( 77.83, 57.67) --
	( 77.38, 57.67) --
	( 76.93, 57.67) --
	( 76.48, 57.67) --
	( 76.04, 57.67) --
	( 75.59, 57.67) --
	( 75.14, 57.67) --
	( 74.69, 57.67) --
	( 74.24, 57.67) --
	( 73.79, 57.67) --
	( 73.34, 57.67) --
	( 72.89, 57.67) --
	( 72.45, 57.67) --
	( 72.00, 57.67) --
	( 71.55, 57.67) --
	( 71.10, 57.67) --
	( 70.65, 57.67) --
	( 70.20, 57.67) --
	( 69.75, 57.67) --
	( 69.31, 57.67) --
	( 68.86, 57.67) --
	( 68.41, 57.67) --
	( 67.96, 57.67) --
	( 67.51, 57.67) --
	( 67.06, 57.67) --
	( 66.61, 57.67) --
	( 66.16, 57.67) --
	( 65.72, 57.67) --
	( 65.27, 57.67) --
	( 64.82, 57.67) --
	( 64.37, 57.67) --
	( 63.92, 57.67) --
	( 63.47, 57.67) --
	( 63.02, 57.67) --
	( 62.57, 57.67) --
	( 62.13, 57.67) --
	( 61.68, 57.67) --
	( 61.23, 57.67) --
	( 60.78, 57.67) --
	( 60.33, 57.67) --
	( 59.88, 57.67) --
	( 59.43, 57.67) --
	( 58.99, 57.67) --
	( 58.54, 57.67) --
	( 58.09, 57.67) --
	( 57.64, 57.67) --
	( 57.19, 57.67) --
	( 56.74, 57.67) --
	( 56.29, 57.67) --
	( 55.84, 57.67) --
	( 55.40, 57.67) --
	( 54.95, 57.67) --
	( 54.50, 57.67) --
	( 54.05, 57.67) --
	( 53.60, 57.67) --
	( 53.15, 57.67) --
	( 52.70, 57.67) --
	( 52.25, 57.67) --
	( 51.81, 57.67) --
	( 51.36, 57.67) --
	( 50.91, 57.67) --
	( 50.46, 57.67) --
	( 50.01, 57.67) --
	( 49.56, 57.67) --
	( 49.11, 57.67) --
	( 48.67, 57.67) --
	( 48.22, 57.67) --
	( 47.77, 57.67) --
	( 47.32, 57.67) --
	( 46.87, 57.67) --
	( 46.42, 57.67) --
	( 45.97, 57.67) --
	( 45.52, 57.67) --
	( 45.08, 57.67) --
	( 44.63, 57.67) --
	( 44.18, 57.67) --
	( 43.73, 57.67) --
	( 43.28, 57.67) --
	( 42.83, 57.67) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round,line cap=round] ( 42.83, 57.70) --
	( 43.28, 57.71) --
	( 43.73, 57.71) --
	( 44.18, 57.71) --
	( 44.63, 57.71) --
	( 45.08, 57.71) --
	( 45.52, 57.71) --
	( 45.97, 57.71) --
	( 46.42, 57.71) --
	( 46.87, 57.72) --
	( 47.32, 57.72) --
	( 47.77, 57.73) --
	( 48.22, 57.73) --
	( 48.67, 57.74) --
	( 49.11, 57.75) --
	( 49.56, 57.76) --
	( 50.01, 57.77) --
	( 50.46, 57.77) --
	( 50.91, 57.78) --
	( 51.36, 57.78) --
	( 51.81, 57.78) --
	( 52.25, 57.78) --
	( 52.70, 57.77) --
	( 53.15, 57.77) --
	( 53.60, 57.76) --
	( 54.05, 57.76) --
	( 54.50, 57.75) --
	( 54.95, 57.75) --
	( 55.40, 57.75) --
	( 55.84, 57.76) --
	( 56.29, 57.76) --
	( 56.74, 57.77) --
	( 57.19, 57.77) --
	( 57.64, 57.78) --
	( 58.09, 57.79) --
	( 58.54, 57.80) --
	( 58.99, 57.80) --
	( 59.43, 57.81) --
	( 59.88, 57.82) --
	( 60.33, 57.82) --
	( 60.78, 57.83) --
	( 61.23, 57.83) --
	( 61.68, 57.84) --
	( 62.13, 57.84) --
	( 62.57, 57.84) --
	( 63.02, 57.85) --
	( 63.47, 57.85) --
	( 63.92, 57.86) --
	( 64.37, 57.87) --
	( 64.82, 57.88) --
	( 65.27, 57.89) --
	( 65.72, 57.90) --
	( 66.16, 57.90) --
	( 66.61, 57.91) --
	( 67.06, 57.91) --
	( 67.51, 57.91) --
	( 67.96, 57.91) --
	( 68.41, 57.90) --
	( 68.86, 57.90) --
	( 69.31, 57.90) --
	( 69.75, 57.90) --
	( 70.20, 57.90) --
	( 70.65, 57.90) --
	( 71.10, 57.91) --
	( 71.55, 57.92) --
	( 72.00, 57.93) --
	( 72.45, 57.94) --
	( 72.89, 57.96) --
	( 73.34, 57.98) --
	( 73.79, 58.00) --
	( 74.24, 58.02) --
	( 74.69, 58.05) --
	( 75.14, 58.07) --
	( 75.59, 58.10) --
	( 76.04, 58.13) --
	( 76.48, 58.16) --
	( 76.93, 58.19) --
	( 77.38, 58.21) --
	( 77.83, 58.23) --
	( 78.28, 58.25) --
	( 78.73, 58.26) --
	( 79.18, 58.26) --
	( 79.63, 58.26) --
	( 80.07, 58.26) --
	( 80.52, 58.26) --
	( 80.97, 58.25) --
	( 81.42, 58.24) --
	( 81.87, 58.23) --
	( 82.32, 58.23) --
	( 82.77, 58.22) --
	( 83.21, 58.22) --
	( 83.66, 58.23) --
	( 84.11, 58.24) --
	( 84.56, 58.26) --
	( 85.01, 58.29) --
	( 85.46, 58.32) --
	( 85.91, 58.36) --
	( 86.36, 58.41) --
	( 86.80, 58.47) --
	( 87.25, 58.52) --
	( 87.70, 58.58) --
	( 88.15, 58.64) --
	( 88.60, 58.69) --
	( 89.05, 58.73) --
	( 89.50, 58.75) --
	( 89.95, 58.76) --
	( 90.39, 58.75) --
	( 90.84, 58.74) --
	( 91.29, 58.72) --
	( 91.74, 58.70) --
	( 92.19, 58.69) --
	( 92.64, 58.70) --
	( 93.09, 58.72) --
	( 93.53, 58.75) --
	( 93.98, 58.79) --
	( 94.43, 58.84) --
	( 94.88, 58.89) --
	( 95.33, 58.94) --
	( 95.78, 58.99) --
	( 96.23, 59.04) --
	( 96.68, 59.08) --
	( 97.12, 59.12) --
	( 97.57, 59.16) --
	( 98.02, 59.20) --
	( 98.47, 59.25) --
	( 98.92, 59.29) --
	( 99.37, 59.33) --
	( 99.82, 59.37) --
	(100.27, 59.41) --
	(100.71, 59.45) --
	(101.16, 59.50) --
	(101.61, 59.54) --
	(102.06, 59.58) --
	(102.51, 59.63) --
	(102.96, 59.69) --
	(103.41, 59.75) --
	(103.85, 59.82) --
	(104.30, 59.90) --
	(104.75, 59.99) --
	(105.20, 60.07) --
	(105.65, 60.14) --
	(106.10, 60.21) --
	(106.55, 60.26) --
	(107.00, 60.29) --
	(107.44, 60.30) --
	(107.89, 60.29) --
	(108.34, 60.25) --
	(108.79, 60.21) --
	(109.24, 60.16) --
	(109.69, 60.11) --
	(110.14, 60.07) --
	(110.59, 60.06) --
	(111.03, 60.07) --
	(111.48, 60.10) --
	(111.93, 60.15) --
	(112.38, 60.23) --
	(112.83, 60.32) --
	(113.28, 60.41) --
	(113.73, 60.52) --
	(114.17, 60.62) --
	(114.62, 60.71) --
	(115.07, 60.80) --
	(115.52, 60.86) --
	(115.97, 60.91) --
	(116.42, 60.94) --
	(116.87, 60.96) --
	(117.32, 60.96) --
	(117.76, 60.95) --
	(118.21, 60.94) --
	(118.66, 60.95) --
	(119.11, 60.97) --
	(119.56, 61.01) --
	(120.01, 61.07) --
	(120.46, 61.16) --
	(120.91, 61.26) --
	(121.35, 61.37) --
	(121.80, 61.49) --
	(122.25, 61.60) --
	(122.70, 61.70) --
	(123.15, 61.78) --
	(123.60, 61.86) --
	(124.05, 61.92) --
	(124.49, 61.97) --
	(124.94, 62.02) --
	(125.39, 62.07) --
	(125.84, 62.12) --
	(126.29, 62.18) --
	(126.74, 62.24) --
	(127.19, 62.31) --
	(127.64, 62.38) --
	(128.08, 62.45) --
	(128.53, 62.52) --
	(128.98, 62.58) --
	(129.43, 62.65) --
	(129.88, 62.72) --
	(130.33, 62.79) --
	(130.78, 62.87) --
	(131.23, 62.95) --
	(131.67, 63.04) --
	(132.12, 63.13) --
	(132.57, 63.22) --
	(133.02, 63.31) --
	(133.47, 63.38) --
	(133.92, 63.44) --
	(134.37, 63.48) --
	(134.81, 63.51) --
	(135.26, 63.53) --
	(135.71, 63.55) --
	(136.16, 63.59) --
	(136.61, 63.64) --
	(137.06, 63.72) --
	(137.51, 63.82) --
	(137.96, 63.95) --
	(138.40, 64.09) --
	(138.85, 64.24) --
	(139.30, 64.40) --
	(139.75, 64.56) --
	(140.20, 64.72) --
	(140.65, 64.88) --
	(141.10, 65.03) --
	(141.55, 65.19) --
	(141.99, 65.36) --
	(142.44, 65.56) --
	(142.89, 65.80) --
	(143.34, 66.12) --
	(143.79, 66.54) --
	(144.24, 67.13) --
	(144.69, 67.91) --
	(145.13, 68.93) --
	(145.58, 70.17) --
	(146.03, 71.63) --
	(146.48, 73.22) --
	(146.93, 74.86) --
	(147.38, 76.42) --
	(147.83, 77.77) --
	(148.28, 78.79) --
	(148.72, 79.40) --
	(149.17, 79.57) --
	(149.62, 79.33) --
	(150.07, 78.77) --
	(150.52, 77.99) --
	(150.97, 77.11) --
	(151.42, 76.28) --
	(151.87, 75.57) --
	(152.31, 75.03) --
	(152.76, 74.67) --
	(153.21, 74.51) --
	(153.66, 74.52) --
	(154.11, 74.68) --
	(154.56, 75.00) --
	(155.01, 75.48) --
	(155.45, 76.14) --
	(155.90, 77.03) --
	(156.35, 78.18) --
	(156.80, 79.65) --
	(157.25, 81.43) --
	(157.70, 83.53) --
	(158.15, 85.86) --
	(158.60, 88.28) --
	(159.04, 90.62) --
	(159.49, 92.70) --
	(159.94, 94.36) --
	(160.39, 95.47) --
	(160.84, 96.01) --
	(161.29, 96.02) --
	(161.74, 95.62) --
	(162.19, 94.99) --
	(162.63, 94.32) --
	(163.08, 93.84) --
	(163.53, 93.70) --
	(163.98, 94.03) --
	(164.43, 94.90) --
	(164.88, 96.25) --
	(165.33, 97.99) --
	(165.77, 99.96) --
	(166.22,102.01) --
	(166.67,104.00) --
	(167.12,105.84) --
	(167.57,107.52) --
	(168.02,109.08) --
	(168.47,110.65) --
	(168.92,112.37) --
	(169.36,114.38) --
	(169.81,116.76) --
	(170.26,119.52) --
	(170.71,122.57) --
	(171.16,125.76) --
	(171.61,128.87) --
	(172.06,131.72) --
	(172.51,134.22) --
	(172.95,136.36) --
	(173.40,138.16) --
	(173.85,139.72) --
	(174.30,141.10) --
	(174.75,142.33) --
	(175.20,143.42) --
	(175.65,144.33) --
	(176.09,145.02) --
	(176.54,145.44) --
	(176.99,145.63) --
	(177.44,145.61) --
	(177.89,145.48) --
	(178.34,145.30) --
	(178.79,145.15) --
	(179.24,145.07) --
	(179.68,145.04) --
	(180.13,145.08) --
	(180.58,145.16) --
	(181.03,145.27) --
	(181.48,145.40) --
	(181.93,145.54) --
	(182.38,145.69) --
	(182.83,145.85) --
	(183.27,146.02) --
	(183.72,146.20) --
	(184.17,146.41) --
	(184.62,146.64) --
	(185.07,146.91) --
	(185.52,147.23) --
	(185.97,147.60) --
	(186.41,148.03) --
	(186.86,148.51) --
	(187.31,149.05) --
	(187.76,149.62) --
	(188.21,150.21) --
	(188.66,150.81) --
	(189.11,151.41) --
	(189.56,151.99) --
	(190.00,152.57) --
	(190.45,153.13) --
	(190.90,153.68) --
	(191.35,154.23) --
	(191.80,154.80) --
	(192.25,155.41) --
	(192.70,156.06) --
	(193.15,156.76) --
	(193.59,157.50) --
	(194.04,158.24) --
	(194.49,158.94) --
	(194.94,159.54) --
	(195.39,159.95) --
	(195.84,160.10) --
	(196.29,159.92) --
	(196.73,159.37) --
	(197.18,158.45) --
	(197.63,157.17) --
	(198.08,155.62) --
	(198.53,153.90) --
	(198.98,152.15) --
	(199.43,150.47) --
	(199.88,148.96) --
	(200.32,147.67) --
	(200.77,146.61) --
	(201.22,145.75) --
	(201.67,145.01) --
	(202.12,144.31) --
	(202.57,143.54) --
	(203.02,142.61) --
	(203.47,141.43) --
	(203.91,139.92) --
	(204.36,138.00) --
	(204.81,135.62) --
	(205.26,132.72) --
	(205.71,129.32) --
	(206.16,125.43) --
	(206.61,121.08) --
	(207.05,116.37) --
	(207.50,111.40) --
	(207.95,106.30) --
	(208.40,101.20) --
	(208.85, 96.24) --
	(209.30, 91.51) --
	(209.75, 87.10) --
	(210.20, 83.04) --
	(210.64, 79.35) --
	(211.09, 76.03) --
	(211.54, 73.07) --
	(211.99, 70.44) --
	(212.44, 68.11) --
	(212.89, 66.07) --
	(213.34, 64.30) --
	(213.79, 62.80) --
	(214.23, 61.55) --
	(214.68, 60.54) --
	(215.13, 59.73) --
	(215.58, 59.12) --
	(216.03, 58.65) --
	(216.48, 58.32) --
	(216.93, 58.09) --
	(217.37, 57.93) --
	(217.82, 57.82) --
	(218.27, 57.76) --
	(218.72, 57.72) --
	(219.17, 57.70) --
	(219.62, 57.68) --
	(220.07, 57.68) --
	(220.52, 57.67) --
	(220.96, 57.67) --
	(221.41, 57.67) --
	(221.86, 57.67) --
	(222.31, 57.67) --
	(222.76, 57.67) --
	(223.21, 57.67) --
	(223.66, 57.67) --
	(224.11, 57.67) --
	(224.55, 57.67) --
	(225.00, 57.67) --
	(225.45, 57.67) --
	(225.90, 57.67) --
	(226.35, 57.67) --
	(226.80, 57.67) --
	(227.25, 57.67) --
	(227.69, 57.67) --
	(228.14, 57.67) --
	(228.59, 57.67) --
	(229.04, 57.67) --
	(229.49, 57.67) --
	(229.94, 57.67) --
	(230.39, 57.67) --
	(230.84, 57.67) --
	(231.28, 57.67) --
	(231.73, 57.67) --
	(232.18, 57.67) --
	(232.63, 57.67) --
	(233.08, 57.67) --
	(233.53, 57.67) --
	(233.98, 57.67) --
	(234.43, 57.67) --
	(234.87, 57.67) --
	(235.32, 57.67) --
	(235.77, 57.67) --
	(236.22, 57.67) --
	(236.67, 57.67) --
	(237.12, 57.67) --
	(237.57, 57.67) --
	(238.01, 57.67) --
	(238.46, 57.67) --
	(238.91, 57.67) --
	(239.36, 57.67) --
	(239.81, 57.67) --
	(240.26, 57.67) --
	(240.71, 57.67) --
	(241.16, 57.67) --
	(241.60, 57.67) --
	(242.05, 57.67) --
	(242.50, 57.67) --
	(242.95, 57.67) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67);

\path[] ( 42.83, 57.70) --
	( 43.28, 57.70) --
	( 43.73, 57.71) --
	( 44.18, 57.71) --
	( 44.63, 57.71) --
	( 45.08, 57.71) --
	( 45.52, 57.71) --
	( 45.97, 57.71) --
	( 46.42, 57.72) --
	( 46.87, 57.72) --
	( 47.32, 57.72) --
	( 47.77, 57.73) --
	( 48.22, 57.73) --
	( 48.67, 57.74) --
	( 49.11, 57.75) --
	( 49.56, 57.76) --
	( 50.01, 57.77) --
	( 50.46, 57.77) --
	( 50.91, 57.78) --
	( 51.36, 57.78) --
	( 51.81, 57.78) --
	( 52.25, 57.78) --
	( 52.70, 57.77) --
	( 53.15, 57.77) --
	( 53.60, 57.76) --
	( 54.05, 57.76) --
	( 54.50, 57.76) --
	( 54.95, 57.75) --
	( 55.40, 57.76) --
	( 55.84, 57.76) --
	( 56.29, 57.76) --
	( 56.74, 57.77) --
	( 57.19, 57.77) --
	( 57.64, 57.78) --
	( 58.09, 57.79) --
	( 58.54, 57.80) --
	( 58.99, 57.80) --
	( 59.43, 57.81) --
	( 59.88, 57.82) --
	( 60.33, 57.82) --
	( 60.78, 57.83) --
	( 61.23, 57.83) --
	( 61.68, 57.84) --
	( 62.13, 57.84) --
	( 62.57, 57.85) --
	( 63.02, 57.85) --
	( 63.47, 57.86) --
	( 63.92, 57.86) --
	( 64.37, 57.87) --
	( 64.82, 57.88) --
	( 65.27, 57.89) --
	( 65.72, 57.90) --
	( 66.16, 57.90) --
	( 66.61, 57.91) --
	( 67.06, 57.91) --
	( 67.51, 57.91) --
	( 67.96, 57.90) --
	( 68.41, 57.90) --
	( 68.86, 57.90) --
	( 69.31, 57.90) --
	( 69.75, 57.90) --
	( 70.20, 57.90) --
	( 70.65, 57.90) --
	( 71.10, 57.91) --
	( 71.55, 57.92) --
	( 72.00, 57.93) --
	( 72.45, 57.94) --
	( 72.89, 57.96) --
	( 73.34, 57.98) --
	( 73.79, 58.00) --
	( 74.24, 58.02) --
	( 74.69, 58.05) --
	( 75.14, 58.07) --
	( 75.59, 58.10) --
	( 76.04, 58.13) --
	( 76.48, 58.16) --
	( 76.93, 58.18) --
	( 77.38, 58.21) --
	( 77.83, 58.23) --
	( 78.28, 58.24) --
	( 78.73, 58.25) --
	( 79.18, 58.26) --
	( 79.63, 58.26) --
	( 80.07, 58.26) --
	( 80.52, 58.26) --
	( 80.97, 58.25) --
	( 81.42, 58.24) --
	( 81.87, 58.24) --
	( 82.32, 58.23) --
	( 82.77, 58.23) --
	( 83.21, 58.23) --
	( 83.66, 58.24) --
	( 84.11, 58.25) --
	( 84.56, 58.27) --
	( 85.01, 58.29) --
	( 85.46, 58.33) --
	( 85.91, 58.37) --
	( 86.36, 58.41) --
	( 86.80, 58.47) --
	( 87.25, 58.52) --
	( 87.70, 58.58) --
	( 88.15, 58.64) --
	( 88.60, 58.68) --
	( 89.05, 58.72) --
	( 89.50, 58.74) --
	( 89.95, 58.75) --
	( 90.39, 58.75) --
	( 90.84, 58.73) --
	( 91.29, 58.72) --
	( 91.74, 58.71) --
	( 92.19, 58.70) --
	( 92.64, 58.71) --
	( 93.09, 58.73) --
	( 93.53, 58.76) --
	( 93.98, 58.80) --
	( 94.43, 58.84) --
	( 94.88, 58.89) --
	( 95.33, 58.94) --
	( 95.78, 58.99) --
	( 96.23, 59.04) --
	( 96.68, 59.08) --
	( 97.12, 59.12) --
	( 97.57, 59.16) --
	( 98.02, 59.21) --
	( 98.47, 59.25) --
	( 98.92, 59.29) --
	( 99.37, 59.33) --
	( 99.82, 59.37) --
	(100.27, 59.41) --
	(100.71, 59.46) --
	(101.16, 59.50) --
	(101.61, 59.54) --
	(102.06, 59.58) --
	(102.51, 59.64) --
	(102.96, 59.69) --
	(103.41, 59.76) --
	(103.85, 59.83) --
	(104.30, 59.90) --
	(104.75, 59.98) --
	(105.20, 60.06) --
	(105.65, 60.14) --
	(106.10, 60.20) --
	(106.55, 60.25) --
	(107.00, 60.28) --
	(107.44, 60.29) --
	(107.89, 60.27) --
	(108.34, 60.24) --
	(108.79, 60.20) --
	(109.24, 60.16) --
	(109.69, 60.12) --
	(110.14, 60.09) --
	(110.59, 60.08) --
	(111.03, 60.08) --
	(111.48, 60.11) --
	(111.93, 60.16) --
	(112.38, 60.24) --
	(112.83, 60.32) --
	(113.28, 60.42) --
	(113.73, 60.52) --
	(114.17, 60.62) --
	(114.62, 60.71) --
	(115.07, 60.79) --
	(115.52, 60.85) --
	(115.97, 60.90) --
	(116.42, 60.93) --
	(116.87, 60.95) --
	(117.32, 60.95) --
	(117.76, 60.95) --
	(118.21, 60.95) --
	(118.66, 60.96) --
	(119.11, 60.98) --
	(119.56, 61.02) --
	(120.01, 61.08) --
	(120.46, 61.17) --
	(120.91, 61.26) --
	(121.35, 61.37) --
	(121.80, 61.48) --
	(122.25, 61.59) --
	(122.70, 61.69) --
	(123.15, 61.77) --
	(123.60, 61.85) --
	(124.05, 61.91) --
	(124.49, 61.97) --
	(124.94, 62.02) --
	(125.39, 62.07) --
	(125.84, 62.12) --
	(126.29, 62.18) --
	(126.74, 62.25) --
	(127.19, 62.31) --
	(127.64, 62.38) --
	(128.08, 62.45) --
	(128.53, 62.51) --
	(128.98, 62.58) --
	(129.43, 62.65) --
	(129.88, 62.72) --
	(130.33, 62.79) --
	(130.78, 62.87) --
	(131.23, 62.95) --
	(131.67, 63.04) --
	(132.12, 63.13) --
	(132.57, 63.22) --
	(133.02, 63.30) --
	(133.47, 63.37) --
	(133.92, 63.43) --
	(134.37, 63.47) --
	(134.81, 63.50) --
	(135.26, 63.53) --
	(135.71, 63.56) --
	(136.16, 63.60) --
	(136.61, 63.66) --
	(137.06, 63.73) --
	(137.51, 63.84) --
	(137.96, 63.96) --
	(138.40, 64.10) --
	(138.85, 64.25) --
	(139.30, 64.40) --
	(139.75, 64.56) --
	(140.20, 64.71) --
	(140.65, 64.87) --
	(141.10, 65.01) --
	(141.55, 65.16) --
	(141.99, 65.30) --
	(142.44, 65.44) --
	(142.89, 65.58) --
	(143.34, 65.72) --
	(143.79, 65.87) --
	(144.24, 66.03) --
	(144.69, 66.20) --
	(145.13, 66.38) --
	(145.58, 66.57) --
	(146.03, 66.77) --
	(146.48, 66.97) --
	(146.93, 67.18) --
	(147.38, 67.39) --
	(147.83, 67.61) --
	(148.28, 67.83) --
	(148.72, 68.05) --
	(149.17, 68.27) --
	(149.62, 68.49) --
	(150.07, 68.70) --
	(150.52, 68.89) --
	(150.97, 69.05) --
	(151.42, 69.19) --
	(151.87, 69.32) --
	(152.31, 69.43) --
	(152.76, 69.55) --
	(153.21, 69.69) --
	(153.66, 69.86) --
	(154.11, 70.09) --
	(154.56, 70.38) --
	(155.01, 70.77) --
	(155.45, 71.26) --
	(155.90, 71.88) --
	(156.35, 72.64) --
	(156.80, 73.55) --
	(157.25, 74.61) --
	(157.70, 75.81) --
	(158.15, 77.11) --
	(158.60, 78.46) --
	(159.04, 79.78) --
	(159.49, 80.99) --
	(159.94, 82.04) --
	(160.39, 82.88) --
	(160.84, 83.47) --
	(161.29, 83.81) --
	(161.74, 83.94) --
	(162.19, 83.91) --
	(162.63, 83.78) --
	(163.08, 83.61) --
	(163.53, 83.45) --
	(163.98, 83.35) --
	(164.43, 83.34) --
	(164.88, 83.42) --
	(165.33, 83.61) --
	(165.77, 83.89) --
	(166.22, 84.25) --
	(166.67, 84.72) --
	(167.12, 85.28) --
	(167.57, 85.95) --
	(168.02, 86.76) --
	(168.47, 87.72) --
	(168.92, 88.84) --
	(169.36, 90.12) --
	(169.81, 91.55) --
	(170.26, 93.09) --
	(170.71, 94.68) --
	(171.16, 96.24) --
	(171.61, 97.68) --
	(172.06, 98.94) --
	(172.51,100.00) --
	(172.95,100.85) --
	(173.40,101.53) --
	(173.85,102.09) --
	(174.30,102.63) --
	(174.75,103.22) --
	(175.20,103.94) --
	(175.65,104.86) --
	(176.09,106.03) --
	(176.54,107.45) --
	(176.99,109.11) --
	(177.44,110.98) --
	(177.89,112.99) --
	(178.34,115.06) --
	(178.79,117.14) --
	(179.24,119.19) --
	(179.68,121.19) --
	(180.13,123.16) --
	(180.58,125.12) --
	(181.03,127.11) --
	(181.48,129.17) --
	(181.93,131.29) --
	(182.38,133.46) --
	(182.83,135.63) --
	(183.27,137.75) --
	(183.72,139.75) --
	(184.17,141.58) --
	(184.62,143.26) --
	(185.07,144.80) --
	(185.52,146.26) --
	(185.97,147.65) --
	(186.41,149.01) --
	(186.86,150.33) --
	(187.31,151.57) --
	(187.76,152.70) --
	(188.21,153.69) --
	(188.66,154.49) --
	(189.11,155.09) --
	(189.56,155.49) --
	(190.00,155.73) --
	(190.45,155.80) --
	(190.90,155.77) --
	(191.35,155.66) --
	(191.80,155.50) --
	(192.25,155.31) --
	(192.70,155.11) --
	(193.15,154.89) --
	(193.59,154.66) --
	(194.04,154.40) --
	(194.49,154.09) --
	(194.94,153.72) --
	(195.39,153.27) --
	(195.84,152.73) --
	(196.29,152.11) --
	(196.73,151.42) --
	(197.18,150.67) --
	(197.63,149.88) --
	(198.08,149.07) --
	(198.53,148.24) --
	(198.98,147.39) --
	(199.43,146.52) --
	(199.88,145.60) --
	(200.32,144.64) --
	(200.77,143.64) --
	(201.22,142.59) --
	(201.67,141.51) --
	(202.12,140.40) --
	(202.57,139.28) --
	(203.02,138.17) --
	(203.47,137.08) --
	(203.91,136.02) --
	(204.36,135.01) --
	(204.81,134.04) --
	(205.26,133.12) --
	(205.71,132.25) --
	(206.16,131.42) --
	(206.61,130.65) --
	(207.05,129.93) --
	(207.50,129.27) --
	(207.95,128.68) --
	(208.40,128.16) --
	(208.85,127.70) --
	(209.30,127.32) --
	(209.75,127.01) --
	(210.20,126.77) --
	(210.64,126.58) --
	(211.09,126.43) --
	(211.54,126.28) --
	(211.99,126.12) --
	(212.44,125.90) --
	(212.89,125.59) --
	(213.34,125.14) --
	(213.79,124.52) --
	(214.23,123.67) --
	(214.68,122.57) --
	(215.13,121.18) --
	(215.58,119.49) --
	(216.03,117.48) --
	(216.48,115.13) --
	(216.93,112.46) --
	(217.37,109.50) --
	(217.82,106.29) --
	(218.27,102.88) --
	(218.72, 99.33) --
	(219.17, 95.72) --
	(219.62, 92.11) --
	(220.07, 88.59) --
	(220.52, 85.21) --
	(220.96, 82.01) --
	(221.41, 79.03) --
	(221.86, 76.28) --
	(222.31, 73.77) --
	(222.76, 71.47) --
	(223.21, 69.41) --
	(223.66, 67.54) --
	(224.11, 65.86) --
	(224.55, 64.36) --
	(225.00, 63.03) --
	(225.45, 61.89) --
	(225.90, 60.92) --
	(226.35, 60.11) --
	(226.80, 59.46) --
	(227.25, 58.94) --
	(227.69, 58.55) --
	(228.14, 58.26) --
	(228.59, 58.06) --
	(229.04, 57.91) --
	(229.49, 57.82) --
	(229.94, 57.76) --
	(230.39, 57.72) --
	(230.84, 57.70) --
	(231.28, 57.69) --
	(231.73, 57.68) --
	(232.18, 57.67) --
	(232.63, 57.67) --
	(233.08, 57.67) --
	(233.53, 57.67) --
	(233.98, 57.67) --
	(234.43, 57.67) --
	(234.87, 57.67) --
	(235.32, 57.67) --
	(235.77, 57.67) --
	(236.22, 57.67) --
	(236.67, 57.67) --
	(237.12, 57.67) --
	(237.57, 57.67) --
	(238.01, 57.67) --
	(238.46, 57.67) --
	(238.91, 57.67) --
	(239.36, 57.67) --
	(239.81, 57.67) --
	(240.26, 57.67) --
	(240.71, 57.67) --
	(241.16, 57.67) --
	(241.60, 57.67) --
	(242.05, 57.67) --
	(242.50, 57.67) --
	(242.95, 57.67) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67) --
	(272.12, 57.67) --
	(271.67, 57.67) --
	(271.22, 57.67) --
	(270.77, 57.67) --
	(270.32, 57.67) --
	(269.87, 57.67) --
	(269.42, 57.67) --
	(268.97, 57.67) --
	(268.53, 57.67) --
	(268.08, 57.67) --
	(267.63, 57.67) --
	(267.18, 57.67) --
	(266.73, 57.67) --
	(266.28, 57.67) --
	(265.83, 57.67) --
	(265.39, 57.67) --
	(264.94, 57.67) --
	(264.49, 57.67) --
	(264.04, 57.67) --
	(263.59, 57.67) --
	(263.14, 57.67) --
	(262.69, 57.67) --
	(262.24, 57.67) --
	(261.80, 57.67) --
	(261.35, 57.67) --
	(260.90, 57.67) --
	(260.45, 57.67) --
	(260.00, 57.67) --
	(259.55, 57.67) --
	(259.10, 57.67) --
	(258.65, 57.67) --
	(258.21, 57.67) --
	(257.76, 57.67) --
	(257.31, 57.67) --
	(256.86, 57.67) --
	(256.41, 57.67) --
	(255.96, 57.67) --
	(255.51, 57.67) --
	(255.07, 57.67) --
	(254.62, 57.67) --
	(254.17, 57.67) --
	(253.72, 57.67) --
	(253.27, 57.67) --
	(252.82, 57.67) --
	(252.37, 57.67) --
	(251.92, 57.67) --
	(251.48, 57.67) --
	(251.03, 57.67) --
	(250.58, 57.67) --
	(250.13, 57.67) --
	(249.68, 57.67) --
	(249.23, 57.67) --
	(248.78, 57.67) --
	(248.33, 57.67) --
	(247.89, 57.67) --
	(247.44, 57.67) --
	(246.99, 57.67) --
	(246.54, 57.67) --
	(246.09, 57.67) --
	(245.64, 57.67) --
	(245.19, 57.67) --
	(244.75, 57.67) --
	(244.30, 57.67) --
	(243.85, 57.67) --
	(243.40, 57.67) --
	(242.95, 57.67) --
	(242.50, 57.67) --
	(242.05, 57.67) --
	(241.60, 57.67) --
	(241.16, 57.67) --
	(240.71, 57.67) --
	(240.26, 57.67) --
	(239.81, 57.67) --
	(239.36, 57.67) --
	(238.91, 57.67) --
	(238.46, 57.67) --
	(238.01, 57.67) --
	(237.57, 57.67) --
	(237.12, 57.67) --
	(236.67, 57.67) --
	(236.22, 57.67) --
	(235.77, 57.67) --
	(235.32, 57.67) --
	(234.87, 57.67) --
	(234.43, 57.67) --
	(233.98, 57.67) --
	(233.53, 57.67) --
	(233.08, 57.67) --
	(232.63, 57.67) --
	(232.18, 57.67) --
	(231.73, 57.67) --
	(231.28, 57.67) --
	(230.84, 57.67) --
	(230.39, 57.67) --
	(229.94, 57.67) --
	(229.49, 57.67) --
	(229.04, 57.67) --
	(228.59, 57.67) --
	(228.14, 57.67) --
	(227.69, 57.67) --
	(227.25, 57.67) --
	(226.80, 57.67) --
	(226.35, 57.67) --
	(225.90, 57.67) --
	(225.45, 57.67) --
	(225.00, 57.67) --
	(224.55, 57.67) --
	(224.11, 57.67) --
	(223.66, 57.67) --
	(223.21, 57.67) --
	(222.76, 57.67) --
	(222.31, 57.67) --
	(221.86, 57.67) --
	(221.41, 57.67) --
	(220.96, 57.67) --
	(220.52, 57.67) --
	(220.07, 57.67) --
	(219.62, 57.67) --
	(219.17, 57.67) --
	(218.72, 57.67) --
	(218.27, 57.67) --
	(217.82, 57.67) --
	(217.37, 57.67) --
	(216.93, 57.67) --
	(216.48, 57.67) --
	(216.03, 57.67) --
	(215.58, 57.67) --
	(215.13, 57.67) --
	(214.68, 57.67) --
	(214.23, 57.67) --
	(213.79, 57.67) --
	(213.34, 57.67) --
	(212.89, 57.67) --
	(212.44, 57.67) --
	(211.99, 57.67) --
	(211.54, 57.67) --
	(211.09, 57.67) --
	(210.64, 57.67) --
	(210.20, 57.67) --
	(209.75, 57.67) --
	(209.30, 57.67) --
	(208.85, 57.67) --
	(208.40, 57.67) --
	(207.95, 57.67) --
	(207.50, 57.67) --
	(207.05, 57.67) --
	(206.61, 57.67) --
	(206.16, 57.67) --
	(205.71, 57.67) --
	(205.26, 57.67) --
	(204.81, 57.67) --
	(204.36, 57.67) --
	(203.91, 57.67) --
	(203.47, 57.67) --
	(203.02, 57.67) --
	(202.57, 57.67) --
	(202.12, 57.67) --
	(201.67, 57.67) --
	(201.22, 57.67) --
	(200.77, 57.67) --
	(200.32, 57.67) --
	(199.88, 57.67) --
	(199.43, 57.67) --
	(198.98, 57.67) --
	(198.53, 57.67) --
	(198.08, 57.67) --
	(197.63, 57.67) --
	(197.18, 57.67) --
	(196.73, 57.67) --
	(196.29, 57.67) --
	(195.84, 57.67) --
	(195.39, 57.67) --
	(194.94, 57.67) --
	(194.49, 57.67) --
	(194.04, 57.67) --
	(193.59, 57.67) --
	(193.15, 57.67) --
	(192.70, 57.67) --
	(192.25, 57.67) --
	(191.80, 57.67) --
	(191.35, 57.67) --
	(190.90, 57.67) --
	(190.45, 57.67) --
	(190.00, 57.67) --
	(189.56, 57.67) --
	(189.11, 57.67) --
	(188.66, 57.67) --
	(188.21, 57.67) --
	(187.76, 57.67) --
	(187.31, 57.67) --
	(186.86, 57.67) --
	(186.41, 57.67) --
	(185.97, 57.67) --
	(185.52, 57.67) --
	(185.07, 57.67) --
	(184.62, 57.67) --
	(184.17, 57.67) --
	(183.72, 57.67) --
	(183.27, 57.67) --
	(182.83, 57.67) --
	(182.38, 57.67) --
	(181.93, 57.67) --
	(181.48, 57.67) --
	(181.03, 57.67) --
	(180.58, 57.67) --
	(180.13, 57.67) --
	(179.68, 57.67) --
	(179.24, 57.67) --
	(178.79, 57.67) --
	(178.34, 57.67) --
	(177.89, 57.67) --
	(177.44, 57.67) --
	(176.99, 57.67) --
	(176.54, 57.67) --
	(176.09, 57.67) --
	(175.65, 57.67) --
	(175.20, 57.67) --
	(174.75, 57.67) --
	(174.30, 57.67) --
	(173.85, 57.67) --
	(173.40, 57.67) --
	(172.95, 57.67) --
	(172.51, 57.67) --
	(172.06, 57.67) --
	(171.61, 57.67) --
	(171.16, 57.67) --
	(170.71, 57.67) --
	(170.26, 57.67) --
	(169.81, 57.67) --
	(169.36, 57.67) --
	(168.92, 57.67) --
	(168.47, 57.67) --
	(168.02, 57.67) --
	(167.57, 57.67) --
	(167.12, 57.67) --
	(166.67, 57.67) --
	(166.22, 57.67) --
	(165.77, 57.67) --
	(165.33, 57.67) --
	(164.88, 57.67) --
	(164.43, 57.67) --
	(163.98, 57.67) --
	(163.53, 57.67) --
	(163.08, 57.67) --
	(162.63, 57.67) --
	(162.19, 57.67) --
	(161.74, 57.67) --
	(161.29, 57.67) --
	(160.84, 57.67) --
	(160.39, 57.67) --
	(159.94, 57.67) --
	(159.49, 57.67) --
	(159.04, 57.67) --
	(158.60, 57.67) --
	(158.15, 57.67) --
	(157.70, 57.67) --
	(157.25, 57.67) --
	(156.80, 57.67) --
	(156.35, 57.67) --
	(155.90, 57.67) --
	(155.45, 57.67) --
	(155.01, 57.67) --
	(154.56, 57.67) --
	(154.11, 57.67) --
	(153.66, 57.67) --
	(153.21, 57.67) --
	(152.76, 57.67) --
	(152.31, 57.67) --
	(151.87, 57.67) --
	(151.42, 57.67) --
	(150.97, 57.67) --
	(150.52, 57.67) --
	(150.07, 57.67) --
	(149.62, 57.67) --
	(149.17, 57.67) --
	(148.72, 57.67) --
	(148.28, 57.67) --
	(147.83, 57.67) --
	(147.38, 57.67) --
	(146.93, 57.67) --
	(146.48, 57.67) --
	(146.03, 57.67) --
	(145.58, 57.67) --
	(145.13, 57.67) --
	(144.69, 57.67) --
	(144.24, 57.67) --
	(143.79, 57.67) --
	(143.34, 57.67) --
	(142.89, 57.67) --
	(142.44, 57.67) --
	(141.99, 57.67) --
	(141.55, 57.67) --
	(141.10, 57.67) --
	(140.65, 57.67) --
	(140.20, 57.67) --
	(139.75, 57.67) --
	(139.30, 57.67) --
	(138.85, 57.67) --
	(138.40, 57.67) --
	(137.96, 57.67) --
	(137.51, 57.67) --
	(137.06, 57.67) --
	(136.61, 57.67) --
	(136.16, 57.67) --
	(135.71, 57.67) --
	(135.26, 57.67) --
	(134.81, 57.67) --
	(134.37, 57.67) --
	(133.92, 57.67) --
	(133.47, 57.67) --
	(133.02, 57.67) --
	(132.57, 57.67) --
	(132.12, 57.67) --
	(131.67, 57.67) --
	(131.23, 57.67) --
	(130.78, 57.67) --
	(130.33, 57.67) --
	(129.88, 57.67) --
	(129.43, 57.67) --
	(128.98, 57.67) --
	(128.53, 57.67) --
	(128.08, 57.67) --
	(127.64, 57.67) --
	(127.19, 57.67) --
	(126.74, 57.67) --
	(126.29, 57.67) --
	(125.84, 57.67) --
	(125.39, 57.67) --
	(124.94, 57.67) --
	(124.49, 57.67) --
	(124.05, 57.67) --
	(123.60, 57.67) --
	(123.15, 57.67) --
	(122.70, 57.67) --
	(122.25, 57.67) --
	(121.80, 57.67) --
	(121.35, 57.67) --
	(120.91, 57.67) --
	(120.46, 57.67) --
	(120.01, 57.67) --
	(119.56, 57.67) --
	(119.11, 57.67) --
	(118.66, 57.67) --
	(118.21, 57.67) --
	(117.76, 57.67) --
	(117.32, 57.67) --
	(116.87, 57.67) --
	(116.42, 57.67) --
	(115.97, 57.67) --
	(115.52, 57.67) --
	(115.07, 57.67) --
	(114.62, 57.67) --
	(114.17, 57.67) --
	(113.73, 57.67) --
	(113.28, 57.67) --
	(112.83, 57.67) --
	(112.38, 57.67) --
	(111.93, 57.67) --
	(111.48, 57.67) --
	(111.03, 57.67) --
	(110.59, 57.67) --
	(110.14, 57.67) --
	(109.69, 57.67) --
	(109.24, 57.67) --
	(108.79, 57.67) --
	(108.34, 57.67) --
	(107.89, 57.67) --
	(107.44, 57.67) --
	(107.00, 57.67) --
	(106.55, 57.67) --
	(106.10, 57.67) --
	(105.65, 57.67) --
	(105.20, 57.67) --
	(104.75, 57.67) --
	(104.30, 57.67) --
	(103.85, 57.67) --
	(103.41, 57.67) --
	(102.96, 57.67) --
	(102.51, 57.67) --
	(102.06, 57.67) --
	(101.61, 57.67) --
	(101.16, 57.67) --
	(100.71, 57.67) --
	(100.27, 57.67) --
	( 99.82, 57.67) --
	( 99.37, 57.67) --
	( 98.92, 57.67) --
	( 98.47, 57.67) --
	( 98.02, 57.67) --
	( 97.57, 57.67) --
	( 97.12, 57.67) --
	( 96.68, 57.67) --
	( 96.23, 57.67) --
	( 95.78, 57.67) --
	( 95.33, 57.67) --
	( 94.88, 57.67) --
	( 94.43, 57.67) --
	( 93.98, 57.67) --
	( 93.53, 57.67) --
	( 93.09, 57.67) --
	( 92.64, 57.67) --
	( 92.19, 57.67) --
	( 91.74, 57.67) --
	( 91.29, 57.67) --
	( 90.84, 57.67) --
	( 90.39, 57.67) --
	( 89.95, 57.67) --
	( 89.50, 57.67) --
	( 89.05, 57.67) --
	( 88.60, 57.67) --
	( 88.15, 57.67) --
	( 87.70, 57.67) --
	( 87.25, 57.67) --
	( 86.80, 57.67) --
	( 86.36, 57.67) --
	( 85.91, 57.67) --
	( 85.46, 57.67) --
	( 85.01, 57.67) --
	( 84.56, 57.67) --
	( 84.11, 57.67) --
	( 83.66, 57.67) --
	( 83.21, 57.67) --
	( 82.77, 57.67) --
	( 82.32, 57.67) --
	( 81.87, 57.67) --
	( 81.42, 57.67) --
	( 80.97, 57.67) --
	( 80.52, 57.67) --
	( 80.07, 57.67) --
	( 79.63, 57.67) --
	( 79.18, 57.67) --
	( 78.73, 57.67) --
	( 78.28, 57.67) --
	( 77.83, 57.67) --
	( 77.38, 57.67) --
	( 76.93, 57.67) --
	( 76.48, 57.67) --
	( 76.04, 57.67) --
	( 75.59, 57.67) --
	( 75.14, 57.67) --
	( 74.69, 57.67) --
	( 74.24, 57.67) --
	( 73.79, 57.67) --
	( 73.34, 57.67) --
	( 72.89, 57.67) --
	( 72.45, 57.67) --
	( 72.00, 57.67) --
	( 71.55, 57.67) --
	( 71.10, 57.67) --
	( 70.65, 57.67) --
	( 70.20, 57.67) --
	( 69.75, 57.67) --
	( 69.31, 57.67) --
	( 68.86, 57.67) --
	( 68.41, 57.67) --
	( 67.96, 57.67) --
	( 67.51, 57.67) --
	( 67.06, 57.67) --
	( 66.61, 57.67) --
	( 66.16, 57.67) --
	( 65.72, 57.67) --
	( 65.27, 57.67) --
	( 64.82, 57.67) --
	( 64.37, 57.67) --
	( 63.92, 57.67) --
	( 63.47, 57.67) --
	( 63.02, 57.67) --
	( 62.57, 57.67) --
	( 62.13, 57.67) --
	( 61.68, 57.67) --
	( 61.23, 57.67) --
	( 60.78, 57.67) --
	( 60.33, 57.67) --
	( 59.88, 57.67) --
	( 59.43, 57.67) --
	( 58.99, 57.67) --
	( 58.54, 57.67) --
	( 58.09, 57.67) --
	( 57.64, 57.67) --
	( 57.19, 57.67) --
	( 56.74, 57.67) --
	( 56.29, 57.67) --
	( 55.84, 57.67) --
	( 55.40, 57.67) --
	( 54.95, 57.67) --
	( 54.50, 57.67) --
	( 54.05, 57.67) --
	( 53.60, 57.67) --
	( 53.15, 57.67) --
	( 52.70, 57.67) --
	( 52.25, 57.67) --
	( 51.81, 57.67) --
	( 51.36, 57.67) --
	( 50.91, 57.67) --
	( 50.46, 57.67) --
	( 50.01, 57.67) --
	( 49.56, 57.67) --
	( 49.11, 57.67) --
	( 48.67, 57.67) --
	( 48.22, 57.67) --
	( 47.77, 57.67) --
	( 47.32, 57.67) --
	( 46.87, 57.67) --
	( 46.42, 57.67) --
	( 45.97, 57.67) --
	( 45.52, 57.67) --
	( 45.08, 57.67) --
	( 44.63, 57.67) --
	( 44.18, 57.67) --
	( 43.73, 57.67) --
	( 43.28, 57.67) --
	( 42.83, 57.67) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 42.83, 57.70) --
	( 43.28, 57.70) --
	( 43.73, 57.71) --
	( 44.18, 57.71) --
	( 44.63, 57.71) --
	( 45.08, 57.71) --
	( 45.52, 57.71) --
	( 45.97, 57.71) --
	( 46.42, 57.72) --
	( 46.87, 57.72) --
	( 47.32, 57.72) --
	( 47.77, 57.73) --
	( 48.22, 57.73) --
	( 48.67, 57.74) --
	( 49.11, 57.75) --
	( 49.56, 57.76) --
	( 50.01, 57.77) --
	( 50.46, 57.77) --
	( 50.91, 57.78) --
	( 51.36, 57.78) --
	( 51.81, 57.78) --
	( 52.25, 57.78) --
	( 52.70, 57.77) --
	( 53.15, 57.77) --
	( 53.60, 57.76) --
	( 54.05, 57.76) --
	( 54.50, 57.76) --
	( 54.95, 57.75) --
	( 55.40, 57.76) --
	( 55.84, 57.76) --
	( 56.29, 57.76) --
	( 56.74, 57.77) --
	( 57.19, 57.77) --
	( 57.64, 57.78) --
	( 58.09, 57.79) --
	( 58.54, 57.80) --
	( 58.99, 57.80) --
	( 59.43, 57.81) --
	( 59.88, 57.82) --
	( 60.33, 57.82) --
	( 60.78, 57.83) --
	( 61.23, 57.83) --
	( 61.68, 57.84) --
	( 62.13, 57.84) --
	( 62.57, 57.85) --
	( 63.02, 57.85) --
	( 63.47, 57.86) --
	( 63.92, 57.86) --
	( 64.37, 57.87) --
	( 64.82, 57.88) --
	( 65.27, 57.89) --
	( 65.72, 57.90) --
	( 66.16, 57.90) --
	( 66.61, 57.91) --
	( 67.06, 57.91) --
	( 67.51, 57.91) --
	( 67.96, 57.90) --
	( 68.41, 57.90) --
	( 68.86, 57.90) --
	( 69.31, 57.90) --
	( 69.75, 57.90) --
	( 70.20, 57.90) --
	( 70.65, 57.90) --
	( 71.10, 57.91) --
	( 71.55, 57.92) --
	( 72.00, 57.93) --
	( 72.45, 57.94) --
	( 72.89, 57.96) --
	( 73.34, 57.98) --
	( 73.79, 58.00) --
	( 74.24, 58.02) --
	( 74.69, 58.05) --
	( 75.14, 58.07) --
	( 75.59, 58.10) --
	( 76.04, 58.13) --
	( 76.48, 58.16) --
	( 76.93, 58.18) --
	( 77.38, 58.21) --
	( 77.83, 58.23) --
	( 78.28, 58.24) --
	( 78.73, 58.25) --
	( 79.18, 58.26) --
	( 79.63, 58.26) --
	( 80.07, 58.26) --
	( 80.52, 58.26) --
	( 80.97, 58.25) --
	( 81.42, 58.24) --
	( 81.87, 58.24) --
	( 82.32, 58.23) --
	( 82.77, 58.23) --
	( 83.21, 58.23) --
	( 83.66, 58.24) --
	( 84.11, 58.25) --
	( 84.56, 58.27) --
	( 85.01, 58.29) --
	( 85.46, 58.33) --
	( 85.91, 58.37) --
	( 86.36, 58.41) --
	( 86.80, 58.47) --
	( 87.25, 58.52) --
	( 87.70, 58.58) --
	( 88.15, 58.64) --
	( 88.60, 58.68) --
	( 89.05, 58.72) --
	( 89.50, 58.74) --
	( 89.95, 58.75) --
	( 90.39, 58.75) --
	( 90.84, 58.73) --
	( 91.29, 58.72) --
	( 91.74, 58.71) --
	( 92.19, 58.70) --
	( 92.64, 58.71) --
	( 93.09, 58.73) --
	( 93.53, 58.76) --
	( 93.98, 58.80) --
	( 94.43, 58.84) --
	( 94.88, 58.89) --
	( 95.33, 58.94) --
	( 95.78, 58.99) --
	( 96.23, 59.04) --
	( 96.68, 59.08) --
	( 97.12, 59.12) --
	( 97.57, 59.16) --
	( 98.02, 59.21) --
	( 98.47, 59.25) --
	( 98.92, 59.29) --
	( 99.37, 59.33) --
	( 99.82, 59.37) --
	(100.27, 59.41) --
	(100.71, 59.46) --
	(101.16, 59.50) --
	(101.61, 59.54) --
	(102.06, 59.58) --
	(102.51, 59.64) --
	(102.96, 59.69) --
	(103.41, 59.76) --
	(103.85, 59.83) --
	(104.30, 59.90) --
	(104.75, 59.98) --
	(105.20, 60.06) --
	(105.65, 60.14) --
	(106.10, 60.20) --
	(106.55, 60.25) --
	(107.00, 60.28) --
	(107.44, 60.29) --
	(107.89, 60.27) --
	(108.34, 60.24) --
	(108.79, 60.20) --
	(109.24, 60.16) --
	(109.69, 60.12) --
	(110.14, 60.09) --
	(110.59, 60.08) --
	(111.03, 60.08) --
	(111.48, 60.11) --
	(111.93, 60.16) --
	(112.38, 60.24) --
	(112.83, 60.32) --
	(113.28, 60.42) --
	(113.73, 60.52) --
	(114.17, 60.62) --
	(114.62, 60.71) --
	(115.07, 60.79) --
	(115.52, 60.85) --
	(115.97, 60.90) --
	(116.42, 60.93) --
	(116.87, 60.95) --
	(117.32, 60.95) --
	(117.76, 60.95) --
	(118.21, 60.95) --
	(118.66, 60.96) --
	(119.11, 60.98) --
	(119.56, 61.02) --
	(120.01, 61.08) --
	(120.46, 61.17) --
	(120.91, 61.26) --
	(121.35, 61.37) --
	(121.80, 61.48) --
	(122.25, 61.59) --
	(122.70, 61.69) --
	(123.15, 61.77) --
	(123.60, 61.85) --
	(124.05, 61.91) --
	(124.49, 61.97) --
	(124.94, 62.02) --
	(125.39, 62.07) --
	(125.84, 62.12) --
	(126.29, 62.18) --
	(126.74, 62.25) --
	(127.19, 62.31) --
	(127.64, 62.38) --
	(128.08, 62.45) --
	(128.53, 62.51) --
	(128.98, 62.58) --
	(129.43, 62.65) --
	(129.88, 62.72) --
	(130.33, 62.79) --
	(130.78, 62.87) --
	(131.23, 62.95) --
	(131.67, 63.04) --
	(132.12, 63.13) --
	(132.57, 63.22) --
	(133.02, 63.30) --
	(133.47, 63.37) --
	(133.92, 63.43) --
	(134.37, 63.47) --
	(134.81, 63.50) --
	(135.26, 63.53) --
	(135.71, 63.56) --
	(136.16, 63.60) --
	(136.61, 63.66) --
	(137.06, 63.73) --
	(137.51, 63.84) --
	(137.96, 63.96) --
	(138.40, 64.10) --
	(138.85, 64.25) --
	(139.30, 64.40) --
	(139.75, 64.56) --
	(140.20, 64.71) --
	(140.65, 64.87) --
	(141.10, 65.01) --
	(141.55, 65.16) --
	(141.99, 65.30) --
	(142.44, 65.44) --
	(142.89, 65.58) --
	(143.34, 65.72) --
	(143.79, 65.87) --
	(144.24, 66.03) --
	(144.69, 66.20) --
	(145.13, 66.38) --
	(145.58, 66.57) --
	(146.03, 66.77) --
	(146.48, 66.97) --
	(146.93, 67.18) --
	(147.38, 67.39) --
	(147.83, 67.61) --
	(148.28, 67.83) --
	(148.72, 68.05) --
	(149.17, 68.27) --
	(149.62, 68.49) --
	(150.07, 68.70) --
	(150.52, 68.89) --
	(150.97, 69.05) --
	(151.42, 69.19) --
	(151.87, 69.32) --
	(152.31, 69.43) --
	(152.76, 69.55) --
	(153.21, 69.69) --
	(153.66, 69.86) --
	(154.11, 70.09) --
	(154.56, 70.38) --
	(155.01, 70.77) --
	(155.45, 71.26) --
	(155.90, 71.88) --
	(156.35, 72.64) --
	(156.80, 73.55) --
	(157.25, 74.61) --
	(157.70, 75.81) --
	(158.15, 77.11) --
	(158.60, 78.46) --
	(159.04, 79.78) --
	(159.49, 80.99) --
	(159.94, 82.04) --
	(160.39, 82.88) --
	(160.84, 83.47) --
	(161.29, 83.81) --
	(161.74, 83.94) --
	(162.19, 83.91) --
	(162.63, 83.78) --
	(163.08, 83.61) --
	(163.53, 83.45) --
	(163.98, 83.35) --
	(164.43, 83.34) --
	(164.88, 83.42) --
	(165.33, 83.61) --
	(165.77, 83.89) --
	(166.22, 84.25) --
	(166.67, 84.72) --
	(167.12, 85.28) --
	(167.57, 85.95) --
	(168.02, 86.76) --
	(168.47, 87.72) --
	(168.92, 88.84) --
	(169.36, 90.12) --
	(169.81, 91.55) --
	(170.26, 93.09) --
	(170.71, 94.68) --
	(171.16, 96.24) --
	(171.61, 97.68) --
	(172.06, 98.94) --
	(172.51,100.00) --
	(172.95,100.85) --
	(173.40,101.53) --
	(173.85,102.09) --
	(174.30,102.63) --
	(174.75,103.22) --
	(175.20,103.94) --
	(175.65,104.86) --
	(176.09,106.03) --
	(176.54,107.45) --
	(176.99,109.11) --
	(177.44,110.98) --
	(177.89,112.99) --
	(178.34,115.06) --
	(178.79,117.14) --
	(179.24,119.19) --
	(179.68,121.19) --
	(180.13,123.16) --
	(180.58,125.12) --
	(181.03,127.11) --
	(181.48,129.17) --
	(181.93,131.29) --
	(182.38,133.46) --
	(182.83,135.63) --
	(183.27,137.75) --
	(183.72,139.75) --
	(184.17,141.58) --
	(184.62,143.26) --
	(185.07,144.80) --
	(185.52,146.26) --
	(185.97,147.65) --
	(186.41,149.01) --
	(186.86,150.33) --
	(187.31,151.57) --
	(187.76,152.70) --
	(188.21,153.69) --
	(188.66,154.49) --
	(189.11,155.09) --
	(189.56,155.49) --
	(190.00,155.73) --
	(190.45,155.80) --
	(190.90,155.77) --
	(191.35,155.66) --
	(191.80,155.50) --
	(192.25,155.31) --
	(192.70,155.11) --
	(193.15,154.89) --
	(193.59,154.66) --
	(194.04,154.40) --
	(194.49,154.09) --
	(194.94,153.72) --
	(195.39,153.27) --
	(195.84,152.73) --
	(196.29,152.11) --
	(196.73,151.42) --
	(197.18,150.67) --
	(197.63,149.88) --
	(198.08,149.07) --
	(198.53,148.24) --
	(198.98,147.39) --
	(199.43,146.52) --
	(199.88,145.60) --
	(200.32,144.64) --
	(200.77,143.64) --
	(201.22,142.59) --
	(201.67,141.51) --
	(202.12,140.40) --
	(202.57,139.28) --
	(203.02,138.17) --
	(203.47,137.08) --
	(203.91,136.02) --
	(204.36,135.01) --
	(204.81,134.04) --
	(205.26,133.12) --
	(205.71,132.25) --
	(206.16,131.42) --
	(206.61,130.65) --
	(207.05,129.93) --
	(207.50,129.27) --
	(207.95,128.68) --
	(208.40,128.16) --
	(208.85,127.70) --
	(209.30,127.32) --
	(209.75,127.01) --
	(210.20,126.77) --
	(210.64,126.58) --
	(211.09,126.43) --
	(211.54,126.28) --
	(211.99,126.12) --
	(212.44,125.90) --
	(212.89,125.59) --
	(213.34,125.14) --
	(213.79,124.52) --
	(214.23,123.67) --
	(214.68,122.57) --
	(215.13,121.18) --
	(215.58,119.49) --
	(216.03,117.48) --
	(216.48,115.13) --
	(216.93,112.46) --
	(217.37,109.50) --
	(217.82,106.29) --
	(218.27,102.88) --
	(218.72, 99.33) --
	(219.17, 95.72) --
	(219.62, 92.11) --
	(220.07, 88.59) --
	(220.52, 85.21) --
	(220.96, 82.01) --
	(221.41, 79.03) --
	(221.86, 76.28) --
	(222.31, 73.77) --
	(222.76, 71.47) --
	(223.21, 69.41) --
	(223.66, 67.54) --
	(224.11, 65.86) --
	(224.55, 64.36) --
	(225.00, 63.03) --
	(225.45, 61.89) --
	(225.90, 60.92) --
	(226.35, 60.11) --
	(226.80, 59.46) --
	(227.25, 58.94) --
	(227.69, 58.55) --
	(228.14, 58.26) --
	(228.59, 58.06) --
	(229.04, 57.91) --
	(229.49, 57.82) --
	(229.94, 57.76) --
	(230.39, 57.72) --
	(230.84, 57.70) --
	(231.28, 57.69) --
	(231.73, 57.68) --
	(232.18, 57.67) --
	(232.63, 57.67) --
	(233.08, 57.67) --
	(233.53, 57.67) --
	(233.98, 57.67) --
	(234.43, 57.67) --
	(234.87, 57.67) --
	(235.32, 57.67) --
	(235.77, 57.67) --
	(236.22, 57.67) --
	(236.67, 57.67) --
	(237.12, 57.67) --
	(237.57, 57.67) --
	(238.01, 57.67) --
	(238.46, 57.67) --
	(238.91, 57.67) --
	(239.36, 57.67) --
	(239.81, 57.67) --
	(240.26, 57.67) --
	(240.71, 57.67) --
	(241.16, 57.67) --
	(241.60, 57.67) --
	(242.05, 57.67) --
	(242.50, 57.67) --
	(242.95, 57.67) --
	(243.40, 57.67) --
	(243.85, 57.67) --
	(244.30, 57.67) --
	(244.75, 57.67) --
	(245.19, 57.67) --
	(245.64, 57.67) --
	(246.09, 57.67) --
	(246.54, 57.67) --
	(246.99, 57.67) --
	(247.44, 57.67) --
	(247.89, 57.67) --
	(248.33, 57.67) --
	(248.78, 57.67) --
	(249.23, 57.67) --
	(249.68, 57.67) --
	(250.13, 57.67) --
	(250.58, 57.67) --
	(251.03, 57.67) --
	(251.48, 57.67) --
	(251.92, 57.67) --
	(252.37, 57.67) --
	(252.82, 57.67) --
	(253.27, 57.67) --
	(253.72, 57.67) --
	(254.17, 57.67) --
	(254.62, 57.67) --
	(255.07, 57.67) --
	(255.51, 57.67) --
	(255.96, 57.67) --
	(256.41, 57.67) --
	(256.86, 57.67) --
	(257.31, 57.67) --
	(257.76, 57.67) --
	(258.21, 57.67) --
	(258.65, 57.67) --
	(259.10, 57.67) --
	(259.55, 57.67) --
	(260.00, 57.67) --
	(260.45, 57.67) --
	(260.90, 57.67) --
	(261.35, 57.67) --
	(261.80, 57.67) --
	(262.24, 57.67) --
	(262.69, 57.67) --
	(263.14, 57.67) --
	(263.59, 57.67) --
	(264.04, 57.67) --
	(264.49, 57.67) --
	(264.94, 57.67) --
	(265.39, 57.67) --
	(265.83, 57.67) --
	(266.28, 57.67) --
	(266.73, 57.67) --
	(267.18, 57.67) --
	(267.63, 57.67) --
	(268.08, 57.67) --
	(268.53, 57.67) --
	(268.97, 57.67) --
	(269.42, 57.67) --
	(269.87, 57.67) --
	(270.32, 57.67) --
	(270.77, 57.67) --
	(271.22, 57.67) --
	(271.67, 57.67) --
	(272.12, 57.67);

\path[] ( 42.83, 57.70) --
	( 43.28, 57.70) --
	( 43.73, 57.71) --
	( 44.18, 57.71) --
	( 44.63, 57.71) --
	( 45.08, 57.71) --
	( 45.52, 57.71) --
	( 45.97, 57.72) --
	( 46.42, 57.72) --
	( 46.87, 57.72) --
	( 47.32, 57.73) --
	( 47.77, 57.73) --
	( 48.22, 57.74) --
	( 48.67, 57.74) --
	( 49.11, 57.75) --
	( 49.56, 57.75) --
	( 50.01, 57.76) --
	( 50.46, 57.76) --
	( 50.91, 57.77) --
	( 51.36, 57.77) --
	( 51.81, 57.77) --
	( 52.25, 57.77) --
	( 52.70, 57.77) --
	( 53.15, 57.77) --
	( 53.60, 57.77) --
	( 54.05, 57.76) --
	( 54.50, 57.76) --
	( 54.95, 57.76) --
	( 55.40, 57.77) --
	( 55.84, 57.77) --
	( 56.29, 57.77) --
	( 56.74, 57.77) --
	( 57.19, 57.78) --
	( 57.64, 57.78) --
	( 58.09, 57.79) --
	( 58.54, 57.80) --
	( 58.99, 57.80) --
	( 59.43, 57.81) --
	( 59.88, 57.82) --
	( 60.33, 57.82) --
	( 60.78, 57.83) --
	( 61.23, 57.83) --
	( 61.68, 57.84) --
	( 62.13, 57.84) --
	( 62.57, 57.85) --
	( 63.02, 57.85) --
	( 63.47, 57.86) --
	( 63.92, 57.87) --
	( 64.37, 57.87) --
	( 64.82, 57.88) --
	( 65.27, 57.88) --
	( 65.72, 57.89) --
	( 66.16, 57.89) --
	( 66.61, 57.90) --
	( 67.06, 57.90) --
	( 67.51, 57.90) --
	( 67.96, 57.90) --
	( 68.41, 57.90) --
	( 68.86, 57.90) --
	( 69.31, 57.91) --
	( 69.75, 57.91) --
	( 70.20, 57.91) --
	( 70.65, 57.92) --
	( 71.10, 57.93) --
	( 71.55, 57.94) --
	( 72.00, 57.95) --
	( 72.45, 57.96) --
	( 72.89, 57.98) --
	( 73.34, 57.99) --
	( 73.79, 58.01) --
	( 74.24, 58.03) --
	( 74.69, 58.06) --
	( 75.14, 58.08) --
	( 75.59, 58.10) --
	( 76.04, 58.12) --
	( 76.48, 58.15) --
	( 76.93, 58.17) --
	( 77.38, 58.19) --
	( 77.83, 58.20) --
	( 78.28, 58.22) --
	( 78.73, 58.23) --
	( 79.18, 58.23) --
	( 79.63, 58.24) --
	( 80.07, 58.24) --
	( 80.52, 58.24) --
	( 80.97, 58.25) --
	( 81.42, 58.25) --
	( 81.87, 58.25) --
	( 82.32, 58.25) --
	( 82.77, 58.25) --
	( 83.21, 58.26) --
	( 83.66, 58.27) --
	( 84.11, 58.29) --
	( 84.56, 58.31) --
	( 85.01, 58.34) --
	( 85.46, 58.37) --
	( 85.91, 58.40) --
	( 86.36, 58.44) --
	( 86.80, 58.48) --
	( 87.25, 58.52) --
	( 87.70, 58.56) --
	( 88.15, 58.59) --
	( 88.60, 58.63) --
	( 89.05, 58.65) --
	( 89.50, 58.68) --
	( 89.95, 58.70) --
	( 90.39, 58.71) --
	( 90.84, 58.72) --
	( 91.29, 58.73) --
	( 91.74, 58.74) --
	( 92.19, 58.75) --
	( 92.64, 58.76) --
	( 93.09, 58.78) --
	( 93.53, 58.81) --
	( 93.98, 58.84) --
	( 94.43, 58.87) --
	( 94.88, 58.91) --
	( 95.33, 58.95) --
	( 95.78, 58.99) --
	( 96.23, 59.03) --
	( 96.68, 59.07) --
	( 97.12, 59.12) --
	( 97.57, 59.16) --
	( 98.02, 59.20) --
	( 98.47, 59.25) --
	( 98.92, 59.29) --
	( 99.37, 59.33) --
	( 99.82, 59.38) --
	(100.27, 59.42) --
	(100.71, 59.46) --
	(101.16, 59.51) --
	(101.61, 59.56) --
	(102.06, 59.61) --
	(102.51, 59.67) --
	(102.96, 59.73) --
	(103.41, 59.78) --
	(103.85, 59.85) --
	(104.30, 59.91) --
	(104.75, 59.97) --
	(105.20, 60.02) --
	(105.65, 60.07) --
	(106.10, 60.11) --
	(106.55, 60.15) --
	(107.00, 60.17) --
	(107.44, 60.19) --
	(107.89, 60.19) --
	(108.34, 60.19) --
	(108.79, 60.19) --
	(109.24, 60.18) --
	(109.69, 60.17) --
	(110.14, 60.18) --
	(110.59, 60.18) --
	(111.03, 60.20) --
	(111.48, 60.23) --
	(111.93, 60.27) --
	(112.38, 60.32) --
	(112.83, 60.38) --
	(113.28, 60.45) --
	(113.73, 60.51) --
	(114.17, 60.58) --
	(114.62, 60.65) --
	(115.07, 60.71) --
	(115.52, 60.77) --
	(115.97, 60.82) --
	(116.42, 60.86) --
	(116.87, 60.90) --
	(117.32, 60.93) --
	(117.76, 60.96) --
	(118.21, 60.99) --
	(118.66, 61.03) --
	(119.11, 61.07) --
	(119.56, 61.12) --
	(120.01, 61.18) --
	(120.46, 61.25) --
	(120.91, 61.32) --
	(121.35, 61.40) --
	(121.80, 61.48) --
	(122.25, 61.56) --
	(122.70, 61.64) --
	(123.15, 61.72) --
	(123.60, 61.80) --
	(124.05, 61.87) --
	(124.49, 61.94) --
	(124.94, 62.01) --
	(125.39, 62.07) --
	(125.84, 62.13) --
	(126.29, 62.20) --
	(126.74, 62.26) --
	(127.19, 62.32) --
	(127.64, 62.39) --
	(128.08, 62.45) --
	(128.53, 62.52) --
	(128.98, 62.59) --
	(129.43, 62.66) --
	(129.88, 62.74) --
	(130.33, 62.81) --
	(130.78, 62.89) --
	(131.23, 62.96) --
	(131.67, 63.04) --
	(132.12, 63.11) --
	(132.57, 63.18) --
	(133.02, 63.25) --
	(133.47, 63.32) --
	(133.92, 63.38) --
	(134.37, 63.44) --
	(134.81, 63.50) --
	(135.26, 63.55) --
	(135.71, 63.62) --
	(136.16, 63.69) --
	(136.61, 63.76) --
	(137.06, 63.85) --
	(137.51, 63.95) --
	(137.96, 64.05) --
	(138.40, 64.17) --
	(138.85, 64.30) --
	(139.30, 64.43) --
	(139.75, 64.57) --
	(140.20, 64.71) --
	(140.65, 64.86) --
	(141.10, 65.00) --
	(141.55, 65.15) --
	(141.99, 65.30) --
	(142.44, 65.45) --
	(142.89, 65.60) --
	(143.34, 65.76) --
	(143.79, 65.92) --
	(144.24, 66.09) --
	(144.69, 66.26) --
	(145.13, 66.44) --
	(145.58, 66.62) --
	(146.03, 66.81) --
	(146.48, 67.01) --
	(146.93, 67.21) --
	(147.38, 67.41) --
	(147.83, 67.62) --
	(148.28, 67.82) --
	(148.72, 68.03) --
	(149.17, 68.23) --
	(149.62, 68.42) --
	(150.07, 68.61) --
	(150.52, 68.79) --
	(150.97, 68.96) --
	(151.42, 69.13) --
	(151.87, 69.30) --
	(152.31, 69.47) --
	(152.76, 69.65) --
	(153.21, 69.85) --
	(153.66, 70.07) --
	(154.11, 70.32) --
	(154.56, 70.61) --
	(155.01, 70.93) --
	(155.45, 71.29) --
	(155.90, 71.69) --
	(156.35, 72.13) --
	(156.80, 72.61) --
	(157.25, 73.11) --
	(157.70, 73.64) --
	(158.15, 74.17) --
	(158.60, 74.71) --
	(159.04, 75.24) --
	(159.49, 75.76) --
	(159.94, 76.24) --
	(160.39, 76.70) --
	(160.84, 77.12) --
	(161.29, 77.51) --
	(161.74, 77.85) --
	(162.19, 78.17) --
	(162.63, 78.46) --
	(163.08, 78.72) --
	(163.53, 78.98) --
	(163.98, 79.23) --
	(164.43, 79.49) --
	(164.88, 79.75) --
	(165.33, 80.04) --
	(165.77, 80.35) --
	(166.22, 80.68) --
	(166.67, 81.04) --
	(167.12, 81.42) --
	(167.57, 81.83) --
	(168.02, 82.26) --
	(168.47, 82.72) --
	(168.92, 83.20) --
	(169.36, 83.71) --
	(169.81, 84.24) --
	(170.26, 84.79) --
	(170.71, 85.37) --
	(171.16, 85.96) --
	(171.61, 86.58) --
	(172.06, 87.21) --
	(172.51, 87.86) --
	(172.95, 88.54) --
	(173.40, 89.23) --
	(173.85, 89.94) --
	(174.30, 90.67) --
	(174.75, 91.43) --
	(175.20, 92.21) --
	(175.65, 93.02) --
	(176.09, 93.87) --
	(176.54, 94.74) --
	(176.99, 95.65) --
	(177.44, 96.59) --
	(177.89, 97.55) --
	(178.34, 98.54) --
	(178.79, 99.54) --
	(179.24,100.53) --
	(179.68,101.52) --
	(180.13,102.48) --
	(180.58,103.41) --
	(181.03,104.31) --
	(181.48,105.18) --
	(181.93,106.03) --
	(182.38,106.86) --
	(182.83,107.68) --
	(183.27,108.52) --
	(183.72,109.40) --
	(184.17,110.33) --
	(184.62,111.31) --
	(185.07,112.38) --
	(185.52,113.52) --
	(185.97,114.73) --
	(186.41,116.03) --
	(186.86,117.38) --
	(187.31,118.80) --
	(187.76,120.26) --
	(188.21,121.74) --
	(188.66,123.24) --
	(189.11,124.74) --
	(189.56,126.22) --
	(190.00,127.67) --
	(190.45,129.10) --
	(190.90,130.47) --
	(191.35,131.80) --
	(191.80,133.05) --
	(192.25,134.23) --
	(192.70,135.33) --
	(193.15,136.32) --
	(193.59,137.20) --
	(194.04,137.96) --
	(194.49,138.59) --
	(194.94,139.09) --
	(195.39,139.47) --
	(195.84,139.74) --
	(196.29,139.90) --
	(196.73,139.95) --
	(197.18,139.91) --
	(197.63,139.78) --
	(198.08,139.56) --
	(198.53,139.28) --
	(198.98,138.91) --
	(199.43,138.48) --
	(199.88,137.97) --
	(200.32,137.40) --
	(200.77,136.76) --
	(201.22,136.05) --
	(201.67,135.29) --
	(202.12,134.47) --
	(202.57,133.60) --
	(203.02,132.69) --
	(203.47,131.73) --
	(203.91,130.74) --
	(204.36,129.72) --
	(204.81,128.68) --
	(205.26,127.62) --
	(205.71,126.55) --
	(206.16,125.46) --
	(206.61,124.38) --
	(207.05,123.29) --
	(207.50,122.22) --
	(207.95,121.17) --
	(208.40,120.15) --
	(208.85,119.18) --
	(209.30,118.27) --
	(209.75,117.43) --
	(210.20,116.66) --
	(210.64,115.97) --
	(211.09,115.36) --
	(211.54,114.82) --
	(211.99,114.34) --
	(212.44,113.91) --
	(212.89,113.53) --
	(213.34,113.16) --
	(213.79,112.81) --
	(214.23,112.44) --
	(214.68,112.06) --
	(215.13,111.65) --
	(215.58,111.21) --
	(216.03,110.74) --
	(216.48,110.24) --
	(216.93,109.72) --
	(217.37,109.19) --
	(217.82,108.65) --
	(218.27,108.11) --
	(218.72,107.59) --
	(219.17,107.07) --
	(219.62,106.58) --
	(220.07,106.10) --
	(220.52,105.63) --
	(220.96,105.17) --
	(221.41,104.70) --
	(221.86,104.23) --
	(222.31,103.75) --
	(222.76,103.25) --
	(223.21,102.72) --
	(223.66,102.17) --
	(224.11,101.59) --
	(224.55,100.98) --
	(225.00,100.33) --
	(225.45, 99.65) --
	(225.90, 98.94) --
	(226.35, 98.20) --
	(226.80, 97.44) --
	(227.25, 96.65) --
	(227.69, 95.85) --
	(228.14, 95.03) --
	(228.59, 94.20) --
	(229.04, 93.36) --
	(229.49, 92.52) --
	(229.94, 91.68) --
	(230.39, 90.84) --
	(230.84, 90.00) --
	(231.28, 89.17) --
	(231.73, 88.35) --
	(232.18, 87.53) --
	(232.63, 86.72) --
	(233.08, 85.93) --
	(233.53, 85.14) --
	(233.98, 84.36) --
	(234.43, 83.60) --
	(234.87, 82.84) --
	(235.32, 82.08) --
	(235.77, 81.33) --
	(236.22, 80.59) --
	(236.67, 79.85) --
	(237.12, 79.11) --
	(237.57, 78.38) --
	(238.01, 77.66) --
	(238.46, 76.95) --
	(238.91, 76.26) --
	(239.36, 75.59) --
	(239.81, 74.94) --
	(240.26, 74.31) --
	(240.71, 73.71) --
	(241.16, 73.14) --
	(241.60, 72.58) --
	(242.05, 72.05) --
	(242.50, 71.54) --
	(242.95, 71.05) --
	(243.40, 70.59) --
	(243.85, 70.14) --
	(244.30, 69.70) --
	(244.75, 69.29) --
	(245.19, 68.89) --
	(245.64, 68.51) --
	(246.09, 68.14) --
	(246.54, 67.79) --
	(246.99, 67.45) --
	(247.44, 67.13) --
	(247.89, 66.82) --
	(248.33, 66.52) --
	(248.78, 66.23) --
	(249.23, 65.96) --
	(249.68, 65.69) --
	(250.13, 65.43) --
	(250.58, 65.17) --
	(251.03, 64.91) --
	(251.48, 64.64) --
	(251.92, 64.37) --
	(252.37, 64.09) --
	(252.82, 63.79) --
	(253.27, 63.48) --
	(253.72, 63.16) --
	(254.17, 62.83) --
	(254.62, 62.50) --
	(255.07, 62.16) --
	(255.51, 61.82) --
	(255.96, 61.49) --
	(256.41, 61.17) --
	(256.86, 60.86) --
	(257.31, 60.57) --
	(257.76, 60.30) --
	(258.21, 60.04) --
	(258.65, 59.81) --
	(259.10, 59.60) --
	(259.55, 59.41) --
	(260.00, 59.23) --
	(260.45, 59.08) --
	(260.90, 58.94) --
	(261.35, 58.81) --
	(261.80, 58.71) --
	(262.24, 58.61) --
	(262.69, 58.53) --
	(263.14, 58.47) --
	(263.59, 58.41) --
	(264.04, 58.37) --
	(264.49, 58.33) --
	(264.94, 58.31) --
	(265.39, 58.29) --
	(265.83, 58.28) --
	(266.28, 58.27) --
	(266.73, 58.27) --
	(267.18, 58.27) --
	(267.63, 58.26) --
	(268.08, 58.25) --
	(268.53, 58.24) --
	(268.97, 58.22) --
	(269.42, 58.20) --
	(269.87, 58.17) --
	(270.32, 58.14) --
	(270.77, 58.10) --
	(271.22, 58.06) --
	(271.67, 58.02) --
	(272.12, 57.97) --
	(272.12, 57.67) --
	(271.67, 57.67) --
	(271.22, 57.67) --
	(270.77, 57.67) --
	(270.32, 57.67) --
	(269.87, 57.67) --
	(269.42, 57.67) --
	(268.97, 57.67) --
	(268.53, 57.67) --
	(268.08, 57.67) --
	(267.63, 57.67) --
	(267.18, 57.67) --
	(266.73, 57.67) --
	(266.28, 57.67) --
	(265.83, 57.67) --
	(265.39, 57.67) --
	(264.94, 57.67) --
	(264.49, 57.67) --
	(264.04, 57.67) --
	(263.59, 57.67) --
	(263.14, 57.67) --
	(262.69, 57.67) --
	(262.24, 57.67) --
	(261.80, 57.67) --
	(261.35, 57.67) --
	(260.90, 57.67) --
	(260.45, 57.67) --
	(260.00, 57.67) --
	(259.55, 57.67) --
	(259.10, 57.67) --
	(258.65, 57.67) --
	(258.21, 57.67) --
	(257.76, 57.67) --
	(257.31, 57.67) --
	(256.86, 57.67) --
	(256.41, 57.67) --
	(255.96, 57.67) --
	(255.51, 57.67) --
	(255.07, 57.67) --
	(254.62, 57.67) --
	(254.17, 57.67) --
	(253.72, 57.67) --
	(253.27, 57.67) --
	(252.82, 57.67) --
	(252.37, 57.67) --
	(251.92, 57.67) --
	(251.48, 57.67) --
	(251.03, 57.67) --
	(250.58, 57.67) --
	(250.13, 57.67) --
	(249.68, 57.67) --
	(249.23, 57.67) --
	(248.78, 57.67) --
	(248.33, 57.67) --
	(247.89, 57.67) --
	(247.44, 57.67) --
	(246.99, 57.67) --
	(246.54, 57.67) --
	(246.09, 57.67) --
	(245.64, 57.67) --
	(245.19, 57.67) --
	(244.75, 57.67) --
	(244.30, 57.67) --
	(243.85, 57.67) --
	(243.40, 57.67) --
	(242.95, 57.67) --
	(242.50, 57.67) --
	(242.05, 57.67) --
	(241.60, 57.67) --
	(241.16, 57.67) --
	(240.71, 57.67) --
	(240.26, 57.67) --
	(239.81, 57.67) --
	(239.36, 57.67) --
	(238.91, 57.67) --
	(238.46, 57.67) --
	(238.01, 57.67) --
	(237.57, 57.67) --
	(237.12, 57.67) --
	(236.67, 57.67) --
	(236.22, 57.67) --
	(235.77, 57.67) --
	(235.32, 57.67) --
	(234.87, 57.67) --
	(234.43, 57.67) --
	(233.98, 57.67) --
	(233.53, 57.67) --
	(233.08, 57.67) --
	(232.63, 57.67) --
	(232.18, 57.67) --
	(231.73, 57.67) --
	(231.28, 57.67) --
	(230.84, 57.67) --
	(230.39, 57.67) --
	(229.94, 57.67) --
	(229.49, 57.67) --
	(229.04, 57.67) --
	(228.59, 57.67) --
	(228.14, 57.67) --
	(227.69, 57.67) --
	(227.25, 57.67) --
	(226.80, 57.67) --
	(226.35, 57.67) --
	(225.90, 57.67) --
	(225.45, 57.67) --
	(225.00, 57.67) --
	(224.55, 57.67) --
	(224.11, 57.67) --
	(223.66, 57.67) --
	(223.21, 57.67) --
	(222.76, 57.67) --
	(222.31, 57.67) --
	(221.86, 57.67) --
	(221.41, 57.67) --
	(220.96, 57.67) --
	(220.52, 57.67) --
	(220.07, 57.67) --
	(219.62, 57.67) --
	(219.17, 57.67) --
	(218.72, 57.67) --
	(218.27, 57.67) --
	(217.82, 57.67) --
	(217.37, 57.67) --
	(216.93, 57.67) --
	(216.48, 57.67) --
	(216.03, 57.67) --
	(215.58, 57.67) --
	(215.13, 57.67) --
	(214.68, 57.67) --
	(214.23, 57.67) --
	(213.79, 57.67) --
	(213.34, 57.67) --
	(212.89, 57.67) --
	(212.44, 57.67) --
	(211.99, 57.67) --
	(211.54, 57.67) --
	(211.09, 57.67) --
	(210.64, 57.67) --
	(210.20, 57.67) --
	(209.75, 57.67) --
	(209.30, 57.67) --
	(208.85, 57.67) --
	(208.40, 57.67) --
	(207.95, 57.67) --
	(207.50, 57.67) --
	(207.05, 57.67) --
	(206.61, 57.67) --
	(206.16, 57.67) --
	(205.71, 57.67) --
	(205.26, 57.67) --
	(204.81, 57.67) --
	(204.36, 57.67) --
	(203.91, 57.67) --
	(203.47, 57.67) --
	(203.02, 57.67) --
	(202.57, 57.67) --
	(202.12, 57.67) --
	(201.67, 57.67) --
	(201.22, 57.67) --
	(200.77, 57.67) --
	(200.32, 57.67) --
	(199.88, 57.67) --
	(199.43, 57.67) --
	(198.98, 57.67) --
	(198.53, 57.67) --
	(198.08, 57.67) --
	(197.63, 57.67) --
	(197.18, 57.67) --
	(196.73, 57.67) --
	(196.29, 57.67) --
	(195.84, 57.67) --
	(195.39, 57.67) --
	(194.94, 57.67) --
	(194.49, 57.67) --
	(194.04, 57.67) --
	(193.59, 57.67) --
	(193.15, 57.67) --
	(192.70, 57.67) --
	(192.25, 57.67) --
	(191.80, 57.67) --
	(191.35, 57.67) --
	(190.90, 57.67) --
	(190.45, 57.67) --
	(190.00, 57.67) --
	(189.56, 57.67) --
	(189.11, 57.67) --
	(188.66, 57.67) --
	(188.21, 57.67) --
	(187.76, 57.67) --
	(187.31, 57.67) --
	(186.86, 57.67) --
	(186.41, 57.67) --
	(185.97, 57.67) --
	(185.52, 57.67) --
	(185.07, 57.67) --
	(184.62, 57.67) --
	(184.17, 57.67) --
	(183.72, 57.67) --
	(183.27, 57.67) --
	(182.83, 57.67) --
	(182.38, 57.67) --
	(181.93, 57.67) --
	(181.48, 57.67) --
	(181.03, 57.67) --
	(180.58, 57.67) --
	(180.13, 57.67) --
	(179.68, 57.67) --
	(179.24, 57.67) --
	(178.79, 57.67) --
	(178.34, 57.67) --
	(177.89, 57.67) --
	(177.44, 57.67) --
	(176.99, 57.67) --
	(176.54, 57.67) --
	(176.09, 57.67) --
	(175.65, 57.67) --
	(175.20, 57.67) --
	(174.75, 57.67) --
	(174.30, 57.67) --
	(173.85, 57.67) --
	(173.40, 57.67) --
	(172.95, 57.67) --
	(172.51, 57.67) --
	(172.06, 57.67) --
	(171.61, 57.67) --
	(171.16, 57.67) --
	(170.71, 57.67) --
	(170.26, 57.67) --
	(169.81, 57.67) --
	(169.36, 57.67) --
	(168.92, 57.67) --
	(168.47, 57.67) --
	(168.02, 57.67) --
	(167.57, 57.67) --
	(167.12, 57.67) --
	(166.67, 57.67) --
	(166.22, 57.67) --
	(165.77, 57.67) --
	(165.33, 57.67) --
	(164.88, 57.67) --
	(164.43, 57.67) --
	(163.98, 57.67) --
	(163.53, 57.67) --
	(163.08, 57.67) --
	(162.63, 57.67) --
	(162.19, 57.67) --
	(161.74, 57.67) --
	(161.29, 57.67) --
	(160.84, 57.67) --
	(160.39, 57.67) --
	(159.94, 57.67) --
	(159.49, 57.67) --
	(159.04, 57.67) --
	(158.60, 57.67) --
	(158.15, 57.67) --
	(157.70, 57.67) --
	(157.25, 57.67) --
	(156.80, 57.67) --
	(156.35, 57.67) --
	(155.90, 57.67) --
	(155.45, 57.67) --
	(155.01, 57.67) --
	(154.56, 57.67) --
	(154.11, 57.67) --
	(153.66, 57.67) --
	(153.21, 57.67) --
	(152.76, 57.67) --
	(152.31, 57.67) --
	(151.87, 57.67) --
	(151.42, 57.67) --
	(150.97, 57.67) --
	(150.52, 57.67) --
	(150.07, 57.67) --
	(149.62, 57.67) --
	(149.17, 57.67) --
	(148.72, 57.67) --
	(148.28, 57.67) --
	(147.83, 57.67) --
	(147.38, 57.67) --
	(146.93, 57.67) --
	(146.48, 57.67) --
	(146.03, 57.67) --
	(145.58, 57.67) --
	(145.13, 57.67) --
	(144.69, 57.67) --
	(144.24, 57.67) --
	(143.79, 57.67) --
	(143.34, 57.67) --
	(142.89, 57.67) --
	(142.44, 57.67) --
	(141.99, 57.67) --
	(141.55, 57.67) --
	(141.10, 57.67) --
	(140.65, 57.67) --
	(140.20, 57.67) --
	(139.75, 57.67) --
	(139.30, 57.67) --
	(138.85, 57.67) --
	(138.40, 57.67) --
	(137.96, 57.67) --
	(137.51, 57.67) --
	(137.06, 57.67) --
	(136.61, 57.67) --
	(136.16, 57.67) --
	(135.71, 57.67) --
	(135.26, 57.67) --
	(134.81, 57.67) --
	(134.37, 57.67) --
	(133.92, 57.67) --
	(133.47, 57.67) --
	(133.02, 57.67) --
	(132.57, 57.67) --
	(132.12, 57.67) --
	(131.67, 57.67) --
	(131.23, 57.67) --
	(130.78, 57.67) --
	(130.33, 57.67) --
	(129.88, 57.67) --
	(129.43, 57.67) --
	(128.98, 57.67) --
	(128.53, 57.67) --
	(128.08, 57.67) --
	(127.64, 57.67) --
	(127.19, 57.67) --
	(126.74, 57.67) --
	(126.29, 57.67) --
	(125.84, 57.67) --
	(125.39, 57.67) --
	(124.94, 57.67) --
	(124.49, 57.67) --
	(124.05, 57.67) --
	(123.60, 57.67) --
	(123.15, 57.67) --
	(122.70, 57.67) --
	(122.25, 57.67) --
	(121.80, 57.67) --
	(121.35, 57.67) --
	(120.91, 57.67) --
	(120.46, 57.67) --
	(120.01, 57.67) --
	(119.56, 57.67) --
	(119.11, 57.67) --
	(118.66, 57.67) --
	(118.21, 57.67) --
	(117.76, 57.67) --
	(117.32, 57.67) --
	(116.87, 57.67) --
	(116.42, 57.67) --
	(115.97, 57.67) --
	(115.52, 57.67) --
	(115.07, 57.67) --
	(114.62, 57.67) --
	(114.17, 57.67) --
	(113.73, 57.67) --
	(113.28, 57.67) --
	(112.83, 57.67) --
	(112.38, 57.67) --
	(111.93, 57.67) --
	(111.48, 57.67) --
	(111.03, 57.67) --
	(110.59, 57.67) --
	(110.14, 57.67) --
	(109.69, 57.67) --
	(109.24, 57.67) --
	(108.79, 57.67) --
	(108.34, 57.67) --
	(107.89, 57.67) --
	(107.44, 57.67) --
	(107.00, 57.67) --
	(106.55, 57.67) --
	(106.10, 57.67) --
	(105.65, 57.67) --
	(105.20, 57.67) --
	(104.75, 57.67) --
	(104.30, 57.67) --
	(103.85, 57.67) --
	(103.41, 57.67) --
	(102.96, 57.67) --
	(102.51, 57.67) --
	(102.06, 57.67) --
	(101.61, 57.67) --
	(101.16, 57.67) --
	(100.71, 57.67) --
	(100.27, 57.67) --
	( 99.82, 57.67) --
	( 99.37, 57.67) --
	( 98.92, 57.67) --
	( 98.47, 57.67) --
	( 98.02, 57.67) --
	( 97.57, 57.67) --
	( 97.12, 57.67) --
	( 96.68, 57.67) --
	( 96.23, 57.67) --
	( 95.78, 57.67) --
	( 95.33, 57.67) --
	( 94.88, 57.67) --
	( 94.43, 57.67) --
	( 93.98, 57.67) --
	( 93.53, 57.67) --
	( 93.09, 57.67) --
	( 92.64, 57.67) --
	( 92.19, 57.67) --
	( 91.74, 57.67) --
	( 91.29, 57.67) --
	( 90.84, 57.67) --
	( 90.39, 57.67) --
	( 89.95, 57.67) --
	( 89.50, 57.67) --
	( 89.05, 57.67) --
	( 88.60, 57.67) --
	( 88.15, 57.67) --
	( 87.70, 57.67) --
	( 87.25, 57.67) --
	( 86.80, 57.67) --
	( 86.36, 57.67) --
	( 85.91, 57.67) --
	( 85.46, 57.67) --
	( 85.01, 57.67) --
	( 84.56, 57.67) --
	( 84.11, 57.67) --
	( 83.66, 57.67) --
	( 83.21, 57.67) --
	( 82.77, 57.67) --
	( 82.32, 57.67) --
	( 81.87, 57.67) --
	( 81.42, 57.67) --
	( 80.97, 57.67) --
	( 80.52, 57.67) --
	( 80.07, 57.67) --
	( 79.63, 57.67) --
	( 79.18, 57.67) --
	( 78.73, 57.67) --
	( 78.28, 57.67) --
	( 77.83, 57.67) --
	( 77.38, 57.67) --
	( 76.93, 57.67) --
	( 76.48, 57.67) --
	( 76.04, 57.67) --
	( 75.59, 57.67) --
	( 75.14, 57.67) --
	( 74.69, 57.67) --
	( 74.24, 57.67) --
	( 73.79, 57.67) --
	( 73.34, 57.67) --
	( 72.89, 57.67) --
	( 72.45, 57.67) --
	( 72.00, 57.67) --
	( 71.55, 57.67) --
	( 71.10, 57.67) --
	( 70.65, 57.67) --
	( 70.20, 57.67) --
	( 69.75, 57.67) --
	( 69.31, 57.67) --
	( 68.86, 57.67) --
	( 68.41, 57.67) --
	( 67.96, 57.67) --
	( 67.51, 57.67) --
	( 67.06, 57.67) --
	( 66.61, 57.67) --
	( 66.16, 57.67) --
	( 65.72, 57.67) --
	( 65.27, 57.67) --
	( 64.82, 57.67) --
	( 64.37, 57.67) --
	( 63.92, 57.67) --
	( 63.47, 57.67) --
	( 63.02, 57.67) --
	( 62.57, 57.67) --
	( 62.13, 57.67) --
	( 61.68, 57.67) --
	( 61.23, 57.67) --
	( 60.78, 57.67) --
	( 60.33, 57.67) --
	( 59.88, 57.67) --
	( 59.43, 57.67) --
	( 58.99, 57.67) --
	( 58.54, 57.67) --
	( 58.09, 57.67) --
	( 57.64, 57.67) --
	( 57.19, 57.67) --
	( 56.74, 57.67) --
	( 56.29, 57.67) --
	( 55.84, 57.67) --
	( 55.40, 57.67) --
	( 54.95, 57.67) --
	( 54.50, 57.67) --
	( 54.05, 57.67) --
	( 53.60, 57.67) --
	( 53.15, 57.67) --
	( 52.70, 57.67) --
	( 52.25, 57.67) --
	( 51.81, 57.67) --
	( 51.36, 57.67) --
	( 50.91, 57.67) --
	( 50.46, 57.67) --
	( 50.01, 57.67) --
	( 49.56, 57.67) --
	( 49.11, 57.67) --
	( 48.67, 57.67) --
	( 48.22, 57.67) --
	( 47.77, 57.67) --
	( 47.32, 57.67) --
	( 46.87, 57.67) --
	( 46.42, 57.67) --
	( 45.97, 57.67) --
	( 45.52, 57.67) --
	( 45.08, 57.67) --
	( 44.63, 57.67) --
	( 44.18, 57.67) --
	( 43.73, 57.67) --
	( 43.28, 57.67) --
	( 42.83, 57.67) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 42.83, 57.70) --
	( 43.28, 57.70) --
	( 43.73, 57.71) --
	( 44.18, 57.71) --
	( 44.63, 57.71) --
	( 45.08, 57.71) --
	( 45.52, 57.71) --
	( 45.97, 57.72) --
	( 46.42, 57.72) --
	( 46.87, 57.72) --
	( 47.32, 57.73) --
	( 47.77, 57.73) --
	( 48.22, 57.74) --
	( 48.67, 57.74) --
	( 49.11, 57.75) --
	( 49.56, 57.75) --
	( 50.01, 57.76) --
	( 50.46, 57.76) --
	( 50.91, 57.77) --
	( 51.36, 57.77) --
	( 51.81, 57.77) --
	( 52.25, 57.77) --
	( 52.70, 57.77) --
	( 53.15, 57.77) --
	( 53.60, 57.77) --
	( 54.05, 57.76) --
	( 54.50, 57.76) --
	( 54.95, 57.76) --
	( 55.40, 57.77) --
	( 55.84, 57.77) --
	( 56.29, 57.77) --
	( 56.74, 57.77) --
	( 57.19, 57.78) --
	( 57.64, 57.78) --
	( 58.09, 57.79) --
	( 58.54, 57.80) --
	( 58.99, 57.80) --
	( 59.43, 57.81) --
	( 59.88, 57.82) --
	( 60.33, 57.82) --
	( 60.78, 57.83) --
	( 61.23, 57.83) --
	( 61.68, 57.84) --
	( 62.13, 57.84) --
	( 62.57, 57.85) --
	( 63.02, 57.85) --
	( 63.47, 57.86) --
	( 63.92, 57.87) --
	( 64.37, 57.87) --
	( 64.82, 57.88) --
	( 65.27, 57.88) --
	( 65.72, 57.89) --
	( 66.16, 57.89) --
	( 66.61, 57.90) --
	( 67.06, 57.90) --
	( 67.51, 57.90) --
	( 67.96, 57.90) --
	( 68.41, 57.90) --
	( 68.86, 57.90) --
	( 69.31, 57.91) --
	( 69.75, 57.91) --
	( 70.20, 57.91) --
	( 70.65, 57.92) --
	( 71.10, 57.93) --
	( 71.55, 57.94) --
	( 72.00, 57.95) --
	( 72.45, 57.96) --
	( 72.89, 57.98) --
	( 73.34, 57.99) --
	( 73.79, 58.01) --
	( 74.24, 58.03) --
	( 74.69, 58.06) --
	( 75.14, 58.08) --
	( 75.59, 58.10) --
	( 76.04, 58.12) --
	( 76.48, 58.15) --
	( 76.93, 58.17) --
	( 77.38, 58.19) --
	( 77.83, 58.20) --
	( 78.28, 58.22) --
	( 78.73, 58.23) --
	( 79.18, 58.23) --
	( 79.63, 58.24) --
	( 80.07, 58.24) --
	( 80.52, 58.24) --
	( 80.97, 58.25) --
	( 81.42, 58.25) --
	( 81.87, 58.25) --
	( 82.32, 58.25) --
	( 82.77, 58.25) --
	( 83.21, 58.26) --
	( 83.66, 58.27) --
	( 84.11, 58.29) --
	( 84.56, 58.31) --
	( 85.01, 58.34) --
	( 85.46, 58.37) --
	( 85.91, 58.40) --
	( 86.36, 58.44) --
	( 86.80, 58.48) --
	( 87.25, 58.52) --
	( 87.70, 58.56) --
	( 88.15, 58.59) --
	( 88.60, 58.63) --
	( 89.05, 58.65) --
	( 89.50, 58.68) --
	( 89.95, 58.70) --
	( 90.39, 58.71) --
	( 90.84, 58.72) --
	( 91.29, 58.73) --
	( 91.74, 58.74) --
	( 92.19, 58.75) --
	( 92.64, 58.76) --
	( 93.09, 58.78) --
	( 93.53, 58.81) --
	( 93.98, 58.84) --
	( 94.43, 58.87) --
	( 94.88, 58.91) --
	( 95.33, 58.95) --
	( 95.78, 58.99) --
	( 96.23, 59.03) --
	( 96.68, 59.07) --
	( 97.12, 59.12) --
	( 97.57, 59.16) --
	( 98.02, 59.20) --
	( 98.47, 59.25) --
	( 98.92, 59.29) --
	( 99.37, 59.33) --
	( 99.82, 59.38) --
	(100.27, 59.42) --
	(100.71, 59.46) --
	(101.16, 59.51) --
	(101.61, 59.56) --
	(102.06, 59.61) --
	(102.51, 59.67) --
	(102.96, 59.73) --
	(103.41, 59.78) --
	(103.85, 59.85) --
	(104.30, 59.91) --
	(104.75, 59.97) --
	(105.20, 60.02) --
	(105.65, 60.07) --
	(106.10, 60.11) --
	(106.55, 60.15) --
	(107.00, 60.17) --
	(107.44, 60.19) --
	(107.89, 60.19) --
	(108.34, 60.19) --
	(108.79, 60.19) --
	(109.24, 60.18) --
	(109.69, 60.17) --
	(110.14, 60.18) --
	(110.59, 60.18) --
	(111.03, 60.20) --
	(111.48, 60.23) --
	(111.93, 60.27) --
	(112.38, 60.32) --
	(112.83, 60.38) --
	(113.28, 60.45) --
	(113.73, 60.51) --
	(114.17, 60.58) --
	(114.62, 60.65) --
	(115.07, 60.71) --
	(115.52, 60.77) --
	(115.97, 60.82) --
	(116.42, 60.86) --
	(116.87, 60.90) --
	(117.32, 60.93) --
	(117.76, 60.96) --
	(118.21, 60.99) --
	(118.66, 61.03) --
	(119.11, 61.07) --
	(119.56, 61.12) --
	(120.01, 61.18) --
	(120.46, 61.25) --
	(120.91, 61.32) --
	(121.35, 61.40) --
	(121.80, 61.48) --
	(122.25, 61.56) --
	(122.70, 61.64) --
	(123.15, 61.72) --
	(123.60, 61.80) --
	(124.05, 61.87) --
	(124.49, 61.94) --
	(124.94, 62.01) --
	(125.39, 62.07) --
	(125.84, 62.13) --
	(126.29, 62.20) --
	(126.74, 62.26) --
	(127.19, 62.32) --
	(127.64, 62.39) --
	(128.08, 62.45) --
	(128.53, 62.52) --
	(128.98, 62.59) --
	(129.43, 62.66) --
	(129.88, 62.74) --
	(130.33, 62.81) --
	(130.78, 62.89) --
	(131.23, 62.96) --
	(131.67, 63.04) --
	(132.12, 63.11) --
	(132.57, 63.18) --
	(133.02, 63.25) --
	(133.47, 63.32) --
	(133.92, 63.38) --
	(134.37, 63.44) --
	(134.81, 63.50) --
	(135.26, 63.55) --
	(135.71, 63.62) --
	(136.16, 63.69) --
	(136.61, 63.76) --
	(137.06, 63.85) --
	(137.51, 63.95) --
	(137.96, 64.05) --
	(138.40, 64.17) --
	(138.85, 64.30) --
	(139.30, 64.43) --
	(139.75, 64.57) --
	(140.20, 64.71) --
	(140.65, 64.86) --
	(141.10, 65.00) --
	(141.55, 65.15) --
	(141.99, 65.30) --
	(142.44, 65.45) --
	(142.89, 65.60) --
	(143.34, 65.76) --
	(143.79, 65.92) --
	(144.24, 66.09) --
	(144.69, 66.26) --
	(145.13, 66.44) --
	(145.58, 66.62) --
	(146.03, 66.81) --
	(146.48, 67.01) --
	(146.93, 67.21) --
	(147.38, 67.41) --
	(147.83, 67.62) --
	(148.28, 67.82) --
	(148.72, 68.03) --
	(149.17, 68.23) --
	(149.62, 68.42) --
	(150.07, 68.61) --
	(150.52, 68.79) --
	(150.97, 68.96) --
	(151.42, 69.13) --
	(151.87, 69.30) --
	(152.31, 69.47) --
	(152.76, 69.65) --
	(153.21, 69.85) --
	(153.66, 70.07) --
	(154.11, 70.32) --
	(154.56, 70.61) --
	(155.01, 70.93) --
	(155.45, 71.29) --
	(155.90, 71.69) --
	(156.35, 72.13) --
	(156.80, 72.61) --
	(157.25, 73.11) --
	(157.70, 73.64) --
	(158.15, 74.17) --
	(158.60, 74.71) --
	(159.04, 75.24) --
	(159.49, 75.76) --
	(159.94, 76.24) --
	(160.39, 76.70) --
	(160.84, 77.12) --
	(161.29, 77.51) --
	(161.74, 77.85) --
	(162.19, 78.17) --
	(162.63, 78.46) --
	(163.08, 78.72) --
	(163.53, 78.98) --
	(163.98, 79.23) --
	(164.43, 79.49) --
	(164.88, 79.75) --
	(165.33, 80.04) --
	(165.77, 80.35) --
	(166.22, 80.68) --
	(166.67, 81.04) --
	(167.12, 81.42) --
	(167.57, 81.83) --
	(168.02, 82.26) --
	(168.47, 82.72) --
	(168.92, 83.20) --
	(169.36, 83.71) --
	(169.81, 84.24) --
	(170.26, 84.79) --
	(170.71, 85.37) --
	(171.16, 85.96) --
	(171.61, 86.58) --
	(172.06, 87.21) --
	(172.51, 87.86) --
	(172.95, 88.54) --
	(173.40, 89.23) --
	(173.85, 89.94) --
	(174.30, 90.67) --
	(174.75, 91.43) --
	(175.20, 92.21) --
	(175.65, 93.02) --
	(176.09, 93.87) --
	(176.54, 94.74) --
	(176.99, 95.65) --
	(177.44, 96.59) --
	(177.89, 97.55) --
	(178.34, 98.54) --
	(178.79, 99.54) --
	(179.24,100.53) --
	(179.68,101.52) --
	(180.13,102.48) --
	(180.58,103.41) --
	(181.03,104.31) --
	(181.48,105.18) --
	(181.93,106.03) --
	(182.38,106.86) --
	(182.83,107.68) --
	(183.27,108.52) --
	(183.72,109.40) --
	(184.17,110.33) --
	(184.62,111.31) --
	(185.07,112.38) --
	(185.52,113.52) --
	(185.97,114.73) --
	(186.41,116.03) --
	(186.86,117.38) --
	(187.31,118.80) --
	(187.76,120.26) --
	(188.21,121.74) --
	(188.66,123.24) --
	(189.11,124.74) --
	(189.56,126.22) --
	(190.00,127.67) --
	(190.45,129.10) --
	(190.90,130.47) --
	(191.35,131.80) --
	(191.80,133.05) --
	(192.25,134.23) --
	(192.70,135.33) --
	(193.15,136.32) --
	(193.59,137.20) --
	(194.04,137.96) --
	(194.49,138.59) --
	(194.94,139.09) --
	(195.39,139.47) --
	(195.84,139.74) --
	(196.29,139.90) --
	(196.73,139.95) --
	(197.18,139.91) --
	(197.63,139.78) --
	(198.08,139.56) --
	(198.53,139.28) --
	(198.98,138.91) --
	(199.43,138.48) --
	(199.88,137.97) --
	(200.32,137.40) --
	(200.77,136.76) --
	(201.22,136.05) --
	(201.67,135.29) --
	(202.12,134.47) --
	(202.57,133.60) --
	(203.02,132.69) --
	(203.47,131.73) --
	(203.91,130.74) --
	(204.36,129.72) --
	(204.81,128.68) --
	(205.26,127.62) --
	(205.71,126.55) --
	(206.16,125.46) --
	(206.61,124.38) --
	(207.05,123.29) --
	(207.50,122.22) --
	(207.95,121.17) --
	(208.40,120.15) --
	(208.85,119.18) --
	(209.30,118.27) --
	(209.75,117.43) --
	(210.20,116.66) --
	(210.64,115.97) --
	(211.09,115.36) --
	(211.54,114.82) --
	(211.99,114.34) --
	(212.44,113.91) --
	(212.89,113.53) --
	(213.34,113.16) --
	(213.79,112.81) --
	(214.23,112.44) --
	(214.68,112.06) --
	(215.13,111.65) --
	(215.58,111.21) --
	(216.03,110.74) --
	(216.48,110.24) --
	(216.93,109.72) --
	(217.37,109.19) --
	(217.82,108.65) --
	(218.27,108.11) --
	(218.72,107.59) --
	(219.17,107.07) --
	(219.62,106.58) --
	(220.07,106.10) --
	(220.52,105.63) --
	(220.96,105.17) --
	(221.41,104.70) --
	(221.86,104.23) --
	(222.31,103.75) --
	(222.76,103.25) --
	(223.21,102.72) --
	(223.66,102.17) --
	(224.11,101.59) --
	(224.55,100.98) --
	(225.00,100.33) --
	(225.45, 99.65) --
	(225.90, 98.94) --
	(226.35, 98.20) --
	(226.80, 97.44) --
	(227.25, 96.65) --
	(227.69, 95.85) --
	(228.14, 95.03) --
	(228.59, 94.20) --
	(229.04, 93.36) --
	(229.49, 92.52) --
	(229.94, 91.68) --
	(230.39, 90.84) --
	(230.84, 90.00) --
	(231.28, 89.17) --
	(231.73, 88.35) --
	(232.18, 87.53) --
	(232.63, 86.72) --
	(233.08, 85.93) --
	(233.53, 85.14) --
	(233.98, 84.36) --
	(234.43, 83.60) --
	(234.87, 82.84) --
	(235.32, 82.08) --
	(235.77, 81.33) --
	(236.22, 80.59) --
	(236.67, 79.85) --
	(237.12, 79.11) --
	(237.57, 78.38) --
	(238.01, 77.66) --
	(238.46, 76.95) --
	(238.91, 76.26) --
	(239.36, 75.59) --
	(239.81, 74.94) --
	(240.26, 74.31) --
	(240.71, 73.71) --
	(241.16, 73.14) --
	(241.60, 72.58) --
	(242.05, 72.05) --
	(242.50, 71.54) --
	(242.95, 71.05) --
	(243.40, 70.59) --
	(243.85, 70.14) --
	(244.30, 69.70) --
	(244.75, 69.29) --
	(245.19, 68.89) --
	(245.64, 68.51) --
	(246.09, 68.14) --
	(246.54, 67.79) --
	(246.99, 67.45) --
	(247.44, 67.13) --
	(247.89, 66.82) --
	(248.33, 66.52) --
	(248.78, 66.23) --
	(249.23, 65.96) --
	(249.68, 65.69) --
	(250.13, 65.43) --
	(250.58, 65.17) --
	(251.03, 64.91) --
	(251.48, 64.64) --
	(251.92, 64.37) --
	(252.37, 64.09) --
	(252.82, 63.79) --
	(253.27, 63.48) --
	(253.72, 63.16) --
	(254.17, 62.83) --
	(254.62, 62.50) --
	(255.07, 62.16) --
	(255.51, 61.82) --
	(255.96, 61.49) --
	(256.41, 61.17) --
	(256.86, 60.86) --
	(257.31, 60.57) --
	(257.76, 60.30) --
	(258.21, 60.04) --
	(258.65, 59.81) --
	(259.10, 59.60) --
	(259.55, 59.41) --
	(260.00, 59.23) --
	(260.45, 59.08) --
	(260.90, 58.94) --
	(261.35, 58.81) --
	(261.80, 58.71) --
	(262.24, 58.61) --
	(262.69, 58.53) --
	(263.14, 58.47) --
	(263.59, 58.41) --
	(264.04, 58.37) --
	(264.49, 58.33) --
	(264.94, 58.31) --
	(265.39, 58.29) --
	(265.83, 58.28) --
	(266.28, 58.27) --
	(266.73, 58.27) --
	(267.18, 58.27) --
	(267.63, 58.26) --
	(268.08, 58.25) --
	(268.53, 58.24) --
	(268.97, 58.22) --
	(269.42, 58.20) --
	(269.87, 58.17) --
	(270.32, 58.14) --
	(270.77, 58.10) --
	(271.22, 58.06) --
	(271.67, 58.02) --
	(272.12, 57.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.70, 51.21) -- (219.70, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.32, 51.21) -- (187.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.84, 51.21) -- (224.84, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.85, 51.21) -- (196.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.46, 51.21) -- (194.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.92, 51.21) -- (214.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.07, 51.21) -- (207.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (241.70, 51.21) -- (241.70, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.09, 51.21) -- (227.09, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.97, 51.21) -- (218.97, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (248.52, 51.21) -- (248.52, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.24, 51.21) -- (226.24, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.82, 51.21) -- (174.82, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (248.64, 51.21) -- (248.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (240.16, 51.21) -- (240.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.88, 51.21) -- (201.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.87, 51.21) -- (214.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.85, 51.21) -- (222.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.06, 51.21) -- (228.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.98, 51.21) -- (188.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.40, 51.21) -- (180.40, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.59, 51.21) -- (198.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.46, 51.21) -- (216.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.40, 51.21) -- (203.40, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.18, 51.21) -- (200.18, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.89, 51.21) -- (212.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.89, 51.21) -- (207.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.13, 51.21) -- (201.13, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.84, 51.21) -- (193.84, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.60, 51.21) -- (196.60, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.81, 51.21) -- (170.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.34, 51.21) -- (176.34, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.35, 51.21) -- (173.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (235.06, 51.21) -- (235.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.15, 51.21) -- (231.15, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.75, 51.21) -- (216.75, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.40, 51.21) -- (221.40, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.22, 51.21) -- (236.22, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.50, 51.21) -- (178.50, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.03, 51.21) -- (234.03, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.35, 51.21) -- (185.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.39, 51.21) -- (231.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.66, 51.21) -- (156.66, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (150.19, 51.21) -- (150.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.35, 51.21) -- (205.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.95, 51.21) -- (192.95, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.90, 51.21) -- (204.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (249.29, 51.21) -- (249.29, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (243.13, 51.21) -- (243.13, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.52, 51.21) -- (182.52, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.70, 51.21) -- (187.70, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (255.25, 51.21) -- (255.25, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.99, 51.21) -- (185.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (128.62, 51.21) -- (128.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.08, 51.21) -- (226.08, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.26, 51.21) -- (199.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.74, 51.21) -- (204.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.55, 51.21) -- (197.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.96, 51.21) -- (195.96, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.69, 51.21) -- (176.69, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.45, 51.21) -- (207.45, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (133.55, 51.21) -- (133.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.99, 51.21) -- (208.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.19, 51.21) -- (220.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.32, 51.21) -- (163.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (248.88, 51.21) -- (248.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.96, 51.21) -- (225.96, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (159.12, 51.21) -- (159.12, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.20, 51.21) -- (236.20, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.14, 51.21) -- (201.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.24, 51.21) -- (194.24, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.67, 51.21) -- (208.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.17, 51.21) -- (223.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.17, 51.21) -- (164.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (239.05, 51.21) -- (239.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.04, 51.21) -- (222.04, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.74, 51.21) -- (194.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.99, 51.21) -- (216.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.77, 51.21) -- (232.77, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.47, 51.21) -- (205.47, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (246.15, 51.21) -- (246.15, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.35, 51.21) -- (225.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.02, 51.21) -- (216.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (145.87, 51.21) -- (145.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.34, 51.21) -- (202.34, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.47, 51.21) -- (206.47, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.24, 51.21) -- (212.24, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.79, 51.21) -- (190.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (257.14, 51.21) -- (257.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (227.63, 51.21) -- (227.63, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (250.78, 51.21) -- (250.78, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.38, 51.21) -- (195.38, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (111.85, 51.21) -- (111.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (242.13, 51.21) -- (242.13, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.22, 51.21) -- (156.22, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.42, 51.21) -- (234.42, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.05, 51.21) -- (201.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.59, 51.21) -- (221.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.49, 51.21) -- (202.49, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.89, 51.21) -- (173.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (249.32, 51.21) -- (249.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.23, 51.21) -- (214.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.59, 51.21) -- (218.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.75, 51.21) -- (164.75, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (234.79, 51.21) -- (234.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.40, 51.21) -- (210.40, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (171.10, 51.21) -- (171.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.26, 51.21) -- (210.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.64, 51.21) -- (188.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.60, 51.21) -- (194.60, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.35, 51.21) -- (215.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.14, 51.21) -- (197.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (226.17, 51.21) -- (226.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.51, 51.21) -- (232.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.28, 51.21) -- (205.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.40, 51.21) -- (195.40, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.93, 51.21) -- (178.93, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.69, 51.21) -- (216.69, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (231.25, 51.21) -- (231.25, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.74, 51.21) -- (222.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.98, 51.21) -- (211.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.80, 51.21) -- (174.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.07, 51.21) -- (204.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (150.46, 51.21) -- (150.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (221.80, 51.21) -- (221.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.98, 51.21) -- (174.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.65, 51.21) -- (195.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.13, 51.21) -- (225.13, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.42, 51.21) -- (223.42, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.80, 51.21) -- (191.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.01, 51.21) -- (187.01, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.54, 51.21) -- (198.54, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (167.08, 51.21) -- (167.08, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.56, 51.21) -- (200.56, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.19, 51.21) -- (204.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (229.57, 51.21) -- (229.57, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.64, 51.21) -- (202.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.49, 51.21) -- (185.49, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.71, 51.21) -- (198.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.43, 51.21) -- (228.43, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.89, 51.21) -- (206.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.68, 51.21) -- (156.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.98, 51.21) -- (184.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.88, 51.21) -- (195.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.28, 51.21) -- (175.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.03, 51.21) -- (215.03, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.63, 51.21) -- (205.63, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.86, 51.21) -- (177.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.68, 51.21) -- (201.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.14, 51.21) -- (206.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.56, 51.21) -- (224.56, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.74, 51.21) -- (196.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.53, 51.21) -- (189.53, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (122.72, 51.21) -- (122.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.96, 51.21) -- (196.96, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.65, 51.21) -- (181.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (240.50, 51.21) -- (240.50, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.62, 51.21) -- (212.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.71, 51.21) -- (186.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.76, 51.21) -- (196.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.83, 51.21) -- (198.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.09, 51.21) -- (225.09, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.42, 51.21) -- (183.42, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (238.16, 51.21) -- (238.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.10, 51.21) -- (207.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.76, 51.21) -- (176.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.37, 51.21) -- (211.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.68, 51.21) -- (215.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (159.39, 51.21) -- (159.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.00, 51.21) -- (222.00, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.81, 51.21) -- (213.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (237.31, 51.21) -- (237.31, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.64, 51.21) -- (196.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (230.28, 51.21) -- (230.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.79, 51.21) -- (204.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.10, 51.21) -- (182.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (223.96, 51.21) -- (223.96, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.53, 51.21) -- (209.53, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (237.84, 51.21) -- (237.84, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.41, 51.21) -- (200.41, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.61, 51.21) -- (199.61, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.99, 51.21) -- (164.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.02, 51.21) -- (191.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.96, 51.21) -- (188.96, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.07, 51.21) -- (208.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.27, 51.21) -- (215.27, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.30, 51.21) -- (224.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.83, 51.21) -- (233.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (247.53, 51.21) -- (247.53, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (153.58, 51.21) -- (153.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.41, 51.21) -- (201.41, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.96, 51.21) -- (193.96, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.01, 51.21) -- (190.01, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (236.94, 51.21) -- (236.94, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.21, 51.21) -- (186.21, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.23, 51.21) -- (224.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (228.51, 51.21) -- (228.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (232.28, 51.21) -- (232.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (146.26, 51.21) -- (146.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.09, 51.21) -- (208.09, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.59, 51.21) -- (222.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.07, 51.21) -- (206.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.52, 51.21) -- (199.52, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (225.11, 51.21) -- (225.11, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.08, 51.21) -- (209.08, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.85, 51.21) -- (213.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (233.33, 51.21) -- (233.33, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.15, 51.21) -- (217.15, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.91, 51.21) -- (174.91, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.71, 51.21) -- (220.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.99, 51.21) -- (195.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.70, 51.21) -- (175.70, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.08, 51.21) -- (195.08, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.25, 51.21) -- (183.25, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.78, 51.21) -- (182.78, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.15, 51.21) -- (207.15, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.10, 51.21) -- (199.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.69, 51.21) -- (210.69, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.92, 51.21) -- (211.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.79, 51.21) -- (208.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.07, 51.21) -- (205.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.56, 51.21) -- (212.56, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.87, 51.21) -- (173.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.05, 51.21) -- (219.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.92, 51.21) -- (198.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.60, 51.21) -- (185.60, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.88, 51.21) -- (209.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.81, 51.21) -- (212.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.05, 51.21) -- (215.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.89, 51.21) -- (187.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.58, 51.21) -- (172.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.30, 51.21) -- (188.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.65, 51.21) -- (212.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.70, 51.21) -- (187.70, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.63, 51.21) -- (196.63, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.35, 51.21) -- (207.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.19, 51.21) -- (204.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.72, 51.21) -- (189.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.18, 51.21) -- (186.18, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.71, 51.21) -- (193.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (167.99, 51.21) -- (167.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.34, 51.21) -- (176.34, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (167.56, 51.21) -- (167.56, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.99, 51.21) -- (209.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.50, 51.21) -- (203.50, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.46, 51.21) -- (207.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.41, 51.21) -- (208.41, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.56, 51.21) -- (215.56, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.50, 51.21) -- (178.50, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.87, 51.21) -- (211.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.59, 51.21) -- (183.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (220.28, 51.21) -- (220.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.66, 51.21) -- (156.66, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (150.19, 51.21) -- (150.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.26, 51.21) -- (193.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.07, 51.21) -- (184.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.44, 51.21) -- (190.44, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.44, 51.21) -- (211.44, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.78, 51.21) -- (212.78, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.05, 51.21) -- (179.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.70, 51.21) -- (187.70, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (222.53, 51.21) -- (222.53, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.99, 51.21) -- (185.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (128.62, 51.21) -- (128.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.55, 51.21) -- (218.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.71, 51.21) -- (191.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.42, 51.21) -- (201.42, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.06, 51.21) -- (190.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.71, 51.21) -- (195.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.69, 51.21) -- (176.69, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.98, 51.21) -- (182.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (133.55, 51.21) -- (133.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.02, 51.21) -- (202.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.86, 51.21) -- (212.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.05, 51.21) -- (219.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.89, 51.21) -- (195.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (159.12, 51.21) -- (159.12, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.11, 51.21) -- (219.11, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.86, 51.21) -- (194.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.24, 51.21) -- (194.24, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.75, 51.21) -- (201.75, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.05, 51.21) -- (214.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.63, 51.21) -- (216.63, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.05, 51.21) -- (211.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.07, 51.21) -- (184.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.35, 51.21) -- (203.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.33, 51.21) -- (215.33, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.69, 51.21) -- (197.69, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.12, 51.21) -- (208.12, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.92, 51.21) -- (197.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.42, 51.21) -- (215.42, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (145.87, 51.21) -- (145.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.41, 51.21) -- (196.41, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.21, 51.21) -- (186.21, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.83, 51.21) -- (186.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.34, 51.21) -- (182.34, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (224.64, 51.21) -- (224.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.40, 51.21) -- (214.40, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.52, 51.21) -- (217.52, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.20, 51.21) -- (193.20, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (111.85, 51.21) -- (111.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.29, 51.21) -- (218.29, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.22, 51.21) -- (156.22, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (219.68, 51.21) -- (219.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.05, 51.21) -- (200.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.03, 51.21) -- (193.03, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.81, 51.21) -- (190.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.89, 51.21) -- (173.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.49, 51.21) -- (218.49, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.77, 51.21) -- (211.77, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (213.92, 51.21) -- (213.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.75, 51.21) -- (164.75, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.77, 51.21) -- (217.77, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.19, 51.21) -- (200.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (171.10, 51.21) -- (171.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.89, 51.21) -- (206.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.64, 51.21) -- (188.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.60, 51.21) -- (194.60, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.92, 51.21) -- (197.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.38, 51.21) -- (187.38, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.48, 51.21) -- (207.48, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.51, 51.21) -- (216.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.17, 51.21) -- (201.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.15, 51.21) -- (192.15, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.93, 51.21) -- (178.93, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.81, 51.21) -- (210.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.77, 51.21) -- (215.77, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.12, 51.21) -- (212.12, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.48, 51.21) -- (183.48, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.16, 51.21) -- (174.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.74, 51.21) -- (201.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (150.46, 51.21) -- (150.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.79, 51.21) -- (206.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.72, 51.21) -- (170.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.07, 51.21) -- (195.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.75, 51.21) -- (216.75, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.05, 51.21) -- (211.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.80, 51.21) -- (191.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.36, 51.21) -- (183.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.54, 51.21) -- (198.54, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.16, 51.21) -- (164.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.76, 51.21) -- (182.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.31, 51.21) -- (198.31, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.31, 51.21) -- (217.31, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.64, 51.21) -- (202.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.49, 51.21) -- (185.49, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.35, 51.21) -- (181.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.05, 51.21) -- (214.05, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.31, 51.21) -- (199.31, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.68, 51.21) -- (156.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.98, 51.21) -- (184.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.49, 51.21) -- (185.49, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.28, 51.21) -- (175.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.01, 51.21) -- (203.01, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.53, 51.21) -- (193.53, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.86, 51.21) -- (177.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.97, 51.21) -- (198.97, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.51, 51.21) -- (198.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.24, 51.21) -- (202.24, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.06, 51.21) -- (175.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.10, 51.21) -- (189.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (122.72, 51.21) -- (122.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.96, 51.21) -- (196.96, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.61, 51.21) -- (218.61, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.07, 51.21) -- (184.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.17, 51.21) -- (182.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.76, 51.21) -- (196.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.88, 51.21) -- (189.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.91, 51.21) -- (195.91, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.80, 51.21) -- (172.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.07, 51.21) -- (211.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.71, 51.21) -- (203.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.60, 51.21) -- (163.60, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.07, 51.21) -- (195.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.17, 51.21) -- (204.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (159.39, 51.21) -- (159.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (211.57, 51.21) -- (211.57, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.29, 51.21) -- (204.29, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (218.04, 51.21) -- (218.04, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.07, 51.21) -- (184.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.54, 51.21) -- (209.54, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.07, 51.21) -- (184.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.10, 51.21) -- (182.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.84, 51.21) -- (202.84, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.09, 51.21) -- (207.09, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.42, 51.21) -- (212.42, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.89, 51.21) -- (187.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.80, 51.21) -- (184.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.99, 51.21) -- (164.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.68, 51.21) -- (182.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.67, 51.21) -- (185.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.66, 51.21) -- (195.66, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.85, 51.21) -- (199.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.47, 51.21) -- (214.47, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (217.41, 51.21) -- (217.41, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (214.52, 51.21) -- (214.52, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (153.58, 51.21) -- (153.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.00, 51.21) -- (201.00, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.38, 51.21) -- (187.38, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.01, 51.21) -- (190.01, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.76, 51.21) -- (209.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.21, 51.21) -- (186.21, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.22, 51.21) -- (212.22, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.33, 51.21) -- (215.33, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.92, 51.21) -- (206.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (146.26, 51.21) -- (146.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.47, 51.21) -- (200.47, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (215.97, 51.21) -- (215.97, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.77, 51.21) -- (202.77, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.85, 51.21) -- (197.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (216.13, 51.21) -- (216.13, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.81, 51.21) -- (204.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.17, 51.21) -- (205.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.52, 51.21) -- (206.52, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.37, 51.21) -- (201.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.91, 51.21) -- (174.91, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.14, 51.21) -- (209.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.22, 51.21) -- (184.22, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.74, 51.21) -- (166.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.07, 51.21) -- (184.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.35, 51.21) -- (173.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.95, 51.21) -- (196.95, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.88, 51.21) -- (187.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.85, 51.21) -- (198.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.82, 51.21) -- (205.82, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.76, 51.21) -- (198.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.63, 51.21) -- (193.63, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.89, 51.21) -- (200.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (165.17, 51.21) -- (165.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.21, 51.21) -- (207.21, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.88, 51.21) -- (187.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.17, 51.21) -- (175.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.49, 51.21) -- (200.49, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.25, 51.21) -- (202.25, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.53, 51.21) -- (203.53, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.83, 51.21) -- (180.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (165.36, 51.21) -- (165.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.86, 51.21) -- (176.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.87, 51.21) -- (202.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.36, 51.21) -- (177.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (189.73, 51.21) -- (189.73, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.69, 51.21) -- (199.69, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.98, 51.21) -- (197.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.16, 51.21) -- (179.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.04, 51.21) -- (176.04, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.92, 51.21) -- (183.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.88, 51.21) -- (175.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.76, 51.21) -- (160.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.38, 51.21) -- (198.38, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.43, 51.21) -- (192.43, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.87, 51.21) -- (202.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.80, 51.21) -- (200.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.58, 51.21) -- (204.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (171.73, 51.21) -- (171.73, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.89, 51.21) -- (200.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.29, 51.21) -- (179.29, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.76, 51.21) -- (209.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.66, 51.21) -- (156.66, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (150.19, 51.21) -- (150.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.79, 51.21) -- (181.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.16, 51.21) -- (179.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.72, 51.21) -- (199.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.32, 51.21) -- (201.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (167.32, 51.21) -- (167.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.41, 51.21) -- (187.41, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (210.69, 51.21) -- (210.69, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.99, 51.21) -- (185.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (128.62, 51.21) -- (128.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.78, 51.21) -- (206.78, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.68, 51.21) -- (181.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.26, 51.21) -- (194.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.07, 51.21) -- (182.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.58, 51.21) -- (188.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.22, 51.21) -- (174.22, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (133.55, 51.21) -- (133.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.01, 51.21) -- (193.01, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.76, 51.21) -- (201.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.21, 51.21) -- (207.21, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.07, 51.21) -- (184.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.75, 51.21) -- (207.75, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.18, 51.21) -- (186.18, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.50, 51.21) -- (186.50, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.73, 51.21) -- (191.73, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.87, 51.21) -- (204.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.85, 51.21) -- (204.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.35, 51.21) -- (202.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.20, 51.21) -- (192.20, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.64, 51.21) -- (204.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.44, 51.21) -- (188.44, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.46, 51.21) -- (199.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.08, 51.21) -- (186.08, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.28, 51.21) -- (209.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (145.87, 51.21) -- (145.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.56, 51.21) -- (185.56, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.27, 51.21) -- (176.27, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.04, 51.21) -- (176.04, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (212.80, 51.21) -- (212.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.03, 51.21) -- (204.03, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.89, 51.21) -- (205.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.32, 51.21) -- (184.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (111.85, 51.21) -- (111.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.65, 51.21) -- (206.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.22, 51.21) -- (156.22, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (209.47, 51.21) -- (209.47, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.26, 51.21) -- (198.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.79, 51.21) -- (181.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.16, 51.21) -- (179.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.89, 51.21) -- (173.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.65, 51.21) -- (206.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.13, 51.21) -- (204.13, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.68, 51.21) -- (204.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (162.60, 51.21) -- (162.60, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.07, 51.21) -- (206.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.45, 51.21) -- (198.45, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (168.65, 51.21) -- (168.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.92, 51.21) -- (197.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.19, 51.21) -- (184.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.25, 51.21) -- (193.25, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.08, 51.21) -- (186.08, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.21, 51.21) -- (180.21, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.91, 51.21) -- (195.91, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (208.14, 51.21) -- (208.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.46, 51.21) -- (192.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.60, 51.21) -- (187.60, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.28, 51.21) -- (169.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.09, 51.21) -- (199.09, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.32, 51.21) -- (204.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.56, 51.21) -- (200.56, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.63, 51.21) -- (173.63, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (168.19, 51.21) -- (168.19, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.25, 51.21) -- (191.25, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (150.46, 51.21) -- (150.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.26, 51.21) -- (200.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (161.57, 51.21) -- (161.57, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (186.43, 51.21) -- (186.43, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.96, 51.21) -- (205.96, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.21, 51.21) -- (201.21, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.80, 51.21) -- (191.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.94, 51.21) -- (197.94, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (155.40, 51.21) -- (155.40, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.81, 51.21) -- (188.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.47, 51.21) -- (205.47, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.38, 51.21) -- (197.38, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.67, 51.21) -- (184.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (171.46, 51.21) -- (171.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (202.84, 51.21) -- (202.84, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.80, 51.21) -- (190.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.68, 51.21) -- (156.68, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.98, 51.21) -- (184.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.33, 51.21) -- (175.33, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.28, 51.21) -- (175.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (193.93, 51.21) -- (193.93, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.78, 51.21) -- (183.78, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.51, 51.21) -- (174.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.97, 51.21) -- (188.97, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (187.88, 51.21) -- (187.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.00, 51.21) -- (191.00, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (165.64, 51.21) -- (165.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.16, 51.21) -- (179.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (122.72, 51.21) -- (122.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.12, 51.21) -- (194.12, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.89, 51.21) -- (206.89, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.73, 51.21) -- (175.73, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.81, 51.21) -- (192.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.57, 51.21) -- (180.57, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (184.07, 51.21) -- (184.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (167.70, 51.21) -- (167.70, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.61, 51.21) -- (199.61, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (200.61, 51.21) -- (200.61, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (154.45, 51.21) -- (154.45, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.02, 51.21) -- (188.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (198.64, 51.21) -- (198.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (149.25, 51.21) -- (149.25, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.24, 51.21) -- (201.24, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (192.90, 51.21) -- (192.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (207.61, 51.21) -- (207.61, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.92, 51.21) -- (197.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.10, 51.21) -- (182.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.00, 51.21) -- (191.00, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.10, 51.21) -- (197.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.45, 51.21) -- (201.45, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.06, 51.21) -- (176.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.02, 51.21) -- (179.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.02, 51.21) -- (176.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.03, 51.21) -- (179.03, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.55, 51.21) -- (185.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (188.14, 51.21) -- (188.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.71, 51.21) -- (204.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.88, 51.21) -- (205.88, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (203.48, 51.21) -- (203.48, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.31, 51.21) -- (195.31, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.04, 51.21) -- (176.04, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.58, 51.21) -- (185.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.92, 51.21) -- (197.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.86, 51.21) -- (185.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (201.13, 51.21) -- (201.13, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (205.64, 51.21) -- (205.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (196.23, 51.21) -- (196.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (146.26, 51.21) -- (146.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.79, 51.21) -- (191.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (204.73, 51.21) -- (204.73, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (191.93, 51.21) -- (191.93, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (195.27, 51.21) -- (195.27, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (206.65, 51.21) -- (206.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (197.53, 51.21) -- (197.53, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.24, 51.21) -- (194.24, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (194.92, 51.21) -- (194.92, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (190.54, 51.21) -- (190.54, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (168.40, 51.21) -- (168.40, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (199.12, 51.21) -- (199.12, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (157.33, 51.21) -- (157.33, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (139.83, 51.21) -- (139.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.58, 51.21) -- (156.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.46, 51.21) -- (169.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (171.36, 51.21) -- (171.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.26, 51.21) -- (180.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (171.36, 51.21) -- (171.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.14, 51.21) -- (166.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.86, 51.21) -- (173.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (139.83, 51.21) -- (139.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.72, 51.21) -- (179.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (150.27, 51.21) -- (150.27, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.71, 51.21) -- (176.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.35, 51.21) -- (175.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.04, 51.21) -- (176.04, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (154.30, 51.21) -- (154.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (139.83, 51.21) -- (139.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.29, 51.21) -- (177.29, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.62, 51.21) -- (174.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.58, 51.21) -- (156.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (132.90, 51.21) -- (132.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (158.27, 51.21) -- (158.27, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (138.18, 51.21) -- (138.18, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (171.36, 51.21) -- (171.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.14, 51.21) -- (166.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.98, 51.21) -- (177.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.35, 51.21) -- (175.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.36, 51.21) -- (177.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (149.28, 51.21) -- (149.28, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.86, 51.21) -- (173.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (168.93, 51.21) -- (168.93, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.27, 51.21) -- (182.27, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (132.90, 51.21) -- (132.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (139.83, 51.21) -- (139.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (154.30, 51.21) -- (154.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.62, 51.21) -- (174.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (139.83, 51.21) -- (139.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.43, 51.21) -- (166.43, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (183.20, 51.21) -- (183.20, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (165.63, 51.21) -- (165.63, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (121.06, 51.21) -- (121.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.72, 51.21) -- (179.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (154.30, 51.21) -- (154.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.46, 51.21) -- (169.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.53, 51.21) -- (156.53, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.87, 51.21) -- (166.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (121.06, 51.21) -- (121.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.14, 51.21) -- (166.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.62, 51.21) -- (174.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (121.06, 51.21) -- (121.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.72, 51.21) -- (179.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.58, 51.21) -- (156.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (121.06, 51.21) -- (121.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.26, 51.21) -- (180.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (162.02, 51.21) -- (162.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.14, 51.21) -- (166.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.10, 51.21) -- (178.10, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (121.06, 51.21) -- (121.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.36, 51.21) -- (177.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.65, 51.21) -- (176.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.14, 51.21) -- (166.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.36, 51.21) -- (177.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (162.02, 51.21) -- (162.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.17, 51.21) -- (181.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (158.59, 51.21) -- (158.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.79, 51.21) -- (181.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (132.90, 51.21) -- (132.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (158.59, 51.21) -- (158.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.58, 51.21) -- (151.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (185.31, 51.21) -- (185.31, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.75, 51.21) -- (177.75, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.58, 51.21) -- (178.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (157.76, 51.21) -- (157.76, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (111.85, 51.21) -- (111.85, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.16, 51.21) -- (179.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (143.80, 51.21) -- (143.80, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (182.27, 51.21) -- (182.27, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.62, 51.21) -- (174.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (154.30, 51.21) -- (154.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (160.39, 51.21) -- (160.39, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.16, 51.21) -- (179.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.72, 51.21) -- (179.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.66, 51.21) -- (177.66, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (141.86, 51.21) -- (141.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.58, 51.21) -- (178.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.35, 51.21) -- (175.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (146.47, 51.21) -- (146.47, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.43, 51.21) -- (170.43, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (158.59, 51.21) -- (158.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.17, 51.21) -- (170.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (158.59, 51.21) -- (158.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (158.13, 51.21) -- (158.13, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (168.42, 51.21) -- (168.42, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (181.30, 51.21) -- (181.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.84, 51.21) -- (166.84, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (147.81, 51.21) -- (147.81, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.36, 51.21) -- (177.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.07, 51.21) -- (173.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (143.79, 51.21) -- (143.79, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (165.98, 51.21) -- (165.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (132.90, 51.21) -- (132.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.17, 51.21) -- (176.17, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (138.12, 51.21) -- (138.12, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (162.02, 51.21) -- (162.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.58, 51.21) -- (178.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.62, 51.21) -- (174.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.46, 51.21) -- (169.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.62, 51.21) -- (174.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (139.52, 51.21) -- (139.52, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.07, 51.21) -- (164.07, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.98, 51.21) -- (177.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.43, 51.21) -- (170.43, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.35, 51.21) -- (175.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.57, 51.21) -- (164.57, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (141.65, 51.21) -- (141.65, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.46, 51.21) -- (169.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.58, 51.21) -- (156.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (162.98, 51.21) -- (162.98, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (162.02, 51.21) -- (162.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (139.83, 51.21) -- (139.83, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (121.06, 51.21) -- (121.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.71, 51.21) -- (170.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (132.90, 51.21) -- (132.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.72, 51.21) -- (179.72, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.69, 51.21) -- (173.69, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (154.30, 51.21) -- (154.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (156.58, 51.21) -- (156.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.23, 51.21) -- (172.23, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.71, 51.21) -- (176.71, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (132.90, 51.21) -- (132.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (167.32, 51.21) -- (167.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.86, 51.21) -- (173.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (124.29, 51.21) -- (124.29, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.45, 51.21) -- (174.45, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.14, 51.21) -- (166.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (180.26, 51.21) -- (180.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.43, 51.21) -- (170.43, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.74, 51.21) -- (144.74, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (162.02, 51.21) -- (162.02, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.82, 51.21) -- (170.82, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (175.35, 51.21) -- (175.35, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.64, 51.21) -- (148.64, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (151.67, 51.21) -- (151.67, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (132.90, 51.21) -- (132.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (152.29, 51.21) -- (152.29, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (154.30, 51.21) -- (154.30, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (158.59, 51.21) -- (158.59, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (161.62, 51.21) -- (161.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.90, 51.21) -- (177.90, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.58, 51.21) -- (178.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (176.04, 51.21) -- (176.04, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (121.06, 51.21) -- (121.06, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (171.61, 51.21) -- (171.61, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] ( 31.37, 51.21) -- ( 31.37, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (148.55, 51.21) -- (148.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (161.42, 51.21) -- (161.42, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (170.43, 51.21) -- (170.43, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (174.62, 51.21) -- (174.62, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (178.58, 51.21) -- (178.58, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (169.46, 51.21) -- (169.46, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (139.26, 51.21) -- (139.26, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (166.14, 51.21) -- (166.14, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (177.36, 51.21) -- (177.36, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (164.87, 51.21) -- (164.87, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (172.55, 51.21) -- (172.55, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (179.16, 51.21) -- (179.16, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.99, 51.21) -- (173.99, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (167.32, 51.21) -- (167.32, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (167.86, 51.21) -- (167.86, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (163.51, 51.21) -- (163.51, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (144.66, 51.21) -- (144.66, 54.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.1pt,line join=round,line cap=round] (173.86, 51.21) -- (173.86, 54.71);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 51.21) rectangle (283.58,193.24);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 54.91) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 80.74) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,106.56) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,132.38) {0.3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,158.21) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,184.03) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 57.67) --
	( 31.37, 57.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 83.49) --
	( 31.37, 83.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,109.32) --
	( 31.37,109.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,135.14) --
	( 31.37,135.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,160.96) --
	( 31.37,160.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,186.79) --
	( 31.37,186.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 69.75, 48.46) --
	( 69.75, 51.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.99, 48.46) --
	(120.99, 51.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.23, 48.46) --
	(172.23, 51.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.48, 48.46) --
	(223.48, 51.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.72, 48.46) --
	(274.72, 51.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 69.75, 40.75) {0.002};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (120.99, 40.75) {0.050};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (172.23, 40.75) {1.000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (223.48, 40.75) {20.086};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (274.72, 40.75) {403.429};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (157.47, 30.25) {Cumulative exposure (mg/m$^3\cdot\,$years)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,122.23) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 71.86,  5.50) rectangle (243.09, 26.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 82.86, 11.00) rectangle ( 92.86, 21.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect] ( 83.57, 11.71) rectangle ( 92.15, 20.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (119.85, 11.00) rectangle (129.85, 21.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line cap=rect] (120.57, 11.71) rectangle (129.14, 20.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (156.85, 11.00) rectangle (166.85, 21.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect] (157.56, 11.71) rectangle (166.14, 20.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (189.35, 11.00) rectangle (199.35, 21.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line cap=rect] (190.06, 11.71) rectangle (198.64, 20.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 98.36, 12.90) {0.05};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (135.35, 12.90) {0.25};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (172.35, 12.90) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,198.74);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (204.85, 12.90) {No limit};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-06-03 blip.R

@@ -1,0 +1,95 @@
+# Blip function for stochastic intervention ####
+# Kevin
+# April 21, 2021
+
+get.blip_intervention <- function(dta, mwf.intervention = mwf.which, a = 1, delta = 0.6) {
+
+	if (a == 1) {
+		for (mwf.which in mwf.intervention) {
+
+			dta.a1 <- data.table::copy(dta)
+
+			mwf <- unlist(dta.a1[, mwf.which, with = F])
+			intervention.which <- which(mwf > min(mwf) + delta)
+
+			mwf[intervention.which] <- mwf[intervention.which] - delta
+
+			# Change continuous
+			dta.a1[, (mwf.which) := list(mwf)]
+			dta.a1[, (paste0("cum_", mwf.which)) := list(cumsum(get(mwf.which))), by = .(studyno)]
+
+			dta.a1[,(c(str_to_title( mwf.which),
+								 paste0("Cumulative ", mwf.which))) := list(
+								 	get.cut(get(mwf.which), mwf.breaks, mwf.which),
+								 	get.cut(get(paste0("cum_", mwf.which)), mwf.breaks, paste0("cum_", mwf.which))
+								 )]
+
+		}
+		return(dta.a1)
+	} else {return(dta)}
+}
+
+get.static_intervention <- function(dta, mwf.intervention = mwf.which, a = 0, delta = NULL) {
+
+	a <- a + 1
+
+	for (mwf.which in mwf.intervention) {
+
+		dta.a1 <- data.table::copy(dta)
+		mwf <- mwf.breaks[a:(a + 1), mwf.which, with = F]
+		if (a == 1) {
+			mwf <- max(mwf)
+		} else {
+			if (a >= length(table(dta.a1[,str_to_title(mwf.which), with = F]))) {
+				mwf <- min(mwf)
+			} else {
+				mwf <- median(mwf)
+			}
+		}
+
+		dta.a1[,(mwf.which) := list(mwf)]
+		dta.a1[, (paste0("cum_", mwf.which)) := list(cumsum(get(mwf.which))), by = .(studyno)]
+		# dta.a1[,.(studyno, soluble, Soluble, cum_soluble, `Cumulative soluble`)]
+		dta.a1[,(c(str_to_title( mwf.which),
+							 paste0("Cumulative ", mwf.which))) := list(
+							 	get.cut(get(mwf.which), mwf.breaks, mwf.which),
[…]

### 2022-06-03 g-formula.R

@@ -1,0 +1,578 @@
+# Parametric g-formula ####
+# Kevin Chen
+# November 3, 2020
+
+library(here)
+library(boxr)
+library(survival)
+box_auth()
+
+# Get raw data and helper functions ####
+exposure.lag <- 10
+race.imputed.melt <- NULL
+source("~/headRs/00-my-theme.R")
+library(data.table)
+# # paste(ls(), collapse = ",\n") %>% clipr::write_clip()
+source(here::here("../gm-cancer-inc/breaks.R"))
+source("blip.r")
+
+# Relevant covariates ####
+covariates.which <- c(
+	"studyno", "I", "year", "immortal",
+	"status", "Censored", "Other event", "All causes",
+	"age.year2", "Age", "year2", "Year",
+	"straight", "soluble", "synthetic",
+	"Straight", "Soluble", "Synthetic",
+	"Cumulative straight", "Cumulative soluble", "Cumulative synthetic",
+	"cum_straight", "cum_soluble", "cum_synthetic",
+	"Employment status",
+	"Duration of employment", "employment.years",
+	"Cumulative time off", "cum_off",
+	"Year of hire", "yin.gm", "Sex", "Race", "Plant")
+
+#####################################################
+# Iterated conditional expectation g-computation ####
+#####################################################
+
+# Hazard-extended ICE implementation of g-formula ####
+# Wen et al. (2020)
+ice_gcomp <- function(
+	a = 0,
+	dta = copy(dat.reduced[,covariates.which, with = F]),
+	dta.a1 = NULL,
+	# dta.a1 = copy(dat.a),
+	times = sort(unique(dat.reduced[status == 1]$I), decreasing = T),
+	mwf.name = "soluble",
+	quiet = F,
+	total_effect = F
+) {
+
+	if (total_effect) {
+		dta[,`Other event` := max(`Other event`), studyno]
+	}
+
+	if ("immortal" %in% names(dta.a1)){
+		dta.a1 <- dta.a1[,-c("immortal", "I", "I.which"), with = F]
+	}
+
+	if (a != 0) {
+		# nrow(dta.a1) == nrow(dta)
+		dta.a1 <- merge(
+			dta.a1[,c("studyno", "year", grep(
[…]

### 2022-06-03 get-data.R

@@ -1,0 +1,144 @@
+# Get data for cancer incidence ####
+# Kevin Chen
+# November 3, 2020
+
+library(here)
+
+library(survival)
+
+if (!("exposure.lag" %in% ls())) {exposure.lag <- 10}
+
+year.max <- 2015
+employment_status.lag <- 0
+yout.which <- "yout"
+
+# Source 00-hello.R
+if (!('cohort' %in% ls(envir = .GlobalEnv))) {
+	source(here::here('../gm-wrangling/wrangling', '00-hello.R'))
+}
+
+# Source script for cancer incidence helper functions
+source(here::here('../gm-cancer-inc', 'incidence.R'))
+
+incidence.key <- data.table::fread(here::here("../gm-wrangling/cancer incidence", 'cancer-key.tsv'))
+# Expand incidence key ####
+incidence.key[, `:=`(
+	var.name = paste0("canc_", code),
+	date.name = paste0("ddiag_", code))]
+incidence.key <- rbindlist(
+	list(incidence.key,
+			 data.table(
+			 	code = c("first", "copd", "external"),
+			 	description = c(
+			 		"All cancers",
+			 		"Chronic obstructive pulmonary disease",
+			 		"All external causes"),
+			 	var.name = c(
+			 		"canc_first",
+			 		"Chronic obstructive pulmonary disease",
+			 		"All external causes"),
+			 	date.name = c(
+			 		"ddiag_first",
+			 		"yod", "yod")
+			 )))
+
+# Get cohort analytic ####
+if (!('cohort_analytic' %in% ls())) {
+	outcome.type <- 'incidence'
+	cohort_analytic <- get.cohort_analytic(
+		outcome_type = outcome.type,
+		exposure.lag = exposure.lag,
+		deathage.max = NULL,
+		year.max = year.max,
+		hire.year.min = -Inf,
+		use_seer = T,
+	)
+	setorder(cohort_analytic, studyno, year)
+	cohort_analytic[, `:=`(yin.gm = date.to.gm(yin))]
+
+	# Keep only people who appear in the exposure data
+	cohort_analytic <- cohort_analytic[studyno %in% unique(exposure$studyno)]
+
+	# PICK YOUT ####
+	cohort_analytic[, jobloss.date := get(yout.which)]
+	cohort_analytic[year > year(jobloss.date), employment := "Left work"]
[…]

### 2022-06-03 run_g-formula.R

@@ -1,0 +1,593 @@
+# Run parametric g-formula ####
+# Kevin Chen
+# November 3, 2020
+
+library(here)
+source(here("g-formula.R"))
+
+# # Shape data
+# source(here::here("shape-data.R"))
+
+dat.reduced <- box_read(928445783979)
+
+# name          : dat.total.reduced.rds
+dat.total.reduced <- box_read(928452001570)
+
+# name          : dat.str.reduced.rds
+dat.str.reduced <- box_read(928446426341)
+# name          : dat.str_total.reduced.rds
+dat.str_total.reduced <- box_read(928447106294)
+
+# name          : dat.sol.reduced.rds
+dat.sol.reduced <- box_read(928445303042)
+# name          : dat.sol_total.reduced.rds
+dat.sol_total.reduced <- box_read(928447942153)
+
+# name          : dat.syn.reduced.rds
+dat.syn.reduced <- box_read(928451552327)
+# name          : dat.syn_total.reduced.rds
+dat.syn_total.reduced <- box_read(928447597463)
+
+# name          : dat.total.reduced2.rds
+dat.total.reduced2 <- box_read(929952423129)
+
+# name          : dat.str.reduced2.rds
+dat.str.reduced2 <- box_read(929952765078)
+# name          : dat.sol.reduced2.rds
+dat.sol.reduced2 <- box_read(929953044799)
+# name          : dat.syn.reduced2.rds
+dat.syn.reduced2 <- box_read(929951401906)
+
+# name          : dat.str_total.reduced2.rds
+dat.str_total.reduced2 <- box_read(929957702377)
+# name          : dat.sol_total.reduced2.rds
+dat.sol_total.reduced2 <- box_read(929954713019)
+# name          : dat.syn_total.reduced2.rds
+dat.syn_total.reduced2 <- box_read(929954585841)
+
+# name          : dat.str.reduced10.rds
+dat.str.reduced10 <- box_read(942770799114)
+# name          : dat.sol.reduced10.rds
+dat.sol.reduced10 <- box_read(930687554963)
+# name          : dat.syn.reduced10.rds
+dat.syn.reduced10 <- box_read(942772072287)
+
+
+#####################################################
[…]

### 2022-06-03 shape-data.R

@@ -1,0 +1,964 @@
+# Shaping data for parametric g-formula and the sdr lmtp ####
+# Kevin Chen
+# November 3, 2020
+
+library(here)
+library(boxr)
+library(survival)
+box_auth()
+
+# Get raw data and helper functions ####
+exposure.lag <- 10
+race.imputed.melt <- NULL
+source("~/headRs/00-my-theme.R")
+library(data.table)
+# # paste(ls(), collapse = ",\n") %>% clipr::write_clip()
+source(here::here("../gm-cancer-inc/breaks.R"))
+source("blip.r")
+
+# Get data ####
+source(here::here("get-data.R"))
+# Clear out unnecessary gunk
+rm(
+	additional_outcomes,
+	dta,
+	exposure,
+	get.coef,
+	get.cohort2,
+	get.exposure,
+	get.facet_tikz,
+	get.ggtab,
+	get.hwse.ggtab,
+	get.hwse2.coxph,
+	get.hwse3.coxph,
+	get.jobhist,
+	get.tikz,
+	icd_codes.function,
+	jobhist,
+	jobhist_py,
+	jobhist_py.cast,
+	ltab_age,
+	ltab_calendar,
+	seer,
+	self_injury.function,
+	spec_icd_codes
+)
+
+# Which outcome ?
+outcomes.which <- grep("hodgkin", incidence.key$description, ignore.case = T)
+incidence.key[outcomes.which,]
+
+# Remove people who experienced event in first year
+dat <- cohort_analytic[!studyno %in% c(103598, 132387)]
+# dat <- copy(cohort_analytic)
+
+# Lag time off
+dat[,`:=`(
+	off = shift(off, exposure.lag, 0),
+	cum_off = shift(cum_off, exposure.lag, 0)
+)]
+# dat <- dat[yin <= as.Date("1983-01-01") & year >= 1985 & year <= 1994 + exposure.lag]
+# Get data analytic ####
+get.coxph(
+	cohort_name = "dat",
+	run_model = F,
+	time_scale = "age",
+	start.year = -Inf,
+	employment_status.lag = exposure.lag)
+dat <- copy(nhl.dat)
+
+# TV covariates: calendar year, duration of employment, time spent off, cumulative MWF exposure up to ___ year, employment status, censoring/death
[…]

### 2022-09-15 reports/paper/01-introduction.rmd
Another draft of  manuscript

@@
 
-Metalworking fluids (MWF) are complex chemical mixtures used to lubricate and cool machinery during manufacturing processes.
-Straight MWF are the oldest class of MWF, comprising of simple oils or combinations of oils.
-By the mid 20th century, straight MWF waned in popularity and ceded market share to soluble MWF.
-Soluble MWF are water-oil mixtures with diverse additives for improving performance and durability.
-By the 1970s, semisynthetic and synthetic MWF, which contain little to no oil, overtook straight oils in market share.
-Nonetheless, at the turn of the millennium, soluble MWFs still retained the largest share of the MWF market [@Childers_2005].
-Carcinogenicity of MWFs has been of concern since as early as the 1970s, when the International Agency for Research on Cancer (IARC) classified mineral oils as carcinogenic, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973].
-Concerns over the health effects of straight MWF hastened the adoption of soluble MWF, which contain less oil per volume, but a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrosamines, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987;@IARC_2014;@IARC_2017].
-Health and environmental considerations led to substantial variation in MWF composition over time, but the elimination of particular etiologic agents often leads to their replacement with other potentially hazardous chemical compounds.
-Exposure limits for MWF as a mixture encourage limiting occupational exposure to multiple agents simultaneously.
+Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered intense research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons [@seer_1994;@Ekstrom-Smedby_2006].
+The strongest known risk factor of NHL is immunosuppression, both congenital and acquired [@Filipovich_1992;@Chiu_2015].
+Modulation of immune function contributes to the pathogenesis of NHL directly by perturbing lymphocyte function or indirectly by reducing immunosurveillance against neoplasms.
+Immunodeficiency may also interact with infection with Epstein-Barr Virus, resulting in uncontrolled B-cell proliferation [@Oertel_2002].
+Acquired immunodeficiency through infection with human immunodeficiency virus (HIV) can lead to genetic lesions and dysregulation while increasing vulnerability to infection by other oncogenic agents [@Grulich_1999;@Alexander_2007].
+However, since immunodeficiency and infection with HIV are rare, they cannot fully explain the historic rise or present burden of NHL [@Shiels_2013].
+Since the rise in NHL incidence coincided with a period of rapid and extensive chemicalization in industry, agriculture and warfare, there has been stronger interest in the environmental and occupational epidemiology on NHL [@Nelson_2005;@Romero_2021].
+A meta-analysis of 44 articles published between 1980 and 2014 found statistically significant associations between NHL and exposure to pesticides of several classes including carbamate, organophosporus, triazine, and organochlorine [@Schinasi_2014].
+While this meta-analysis presents striking evidence of the potential explanatory role of occupational exposures, it also highlights the limited breadth of occupational exposures studied.
 
-Here, we assess the effect of hypothetical exposure limits on non-Hodgkin lymphoma (NHL) cumulative incidence (risk) from 1985 to 2005 in the United Auto Workers-General Motors (UAW-GM) Occupational Cohort Study.
-The large size of the study population and rich time-varying, quantitative MWF exposure data provide an opportunity to study this relatively rare cancer while contrasting realistic interventions on MWF exposure in a longitudinal cohort setting.
-Though NHL accounts for a small proportion of cancer incidence of all sites, it has garnered intense research attention because its incidence nearly quadrupled since 1960 [@Ekstrom-Smedby_2006].
-Immune modulation due to immunosuppressive therapy and infection by human immunodeficiency virus (HIV) are the most prominent risk factors of NHL, but they cannot fully explain this rise in NHL incidence [@Shiels_2013;@Chiu_2015].
-Epidemiologic investigations of environmental and occupational exposures have yielded varied results [@Ekstrom-Smedby_2006;@Alexander_2007].
-This variation in epidemiologic findings may reflect the substantial etiologic heterogeneity of NHL, but studies of specific NHL subtypes are limited by the lack of quantitative exposure information and the lack of control for the healthy worker survivor effect (HWSE) or other forms of time-varying confounding affected by prior exposure [@Evens_2008;@Morton_2014].
-The HWSE, a key concern in occupational epidemiology, is the dynamic selection process by which healthier individuals remain at work, where they accumulate more occupational exposure, and less healthy individuals leave work [@Arrighi_1994].
-Standard analyses of occupational cohorts affected by the HWSE result in a downward bias on the exposure-outcome associations of interest.
+Studies of NHL and other important occupational exposures including oils, solvents, and lubricants remain inconclusive [@Ekstrom-Smedby_2006].
+Furthermore, since NHL is relatively rare, nearly all studies of NHL incidence follow a single time-point case-control design [@Schinasi_2014;@Alexander_2007].
+Large multicenter studies including EPILYMPH and InterLymph attained large enough numbers of cases to investigate particular NHL subtypes, but despite their impressive size and comprehensiveness, were limited by the lack of quantitative time-varying exposure information and the lack of adjustment for time-varying sources of bias [@Besson_2006;@Morton_2014].
+In the case of occupational studies, the healthy worker survivor effect (HWSE) is a key concern.
+The HWSE is the dynamic selection process by which healthier individuals remain at work, where they accumulate more occupational exposure, and less healthy individuals leave work [@Arrighi_1994].
+Standard analyses of occupational cohorts affected by the HWSE result in a downward bias on the exposure-outcome associations of interest, as less healthy workers typically accrue less exposure than healthier workers.
 
-In the present analysis of the UAW-GM Cohort Study, we estimated NHL risk from 1985 to 2005 under hypothetical limits on average annual soluble MWF by applying the novel hazard-extended iterative conditional expectation (ICE) parametric g-formula estimator [@Wen_2020].
-We leveraged time-varying quantitative MWF exposure data in tandem with employment data to adjust for the HWSE.
-In particular, we estimated the expected number of NHL cases we would observe if the hypothetical limits of 0.5, 0.25, and 0.05 mg/m^3^ were enforced for soluble MWF over workers' entire working lifetimes.
-Since workers were exposed to MWF of other types as well, we also evaluated the effect of dynamically reducing soluble MWF exposure with the goal of limiting total MWF exposure to 0.5 and 0.25 mg/m^3^.
+Metalworking fluids (MWF), an important class of occupational exposures, are complex mixtures of oils and chemicals used to lubricate and cool metal during manufacturing processes.
+During use, MWFs aerosolize and present a potential health hazard to exposed workers.
+The type of MWF applied depends in part on the particular metalworking operation.
+Straight MWF, the oldest class of MWF, is comprised mostly of mineral oil.
+Concerns over the carcinogenicity of MWF began as early as the 1970s, when the International Agency for Research on Cancer (IARC) classified mineral oils as carcinogenic, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973].
+The combination of health concerns, the high cost of oil in the 1970s, and the introduction of performance-enhancing water-soluble chemical additives led to the gradual replacement of straight MWF with water-based soluble and synthetic MWFs for many, but not all operations [@Childers_2005].
+The elimination of particular etiologic agents often leads to their replacement with other potentially hazardous chemical compounds, however [@Kassotis_2020;@Maertens_2021].
+Although water-based MWF contain little to no mineral oil, they contain a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987;@IARC_2014;@IARC_2017].
+Hence, limits on entire classes of exposures grouped by functional use may result in stronger, more lasting protections for worker health than limits on particular etiologic agents because they will remain in place even as the composition and formulation of complex occupational exposures change [@Maertens_2021].
+More than 20 years after the IARC classification of mineral oils as carcinogenic, the National Institute for Occupational Safety and Health (NIOSH) concluded that there exists substantial evidence linking all MWF exposure to several different cancers and now recommends an exposure limit of 0.5 mg/m^3^ for total particulate matter derived from any type of MWF [@niosh_1998;@Mirer_2003].
+
+Here, we assess the effect of hypothetical MWF exposure limits on NHL cumulative incidence in the United Auto Workers-General Motors (UAW-GM) Occupational Cohort Study.
+In particular, we assess the effect of limits on soluble MWF that (1) ignore exposure to other types of MWF and (2) account for other types of MWF exposure by intervening more strongly on soluble MWF when exposure to all types of MWF is high.
+The latter approach is more consistent with the NIOSH REL, which was recommended for exposure to any type of MWF.
+The large size of the study population and rich time-varying, quantitative MWF exposure data provide an opportunity to study this relatively rare cancer and evaluate realistic interventions on MWF exposure in a longitudinal cohort setting.
+A recent study of cancer incidence in this iconic occupational cohort found a monotonic association between NHL and exposure to soluble MWF [@Colbeth_2022].
+This association was based on a traditional Cox proportional hazards regression, a method vulnerable to bias due to confounding by time-varying factors affected by prior exposure.
+We therefore explore this association using a novel causal estimator capable of adjusting for time-varying confounding and censoring affected by past exposure.
+This estimator also yields marginal effect estimates of hypothetical interventions, which are more compatible with a population health framework than conditional measures.

### 2022-09-15 reports/paper/02-methods.rmd
Another draft of  manuscript

@@
 
+We estimated NHL risk from 1985 to 2005 under hypothetical limits on average annual exposure to soluble MWF by applying the novel hazard-extended iterative conditional expectation (ICE) parametric g-formula estimator [@Wen_2020].
+We leveraged time-varying quantitative MWF exposure data in tandem with employment records to adjust for the HWSE.
+First, we estimated the expected number of NHL cases per 1000 workers that we would observe if there were no competing risks.
+We contrasted  this counterfactual risk to that when in addition, the hypothetical exposure limits of 0.5, 0.25, and 0.05 mg/m^3^ were enforced for soluble MWF over workers' entire working lifetimes.
+These hypothetical limits are static interventions because they do not consider other covariates or exposures.
+However, since workers were often exposed to multiple types of MWF, both daily and cumulatively, we also evaluated the effect of limiting total MWF exposure to those hypothetical limits by intervening only on exposure to soluble MWF.
+These interventions, which take into consideration exposure to MWF of other types, are dynamic interventions on exposure to soluble MWF.
+All of the hypothetical interventions we evaluate are stochastic interventions rather than deterministic interventions because post-intervention exposures take on a range of values.
+
 ## Study population
 
-The UAW-GM Cohort includes hourly workers at three automobile manufacturing plants in Michigan who had worked at least 3 years by 1985.
+The UAW-GM cohort includes all hourly workers at three automobile manufacturing plants in Michigan who had worked at least 3 years by 1985.
 Past papers provide detailed descriptions of the cohort [@Eisen_1992;@Eisen_2001].
-The present study population (N = 34,738) was restricted to the autoworkers who were at work in 1941 or not yet hired, alive at the start of follow-up, and missing no more than half of their employment history.
-Autoworkers in the study population were followed for NHL incidence from January 1, 1995 until NHL diagnosis, death, December 31, 2004, or upon reaching the oldest observed age at death, whichever came earlier.
+The present study population (N = 34,738) was restricted to the autoworkers who were at work in 1941 or not yet hired, missing no more than half of their employment history, and still alive at the start of follow-up.
+Autoworkers in the study population were followed for NHL incidence from January 1, 1985 until NHL diagnosis, death, 10 years after the end of employment records, or upon reaching the oldest observed age at death (108 years), whichever came earlier.
 
@@
 Details regarding cancer incidence follow-up are described elsewhere [@Colbeth_2022].
-Vital status was ascertained by company records and by linkage to Social Security Administration, National Death Index, death certificate, and state mortality files.
+Vital status was ascertained from company records and by linkage to Social Security Administration, National Death Index, and state mortality files.
 
 Covariates including year of hire, sex, race, and plant location were obtained from company records.
-Race data were missing for about 16% of the workers.
-In analyses, missing race was considered a distinct category of race.
+Race was missing for about 16% of the cohort, most commonly among workers hired before 1960 in Plant 2.
+In analyses, missing race was considered a distinct category.
 
@@
 
-For each combination of job type, department, and plant industrial hygienists collected several hundred personal and area samples for particulate matter (mg/m^3^) over the course of three decades to derive quantitative 8-hour time-weighted average exposure estimates to soluble, straight, and synthetic MWFs.
-Workers' time-weighted average annual exposure to each MWF type was determined according to employment records, which recorded time-varying job type, department, and plant.
-For employment records that were no less than half complete, gaps in the record were interpolated by carrying forward the last known job type.
-In each year, cumulative exposures to soluble, straight, and synthetic MWFs (mg/m^3^-years) were calculated by taking cumulative sums of average annual exposures.
-In analyses, MWF exposure was lagged 10 years.
-Exposure assessment is described in detail elsewhere [@Hallock_1994;@Woskie_1994;@Woskie_2003].
+Company industrial hygienists collected several hundred personal and area samples for total particulate matter (mg/m^3^) composed of MWF over many decades.
+Research industrial hygienists collected additional air sampling data when the cohort study was launched in the mid 1980s.
+These data were combined with the historical data to derive quantitative 8-hour time-weighted average exposure estimates to soluble, straight, and synthetic MWFs for each combination of job, department, and plant over time.
+Workers' time-weighted average annual exposure to each MWF type was determined by combining this job-exposure matrix with employment records, which recorded time-varying job type, department, and plant.
+For employment records that were at least half complete, gaps in the record were interpolated by carrying forward the last known job type.
+The exposure assessment is described in detail elsewhere [@Hallock_1994;@Woskie_1994;@Woskie_2003].
+Previous analyses of NHL applied exposure lags of 1 to 20 years; we lagged cumulative MWF exposures by 10 years to account for disease latency [@Smith_2007;@Karipidis_2007;@Zhang_2019].
 
@@
 
-We applied the hazard-extended ICE parametric g-formula with pooling over treatment history [@Wen_2020] to estimate 20-year counterfactual risk of non-Hodgkin lymphoma under five hypothetical stochastic interventions on exposure to soluble MWFs with the elimination of censoring/competing risks.
-The first three interventions were static interventions that limited average annual exposure to soluble MWF to 0.5, 0.25, and 0.05 mg/m^3^.
-The remaining two were dynamic interventions that reduced average annual exposure to soluble MWF so that exposure to all MWF types was capped at 0.5 and 0.25 mg/m^3^, if possible.
-If those limits on total average annual exposure were not possible by intervention on soluble MWF alone, average annual exposure to soluble MWF was reduced to 0.
+We applied the hazard-extended ICE parametric g-formula with pooling over treatment history [@Wen_2020] to estimate 20-year counterfactual risk of non-Hodgkin lymphoma.
+We considered six stochastic interventions on average annual exposure to soluble MWFs after the elimination of censoring/competing risks.
+We considered hypothetical exposure limits starting with the NIOSH Recommended Exposure Limit (REL) for total particulate mass (PM) from MWFs (0.5 mg/m^3^).
+Then, we estimated the risk at half the REL (0.25 mg/m^3^), and a tenth of the REL (0.05 mg/m^3^) [@niosh_1998].
+The first three interventions were static interventions which enforced these hypothetical limits on average annual exposure to soluble MWF.
+The remaining three interventions were dynamic interventions that reduced average annual exposure to soluble MWF with the goal of enforcing the hypothetical limits for total exposure to MWF, regardless of type.
+If those limits on total average annual exposure were not possible by intervention on exposure to soluble MWF alone, average annual exposure to soluble MWF was reduced to 0.
 Interventions were applied at hire, before the start of follow-up, through the end of follow-up.
-Person-years in which average annual exposure was below the hypothetical limits were not intervened upon.
-These hypothetical exposure limits reflect the Recommended Exposure Limit (REL) of the National Institute for Occupational Safety and Health (NIOSH) for total particulate mass from MWFs (0.5 mg/m^3^), half the REL (0.25 mg/m^3^), and a tenth of the REL (0.05 mg/m^3^) [@niosh_1998].
+Person-years were not intervened upon if the observed average annual exposure was below the hypothetical limit.
+Figure 1 illustrates the static and dynamic interventions for three person-year examples.
+Panel A shows the observed levels of exposure to soluble MWF and to MWF of other types.
+Panel B shows the post-intervention levels of exposure under a static intervention capping exposure to soluble MWF at the hypothetical limit (dotted line).
+Panel C shows the post-intervention levels under a dynamic intervention reducing exposure to soluble MWF with the goal of capping total MWF exposure at the hypothetical limit.
+Note that in person-year 3, the observed level of exposure to total MWF (and thus, to soluble MWF) is below the hypothetical limit, so the post-intervention exposure is left at the observed level.
 
-The hazard-extended ICE parametric g-formula estimator is an ICE expression of the parametric g-formula estimator, further extended to incorporate the predicted hazard of past outcomes.
-This differs from the classical ICE estimator, which incorporates past outcome data as indicators [@Wen_2020].
-Under the assumptions of conditional exchangeability at all time points, positivity, counterfactual consistency, and correct model specification, the hazard-extended parametric g-formula yields unbiased estimates of counterfactual risk with greater statistical efficiency than both propensity-score based estimators and the classical ICE g-formula.
+![Figure 1.
+Observed and post-intervention levels of exposure to soluble MWF and MWF of other types in three example person-years.
+The white boxes represent exposure to soluble MWF, and the shaded boxes represent exposure to MWF of other types.
+The horizontal dotted line represents the hypothetical exposure limit.](`r here::here("resources/images", "interventions.png")`){width=6.5in}
+
+The hazard-extended ICE parametric g-formula estimator is an ICE expression of the parametric g-formula estimator further extended to incorporate the predicted hazard of past outcomes [@Wen_2020].
+The classical ICE g-formula estimator is algebraically equivalent to the noniterative conditional expectation (NICE) g-formula estimator, which typically involves computing covariate-standardized estimates sequentially, starting at the index time, by specifying parametric models for the joint distribution of the confounders, exposures, and outcomes at each time point [@Taubman_2009].
+In contrast, ICE g-formula estimators avoid the need for modeling the entire joint distribution of observed variables and only require outcome models for each time point.
+Counterfactual outcome estimates over the follow-up period are computed from interval-specific conditional estimates by applying the tower rule of expectation.
+Under the assumptions of conditional exchangeability at all time points, positivity, counterfactual consistency, and correct model specification, the hazard-extended parametric g-formula yields unbiased estimates of counterfactual risk with greater statistical efficiency than both propensity score-based estimators and the classical ICE g-formula.
 
@@
 In each iteration, predicted discrete hazards were standardized over post-intervention exposure and covariate histories before combining with discrete hazards from the previous iteration.
-The result of this iterative process was sequentially-standardized estimates of the NHL risk over the entire follow-up period.
+This iterative process resulted in sequentially standardized estimates of NHL risk over the entire follow-up period.
 Averaging over the baseline distribution of covariates yielded the counterfactual risk estimate of NHL when the intervention of interest was enforced for the entire study population.
 
-We split the 20-year follow-up period into eight periods; the first two periods spanned four years each, and the remaining six periods spanned two years each.
+We split the 20-year follow-up period into eight time periods; the first two periods spanned four years each, and the remaining six periods spanned two years each.
+The first two periods are longer in length to account for the smaller number of cases in those years.
 Post-intervention exposure and exposure history were summarized as cumulative exposure.
@@
 All continuous variables were represented as categorical variables with cut points determined by the tertiles of nonzero values among NHL cases.
-During the iterative combination of discrete hazards, we performed model-based standardization over baseline covariates and the complete set time-varying covariate histories.
+During the iterative combination of discrete hazards, we performed model-based standardization over baseline covariates and the complete set of time-varying covariate histories.
 
-We estimated risk under the observed distribution of soluble MWF exposure (natural course) and under the five interventions.
+We estimated risk under the observed distribution of soluble MWF exposure (natural course) and under the six interventions.
 We contrasted the risk under intervention to that under the natural course by computing relative risks.
 Confidence intervals were computed using the nonparametric bootstrap with 1000 samples and centering on the estimate computed from observed data.
-In secondary analyses (Appendix), we repeated the analysis to evaluate interventions on exposure to straight and synthetic MWFs.
 

### 2022-09-15 reports/paper/03-results.rmd
Another draft of  manuscript

@@
 The cohort is predominantly white (66%) and male (87%).
-Plant 2 employed the largest number of workers while Plant 1 employed the fewest.
-The median year of hire among those diagnosed with NHL was 1959 whereas the median year of hire in the full study population was 1967.
+The median year of hire among those diagnosed with NHL was 1959 whereas the median year of hire in the full study population was almost a decade later.
 Age at hire was approximately the same among those with NHL and the full study population.
@@
 Soluble MWFs were the most widely used MWF type, with approximately 90% of workers ever exposed.
-Median cumulative exposure among exposed was 6.5 times higher for soluble than for straight MWFs.
-Figure 1 shows median average annual exposure to the three MWF types among exposed workers over calendar time.
+Median cumulative exposure among the exposed was 6.5 times higher for soluble than for straight MWFs.
+Figure 2 shows median average annual exposure to the three MWF types among exposed workers over calendar time.
 Exposure to MWF generally followed a downward trend over time.
-Figure 2 shows the post-intervention distribution of the logarithm of cumulative exposure to soluble MWF at end of follow-up if hypothetical limits on average annual exposure were enforced for all workers starting at hire.
+<!-- Figure 2 shows the post-intervention distribution of the logarithm of cumulative exposure to soluble MWF at end of follow-up if hypothetical limits on average annual exposure were enforced for all workers starting at hire.
 The interventions shifted the distribution of cumulative exposure rather than deterministically assigning exposure to a particular value.
+-->
 
@@
 
-![Figure 1. Median average annual exposure to straight, soluble, and synthetic metalworking fluids among exposed workers over time.](`r here::here("resources/images", "exposure.png")`){width=6.5in}
-
-\
-
-![Figure 2.
-Post-intervention distribution of cumulative exposure to soluble metalworking fluids at end of follow-up under hypothetical limits on average annual exposure (mg/m^3^).
-The rugplot shows maximum cumulative exposure accrued by non-Hodgkin lymphoma cases.](`r here::here("resources/images", "shift-soluble.png")`){width=4in}
+![Figure 2. Median average annual exposure to soluble, straight, and synthetic metalworking fluids among exposed workers over time.](`r here::here("resources/images", "exposure.png")`){width=6.5in}
 
@@
 		"dat.sol_total.reduced", "dat.sol_total.reduced2",
+		"dat.sol_total.reduced10",
 		"dat.str.reduced", "dat.str.reduced2", "dat.str.reduced10",
 		"dat.str_total.reduced", "dat.str_total.reduced2",
+		"dat.str_total.reduced10",
 		"dat.syn.reduced", "dat.syn.reduced2", "dat.syn.reduced10",
-		"dat.syn_total.reduced", "dat.syn_total.reduced2"),
+		"dat.syn_total.reduced", "dat.syn_total.reduced2",
+		 "dat.syn_total.reduced10"),
 	variable.dat = c(
@@
 		"total by soluble", "total by soluble2",
+		 "total by soluble10",
 		"straight", "straight2", "straight10",
 		"total by straight", "total by straight2",
+		 "total by straight10",
 		"synthetic", "synthetic2", "synthetic10",
-		"total by synthetic", "total by synthetic2"
+		"total by synthetic", "total by synthetic2",
+		 "total by synthetic10"
 	)
@@
 		"straight", "total by straight", "straight2", "total by straight2",
-		"straight10",
+		"straight10", "total by straight10",
 		"soluble", "total by soluble", "soluble2", "total by soluble2",
-		"soluble10",
+		"soluble10", "total by soluble10",
 		"synthetic", "total by synthetic", "synthetic2", "total by synthetic2",
-		"synthetic10",
-		"scale all", "scale all2", "natural"),
+		"synthetic10", "total by synthetic10",
+		"natural"),
 	estimate = c(
 		h.reduction.str, h.reduction.str_total, h.reduction.str2, h.reduction.str_total2,
-		h.reduction.str10,
+		h.reduction.str10, h.reduction.str_total10,
 		h.reduction.sol, h.reduction.sol_total, h.reduction.sol2, h.reduction.sol_total2,
-		h.reduction.sol10,
+		h.reduction.sol10, h.reduction.sol_total10,
 		h.reduction.syn, h.reduction.syn_total, h.reduction.syn2, h.reduction.syn_total2,
-		h.reduction.syn10,
-		h.reduction.total, h.reduction.total, h.baseline)
+		h.reduction.syn10,h.reduction.syn_total10,
+		h.baseline)
 )
@@
 		"total by straight2", "total by soluble2", "total by synthetic2",
-		"scale all", "scale all2"
+		"total by straight10", "total by soluble10", "total by synthetic10"
 	),
@@
 		"None", rep("0.5", 3), rep("0.25", 3), rep("0.05", 3),
-		"max(0, 0.5 - sol - syn)", "max(0, 0.5 - str - syn)", "max(0, 0.5 - str - sol)",
-		"max(0, 0.25 - sol - syn)", "max(0, 0.25 - str - syn)", "max(0, 0.25 - str - sol)",
-		"scale all to 0.5", "scale all to 0.25"
+		"max(0, 0.5 – sol – syn)", "max(0, 0.5 – str – syn)", "max(0, 0.5 – str – sol)",
+		"max(0, 0.25 – sol – syn)", "max(0, 0.25 – str – syn)", "max(0, 0.25 – str – sol)",
+		"max(0, 0.05 – sol – syn)", "max(0, 0.05 – str – syn)", "max(0, 0.05 – str – sol)"
 	)
@@
 The observed risk of NHL over the 20-year follow-up period was 6.65 per 1000.
-Table 2 presents the hazard-extended ICE parametric g-formula estimates of the risk and risk ratios contrasting hypothetical limits on exposure to soluble MWF to no limit, with elimination of competing risks throughout.
+Table 2 presents the hazard-extended ICE parametric g-formula estimates of the risk and risk ratios contrasting hypothetical limits on exposure to soluble MWF to no limit, after elimination of competing risks.
 The estimated risk under no limit on MWF exposure was 9.56 (8.15, 10.89) per 1000.
 Stronger limits on average annual exposure to soluble MWFs resulted in monotonically stronger reductions in the risk of NHL.
-Capping average annual exposure to soluble MWFs at the NIOSH REL of 0.5 mg/m^3^ and a tenth of the REL resulted in a risk of 8.30 (6.52, 10.19) and 7.52 (5.73, 9.51) per 1000, respectively.
-The risk ratios contrasting these hypothetical limits to no limit were 0.87 (0.72, 1.02) and 0.79 (0.62, 0.97).
-Dynamic reductions in soluble exposure with the aim of limiting total MWF exposure to the REL and half the REL also yielded protective risk ratios: 0.84 (0.69, 0.99) and 0.80 (0.64, 0.98).
-These dynamic interventions attain risk reductions of similar magnitude as the static interventions enforcing exposure limits at 0.25 and 0.05 mg/m^3^, but do so while intervening on a smaller proportion of person-years.
+Capping average annual exposure to soluble MWFs at 0.5 mg/m^3^, 0.25 mg/m^3^, and 0.05 mg/m^3^ resulted in a risk of 8.30 (6.52, 10.19), 8.06 (6.15, 10.15), and 7.52 (5.73, 9.51) per 1000, respectively.
+The risk ratios contrasting these hypothetical limits to no limit were 0.87 (0.72, 1.02), 0.84 (0.68, 1.01), and 0.79 (0.62, 0.97).
+Dynamic reductions in soluble exposure with the aim of capping total MWF exposure also yielded monotonically protective risk ratios: 0.84 (0.69, 0.99), 0.80 (0.64, 0.98), and 0.72 (0.48, 1.01).
+The dynamic interventions seeking to cap total MWF exposure at 0.5 mg/m^3^ and 0.25 mg/m^3^ attained risk reductions of similar magnitude as the static interventions enforcing (stronger) exposure limits at 0.25 and 0.05 mg/m^3^, respectively, but do so while intervening on a smaller proportion of person-years.
 
-Results for interventions on straight and synthetic MWF are presented in Tables S1 and S2 in the Appendix.
+<!-- Results for interventions on straight and synthetic MWF are presented in Tables S1 and S2 in the Appendix.
 The relative risks contrasting interventions on straight and synthetic MWF exposure to the natural course were much smaller in magnitude than those for soluble; none were statistically significant.
@@
 Limiting straight and synthetic MWF exposure to the REL affected 3.2% and 1.1% of the person-years under follow-up, respectively.
+-->
 
@@
 	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
-	 )][c(1, 2, 4, 3, 5, 6),] -> sol.tab
+	 )][c(1, 2, 4, 3, 5, 7, 6),] -> sol.tab
+
+# saveRDS(sol.tab, here::here('resources', 'sol.tab.rds'))
 
@@
 ```
-\
 
@@
 	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
-	 )][c(1, 2, 4, 3, 5, 6),] -> str.tab
+	 )][c(1, 2, 4, 3, 5, 7, 6),] -> str.tab
 
@@
 	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
-	 )][c(1, 2, 4, 3, 5, 6),] -> syn.tab
+	 )][c(1, 2, 4, 3, 5, 7, 6),] -> syn.tab
 

### 2022-09-15 reports/paper/04-discussion.rmd
Another draft of  manuscript

@@
 bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
-csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
+csl: "`r path.expand('~/HeadRs/csl/ama_2.csl')`"
 ---
@@
 
-We estimated counterfactual 20-year risks of NHL from 1985 to 2005 in the UAW-GM  Cohort Study under different hypothetical interventions targeting exposure to soluble MWFs using the hazard-extended ICE parametric g-formula.
-We found a monotonic dose-dependent relationship with lower risk estimates arising from stronger limits.
-Contrasts in estimated NHL risk were statistically significant under the strongest static intervention, which limited soluble MWF exposure to 0.05 mg/m^3^, and the two dynamic interventions, which reduced exposure so that total MWF exposure would be capped at 0.5 or 0.25 mg/m^3^, if possible.
-The dynamic interventions, which take into consideration exposure to the other MWF types, may be more efficient at reducing risk of NHL than the static interventions, which ignore exposure to the other MWF types.
+We estimated counterfactual 20-year risks of NHL from 1985 to 2005 in the UAW-GM  Cohort Study under different hypothetical interventions on exposure to soluble MWFs using the hazard-extended ICE parametric g-formula.
+We found a monotonic exposure-dependent relationship with lower risk estimates arising from stronger limits.
+Contrasts in estimated NHL risk were statistically significant under the strongest static intervention, which limited soluble MWF exposure to 0.05 mg/m^3^ (a tenth of the current NIOSH REL), and the two dynamic interventions, which sought to limit total MWF exposure to 0.5 and 0.25 mg/m^3^ (the REL and half the REL, respectively) by intervening only on exposure to soluble MWF.
 
-Colbeth et al.
-first reported an association between NHL and MWF exposure in this cohort in their standard survival analyses, which investigated associations between MWF exposure and several cancer incidence outcomes [@Colbeth_2022].
-We verified and further examined this association in an approach capable of adjusting for time-varying confounding possibly affected by past exposure.
-The present approach also yielded marginal rather than conditional estimates of effect while evaluating realistic interventions, and is thus more compatible with a population health framework.
 Under the assumptions of conditional exchangeability, positivity, consistency, and correct model specification, our estimates are unbiased for the true counterfactual risk under the hypothetical interventions.
-
 Conditional exchangeability means that for all time points, there is no confounding of the relationship between exposure/censoring and NHL status at all future time points given the observed past, including past exposure and covariates.
 A major threat to conditional exchangeability in longitudinal occupational studies is the HWSE.
-We limit potential bias due to the HWSE by conditioning on all past cumulative exposure, employment status, and cumulative time off at each time point.
-Cumulative time off and employment status are reasonable mediators of the causal paths linking past health to future exposure and health, but may not be sufficient to fully adjust for the HWSE.
+We limit potential bias due to the HWSE by conditioning on cumulative exposure, employment status, and cumulative time off history at each time point.
+Cumulative time off and employment status are reasonable mediators of the causal paths linking past health to future exposure and health, but adjustment for these variables may not be sufficient for eliminating bias due to the HWSE.
 Declines in a worker's health may lead to reductions in work-related exposure without affecting employment status or time off work [@Garcia_2017].
-We expect the absence of good time-varying measures of worker health over the life course to result in bias toward the null.
+We expect the absence of valid time-varying measures of worker health over the life course to result in bias toward the null.
 
@@
 Even under conditional exchangeability, where exposures within these strata may be considered the result of experimental assignment, expected counterfactual outcomes under different exposures may not be estimable if there is sparsity in the observed distribution of exposures [@Maldonado_2002].
-We investigated static and dynamic stochastic interventions on soluble MWF exposure which intervened only when average annual exposure exceeded the hypothetical limit under consideration.
+We investigated static and dynamic stochastic interventions on soluble MWF exposure that intervened only when average annual exposure exceeded the hypothetical limit under consideration.
 Hence, our parameters of interest achieve positivity more easily than those for deterministic interventions e.g.
-setting all to exposed versus unexposed.
-Nonetheless, violations in positivity were still of concern due to the high dimensionality of covariates, as in common in longitudinal settings.
+setting all to a single level of exposure.
+Nonetheless, violations in positivity were still of concern due to the high dimensionality of covariates, as is common in longitudinal settings.
 We addressed sparsity by summarizing the 20 years of follow-up over a coarser timescale with only 8 follow-up periods and by representing covariates using fewer categories.
@@
 In practice, causal inference using observational data must always balance positivity, covariate adjustment, and model specification [@Petersen_2012].
-When estimating causal effects using estimators that do not require exposure modeling, as is the case with g-formula methods, concerns over potential bias due to practical violations in positivity may be relaxed if correct model specification is attained.
+When estimating causal effects using estimators that do not require exposure modeling, as is the case with ICE g-formula methods, concerns over potential bias due to practical violations in positivity may be relaxed if correct model specification, discussed below, is attained.
 
@@
 This assumption would be violated if there were multiple versions of treatment causally associated with different outcomes.
-This basic notion of consistency is violated in our analysis because our exposure of interest is a complex mixture of diverse components with substantial variation over time due to changes in formulation and due to the natural physical, chemical, and biological changes in the MWF over the course of its use [@Howell_2006].
-However, causal effects estimates under violations in the consistency assumption are still valid and unbiased if there is adequate adjustment for confounders of the exposure-version relationship [@VanderWeele_2013].
+This basic notion of consistency is violated in our analysis because our exposure of interest is a complex mixture of diverse components with substantial variation over time due to changes in formulation as well as the natural physical, chemical, and biological changes in the MWF over the course of its use and reuse [@Howell_2006].
+However, causal effect estimates under violations in the consistency assumption are still valid and unbiased if there is adequate adjustment for confounders of the exposure-version relationship [@VanderWeele_2013].
 This may be thought of as conditional consistency within strata, in which there is only one version of treatment.
@@
 
-Correct model specification is a standard assumption in all analyses.
+Correct model specification is a standard assumption in all parametric analyses.
 The estimator we applied offers greater statistical efficiency than the classical ICE parametric g-formula estimator because it leverages greater parametric smoothing.
-In causal analyses of longitudinal cohort studies, both the hazard-extended and classical ICE parametric g-formula estimators are less common than the non-iterative expression (NICE) of the parametric g-formula [@Keil_2014].
-However, a major limitation of the NICE g-formula is the g-null paradox: the guaranteed misspecification of parametric models resulting in the false rejection of the null hypothesis when the null is true and there is time-varying confounding affected by past exposure [@Naimi_2015;@McGrath_2022].
+In causal analyses of longitudinal cohort studies, both the hazard-extended and classical ICE parametric g-formula estimators are less common than the NICE parametric g-formula [@Keil_2014].
+However, a major limitation of the NICE g-formula is the g-null paradox: the guaranteed misspecification of parametric models resulting in the false rejection of the null hypothesis when the null is true and when there is time-varying confounding affected by past exposure [@Naimi_2015;@McGrath_2022].
 As with all ICE g-formula estimators, the estimator we applied is not subject to the g-null paradox.
@@
 
-Much of the existing epidemiologic literature linking occupational and environmental exposures to NHL risk report findings from case-control studies where exposures are measured crudely as binary indicators of exposure or membership in a particular occupational group [@Cano_2001;@Costantini_2001;@Karunanayake_2008;@t-Mannetje_2016].
+Much of the existing epidemiologic literature linking occupational and environmental exposures to NHL report findings from case-control studies where exposures are measured crudely as binary indicators of exposure or membership in a particular occupational group [@Cano_2001;@Costantini_2001;@Karunanayake_2008;@t-Mannetje_2016].
 Associations between occupations and NHL risk vary considerably, but one study of working men in Kansas and Nebraska found strong associations between NHL risk and occupations involving metalworking and motor vehicles [@Zheng_2002].
-Both of these occupations may entail exposure to soluble MWFs, which contain a number of additives of concern for human health and NHL risk in particular.
+Both of these occupations may entail exposure to soluble MWFs, which contain a number of additives of concern for human health and for NHL risk in particular.
 Organic compounds containing phosphorous, chlorine, sulfur, nitrogen, and boron are commonly added to soluble MWF to control microbial growth, improve performance under high heat/pressure, and inhibit corrosion [@Evans_2020].
-Organophosphorous compounds include organophosphate pesticides, which have been linked to cancer risk in epidemiologic and animal studies.
+Organophosphorus compounds include organophosphate pesticides, which have been linked to cancer risk in epidemiologic and animal studies.
 Some were classified as possibly carcinogenic by the IARC [@IARC_2017].
 Studies of occupational exposure to chlorinated solvents and pesticides have also been linked to NHL risk [@Cocco_2008;@Purdue_2011;@Cocco_2013;@Vlaanderen_2013;@Callahan_2018].
-In 2014, the International Agency for Research on Cancer classified trichloroethylene, tetrachloroethylene, and other chlorinated agents as Group 1 carcinogens [@IARC_2014].
+In 2014, the IARC classified trichloroethylene, tetrachloroethylene, and other chlorinated agents as Group 1 carcinogens [@IARC_2014].
 Chlorinated solvents are commonly used as degreasers in industrial settings, but their use in the plants under study here was uncommon and limited to particular operations [@Shrestha_2016].
-The structural characteristics shared by MWF additives and known/suspected carcinogens suggest similarities in molecular function and carcinogenesis.
+The structural characteristics shared by MWF additives and known/suspected carcinogens suggest potential similarities in their behavior in biological systems.
 
-This study investigated the effect of hypothetical limits on average annual exposure to MWF by comparing the standardized distribution of NHL under various distributions of cumulative exposure induced by applying upper bounds to annual exposure.
+This study investigated the effect of hypothetical limits on MWF exposure by comparing the standardized distributions of NHL under various distributions of cumulative exposure induced by applying upper bounds to average annual exposure to soluble MWF.
 When average annual exposure did not exceed the hypothetical limit, it was left at the observed level of exposure.
 We selected these hypothetical limits based on the NIOSH REL of 0.5 mg/m^3^ [@niosh_1998].
-Without enforcement of the REL, we still observed average annual exposures below the REL for many person-years.
+In the real world, there is no enforcement of the REL, but we nonetheless observed average annual exposures below the REL in these GM plants for many years.
 If the REL were enforced in the real world, we would not expect reductions in exposure for these low-exposure person-years.
-Hence, contrasting the counterfactual scenario where all workers experienced annual exposure at the REL to one where all workers experienced annual exposure at some higher level would result in an overestimate of the expected real-world benefit of REL enforcement.
-By considering stochastic interventions that result in exposure distributions more similar to what we would expect in the real world, our analysis yielded results that more realistically quantify the effects of policy than those investigating deterministic interventions [@Bembom_2007;@Munoz_2012].
+Hence, contrasting the counterfactual scenario where all workers experienced average annual exposure at the REL to one where all workers experienced average annual exposure at some higher level would result in an overestimate of the expected real-world benefit of REL enforcement.
+Furthermore, since the REL is for MWF exposure of all types, we evaluated dynamic stochastic interventions that better reflect this target policy because they reduce exposure to soluble MWF with the goal of reducing MWF exposure of all types to a certain limit.
+The interventions we considered result in exposure distributions more similar to what we would expect in the real world; our analysis yielded results that more realistically quantify the effects of policy than those investigating deterministic interventions [@Bembom_2007;@Munoz_2012].
 
@@
 We found evidence that exposure to soluble MWF was associated with NHL incidence after adjustment for time-varying confounding affected by prior exposure using the hazard-extended ICE parametric g-formula.
-Shifting the distribution of cumulative exposure to soluble MWF by limiting average annual exposure resulted in reductions in NHL incidence.
-Limits on exposure to soluble MWF that take into consideration exposure to straight and synthetic MWFs led to greater reductions NHL incidence while intervening on fewer person-years.
+Reducing cumulative exposure to soluble MWF by enforcing hypothetical, but realistic, interventions on average annual exposure would reduce NHL incidence.

### 2022-09-15 reports/paper/05-appendix.rmd
Another draft of  manuscript

@@
 ```{=tex}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thefigure}{A\arabic{figure}}
 \renewcommand{\arraystretch}{1}
@@
 
-```{r, tab.cap.pre="Table A"}
+![Oberved and post-intervention distributions of average annual exposure (mg/m^3^).
+The rugplot shows maximum cumulative exposure accrued by non-Hodgkin lymphoma cases.](`r here::here("resources/images", "shift-avg-soluble.png")`){width=6in}
+
+![Oberved and post-intervention distributions of cumulative exposure to soluble metalworking fluids (mg/m$^3\cdot$years) at end of follow-up.
+The rugplot shows maximum cumulative exposure accrued by non-Hodgkin lymphoma cases.](`r here::here("resources/images", "shift-cum-soluble.png")`){width=6in}
+
+```{r, tab.cap.pre="Table A", include=F}
 str.flextab <- readRDS("str.flextab.rds")
@@
 
-```{r}
+```{r, include=F}
 syn.flextab <- readRDS("syn.flextab.rds")

### 2022-09-15 reports/paper/paper.Rmd
Another draft of  manuscript

@@
 csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
+notes-after-punctuation: true
 ---
@@
 
-**Manuscript title:** Evaluating hypothetical limits on metalworking fluid exposure for reducing non-Hodgkin lymphoma incidence: An application of the hazard-extended iterative conditional expectation parametric g-formula
+**Manuscript title:** Evaluating hypothetical limits on metalworking fluid exposure for reducing non-Hodgkin lymphoma incidence: An application of the hazard-extended parametric g-formula
 
-**Authors:** Kevin T. Chen,^a,b^, Sally Picciotto^b^, Ellen A. Eisen^b^
+**Authors:** Kevin T. Chen^a,b^, Sally Picciotto^b^, Ellen A. Eisen^b^
 
@@
 
-**Data and computing code:**
+**Data and computing code:** Code for reproducing analyses and reports are available on [Github](https://github.com/kvntchn/gm-nhl-ice). Data are available upon reasonable request.
+
+**Acknowledgements:**
 
@@
 
-# Abstract (250 words)
+# Abstract
 
-**Background:** The second half of the 20th century saw a fourfold rise in non-Hodgkin lymphoma (NHL) incidence.
-Over the same period, concerns about the carcinogenicity of oil-based metalworking fluids (MWF) in automobile manufacturing fueled a transition to water-based soluble MWF.
-Soluble MWF, a complex mixture of diverse chemical additives, has become the most widely used class of MWF in the industry.
-We estimated the effect of limiting annual exposure to soluble MWF on NHL incidence in the United Auto Workers-General Motors (UAW-GM) Cohort Study (n = 33,138).
-We based our hypothetical interventions on the NIOSH recommended exposure limit (REL) of 0.5 mg/m3 for total MWF particulate mass.
+(Limit: 250 words)
 
-**Methods:** We estimated counterfactual cumulative incidence of NHL from 1985 to 2004 in the UAW-GM cohort of hourly autoworkers ever employed at 3 Michigan plants for at least 3 years.
-Using the hazard-extended iterative conditional expectation g-computation, we adjusted for time-varying confounding and censoring affected by prior exposure.
-We contrasted counterfactual cumulative incidence under no intervention on exposure to when annual soluble exposure was capped at the REL, half the REL, and a tenth of the REL.
-Confidence intervals were computed using the nonparametric bootstrap.
+**Background:** Non-Hodgkin lymphoma (NHL) incidence has increased significantly since 1960 and was recently linked with workplace exposure in the United Auto Workers-General Motors (UAW-GM) Cohort Study.
+Here, we investigate hypothetical interventions on workplace exposure to soluble metalworking fluids (MWF) in relation to NHL risk.
+Interventions on entire classes of occupational exposures rather than particular agents may result in stronger lasting protections for worker health while preventing regrettable replacements.
 
-Results: There were 211 NHL cases during the follow-up period.
-Lower annual soluble exposure resulted in lower cumulative incidence of NHL.
-The risk ratio when capping soluble exposure at the REL compared to no intervention was 0.90 (95% CI: 0.78, 1.03).
-The corresponding difference in cumulative incidence was -28 cases (95%CI: -63, 8 cases).
-Capping soluble exposure at a tenth of the REL resulted in a risk ratio of 0.84 (95% CI: 0.68, 1.00) and a difference in cumulative incidence of -45 cases (95%CI: -88, 1 case).
-Conclusion: The current REL was based on evidence linking MWF exposure to respiratory and skin diseases, rather than cancer, and may not be adequate to prevent NHL in exposed autoworkers.
+**Methods:** We estimated counterfactual risk of NHL from 1985 to 2004 in the UAW-GM cohort of hourly autoworkers exposed to straight, soluble, and synthetic MWF at 3 Michigan plants under hypothetical interventions.
+We contrasted counterfactual risk under stochastic interventions on average annual exposure to soluble MWF to that under no intervention on exposure.
+These stochastic interventions included (1) static interventions on soluble MWF that ignore exposure to other types and (2) dynamic interventions that seek to cap total exposure to any type of MWF by intervening on exposure to soluble MWF only.
 
-# What this study adds (100 words)
+**Results:** During follow-up, 231 NHL cases occurred.
+Stronger hypothetical limits on average annual exposure to soluble MWF resulted in monotonically stronger reductions in NHL risk.
+Capping exposure to soluble MWF at 0.05 mg/m^3^ resulted in a risk ratio of 0.79 (95% CI: 0.62, 0.97).
+Capping total MWF exposure at 0.05 mg/m3 by intervening only on exposure to soluble MWF resulted in a risk ratio of 0.72 (95% CI: 0.48, 1.01).
+
+**Conclusion:** We considered realistic interventions more compatible with a population health framework than deterministic interventions and showed that stronger limits on average annual exposure to soluble MWF may confer stronger protection against NHL risk.
+
+# What this study adds
+
+(Limit: 100 words)
+
+Little is known about possible links between occupational exposures and non-Hodgkin lymphoma.
+Existing studies are generally single time-point case-control studies with limited exposure assessment.
+We leveraged the large study population size and quantitative exposure assessment of the United Auto Workers-General Motors Cohort Study to estimate counterfactual risk of non-Hodgkin lymphoma under realistic interventions using a novel causal estimator capable of adjusting for time-varying confounding affected by past exposure.
 

### 2022-09-15 reports/slides/slides.Rmd
Another draft of  manuscript

---
title: "Evaluating hypothetical limits on metalworking fluid exposure for reducing non-Hodgkin lymphoma incidence"
subtitle: "An application of the hazard-extended parametric g-formula"
# author: "Kevin Chen"
date: \today
# classoption: aspectratio=169
fontsize: 11pt
output:
  beamer_presentation:
    toc: false
    # latex_engine: lualatex
    includes:
      in_header: "~/HeadRs/BeamerHead.sty"
    keep_tex: true
header-includes:
- \setlength{\itemindent}{0em}
- \setlength{\leftmargini}{1em}
- \setlength{\leftmarginii}{1em}
- \setlength{\leftmarginiii}{1em}
- \usepackage{bbold}
# - \setlist*[itemize]{labelindent=\parindent,itemindent=0pt,leftmargin=*}
# - \usepackage{pgfpages}
# - \setbeamertemplate{note page}[plain]
# - \setbeameroption{show notes on second screen=right}
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
---

```{r, include=F}
library(tidyverse)
library(xtable)
```

# Non-Hodgkin Lymphoma

- 7th most common cancer in the US
- Incidence rose dramatically 1960 to 1990 around the world
	- In the US:  8.5 to 18.3 per 100,000 between 1973 and 2019
- Strongest risk factors [@Ekstrom-Smedby_2006]
	- Immunosuppression, both genetic and acquired
	- Infection by _H. pylori_, Epstein-Barr virus, Hepatitis C virus, HIV
- Known risk factors account for about 50% of observed incidence [@Hartge_1992]

\note{
In order of frequency (2020):
1. breast
2. lung/bronchus
3. prostate
4. colorectal
5. melanoma
6. bladder
7. NHL
8. kidney \& renal pelvis,
9. endometrial
10. leukemia
}

# NHL and peseticides

- Rise in NHL mirrors rise in chemicalization of agriculture, industry, and warfare [@Nelson_2005]
	- Agricultural exposure to pesticides very well studied
	- Meta-analyses yielded consistent associations with pesticides:\
	carbamate, organophosphorous, triazine, organochlorine [@Schinasi_2014]

\begin{center}
\includegraphics[width=2in]{./resources/pesticide_aircraft.jpg}
\end{center}

\note{
Several organophosphorous pesticides considered possibly carcinogenic by IARC
Several chlorinated solvents are IARC Group 1 carcinogens
}

# Soluble MWF

- Water-based soluble MWFs contain diverse additives:\
	- Triazines: biocides
	- Nitrites: rust inhibitors
	- Sulfonates: emulsifiers
	- Organochlorines: extreme pressure performance enhancers
- In UAW-GM, soluble MWF was used more frequently and in much larger quantities than straight and synthetic MWF
- Globally, soluble MWF is the most common

# MWF exposure in UAW-GM

![Median average annual exposure among exposed workers over time.](`r here::here("resources/images", "exposure.png")`){width=4in}

- 89% ever exposed to soluble
- 57% ever exposed to straight
- 35% ever exposed to synthetic

# MWF exposure and NHL in UAW-GM

![NHL and soluble MWF exposure in recent cancer incidence analysis (Hilary's paper, in press).](`r here::here("../gm-cancer-inc/reports/resources/Lag 21/subplots", "AJE-01232-2021 Colbeth Figure 2N.pdf")`){width=4in}

# Iterated conditional expectation (ICE) g-formula

ICE g-formula estimators rely on the tower property of expectation (from law of total probability)

- For example, $\mathbb E\, \mathbb E \left[Y \mid A = \check{a}, W \right] = \mathbb E \left[Y \mid A = \check{a}\right]$
- For discrete $W$, we have\
$\mathbb E \left[Y \mid A = \check{a}\right] = \sum_{w \in \mathcal W} \mathbb E\, \left[Y \mid A = \check{a}, W = w\right] \Prob{W = w}$\
This is the non-parametric $g$-computation result, which we can estimate parametrically by specifying a model:
\begin{center}$\mathbb E\left[Y \mid A = \check{a}, W = w\right] = \beta_0 + \beta_1 \check{a} + \beta_2 w$\end{center}

	- Avoids the need for propensity score
	- Relies heavily on correct model specification
	- Equivalent to model-based standardization

# ICE g-formula for multiple timepoints

\footnotesize\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ll}
Put & $\psi =  \E[f_{Y_J}]{Y_J(1 - Y_{J - 1}) \mid \bar L_{J}, \bar A_{J} = \bar A^g_{J}, \bar Y_{J - 1} = C_J = 0}$ \\
Put & $\psi =  \E[f_{L_{J}}]{\,\psi\, \mid \bar L_{J - 1}, \bar A_{J - 1} = \bar A^g_{J - 1}, \bar Y_{J - 1} = C_{J} = 0}$ \\
Put & $\psi =  \E[f_{Y_{J - 1}}]{Y_{J - 1} (1 - Y_{J - 2}) + \,\psi\, \mid \bar L_{J - 1}, \bar A_{J - 1} = \bar A^g_{J - 1}, \bar Y_{J - 2} = C_{J - 1} = 0}$ \\
& $\hspace{4pt} \vdots$ \\
Put & $\psi =  \E[f_{Y_1}]{Y_1 + \,\psi\, \mid L_1, A_1 = A^g_1, \bar Y_{0} = C_0 = 0}$ \\
\\
$\leadsto$ &  $\E{Y^g_J} =  \E[f_{L_{1}}]{\,\psi\,}$
\end{tabular}

For _hazard-extended_ ICE g-formula,\
we use discrete hazard estimate for interval $(j - 1, j]$ in place of $Y_j$

# Intervention of interest

- Static stochastic interventions: limit soluble MWF to\
	- 0.5 mg/m^3^ (NIOSH REL)
	- 0.25 mg/m^3^
	- 0.05 mg/m^3^
- Dynamic stochastic interventions: reduce soluble MWF such that total MWF exposure limited to 0.5, 0.25, and 0.05 mg/m^3^
	- Translates to the following exposure limits on soluble MWF:
		- $\max\left(0,\ 0.5 - \text{str} - \text{syn}\right)$
		- $\max\left(0,\ 0.25 - \text{str} - \text{syn}\right)$
		- $\max\left(0,\ 0.05 - \text{str} - \text{syn}\right)$

# Illustration of interventions when applied

![Observed and post-intervention levels of exposure in three example person-years.](`r here::here("resources", "interventions.pdf")`){width=4.25in}

# Results

\scriptsize\setlength{\tabcolsep}{3pt}
```{r, echo=F, results="asis", warning=F, message=F}
sol.tab <- readRDS(here::here('resources', 'sol.tab.rds'))
names(sol.tab)[grep("%", names(sol.tab))] <- gsub('%', '\\\\%', names(sol.tab)[grep("%", names(sol.tab))])
names(sol.tab)[1] <- "Exposure limit on soluble MWF (mg/m$^3$)"
sol.tab %>% xtable(align = 'cp{0.27\\linewidth}C{0.18\\linewidth}C{0.1\\linewidth}ccc') %>%
	print(comment = F, include.rownames = F,
				sanitize.text.function = function(x) {x})
```

# Discussion

- Assumption of correct model specification is doing heavy duty
	- Trade-off between satisfying positivity and correct model specification
	- But approach is much more flexible than Cox PH
- Why bother with stochastic intervention?
	- In reality, companies may not reduce exposures already below REL
	- In estimation, we can achieve positivity more easily
- Why bother with complex _dynamic_ stochastic intervention
	- NIOSH REL is for total MWF exposure?
	- Dynamic interventions can achieve risk reductions by intervening on fewer person-years (analytically) and processes (in reality)

# Citations

\singlespacing\footnotesize

### 2022-09-15 resources/interventions.tex
Another draft of  manuscript

% Created by tikzDevice version 0.12.3.1 on 2022-06-28 15:57:56
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\end{document}
re}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (469.75,216.81);
\begin{scope}
\path[clip] ( 25.15, 47.51) rectangle (167.85,198.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.15, 47.51) rectangle (167.85,198.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 31.63, 54.37) rectangle ( 68.70,164.08);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 77.97, 54.37) rectangle (115.03,122.94);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (124.30, 54.37) rectangle (161.36, 68.09);
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 31.63,164.08) rectangle ( 68.70,191.51);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 77.97,122.94) rectangle (115.03,191.51);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (124.30, 68.09) rectangle (161.36, 81.80);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 25.15, 88.66) -- (167.85, 88.66);
\end{scope}
\begin{scope}
\path[clip] (173.35, 47.51) rectangle (316.05,198.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (173.35, 47.51) rectangle (316.05,198.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (179.84, 54.37) rectangle (216.90, 88.66);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (226.17, 54.37) rectangle (263.23, 88.66);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (272.50, 54.37) rectangle (309.57, 68.09);
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (179.84, 88.66) rectangle (216.90,116.08);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (226.17, 88.66) rectangle (263.23,157.22);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (272.50, 68.09) rectangle (309.57, 81.80);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (173.35, 88.66) -- (316.05, 88.66);
\end{scope}
\begin{scope}
\path[clip] (321.55, 47.51) rectangle (464.26,198.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (321.55, 47.51) rectangle (464.25,198.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (328.04, 54.37) rectangle (365.10, 61.23);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (374.37, 54.37) rectangle (411.44, 54.37);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (420.70, 54.37) rectangle (457.77, 68.09);
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (328.04, 61.23) rectangle (365.10, 88.66);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (374.37, 54.37) rectangle (411.44,122.94);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (420.70, 68.09) rectangle (457.77, 81.80);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (321.55, 88.66) -- (464.26, 88.66);
\end{scope}
\begin{scope}
\path[clip] ( 25.15,198.36) rectangle (167.85,211.31);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] ( 25.15,198.36) rectangle (167.85,211.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 27.65,201.74) {A) No intervention};
\end{scope}
\begin{scope}
\path[clip] (173.35,198.36) rectangle (316.05,211.31);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] (173.35,198.36) rectangle (316.05,211.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (175.85,201.74) {B) Static intervention};
\end{scope}
\begin{scope}
\path[clip] (321.55,198.36) rectangle (464.26,211.31);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] (321.55,198.36) rectangle (464.25,211.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (324.05,201.74) {C) Dynamic intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 50.17, 37.06) {p-yr 1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.50, 37.06) {p-yr 2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.83, 37.06) {p-yr 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (198.37, 37.06) {p-yr 1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (244.70, 37.06) {p-yr 2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (291.03, 37.06) {p-yr 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (346.57, 37.06) {p-yr 1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (392.90, 37.06) {p-yr 2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (439.24, 37.06) {p-yr 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 47.51) --
	( 25.15,198.36);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 51.62) {0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 54.37) --
	( 25.15, 54.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 88.66) --
	( 25.15, 88.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,122.94) --
	( 25.15,122.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,157.22) --
	( 25.15,157.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,191.51) --
	( 25.15,191.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,122.94) {Average annual exposure (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 49.28,  5.50) rectangle (189.07, 24.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 60.28, 11.00) rectangle ( 68.28, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] ( 60.99, 11.71) rectangle ( 67.56, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 73.78, 11.90) {Hypothetical exposure limit};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (200.07,  5.50) rectangle (440.13, 24.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (211.07, 11.00) rectangle (219.07, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (211.79, 11.71) rectangle (218.36, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (211.79, 11.71) rectangle (218.36, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (334.17, 11.00) rectangle (342.17, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (334.88, 11.71) rectangle (341.46, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (334.88, 11.71) rectangle (341.46, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (224.57, 11.90) {Exposure to soluble MWF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (347.67, 11.90) {Other MWF  exposure};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-09-15 intervention_figure.R

@@ -1,0 +1,122 @@
+# Making figure for explaining interventions ####
+# Kevin Chen
+# June 28, 2022
+
+library(here)
+source("~/headrs/00-my-theme.R")
+library(data.table)
+
+eg.dat <- data.table(
+	Exposure = c(0.16, 0.1, 0.02),
+	`Other exposure` = c(0.04, 0.1, 0.02)
+)
+
+eg.dat[, Static := {
+	x <- Exposure
+	x[x > 0.05] <- 0.05
+	x
+}]
+
+eg.dat[Exposure + `Other exposure` > 0.05, Dynamic := {
+	x <- Exposure
+	x <- 0.05 - `Other exposure`
+	x[x < 0] <- 0
+	x
+}]
+
+eg.dat[Exposure + `Other exposure` < 0.05, Dynamic := Exposure]
+
+eg.melt <- data.table(
+	mid = c(eg.dat$Exposure, eg.dat$Static,
+					eg.dat$Exposure, eg.dat$Dynamic),
+	upper = c(eg.dat$`Other exposure`,
+						eg.dat$`Other exposure`,
+						eg.dat$`Other exposure` + eg.dat$Exposure,
+						eg.dat$`Other exposure` + eg.dat$Dynamic),
+	exposure = c(rep("Observed exposure", 3), rep("Post-intervention exposure", 3),
+							 rep("Observed exposure", 3), rep("Post-intervention exposure", 3)),
+	intervention = c(rep("Static", 6), rep("Dynamic", 6))
+)
+
+eg.melt[,upper := mid + rep(eg.dat$`Other exposure`, 4)]
+
+eg.melt[,intervention := factor(
+	intervention,
+	c("Static", "Dynamic"),
+	c("Static intervention", "Dynamic intervention"))]
+
+eg.melt[,`:=`(
+	xmin = rep(1:3 - 0.4, 4),
+	xmax = rep(1:3 + 0.4, 4)
+)]
+
+# Simplified layout?
+eg.melt <- eg.melt[c(1:6, 10:12)]
+eg.melt$type <- rep(c(
+	"No intervention",
+	"Static intervention",
+	"Dynamic intervention"), each = 3)
+eg.melt[,type:= factor(type, c(
+	"No intervention",
+	"Static intervention",
+	"Dynamic intervention"),
+	c(
+	"A) No intervention",
+	"B) Static intervention",
[…]

### 2022-09-15 run_g-formula.R

@@ -10,9 +10,6 @@ source(here("g-formula.R"))
 
 dat.reduced <- box_read(928445783979)
 
-# name          : dat.total.reduced.rds
-dat.total.reduced <- box_read(928452001570)
-
 # name          : dat.str.reduced.rds
 dat.str.reduced <- box_read(928446426341)
 # name          : dat.str_total.reduced.rds
@@ -52,6 +49,13 @@ dat.sol.reduced10 <- box_read(930687554963)
 # name          : dat.syn.reduced10.rds
 dat.syn.reduced10 <- box_read(942772072287)
 
+# name          : dat.str_total.reduced10.rds
+dat.str_total.reduced10 <- box_read(978943764524)
+# name          : dat.sol_total.reduced10.rds
+dat.sol_total.reduced10 <- box_read(978944866752)
+# name          : dat.syn_total.reduced10.rds
+dat.syn_total.reduced10 <- box_read(978947609426)
+
 
 #####################################################
 # Post-intervention distribution of exposure     ####
@@ -61,10 +65,13 @@ dat.syn.reduced10 <- box_read(942772072287)
 # 	dt.name = c(
 # 		"dat.sol.reduced", "dat.sol.reduced2", "dat.sol.reduced10",
 # 		"dat.sol_total.reduced", "dat.sol_total.reduced2",
+# 		"dat.sol_total.reduced10",
 # 		"dat.str.reduced", "dat.str.reduced2", "dat.str.reduced10",
 # 		"dat.str_total.reduced", "dat.str_total.reduced2",
+# 		"dat.str_total.reduced10",
 # 		"dat.syn.reduced", "dat.syn.reduced2", "dat.syn.reduced10",
-# 		"dat.syn_total.reduced", "dat.syn_total.reduced2"
+# 		"dat.syn_total.reduced", "dat.syn_total.reduced2",
+# 		"dat.syn_total.reduced10"
 # 	)
 # )
 # interventions$mwf <- sapply(
@@ -84,27 +91,52 @@ dat.syn.reduced10 <- box_read(942772072287)
 # })
 #
 # saveRDS(interventions, here::here("resources", "percent-py-intervened.rds"))
-#
+
 exposure.comparison <- rbindlist(c(
 	list(dat.reduced[, .(
-		studyno, I, status, year, py, `Cumulative soluble`, cum_soluble)]),
[…]

### 2022-09-15 shape-data.R

@@ -552,7 +552,7 @@ get.limit_total_intervention <- function(
 			return(x)
 		})]
 
-	df[straight + soluble + synthetic < limit, .(straight, studyno, year)]
+	df[straight + soluble + synthetic <= limit, .(straight, studyno, year)]
 
 	df[, (paste0("cum_", mwf)) := cumsum(get(mwf)), by = .(studyno)]
 	df[,(c(str_to_title(mwf), paste0("Cumulative ", mwf))) := list(
@@ -577,6 +577,7 @@ dat.str10 <- get.limit_intervention(mwf = 'str', limit = 0.5/10)
 
 dat.str_total  <- get.limit_total_intervention(mwf = "str", limit = 0.5)
 dat.str_total2 <- get.limit_total_intervention(mwf = "str", limit = 0.5/2)
+dat.str_total10 <- get.limit_total_intervention(mwf = "str", limit = 0.5/10)
 
 #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 # Soluble to REL							                   ####
@@ -592,6 +593,7 @@ dat.sol10 <- get.limit_intervention(mwf = 'sol', limit = 0.5/10)
 
 dat.sol_total  <- get.limit_total_intervention(mwf = "sol", limit = 0.5)
 dat.sol_total2 <- get.limit_total_intervention(mwf = "sol", limit = 0.5/2)
+dat.sol_total10 <- get.limit_total_intervention(mwf = "sol", limit = 0.5/10)
 
 #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 # Synthetic to REL							                 ####
@@ -607,6 +609,7 @@ dat.syn10 <- get.limit_intervention(mwf = 'syn', limit = 0.5/10)
 
 dat.syn_total  <- get.limit_total_intervention(mwf = "syn", limit = 0.5)
 dat.syn_total2 <- get.limit_total_intervention(mwf = "syn", limit = 0.5/2)
+dat.syn_total10 <- get.limit_total_intervention(mwf = "syn", limit = 0.5/10)
 
 #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 # Compare exposure before/after intervention     ####
[…]

### 2022-09-30 reports/paper/03-results.rmd
New revisions

@@
 				x <- value
-				x[!is.na(x)] <- quantile(x[!is.na(x)], 0.025) - mean(x[!is.na(x)]) + estimate[1]},
+				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
 			upper = {
 				x <- value
-				x[!is.na(x)] <- quantile(x[!is.na(x)], 1 - 0.025) - mean(x[!is.na(x)]) + estimate[1]}
+				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
 			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),

### 2022-09-30 reports/paper/paper.Rmd
New revisions

@@
 
-**Authors:** Kevin T. Chen^a,b^, Sally Picciotto^b^, Ellen A. Eisen^b^
+**Authors:** Kevin T. Chen^a,b^, Ellen A. Eisen^b^, Sally Picciotto^b^
 
@@
 
-**Sources of financial support:** Supported by Training Grant T42OH008429, funded by the National Institute for Occupational Safety and Health (NIOSH) / Centers for Disease Control and Prevention (CDC)
+**Sources of financial support:** This work was supported by Training Grant T42OH008429 and Research Project Grant R01OH011092, both funded by the National Institute for Occupational Safety and Health (NIOSH) / Centers for Disease Control and Prevention (CDC).
 
@@
 These stochastic interventions included (1) static interventions on soluble MWF that ignore exposure to other types and (2) dynamic interventions that seek to cap total exposure to any type of MWF by intervening on exposure to soluble MWF only.
+Static interventions may be more feasible as real-world policy, but dynamic interventions may result in stronger protections.
 

### 2022-09-30 reports/ACIC (2022)/poster/resources/rr.tex
Clean up and prepare for submission

@@
-% Created by tikzDevice version 0.12.3.1 on 2022-05-20 15:39:29
+% Created by tikzDevice version 0.12.3.1 on 2022-09-30 16:23:45
 % !TEX encoding = UTF-8 Unicode
 \documentclass[10pt]{article}
-\usepackage{amssymb}
-\usepackage[no-math]{fontspec}
-
-\setmainfont{Arial}
-
-\usepackage[italic]{mathastext}
 \usepackage{tikz}
@@
 
-\begin{tikzpicture}[x=1pt,y=1pt]
-\definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,126.47);
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
-\definecolor{drawColor}{RGB}{255,255,255}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,126.47);
-\end{scope}
-\begin{scope}
-\path[clip] ( 35.37, 28.21) rectangle (283.58,120.97);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 35.37, 28.21) rectangle (283.58,120.97);
-\definecolor{drawColor}{RGB}{16,36,81}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.11,101.41) --
-	(213.11,105.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.11,103.58) --
-	(118.54,103.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (118.54,101.41) --
-	(118.54,105.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (197.44, 43.43) --
-	(197.44, 47.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (197.44, 45.61) --
-	( 86.05, 45.61);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.05, 43.43) --
-	( 86.05, 47.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (212.09, 72.42) --
-	(212.09, 76.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (212.09, 74.59) --
-	(104.01, 74.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (104.01, 72.42) --
-	(104.01, 76.77);
-\definecolor{fillColor}{RGB}{16,36,81}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.35,103.58) circle (  1.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.20, 45.61) circle (  1.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.25, 74.59) circle (  1.32);
-\definecolor{drawColor}{RGB}{16,36,81}
-
-\path[draw=drawColor,draw opacity=0.70,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (207.83, 28.21) -- (207.83,120.97);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37, 28.21) rectangle (283.58,120.97);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 42.85) {0.05};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 71.84) {0.25};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,100.83) {0.5};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 45.61) --
-	( 35.37, 45.61);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 74.59) --
-	( 35.37, 74.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,103.58) --
-	( 35.37,103.58);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.88, 25.46) --
-	( 78.88, 28.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (143.36, 25.46) --
-	(143.36, 28.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.83, 25.46) --
-	(207.83, 28.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (272.30, 25.46) --
-	(272.30, 28.21);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 78.88, 17.75) {0.6};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (143.36, 17.75) {0.8};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (207.83, 17.75) {1.0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (272.30, 17.75) {1.2};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (159.47,  7.25) {Risk ratio};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,126.47);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70, 74.59) {Hypothetical limit (mg/m$^3$)};
-\end{scope}
-\end{tikzpicture}
-
 \end{document}

### 2022-09-30 reports/paper/01-introduction.rmd
New revisions
Clean up and prepare for submission

@@
 
-Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered intense research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons [@seer_1994;@Ekstrom-Smedby_2006].
+Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered intense research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons per year [@seer_1994;@Ekstrom-Smedby_2006].
 The strongest known risk factor of NHL is immunosuppression, both congenital and acquired [@Filipovich_1992;@Chiu_2015].
@@
 Here, we assess the effect of hypothetical MWF exposure limits on NHL cumulative incidence in the United Auto Workers-General Motors (UAW-GM) Occupational Cohort Study.
-In particular, we assess the effect of limits on soluble MWF that (1) ignore exposure to other types of MWF and (2) account for other types of MWF exposure by intervening more strongly on soluble MWF when exposure to all types of MWF is high.
+In particular, we assess the effect of limits on soluble MWF that (1) ignore exposure to other types of MWF and (2) account for other types of MWF exposure by intervening more strongly on soluble MWF when the sum of exposure to all types of MWF is high.
 The latter approach is more consistent with the NIOSH REL, which was recommended for exposure to any type of MWF.
+However, taking into account workers' exposure to different types of MWF may require closer monitoring and more intensive intervention.
 The large size of the study population and rich time-varying, quantitative MWF exposure data provide an opportunity to study this relatively rare cancer and evaluate realistic interventions on MWF exposure in a longitudinal cohort setting.
@@
 This association was based on a traditional Cox proportional hazards regression, a method vulnerable to bias due to confounding by time-varying factors affected by prior exposure.
-We therefore explore this association using a novel causal estimator capable of adjusting for time-varying confounding and censoring affected by past exposure.
+We therefore explore this association using a novel estimator capable of adjusting for time-varying confounding and censoring affected by past exposure.
 This estimator also yields marginal effect estimates of hypothetical interventions, which are more compatible with a population health framework than conditional measures.

### 2022-09-30 reports/paper/02-methods.rmd
Clean up and prepare for submission

@@
 However, since workers were often exposed to multiple types of MWF, both daily and cumulatively, we also evaluated the effect of limiting total MWF exposure to those hypothetical limits by intervening only on exposure to soluble MWF.
-These interventions, which take into consideration exposure to MWF of other types, are dynamic interventions on exposure to soluble MWF.
+These interventions, which take into consideration exposure to MWF of other types when deciding how much soluble MWF exposure to assign, are dynamic interventions on exposure to soluble MWF.
 All of the hypothetical interventions we evaluate are stochastic interventions rather than deterministic interventions because post-intervention exposures take on a range of values.
@@
 The present study population (N = 34,738) was restricted to the autoworkers who were at work in 1941 or not yet hired, missing no more than half of their employment history, and still alive at the start of follow-up.
-Autoworkers in the study population were followed for NHL incidence from January 1, 1985 until NHL diagnosis, death, 10 years after the end of employment records, or upon reaching the oldest observed age at death (108 years), whichever came earlier.
+Autoworkers in the study population were followed for NHL incidence from January 1, 1985 until NHL diagnosis, death, January 1, 2005 (10 years after the end of employment record availability), or age 108 years (the oldest observed age at death), whichever came earlier.
 
@@
 These data were combined with the historical data to derive quantitative 8-hour time-weighted average exposure estimates to soluble, straight, and synthetic MWFs for each combination of job, department, and plant over time.
-Workers' time-weighted average annual exposure to each MWF type was determined by combining this job-exposure matrix with employment records, which recorded time-varying job type, department, and plant.
+Workers' time-weighted average annual exposure to each MWF type was determined by combining this job-exposure matrix with employment records, which recorded time-varying job type, department, and plant through 1994.
 For employment records that were at least half complete, gaps in the record were interpolated by carrying forward the last known job type.
 The exposure assessment is described in detail elsewhere [@Hallock_1994;@Woskie_1994;@Woskie_2003].
-Previous analyses of NHL applied exposure lags of 1 to 20 years; we lagged cumulative MWF exposures by 10 years to account for disease latency [@Smith_2007;@Karipidis_2007;@Zhang_2019].
+Previous analyses of NHL applied exposure lags of 1 to 20 years; we lagged cumulative MWF exposures by 10 years to account for disease latency and therefore ended follow-up on January 1, 2005 [@Smith_2007;@Karipidis_2007;@Zhang_2019].
 
@@
 The remaining three interventions were dynamic interventions that reduced average annual exposure to soluble MWF with the goal of enforcing the hypothetical limits for total exposure to MWF, regardless of type.
-If those limits on total average annual exposure were not possible by intervention on exposure to soluble MWF alone, average annual exposure to soluble MWF was reduced to 0.
+Under these interventions, exposures in some person-years did not comply with the hypothetical limit on total exposure to MWF.
+That is, if the sum of exposures to straight and synthetic MWF exceeded the hypothetical limit, average annual exposure to soluble MWF was simply reduced to 0; we did not evaluate interventions on exposures to the other two classes of MWF.
 Interventions were applied at hire, before the start of follow-up, through the end of follow-up.

### 2022-09-30 reports/paper/03-results.rmd
Clean up and prepare for submission

@@
 Exposure to MWF generally followed a downward trend over time.
-<!-- Figure 2 shows the post-intervention distribution of the logarithm of cumulative exposure to soluble MWF at end of follow-up if hypothetical limits on average annual exposure were enforced for all workers starting at hire.
-The interventions shifted the distribution of cumulative exposure rather than deterministically assigning exposure to a particular value.
--->
 
@@
 Table 2 presents the hazard-extended ICE parametric g-formula estimates of the risk and risk ratios contrasting hypothetical limits on exposure to soluble MWF to no limit, after elimination of competing risks.
-The estimated risk under no limit on MWF exposure was 9.56 (8.15, 10.89) per 1000.
+Under an intervention eliminating competing risks, the estimated risk under no limit on MWF exposure was 9.56 (8.15, 10.89) per 1000.
 Stronger limits on average annual exposure to soluble MWFs resulted in monotonically stronger reductions in the risk of NHL.
-Capping average annual exposure to soluble MWFs at 0.5 mg/m^3^, 0.25 mg/m^3^, and 0.05 mg/m^3^ resulted in a risk of 8.30 (6.52, 10.19), 8.06 (6.15, 10.15), and 7.52 (5.73, 9.51) per 1000, respectively.
-The risk ratios contrasting these hypothetical limits to no limit were 0.87 (0.72, 1.02), 0.84 (0.68, 1.01), and 0.79 (0.62, 0.97).
-Dynamic reductions in soluble exposure with the aim of capping total MWF exposure also yielded monotonically protective risk ratios: 0.84 (0.69, 0.99), 0.80 (0.64, 0.98), and 0.72 (0.48, 1.01).
+Capping average annual exposure to soluble MWFs at 0.5 mg/m^3^, 0.25 mg/m^3^, and 0.05 mg/m^3^ resulted in a risk of 8.30 (6.44, 10.12), 8.06 (6.00, 10.01), and 7.52 (5.57, 9.35) per 1000, respectively.
+The risk ratios contrasting these hypothetical limits to no limit were 0.87 (0.73, 1.02), 0.84 (0.68, 1.01), and 0.79 (0.61, 0.97).
+Dynamic reductions in soluble exposure with the aim of capping total MWF exposure also yielded monotonically protective risk ratios: 0.84 (0.69, 0.99), 0.80 (0.64, 0.97), and 0.72 (0.44, 0.97).
 The dynamic interventions seeking to cap total MWF exposure at 0.5 mg/m^3^ and 0.25 mg/m^3^ attained risk reductions of similar magnitude as the static interventions enforcing (stronger) exposure limits at 0.25 and 0.05 mg/m^3^, respectively, but do so while intervening on a smaller proportion of person-years.
-
-<!-- Results for interventions on straight and synthetic MWF are presented in Tables S1 and S2 in the Appendix.
-The relative risks contrasting interventions on straight and synthetic MWF exposure to the natural course were much smaller in magnitude than those for soluble; none were statistically significant.
-Since exposure to soluble MWF was greatest in prevalence and magnitude, limits on soluble MWF would result in interventions on a greater percentage of person-years than limits on straight or synthetic MWF.
-The intervention capping average annual exposure to soluble MWF at the REL affected 23.8% of the person-years in the follow-up period.
-Limiting straight and synthetic MWF exposure to the REL affected 3.2% and 1.1% of the person-years under follow-up, respectively.
--->
 

### 2022-09-30 reports/paper/paper.Rmd
Clean up and prepare for submission

@@
 
-**Running head suggestion:** Limits on metalworking fluid for preventing NHL
+**Running head suggestion:** Limits on metalworking fluid for preventing NHL.
 
-**Conflicts of interests:** Authors declare no conflicts of interest
+**Conflicts of interests:** Authors declare no conflicts of interest.
 
@@
 **Background:** Non-Hodgkin lymphoma (NHL) incidence has increased significantly since 1960 and was recently linked with workplace exposure in the United Auto Workers-General Motors (UAW-GM) Cohort Study.
-Here, we investigate hypothetical interventions on workplace exposure to soluble metalworking fluids (MWF) in relation to NHL risk.
-Interventions on entire classes of occupational exposures rather than particular agents may result in stronger lasting protections for worker health while preventing regrettable replacements.
+Here, we investigate hypothetical interventions on workplace exposure to oil- and water-based soluble metalworking fluids (MWF) in relation to NHL risk.
+Interventions on entire classes of occupational exposures rather than particular agents may result in stronger lasting protections for worker health.
 
-**Methods:** We estimated counterfactual risk of NHL from 1985 to 2004 in the UAW-GM cohort of hourly autoworkers exposed to straight, soluble, and synthetic MWF at 3 Michigan plants under hypothetical interventions.
-We contrasted counterfactual risk under stochastic interventions on average annual exposure to soluble MWF to that under no intervention on exposure.
-These stochastic interventions included (1) static interventions on soluble MWF that ignore exposure to other types and (2) dynamic interventions that seek to cap total exposure to any type of MWF by intervening on exposure to soluble MWF only.
-Static interventions may be more feasible as real-world policy, but dynamic interventions may result in stronger protections.
+**Methods:** We estimated counterfactual risk of NHL between 1985 and 2004 in the UAW-GM cohort of autoworkers exposed to straight, soluble, and synthetic MWF at three Michigan plants under hypothetical interventions.
+We estimated the effect of static and dynamic stochastic interventions on average annual exposure to soluble MWF.
+Unlike the static interventions, dynamic interventions take into account exposures to the other two classes of metalworking fluids, reflecting the fact that currently recommended limits apply to the total of all three exposures.
 
@@
 Stronger hypothetical limits on average annual exposure to soluble MWF resulted in monotonically stronger reductions in NHL risk.
-Capping exposure to soluble MWF at 0.05 mg/m^3^ resulted in a risk ratio of 0.79 (95% CI: 0.62, 0.97).
-Capping total MWF exposure at 0.05 mg/m3 by intervening only on exposure to soluble MWF resulted in a risk ratio of 0.72 (95% CI: 0.48, 1.01).
+Capping exposure to soluble MWF at 0.05 mg/m^3^ resulted in a risk ratio of 0.79 (95% CI: 0.61, 0.96).
+Capping total MWF exposure at 0.05 mg/m^3^ by intervening only on exposure to soluble MWF resulted in a risk ratio of 0.72 (95% CI: 0.44, 0.97).
 
-**Conclusion:** We considered realistic interventions more compatible with a population health framework than deterministic interventions and showed that stronger limits on average annual exposure to soluble MWF may confer stronger protection against NHL risk.
+**Conclusion:** We considered interventions on soluble MWF that address total MWF exposure levels and showed that stronger limits on average annual exposure to soluble MWF may confer stronger protection against NHL risk.
 

### 2022-09-30 blip.R

@@ -1,95 +1,0 @@
-# Blip function for stochastic intervention ####
-# Kevin
-# April 21, 2021
-
-get.blip_intervention <- function(dta, mwf.intervention = mwf.which, a = 1, delta = 0.6) {
-
-	if (a == 1) {
-		for (mwf.which in mwf.intervention) {
-
-			dta.a1 <- data.table::copy(dta)
-
-			mwf <- unlist(dta.a1[, mwf.which, with = F])
-			intervention.which <- which(mwf > min(mwf) + delta)
-
-			mwf[intervention.which] <- mwf[intervention.which] - delta
-
-			# Change continuous
-			dta.a1[, (mwf.which) := list(mwf)]
-			dta.a1[, (paste0("cum_", mwf.which)) := list(cumsum(get(mwf.which))), by = .(studyno)]
-
-			dta.a1[,(c(str_to_title( mwf.which),
-								 paste0("Cumulative ", mwf.which))) := list(
-								 	get.cut(get(mwf.which), mwf.breaks, mwf.which),
-								 	get.cut(get(paste0("cum_", mwf.which)), mwf.breaks, paste0("cum_", mwf.which))
-								 )]
-
-		}
-		return(dta.a1)
-	} else {return(dta)}
-}
-
-get.static_intervention <- function(dta, mwf.intervention = mwf.which, a = 0, delta = NULL) {
-
-	a <- a + 1
-
-	for (mwf.which in mwf.intervention) {
-
-		dta.a1 <- data.table::copy(dta)
-		mwf <- mwf.breaks[a:(a + 1), mwf.which, with = F]
-		if (a == 1) {
-			mwf <- max(mwf)
-		} else {
-			if (a >= length(table(dta.a1[,str_to_title(mwf.which), with = F]))) {
-				mwf <- min(mwf)
-			} else {
-				mwf <- median(mwf)
-			}
-		}
-
-		dta.a1[,(mwf.which) := list(mwf)]
-		dta.a1[, (paste0("cum_", mwf.which)) := list(cumsum(get(mwf.which))), by = .(studyno)]
-		# dta.a1[,.(studyno, soluble, Soluble, cum_soluble, `Cumulative soluble`)]
-		dta.a1[,(c(str_to_title( mwf.which),
-							 paste0("Cumulative ", mwf.which))) := list(
-							 	get.cut(get(mwf.which), mwf.breaks, mwf.which),
[…]

### 2022-09-30 g-formula.R

@@ -14,7 +14,6 @@ source("~/headRs/00-my-theme.R")
 library(data.table)
 # # paste(ls(), collapse = ",\n") %>% clipr::write_clip()
 source(here::here("../gm-cancer-inc/breaks.R"))
-source("blip.r")
 
 # Relevant covariates ####
 covariates.which <- c(
@@ -37,14 +36,14 @@ covariates.which <- c(
 # Hazard-extended ICE implementation of g-formula ####
 # Wen et al. (2020)
 ice_gcomp <- function(
-	a = 0,
-	dta = copy(dat.reduced[,covariates.which, with = F]),
-	dta.a1 = NULL,
-	# dta.a1 = copy(dat.a),
-	times = sort(unique(dat.reduced[status == 1]$I), decreasing = T),
-	mwf.name = "soluble",
-	quiet = F,
-	total_effect = F
+		a = 0,
+		dta = copy(dat.reduced[,covariates.which, with = F]),
+		dta.a1 = NULL,
+		# dta.a1 = copy(dat.a),
+		times = sort(unique(dat.reduced[status == 1]$I), decreasing = T),
+		mwf.name = "soluble",
+		quiet = F,
+		total_effect = F
 ) {
 
 	if (total_effect) {
@@ -149,42 +148,42 @@ ice_gcomp <- function(
 
 	# Check positivity
 	if (a != 0) {
-			dta.g <- merge(
-				dta.a1[immortal == 0 & I %in% (J - 1):J, c("studyno",
-								paste0("Cumulative ", mwf.name)
-							),
-							with = F],
-				dta[immortal == 0 & I %in% (J - 1):J & Censored == 0]
-			)
+		dta.g <- merge(
+			dta.a1[immortal == 0 & I %in% (J - 1):J, c("studyno",
+																								 paste0("Cumulative ", mwf.name)
+			),
+			with = F],
+			dta[immortal == 0 & I %in% (J - 1):J & Censored == 0]
+		)
 
-			dta.g.tab <- dta.g[get(
+		dta.g.tab <- dta.g[get(
+			paste0("Cumulative ", mwf.name, ".x")
+		) == get(
+			paste0("Cumulative ", mwf.name, ".y")
+		), .(
+			n = n_distinct(studyno),
+			overlap = sum(get(
 				paste0("Cumulative ", mwf.name, ".x")
 			) == get(
 				paste0("Cumulative ", mwf.name, ".y")
-			), .(
-				n = n_distinct(studyno),
-				overlap = sum(get(
[…]

### 2022-09-30 get-data.R

@@ -74,7 +74,7 @@ if (!('cohort_analytic' %in% ls())) {
 		straight = zoo::na.locf(straight),
 		soluble = zoo::na.locf(soluble),
 		synthetic = zoo::na.locf(synthetic)
-		), by = .(studyno)]
+	), by = .(studyno)]
 
 	cohort_analytic[,`:=`(
 		off = {

### 2022-09-30 run_g-formula.R

@@ -336,87 +336,6 @@ save(
 load(here::here("resources", paste0("estimates.rdata")))
 load(here::here("resources", paste0("h.estimates.rdata")))
 
-
-# Print results
-cat("Observed cumulative incidence:", observed,
-		"\nIntervention cumulative incidence:",
-		"\nNatural course cumulative incidence:\t\t", h.baseline,
-		"\n\tReduce straight to REL:\t\t\t", h.reduction.str,
-		"\n\tReduce straight for total under REL:\t", h.reduction.str_total,
-		"\n\tReduce straight to REL/2:\t\t", h.reduction.str2,
-		"\n\tReduce straight for total under REL/2:\t", h.reduction.str_total2,
-		"\n\tReduce straight to REL/10:\t\t", h.reduction.str10,
-		"\n\tReduce straight for total under REL/10:\t", h.reduction.str_total10,
-		"\n\tReduce soluble to REL:\t\t\t", h.reduction.sol,
-		"\n\tReduce soluble for total under REL:\t", h.reduction.sol_total,
-		"\n\tReduce soluble to REL/2:\t\t", h.reduction.sol,
-		"\n\tReduce soluble for total under REL/2:\t", h.reduction.sol_total,
-		"\n\tReduce soluble to REL/10:\t\t", h.reduction.sol10,
-		"\n\tReduce synthetic to REL:\t\t", h.reduction.syn,
-		"\n\tReduce synthetic for total under REL:\t", h.reduction.syn_total,
-		"\n\tReduce synthetic to REL/2:\t\t", h.reduction.syn,
-		"\n\tReduce synthetic for total under REL/2:\t", h.reduction.syn_total,
-		"\n\tReduce synthetic to REL/10:\t\t", h.reduction.syn10,
-		"\n",
-		"Risk ratio:",
-		"\n\tReduce straight to REL:\t\t\t", h.reduction.str/h.baseline,
-		"\n\tReduce straight to REL/2:\t\t", h.reduction.str2/h.baseline,
-		"\n\tReduce straight for total under REL:\t", h.reduction.str_total/h.baseline,
-		"\n\tReduce straight for total under REL/2:\t", h.reduction.str_total2/h.baseline,
-		"\n\tReduce straight for total under REL/10:\t", h.reduction.str_total10/h.baseline,
[…]

### 2022-09-30 shape-data.R

@@ -14,7 +14,6 @@ source("~/headRs/00-my-theme.R")
 library(data.table)
 # # paste(ls(), collapse = ",\n") %>% clipr::write_clip()
 source(here::here("../gm-cancer-inc/breaks.R"))
-source("blip.r")
 
 # Get data ####
 source(here::here("get-data.R"))
@@ -126,7 +125,7 @@ exposure.ggplot <- dat[, .(
 	ggplot(aes(x = year, y = value)) +
 	geom_line()
 tikzDevice::tikz(here::here("resources", "exposure.tex"), height = 2.5, width = 6, standAlone = T)
- exposure.ggplot +
+exposure.ggplot +
 	facet_wrap(. ~ mwf) +
 	labs(x = "Calendar year",
 			 y = "Median exposure (mg/m$^3$) among exposed") +
@@ -136,7 +135,7 @@ dev.off()
 lualatex("^exposure\\.tex", here::here("resources"))
 
 tikzDevice::tikz(here::here("resources", "exposure_long.tex"), height = 5.5, width = 3, standAlone = T)
- exposure.ggplot +
+exposure.ggplot +
 	facet_wrap(. ~ mwf, nrow = 3) +
 	labs(x = "Calendar year",
 			 y = "Median exposure (mg/m$^3$) among exposed") +
@@ -147,13 +146,13 @@ lualatex("^exposure_long\\.tex", here::here("resources"))
 
 # Population characteristics ####
 get.tab1 <- function(
-	df = dat[year >= 1985 & year <= 1994 + exposure.lag],
-	table.engine = "pander",
-	use_finrace = T,
-	incidence = F,
-	py = "py",
-	mathmode = F,
-	nrow_as_fu = T) {
+		df = dat[year >= 1985 & year <= 1994 + exposure.lag],
+		table.engine = "pander",
+		use_finrace = T,
+		incidence = F,
+		py = "py",
+		mathmode = F,
+		nrow_as_fu = T) {
 
 	setorder(df, studyno, year)
 	# Individual-level summary
@@ -201,7 +200,7 @@ get.tab1 <- function(
 		# Years since follow-up
 		"\\hline Years of follow-up" = if (nrow_as_fu) {.N} else {
 			as.numeric(difftime(min(yod[1], yoc[1], as.Date(paste0(max(year), "-12-31")), na.rm = T),
[…]

### 2023-03-02 reports/paper/01-introduction.rmd
manuscript prepared

--- 2022-09-15 reports/paper/01-introduction.rmd
@@
 
-Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered intense research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons [@seer_1994;@Ekstrom-Smedby_2006].
+Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered substantial research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons per year [@seer_1994;@Ekstrom-Smedby_2006].
 The strongest known risk factor of NHL is immunosuppression, both congenital and acquired [@Filipovich_1992;@Chiu_2015].
@@
 Since the rise in NHL incidence coincided with a period of rapid and extensive chemicalization in industry, agriculture and warfare, there has been stronger interest in the environmental and occupational epidemiology on NHL [@Nelson_2005;@Romero_2021].
+
+Pesticide exposure in agricultural occupational settings was a common target of NHL research in recent decades.
 A meta-analysis of 44 articles published between 1980 and 2014 found statistically significant associations between NHL and exposure to pesticides of several classes including carbamate, organophosporus, triazine, and organochlorine [@Schinasi_2014].
-While this meta-analysis presents striking evidence of the potential explanatory role of occupational exposures, it also highlights the limited breadth of occupational exposures studied.
+Occupations associated with NHL are not limited to the agricultural sector, however.
+Metal processors, health workers, salespeople, machinists, and electricians have all been identified as occupational groups with higher risk of NLH [@Fritschi_2005a; @Mester_2006; @Ekstrom-Smedby_2006].
+Studies contrasting occupational groups to the general population are vulnerable to exposure misclassification of the true causal agent.
+When different causal agents contribute to overall NHL risk by their effect on particular subtypes of NHL, their etiologic role may be obscured in analyses not stratified by subtype.
+Large multicenter studies including EPILYMPH and INTERLYMPH seek to disentangle effect heterogeneity across NHL subtypes, but are limited by the lack of quantitative time-varying exposure information [@Besson_2006;@t-Mannetje_2008;@Morton_2014].
 
-Studies of NHL and other important occupational exposures including oils, solvents, and lubricants remain inconclusive [@Ekstrom-Smedby_2006].
-Furthermore, since NHL is relatively rare, nearly all studies of NHL incidence follow a single time-point case-control design [@Schinasi_2014;@Alexander_2007].
-Large multicenter studies including EPILYMPH and InterLymph attained large enough numbers of cases to investigate particular NHL subtypes, but despite their impressive size and comprehensiveness, were limited by the lack of quantitative time-varying exposure information and the lack of adjustment for time-varying sources of bias [@Besson_2006;@Morton_2014].
-In the case of occupational studies, the healthy worker survivor effect (HWSE) is a key concern.
+Measures of time-varying exposure are essential to statistical adjustment for forms of time-varying confounding affected by past exposure such as the healthy worker survivor effect (HWSE).
 The HWSE is the dynamic selection process by which healthier individuals remain at work, where they accumulate more occupational exposure, and less healthy individuals leave work [@Arrighi_1994].
@@
 The type of MWF applied depends in part on the particular metalworking operation.
-Straight MWF, the oldest class of MWF, is comprised mostly of mineral oil.
-Concerns over the carcinogenicity of MWF began as early as the 1970s, when the International Agency for Research on Cancer (IARC) classified mineral oils as carcinogenic, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973].
+Straight MWF, the oldest class of MWF, is comprised mostly of mineral oils, which were classified as carcinogenic by the International Agency for Research on Cancer (IARC) in 1973, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973].
 The combination of health concerns, the high cost of oil in the 1970s, and the introduction of performance-enhancing water-soluble chemical additives led to the gradual replacement of straight MWF with water-based soluble and synthetic MWFs for many, but not all operations [@Childers_2005].
-The elimination of particular etiologic agents often leads to their replacement with other potentially hazardous chemical compounds, however [@Kassotis_2020;@Maertens_2021].
+
 Although water-based MWF contain little to no mineral oil, they contain a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987;@IARC_2014;@IARC_2017].
+The elimination of particular etiologic agents often leads to their replacement with other potentially hazardous chemical compounds [@Kassotis_2020;@Maertens_2021].
 Hence, limits on entire classes of exposures grouped by functional use may result in stronger, more lasting protections for worker health than limits on particular etiologic agents because they will remain in place even as the composition and formulation of complex occupational exposures change [@Maertens_2021].
-More than 20 years after the IARC classification of mineral oils as carcinogenic, the National Institute for Occupational Safety and Health (NIOSH) concluded that there exists substantial evidence linking all MWF exposure to several different cancers and now recommends an exposure limit of 0.5 mg/m^3^ for total particulate matter derived from any type of MWF [@niosh_1998;@Mirer_2003].
+More than 20 years after the IARC classification of mineral oils as carcinogenic, the National Institute for Occupational Safety and Health (NIOSH) concluded that there exists substantial evidence linking all MWF exposure to several different cancers.
+However, the NIOSH recommended exposure limit of 0.5 mg/m^3^ for total particulate matter derived from any type of MWF was intended to reduce respiratory disorders and not cancer [@niosh_1998;@Mirer_2003].
 
-Here, we assess the effect of hypothetical MWF exposure limits on NHL cumulative incidence in the United Auto Workers-General Motors (UAW-GM) Occupational Cohort Study.
-In particular, we assess the effect of limits on soluble MWF that (1) ignore exposure to other types of MWF and (2) account for other types of MWF exposure by intervening more strongly on soluble MWF when exposure to all types of MWF is high.
-The latter approach is more consistent with the NIOSH REL, which was recommended for exposure to any type of MWF.
+Here, we assess the effect of hypothetical MWF exposure limits on NHL cumulative incidence (which we will refer to as risk) from 1985 to 2005 in the United Auto Workers-General Motors (UAW-GM) Occupational Cohort Study.
 The large size of the study population and rich time-varying, quantitative MWF exposure data provide an opportunity to study this relatively rare cancer and evaluate realistic interventions on MWF exposure in a longitudinal cohort setting.
 A recent study of cancer incidence in this iconic occupational cohort found a monotonic association between NHL and exposure to soluble MWF [@Colbeth_2022].
-This association was based on a traditional Cox proportional hazards regression, a method vulnerable to bias due to confounding by time-varying factors affected by prior exposure.
-We therefore explore this association using a novel causal estimator capable of adjusting for time-varying confounding and censoring affected by past exposure.
-This estimator also yields marginal effect estimates of hypothetical interventions, which are more compatible with a population health framework than conditional measures.
+This association was based on standard Cox proportional hazards regression, a method vulnerable to bias due to confounding by time-varying factors affected by past exposure.
+We therefore explore this association using an estimator capable of adjusting for time-varying confounding and censoring affected by past exposure: the hazard-extended iterative conditional expectation (ICE) parametric g-formula.
+Like other causal estimators in statistics, the hazard-extended ICE g-formula yields marginal effect estimates of hypothetical interventions, which are more compatible with a population health framework than conditional measures.
+
+The g-formula is a well-known result in causal inference for the identification of causal effects in the presence of time-varying confounding affected by past exposure [@Robins_1986].
+Standard representations of the g-formula include (1) a non-iterated expectation over the joint density of covariates, (2) the ICE over time, and (3) an inverse probability weighted expectation.
+The parametric g-formula is a plug in estimator for the g-formula under its first, non-iterative, representation.
+It involves the parametric modeling of the full joint distribution of the outcome, exposure, and covariates under study for each time point [@Taubman_2009;@Young_2014].
+Counterfactual quantities under hypothetical interventions of interest are computed from Monte Carlo samples from distributions implied by the fitted parametric models.
+In longitudinal settings, this approach often requires specifying and fitting large number of models in order to satisfy the exchangeability assumptions necessary for causal identification.
+<!-- Since applications of the parametric g-formula are often context-laden, there are no unified guidelines for model specification. -->
+
+When researchers are not wholly comfortable with the full set of parametric assumptions required by the parametric g-formula, the ICE g-formula may be preferred.
+Parametric estimators using the ICE representation of the g-formula require modeling only the conditional outcome distributions, so they require fewer parametric assumptions than non-iterative parametric g-formula estimators.
+Counterfactual outcome estimates over the follow-up period are computed from interval-specific conditional estimates by applying the tower rule of expectation.
+Under the assumptions of conditional exchangeability at all time points, positivity, counterfactual consistency, and correct model specification, the hazard-extended parametric g-formula yields unbiased estimates of counterfactual risk with greater statistical efficiency than both propensity score-based estimators and the classical ICE g-formula.

### 2023-03-02 reports/paper/02-methods.rmd
manuscript prepared

@@
 
-We estimated NHL risk from 1985 to 2005 under hypothetical limits on average annual exposure to soluble MWF by applying the novel hazard-extended iterative conditional expectation (ICE) parametric g-formula estimator [@Wen_2020].
+We estimated NHL risk from 1985 to 2005 under hypothetical limits on average annual exposure to soluble MWF by applying the hazard-extended iterative conditional expectation (ICE) parametric g-formula estimator [@Wen_2020].
 We leveraged time-varying quantitative MWF exposure data in tandem with employment records to adjust for the HWSE.
-First, we estimated the expected number of NHL cases per 1000 workers that we would observe if there were no competing risks.
-We contrasted  this counterfactual risk to that when in addition, the hypothetical exposure limits of 0.5, 0.25, and 0.05 mg/m^3^ were enforced for soluble MWF over workers' entire working lifetimes.
-These hypothetical limits are static interventions because they do not consider other covariates or exposures.
-However, since workers were often exposed to multiple types of MWF, both daily and cumulatively, we also evaluated the effect of limiting total MWF exposure to those hypothetical limits by intervening only on exposure to soluble MWF.
-These interventions, which take into consideration exposure to MWF of other types when deciding how much soluble MWF exposure to assign, are dynamic interventions on exposure to soluble MWF.
-All of the hypothetical interventions we evaluate are stochastic interventions rather than deterministic interventions because post-intervention exposures take on a range of values.
+First, we estimated the expected number of NHL cases that we would observe if there were no censoring by competing risks.
+Then, we contrasted this counterfactual risk to that when in addition, the hypothetical exposure limits of (1) the NIOSH Recommended Exposure Limit (REL) for total particulate mass (PM) from MWFs (0.5 mg/m^3^), (2) half the REL (0.25 mg/m^3^), and (3) a tenth of the REL (0.05 mg/m^3^) were enforced for soluble MWF over workers' entire working lifetimes [@niosh_1998].
+Under these hypothetical interventions, exposure was set at the hypothetical limit if observed exposure was greater than that limit.
+Otherwise, exposure not intervened upon.
+This kind of intervention is known as a threshold longitudinal modified treatment policy [@Taubman_2009;@Richardson_2013;@Haneuse_2013;@Young_2014].
+Longitudinal modified treatment policies are intervention strategies that depend on the natural value of exposure at a particular time ie the value of exposure that would have been observed at that time if the intervention were discontinued immediately prior [@Richardson_2013;@Diaz_2021].
 
@@
 
-We identified incident cancers in the UAW-GM Cohort that occurred between 1985 and 2004 by linkage to the Michigan Cancer Registry (MCR).
+We identified incident cancers in the UAW-GM Cohort that occurred between 1985 and 2005 by linkage to the Michigan Cancer Registry (MCR).
 Workers at Plants 1 and 2, located in the greater Detroit metropolitan area, were also linked to the Detroit Regional Registry of the Surveillance, Epidemiology, and End Results (SEER) Program.
@@
 Non-Hodgkin lymphoma was defined by cancers with any of the following ICD-O-3 Histology codes: 9590-9597, 9670-9671, 9673, 9675, 9678-9680, 9684, 9687-9691, 9695, 9698-9702, 9705, 9708-9709, 9712, 9714-9719, 9724-9729, 9735, 9737-9738, 9811-9818, 9823, 9827, 9837.
+Subtypes of NHL were also identified for sensitivity analyses.
 Details regarding cancer incidence follow-up are described elsewhere [@Colbeth_2022].
@@
 In analyses, missing race was considered a distinct category.
+All covariates were coded as categorical variables.
+Cut-points for continuous covariates were determined according to the quantiles among cases.
 
@@
 
+Quantitative measurement of time-varying MWF exposure is a distinguishing strength of the UAW-GM cohort relative to other studies of occupational exposure.
+Exposure assessment was based on direct sampling as well as company records.
 Company industrial hygienists collected several hundred personal and area samples for total particulate matter (mg/m^3^) composed of MWF over many decades.
 Research industrial hygienists collected additional air sampling data when the cohort study was launched in the mid 1980s.
-These data were combined with the historical data to derive quantitative 8-hour time-weighted average exposure estimates to soluble, straight, and synthetic MWFs for each combination of job, department, and plant over time.
+These data were combined with the historical data and company records to derive quantitative 8-hour time-weighted average exposure estimates to soluble, straight, and synthetic MWFs for each combination of job, department, and plant over time.
 Workers' time-weighted average annual exposure to each MWF type was determined by combining this job-exposure matrix with employment records, which recorded time-varying job type, department, and plant through 1994.
@@
 Previous analyses of NHL applied exposure lags of 1 to 20 years; we lagged cumulative MWF exposures by 10 years to account for disease latency and therefore ended follow-up on January 1, 2005 [@Smith_2007;@Karipidis_2007;@Zhang_2019].
+In analyses, MWF exposure history was summarized as the cumulative sum of annual exposure intensities and coded as categorical variables with cut-points determined according the quantiles of cumulative exposure among cases.
 
@@
 
-We applied the hazard-extended ICE parametric g-formula with pooling over treatment history [@Wen_2020] to estimate 20-year counterfactual risk of non-Hodgkin lymphoma.
-We considered six stochastic interventions on average annual exposure to soluble MWFs after the elimination of censoring/competing risks.
-We considered hypothetical exposure limits starting with the NIOSH Recommended Exposure Limit (REL) for total particulate mass (PM) from MWFs (0.5 mg/m^3^).
-Then, we estimated the risk at half the REL (0.25 mg/m^3^), and a tenth of the REL (0.05 mg/m^3^) [@niosh_1998].
-The first three interventions were static interventions which enforced these hypothetical limits on average annual exposure to soluble MWF.
-The remaining three interventions were dynamic interventions that reduced average annual exposure to soluble MWF with the goal of enforcing the hypothetical limits for total exposure to MWF, regardless of type.
-Under these interventions, exposures in some person-years did not comply with the hypothetical limit on total exposure to MWF.
-That is, if the sum of exposures to straight and synthetic MWF exceeded the hypothetical limit, average annual exposure to soluble MWF was simply reduced to 0; we did not evaluate interventions on exposures to the other two classes of MWF.
-Interventions were applied at hire, before the start of follow-up, through the end of follow-up.
-Person-years were not intervened upon if the observed average annual exposure was below the hypothetical limit.
-Figure 1 illustrates the static and dynamic interventions for three person-year examples.
-Panel A shows the observed levels of exposure to soluble MWF and to MWF of other types.
-Panel B shows the post-intervention levels of exposure under a static intervention capping exposure to soluble MWF at the hypothetical limit (dotted line).
-Panel C shows the post-intervention levels under a dynamic intervention reducing exposure to soluble MWF with the goal of capping total MWF exposure at the hypothetical limit.
-Note that in person-year 3, the observed level of exposure to total MWF (and thus, to soluble MWF) is below the hypothetical limit, so the post-intervention exposure is left at the observed level.
-
-![Figure 1.
-Observed and post-intervention levels of exposure to soluble MWF and MWF of other types in three example person-years.
-The white boxes represent exposure to soluble MWF, and the shaded boxes represent exposure to MWF of other types.
-The horizontal dotted line represents the hypothetical exposure limit.](`r here::here("resources/images", "interventions.png")`){width=6.5in}
-
-The hazard-extended ICE parametric g-formula estimator is an ICE expression of the parametric g-formula estimator further extended to incorporate the predicted hazard of past outcomes [@Wen_2020].
-The classical ICE g-formula estimator is algebraically equivalent to the noniterative conditional expectation (NICE) g-formula estimator, which typically involves computing covariate-standardized estimates sequentially, starting at the index time, by specifying parametric models for the joint distribution of the confounders, exposures, and outcomes at each time point [@Taubman_2009].
-In contrast, ICE g-formula estimators avoid the need for modeling the entire joint distribution of observed variables and only require outcome models for each time point.
-Counterfactual outcome estimates over the follow-up period are computed from interval-specific conditional estimates by applying the tower rule of expectation.
-Under the assumptions of conditional exchangeability at all time points, positivity, counterfactual consistency, and correct model specification, the hazard-extended parametric g-formula yields unbiased estimates of counterfactual risk with greater statistical efficiency than both propensity score-based estimators and the classical ICE g-formula.
-
-Our implementation of the hazard-extended ICE parametric g-formula involved a series of model-based standardization steps using logistic regression.
+The hazard-extended ICE parametric g-formula may be thought of as a series of model-based standardization steps, which we implemented using logistic regression.
+We split the 20-year follow-up period into eight time periods; the first two periods spanned four years each, and the remaining six periods spanned two years each.
+The first two periods are longer in length to account for the smaller number of cases in those years.
 Post-intervention estimates of the discrete hazard of NHL given all exposures and covariates were combined iteratively from the end of follow-up to the start.
 In each iteration, predicted discrete hazards were standardized over post-intervention exposure and covariate histories before combining with discrete hazards from the previous iteration.
-This iterative process resulted in sequentially standardized estimates of NHL risk over the entire follow-up period.
-Averaging over the baseline distribution of covariates yielded the counterfactual risk estimate of NHL when the intervention of interest was enforced for the entire study population.
+This iterative process results in sequentially standardized estimates of NHL risk over the entire follow-up period.
+Averaging over the baseline distribution of covariates yields the counterfactual risk estimate of NHL when the intervention of interest was enforced for the entire study population.
 
-We split the 20-year follow-up period into eight time periods; the first two periods spanned four years each, and the remaining six periods spanned two years each.
-The first two periods are longer in length to account for the smaller number of cases in those years.
 Post-intervention exposure and exposure history were summarized as cumulative exposure.
@@
 All continuous variables were represented as categorical variables with cut points determined by the tertiles of nonzero values among NHL cases.
-During the iterative combination of discrete hazards, we performed model-based standardization over baseline covariates and the complete set of time-varying covariate histories.
+An overview of the general steps of the estimation procedure are presented below.
+
+0.  For the hypothetical exposure limit of interest, compute the cumulative exposure
+    each worker would have accrued by the end of each follow-up period since hire.
+1.  Fit a pooled logistic regression to the observed data for NHL on covariates and
+    cumulative exposure over all at-risk person-periods, excluding those ending with a
+    censoring event.
+2.  Replace the cumulative exposure vector in the observed data with the
+    post-intervention cumulative exposure vector. Using the model fitted in the 
+    previous step, compute estimates of the post-intervention discrete hazard for
+    each at-risk person-period including those that end with a censoring event.
+3.  Set $k = K - 1$ where $K = 8$ is the number of follow-up periods:
+
+	a) Among those who were event-free and uncensored through the $k$^th^ period,
+		 fit a logistic regression on the predicted post-intervention discrete hazard
+		 for the period spanning the $(k + 1)$ through $K$^th^ periods given observed
+		 covariate and exposure history up through (and including) the $k$^th^ period.
+	b) Replace the cumulative exposure vector in the observed data with the
+		 post-intervention cumulative exposure vector. Using the model fitted in the
+		 previous step, obtain predicted values for all those who were at-risk in the
+		 $k$^th^ period.
+	c) Compute the predicted post-intervention discrete hazard for the period spanning
+		 the $k$ through $K$^th^ periods by multiplying the predicted values from the
+		 previous step by 1 minus the discrete hazard estimate used to fit the model
+		 in step 3.a and adding that same discrete hazard estimate to the product.
+	d) If $k > 1$, set $k = k - 1$ and return to step 3.a.
+
+4.  Compute the counterfactual risk by averaging the predicted post-intervention
+		discrete hazards for the entire follow-up period for all units.
 
@@
 We contrasted the risk under intervention to that under the natural course by computing relative risks.
-Confidence intervals were computed using the nonparametric bootstrap with 1000 samples and centering on the estimate computed from observed data.
-
-<!-- GITHUB? -->
+Confidence intervals were computed using the nonparametric bootstrap with 1000 Monte Carlo samples from the population at risk at start of follow-up and centering on the estimate computed from observed data.
+All the necessary script used to reproduce the analyses are available on [GitHub](https://github.com/kvntchn/gm-nhl-ice).

### 2023-03-02 reports/paper/03-results.rmd
manuscript prepared

@@
 											tab.cap.tnd = 1)
-if (!'tidyr' %in% loadedNamespaces()) {library(tidyverse)}
+library(magrittr); library(ggplot2)
 library(flextable)
@@
 
-Table 1 presents summary statistics of exposure and covariates for the full study population and for those diagnosed with NHL between 1985 and 2004.
+Table 1 presents summary statistics of exposure and covariates for the full study population and for those diagnosed with NHL between 1985 and 2005.
 The cohort is predominantly white (66%) and male (87%).
@@
 Soluble MWFs were the most widely used MWF type, with approximately 90% of workers ever exposed.
-Median cumulative exposure among the exposed was 6.5 times higher for soluble than for straight MWFs.
+Median cumulative exposure
+among the exposed was 6.5 times higher for soluble than for straight MWFs.
 Figure 2 shows median average annual exposure to the three MWF types among exposed workers over calendar time.
@@
 # tab1 <- tab1[tab1.which,]
-tab1[,-grep("hspace.logical", colnames(tab1))] %>% 
-	data.frame %>% flextable() %>%
-	delete_part(part = "header") %>%
+tab1[,-grep("hspace.logical", colnames(tab1))] |> 
+	data.frame() |> flextable() |>
+	delete_part(part = "header") |>
 	add_header_row(values = c("", "Study population", "", "NHL cases"),
-								 colwidths = c(1, 2, 1, 2)) %>%
-	hline_top(part = "header") %>%
-	hline_top() %>% hline_bottom() %>%
-	hline(which((grepl("[0-9]\\)", tab1$spread))[-1])[1]) %>% width(4, 0.1) %>%
-	width(1, 2.2) %>% width(c(3, 6), 1.1) %>% width(c(2, 5), 0.65) %>%
+								 colwidths = c(1, 2, 1, 2)) |>
+	hline_top(part = "header") |>
+	hline_top() |> hline_bottom() |>
+	hline(which((grepl("[0-9]\\)", tab1$spread))[-1])[1]) |> width(4, 0.1) |>
+	width(1, 2.2) |> width(c(3, 6), 1.1) |> width(c(2, 5), 0.65) |>
 	flextable::compose(
@@
 		value = as_paragraph("Cumulative exposure to MWFs (mg/m",
-												 as_sup("3"), "-years)")) %>%
-	flextable::align(j = 2:6, align = "center", part = "all") %>%
+												 as_sup("3"), "-years)")) |>
+	flextable::align(j = 2:6, align = "center", part = "all") |>
 	footnote(i = grep("Plant$", rownames(tab1)), j = 1, value = as_paragraph(
 		" Plant of longest employment duration among those who worked at multiple plants"),
-		ref_symbols = "a", inline = T) %>%
+		ref_symbols = "a", inline = T) |>
 	footnote(i = grep("Ever exposed|time off", rownames(tab1)), j = 1, value = as_paragraph(
 		" Lagged 10 years"),
-		ref_symbols = "b", inline = T) %>%
+		ref_symbols = "b", inline = T) |>
 	footnote(i = grep("work", rownames(tab1)), j = 1, value = as_paragraph(
 		" Among those who left work by December 31, 1994"),
-		ref_symbols = "c", inline = T) %>%
+		ref_symbols = "c", inline = T) |>
 	# footnote(i = grep("death", rownames(tab1)), j = 1, value = as_paragraph(
 	# 	" Among deceased"),
-	# 	ref_symbols = "d", inline = T) %>%
+	# 	ref_symbols = "d", inline = T) |>
 	footnote(i = grep("Cumulative exposure", rownames(tab1)), j = 1, value = as_paragraph(
 		" Among ever-exposed individuals, lagged 10 years."),
-		ref_symbols = "d", inline = T) %>%
-	add_footer_row(values = "NHL: non-Hodgkin lymphoma.", colwidths = 6) %>%
-	padding(padding = 1.5, part = "all") %>%
+		ref_symbols = "d", inline = T) |>
+	add_footer_row(values = "NHL: non-Hodgkin lymphoma.", colwidths = 6) |>
+	padding(padding = 1.5, part = "all") |>
 	padding(
@@
 		padding.left = 20
-	) %>%
-	merge_at(i = grep("Cumulative exposure", rownames(tab1))) %>%
-	hline_bottom(part = "footer") %>% font(fontname = 'arial') %>%
+	) |>
+	merge_at(i = grep("Cumulative exposure", rownames(tab1))) |>
+	hline_bottom(part = "footer") |> font(fontname = 'arial') |>
 	set_caption(caption = "Summary of population characteristics. Statistics shown above the horizontal line are count (%). Those shown below are median (quartile 1, quartile 3).")
@@
 intervened_py <- readRDS(here::here("resources", "percent-py-intervened.rds"))
-# paste(paste0("\"", intervened_py$dt.name, "\""), collapse = ",\n") %>% clipr::write_clip()
+# paste(paste0("\"", intervened_py$dt.name, "\""), collapse = ",\n") |> clipr::write_clip()
 dat.names <- data.table(
 	dt.name = c(
-		"dat.sol.reduced", "dat.sol.reduced2", "dat.sol.reduced10",
-		"dat.sol_total.reduced", "dat.sol_total.reduced2",
-		"dat.sol_total.reduced10",
-		"dat.str.reduced", "dat.str.reduced2", "dat.str.reduced10",
-		"dat.str_total.reduced", "dat.str_total.reduced2",
-		"dat.str_total.reduced10",
-		"dat.syn.reduced", "dat.syn.reduced2", "dat.syn.reduced10",
-		"dat.syn_total.reduced", "dat.syn_total.reduced2",
-		 "dat.syn_total.reduced10"),
+		"dat.sol.reduced", "dat.sol.reduced2", "dat.sol.reduced10"),
 	variable.dat = c(
-		"soluble", "soluble2", "soluble10",
-		"total by soluble", "total by soluble2",
-		 "total by soluble10",
-		"straight", "straight2", "straight10",
-		"total by straight", "total by straight2",
-		 "total by straight10",
-		"synthetic", "synthetic2", "synthetic10",
-		"total by synthetic", "total by synthetic2",
-		 "total by synthetic10"
-	)
+		"soluble", "soluble2", "soluble10")
 )
@@
 ```{r}
+# Risk ratios
 do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
@@
 })) %>% melt(measure.vars = names(.)) -> rr.bs
+
+# Risk differences
+do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
+	x - estimates.bs[,2]
+})) %>% melt(measure.vars = names(.)) -> rd.bs
 
@@
 	variable = c(
-		"straight", "total by straight", "straight2", "total by straight2",
-		"straight10", "total by straight10",
-		"soluble", "total by soluble", "soluble2", "total by soluble2",
-		"soluble10", "total by soluble10",
-		"synthetic", "total by synthetic", "synthetic2", "total by synthetic2",
-		"synthetic10", "total by synthetic10",
-		"natural"),
+		"soluble", "soluble2", "soluble10", "natural"),
 	estimate = c(
-		h.reduction.str, h.reduction.str_total, h.reduction.str2, h.reduction.str_total2,
-		h.reduction.str10, h.reduction.str_total10,
-		h.reduction.sol, h.reduction.sol_total, h.reduction.sol2, h.reduction.sol_total2,
-		h.reduction.sol10, h.reduction.sol_total10,
-		h.reduction.syn, h.reduction.syn_total, h.reduction.syn2, h.reduction.syn_total2,
-		h.reduction.syn10,h.reduction.syn_total10,
+		h.reduction.sol, h.reduction.sol2, h.reduction.sol10,
 		h.baseline)
 )
-
+```
+```{r}
 # Calculate risk ratios for each bootstrap sample
@@
 	)],
-	all = T,
+	all.x = F,
 	by = "variable")
@@
 # Get lower and upper 2.5th %tiles
-rr <- rr[,.(estimate = estimate[1],
-			lower = {
+rr <- rr[,.(
+	rr = estimate[1],
+	rr_lower = {
 		x <- value
 		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
-			upper = {
+	rr_upper = {
+		x <- value
+		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
+	# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
+	# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
+),
+variable]
+```
+```{r}
+# Calculate risk differences for each bootstrap sample
+rd <- merge(
+	rd.bs,
+	point_estimates[,.(
+		variable = paste0(variable, ".natural"),
+		estimate = estimate - estimate[variable == "natural"]
+	)],
+	all.x = F,
+	by = "variable")
+
+# Get lower and upper 2.5th %tiles
+rd <- rd[,.(
+	rd = estimate[1],
+	rd_lower = {
+		x <- value
+		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
+	rd_upper = {
 		x <- value
@@
 
-# Colleect risks
+rd[,(c('rd', 'rd_lower', 'rd_upper')) := list(
+	- rd * 34734,
+	- rd_upper * 34734,
+	- rd_lower * 34734
+	)]
+
+```
+
+```{r}
+# Combine differences and ratios
+contrasts.tab <- merge(rr, rd, by = 'variable')
+```
+
+```{r}
+# Collect risks
 risks <- merge(
@@
 	point_estimates,
-	all = T,
+	all.x = F,
 	by = "variable")
@@
 	variable = c(
-		"natural", "straight", "soluble", "synthetic",
-		"straight2", "soluble2", "synthetic2",
-		"straight10", "soluble10", "synthetic10",
-		"total by straight", "total by soluble", "total by synthetic",
-		"total by straight2", "total by soluble2", "total by synthetic2",
-		"total by straight10", "total by soluble10", "total by synthetic10"
+		"natural", "soluble", "soluble2", "soluble10"
 	),
 	label = c(
-		"None", rep("0.5", 3), rep("0.25", 3), rep("0.05", 3),
-		"max(0, 0.5 – sol – syn)", "max(0, 0.5 – str – syn)", "max(0, 0.5 – str – sol)",
-		"max(0, 0.25 – sol – syn)", "max(0, 0.25 – str – syn)", "max(0, 0.25 – str – sol)",
-		"max(0, 0.05 – sol – syn)", "max(0, 0.05 – str – syn)", "max(0, 0.05 – str – sol)"
+		"None", "0.5", "0.25", "0.05"
 	)
 )
+
 # Add intervention labels
-rr <- merge(
-	rr, intervention.labels[,.(variable = paste0(variable, ".natural"), label)],
-	all.x = T,
+contrasts.tab <- merge(
+	contrasts.tab, intervention.labels[,.(variable = paste0(variable, ".natural"), label)],
+	all = T,
 	by = "variable"
 )
+
 ```
@@
 	 			"(",
-	 			sprintf(paste0("%.", digits, "f"), round(x$lower * scale, 2)),
+	 			sprintf(paste0("%.", digits, "f"), round(x$lower * scale, digits)),
 	 			", ", 
-	 			sprintf(paste0("%.", digits, "f"), round(x$upper * scale, 2)),
+	 			sprintf(paste0("%.", digits, "f"), round(x$upper * scale, digits)),
 	 			")"), NA)
@@
 
-mwf.flextable <- function(x) {
-	flextable::compose(x, j = c(4, 6), value = as_paragraph(rep("(95% CI)", 2)),
+mwf.flextable <- function(x, n_col = 8) {
+	flextable::compose(x, j = c(4, n_col), value = as_paragraph(rep("(95% CI)", 2)),
 		part = "header"
-	) %>%
-	border_remove() %>%
-	hline_top(part = "header") %>%
-	hline_top() %>% hline_bottom() %>%
-	flextable::align(j = 2:6, align = "center", part = "all") %>%
-	width(width = c(1.7, 1.1, 0.7, 1, 0.5, 1)) %>%
+	) |>
+	border_remove() |>
+	hline_top(part = "header") |>
+	hline_top() |> hline_bottom() |>
+	flextable::align(j = 2:n_col, align = "center", part = "all") |>
+	width(width = c(1.7, 1.1, 0.7, 1, 0.5, 1, 0.5, 1)) |>
 	padding(padding = 1.5, part = "all")
@@
 
-The observed risk of NHL over the 20-year follow-up period was 6.65 per 1000.
-Table 2 presents the hazard-extended ICE parametric g-formula estimates of the risk and risk ratios contrasting hypothetical limits on exposure to soluble MWF to no limit, after elimination of competing risks.
-Under an intervention eliminating competing risks, the estimated risk under no limit on MWF exposure was 9.56 (8.15, 10.89) per 1000.
+The observed risk of NHL over the 20-year follow-up period was 231 per 34,734 (6.65 per 1000).
+Table 2 presents the hazard-extended ICE parametric g-formula estimates of the counterfactual risk, risk difference, and risk ratios contrasting hypothetical limits on exposure to soluble MWF to no limit, after elimination of competing risks.
+Under an intervention eliminating competing risks, the estimated risk under no limit on MWF exposure was 332 (285, 380) per 34,734.
 Stronger limits on average annual exposure to soluble MWFs resulted in monotonically stronger reductions in the risk of NHL.
-Capping average annual exposure to soluble MWFs at 0.5 mg/m^3^, 0.25 mg/m^3^, and 0.05 mg/m^3^ resulted in a risk of 8.30 (6.44, 10.12), 8.06 (6.00, 10.01), and 7.52 (5.57, 9.35) per 1000, respectively.
-The risk ratios contrasting these hypothetical limits to no limit were 0.87 (0.73, 1.02), 0.84 (0.68, 1.01), and 0.79 (0.61, 0.97).
-Dynamic reductions in soluble exposure with the aim of capping total MWF exposure also yielded monotonically protective risk ratios: 0.84 (0.69, 0.99), 0.80 (0.64, 0.97), and 0.72 (0.44, 0.97).
-The dynamic interventions seeking to cap total MWF exposure at 0.5 mg/m^3^ and 0.25 mg/m^3^ attained risk reductions of similar magnitude as the static interventions enforcing (stronger) exposure limits at 0.25 and 0.05 mg/m^3^, respectively, but do so while intervening on a smaller proportion of person-years.
+Capping average annual exposure to soluble MWFs at 0.5 mg/m^3^, 0.25 mg/m^3^, and 0.05 mg/m^3^ resulted in 44 (-6, 91), 52 (-5, 106), and 71 (12, 129) fewer NHL cases, respectively.
+These correspond to risk ratios 0.87 (0.73, 1.02), 0.84 (0.68, 1.01), and 0.79 (0.61, 0.97).
 
@@
 								 standAlone = T)
-rr[grepl("sol|natural\\.natural", variable) & !grepl(
-	"[a-z]", label),] %>% ggplot(
-	aes(x = factor(label,
-								 rev(c("0.5", "0.25", "0.05"))), y = estimate,
-			ymin = lower, ymax = upper)
+contrasts.tab[grepl("sol|natural\\.natural", variable) & !grepl(
+	"[a-z]", label),] |> ggplot(
+		aes(x = factor(label, rev(c("0.5", "0.25", "0.05"))),
+				y = rd, ymin = rd_lower, ymax = rd_upper)
 	) +
-	geom_errorbar(size = 0.5, width = 0.15, color = '#102451') +
+	geom_errorbar(linewidth = 0.5, width = 0.15, color = '#102451') +
 	geom_point(size = 0.9, color = '#102451') + 
-	geom_hline(yintercept = 1, lty = 2, color = '#102451', alpha = 0.7) + mytheme + labs(
-	y = "Risk ratio",
-	x = "Hypothetical limit (mg/m$^3$)"
-) +
-	coord_flip(ylim = c(0.5, 1.2)) +
+	geom_hline(yintercept = 1, lty = 2, color = '#102451', alpha = 0.7) +
+	labs(
+		y = "Cases averted",
+		x = "Hypothetical limit (mg/m$^3$)") +
+	mytheme +
+	coord_flip(ylim = c(-15, 130)) +
 	theme(panel.grid = element_blank())
@@
 ```{r}
-rr[grepl("sol|natural\\.natural", variable),.(
+contrasts.tab[grepl("sol|natural\\.natural", variable),.(
 	 	label,
 	 	`Person-years intervened (%)` = clean_percent_py(variable),
-	 	`Risk per 1000` = clean_risk(variable, scale = 1000), # 34737),
-	 	`(risk 95% CI)` = clean_risk.ci(variable, scale = 1000), # 34737),
-	 	RR              = sprintf("%.2f", round(estimate, 2)),
-	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
-	 )][c(1, 2, 4, 3, 5, 7, 6),] -> sol.tab
+	 	`Risk`  = clean_risk(variable, 0, 34734),
+	 	`(Risk 95% CI)`      = clean_risk.ci(variable, 0, 34734),
+	 	`RD`    = round(rd),
+	 	`(RD 95% CI)`        = c(NA, paste0(
+	 		"(",
+	 		round(na.exclude(rd_lower)), ", ",
+	 		round(na.exclude(rd_upper)), ")")),
+	 	RR              = sprintf("%.2f", round(rr, 2)),
+	 	`(RR 95% CI)`   = clean_rr.ci(rr, rr_lower, rr_upper)
+	 )][c(1, 2, 4, 3),] -> sol.tab
 
+sol.tab[sol.tab == "NA"] <- NA
 # saveRDS(sol.tab, here::here('resources', 'sol.tab.rds'))
 
-sol.tab %>% flextable %>%
+sol.tab |> flextable() |>
 	flextable::compose(j = 1, value = as_paragraph(
-				"Exposure limit on soluble MWF (mg/m", as_sup("3"), ")"),
+				"Exposure limit (mg/m", as_sup("3"), ")"),
 		part = "header"
-	) %>% mwf.flextable %>%
-	width(width = c(1.7, 1.1, 0.65, 1.1, 0.65, 0.9)) %>%
+	) |> mwf.flextable() |>
+	width(width = c(1.1, 1.1, 0.5, 0.9, 0.45, 0.9, 0.55, 0.9)) |>
 	add_footer_row(values = paste(
-		"MWF: metalworking fluid;",
-		"str: exposure to straight metalworking fluids;",
-		"syn: exposure to synthetic metalworking fluids.",
-		sep = "\n"), colwidths = 6) %>%
-	hline_bottom(part = "footer") %>%
-	set_caption(caption = "Counterfactual risks (per 1000)  and risk ratios contrasting interventions on soluble MWF to the observed course.")
+		"Note. Counterfactual risk and risk difference estimates were expressed per 34,734.",
+		"MWF: metalworking fluid",
+		sep = "\n"), colwidths = 8) |>
+	hline_bottom(part = "footer") |>
+	set_caption(caption = "Counterfactual risk, risk difference, and risk ratio estimates contrasting interventions on soluble MWF to the observed course.")
 
 ```
-
-```{r}
-rr[grepl("str|natural\\.natural", variable),.(
-	 	label,
-	 	`Person-years intervened (%)` = clean_percent_py(variable),
-	 	`Risk per 1000` = clean_risk(variable),
-	 	`(risk 95% CI)` = clean_risk.ci(variable),
-	 	RR              = sprintf("%.2f", round(estimate, 2)),
-	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
-	 )][c(1, 2, 4, 3, 5, 7, 6),] -> str.tab
-
-str.tab %>% flextable %>%
-	flextable::compose(j = 1, value = as_paragraph(
-				"Exposure limit on straight MWF (mg/m", as_sup("3"), ")"),
-		part = "header"
-	) %>% mwf.flextable %>%
-	add_footer_row(values = paste(
-		"MWF: metalworking fluid;",
-		"sol: exposure to soluble metalworking fluids;",
-		"syn: exposure to synthetic metalworking fluids.",
-		sep = "\n"), colwidths = 6) %>%
-	hline_bottom(part = "footer") %>%
-	set_caption(caption = "Counterfactual risks (per 1000)  and risk ratios contrasting interventions on straight MWF to the observed course.") -> str.flextab
-saveRDS(str.flextab, "str.flextab.rds")
-```
-
-```{r}
-rr[grepl("syn|natural\\.natural", variable),.(
-	 	label,
-	 	`Person-years intervened (%)` = clean_percent_py(variable),
-	 	`Risk per 1000` = clean_risk(variable),
-	 	`(risk 95% CI)` = clean_risk.ci(variable),
-	 	RR              = sprintf("%.2f", round(estimate, 2)),
-	 	`(RR 95% CI)`   = clean_rr.ci(estimate, lower, upper)
-	 )][c(1, 2, 4, 3, 5, 7, 6),] -> syn.tab
-
-syn.tab %>% flextable %>%
-	flextable::compose(j = 1, value = as_paragraph(
-				"Exposure limit on synthetic MWF (mg/m", as_sup("3"), ")"),
-		part = "header"
-	) %>% mwf.flextable %>%
-	add_footer_row(values = paste(
-		"MWF: metalworking fluid;",
-		"str: exposure to straight metalworking fluids;",
-		"sol: exposure to soluble metalworking fluids.",
-		sep = "\n"), colwidths = 6) %>%
-	hline_bottom(part = "footer") %>%
-	set_caption(caption = "Counterfactual risks (per 1000)  and risk ratios contrasting interventions on synthetic MWF to the observed course.") -> syn.flextab
-saveRDS(syn.flextab, "syn.flextab.rds")
-```

### 2023-03-02 reports/paper/04-discussion.rmd
manuscript prepared

@@
 We found a monotonic exposure-dependent relationship with lower risk estimates arising from stronger limits.
-Contrasts in estimated NHL risk were statistically significant under the strongest static intervention, which limited soluble MWF exposure to 0.05 mg/m^3^ (a tenth of the current NIOSH REL), and the two dynamic interventions, which sought to limit total MWF exposure to 0.5 and 0.25 mg/m^3^ (the REL and half the REL, respectively) by intervening only on exposure to soluble MWF.
 
 Under the assumptions of conditional exchangeability, positivity, consistency, and correct model specification, our estimates are unbiased for the true counterfactual risk under the hypothetical interventions.
-Conditional exchangeability means that for all time points, there is no confounding of the relationship between exposure/censoring and NHL status at all future time points given the observed past, including past exposure and covariates.
+Conditional exchangeability means that for all time points, there is no confounding of the relationship between exposure/censoring and both future exposure/censoring and NHL status given the observed past, including past exposure and covariates [@Richardson_2013;@Diaz_2021].
 A major threat to conditional exchangeability in longitudinal occupational studies is the HWSE.
@@
 Positivity refers to the need for adequate variation in future exposure among strata formed by observed covariate and intervention-compliant exposure histories.
-Even under conditional exchangeability, where exposures within these strata may be considered the result of experimental assignment, expected counterfactual outcomes under different exposures may not be estimable if there is sparsity in the observed distribution of exposures [@Maldonado_2002].
+Even under conditional exchangeability, where exposures within these strata may be considered the result of experimental assignment, expected counterfactual outcomes under different exposures may not be estimable if there is excessive sparsity in the observed distribution of exposures [@Maldonado_2002].
 We investigated static and dynamic stochastic interventions on soluble MWF exposure that intervened only when average annual exposure exceeded the hypothetical limit under consideration.
-Hence, our parameters of interest achieve positivity more easily than those for deterministic interventions e.g.
+Hence, our parameters of interest achieve positivity more easily than those for static deterministic interventions e.g.
 setting all to a single level of exposure.
@@
 In practice, causal inference using observational data must always balance positivity, covariate adjustment, and model specification [@Petersen_2012].
-When estimating causal effects using estimators that do not require exposure modeling, as is the case with ICE g-formula methods, concerns over potential bias due to practical violations in positivity may be relaxed if correct model specification, discussed below, is attained.
+<!-- When estimating causal effects using estimators that do not require exposure modeling, as is the case with ICE g-formula methods, concerns over potential bias due to practical violations in positivity may be relaxed if correct model specification, discussed below, is attained.
+-->
 
@@
 
-Correct model specification is a standard assumption in all parametric analyses.
+Correct model specification is a standard assumption in all parametric and semi-parametric analyses.
 The estimator we applied offers greater statistical efficiency than the classical ICE parametric g-formula estimator because it leverages greater parametric smoothing.
@@
 In 2014, the IARC classified trichloroethylene, tetrachloroethylene, and other chlorinated agents as Group 1 carcinogens [@IARC_2014].
-Chlorinated solvents are commonly used as degreasers in industrial settings, but their use in the plants under study here was uncommon and limited to particular operations [@Shrestha_2016].
+Chlorinated solvents are commonly used as degreasers in industrial settings, but their use in the plants under study here was rare [@Shrestha_2016].
 The structural characteristics shared by MWF additives and known/suspected carcinogens suggest potential similarities in their behavior in biological systems.
@@
 This study investigated the effect of hypothetical limits on MWF exposure by comparing the standardized distributions of NHL under various distributions of cumulative exposure induced by applying upper bounds to average annual exposure to soluble MWF.
-When average annual exposure did not exceed the hypothetical limit, it was left at the observed level of exposure.
 We selected these hypothetical limits based on the NIOSH REL of 0.5 mg/m^3^ [@niosh_1998].
@@
 Hence, contrasting the counterfactual scenario where all workers experienced average annual exposure at the REL to one where all workers experienced average annual exposure at some higher level would result in an overestimate of the expected real-world benefit of REL enforcement.
-Furthermore, since the REL is for MWF exposure of all types, we evaluated dynamic stochastic interventions that better reflect this target policy because they reduce exposure to soluble MWF with the goal of reducing MWF exposure of all types to a certain limit.
-The interventions we considered result in exposure distributions more similar to what we would expect in the real world; our analysis yielded results that more realistically quantify the effects of policy than those investigating deterministic interventions [@Bembom_2007;@Munoz_2012].
 

### 2023-03-02 reports/paper/paper.Rmd
manuscript prepared

@@
 
-**Manuscript title:** Evaluating hypothetical limits on metalworking fluid exposure for reducing non-Hodgkin lymphoma incidence: An application of the hazard-extended parametric g-formula
+**Manuscript title:** Hypothetical limits on workplace exposure for reducing non-Hodgkin lymphoma: An application of the hazard-extended iterative conditional expectation parametric g-formula
 
-**Authors:** Kevin T. Chen^a,b^, Ellen A. Eisen^b^, Sally Picciotto^b^
+**Authors:** Kevin T. Chen^a,b,c^, Ellen A. Eisen^b^, Sally Picciotto^b^
 
@@
 ^b^ University of California, Berkeley School of Public Health, Division of Environmental Health Sciences
+
+^c^ University of California, Berkeley Department of Statistics
 
@@
 
-**Acknowledgements:**
+**Keywords:** Metalworking fluid, occupational exposure, non-Hodgkin lymphoma, cancer, causal inference, g-formula, healthy-worker effect, United States
 
@@
 
-**Background:** Non-Hodgkin lymphoma (NHL) incidence has increased significantly since 1960 and was recently linked with workplace exposure in the United Auto Workers-General Motors (UAW-GM) Cohort Study.
-Here, we investigate hypothetical interventions on workplace exposure to oil- and water-based soluble metalworking fluids (MWF) in relation to NHL risk.
-Interventions on entire classes of occupational exposures rather than particular agents may result in stronger lasting protections for worker health.
+**Background:** Non-Hodgkin lymphoma (NHL) incidence has increased significantly since 1960 and was recently linked to workplace exposure to soluble metalworking fluids (MWF) in a standard survival analysis of the United Auto Workers-General Motors (UAW-GM) cohort.
+Here, we investigate the causal effects of hypothetical limits on soluble MWF exposure in relation to NHL risk using an iterative conditional expectation (ICE) parametric g-formula estimator.
 
-**Methods:** We estimated counterfactual risk of NHL between 1985 and 2004 in the UAW-GM cohort of autoworkers exposed to straight, soluble, and synthetic MWF at three Michigan plants under hypothetical interventions.
-We estimated the effect of static and dynamic stochastic interventions on average annual exposure to soluble MWF.
-Unlike the static interventions, dynamic interventions take into account exposures to the other two classes of metalworking fluids, reflecting the fact that currently recommended limits apply to the total of all three exposures.
+**Methods:** We estimated counterfactual risk of NHL between 1985 and 2005 in the UAW-GM cohort of autoworkers at three Michigan plants (n = 34,734) under hypothetical limits on average annual exposure to soluble MWF.
+We applied the hazard-extended ICE parametric g-formula, an estimator capable of adjusting for time-varying confounding affected by past exposure.
 
 **Results:** During follow-up, 231 NHL cases occurred.
-Stronger hypothetical limits on average annual exposure to soluble MWF resulted in monotonically stronger reductions in NHL risk.
-Capping exposure to soluble MWF at 0.05 mg/m^3^ resulted in a risk ratio of 0.79 (95% CI: 0.61, 0.96).
-Capping total MWF exposure at 0.05 mg/m^3^ by intervening only on exposure to soluble MWF resulted in a risk ratio of 0.72 (95% CI: 0.44, 0.97).
+Stronger hypothetical limits on soluble MWF exposure resulted in monotonic reductions in NHL risk estimates.
+Capping average annual exposure at 0.5 mg/m^3^, the NIOSH recommended exposure limit, would have prevented 44 (95% CI: -6, 91) cases.
+Capping at 0.25 mg/m^3^ would have prevented 52 (95% CI: -5, 106) cases.
+Finally, capping at 0.05 mg/m^3^ would have prevented 71 (95% CI: 12, 129) cases.
 
-**Conclusion:** We considered interventions on soluble MWF that address total MWF exposure levels and showed that stronger limits on average annual exposure to soluble MWF may confer stronger protection against NHL risk.
-
-# What this study adds
-
-(Limit: 100 words)
-
-Little is known about possible links between occupational exposures and non-Hodgkin lymphoma.
-Existing studies are generally single time-point case-control studies with limited exposure assessment.
-We leveraged the large study population size and quantitative exposure assessment of the United Auto Workers-General Motors Cohort Study to estimate counterfactual risk of non-Hodgkin lymphoma under realistic interventions using a novel causal estimator capable of adjusting for time-varying confounding affected by past exposure.
+**Conclusion:** Stronger limits on soluble MWF exposure would have prevented more cases of NHL in the UAW-GM cohort.
+Our application demonstrates the utility of an ICE g-formula estimator for estimating the effect of realistic exposure interventions on a survival outcome.
+Greater availability of worked examples and software would facilitate wider application of ICE g-formula estimators.
 

### 2023-03-02 resources/interventions.tex
manuscript prepared

@@
-% Created by tikzDevice version 0.12.3.1 on 2022-06-28 15:57:56
+% Created by tikzDevice version 0.12.3.1 on 2023-02-02 14:54:25
 % !TEX encoding = UTF-8 Unicode
@@
 \usepackage{amssymb}
+\usepackage{upgreek}
 \usepackage[no-math]{fontspec}
 
-\setmainfont{Arial}
+\setmainfont{Arial}[Extension = .ttf,
+			UprightFont = *,
+			BoldFont = *bd,
+			talicFont = *i,
+			BoldItalicFont = *bi]
 
@@
 \end{document}
-re}[x=1pt,y=1pt]
-\definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (469.75,216.81);
+ill opacity=0.00] (0,0) rectangle (361.35,216.81);
 \begin{scope}
-\path[clip] ( 25.15, 47.51) rectangle (167.85,198.36);
+\path[clip] ( 25.15, 45.51) rectangle (187.75,198.36);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 25.15, 47.51) rectangle (167.85,198.36);
+\path[fill=fillColor] ( 25.15, 45.51) rectangle (187.75,198.36);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 31.63, 54.37) rectangle ( 68.70,164.08);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 32.54, 52.46) rectangle ( 74.77,163.62);
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 77.97, 54.37) rectangle (115.03,122.94);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 85.33, 52.46) rectangle (127.56,121.94);
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (124.30, 54.37) rectangle (161.36, 68.09);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (138.12, 52.46) rectangle (180.36, 66.36);
 \definecolor{fillColor}{RGB}{211,211,211}
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 31.63,164.08) rectangle ( 68.70,191.51);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 32.54,163.62) rectangle ( 74.77,191.41);
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 77.97,122.94) rectangle (115.03,191.51);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 85.33,121.94) rectangle (127.56,191.41);
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (124.30, 68.09) rectangle (161.36, 81.80);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (138.12, 66.36) rectangle (180.36, 80.25);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (  0.86, 52.46) rectangle (  0.86, 52.46);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (  0.86, 52.46) rectangle (  0.86, 52.46);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (  0.86, 52.46) rectangle (  0.86, 52.46);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 25.15, 88.66) -- (167.85, 88.66);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 25.15, 87.20) -- (187.75, 87.20);
 \end{scope}
 \begin{scope}
-\path[clip] (173.35, 47.51) rectangle (316.05,198.36);
+\path[clip] (193.25, 45.51) rectangle (355.85,198.36);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (173.35, 47.51) rectangle (316.05,198.36);
+\path[fill=fillColor] (193.25, 45.51) rectangle (355.85,198.36);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (179.84, 54.37) rectangle (216.90, 88.66);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (200.64, 52.46) rectangle (242.87, 87.20);
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (226.17, 54.37) rectangle (263.23, 88.66);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (253.43, 52.46) rectangle (295.67, 87.20);
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (272.50, 54.37) rectangle (309.57, 68.09);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (306.22, 52.46) rectangle (348.46, 66.36);
 \definecolor{fillColor}{RGB}{211,211,211}
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (179.84, 88.66) rectangle (216.90,116.08);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (200.64, 87.20) rectangle (242.87,114.99);
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (226.17, 88.66) rectangle (263.23,157.22);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (253.43, 87.20) rectangle (295.67,156.68);
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (272.50, 68.09) rectangle (309.57, 81.80);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (306.22, 66.36) rectangle (348.46, 80.25);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (168.96, 52.46) rectangle (168.96, 52.46);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (168.96, 52.46) rectangle (168.96, 52.46);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (168.96, 52.46) rectangle (168.96, 52.46);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (173.35, 88.66) -- (316.05, 88.66);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (193.25, 87.20) -- (355.85, 87.20);
 \end{scope}
 \begin{scope}
-\path[clip] (321.55, 47.51) rectangle (464.26,198.36);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (321.55, 47.51) rectangle (464.25,198.36);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (328.04, 54.37) rectangle (365.10, 61.23);
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (374.37, 54.37) rectangle (411.44, 54.37);
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (420.70, 54.37) rectangle (457.77, 68.09);
-\definecolor{fillColor}{RGB}{211,211,211}
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (328.04, 61.23) rectangle (365.10, 88.66);
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (374.37, 54.37) rectangle (411.44,122.94);
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (420.70, 68.09) rectangle (457.77, 81.80);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (321.55, 88.66) -- (464.26, 88.66);
-\end{scope}
-\begin{scope}
-\path[clip] ( 25.15,198.36) rectangle (167.85,211.31);
+\path[clip] ( 25.15,198.36) rectangle (187.75,211.31);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] ( 25.15,198.36) rectangle (167.85,211.31);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] ( 25.15,198.36) rectangle (187.75,211.31);
 \definecolor{drawColor}{gray}{0.10}
@@
 \begin{scope}
-\path[clip] (173.35,198.36) rectangle (316.05,211.31);
+\path[clip] (193.25,198.36) rectangle (355.85,211.31);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] (173.35,198.36) rectangle (316.05,211.31);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] (193.25,198.36) rectangle (355.85,211.31);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (175.85,201.74) {B) Static intervention};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (195.75,201.74) {B) Intervention};
 \end{scope}
 \begin{scope}
-\path[clip] (321.55,198.36) rectangle (464.26,211.31);
-\definecolor{drawColor}{RGB}{255,255,255}
-\definecolor{fillColor}{gray}{0.85}
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
+\definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] (321.55,198.36) rectangle (464.25,211.31);
-\definecolor{drawColor}{gray}{0.10}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 53.66, 35.06) {p-yr 1};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (324.05,201.74) {C) Dynamic intervention};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.45, 35.06) {p-yr 2};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (159.24, 35.06) {p-yr 3};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 50.17, 37.06) {p-yr 1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (221.76, 35.06) {p-yr 1};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.50, 37.06) {p-yr 2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (274.55, 35.06) {p-yr 2};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.83, 37.06) {p-yr 3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (327.34, 35.06) {p-yr 3};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (198.37, 37.06) {p-yr 1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (244.70, 37.06) {p-yr 2};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (291.03, 37.06) {p-yr 3};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (346.57, 37.06) {p-yr 1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (392.90, 37.06) {p-yr 2};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (439.24, 37.06) {p-yr 3};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 47.51) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 45.51) --
 	( 25.15,198.36);
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 51.62) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 49.71) {0};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 54.37) --
-	( 25.15, 54.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 52.46) --
+	( 25.15, 52.46);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 88.66) --
-	( 25.15, 88.66);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 87.20) --
+	( 25.15, 87.20);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,122.94) --
-	( 25.15,122.94);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,121.94) --
+	( 25.15,121.94);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,157.22) --
-	( 25.15,157.22);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,156.68) --
+	( 25.15,156.68);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,191.51) --
-	( 25.15,191.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,191.41) --
+	( 25.15,191.41);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,122.94) {Average annual exposure (mg/m$^3$)};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,121.94) {Average annual exposure (mg/m$^3$)};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 49.28,  5.50) rectangle (189.07, 24.50);
+\path[fill=fillColor] ( 75.97, 19.50) rectangle (305.02, 22.50);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 60.28, 11.00) rectangle ( 68.28, 19.00);
+\path[fill=fillColor] ( 81.47, 19.50) rectangle ( 89.47, 27.50);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] ( 60.99, 11.71) rectangle ( 67.56, 18.29);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 82.18, 20.21) rectangle ( 88.76, 26.79);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 73.78, 11.90) {Hypothetical exposure limit};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (200.07,  5.50) rectangle (440.13, 24.50);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (211.07, 11.00) rectangle (219.07, 19.00);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (211.79, 11.71) rectangle (218.36, 18.29);
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 82.18, 20.21) rectangle ( 88.76, 26.79);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (204.57, 19.50) rectangle (212.57, 27.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
+\definecolor{drawColor}{RGB}{0,0,0}
+\definecolor{fillColor}{RGB}{211,211,211}
+
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (205.28, 20.21) rectangle (211.86, 26.79);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
+\definecolor{drawColor}{RGB}{0,0,0}
+\definecolor{fillColor}{RGB}{211,211,211}
+
+\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (205.28, 20.21) rectangle (211.86, 26.79);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 94.97, 20.40) {Exposure to soluble MWF};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (218.07, 20.40) {Other MWF  exposure};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (126.10,  5.50) rectangle (254.90,  8.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (131.60,  5.50) rectangle (139.60, 13.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (211.79, 11.71) rectangle (218.36, 18.29);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (132.31,  6.21) rectangle (138.89, 12.79);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (334.17, 11.00) rectangle (342.17, 19.00);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{RGB}{211,211,211}
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (334.88, 11.71) rectangle (341.46, 18.29);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{RGB}{211,211,211}
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (334.88, 11.71) rectangle (341.46, 18.29);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
+\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (224.57, 11.90) {Exposure to soluble MWF};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (347.67, 11.90) {Other MWF  exposure};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (145.10,  6.40) {Hypothetical exposure limit};
 \end{scope}

### 2023-03-02 g-formula.R

@@ -50,7 +50,7 @@ ice_gcomp <- function(
 		dta[,`Other event` := max(`Other event`), studyno]
 	}
 
-	if ("immortal" %in% names(dta.a1)){
+	if ("immortal" %in% names(dta.a1)) {
 		dta.a1 <- dta.a1[,-c("immortal", "I", "I.which"), with = F]
 	}
 
@@ -109,40 +109,21 @@ ice_gcomp <- function(
 	discrete.formula <- as.formula(paste(
 		"status",
 		"~",
-		# "pspline(age.year2, df = 3) +",
-		# "pspline(year2, df = 2) +",
 		"Age +",
-		# "age.year2 +",
-		# "year +",
 		"`Cumulative straight` +",
-		# "cum_straight + ",
 		"`Cumulative soluble` +",
-		# "cum_soluble + ",
 		"`Cumulative synthetic` +",
-		# "cum_synthetic + ",
-		# "`Duration of employment` +",
-		# "employment.years +",
 		"`Employment status` +",
 		"`Year of hire` +",
-		# "yin.gm +",
 		"`Cumulative time off` +",
-		# "cum_off +",
 		"Sex +",
 		"Race + Plant",
-		# "+",
-		# paste(sapply(
-		# 	c(#timevar_covariates.which, baseline_covariates.which
-		# 		"Sex", "Race"), function(x) {
-		# 		if (!grepl(mwf.name, x)) {
-		# 			x <- paste0("`", x, "`")
-		# 			return(paste0("`Cumulative ", mwf.name, "` * ",
-		# 										x))
-		# 		} else {""}}), collapse = " + ")
 		NULL
 	))
-	h <- fastglm(model.matrix(discrete.formula, data = dta[immortal == 0 & Censored == 0]),
-							 dta[immortal == 0 & Censored == 0]$status,
-							 family = "binomial"
+	h <- fastglm(
+		model.matrix(discrete.formula, data = dta[immortal == 0 & Censored == 0]),
+		dta[immortal == 0 & Censored == 0]$status,
+		family = "binomial"
 	)
 	# summary(h)
 
@@ -197,48 +178,20 @@ ice_gcomp <- function(
 
 	dta[immortal == 0,`:=`(h.pred = shift(h.discrete, -1, NA)), by = .(studyno)]
 
-	# dta[studyno == 100001, .(
-	# 		studyno, I, year, h.pred, h.discrete, Censored
-	# 	)]
-
[…]

### 2023-03-02 intervention_figure.R

@@ -1,122 +1,0 @@
-# Making figure for explaining interventions ####
-# Kevin Chen
-# June 28, 2022
-
-library(here)
-source("~/headrs/00-my-theme.R")
-library(data.table)
-
-eg.dat <- data.table(
-	Exposure = c(0.16, 0.1, 0.02),
-	`Other exposure` = c(0.04, 0.1, 0.02)
-)
-
-eg.dat[, Static := {
-	x <- Exposure
-	x[x > 0.05] <- 0.05
-	x
-}]
-
-eg.dat[Exposure + `Other exposure` > 0.05, Dynamic := {
-	x <- Exposure
-	x <- 0.05 - `Other exposure`
-	x[x < 0] <- 0
-	x
-}]
-
-eg.dat[Exposure + `Other exposure` < 0.05, Dynamic := Exposure]
-
-eg.melt <- data.table(
-	mid = c(eg.dat$Exposure, eg.dat$Static,
-					eg.dat$Exposure, eg.dat$Dynamic),
-	upper = c(eg.dat$`Other exposure`,
-						eg.dat$`Other exposure`,
-						eg.dat$`Other exposure` + eg.dat$Exposure,
-						eg.dat$`Other exposure` + eg.dat$Dynamic),
-	exposure = c(rep("Observed exposure", 3), rep("Post-intervention exposure", 3),
-							 rep("Observed exposure", 3), rep("Post-intervention exposure", 3)),
-	intervention = c(rep("Static", 6), rep("Dynamic", 6))
-)
-
-eg.melt[,upper := mid + rep(eg.dat$`Other exposure`, 4)]
-
-eg.melt[,intervention := factor(
-	intervention,
-	c("Static", "Dynamic"),
-	c("Static intervention", "Dynamic intervention"))]
-
-eg.melt[,`:=`(
-	xmin = rep(1:3 - 0.4, 4),
-	xmax = rep(1:3 + 0.4, 4)
-)]
-
-# Simplified layout?
-eg.melt <- eg.melt[c(1:6, 10:12)]
-eg.melt$type <- rep(c(
-	"No intervention",
-	"Static intervention",
-	"Dynamic intervention"), each = 3)
-eg.melt[,type:= factor(type, c(
-	"No intervention",
-	"Static intervention",
-	"Dynamic intervention"),
-	c(
-	"A) No intervention",
-	"B) Static intervention",
[…]

### 2023-03-02 run_g-formula.R

@@ -10,52 +10,12 @@ source(here("g-formula.R"))
 
 dat.reduced <- box_read(928445783979)
 
-# name          : dat.str.reduced.rds
-dat.str.reduced <- box_read(928446426341)
-# name          : dat.str_total.reduced.rds
-dat.str_total.reduced <- box_read(928447106294)
-
 # name          : dat.sol.reduced.rds
 dat.sol.reduced <- box_read(928445303042)
-# name          : dat.sol_total.reduced.rds
-dat.sol_total.reduced <- box_read(928447942153)
-
-# name          : dat.syn.reduced.rds
-dat.syn.reduced <- box_read(928451552327)
-# name          : dat.syn_total.reduced.rds
-dat.syn_total.reduced <- box_read(928447597463)
-
-# name          : dat.total.reduced2.rds
-dat.total.reduced2 <- box_read(929952423129)
-
-# name          : dat.str.reduced2.rds
-dat.str.reduced2 <- box_read(929952765078)
 # name          : dat.sol.reduced2.rds
 dat.sol.reduced2 <- box_read(929953044799)
-# name          : dat.syn.reduced2.rds
-dat.syn.reduced2 <- box_read(929951401906)
-
-# name          : dat.str_total.reduced2.rds
-dat.str_total.reduced2 <- box_read(929957702377)
-# name          : dat.sol_total.reduced2.rds
-dat.sol_total.reduced2 <- box_read(929954713019)
-# name          : dat.syn_total.reduced2.rds
-dat.syn_total.reduced2 <- box_read(929954585841)
-
-# name          : dat.str.reduced10.rds
-dat.str.reduced10 <- box_read(942770799114)
 # name          : dat.sol.reduced10.rds
 dat.sol.reduced10 <- box_read(930687554963)
-# name          : dat.syn.reduced10.rds
-dat.syn.reduced10 <- box_read(942772072287)
-
-# name          : dat.str_total.reduced10.rds
-dat.str_total.reduced10 <- box_read(978943764524)
-# name          : dat.sol_total.reduced10.rds
-dat.sol_total.reduced10 <- box_read(978944866752)
-# name          : dat.syn_total.reduced10.rds
-dat.syn_total.reduced10 <- box_read(978947609426)
-
 
[…]

### 2023-03-02 shape-data.R

@@ -66,6 +66,23 @@ get.coxph(
 	employment_status.lag = exposure.lag)
 dat <- copy(nhl.dat)
 
+# Getting histology codes from cancer data
+cancer <- box_read('512727972584')
+setDT(cancer)
+
+nhl_morphology <- merge(dat[status == 1, .(studyno, yoi)],
+			unique(cancer[morph %in% c(
+				9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687:9691, 9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729, 9735, 9737:9738, 9811:9818, 9823, 9827, 9837,
+				9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687, 9688, 9689:9691, 9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729, 9735, 9737, 9738,
+				9811:9818, 9823, 9827, 9837
+			),.(studyno, yoi = ddiag, morph)]),
+			by = c("studyno", "yoi"))
+
+dat <- merge(
+	dat, nhl_morphology[,.(studyno, morph = as.integer(morph))],
+	by = "studyno",
+	all.x = T)
+
 # TV covariates: calendar year, duration of employment, time spent off, cumulative MWF exposure up to ___ year, employment status, censoring/death
 # Baseline covariates: year of hire, age at hire, sex, race, plant
 # Outcome: NHL
@@ -437,10 +454,10 @@ clipr::write_clip(
 		mutate(clean.tab1(nhl.tab1), spread = sanitize(spread))
 	)))
 )
+
 #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 # Unknown race as separate category              ####
 #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-
 dat[finrace == 9, Race := "Unknown"]
 
 setorder(dat, studyno, year)
@@ -459,7 +476,7 @@ mwf.breaks[,cum_soluble := cum_soluble5]
 # Scale down all three MWF so total under REL    ####
 #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
[…]

### 2023-03-23 reports/paper/paper.qmd
new direction for paper?

---
# fontsize: 11pt
# mainfont: arial
format:
 html: default
 docx:
    number-sections: false
    global-numbering: true
    reference-doc: "../../../../HeadRs/rmd_templates/style-guide-arial-11.docx"
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
notes-after-punctuation: true
execute:
  freeze: auto
editor_options: 
  chunk_output_type: inline
---

\fancyhead[R]{}
\fancyhead[L]{}
\renewcommand{\headrulewidth}{0pt}
\singlespacing

\thispagestyle{empty}

\setlength{\columnseprule}{0pt}

```{r, include=FALSE}
library(here)
knitr::opts_chunk$set(echo=F, results = 'asis')
library(bibtex)
biblio <- bibtex::read.bib('~/Box Sync/papers/EnvEpi.bib')
library(flextable)
library(data.table)
library(ggplot2); library(magrittr)
```

**Type of manuscript:** Original Research Article

**Manuscript title:** Hypothetical limits on workplace exposure for reducing non-Hodgkin lymphoma: An application of the hazard-extended iterative conditional expectation parametric g-formula

**Authors:** Kevin T. Chen^a,b,c^, Sally Picciotto^b^, Ellen A. Eisen^b^

^a^ University of California, Berkeley School of Public Health, Division of Epidemiology \& Biostatistics

^b^ University of California, Berkeley School of Public Health, Division of Environmental Health Sciences

^c^ University of California, Berkeley Department of Statistics

**Corresponding author:**\
Kevin T. Chen\
2121 Berkeley Way\
Room 5302, Desk 5305-1\
Berkeley, CA 94720-7360\
kevchen@berkeley.edu\
(510) 387-3327

**Running head suggestion:** Limits on metalworking fluid exposure to prevent NHL.

**Conflicts of interests:** Authors declare no conflicts of interest.

**Sources of financial support:** This work was supported by Training Grant T42OH008429 and Research Project Grant R01OH011092, both funded by the National Institute for Occupational Safety and Health (NIOSH) / Centers for Disease Control and Prevention (CDC).

**Data and computing code:** Code for reproducing analyses and reports are available on [Github](https://github.com/kvntchn/gm-nhl-ice). Data are available upon reasonable request.

**Keywords:** Metalworking fluid, occupational exposure, non-Hodgkin lymphoma, cancer, causal inference, g-formula, healthy-worker effect, United States

\newpage

# Abstract

(Limit: 250 words)

**Background:** Non-Hodgkin lymphoma (NHL) incidence has increased substantially in the US since 1960 and was recently linked to workplace exposure to soluble metalworking fluids (MWF) in a standard survival analysis of the United Auto Workers-General Motors (UAW-GM) cohort. To further explore this association, we investigate the causal effects of hypothetical limits on soluble MWF exposure in relation to NHL risk in the same cohort of autoworkers.

**Methods:** We estimated counterfactual risk of NHL between 1985 and 2005 in the UAW-GM cohort of autoworkers at three Michigan plants (n = 34,734) under hypothetical limits on annual average daily exposure to soluble MWF. We applied the hazard-extended ICE parametric g-formula, an estimator capable of adjusting for time-varying confounding affected by past exposure.

**Results:** During follow-up, 231 NHL cases occurred. Stronger hypothetical limits on soluble MWF exposure resulted in monotonic reductions in NHL risk estimates. Capping annual average daily exposure at 0.5 mg/m^3^, the NIOSH recommended exposure limit, would have prevented 44 (95% CI: -6, 91) cases. Capping at 0.25 mg/m^3^ would have prevented 52 (95% CI: -5, 106) cases. Finally, capping at 0.05 mg/m^3^ would have prevented 71 (95% CI: 12, 129) cases.

**Conclusion:** Stronger limits on soluble MWF exposure would have prevented cases of NHL in the UAW-GM cohort. Our application demonstrates the utility of an ICE g-formula estimator for estimating the effect of realistic exposure interventions on a survival outcome. Greater availability of worked examples and software would facilitate wider application of ICE g-formula estimators.

\newpage

# Introduction

The parametric g-formula has become increasingly popular among epidemiologists in the last decade. This analytic approach is attractive in part because it allows investigators to estimate the population-level effect of realistic interventions on exposures that may depend on individuals' covariate history as well as their natural value of exposure. In addition to yielding estimates with a population-level interpretation, the parametric g-formula is also capable of adjusting for time-varying confounding possibly affected by past exposure in longitudinal settings, which is not possible with standard regression methods. In their seminal 2009 paper, Taubman et alia describe the parametric g-formula and illustrate its application in the estimation of the counterfactual risks under several interventions in the Nurses' Health Study [@Taubman_2009]. They introduced a non-iterative conditional expectation parametric g-formula that requires parametric specification of the full joint distribution of confounders, exposures, and outcomes over time.

Full parameterization is an attractive choice for investigators seeking to embed real causal knowledge into the estimation problem. For those who are not completely comfortable with the full set of parametric assumptions, the iterative conditional expectation (ICE) parametric g-formula may be a good alternative. The ICE g-formula was introduced as early as 2004 [@Robins_2004], but its parametric implementations remain far less common in practice than its non-ICE counterpart. Like the non-ICE parametric g-formula, the ICE expression enables adjustment for time-varying confounding possibly affected by past exposure. However, the ICE parametric g-formula requires the parametric specification of models for the outcome only, and not the confounders or exposure. Hence, it requires fewer parametric assumptions than the non-ICE parametric g-formula. Furthermore, the elegance of the ICE parametric g-formula allows analysts to implement the method using standard statistical software, which offers the prospect of greater interpretability and transparency than using "black box" implementations.

Here, we describe the hazard-extended ICE parametric g-formula, an extension of the ICE parametric g-formula for causal survival analyses, and apply it to estimate counterfactual cumulative incidences of non-Hodgkin lymphoma under hypothetical interventions on annual average daily exposure to soluble metalworking fluids (MWF) in the UAW-GM autoworkers cohort between 1984 and 2005. The interventions we evaluate are modified longitudinal treatment policies which depend on the natural value of exposure [@Taubman_2009;@Richardson_2013;@Haneuse_2013;@Young_2014;@Diaz_2021].

<!-- Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered substantial research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons per year [@seer_1994;@Ekstrom-Smedby_2006]. The strongest known risk factor of NHL is immunosuppression, both congenital and acquired [@Filipovich_1992;@Chiu_2015]. Modulation of immune function contributes to the pathogenesis of NHL directly by perturbing lymphocyte function or indirectly by reducing immunosurveillance against neoplasms. Immunodeficiency may also interact with infection with Epstein-Barr Virus, resulting in uncontrolled B-cell proliferation [@Oertel_2002]. Acquired immunodeficiency through infection with human immunodeficiency virus (HIV) can lead to genetic lesions and dysregulation while increasing vulnerability to infection by other oncogenic agents [@Grulich_1999;@Alexander_2007]. However, since immunodeficiency and infection with HIV are rare, they cannot fully explain the historic rise or present burden of NHL [@Shiels_2013]. Since the rise in NHL incidence coincided with a period of rapid and extensive chemicalization in industry, agriculture and warfare, there has been stronger interest in the environmental and occupational epidemiology of NHL [@Nelson_2005;@Romero_2021]. -->

<!-- Pesticide exposure in agricultural occupational settings was a common target of NHL research in recent decades. A meta-analysis of 44 articles published between 1980 and 2014 found statistically significant associations between NHL and exposure to several classes of pesticides including carbamate, organophosporus, triazine, and organochlorine [@Schinasi_2014]. Occupations associated with NHL are not limited to the agricultural sector, however. Metal processors, health workers, salespeople, machinists, and electricians have all been identified as occupational groups with higher risk of NHL [@Fritschi_2005a; @Mester_2006; @Ekstrom-Smedby_2006]. -->

<!-- Metalworking fluids (MWF), an important class of occupational exposures, are complex mixtures of oils and chemicals used to lubricate and cool metal tools and parts during metal cutting and grinding operations in manufacturing processes. During use, MWFs aerosolize and present a potential health hazard to exposed workers. There are three general types of MWF: straight, soluble, and synthetic. The type of MWF applied has changed over the decades and depends in part on the particular metalworking operation. Straight MWF, the oldest class of MWF, is comprised mostly of mineral oils, which were classified as carcinogenic by the International Agency for Research on Cancer (IARC) in 1973, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973]. The combination of health concerns, the high cost of oil in the 1970s, and the introduction of performance-enhancing water-soluble chemical additives led to the gradual replacement of straight MWF with water-based soluble and synthetic MWFs for many, but not all operations [@Childers_2005]. Although water-based MWF contain little to no mineral oil, they contain a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987;@IARC_2014;@IARC_2017]. -->

<!-- In occupational studies, measures of time-varying exposure are essential to statistical adjustment for forms of time-varying confounding affected by past exposure such as the healthy worker survivor effect (HWSE). The HWSE is the dynamic selection process by which healthier individuals remain at work, where they accumulate more occupational exposure, and less healthy individuals leave work [@Arrighi_1994]. Standard analyses of occupational cohorts affected by the HWSE result in a downward bias on the exposure-outcome associations of interest, as less healthy workers typically accrue less exposure than healthier workers. -->

<!-- Here, we assess the effect of hypothetical MWF exposure limits on cumulative incidence of NHL from 1985 to 2005 in the United Auto Workers-General Motors (UAW-GM) occupational cohort study. -->
<!-- A recent study of cancer incidence in this cohort linked NHL with exposure to soluble MWF using a standard survival analysis using Cox proportional hazard regression [@Colbeth_2023]. Standard regression methods are vulnerable to bias due to the HWSE. We therefore further explore this association using an estimator capable of adjusting for time-varying confounding and censoring affected by past exposure: the hazard-extended iterative conditional expectation (ICE) parametric g-formula. Like other causal estimators in statistics, the hazard-extended ICE g-formula yields marginal effect estimates of hypothetical interventions, which may be more interpretable under a population health framework than conditional measures. -->

# Methods

We estimated NHL cumulative incidence from 1985 to 2005 under hypothetical limits on annual average daily exposure to soluble MWF by applying the hazard-extended iterative conditional expectation (ICE) parametric g-formula estimator [@Wen_2020]. We leveraged time-varying quantitative MWF exposure data in tandem with employment records to adjust for the HWSE. First, we estimated the expected number of NHL cases that we would observe if there were no censoring by competing risks. Then, we contrasted this counterfactual cumulative incidence to that under three the hypothetical exposure limits: (1) the National Institute for Occupational Safety and Health (NIOSH) Recommended Exposure Limit (REL) for total particulate mass (PM) composed of MWFs (0.5 mg/m^3^), (2) half the REL (0.25 mg/m^3^), and (3) a tenth of the REL (0.05 mg/m^3^) were enforced for soluble MWF over workers' entire working lifetimes [@niosh_1998]. Under these hypothetical interventions, exposure was set at the hypothetical limit if observed exposure was greater than that limit. Otherwise, exposure was not intervened upon.

## Study population

The UAW-GM cohort includes all hourly workers at three automobile manufacturing plants in Michigan who had worked at least three years by 1985. Past papers provide detailed descriptions of the cohort [@Eisen_1992;@Eisen_2001]. The large size of the study population and rich time-varying, quantitative MWF exposure data provide an opportunity to study a relatively rare cancer and evaluate realistic interventions on MWF exposure in a longitudinal cohort setting. The present study population (N = 34,738) was restricted to the autoworkers who were at work in 1941 or not yet hired, missing no more than half of their employment history, and still alive at the start of follow-up. Autoworkers in the study population were followed for NHL incidence from January 1, 1985 until NHL diagnosis, death, January 1, 2005 (10 years after the end of employment record availability), or age 108 years (the oldest observed age at death), whichever came earlier.

## Outcome and covariates

We identified incident cancers in the UAW-GM cohort that occurred between 1985 and 2005 by linkage to the Michigan Cancer Registry (MCR). Workers at Plants 1 and 2, located in the greater Detroit metropolitan area, were also linked to the Detroit Regional Registry of the Surveillance, Epidemiology, and End Results (SEER) Program. Cancer types were distinguished using site and histology codes conforming to the International classification of Diseases for Oncology, 3^rd^ edition (ICD-O-3). Non-Hodgkin lymphoma was defined by cancers with any of the following ICD-O-3 Histology codes: 9590-9597, 9670-9671, 9673, 9675, 9678-9680, 9684, 9687-9691, 9695, 9698-9702, 9705, 9708-9709, 9712, 9714-9719, 9724-9729, 9735, 9737-9738, 9811-9818, 9823, 9827, 9837. Details regarding cancer incidence follow-up are described elsewhere [@Colbeth_2023]. Vital status was ascertained from company records and by linkage to Social Security Administration, National Death Index, and state mortality files.

Covariates including year of hire, sex, race, and plant location were obtained from company records. Race was missing for about 16% of the cohort, most commonly among workers hired before 1960 in Plant 2. In analyses, missing race was considered a distinct category. All covariates were coded as categorical variables. Cut-points for categorizing continuous covariates were determined according to the quantiles among cases.

## Exposure

Quantitative measurement of time-varying MWF exposure is a distinguishing strength of the UAW-GM cohort study relative to other occupational cohort studies. Exposure assessment was based on direct air sampling as well as company records. Company industrial hygienists collected several hundred personal and area samples for total particulate matter (mg/m^3^) composed of MWF over many decades. Research industrial hygienists collected additional air sampling data when the cohort study was launched in the mid 1980s. These additional data were combined with the historical data and company records to construct a job-exposure matrix of quantitative 8-hour time-weighted average daily exposure estimates to soluble, straight, and synthetic MWFs for each combination of job, department, and plant over time. Workers' time-weighted annual average daily exposure to each MWF type was determined by combining this job-exposure matrix with employment records, which recorded time-varying job type, department, and plant for each employee from hire to termination or 1994, whichever came sooner. For employment records that were at least half complete, gaps in the record were interpolated by carrying forward the last known job type. The exposure assessment is described in detail elsewhere [@Hallock_1994;@Woskie_1994;@Woskie_2003]. Previous analyses of NHL applied exposure lags of 1 to 20 years to account for disease latency; we lagged cumulative MWF exposures by 10 years and therefore ended follow-up on January 1, 2005 [@Smith_2007;@Karipidis_2007;@Zhang_2019]. In analyses, MWF exposure history was summarized as the cumulative sum of annual exposure intensities and coded as categorical variables with cut-points determined according the quantiles of cumulative exposure among cases. In analyses, we estimated the effects of interventions on soluble MWF while treating exposure to straight and synthetic MWFs as potential confounders.

## Statistical methods

The hazard-extended ICE parametric g-formula may be thought of as a series of model-based standardization steps, which we implemented using logistic regression. We split the 20-year follow-up period into eight time periods; the first two periods spanned four years each, and the remaining six periods spanned two years each. The first two periods are longer in length to account for the smaller number of cases in those years. Post-intervention estimates of the discrete hazard of NHL given all exposures and covariates were combined iteratively from the end of follow-up to the start. In each iteration, predicted discrete hazards were standardized over post-intervention exposure and covariate histories before combining with discrete hazards from the previous iteration. This iterative process results in sequentially standardized estimates of NHL cumulative incidence over the entire follow-up period. Averaging over the baseline distribution of covariates yields the counterfactual cumulative incidence estimate of NHL if the intervention of interest were enforced for the entire study population.

Post-intervention exposure to soluble MWF and history of exposure to soluble MWF were summarized as cumulative exposure. We modeled discrete hazards by fitting a pooled logistic regression for NHL over at-risk person-periods given cumulative exposure to straight, soluble, and synthetic MWFs, employment status, cumulative time off, year of hire, sex (male/female), race (Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3). Cumulative exposure to MWFs, employment status, and cumulative time off were lagged 10 years. All continuous variables were represented as categorical variables with cut points determined by the tertiles of nonzero values among NHL cases. An overview of the general steps of the estimation procedure are presented below.

0.  For the hypothetical exposure limit of interest, compute the cumulative exposure
		to soluble MWF that each worker would have accrued by the end of each follow-up
		period since hire.
1.  Fit a pooled logistic regression to the observed data for NHL on covariates and
    cumulative exposure to soluble MWF over all at-risk person-periods, excluding 
    those ending with a .
2.  Replace the cumulative exposure vector in the observed data with the vector
		of post-intervention cumulative exposure to soluble MWF. Using the model fitted
		in the  previous step, compute estimates of the post-intervention discrete hazard
		for each at-risk person-period including those that end with a censoring event.
3.  Set $k = K - 1$ where $K = 8$ is the number of follow-up periods:

	a) Among those who were event-free and uncensored through the $k$^th^ period,
		 fit a logistic regression on the predicted post-intervention discrete hazard
		 for the period spanning the $(k + 1)$ through $K$^th^ periods given observed
		 covariate and exposure history up through (and including) the $k$^th^ period.
	b) Replace the vector of cumulative exposure to soluble MWF in the observed data
		 with the post-intervention vector of cumulative exposure to soluble MWF. Using
		 the model fitted in the previous step, obtain predicted values for all those
		 who were at-risk in the $k$^th^ period.
	c) Compute the predicted post-intervention discrete hazard for the period spanning
		 the $k$ through $K$^th^ periods by multiplying the predicted values from the
		 previous step by 1 minus the discrete hazard estimate used to fit the model
		 in step 3.a and adding that same discrete hazard estimate to the product.
	d) If $k > 1$, set $k = k - 1$ and return to step 3.a.

4.  Compute the counterfactual risk by averaging the predicted post-intervention
		discrete hazards for the entire follow-up period for all units.

We estimated cumulative incidence under the observed distribution of soluble MWF exposure (natural course) and under the six interventions. We contrasted the cumulative incidence under intervention to that under the natural course by computing relative cumulative incidences. Confidence intervals were computed using the nonparametric bootstrap with 1000 Monte Carlo samples from the population at cumulative incidence at start of follow-up and centering on the estimate computed from observed data. All the necessary script used to reproduce the analyses are available on [GitHub](https://github.com/kvntchn/gm-nhl-ice).

# Results

```{r}
source(here::here("../gm-wrangling/wrangling/table1.R"))
clean.tab1 <- function(tab1) {
	# hspace.which <- grepl("\\\\hspace\\{.*\\}", rownames(tab1))
	rownames(tab1) <- gsub("\\\\hspace\\{.*\\}|\\\\hline |\\$.*\\$| among deceased", "", rownames(tab1))

	tab1[!grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2]  <-  paste0(
		"(",
		tab1[!grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2],
		")"
	)

	tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2] <- paste0(
		"(", tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2], ", ",
		tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 3],
		")"
	)

	return(tab1[,1:2])
}
full.tab1 <- readRDS(here::here("resources", "tab1.rds"))
nhl.tab1 <- readRDS(here::here("resources", "nhl.tab1.rds"))

tab1.clean <- clean.tab1(full.tab1)
nhl.tab1.clean <- clean.tab1(nhl.tab1)

tab1 <- cbind(hspace.logical = grepl("\\\\hspace\\{.*\\}", rownames(full.tab1)),
							variable = rownames(tab1.clean), tab1.clean, NA, nhl.tab1.clean)

tab1 <- tab1[!grepl("Years of follow-up", rownames(tab1)),]
tab1$variable[1] <- "N (person-years)"
```

Table 1 presents summary statistics of exposure and covariates for the full study population and for those diagnosed with NHL between 1985 and 2005. The cohort is predominantly white (66%) and male (87%). The median year of hire among those diagnosed with NHL was 1959 whereas the median year of hire in the full study population was almost a decade later. Age at hire was approximately the same among those with NHL and the full study population. Median lagged cumulative exposure to all three MWF types was higher among NHL cases. Soluble MWFs were the most widely used MWF type, with approximately 90% of workers ever exposed. Median cumulative exposure among the exposed was 6.5 times higher for soluble than for straight MWFs. Figure 1 shows median annual average daily exposure to the three MWF types among exposed workers over calendar time. Exposure to MWF generally followed a downward trend over time.

```{r}
# tab1 <- tab1[tab1.which,]
tab1[c(1:13, 15, 14, 16:27, 29, 28, 30),-grep("hspace.logical", colnames(tab1))] |> 
	data.frame() |> flextable() |>
	delete_part(part = "header") |>
	add_header_row(values = c("", "Study population", "", "NHL cases"),
								 colwidths = c(1, 2, 1, 2)) |>
	hline_top(part = "header") |>
	hline_top() |> hline_bottom() |>
	hline(which((grepl("[0-9]\\)", tab1$spread))[-1])[1]) |> width(4, 0.1) |>
	width(1, 2.2) |> width(c(3, 6), 1.1) |> width(c(2, 5), 0.65) |>
	flextable::compose(
		i = grep("Cumulative exposure", rownames(tab1)), j = 1,
		value = as_paragraph("Cumulative exposure to MWFs (mg/m",
												 as_sup("3"), "-years)")) |>
	flextable::align(j = 2:6, align = "center", part = "all") |>
	footnote(i = grep("Plant$", rownames(tab1)), j = 1, value = as_paragraph(
		" Plant of longest employment duration among those who worked at multiple plants"),
		ref_symbols = "a", inline = T) |>
	footnote(i = grep("Ever exposed|time off", rownames(tab1)), j = 1, value = as_paragraph(
		" Lagged 10 years"),
		ref_symbols = "b", inline = T) |>
	footnote(i = grep("work", rownames(tab1)), j = 1, value = as_paragraph(
		" Among those who left work by December 31, 1994"),
		ref_symbols = "c", inline = T) |>
	# footnote(i = grep("death", rownames(tab1)), j = 1, value = as_paragraph(
	# 	" Among deceased"),
	# 	ref_symbols = "d", inline = T) |>
	footnote(i = grep("Cumulative exposure", rownames(tab1)), j = 1, value = as_paragraph(
		" Among ever-exposed individuals, lagged 10 years."),
		ref_symbols = "d", inline = T) |>
	add_footer_row(values = "NHL: non-Hodgkin lymphoma.", colwidths = 6) |>
	padding(padding = 1.5, part = "all") |>
	padding(
		i = which(tab1$hspace.logical),
		j = 1,
		padding.left = 20
	) |>
	merge_at(i = grep("Cumulative exposure", rownames(tab1))) |>
	hline_bottom(part = "footer") |> font(fontname = 'arial') |>
	set_caption(caption = "Summary of population characteristics. Statistics shown above the horizontal line are count (%). Those shown below are median (quartile 1, quartile 3).")
```
\

![Figure 1. Median annual average daily exposure to soluble, straight, and synthetic metalworking fluids among exposed workers over time.](../../resources/images/exposure.png){width=6.5in}

```{r}
intervened_py <- readRDS(here::here("resources", "percent-py-intervened.rds"))
# paste(paste0("\"", intervened_py$dt.name, "\""), collapse = ",\n") |> clipr::write_clip()
dat.names <- data.table(
	dt.name = c(
		"dat.sol.reduced", "dat.sol.reduced2", "dat.sol.reduced10"),
	variable.dat = c(
		"soluble", "soluble2", "soluble10")
)
intervened_py <- as.data.table(merge(
	intervened_py, dat.names,
	by = "dt.name"))
intervened_py <- rbindlist(list(
	data.table(dt.name = NA,
						 mwf = NA, percent_py_intervened = 0,
						 variable.dat = "natural"),
	intervened_py
))
```

```{r}
load(here::here("resources", paste0("h.estimates.rdata")))
estimates.bs <- readRDS(here::here("resources", paste0("estimates.bs.rds")))
```

```{r}
# Risk ratios
do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
	x/estimates.bs[,2]
})) %>% melt(measure.vars = names(.)) -> rr.bs

# Risk differences
do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
	x - estimates.bs[,2]
})) %>% melt(measure.vars = names(.)) -> rd.bs

estimates.bs[,-1] %>% melt(measure.vars = names(.)) -> risk.bs

# Collect point estimates
point_estimates <- data.table(
	variable = c(
		"soluble", "soluble2", "soluble10", "natural"),
	estimate = c(
		h.reduction.sol, h.reduction.sol2, h.reduction.sol10,
		h.baseline)
)
```
```{r}
# Calculate risk ratios for each bootstrap sample
rr <- merge(
	rr.bs,
	point_estimates[,.(
		variable = paste0(variable, ".natural"),
		estimate = estimate/estimate[variable == "natural"]
	)],
	all.x = F,
	by = "variable")

# Get lower and upper 2.5th %tiles
rr <- rr[,.(
	rr = estimate[1],
	rr_lower = {
		x <- value
		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
	rr_upper = {
		x <- value
		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
	# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
	# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
),
variable]
```
```{r}
# Calculate risk differences for each bootstrap sample
rd <- merge(
	rd.bs,
	point_estimates[,.(
		variable = paste0(variable, ".natural"),
		estimate = estimate - estimate[variable == "natural"]
	)],
	all.x = F,
	by = "variable")

# Get lower and upper 2.5th %tiles
rd <- rd[,.(
	rd = estimate[1],
	rd_lower = {
		x <- value
		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
	rd_upper = {
		x <- value
		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
	# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
	# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
),
variable]

rd[,(c('rd', 'rd_lower', 'rd_upper')) := list(
	- rd * 34734,
	- rd_upper * 34734,
	- rd_lower * 34734
	)]

```

```{r}
# Combine differences and ratios
contrasts.tab <- merge(rr, rd, by = 'variable')
```

```{r}
# Collect risks
risks <- merge(
	risk.bs,
	point_estimates,
	all.x = F,
	by = "variable")

# Get lower and upper 2.5th %tiles
risks <- risks[,.(estimate = estimate[1],
			lower = {
				x <- value
				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
			upper = {
				x <- value
				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
			# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
			),
	 .(variable.risks = variable)]
```

```{r}
intervention.labels <- data.table(
	variable = c(
		"natural", "soluble", "soluble2", "soluble10"
	),
	label = c(
		"None", "0.5", "0.25", "0.05"
	)
)

# Add intervention labels
contrasts.tab <- merge(
	contrasts.tab, intervention.labels[,.(variable = paste0(variable, ".natural"), label)],
	all = T,
	by = "variable"
)

```

```{r}
clean_percent_py <- function(variable, digits = 1, scale = 100) {
	sprintf(paste0("%.", digits, "f"), round(
		intervened_py[match(
	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
	 		variable.dat
	), percent_py_intervened] * scale,
	digits))
}

clean_risk <- function(variable, digits = 2, scale = 1000) {
	sprintf(paste0("%.", digits, "f"), round(risks[match(
	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
	 		variable.risks
	), estimate] * scale, digits))
}

clean_risk.ci <- function(variable, digits = 2, scale = 1000) {
	 		x <- risks[match(
	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
	 		variable.risks
	 		),.(lower, upper)]
	 		ifelse(!is.na(x$lower), paste0(
	 			"(",
	 			sprintf(paste0("%.", digits, "f"), round(x$lower * scale, digits)),
	 			", ", 
	 			sprintf(paste0("%.", digits, "f"), round(x$upper * scale, digits)),
	 			")"), NA)
}

clean_rr.ci <- function(estimate, lower, upper, digits = 2) {
	ifelse(!is.na(lower), paste0(
		"(",
		sprintf(paste0("%.", digits, "f"), round(lower, digits)),
		", ",
		sprintf(paste0("%.", digits, "f"), round(upper, digits)),
		")"), NA)
}

mwf.flextable <- function(x, n_col = 8) {
	flextable::compose(x, j = c(4, n_col), value = as_paragraph(rep("(95% CI)", 2)),
		part = "header"
	) |>
	border_remove() |>
	hline_top(part = "header") |>
	hline_top() |> hline_bottom() |>
	flextable::align(j = 2:n_col, align = "center", part = "all") |>
	width(width = c(1.7, 1.1, 0.7, 1, 0.5, 1, 0.5, 1)) |>
	padding(padding = 1.5, part = "all")
}
```

The observed number of NHL cases over the 20-year follow-up period was 231 (corresponding to a 20-year risk of 6.65 per 1000). Table 2 presents the hazard-extended ICE parametric g-formula estimates of the counterfactual number of cases, number of cases averted, and cumulative incidence ratios contrasting hypothetical limits on exposure to soluble MWF to no limit, after elimination of competing risks. Under an intervention eliminating competing risks, the estimated number of cases under no limit on MWF exposure was 332 (285, 380). Stronger limits on annual average daily exposure to soluble MWFs resulted in monotonically stronger reductions in the cumulative incidence of NHL. Capping annual average daily exposure to soluble MWFs at 0.5 mg/m^3^, 0.25 mg/m^3^, and 0.05 mg/m^3^ resulted in 44 (-6, 91), 52 (-5, 106), and 71 (12, 129) fewer NHL cases, respectively. These correspond to cumulative incidence ratios 0.87 (0.73, 1.02), 0.84 (0.68, 1.01), and 0.79 (0.61, 0.97).

```{r, eval=F}
tikzDevice::tikz(here::here("reports/ACIC (2022)/poster/resources/rr.tex"),
								 width = 4, height = 1.75,
								 standAlone = T)
contrasts.tab[grepl("sol|natural\\.natural", variable) & !grepl(
	"[a-z]", label),] |> ggplot(
		aes(x = factor(label, rev(c("0.5", "0.25", "0.05"))),
				y = rd, ymin = rd_lower, ymax = rd_upper)
	) +
	geom_errorbar(linewidth = 0.5, width = 0.15, color = '#102451') +
	geom_point(size = 0.9, color = '#102451') + 
	geom_hline(yintercept = 1, lty = 2, color = '#102451', alpha = 0.7) +
	labs(
		y = "Cases averted",
		x = "Hypothetical limit (mg/m$^3$)") +
	mytheme +
	coord_flip(ylim = c(-15, 130)) +
	theme(panel.grid = element_blank())
dev.off()

lualatex(directory = here::here("reports/ACIC (2022)/poster/resources"))
```

```{r}
contrasts.tab[grepl("sol|natural\\.natural", variable),.(
	 	label,
	 	`Person-years intervened (%)` = clean_percent_py(variable),
	 	`Cases`  = clean_risk(variable, 0, 34734),
	 	`(95% CI)`      = clean_risk.ci(variable, 0, 34734),
	 	`Cases averted`    = round(rd),
	 	`(95% CI1)`        = c(NA, paste0(
	 		"(",
	 		round(na.exclude(rd_lower)), ", ",
	 		round(na.exclude(rd_upper)), ")")),
	 	CIR              = sprintf("%.2f", round(rr, 2)),
	 	`(95% CI2)`   = clean_rr.ci(rr, rr_lower, rr_upper)
	 )][c(1, 2, 4, 3),] -> sol.tab

sol.tab[sol.tab == "NA"] <- NA
# saveRDS(sol.tab, here::here('resources', 'sol.tab.rds'))

sol.tab |> flextable() |>
	flextable::compose(
		j = 1,
		value = as_paragraph("Exposure limit for soluble MWF (mg/m", as_sup("3"), ")"),
		part = "header"
	) |>
	set_header_labels(
		`(95% CI1)` = "(95% CI)",
		`(95% CI2)` = "(95% CI)"
	) |> mwf.flextable() |>
	width(width = c(1.1, 1.1, 0.5, 0.9, 0.55, 0.9, 0.5, 0.9)) |>
	add_footer_row(values = paste(
		"CIR: cumulative incidence ratio. MWF: metalworking fluid",
		sep = "\n"), colwidths = 8) |>
	hline_bottom(part = "footer") |>
	set_caption(caption = "Counterfactual number of cases, number of cases averted, and cumulative incidence ratio estimates contrasting hypothetical limits on soluble MWF exposure to no intervention on exposure.")

```

# Discussion

Although NIOSH concluded that there exists substantial evidence linking MWF exposure to several different cancers, their REL of 0.5 mg/m^3^ for total particulate matter derived from any type of MWF targeted risk of acute respiratory disorders rather than on cancer [@niosh_1998;@Mirer_2003]. Hence, they may be inadequate for protecting against cancer risk. Using the hazard-extended ICE parametric g-formula, We estimated the counterfactual expected number of NHL cases from 1985 to 2005 in the UAW-GM cohort if annual average daily exposure to soluble MWF were limited to the NIOSH REL, half the REL, and a tenth of the REL and found a monotonic exposure-dependent relationship with lower cumulative incidence estimates arising from stronger limits.

The g-formula is a well-known approach in causal inference used for the identification of causal effects in the presence of time-varying confounding affected by past exposure [@Robins_1986]. Standard representations of the g-formula include (1) a non-iterated expectation over the joint density of covariates, (2) the ICE over time, and (3) an inverse probability weighted expectation. The parametric g-formula is a plug in estimator for the g-formula under its first, non-iterative, representation. It involves the parametric modeling of the full joint distribution of the outcome, exposure, and covariates under study for each time point [@Taubman_2009;@Young_2014]. Counterfactual quantities under hypothetical interventions of interest are computed from Monte Carlo samples from distributions implied by the fitted parametric models. In longitudinal settings, this approach often requires specifying and fitting large number of models in order to satisfy the exchangeability assumptions necessary for causal identification.
<!-- Since applications of the parametric g-formula are often context-laden, there are no unified guidelines for model specification. -->

Parametric estimators using the ICE representation of the g-formula require modeling only the conditional outcome distributions, so they require fewer parametric assumptions than non-iterative parametric g-formula estimators. Counterfactual outcome estimates over the follow-up period are computed from interval-specific conditional estimates by applying the tower rule of expectation. Under the assumptions of conditional exchangeability at all time points, positivity, counterfactual consistency, and correct model specification, the hazard-extended parametric g-formula yields unbiased estimates of counterfactual risk with greater statistical efficiency than both propensity score-based estimators and the classical ICE g-formula.

Under the assumptions of conditional exchangeability, positivity, consistency, and correct model specification, our estimates are unbiased for the true counterfactual risk under the hypothetical interventions. Conditional exchangeability means that for all time points, there is no confounding of the relationship between exposure/censoring and both future exposure/censoring and NHL status given the observed past, including past exposure and covariates [@Richardson_2013;@Diaz_2021]. A major threat to conditional exchangeability in longitudinal occupational studies is the HWSE. We limit potential bias due to the HWSE by conditioning on cumulative exposure, employment status, and cumulative time off history at each time point. Cumulative time off and employment status are reasonable mediators of the causal paths linking past health to future exposure and health, but adjustment for these variables may not be sufficient for eliminating bias due to the HWSE. Declines in a worker's health may lead to reductions in work-related exposure without affecting employment status or time off work [@Garcia_2017]. We expect the absence of time-varying measures of worker health over the life course to result in bias toward the null.

Positivity refers to the need for adequate variation in future exposure among strata formed by observed covariate and intervention-compliant exposure histories. Even under conditional exchangeability, where exposures within these strata may be considered the result of experimental assignment, expected counterfactual outcomes under different exposures may not be estimable if there is excessive sparsity in the observed distribution of exposures [@Maldonado_2002]. We investigated static and dynamic stochastic interventions on soluble MWF exposure that intervened only when annual average daily exposure exceeded the hypothetical limit under consideration. Hence, our parameters of interest achieve positivity more easily than those for static deterministic interventions e.g. setting all to a single level of exposure. Nonetheless, violations in positivity were still of concern due to the high dimensionality of covariates, as is common in longitudinal settings. We addressed sparsity by summarizing the 20 years of follow-up over a coarser timescale with only 8 follow-up periods and by representing covariates using fewer categories. Coarsening limits the comprehensiveness of confounding control, but improves positivity. In practice, causal inference using observational data must always balance positivity, covariate adjustment, and model specification [@Petersen_2012].
<!-- When estimating causal effects using estimators that do not require exposure modeling, as is the case with ICE g-formula methods, concerns over potential bias due to practical violations in positivity may be relaxed if correct model specification, discussed below, is attained. -->

The consistency assumption, also known as the no-multiple-versions-of-treatment or stable unit treatment value assumption, is that counterfactual outcomes under each possible exposure value take on a unique value [@Cole_2009;@VanderWeele_2013]. This assumption would be violated if there were multiple versions of treatment causally associated with different outcomes. This basic notion of consistency is violated in our analysis because our exposure of interest is a complex mixture of diverse components with substantial variation over time due to changes in formulation as well as the natural physical, chemical, and biological changes in the MWF over the course of its use and reuse [@Howell_2006]. However, causal effect estimates under violations in the consistency assumption are still valid and unbiased if there is adequate adjustment for confounders of the exposure-version relationship [@VanderWeele_2013]. This may be thought of as conditional consistency within strata, in which there is only one version of treatment. Our analysis indexed time periods over calendar time and adjusted for age, year of hire, and plant. In this way, we limited potential for bias due to variation in MWF composition.

Correct model specification is a standard assumption in all parametric and semi-parametric analyses. The estimator we applied offers greater statistical efficiency than the classical ICE parametric g-formula estimator because it leverages greater parametric smoothing. In causal analyses of longitudinal cohort studies, both the hazard-extended and classical ICE parametric g-formula estimators are less common than the NICE parametric g-formula [@Keil_2014]. However, a major limitation of the NICE g-formula is the g-null paradox: the guaranteed misspecification of parametric models resulting in the false rejection of the null hypothesis when the null is true and when there is time-varying confounding affected by past exposure [@Naimi_2015;@McGrath_2022]. As with all ICE g-formula estimators, the estimator we applied is not subject to the g-null paradox. Furthermore, simulation studies show that the variance of the hazard-extended ICE parametric g-formula is similar to that of the NICE parametric g-formula, so we expect the former to be no less conservative than the latter [@Wen_2020].

<!-- In the last several decades, there have been substantial changes in the formulation of MWF, including the exclusion of nitrogenous compounds and the use of highly-refined mineral oils. The recent establishment of the Ecolabel for lubricants in the European Union reflects the shift toward prioritizing sustainability and health in the design and production of MWF and other lubricants [@EU_2018;@Skerlos_2008]. However, water-based MWF that satisfy Ecolabel criteria are nonetheless susceptible to the accumulation of dirt, metals, microbes, products of microbial metabolism, and unemulsified oil. These contaminants and their control strategies may also induce risks to human health. Furthermore, adoption of this new class of MWF remains limited, as is evidence of their safety. Considering the evolving complexity in MWF composition, epidemiologic investigations remain an invaluable approach for developing evidence-based occupational health policy and estimating their causal effect. -->

Much of the existing epidemiologic literature linking occupational and environmental exposures to NHL report findings from case-control studies where exposures are measured crudely as binary indicators of exposure or membership in a particular occupational group [@Cano_2001;@Costantini_2001;@Karunanayake_2008;@t-Mannetje_2016]. Associations between occupations and NHL risk vary considerably, but one study of working men in Kansas and Nebraska found strong associations between NHL risk and occupations involving metalworking and motor vehicles [@Zheng_2002]. Both of these occupations may entail exposure to soluble MWFs, which contain a number of additives of concern for human health and for NHL risk in particular. Organic compounds containing phosphorous, chlorine, sulfur, nitrogen, and boron are commonly added to soluble MWF to control microbial growth, improve performance under high heat/pressure, and inhibit corrosion [@Evans_2020]. Organophosphorus compounds include organophosphate pesticides, which have been linked to cancer risk in epidemiologic and animal studies. Some were classified as possibly carcinogenic by the IARC [@IARC_2017]. Studies of occupational exposure to chlorinated solvents and pesticides have also been linked to NHL risk [@Cocco_2008;@Purdue_2011;@Cocco_2013;@Vlaanderen_2013;@Callahan_2018]. In 2014, the IARC classified trichloroethylene, tetrachloroethylene, and other chlorinated agents as Group 1 carcinogens [@IARC_2014]. Chlorinated solvents are commonly used as degreasers in industrial settings, but their use in the plants under study here was rare [@Shrestha_2016]. The structural characteristics shared by MWF additives and known/suspected carcinogens suggest potential similarities in their behavior in biological systems.

This study investigated the effect of hypothetical limits on MWF exposure by comparing the standardized distributions of NHL under various distributions of cumulative exposure induced by applying upper bounds to annual average daily exposure to soluble MWF. We selected these hypothetical limits based on the NIOSH REL of 0.5 mg/m^3^ [@niosh_1998]. In the real world, there is no enforcement of the REL, but we nonetheless observed annual average daily exposures below the REL in these GM plants for many years. If the REL were enforced in the real world, we would not expect reductions in exposure for these low-exposure person-years. Hence, contrasting the counterfactual scenario where all workers experienced annual average daily exposure at the REL to one where all workers experienced annual average daily exposure at some higher level would result in an overestimate of the expected real-world benefit of REL enforcement.

<!-- The interventions we considered are stochastic interventions resulting in post-intervention distributions of exposure that better reflect what we would expect if exposure limits were enforced in the real world. The interventions which ignore exposure to straight and synthetic MWFs are static. The interventions which reduce exposure to soluble MWF by a quantity determined by exposure to other MWF are dynamic. The dynamic stochastic interventions respect the fact that the REL is for total MWF, not just soluble MWF. If an individual experienced a large amount of exposure to straight and synthetic MWF in one year, then their exposure to soluble MWF should be bounded at a lower level so that the sum of their exposure to soluble, straight, and synthetic MWFs is no greater than the hypothetical limit.  -->

# Conclusions

Associations between several occupations and risk of NHL have been reported previously, but none evaluated the potential effect of hypothetical limits on occupational exposures [@Ekstrom-Smedby_2006;@Chiu_2015;@t-Mannetje_2016;@Callahan_2018]. We found evidence that exposure to soluble MWF was associated with NHL incidence after adjustment for time-varying confounding affected by prior exposure using the hazard-extended ICE parametric g-formula. Reducing cumulative exposure to soluble MWF by enforcing hypothetical, but realistic, interventions on annual average daily exposure would reduce NHL incidence.
\newpage

# Citations

<div id="refs"></div>

### 2023-04-08 reports/paper/paper.qmd
fixed interventions; BS

@@
 format:
- html: default
+ # html: default
  docx:
@@
 
-**Results:** During follow-up, 231 NHL cases occurred.
-Stronger hypothetical limits on soluble MWF exposure resulted in monotonic reductions in NHL risk estimates.
+**Results:** 231 NHL cases occurred over the 20-year follow-up period.
+Stronger hypothetical limits on soluble MWF exposure resulted in monotonic reductions in NHL risk.
 Capping annual average daily exposure at 0.5 mg/m^3^, the NIOSH recommended exposure limit, would have prevented 44 (95% CI: -6, 91) cases.
@@
 
-**Conclusion:** Stronger limits on soluble MWF exposure would have prevented cases of NHL in the UAW-GM cohort.
-Our application demonstrates the utility of an ICE g-formula estimator for estimating the effect of realistic exposure interventions on a survival outcome.
-Greater availability of worked examples and software would facilitate wider application of ICE g-formula estimators.
+**Conclusion:** Limits on soluble MWF exposure would have prevented cases of NHL in the UAW-GM cohort.
+Although MWF use is expected to decline as the automotive industry turns to electric vehicles, a boom in electric vehicle manufacturing could nonetheless lead to global increases in worker exposure to MWF.
+Strong limits on exposure to MWF may be important for preventing NHL incidence during a period of automotive industry expansion.
 
@@
 
-The parametric g-formula has become increasingly popular among epidemiologists in the last decade.
+<!-- The parametric g-formula has become increasingly popular among epidemiologists in the last decade, and there are several exemplary tutorial papers and illustrative examples [@Taubman_2009;@Breskin_2020].
 This analytic approach is attractive in part because it allows investigators to estimate the population-level effect of realistic interventions on exposures that may depend on individuals' covariate history as well as their natural value of exposure.
@@
 They introduced a non-iterative conditional expectation parametric g-formula that requires parametric specification of the full joint distribution of confounders, exposures, and outcomes over time.
+-->
 
-Full parameterization is an attractive choice for investigators seeking to embed real causal knowledge into the estimation problem.
+<!-- Full parameterization is an attractive choice for investigators seeking to embed real causal knowledge into the estimation problem.
 For those who are not completely comfortable with the full set of parametric assumptions, the iterative conditional expectation (ICE) parametric g-formula may be a good alternative.
@@
 Furthermore, the elegance of the ICE parametric g-formula allows analysts to implement the method using standard statistical software, which offers the prospect of greater interpretability and transparency than using "black box" implementations.
+-->
 
-Here, we describe the hazard-extended ICE parametric g-formula, an extension of the ICE parametric g-formula for causal survival analyses, and apply it to estimate counterfactual cumulative incidences of non-Hodgkin lymphoma under hypothetical interventions on annual average daily exposure to soluble metalworking fluids (MWF) in the UAW-GM autoworkers cohort between 1984 and 2005.
+<!-- Here, we describe the hazard-extended ICE parametric g-formula, an extension of the ICE parametric g-formula for causal survival analyses, and apply it to estimate counterfactual cumulative incidences of non-Hodgkin lymphoma under hypothetical interventions on annual average daily exposure to soluble metalworking fluids (MWF) in the UAW-GM autoworkers cohort between 1984 and 2005.
 The interventions we evaluate are modified longitudinal treatment policies which depend on the natural value of exposure [@Taubman_2009;@Richardson_2013;@Haneuse_2013;@Young_2014;@Diaz_2021].
+-->
 
-<!-- Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered substantial research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons per year [@seer_1994;@Ekstrom-Smedby_2006].
+In recent years, there has been a surge in optimism for growth in American manufacturing [@Carr_2022;@Armbrust_2021].
+While it may be easy to imagine a factory floor crowded with workers and heavy machinery, an essential part of the industrial production of physical goods is easy to overlook: lubricants and coolants.
+In industries that require metalworking, from cutting wafers for semiconductor production to stamping metals for electric vehicle battery casings, metalworking fluids (MWF) are essential.
+During use in drawing, stamping, cutting, and grinding operations, MWF are sprayed and poured onto tools and parts to provide lubrication and cooling.
+Parts may even be submerged in MWF in precision manufacturing applications [@Arrabiyeh_2020].
+
+Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered substantial research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons per year [@seer_1994;@Ekstrom-Smedby_2006].
 The strongest known risk factor of NHL is immunosuppression, both congenital and acquired [@Filipovich_1992;@Chiu_2015].
@@
 Since the rise in NHL incidence coincided with a period of rapid and extensive chemicalization in industry, agriculture and warfare, there has been stronger interest in the environmental and occupational epidemiology of NHL [@Nelson_2005;@Romero_2021].
--->
 
-<!-- Pesticide exposure in agricultural occupational settings was a common target of NHL research in recent decades.
+Pesticide exposure in agricultural occupational settings was a common target of NHL research in recent decades.
 A meta-analysis of 44 articles published between 1980 and 2014 found statistically significant associations between NHL and exposure to several classes of pesticides including carbamate, organophosporus, triazine, and organochlorine [@Schinasi_2014].
@@
 Metal processors, health workers, salespeople, machinists, and electricians have all been identified as occupational groups with higher risk of NHL [@Fritschi_2005a; @Mester_2006; @Ekstrom-Smedby_2006].
--->
 
-<!-- Metalworking fluids (MWF), an important class of occupational exposures, are complex mixtures of oils and chemicals used to lubricate and cool metal tools and parts during metal cutting and grinding operations in manufacturing processes.
+Metalworking fluids (MWF), an important class of occupational exposures, are complex mixtures of oils and chemicals used to lubricate and cool metal tools and parts during metal cutting and grinding operations in manufacturing processes.
 During use, MWFs aerosolize and present a potential health hazard to exposed workers.
@@
 Although water-based MWF contain little to no mineral oil, they contain a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987;@IARC_2014;@IARC_2017].
--->
 
-<!-- In occupational studies, measures of time-varying exposure are essential to statistical adjustment for forms of time-varying confounding affected by past exposure such as the healthy worker survivor effect (HWSE).
+In occupational studies, measures of time-varying exposure are essential to statistical adjustment for forms of time-varying confounding affected by past exposure such as the healthy worker survivor effect (HWSE).
 The HWSE is the dynamic selection process by which healthier individuals remain at work, where they accumulate more occupational exposure, and less healthy individuals leave work [@Arrighi_1994].
 Standard analyses of occupational cohorts affected by the HWSE result in a downward bias on the exposure-outcome associations of interest, as less healthy workers typically accrue less exposure than healthier workers.
--->
 
-<!-- Here, we assess the effect of hypothetical MWF exposure limits on cumulative incidence of NHL from 1985 to 2005 in the United Auto Workers-General Motors (UAW-GM) occupational cohort study. -->
-<!-- A recent study of cancer incidence in this cohort linked NHL with exposure to soluble MWF using a standard survival analysis using Cox proportional hazard regression [@Colbeth_2023].
+Here, we assess the effect of hypothetical MWF exposure limits on cumulative incidence of NHL from 1985 to 2005 in the United Auto Workers-General Motors (UAW-GM) occupational cohort study.
+A recent study of cancer incidence in this cohort linked NHL with exposure to soluble MWF using a standard survival analysis using Cox proportional hazard regression [@Colbeth_2023].
 Standard regression methods are vulnerable to bias due to the HWSE.
@@
 Like other causal estimators in statistics, the hazard-extended ICE g-formula yields marginal effect estimates of hypothetical interventions, which may be more interpretable under a population health framework than conditional measures.
--->
 
@@
 
-We estimated NHL cumulative incidence from 1985 to 2005 under hypothetical limits on annual average daily exposure to soluble MWF by applying the hazard-extended iterative conditional expectation (ICE) parametric g-formula estimator [@Wen_2020].
-We leveraged time-varying quantitative MWF exposure data in tandem with employment records to adjust for the HWSE.
+We estimated NHL cumulative incidence from 1985 to 2005 under hypothetical limits on annual average daily exposure to soluble MWF by applying the hazard-extended ICE parametric g-formula estimator [@Wen_2020].
 First, we estimated the expected number of NHL cases that we would observe if there were no censoring by competing risks.
-Then, we contrasted this counterfactual cumulative incidence to that under three the hypothetical exposure limits: (1) the National Institute for Occupational Safety and Health (NIOSH) Recommended Exposure Limit (REL) for total particulate mass (PM) composed of MWFs (0.5 mg/m^3^), (2) half the REL (0.25 mg/m^3^), and (3) a tenth of the REL (0.05 mg/m^3^) were enforced for soluble MWF over workers' entire working lifetimes [@niosh_1998].
-Under these hypothetical interventions, exposure was set at the hypothetical limit if observed exposure was greater than that limit.
-Otherwise, exposure was not intervened upon.
+Then, we contrasted this counterfactual cumulative incidence to that under three hypothetical exposure limits:
+
+(1) 0.5 mg/m^3^: the National Institute for Occupational Safety and Health (NIOSH) Recommended Exposure Limit (REL) for total particulate mass (PM) composed of MWFs [@niosh_1998]
+(2) 0.25 mg/m^3^: Half the REL
+(3) 0.05 mg/m^3^: One tenth of the REL.
+
+Exposure limits were enforced for soluble MWF over workers' entire working lifetimes, thereby inducing a post-intervention exposure distribution from which exposures are drawn.
 
@@
 
-The UAW-GM cohort includes all hourly workers at three automobile manufacturing plants in Michigan who had worked at least three years by 1985.
+We used data from the UAW-GM cohort, which includes all hourly workers at three automobile manufacturing plants in Michigan who had worked at least three years by 1985.
 Past papers provide detailed descriptions of the cohort [@Eisen_1992;@Eisen_2001].
@@
 
-## Statistical methods
+## Hazard-extended ICE parametric g-formula
 
@@
 ```{r}
-intervened_py <- readRDS(here::here("resources", "percent-py-intervened.rds"))
-# paste(paste0("\"", intervened_py$dt.name, "\""), collapse = ",\n") |> clipr::write_clip()
-dat.names <- data.table(
-	dt.name = c(
-		"dat.sol.reduced", "dat.sol.reduced2", "dat.sol.reduced10"),
-	variable.dat = c(
-		"soluble", "soluble2", "soluble10")
-)
-intervened_py <- as.data.table(merge(
-	intervened_py, dat.names,
-	by = "dt.name"))
-intervened_py <- rbindlist(list(
-	data.table(dt.name = NA,
-						 mwf = NA, percent_py_intervened = 0,
-						 variable.dat = "natural"),
-	intervened_py
-))
-```
-
-```{r}
-load(here::here("resources", paste0("h.estimates.rdata")))
+load(here::here("resources", paste0("estimates.rdata")))
+sapply(estimates, mean) 
 estimates.bs <- readRDS(here::here("resources", paste0("estimates.bs.rds")))
@@
 	variable = c(
-		"soluble", "soluble2", "soluble10", "natural"),
-	estimate = c(
-		h.reduction.sol, h.reduction.sol2, h.reduction.sol10,
-		h.baseline)
+		"200", "100", "50", "25", "05", "Any"),
+	estimate =  c(sapply(estimates[2:6], mean),
+								mean(estimates[[1]]))
 )
@@
 	point_estimates[,.(
-		variable = paste0(variable, ".natural"),
-		estimate = estimate/estimate[variable == "natural"]
+		variable = paste0(variable, ".Any"),
+		estimate = estimate/estimate[variable == "Any"]
 	)],
@@
 	rr = estimate[1],
-	rr_lower = {
-		x <- value
-		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
-	rr_upper = {
-		x <- value
-		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
-	# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
-	# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
+	rr_lower = 2 * estimate[1] - quantile(value, 1 - 0.025),
+	rr_upper = 2 * estimate[1] - quantile(value, 0.025)
 	),
@@
 	point_estimates[,.(
-		variable = paste0(variable, ".natural"),
-		estimate = estimate - estimate[variable == "natural"]
+		variable = paste0(variable, ".Any"),
+		estimate = estimate - estimate[variable == "Any"]
 	)],
@@
 # Get lower and upper 2.5th %tiles
+N <- 33134
 rd <- rd[,.(
 	rd = estimate[1],
-	rd_lower = {
-		x <- value
-		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
-	rd_upper = {
-		x <- value
-		x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
+	rd_lower = (2 * estimate[1] - quantile(value, 1 - 0.025)) * N,
+	rd_upper = (2 * estimate[1] - quantile(value, 0.025)) * N
 	# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
@@
 variable]
-
-rd[,(c('rd', 'rd_lower', 'rd_upper')) := list(
-	- rd * 34734,
-	- rd_upper * 34734,
-	- rd_lower * 34734
-	)]
-
 ```
@@
 risks <- risks[,.(estimate = estimate[1],
-			lower = {
-				x <- value
-				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
-			upper = {
-				x <- value
-				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
+			lower = 2 * mean(value) - quantile(value, 1 - 0.025),
+			upper = 2 * mean(value) - quantile(value, 0.025)
 			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
@@
 	variable = c(
-		"natural", "soluble", "soluble2", "soluble10"
+		"200", "100", "50", "25", "05", "Any"
 	),
 	label = c(
-		"None", "0.5", "0.25", "0.05"
+		"2.0", "1.0", "0.5", "0.25", "0.05", "None"
 	)
@@
 contrasts.tab <- merge(
-	contrasts.tab, intervention.labels[,.(variable = paste0(variable, ".natural"), label)],
+	contrasts.tab, intervention.labels[,.(variable = paste0(variable, ".Any"), label)],
 	all = T,
@@
 		intervened_py[match(
-	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
+	 		sapply(variable, gsub, pattern = ".Any", replacement = ""),
 	 		variable.dat
@@
 	sprintf(paste0("%.", digits, "f"), round(risks[match(
-	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
+	 		sapply(variable, gsub, pattern = ".Any", replacement = ""),
 	 		variable.risks
@@
 	 		x <- risks[match(
-	 		sapply(variable, gsub, pattern = ".natural", replacement = ""),
+	 		sapply(variable, gsub, pattern = ".Any", replacement = ""),
 	 		variable.risks
@@
 
-mwf.flextable <- function(x, n_col = 8) {
-	flextable::compose(x, j = c(4, n_col), value = as_paragraph(rep("(95% CI)", 2)),
+mwf.flextable <- function(x, n_col = 7) {
+	flextable::compose(x, j = c(3, n_col), value = as_paragraph(rep("(95% CI)", 2)),
 		part = "header"
@@
 	flextable::align(j = 2:n_col, align = "center", part = "all") |>
-	width(width = c(1.7, 1.1, 0.7, 1, 0.5, 1, 0.5, 1)) |>
 	padding(padding = 1.5, part = "all")
@@
 								 standAlone = T)
-contrasts.tab[grepl("sol|natural\\.natural", variable) & !grepl(
+contrasts.tab[grepl("sol|natural\\.Any", variable) & !grepl(
 	"[a-z]", label),] |> ggplot(
@@
 ```{r}
-contrasts.tab[grepl("sol|natural\\.natural", variable),.(
+contrasts.tab[,.(
 	 	label,
-	 	`Person-years intervened (%)` = clean_percent_py(variable),
-	 	`Cases`  = clean_risk(variable, 0, 34734),
-	 	`(95% CI)`      = clean_risk.ci(variable, 0, 34734),
-	 	`Cases averted`    = round(rd),
-	 	`(95% CI1)`        = c(NA, paste0(
+	 	# `Person-years intervened (%)` = clean_percent_py(variable),
+	 	`Cases`  = clean_risk(variable, 0, N),
+	 	`(95% CI)`      = clean_risk.ci(variable, 0, N),
+	 	`Cases averted`    = round(rd * N),
+	 	`(95% CI1)`        = paste0(
 	 		"(",
-	 		round(na.exclude(rd_lower)), ", ",
-	 		round(na.exclude(rd_upper)), ")")),
+	 		round(rd_lower), ", ",
+	 		round(rd_upper), ")"),
 	 	CIR              = sprintf("%.2f", round(rr, 2)),
 	 	`(95% CI2)`   = clean_rr.ci(rr, rr_lower, rr_upper)
-	 )][c(1, 2, 4, 3),] -> sol.tab
+	 )][c(6, 3, 2, 5, 4, 1),] -> sol.tab
+sol.tab[label == "None", 4:7] <- NA
 
-sol.tab[sol.tab == "NA"] <- NA
 # saveRDS(sol.tab, here::here('resources', 'sol.tab.rds'))
@@
 	) |> mwf.flextable() |>
-	width(width = c(1.1, 1.1, 0.5, 0.9, 0.55, 0.9, 0.5, 0.9)) |>
+	width(width = c(1.1, 0.5, 0.9, 0.55, 0.9, 0.5, 0.9)) |>
 	add_footer_row(values = paste(
 		"CIR: cumulative incidence ratio. MWF: metalworking fluid",
-		sep = "\n"), colwidths = 8) |>
+		sep = "\n"), colwidths = 7) |>
 	hline_bottom(part = "footer") |>

### 2023-04-08 resources/exposure.tex
manuscript prepared
fixed interventions; BS

@@
-% Created by tikzDevice version 0.12.3.1 on 2022-04-22 17:18:12
+% Created by tikzDevice version 0.12.3.1 on 2023-04-06 10:31:22
 % !TEX encoding = UTF-8 Unicode
@@
 \usepackage{amssymb}
+\usepackage{upgreek}
 \usepackage[no-math]{fontspec}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,180.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,180.68);
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.15, 28.21) rectangle (155.80,162.23);
+\path[clip] ( 35.37, 28.21) rectangle (162.62,162.23);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 25.15, 28.21) rectangle (155.80,162.23);
+\path[fill=fillColor] ( 35.37, 28.21) rectangle (162.62,162.23);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15, 56.10) --
-	(155.80, 56.10);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 44.76) --
+	(162.62, 44.76);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,101.47) --
-	(155.80,101.47);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 69.57) --
+	(162.62, 69.57);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,146.83) --
-	(155.80,146.83);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 94.37) --
+	(162.62, 94.37);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.63, 28.21) --
-	( 48.63,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,119.17) --
+	(162.62,119.17);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 75.63, 28.21) --
-	( 75.63,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,143.98) --
+	(162.62,143.98);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (102.62, 28.21) --
-	(102.62,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.54, 28.21) --
+	( 63.54,162.23);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (129.62, 28.21) --
-	(129.62,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (100.86, 28.21) --
+	(100.86,162.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 33.42) --
-	(155.80, 33.42);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (138.18, 28.21) --
+	(138.18,162.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 78.78) --
-	(155.80, 78.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 32.36) --
+	(162.62, 32.36);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,124.15) --
-	(155.80,124.15);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 57.16) --
+	(162.62, 57.16);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14, 28.21) --
-	( 35.14,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 81.97) --
+	(162.62, 81.97);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.13, 28.21) --
-	( 62.13,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,106.77) --
+	(162.62,106.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.13, 28.21) --
-	( 89.13,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,131.58) --
+	(162.62,131.58);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.12, 28.21) --
-	(116.12,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,156.38) --
+	(162.62,156.38);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (143.12, 28.21) --
-	(143.12,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.88, 28.21) --
+	( 44.88,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.20, 28.21) --
+	( 82.20,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.52, 28.21) --
+	(119.52,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.83, 28.21) --
+	(156.83,162.23);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14,116.20) --
-	( 36.49,154.33) --
-	( 37.83,144.98) --
-	( 39.18,118.42) --
-	( 40.53,121.74) --
-	( 41.88,121.74) --
-	( 43.23,122.07) --
-	( 44.58,133.91) --
-	( 45.93,153.22) --
-	( 47.28,154.33) --
-	( 48.63,154.33) --
-	( 49.98,156.14) --
-	( 51.33,154.33) --
-	( 52.68,133.91) --
-	( 54.03,154.33) --
-	( 55.38,156.14) --
-	( 56.73,156.14) --
-	( 58.08,156.14) --
-	( 59.43,133.91) --
-	( 60.78,154.33) --
-	( 62.13,145.58) --
-	( 63.48,141.88) --
-	( 64.83,120.02) --
-	( 66.18,133.91) --
-	( 67.53,134.46) --
-	( 68.88,122.01) --
-	( 70.23, 94.47) --
-	( 71.58,103.66) --
-	( 72.93, 95.01) --
-	( 74.28, 94.47) --
-	( 75.63, 92.26) --
-	( 76.98, 92.10) --
-	( 78.33, 83.33) --
-	( 79.68, 83.33) --
-	( 81.03, 85.43) --
-	( 82.38, 85.43) --
-	( 83.73, 83.33) --
-	( 85.08, 85.43) --
-	( 86.43, 80.26) --
-	( 87.78, 83.77) --
-	( 89.13, 87.97) --
-	( 90.48, 84.75) --
-	( 91.83, 90.01) --
-	( 93.18, 90.64) --
-	( 94.53, 87.88) --
-	( 95.87, 86.46) --
-	( 97.22, 85.35) --
-	( 98.57, 83.33) --
-	( 99.92, 83.33) --
-	(101.27, 85.19) --
-	(102.62, 52.02) --
-	(103.97, 52.30) --
-	(105.32, 50.60) --
-	(106.67, 50.94) --
-	(108.02, 47.63) --
-	(109.37, 48.18) --
-	(110.72, 49.42) --
-	(112.07, 49.79) --
-	(113.42, 49.46) --
-	(114.77, 49.79) --
-	(116.12, 44.84) --
-	(117.47, 46.82) --
-	(118.82, 43.96) --
-	(120.17, 44.33) --
-	(121.52, 48.46) --
-	(122.87, 46.75) --
-	(124.22, 44.89) --
-	(125.57, 44.67) --
-	(126.92, 43.52) --
-	(128.27, 43.38) --
-	(129.62, 43.35) --
-	(130.97, 42.97) --
-	(132.32, 42.70) --
-	(133.67, 41.95) --
-	(135.02, 39.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.75,139.99) --
+	( 48.61,123.33) --
+	( 50.48,130.79) --
+	( 52.35,140.45) --
+	( 54.21,128.18) --
+	( 56.08,130.82) --
+	( 57.94,143.76) --
+	( 59.81,143.17) --
+	( 61.68,156.14) --
+	( 63.54,142.11) --
+	( 65.41,141.53) --
+	( 67.27,118.13) --
+	( 69.14,127.52) --
+	( 71.00,133.98) --
+	( 72.87,137.54) --
+	( 74.74,132.30) --
+	( 76.60,138.56) --
+	( 78.47,120.48) --
+	( 80.33,141.46) --
+	( 82.20,145.32) --
+	( 84.07,141.53) --
+	( 85.93,149.94) --
+	( 87.80,150.14) --
+	( 89.66,146.20) --
+	( 91.53,141.53) --
+	( 93.39,141.53) --
+	( 95.26,141.53) --
+	( 97.13,141.53) --
+	( 98.99,142.55) --
+	(100.86, 71.73) --
+	(102.72, 72.60) --
+	(104.59, 69.29) --
+	(106.46, 69.92) --
+	(108.32, 62.24) --
+	(110.19, 63.56) --
+	(112.05, 66.32) --
+	(113.92, 68.18) --
+	(115.78, 66.95) --
+	(117.65, 68.18) --
+	(119.52, 57.01) --
+	(121.38, 61.53) --
+	(123.25, 55.24) --
+	(125.11, 55.83) --
+	(126.98, 65.33) --
+	(128.85, 61.53) --
+	(130.71, 57.67) --
+	(132.58, 56.97) --
+	(134.44, 54.48) --
+	(136.31, 54.14) --
+	(138.18, 54.08) --
+	(140.04, 53.17) --
+	(141.91, 52.60) --
+	(143.77, 50.78) --
+	(145.64, 44.72);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15, 28.21) rectangle (155.80,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37, 28.21) rectangle (162.62,162.23);
 \end{scope}
 \begin{scope}
-\path[clip] (161.30, 28.21) rectangle (291.96,162.23);
+\path[clip] (168.12, 28.21) rectangle (295.37,162.23);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (161.30, 28.21) rectangle (291.96,162.23);
+\path[fill=fillColor] (168.12, 28.21) rectangle (295.37,162.23);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30, 56.10) --
-	(291.96, 56.10);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12, 44.76) --
+	(295.37, 44.76);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30,101.47) --
-	(291.96,101.47);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12, 69.57) --
+	(295.37, 69.57);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30,146.83) --
-	(291.96,146.83);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12, 94.37) --
+	(295.37, 94.37);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (184.79, 28.21) --
-	(184.79,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12,119.17) --
+	(295.37,119.17);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (211.79, 28.21) --
-	(211.79,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12,143.98) --
+	(295.37,143.98);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (238.78, 28.21) --
-	(238.78,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (196.29, 28.21) --
+	(196.29,162.23);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (265.78, 28.21) --
-	(265.78,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (233.61, 28.21) --
+	(233.61,162.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30, 33.42) --
-	(291.96, 33.42);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (270.93, 28.21) --
+	(270.93,162.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30, 78.78) --
-	(291.96, 78.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12, 32.36) --
+	(295.37, 32.36);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30,124.15) --
-	(291.96,124.15);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12, 57.16) --
+	(295.37, 57.16);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (171.29, 28.21) --
-	(171.29,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12, 81.97) --
+	(295.37, 81.97);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (198.29, 28.21) --
-	(198.29,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12,106.77) --
+	(295.37,106.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.28, 28.21) --
-	(225.28,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12,131.58) --
+	(295.37,131.58);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (252.28, 28.21) --
-	(252.28,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12,156.38) --
+	(295.37,156.38);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (279.27, 28.21) --
-	(279.27,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (177.63, 28.21) --
+	(177.63,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.95, 28.21) --
+	(214.95,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (252.27, 28.21) --
+	(252.27,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (289.58, 28.21) --
+	(289.58,162.23);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (171.29, 38.43) --
-	(172.64, 41.00) --
-	(173.99, 44.55) --
-	(175.34, 41.44) --
-	(176.69, 41.41) --
-	(178.04, 43.59) --
-	(179.39, 39.58) --
-	(180.74, 45.48) --
-	(182.09, 46.31) --
-	(183.44, 48.44) --
-	(184.79, 44.69) --
-	(186.14, 48.44) --
-	(187.49, 48.44) --
-	(188.84, 40.74) --
-	(190.19, 43.24) --
-	(191.54, 44.57) --
-	(192.89, 44.87) --
-	(194.24, 48.44) --
-	(195.59, 39.48) --
-	(196.94, 48.44) --
-	(198.29, 42.04) --
-	(199.64, 51.78) --
-	(200.99, 48.44) --
-	(202.34, 51.09) --
-	(203.69, 51.78) --
-	(205.04, 47.41) --
-	(206.39, 54.88) --
-	(207.74, 57.99) --
-	(209.09, 52.89) --
-	(210.44, 53.09) --
-	(211.79, 51.22) --
-	(213.14, 43.75) --
-	(214.49, 39.34) --
-	(215.84, 38.74) --
-	(217.19, 39.51) --
-	(218.53, 39.79) --
-	(219.88, 39.48) --
-	(221.23, 39.48) --
-	(222.58, 38.45) --
-	(223.93, 40.70) --
-	(225.28, 40.77) --
-	(226.63, 39.48) --
-	(227.98, 43.17) --
-	(229.33, 43.78) --
-	(230.68, 43.24) --
-	(232.03, 43.81) --
-	(233.38, 43.81) --
-	(234.73, 43.81) --
-	(236.08, 43.81) --
-	(237.43, 43.81) --
-	(238.78, 39.57) --
-	(240.13, 40.14) --
-	(241.48, 40.57) --
-	(242.83, 39.42) --
-	(244.18, 37.52) --
-	(245.53, 37.52) --
-	(246.88, 36.98) --
-	(248.23, 36.49) --
-	(249.58, 36.49) --
-	(250.93, 36.49) --
-	(252.28, 36.49) --
-	(253.63, 36.49) --
-	(254.98, 36.07) --
-	(256.33, 36.38) --
-	(257.68, 36.49) --
-	(259.03, 36.49) --
-	(260.38, 37.34) --
-	(261.73, 37.85) --
-	(263.08, 37.83) --
-	(264.43, 37.00) --
-	(265.78, 37.55) --
-	(267.13, 37.79) --
-	(268.48, 37.52) --
-	(269.83, 37.68) --
-	(271.18, 36.99);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (179.50, 64.49) --
+	(181.37, 67.76) --
+	(183.23, 54.42) --
+	(185.10, 58.48) --
+	(186.96, 50.99) --
+	(188.83, 54.60) --
+	(190.69, 56.67) --
+	(192.56, 51.09) --
+	(194.43, 53.62) --
+	(196.29, 45.62) --
+	(198.16, 43.01) --
+	(200.02, 43.01) --
+	(201.89, 43.37) --
+	(203.76, 43.37) --
+	(205.62, 43.37) --
+	(207.49, 43.37) --
+	(209.35, 43.37) --
+	(211.22, 43.37) --
+	(213.08, 43.37) --
+	(214.95, 44.40) --
+	(216.82, 43.37) --
+	(218.68, 46.38) --
+	(220.55, 45.62) --
+	(222.41, 48.79) --
+	(224.28, 54.13) --
+	(226.15, 55.09) --
+	(228.01, 55.09) --
+	(229.88, 55.09) --
+	(231.74, 55.09) --
+	(233.61, 45.48) --
+	(235.48, 46.84) --
+	(237.34, 48.19) --
+	(239.21, 45.83) --
+	(241.07, 41.35) --
+	(242.94, 41.35) --
+	(244.80, 39.86) --
+	(246.67, 39.08) --
+	(248.54, 39.08) --
+	(250.40, 39.08) --
+	(252.27, 39.08) --
+	(254.13, 39.08) --
+	(256.00, 38.03) --
+	(257.87, 38.83) --
+	(259.73, 39.08) --
+	(261.60, 39.08) --
+	(263.46, 40.81) --
+	(265.33, 42.05) --
+	(267.19, 42.01) --
+	(269.06, 39.65) --
+	(270.93, 41.22) --
+	(272.79, 41.91) --
+	(274.66, 41.29) --
+	(276.52, 41.67) --
+	(278.39, 39.78);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (161.30, 28.21) rectangle (291.96,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.12, 28.21) rectangle (295.37,162.23);
 \end{scope}
 \begin{scope}
-\path[clip] (297.46, 28.21) rectangle (428.12,162.23);
+\path[clip] (300.87, 28.21) rectangle (428.12,162.23);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (297.46, 28.21) rectangle (428.12,162.23);
+\path[fill=fillColor] (300.87, 28.21) rectangle (428.12,162.23);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46, 56.10) --
-	(428.12, 56.10);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87, 44.76) --
+	(428.12, 44.76);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46,101.47) --
-	(428.12,101.47);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87, 69.57) --
+	(428.12, 69.57);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46,146.83) --
-	(428.12,146.83);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87, 94.37) --
+	(428.12, 94.37);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (320.95, 28.21) --
-	(320.95,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87,119.17) --
+	(428.12,119.17);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (347.94, 28.21) --
-	(347.94,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87,143.98) --
+	(428.12,143.98);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (374.94, 28.21) --
-	(374.94,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (329.04, 28.21) --
+	(329.04,162.23);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (401.93, 28.21) --
-	(401.93,162.23);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (366.36, 28.21) --
+	(366.36,162.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46, 33.42) --
-	(428.12, 33.42);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (403.68, 28.21) --
+	(403.68,162.23);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46, 78.78) --
-	(428.12, 78.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87, 32.36) --
+	(428.12, 32.36);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46,124.15) --
-	(428.12,124.15);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87, 57.16) --
+	(428.12, 57.16);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (307.45, 28.21) --
-	(307.45,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87, 81.97) --
+	(428.12, 81.97);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (334.45, 28.21) --
-	(334.45,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87,106.77) --
+	(428.12,106.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.44, 28.21) --
-	(361.44,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87,131.58) --
+	(428.12,131.58);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (388.44, 28.21) --
-	(388.44,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87,156.38) --
+	(428.12,156.38);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (415.43, 28.21) --
-	(415.43,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.38, 28.21) --
+	(310.38,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (347.70, 28.21) --
+	(347.70,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (385.02, 28.21) --
+	(385.02,162.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (422.34, 28.21) --
+	(422.34,162.23);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (308.80, 44.87) --
-	(310.15, 44.87) --
-	(311.50, 44.87) --
-	(312.85, 42.13) --
-	(314.20, 42.13) --
-	(315.55, 44.87) --
-	(316.90, 44.87) --
-	(318.25, 44.27) --
-	(319.60, 42.32) --
-	(320.95, 48.60) --
-	(322.30, 50.46) --
-	(323.65, 69.90) --
-	(325.00, 69.90) --
-	(326.35, 69.90) --
-	(327.70, 42.93) --
-	(329.05, 42.93) --
-	(330.40, 50.03) --
-	(331.75,116.91) --
-	(333.10,120.23) --
-	(334.45, 42.93) --
-	(335.80, 42.93) --
-	(337.15, 64.53) --
-	(338.50, 76.72) --
-	(339.85, 64.53) --
-	(341.19, 53.70) --
-	(342.54, 64.53) --
-	(343.89, 53.70) --
-	(345.24, 43.76) --
-	(346.59, 43.30) --
-	(347.94, 40.78) --
-	(349.29, 50.31) --
-	(350.64, 51.13) --
-	(351.99, 38.87) --
-	(353.34, 38.87) --
-	(354.69, 39.55) --
-	(356.04, 38.90) --
-	(357.39, 40.47) --
-	(358.74, 38.87) --
-	(360.09, 38.87) --
-	(361.44, 38.93) --
-	(362.79, 38.87) --
-	(364.14, 38.87) --
-	(365.49, 38.88) --
-	(366.84, 39.40) --
-	(368.19, 40.34) --
-	(369.54, 39.02) --
-	(370.89, 40.49) --
-	(372.24, 40.05) --
-	(373.59, 41.08) --
-	(374.94, 35.04) --
-	(376.29, 35.19) --
-	(377.64, 35.19) --
-	(378.99, 35.03) --
-	(380.34, 34.30) --
-	(381.69, 34.31) --
-	(383.04, 34.53) --
-	(384.39, 34.50) --
-	(385.74, 34.43) --
-	(387.09, 34.76) --
-	(388.44, 34.80) --
-	(389.79, 34.95) --
-	(391.14, 34.71) --
-	(392.49, 34.93) --
-	(393.84, 35.19) --
-	(395.19, 35.19) --
-	(396.54, 36.02) --
-	(397.89, 36.03) --
-	(399.23, 36.02) --
-	(400.58, 35.81) --
-	(401.93, 36.04) --
-	(403.28, 35.88) --
-	(404.63, 35.23) --
-	(405.98, 36.84) --
-	(407.33, 35.58);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (312.25, 72.54) --
+	(314.12,127.07) --
+	(315.98,127.07) --
+	(317.85,113.74) --
+	(319.71, 88.56) --
+	(321.58,100.41) --
+	(323.45, 76.72) --
+	(325.31, 54.98) --
+	(327.18, 53.98) --
+	(329.04, 48.46) --
+	(330.91, 70.36) --
+	(332.77, 71.10) --
+	(334.64, 44.28) --
+	(336.51, 44.28) --
+	(338.37, 45.88) --
+	(340.24, 44.35) --
+	(342.10, 48.14) --
+	(343.97, 44.28) --
+	(345.84, 44.28) --
+	(347.70, 44.97) --
+	(349.57, 44.28) --
+	(351.43, 44.28) --
+	(353.30, 44.40) --
+	(355.17, 45.60) --
+	(357.03, 47.66) --
+	(358.90, 45.21) --
+	(360.76, 48.23) --
+	(362.63, 47.55) --
+	(364.49, 50.24) --
+	(366.36, 35.96) --
+	(368.23, 36.25) --
+	(370.09, 36.25) --
+	(371.96, 35.89) --
+	(373.82, 34.30) --
+	(375.69, 34.30) --
+	(377.56, 34.62) --
+	(379.42, 34.66) --
+	(381.29, 34.45) --
+	(383.15, 35.26) --
+	(385.02, 35.37) --
+	(386.88, 35.70) --
+	(388.75, 35.18) --
+	(390.62, 35.67) --
+	(392.48, 36.25) --
+	(394.35, 36.25) --
+	(396.21, 38.05) --
+	(398.08, 38.07) --
+	(399.95, 38.05) --
+	(401.81, 37.68) --
+	(403.68, 38.10) --
+	(405.54, 37.67) --
+	(407.41, 36.10) --
+	(409.27, 39.85) --
+	(411.14, 37.05);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.46, 28.21) rectangle (428.12,162.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.87, 28.21) rectangle (428.12,162.23);
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.15,162.23) rectangle (155.80,175.17);
+\path[clip] ( 35.37,162.23) rectangle (162.62,175.17);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,162.23) rectangle (155.80,175.17);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 35.37,162.23) rectangle (162.62,175.17);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 90.48,165.60) {Soluble};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 98.99,165.60) {Soluble};
 \end{scope}
 \begin{scope}
-\path[clip] (161.30,162.23) rectangle (291.96,175.17);
+\path[clip] (168.12,162.23) rectangle (295.37,175.17);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (161.30,162.23) rectangle (291.96,175.17);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (168.12,162.23) rectangle (295.37,175.17);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (226.63,165.60) {Straight};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (231.74,165.60) {Straight};
 \end{scope}
 \begin{scope}
-\path[clip] (297.46,162.23) rectangle (428.12,175.17);
+\path[clip] (300.87,162.23) rectangle (428.12,175.17);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (297.46,162.23) rectangle (428.12,175.17);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (300.87,162.23) rectangle (428.12,175.17);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (362.79,165.60) {Synthetic};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (364.49,165.60) {Synthetic};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14, 25.46) --
-	( 35.14, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.88, 25.46) --
+	( 44.88, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.13, 25.46) --
-	( 62.13, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.20, 25.46) --
+	( 82.20, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.13, 25.46) --
-	( 89.13, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.52, 25.46) --
+	(119.52, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.12, 25.46) --
-	(116.12, 28.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (143.12, 25.46) --
-	(143.12, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.83, 25.46) --
+	(156.83, 28.21);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 35.14, 17.75) {1920};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 44.88, 17.75) {1940};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 62.13, 17.75) {1940};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 82.20, 17.75) {1960};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 89.13, 17.75) {1960};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (119.52, 17.75) {1980};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (116.12, 17.75) {1980};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (143.12, 17.75) {2000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (156.83, 17.75) {2000};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (171.29, 25.46) --
-	(171.29, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (177.63, 25.46) --
+	(177.63, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (198.29, 25.46) --
-	(198.29, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.95, 25.46) --
+	(214.95, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.28, 25.46) --
-	(225.28, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (252.27, 25.46) --
+	(252.27, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (252.28, 25.46) --
-	(252.28, 28.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (279.27, 25.46) --
-	(279.27, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (289.58, 25.46) --
+	(289.58, 28.21);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (171.29, 17.75) {1920};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (177.63, 17.75) {1940};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (198.29, 17.75) {1940};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (214.95, 17.75) {1960};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (225.28, 17.75) {1960};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (252.27, 17.75) {1980};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (252.28, 17.75) {1980};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (279.27, 17.75) {2000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (289.58, 17.75) {2000};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (307.45, 25.46) --
-	(307.45, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.38, 25.46) --
+	(310.38, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (334.45, 25.46) --
-	(334.45, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (347.70, 25.46) --
+	(347.70, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.44, 25.46) --
-	(361.44, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (385.02, 25.46) --
+	(385.02, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (388.44, 25.46) --
-	(388.44, 28.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (415.43, 25.46) --
-	(415.43, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (422.34, 25.46) --
+	(422.34, 28.21);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (307.45, 17.75) {1920};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (310.38, 17.75) {1940};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (334.45, 17.75) {1940};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (347.70, 17.75) {1960};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (361.44, 17.75) {1960};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (385.02, 17.75) {1980};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (388.44, 17.75) {1980};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (415.43, 17.75) {2000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (422.34, 17.75) {2000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 30.66) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 29.61) {0.00};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 76.03) {1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 54.41) {0.25};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,121.39) {2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 79.21) {0.50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,104.02) {0.75};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,128.82) {1.00};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,153.63) {1.25};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 33.42) --
-	( 25.15, 33.42);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 32.36) --
+	( 35.37, 32.36);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 78.78) --
-	( 25.15, 78.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 57.16) --
+	( 35.37, 57.16);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,124.15) --
-	( 25.15,124.15);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 81.97) --
+	( 35.37, 81.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,106.77) --
+	( 35.37,106.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,131.58) --
+	( 35.37,131.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,156.38) --
+	( 35.37,156.38);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (226.63,  7.25) {Calendar year};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (231.74,  7.25) {Calendar year};
 \end{scope}

### 2023-04-08 resources/exposure_long.tex
manuscript prepared
fixed interventions; BS

@@
-% Created by tikzDevice version 0.12.3.1 on 2022-05-11 14:49:57
+% Created by tikzDevice version 0.12.3.1 on 2023-04-06 10:31:57
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 25.15,274.39) rectangle (211.31,379.04);
+\path[clip] ( 35.37,274.39) rectangle (211.31,379.04);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 25.15,274.39) rectangle (211.31,379.04);
+\path[fill=fillColor] ( 35.37,274.39) rectangle (211.31,379.04);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,296.17) --
-	(211.31,296.17);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,287.32) --
+	(211.31,287.32);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,331.59) --
-	(211.31,331.59);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,306.68) --
+	(211.31,306.68);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,367.02) --
-	(211.31,367.02);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,326.05) --
+	(211.31,326.05);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 58.61,274.39) --
-	( 58.61,379.04);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,345.42) --
+	(211.31,345.42);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 97.07,274.39) --
-	( 97.07,379.04);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,364.79) --
+	(211.31,364.79);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (135.54,274.39) --
-	(135.54,379.04);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 66.99,274.39) --
+	( 66.99,379.04);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (174.00,274.39) --
-	(174.00,379.04);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (103.34,274.39) --
+	(103.34,379.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,278.46) --
-	(211.31,278.46);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (139.70,274.39) --
+	(139.70,379.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,313.88) --
-	(211.31,313.88);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (176.05,274.39) --
+	(176.05,379.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,349.30) --
-	(211.31,349.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,277.63) --
+	(211.31,277.63);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38,274.39) --
-	( 39.38,379.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,297.00) --
+	(211.31,297.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.84,274.39) --
-	( 77.84,379.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,316.37) --
+	(211.31,316.37);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.31,274.39) --
-	(116.31,379.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,335.74) --
+	(211.31,335.74);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.77,274.39) --
-	(154.77,379.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,355.10) --
+	(211.31,355.10);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (193.23,274.39) --
-	(193.23,379.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,374.47) --
+	(211.31,374.47);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.82,274.39) --
+	( 48.82,379.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.17,274.39) --
+	( 85.17,379.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.52,274.39) --
+	(121.52,379.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (157.87,274.39) --
+	(157.87,379.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.22,274.39) --
+	(194.22,379.04);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38,343.10) --
-	( 41.30,372.87) --
-	( 43.22,365.57) --
-	( 45.15,344.83) --
-	( 47.07,347.42) --
-	( 48.99,347.42) --
-	( 50.92,347.68) --
-	( 52.84,356.93) --
-	( 54.76,372.01) --
-	( 56.69,372.87) --
-	( 58.61,372.87) --
-	( 60.53,374.28) --
-	( 62.46,372.87) --
-	( 64.38,356.93) --
-	( 66.30,372.87) --
-	( 68.23,374.28) --
-	( 70.15,374.28) --
-	( 72.07,374.28) --
-	( 74.00,356.93) --
-	( 75.92,372.87) --
-	( 77.84,366.04) --
-	( 79.77,363.15) --
-	( 81.69,346.08) --
-	( 83.61,356.93) --
-	( 85.53,357.36) --
-	( 87.46,347.63) --
-	( 89.38,326.13) --
-	( 91.30,333.31) --
-	( 93.23,326.55) --
-	( 95.15,326.13) --
-	( 97.07,324.41) --
-	( 99.00,324.28) --
-	(100.92,317.43) --
-	(102.84,317.43) --
-	(104.77,319.07) --
-	(106.69,319.07) --
-	(108.61,317.43) --
-	(110.54,319.07) --
-	(112.46,315.04) --
-	(114.38,317.78) --
-	(116.31,321.06) --
-	(118.23,318.54) --
-	(120.15,322.65) --
-	(122.07,323.14) --
-	(124.00,320.99) --
-	(125.92,319.88) --
-	(127.84,319.01) --
-	(129.77,317.43) --
-	(131.69,317.43) --
-	(133.61,318.88) --
-	(135.54,292.99) --
-	(137.46,293.20) --
-	(139.38,291.87) --
-	(141.31,292.14) --
-	(143.23,289.56) --
-	(145.15,289.99) --
-	(147.08,290.95) --
-	(149.00,291.24) --
-	(150.92,290.98) --
-	(152.85,291.24) --
-	(154.77,287.38) --
-	(156.69,288.92) --
-	(158.62,286.69) --
-	(160.54,286.98) --
-	(162.46,290.20) --
-	(164.38,288.87) --
-	(166.31,287.41) --
-	(168.23,287.24) --
-	(170.15,286.34) --
-	(172.08,286.23) --
-	(174.00,286.21) --
-	(175.92,285.91) --
-	(177.85,285.70) --
-	(179.77,285.12) --
-	(181.69,282.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99,361.67) --
+	( 88.80,348.66) --
+	( 90.62,354.49) --
+	( 92.44,362.03) --
+	( 94.26,352.45) --
+	( 96.07,354.51) --
+	( 97.89,364.62) --
+	( 99.71,364.16) --
+	(101.53,374.28) --
+	(103.34,363.33) --
+	(105.16,362.87) --
+	(106.98,344.61) --
+	(108.80,351.93) --
+	(110.62,356.98) --
+	(112.43,359.76) --
+	(114.25,355.67) --
+	(116.07,360.55) --
+	(117.89,346.44) --
+	(119.70,362.82) --
+	(121.52,365.84) --
+	(123.34,362.87) --
+	(125.16,369.44) --
+	(126.97,369.60) --
+	(128.79,366.53) --
+	(130.61,362.87) --
+	(132.43,362.87) --
+	(134.24,362.87) --
+	(136.06,362.87) --
+	(137.88,363.68) --
+	(139.70,308.37) --
+	(141.51,309.05) --
+	(143.33,306.47) --
+	(145.15,306.96) --
+	(146.97,300.96) --
+	(148.78,301.99) --
+	(150.60,304.15) --
+	(152.42,305.60) --
+	(154.24,304.64) --
+	(156.06,305.60) --
+	(157.87,296.88) --
+	(159.69,300.41) --
+	(161.51,295.50) --
+	(163.33,295.96) --
+	(165.14,303.38) --
+	(166.96,300.41) --
+	(168.78,297.39) --
+	(170.60,296.85) --
+	(172.41,294.91) --
+	(174.23,294.64) --
+	(176.05,294.59) --
+	(177.87,293.88) --
+	(179.68,293.44) --
+	(181.50,292.01) --
+	(183.32,287.29);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15,274.39) rectangle (211.31,379.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37,274.39) rectangle (211.31,379.04);
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.15,151.30) rectangle (211.31,255.95);
+\path[clip] ( 35.37,151.30) rectangle (211.31,255.95);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 25.15,151.30) rectangle (211.31,255.95);
+\path[fill=fillColor] ( 35.37,151.30) rectangle (211.31,255.95);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,173.08) --
-	(211.31,173.08);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,164.23) --
+	(211.31,164.23);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,208.50) --
-	(211.31,208.50);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,183.59) --
+	(211.31,183.59);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,243.93) --
-	(211.31,243.93);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,202.96) --
+	(211.31,202.96);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 58.61,151.30) --
-	( 58.61,255.95);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,222.33) --
+	(211.31,222.33);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 97.07,151.30) --
-	( 97.07,255.95);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,241.70) --
+	(211.31,241.70);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (135.54,151.30) --
-	(135.54,255.95);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 66.99,151.30) --
+	( 66.99,255.95);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (174.00,151.30) --
-	(174.00,255.95);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (103.34,151.30) --
+	(103.34,255.95);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,155.37) --
-	(211.31,155.37);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (139.70,151.30) --
+	(139.70,255.95);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,190.79) --
-	(211.31,190.79);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (176.05,151.30) --
+	(176.05,255.95);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,226.21) --
-	(211.31,226.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,154.54) --
+	(211.31,154.54);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38,151.30) --
-	( 39.38,255.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,173.91) --
+	(211.31,173.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.84,151.30) --
-	( 77.84,255.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,193.28) --
+	(211.31,193.28);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.31,151.30) --
-	(116.31,255.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,212.65) --
+	(211.31,212.65);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.77,151.30) --
-	(154.77,255.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,232.01) --
+	(211.31,232.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (193.23,151.30) --
-	(193.23,255.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,251.38) --
+	(211.31,251.38);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.82,151.30) --
+	( 48.82,255.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.17,151.30) --
+	( 85.17,255.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.52,151.30) --
+	(121.52,255.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (157.87,151.30) --
+	(157.87,255.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.22,151.30) --
+	(194.22,255.95);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38,159.28) --
-	( 41.30,161.29) --
-	( 43.22,164.06) --
-	( 45.15,161.63) --
-	( 47.07,161.61) --
-	( 48.99,163.31) --
-	( 50.92,160.18) --
-	( 52.84,164.79) --
-	( 54.76,165.43) --
-	( 56.69,167.10) --
-	( 58.61,164.17) --
-	( 60.53,167.10) --
-	( 62.46,167.10) --
-	( 64.38,161.09) --
-	( 66.30,163.03) --
-	( 68.23,164.08) --
-	( 70.15,164.31) --
-	( 72.07,167.10) --
-	( 74.00,160.10) --
-	( 75.92,167.10) --
-	( 77.84,162.10) --
-	( 79.77,169.71) --
-	( 81.69,167.10) --
-	( 83.61,169.16) --
-	( 85.53,169.71) --
-	( 87.46,166.30) --
-	( 89.38,172.13) --
-	( 91.30,174.56) --
-	( 93.23,170.57) --
-	( 95.15,170.73) --
-	( 97.07,169.26) --
-	( 99.00,163.43) --
-	(100.92,159.99) --
-	(102.84,159.53) --
-	(104.77,160.13) --
-	(106.69,160.34) --
-	(108.61,160.10) --
-	(110.54,160.10) --
-	(112.46,159.30) --
-	(114.38,161.05) --
-	(116.31,161.11) --
-	(118.23,160.10) --
-	(120.15,162.98) --
-	(122.07,163.46) --
-	(124.00,163.03) --
-	(125.92,163.48) --
-	(127.84,163.48) --
-	(129.77,163.48) --
-	(131.69,163.48) --
-	(133.61,163.48) --
-	(135.54,160.17) --
-	(137.46,160.62) --
-	(139.38,160.95) --
-	(141.31,160.05) --
-	(143.23,158.57) --
-	(145.15,158.57) --
-	(147.08,158.15) --
-	(149.00,157.76) --
-	(150.92,157.76) --
-	(152.85,157.76) --
-	(154.77,157.76) --
-	(156.69,157.76) --
-	(158.62,157.44) --
-	(160.54,157.68) --
-	(162.46,157.76) --
-	(164.38,157.76) --
-	(166.31,158.43) --
-	(168.23,158.83) --
-	(170.15,158.81) --
-	(172.08,158.16) --
-	(174.00,158.59) --
-	(175.92,158.78) --
-	(177.85,158.57) --
-	(179.77,158.70) --
-	(181.69,158.16);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99,179.63) --
+	( 88.80,182.18) --
+	( 90.62,171.77) --
+	( 92.44,174.94) --
+	( 94.26,169.09) --
+	( 96.07,171.91) --
+	( 97.89,173.52) --
+	( 99.71,169.17) --
+	(101.53,171.14) --
+	(103.34,164.90) --
+	(105.16,162.86) --
+	(106.98,162.86) --
+	(108.80,163.14) --
+	(110.62,163.14) --
+	(112.43,163.14) --
+	(114.25,163.14) --
+	(116.07,163.14) --
+	(117.89,163.14) --
+	(119.70,163.14) --
+	(121.52,163.95) --
+	(123.34,163.14) --
+	(125.16,165.49) --
+	(126.97,164.90) --
+	(128.79,167.37) --
+	(130.61,171.54) --
+	(132.43,172.29) --
+	(134.24,172.29) --
+	(136.06,172.29) --
+	(137.88,172.29) --
+	(139.70,164.79) --
+	(141.51,165.85) --
+	(143.33,166.90) --
+	(145.15,165.06) --
+	(146.97,161.56) --
+	(148.78,161.56) --
+	(150.60,160.39) --
+	(152.42,159.79) --
+	(154.24,159.79) --
+	(156.06,159.79) --
+	(157.87,159.79) --
+	(159.69,159.79) --
+	(161.51,158.97) --
+	(163.33,159.59) --
+	(165.14,159.79) --
+	(166.96,159.79) --
+	(168.78,161.14) --
+	(170.60,162.11) --
+	(172.41,162.08) --
+	(174.23,160.23) --
+	(176.05,161.46) --
+	(177.87,162.00) --
+	(179.68,161.52) --
+	(181.50,161.81) --
+	(183.32,160.34);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15,151.30) rectangle (211.31,255.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37,151.30) rectangle (211.31,255.95);
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.15, 28.21) rectangle (211.31,132.86);
+\path[clip] ( 35.37, 28.21) rectangle (211.31,132.86);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 25.15, 28.21) rectangle (211.31,132.86);
+\path[fill=fillColor] ( 35.37, 28.21) rectangle (211.31,132.86);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15, 49.99) --
-	(211.31, 49.99);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 41.14) --
+	(211.31, 41.14);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15, 85.41) --
-	(211.31, 85.41);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 60.50) --
+	(211.31, 60.50);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,120.84) --
-	(211.31,120.84);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 79.87) --
+	(211.31, 79.87);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 58.61, 28.21) --
-	( 58.61,132.86);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 99.24) --
+	(211.31, 99.24);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 97.07, 28.21) --
-	( 97.07,132.86);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,118.61) --
+	(211.31,118.61);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (135.54, 28.21) --
-	(135.54,132.86);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 66.99, 28.21) --
+	( 66.99,132.86);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (174.00, 28.21) --
-	(174.00,132.86);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (103.34, 28.21) --
+	(103.34,132.86);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 32.28) --
-	(211.31, 32.28);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (139.70, 28.21) --
+	(139.70,132.86);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 67.70) --
-	(211.31, 67.70);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (176.05, 28.21) --
+	(176.05,132.86);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,103.12) --
-	(211.31,103.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 31.45) --
+	(211.31, 31.45);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38, 28.21) --
-	( 39.38,132.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 50.82) --
+	(211.31, 50.82);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.84, 28.21) --
-	( 77.84,132.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 70.19) --
+	(211.31, 70.19);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.31, 28.21) --
-	(116.31,132.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 89.56) --
+	(211.31, 89.56);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.77, 28.21) --
-	(154.77,132.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,108.92) --
+	(211.31,108.92);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (193.23, 28.21) --
-	(193.23,132.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,128.29) --
+	(211.31,128.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.82, 28.21) --
+	( 48.82,132.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.17, 28.21) --
+	( 85.17,132.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.52, 28.21) --
+	(121.52,132.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (157.87, 28.21) --
+	(157.87,132.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.22, 28.21) --
+	(194.22,132.86);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.30, 41.22) --
-	( 43.22, 41.22) --
-	( 45.15, 41.22) --
-	( 47.07, 39.08) --
-	( 48.99, 39.08) --
-	( 50.92, 41.22) --
-	( 52.84, 41.22) --
-	( 54.76, 40.75) --
-	( 56.69, 39.23) --
-	( 58.61, 44.13) --
-	( 60.53, 45.59) --
-	( 62.46, 60.76) --
-	( 64.38, 60.76) --
-	( 66.30, 60.76) --
-	( 68.23, 39.70) --
-	( 70.15, 39.70) --
-	( 72.07, 45.25) --
-	( 74.00, 97.47) --
-	( 75.92,100.06) --
-	( 77.84, 39.70) --
-	( 79.77, 39.70) --
-	( 81.69, 56.57) --
-	( 83.61, 66.09) --
-	( 85.53, 56.57) --
-	( 87.46, 48.11) --
-	( 89.38, 56.57) --
-	( 91.30, 48.11) --
-	( 93.23, 40.35) --
-	( 95.15, 39.99) --
-	( 97.07, 38.02) --
-	( 99.00, 45.46) --
-	(100.92, 46.11) --
-	(102.84, 36.53) --
-	(104.77, 36.53) --
-	(106.69, 37.07) --
-	(108.61, 36.56) --
-	(110.54, 37.79) --
-	(112.46, 36.53) --
-	(114.38, 36.53) --
-	(116.31, 36.58) --
-	(118.23, 36.53) --
-	(120.15, 36.53) --
-	(122.07, 36.54) --
-	(124.00, 36.95) --
-	(125.92, 37.68) --
-	(127.84, 36.65) --
-	(129.77, 37.80) --
-	(131.69, 37.46) --
-	(133.61, 38.26) --
-	(135.54, 33.55) --
-	(137.46, 33.66) --
-	(139.38, 33.66) --
-	(141.31, 33.53) --
-	(143.23, 32.97) --
-	(145.15, 32.97) --
-	(147.08, 33.14) --
-	(149.00, 33.12) --
-	(150.92, 33.07) --
-	(152.85, 33.33) --
-	(154.77, 33.36) --
-	(156.69, 33.47) --
-	(158.62, 33.29) --
-	(160.54, 33.46) --
-	(162.46, 33.66) --
-	(164.38, 33.66) --
-	(166.31, 34.31) --
-	(168.23, 34.31) --
-	(170.15, 34.31) --
-	(172.08, 34.14) --
-	(174.00, 34.32) --
-	(175.92, 34.20) --
-	(177.85, 33.69) --
-	(179.77, 34.95) --
-	(181.69, 33.96);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 62.82) --
+	( 88.80,105.41) --
+	( 90.62,105.41) --
+	( 92.44, 95.00) --
+	( 94.26, 75.34) --
+	( 96.07, 84.59) --
+	( 97.89, 66.09) --
+	( 99.71, 49.12) --
+	(101.53, 48.33) --
+	(103.34, 44.02) --
+	(105.16, 61.12) --
+	(106.98, 61.70) --
+	(108.80, 40.76) --
+	(110.62, 40.76) --
+	(112.43, 42.01) --
+	(114.25, 40.81) --
+	(116.07, 43.77) --
+	(117.89, 40.76) --
+	(119.70, 40.76) --
+	(121.52, 41.30) --
+	(123.34, 40.76) --
+	(125.16, 40.76) --
+	(126.97, 40.85) --
+	(128.79, 41.79) --
+	(130.61, 43.40) --
+	(132.43, 41.49) --
+	(134.24, 43.85) --
+	(136.06, 43.31) --
+	(137.88, 45.41) --
+	(139.70, 34.26) --
+	(141.51, 34.49) --
+	(143.33, 34.49) --
+	(145.15, 34.20) --
+	(146.97, 32.97) --
+	(148.78, 32.97) --
+	(150.60, 33.21) --
+	(152.42, 33.25) --
+	(154.24, 33.08) --
+	(156.06, 33.71) --
+	(157.87, 33.80) --
+	(159.69, 34.06) --
+	(161.51, 33.66) --
+	(163.33, 34.04) --
+	(165.14, 34.49) --
+	(166.96, 34.49) --
+	(168.78, 35.90) --
+	(170.60, 35.91) --
+	(172.41, 35.90) --
+	(174.23, 35.61) --
+	(176.05, 35.93) --
+	(177.87, 35.60) --
+	(179.68, 34.37) --
+	(181.50, 37.30) --
+	(183.32, 35.12);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15, 28.21) rectangle (211.31,132.86);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37, 28.21) rectangle (211.31,132.86);
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.15,132.86) rectangle (211.31,145.80);
+\path[clip] ( 35.37,132.86) rectangle (211.31,145.80);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,132.86) rectangle (211.31,145.80);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 35.37,132.86) rectangle (211.31,145.80);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (118.23,136.23) {Synthetic};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (123.34,136.23) {Synthetic};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.15,255.95) rectangle (211.31,268.89);
+\path[clip] ( 35.37,255.95) rectangle (211.31,268.89);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,255.95) rectangle (211.31,268.89);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 35.37,255.95) rectangle (211.31,268.89);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (118.23,259.32) {Straight};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (123.34,259.32) {Straight};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.15,379.04) rectangle (211.31,391.99);
+\path[clip] ( 35.37,379.04) rectangle (211.31,391.99);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,379.04) rectangle (211.31,391.98);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 35.37,379.04) rectangle (211.31,391.98);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (118.23,382.41) {Soluble};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (123.34,382.41) {Soluble};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.38, 25.46) --
-	( 39.38, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.82, 25.46) --
+	( 48.82, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.84, 25.46) --
-	( 77.84, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.17, 25.46) --
+	( 85.17, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.31, 25.46) --
-	(116.31, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.52, 25.46) --
+	(121.52, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.77, 25.46) --
-	(154.77, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (157.87, 25.46) --
+	(157.87, 28.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (193.23, 25.46) --
-	(193.23, 28.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.22, 25.46) --
+	(194.22, 28.21);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 39.38, 17.75) {1920};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 48.82, 17.75) {1920};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 77.84, 17.75) {1940};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 85.17, 17.75) {1940};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (116.31, 17.75) {1960};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (121.52, 17.75) {1960};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (154.77, 17.75) {1980};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (157.87, 17.75) {1980};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (193.23, 17.75) {2000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (194.22, 17.75) {2000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,275.70) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,274.88) {0.00};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,311.13) {1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,294.25) {0.25};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,346.55) {2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,313.61) {0.50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,332.98) {0.75};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,352.35) {1.00};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,371.72) {1.25};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,278.46) --
-	( 25.15,278.46);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,277.63) --
+	( 35.37,277.63);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,313.88) --
-	( 25.15,313.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,297.00) --
+	( 35.37,297.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,349.30) --
-	( 25.15,349.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,316.37) --
+	( 35.37,316.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,335.74) --
+	( 35.37,335.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,355.10) --
+	( 35.37,355.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,374.47) --
+	( 35.37,374.47);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,152.61) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,151.79) {0.00};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,188.04) {1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,171.16) {0.25};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,223.46) {2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,190.52) {0.50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,209.89) {0.75};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,229.26) {1.00};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,248.63) {1.25};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,155.37) --
-	( 25.15,155.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,154.54) --
+	( 35.37,154.54);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,190.79) --
-	( 25.15,190.79);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,173.91) --
+	( 35.37,173.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,226.21) --
-	( 25.15,226.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,193.28) --
+	( 35.37,193.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,212.65) --
+	( 35.37,212.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,232.01) --
+	( 35.37,232.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,251.38) --
+	( 35.37,251.38);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 29.52) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 28.70) {0.00};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 64.94) {1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 48.06) {0.25};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20,100.37) {2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 67.43) {0.50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 86.80) {0.75};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,106.17) {1.00};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,125.54) {1.25};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 32.28) --
-	( 25.15, 32.28);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 31.45) --
+	( 35.37, 31.45);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 67.70) --
-	( 25.15, 67.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 50.82) --
+	( 35.37, 50.82);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,103.12) --
-	( 25.15,103.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 70.19) --
+	( 35.37, 70.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 89.56) --
+	( 35.37, 89.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,108.92) --
+	( 35.37,108.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,128.29) --
+	( 35.37,128.29);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (118.23,  7.25) {Calendar year};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (123.34,  7.25) {Calendar year};
 \end{scope}

### 2023-04-08 breaks.R

@@ -1,0 +1,173 @@
+# Define quantiles ####
+get.covariate.breaks <- function(dat, cutpoints = c(100, 80, 60, 40) - 20) {
+	covariate.breaks <- apply(dat[status == 1, .(
+		year,
+		yin = yin.gm,
+		employment.years,
+		age = age.year2 / 365,
+		cum_off)], 2, function(x) {
+			if (length(x) > cutpoints[1]) {
+				breaks <- quantile(x, seq(0, 1, 1 / 6))
+			} else if (length(x) > cutpoints[2]) {
+				breaks <- quantile(x, seq(0, 1, 1 / 5))
+			} else if (length(x) > cutpoints[3]) {
+				breaks <- quantile(x, seq(0, 1, 1 / 4))
+			} else if (length(x) > cutpoints[4]) {
+				breaks <- quantile(x, seq(0, 1, 1 / 3))
+			} else {
+				breaks <- quantile(x, seq(0, 1, 1 / 2))
+			}
+			breaks[-length(breaks)] <- floor(breaks[-length(breaks)])
+			breaks[length(breaks)] <- ceiling(breaks[length(breaks)])
+			breaks[c(1, length(breaks))] <- c(-Inf, Inf)
+			breaks
+		})
+
+	covariate.breaks <- as.data.table(covariate.breaks)
+
+	return(covariate.breaks)
+}
+
+get.mwf.breaks <- function(dat) {
+	mwf.breaks <- cbind(apply(dat[status == 1, .(
+		straight,
+		soluble,
+		synthetic,
+		off,
+		cum_straight,
+		# cum_soluble,
+		cum_synthetic,
+		cum_off)], 2, function(x) {
+			x <- x[x > 0]
+			if (length(x) > 40) {
+				if (length(x) > 60) {
+					probs <- seq(0, 1, 1 / 3)
+				} else {
+					probs <- seq(0, 1, 1 / 2)
+				}
+				breaks <- quantile(x, probs)
+				breaks[c(1, length(probs))] <- c(0, Inf)
+				breaks <- c(-Inf, breaks)
+			} else {
+				breaks <- c(-Inf, 0, Inf)
+			}
+			if (length(breaks) < 5) {
+				breaks <- c(breaks, rep(NA, 5 - length(breaks)))
+			}
+			names(breaks) <- NULL
+			breaks
+		}),
+		apply(dat[status == 1, .(cum_soluble)], 2, function(x) {
[…]

### 2023-04-08 g-formula.R

@@ -3,180 +3,172 @@
 # November 3, 2020
 
 library(here)
-library(boxr)
+library(boxr); box_auth()
 library(survival)
-box_auth()
 
 # Get raw data and helper functions ####
-exposure.lag <- 10
 race.imputed.melt <- NULL
 source("~/headRs/00-my-theme.R")
 library(data.table)
 # # paste(ls(), collapse = ",\n") %>% clipr::write_clip()
-source(here::here("../gm-cancer-inc/breaks.R"))
-
-# Relevant covariates ####
-covariates.which <- c(
-	"studyno", "I", "year", "immortal",
-	"status", "Censored", "Other event", "All causes",
-	"age.year2", "Age", "year2", "Year",
-	"straight", "soluble", "synthetic",
-	"Straight", "Soluble", "Synthetic",
-	"Cumulative straight", "Cumulative soluble", "Cumulative synthetic",
-	"cum_straight", "cum_soluble", "cum_synthetic",
-	"Employment status",
-	"Duration of employment", "employment.years",
-	"Cumulative time off", "cum_off",
-	"Year of hire", "yin.gm", "Sex", "Race", "Plant")
+source(here::here("breaks.R"))
 
 #####################################################
 # Iterated conditional expectation g-computation ####
 #####################################################
-
 # Hazard-extended ICE implementation of g-formula ####
 # Wen et al. (2020)
 ice_gcomp <- function(
-		a = 0,
-		dta = copy(dat.reduced[,covariates.which, with = F]),
-		dta.a1 = NULL,
-		# dta.a1 = copy(dat.a),
+		a = "50",
+		dta = copy(dat.reduced[!is.na(I), covariates.which, with = F]),
 		times = sort(unique(dat.reduced[status == 1]$I), decreasing = T),
-		mwf.name = "soluble",
-		quiet = F,
-		total_effect = F
+		quiet = F
 ) {
 
-	if (total_effect) {
-		dta[,`Other event` := max(`Other event`), studyno]
-	}
-
-	if ("immortal" %in% names(dta.a1)) {
-		dta.a1 <- dta.a1[,-c("immortal", "I", "I.which"), with = F]
-	}
-
-	if (a != 0) {
-		# nrow(dta.a1) == nrow(dta)
-		dta.a1 <- merge(
-			dta.a1[,c("studyno", "year", grep(
[…]

### 2023-04-08 run_g-formula.R

@@ -3,287 +3,130 @@
 # November 3, 2020
 
 library(here)
-source(here("g-formula.R"))
+library(boxr); box_auth()
 
 # # Shape data
 # source(here::here("shape-data.R"))
-
+# dat <- box_read(1179471733155)
+# dat <- dat[yin.gm >= 1965]
 dat.reduced <- box_read(928445783979)
+N <- length(unique(dat.reduced[!is.na(I)]$studyno))
+message(sum(dat.reduced[!is.na(I)]$status))
+source(here("g-formula.R"))
 
-# name          : dat.sol.reduced.rds
-dat.sol.reduced <- box_read(928445303042)
-# name          : dat.sol.reduced2.rds
-dat.sol.reduced2 <- box_read(929953044799)
-# name          : dat.sol.reduced10.rds
-dat.sol.reduced10 <- box_read(930687554963)
+followed.names <- c("followed_200", "followed_100", "followed_50",
+										"followed_25",  "followed_05",  "followed_025")
+covariates.which <- c(
+	followed.names,
+	"studyno", "I", "year", "immortal",
+	"status", "Censored", "Other event", "All causes",
+	"age.year2", "Age", "Age at hire",
+	"year2", "Year",
+	"straight", "soluble", "synthetic",
+	"Straight", "Soluble", "Synthetic",
+	"Cumulative straight", "Cumulative synthetic",
+	"Cumulative soluble", "Cumulative soluble shifted",
+	"Baseline cumulative soluble",
+	"Baseline cumulative straight",
+	"Baseline cumulative synthetic",
+	"cum_straight", "cum_soluble", "cum_synthetic",
+	"Employment status",
+	"Duration of employment", "employment.years",
+	"Cumulative time off", "cum_off",
+	"Year of hire", "yin.gm", "Sex", "Race", "Plant", 'py')
+
+dat.reduced[,`:=`(
+	`Baseline cumulative soluble` = `Cumulative soluble`[I == 1],
+	`Baseline cumulative straight` = `Cumulative straight`[I == 1],
+	`Baseline cumulative synthetic` = `Cumulative synthetic`[I == 1]
+), studyno]
 
 #####################################################
-# Post-intervention distribution of exposure     ####
+# Point estimates                                ####
[…]

### 2023-04-08 shape-data.R

@@ -8,12 +8,12 @@ library(survival)
 box_auth()
 
 # Get raw data and helper functions ####
-exposure.lag <- 10
+exposure.lag <- 20
 race.imputed.melt <- NULL
 source("~/headRs/00-my-theme.R")
 library(data.table)
 # # paste(ls(), collapse = ",\n") %>% clipr::write_clip()
-source(here::here("../gm-cancer-inc/breaks.R"))
+source(here::here("breaks.R"))
 
 # Get data ####
 source(here::here("get-data.R"))
@@ -71,12 +71,12 @@ cancer <- box_read('512727972584')
 setDT(cancer)
 
 nhl_morphology <- merge(dat[status == 1, .(studyno, yoi)],
-			unique(cancer[morph %in% c(
-				9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687:9691, 9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729, 9735, 9737:9738, 9811:9818, 9823, 9827, 9837,
-				9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687, 9688, 9689:9691, 9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729, 9735, 9737, 9738,
-				9811:9818, 9823, 9827, 9837
-			),.(studyno, yoi = ddiag, morph)]),
-			by = c("studyno", "yoi"))
+												unique(cancer[morph %in% c(
+													9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687:9691, 9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729, 9735, 9737:9738, 9811:9818, 9823, 9827, 9837,
+													9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687, 9688, 9689:9691, 9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729, 9735, 9737, 9738,
+													9811:9818, 9823, 9827, 9837
+												),.(studyno, yoi = ddiag, morph)]),
+												by = c("studyno", "yoi"))
 
 dat <- merge(
 	dat, nhl_morphology[,.(studyno, morph = as.integer(morph))],
@@ -104,7 +104,7 @@ dat[,`:=`(
 	Plant = which.max(table(Plant))
 ), by = .(studyno)]
 dat[,`:=`(
[…]

### 2023-05-25 reports/paper/paper.qmd
get ready for SER

@@
 ---
-
-\fancyhead[R]{}
-\fancyhead[L]{}
-\renewcommand{\headrulewidth}{0pt}
-\singlespacing
-
-\thispagestyle{empty}
-
-\setlength{\columnseprule}{0pt}
 
@@
 **Background:** Non-Hodgkin lymphoma (NHL) incidence has increased substantially in the US since 1960 and was recently linked to workplace exposure to soluble metalworking fluids (MWF) in a standard survival analysis of the United Auto Workers-General Motors (UAW-GM) cohort.
-To further explore this association, we investigate the causal effects of hypothetical limits on soluble MWF exposure in relation to NHL risk in the same cohort of autoworkers.
+To further explore this association, we estimate the effects of hypothetical limits on soluble MWF exposure in relation to NHL risk in the same cohort of autoworkers.
 
-**Methods:** We estimated counterfactual risk of NHL between 1985 and 2005 in the UAW-GM cohort of autoworkers at three Michigan plants (n = 34,734) under hypothetical limits on annual average daily exposure to soluble MWF.
+**Methods:** We estimated counterfactual risk of NHL between 1985 and 2015 in the UAW-GM cohort of autoworkers at three Michigan plants (n = 33,134) under hypothetical limits on annual average daily exposure to soluble MWF.
 We applied the hazard-extended ICE parametric g-formula, an estimator capable of adjusting for time-varying confounding affected by past exposure.
 
-**Results:** 231 NHL cases occurred over the 20-year follow-up period.
+**Results:** 339 NHL cases occurred over the 30-year follow-up period.
 Stronger hypothetical limits on soluble MWF exposure resulted in monotonic reductions in NHL risk.
-Capping annual average daily exposure at 0.5 mg/m^3^, the NIOSH recommended exposure limit, would have prevented 44 (95% CI: -6, 91) cases.
-Capping at 0.25 mg/m^3^ would have prevented 52 (95% CI: -5, 106) cases.
-Finally, capping at 0.05 mg/m^3^ would have prevented 71 (95% CI: 12, 129) cases.
+Capping annual average daily exposure at 2 mg/m^3^ would have prevented 98 (95% CI: 45, 161) cases of NHL.
+Capping at 0.5 mg/m^3^, the NIOSH recommended exposure limit, would have prevented 112 (95% CI: 57, 181) cases.
+Finally, capping at 0.05 mg/m^3^ would have prevented 129 (95% CI: 66, 214) cases.
 
@@
 Although MWF use is expected to decline as the automotive industry turns to electric vehicles, a boom in electric vehicle manufacturing could nonetheless lead to global increases in worker exposure to MWF.
-Strong limits on exposure to MWF may be important for preventing NHL incidence during a period of automotive industry expansion.
+Maintaining limits on exposure to MWF may protect workers against risk of NHL.
 
@@
 
-In recent years, there has been a surge in optimism for growth in American manufacturing [@Carr_2022;@Armbrust_2021].
+<!-- In recent years, there has been a surge in optimism for growth in American manufacturing [@Carr_2022;@Armbrust_2021].
 While it may be easy to imagine a factory floor crowded with workers and heavy machinery, an essential part of the industrial production of physical goods is easy to overlook: lubricants and coolants.
@@
 Parts may even be submerged in MWF in precision manufacturing applications [@Arrabiyeh_2020].
+-->
 
-Non-Hodgkin Lymphoma (NHL) is the seventh most common cancer type in the United States and has garnered substantial research attention because its incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons per year [@seer_1994;@Ekstrom-Smedby_2006].
+Non-Hodgkin Lymphoma (NHL) incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons per year, making it the seventh most common cancer in the country [@seer_1994;@Ekstrom-Smedby_2006].
 The strongest known risk factor of NHL is immunosuppression, both congenital and acquired [@Filipovich_1992;@Chiu_2015].
@@
 However, since immunodeficiency and infection with HIV are rare, they cannot fully explain the historic rise or present burden of NHL [@Shiels_2013].
-Since the rise in NHL incidence coincided with a period of rapid and extensive chemicalization in industry, agriculture and warfare, there has been stronger interest in the environmental and occupational epidemiology of NHL [@Nelson_2005;@Romero_2021].
+The rise in NHL incidence coincided with a period of rapid and extensive chemicalization in industry, agriculture and warfare, suggesting that environmental and occupational exposures may have an important explanatory role in the epidemiology of NHL [@Nelson_2005;@Romero_2021].
 
@@
 Metal processors, health workers, salespeople, machinists, and electricians have all been identified as occupational groups with higher risk of NHL [@Fritschi_2005a; @Mester_2006; @Ekstrom-Smedby_2006].
+Workers in these occupational groups often come into contact with industrial chemicals such as gasoline, solvents, coolants, and lubricants such as metalworking fluids.
 
-Metalworking fluids (MWF), an important class of occupational exposures, are complex mixtures of oils and chemicals used to lubricate and cool metal tools and parts during metal cutting and grinding operations in manufacturing processes.
-During use, MWFs aerosolize and present a potential health hazard to exposed workers.
+Metalworking fluids (MWF) are complex mixtures of oil, water, and chemical additives that optimize metal machining operations.
+During shaping, grinding, and cutting operations, MWF are misted, poured, or blasted at high pressure onto work surfaces to remove debris, cool metal, improve efficiency, and prevent deterioration of tools.
+Although MWFs provide essential engineering benefits to manufacturing processes, they may also present a potential health hazard to exposed workers, who may inhale or ingest aerosolized MWFs.
 There are three general types of MWF: straight, soluble, and synthetic.
-The type of MWF applied has changed over the decades and depends in part on the particular metalworking operation.
+The type of MWF applied has changed over the decades in response to engineering, economic, and health considerations.
+
 Straight MWF, the oldest class of MWF, is comprised mostly of mineral oils, which were classified as carcinogenic by the International Agency for Research on Cancer (IARC) in 1973, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973].
-The combination of health concerns, the high cost of oil in the 1970s, and the introduction of performance-enhancing water-soluble chemical additives led to the gradual replacement of straight MWF with water-based soluble and synthetic MWFs for many, but not all operations [@Childers_2005].
+In the same decade, additional factors including the high cost of oil and the introduction of performance-enhancing water-soluble chemical additives spurred the gradual replacement of straight MWF with water-based soluble and synthetic MWFs for many, but not all metalworking operations [@Childers_2005].
 Although water-based MWF contain little to no mineral oil, they contain a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987;@IARC_2014;@IARC_2017].
+With policy makers and companies anticipating a boom in domestic manufacturing, occupational exposure to MWFs will remain an important concern for worker health in the US [@Armbrust_2021;@Carr_2022;@Keilman_2023].
 
-In occupational studies, measures of time-varying exposure are essential to statistical adjustment for forms of time-varying confounding affected by past exposure such as the healthy worker survivor effect (HWSE).
+Here, we assess the effect of hypothetical MWF exposure limits on cumulative incidence of NHL from 1985 to 2014 in the United Auto Workers-General Motors (UAW-GM) occupational cohort study.
+A recent study of cancer incidence in this cohort linked NHL with exposure to soluble MWF in a Cox proportional hazards regression [@Colbeth_2023].
+Standard regression methods are vulnerable to downward bias due to the healthy worker survivor effect (HWSE), the process by which healthier individuals remain at work where they accumulate more occupational exposure.
+Therefore, we further explored this association using an estimator capable of adjusting for the HWSE and other sources of time-varying confounding and censoring affected by past exposure: the hazard-extended iterative conditional expectation (ICE) parametric g-formula [@Arrighi_1994;@Wen_2021].
+Like other causal estimators in statistics, the hazard-extended ICE g-formula yields marginal effect estimates of hypothetical interventions, which may be more interpretable under a population health framework than conditional measures.
+
+<!-- The healthy worker survivor effect (HWSE) is a key concern in occupational studies.
 The HWSE is the dynamic selection process by which healthier individuals remain at work, where they accumulate more occupational exposure, and less healthy individuals leave work [@Arrighi_1994].
 Standard analyses of occupational cohorts affected by the HWSE result in a downward bias on the exposure-outcome associations of interest, as less healthy workers typically accrue less exposure than healthier workers.
-
-Here, we assess the effect of hypothetical MWF exposure limits on cumulative incidence of NHL from 1985 to 2005 in the United Auto Workers-General Motors (UAW-GM) occupational cohort study.
-A recent study of cancer incidence in this cohort linked NHL with exposure to soluble MWF using a standard survival analysis using Cox proportional hazard regression [@Colbeth_2023].
-Standard regression methods are vulnerable to bias due to the HWSE.
-We therefore further explore this association using an estimator capable of adjusting for time-varying confounding and censoring affected by past exposure: the hazard-extended iterative conditional expectation (ICE) parametric g-formula.
-Like other causal estimators in statistics, the hazard-extended ICE g-formula yields marginal effect estimates of hypothetical interventions, which may be more interpretable under a population health framework than conditional measures.
+One analytic approach for addressing potential bias due to the HWSE and other time-varying confounders affected by past exposure is the application of longitudinal causal estimators such as the parametric g-formula [@Taubman_2009].
+-->
 
@@
 
-We estimated NHL cumulative incidence from 1985 to 2005 under hypothetical limits on annual average daily exposure to soluble MWF by applying the hazard-extended ICE parametric g-formula estimator [@Wen_2020].
+We estimated NHL cumulative incidence from 1985 to 2014 under hypothetical limits on annual average daily exposure to soluble MWF by applying the hazard-extended ICE parametric g-formula estimator [@Wen_2020].
 First, we estimated the expected number of NHL cases that we would observe if there were no censoring by competing risks.
-Then, we contrasted this counterfactual cumulative incidence to that under three hypothetical exposure limits:
+Then, we contrasted this counterfactual cumulative incidence to that under interventions enforcing one of five hypothetical exposure limits in addition to no censoring, when positivity allows.
+The five limits we evaluated were (1) 2.0 mg/m^3^, (2) 1.0 mg/m^3^, (3) 0.5 mg/m^3^, (4) 0.25 mg/m^3^, and
+(5) 0.05 mg/m^3^.
+The National Institute for Occupational Safety and Health (NIOSH) Recommended Exposure Limit (REL) for total particulate mass (PM) composed of MWFs is 0.5 mg/m^3^ [@niosh_1998].
+These interventions reduce exposures above the hypothetical limit, but allow exposures below the limit to vary according to their natural distribution.
+To prevent extrapolation, interventions considered reduce above-limit exposures to the highest limit-abiding exposure observed among other workers in the study population with the same confounder and exposure history at that time.
+If no such peers existed, the above-limit exposures among those workers would retain their natural distribution.
 
-(1) 0.5 mg/m^3^: the National Institute for Occupational Safety and Health (NIOSH) Recommended Exposure Limit (REL) for total particulate mass (PM) composed of MWFs [@niosh_1998]
-(2) 0.25 mg/m^3^: Half the REL
-(3) 0.05 mg/m^3^: One tenth of the REL.
-
-Exposure limits were enforced for soluble MWF over workers' entire working lifetimes, thereby inducing a post-intervention exposure distribution from which exposures are drawn.
+<!-- These interventions are known as threshold interventions that depend on the natural value of exposure.
+In general, threshold interventions set exposure to the hypothetical limit of interest when the natural value of exposure is beyond the threshold.
+Otherwise, these interventions leave exposure at the natural value.
+Such interventions are analogous to longitudinal stochastic interventions where the intervention distribution of exposure is the distribution of exposure induced by the threshold intervention rule [@Taubman_2009;@Young_2014;@Diaz_2021].
+-->
 
@@
 
-We used data from the UAW-GM cohort, which includes all hourly workers at three automobile manufacturing plants in Michigan who had worked at least three years by 1985.
+We used data from the UAW-GM cohort, which included all hourly workers at three automobile manufacturing plants in Michigan who had worked at least three years by 1985.
 Past papers provide detailed descriptions of the cohort [@Eisen_1992;@Eisen_2001].
 The large size of the study population and rich time-varying, quantitative MWF exposure data provide an opportunity to study a relatively rare cancer and evaluate realistic interventions on MWF exposure in a longitudinal cohort setting.
-The present study population (N = 34,738) was restricted to the autoworkers who were at work in 1941 or not yet hired, missing no more than half of their employment history, and still alive at the start of follow-up.
-Autoworkers in the study population were followed for NHL incidence from January 1, 1985 until NHL diagnosis, death, January 1, 2005 (10 years after the end of employment record availability), or age 108 years (the oldest observed age at death), whichever came earlier.
+The present study population (N = 33,134) was restricted to the autoworkers who were at work in 1941 or not yet hired, missing no more than half of their employment history, and still alive at the start of follow-up.
+Autoworkers in the study population were followed for NHL incidence from January 1, 1985 until NHL diagnosis, death, December 31, 2014 (20 years after the end of employment record availability), or the oldest observed age at death (108 years), whichever came earlier.
 
@@
 
-We identified incident cancers in the UAW-GM cohort that occurred between 1985 and 2005 by linkage to the Michigan Cancer Registry (MCR).
+We identified incident cancers in the UAW-GM cohort that occurred between 1985 and 2014 by linkage to the Michigan Cancer Registry (MCR).
 Workers at Plants 1 and 2, located in the greater Detroit metropolitan area, were also linked to the Detroit Regional Registry of the Surveillance, Epidemiology, and End Results (SEER) Program.
@@
 The exposure assessment is described in detail elsewhere [@Hallock_1994;@Woskie_1994;@Woskie_2003].
-Previous analyses of NHL applied exposure lags of 1 to 20 years to account for disease latency; we lagged cumulative MWF exposures by 10 years and therefore ended follow-up on January 1, 2005 [@Smith_2007;@Karipidis_2007;@Zhang_2019].
-In analyses, MWF exposure history was summarized as the cumulative sum of annual exposure intensities and coded as categorical variables with cut-points determined according the quantiles of cumulative exposure among cases.
+
+Previous analyses of NHL applied exposure lags of 1 to 20 years to account for disease latency; we lagged cumulative MWF exposures by 20 years and therefore ended follow-up on January 1, 2015 [@Smith_2007;@Karipidis_2007;@Zhang_2019].
+In analyses, MWF exposure at start of follow-up was summarized as the cumulative sum of annual exposure intensities.
+Exposure was coded as categorical variables with cut-points at zero and the quintiles of exposure among cases.
 In analyses, we estimated the effects of interventions on soluble MWF while treating exposure to straight and synthetic MWFs as potential confounders.
@@
 
-The hazard-extended ICE parametric g-formula may be thought of as a series of model-based standardization steps, which we implemented using logistic regression.
-We split the 20-year follow-up period into eight time periods; the first two periods spanned four years each, and the remaining six periods spanned two years each.
-The first two periods are longer in length to account for the smaller number of cases in those years.
-Post-intervention estimates of the discrete hazard of NHL given all exposures and covariates were combined iteratively from the end of follow-up to the start.
-In each iteration, predicted discrete hazards were standardized over post-intervention exposure and covariate histories before combining with discrete hazards from the previous iteration.
-This iterative process results in sequentially standardized estimates of NHL cumulative incidence over the entire follow-up period.
-Averaging over the baseline distribution of covariates yields the counterfactual cumulative incidence estimate of NHL if the intervention of interest were enforced for the entire study population.
+We split the 30-year follow-up period into ten time periods based on the deciles of the dates of diagnosis of NHL.
+The number of years per period range from two  to four years.
+The hazard-extended ICE parametric g-formula involves two stages.
+In the first, we estimate counterfactual discrete hazards over the person-periods.
+In the second, we pool those estimates to estimate counterfactual risk over the entire follow-up period.
+During pooling, we iteratively combine estimates of the counterfactual hazard starting with the last two periods, then the last three, then the last four, and so forth.
+In each iteration, we perform model-based standardization over exposure and covariate histories before combining the counterfactual discrete hazard with that pooled over subsequent periods.
+This iterative process results in a sequentially standardized estimate of NHL cumulative incidence over the entire follow-up period under the post-intervention distribution of exposure.
 
-Post-intervention exposure to soluble MWF and history of exposure to soluble MWF were summarized as cumulative exposure.
-We modeled discrete hazards by fitting a pooled logistic regression for NHL over at-risk person-periods given cumulative exposure to straight, soluble, and synthetic MWFs, employment status, cumulative time off, year of hire, sex (male/female), race (Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3).
-Cumulative exposure to MWFs, employment status, and cumulative time off were lagged 10 years.
-All continuous variables were represented as categorical variables with cut points determined by the tertiles of nonzero values among NHL cases.
+At the start of follow-up and in the first stage of estimation, we summarized history of exposure to soluble MWF as the cumulative sum of average daily exposure.
+In the first stage, we fitted a pooled logistic regression for NHL over at-risk person-periods given cumulative exposure to straight, soluble, and synthetic MWFs, employment status, cumulative time off, age, duration of employment, sex (male/female), race (Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3).
+Exposure to MWFs, employment status, time off, and duration of employment were lagged 20 years.
+All continuous variables were represented as categorical variables with cut points determined by the quantiles of nonzero values among NHL cases.
+In the second stage, we conducted model-based standardization using logistic regression on the entire set of exposure and covariate histories.
 An overview of the general steps of the estimation procedure are presented below.
+Note that we refer to discrete hazards simply as hazards.
 
-0.  For the hypothetical exposure limit of interest, compute the cumulative exposure
-		to soluble MWF that each worker would have accrued by the end of each follow-up
-		period since hire.
-1.  Fit a pooled logistic regression to the observed data for NHL on covariates and
-    cumulative exposure to soluble MWF over all at-risk person-periods, excluding 
-    those ending with a .
-2.  Replace the cumulative exposure vector in the observed data with the vector
-		of post-intervention cumulative exposure to soluble MWF. Using the model fitted
-		in the  previous step, compute estimates of the post-intervention discrete hazard
-		for each at-risk person-period including those that end with a censoring event.
-3.  Set $k = K - 1$ where $K = 8$ is the number of follow-up periods:
+1.  Fit a pooled logistic regression of NHL on covariates
+		and exposure over all at-risk person-periods.
+2.  Predict the hazard for each person-period for each possible level of exposure
+		using the model from step 1.
+3.  Within strata formed by unique combinations of covariates, obtain the
+    post-intervention distribution of exposure by applying the intervention rule
+    to the observed exposure distribution.
+4.  Within strata, estimate the counterfactual hazard for each 
+		person-period by taking a weighted sum of the predicted hazards from step 2.
+5.  Starting at the penultimate period of follow-up, estimate the pooled
+    counterfactual hazard:
 
-	a) Among those who were event-free and uncensored through the $k$^th^ period,
-		 fit a logistic regression on the predicted post-intervention discrete hazard
-		 for the period spanning the $(k + 1)$ through $K$^th^ periods given observed
-		 covariate and exposure history up through (and including) the $k$^th^ period.
-	b) Replace the vector of cumulative exposure to soluble MWF in the observed data
-		 with the post-intervention vector of cumulative exposure to soluble MWF. Using
-		 the model fitted in the previous step, obtain predicted values for all those
-		 who were at-risk in the $k$^th^ period.
-	c) Compute the predicted post-intervention discrete hazard for the period spanning
-		 the $k$ through $K$^th^ periods by multiplying the predicted values from the
-		 previous step by 1 minus the discrete hazard estimate used to fit the model
-		 in step 3.a and adding that same discrete hazard estimate to the product.
-	d) If $k > 1$, set $k = k - 1$ and return to step 3.a.
+    a)  Regress the counterfactual hazard pooled over all subsequent periods on
+        exposure and covariate history at the current period.
+    b)  Predict the pooled hazard for each person at risk at the start of the
+    		period and each possible level of exposure using the model from (a).
+    		Retrieve the predicted hazards from step 2. For each person and level
+    		of exposure, multiply the predicted pooled hazard by one minus the 
+    		corresponding predicted hazard and add the predicted hazard to the
+    		product.
+    c)  Within strata formed by exposure and covariate history, obtain the
+        post-intervention distribution of exposure by applying the 
+        intervention rule to the observed exposure distribution.
+    d)  Within strata, estimate the counterfactual hazard pooled over the present
+    		and subsequent periods for each person by taking a weighted sum of the
+    		predicted pooled hazards from (b).
+    e)  If the present period is not first period, set the reference period to the
+    		preceding period and return to (a).
 
-4.  Compute the counterfactual risk by averaging the predicted post-intervention
-		discrete hazards for the entire follow-up period for all units.
+6.  Compute the counterfactual risk by averaging the counterfactual hazard over
+		the entire follow-up period across all persons.
+
+To account for censoring, fit the models in step 1 and step 5a among those who were
+not censored and obtain predicted hazards for all at-risk person-periods, including
+those that were censored.
 
 We estimated cumulative incidence under the observed distribution of soluble MWF exposure (natural course) and under the six interventions.
-We contrasted the cumulative incidence under intervention to that under the natural course by computing relative cumulative incidences.
-Confidence intervals were computed using the nonparametric bootstrap with 1000 Monte Carlo samples from the population at cumulative incidence at start of follow-up and centering on the estimate computed from observed data.
+We contrasted the cumulative incidence under intervention to that under the natural course by computing the number of cases averted and the cumulative incidence ratios.
+Confidence intervals were computed using the basic nonparametric bootstrap with 1000 Monte Carlo samples from the population at the start of follow-up.
 All the necessary script used to reproduce the analyses are available on [GitHub](https://github.com/kvntchn/gm-nhl-ice).
@@
 load(here::here("resources", paste0("estimates.rdata")))
-sapply(estimates, mean) 
 estimates.bs <- readRDS(here::here("resources", paste0("estimates.bs.rds")))
@@
 rd <- rd[,.(
-	rd = estimate[1],
-	rd_lower = (2 * estimate[1] - quantile(value, 1 - 0.025)) * N,
-	rd_upper = (2 * estimate[1] - quantile(value, 0.025)) * N
+  rd = - estimate[1],
+  rd_lower = - (2 * estimate[1] - quantile(value, 0.025)) * N,
+  rd_upper = - (2 * estimate[1] - quantile(value, 1 - 0.025)) * N
   # wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
@@
 
-# saveRDS(sol.tab, here::here('resources', 'sol.tab.rds'))
+# save(sol.tab, mwf.flextable, file = here::here('resources', 'sol.tab.rdata'))
 

### 2023-05-25 g-formula.R

@@ -25,9 +25,10 @@ ice_gcomp <- function(
 		quiet = F
 ) {
 
+	# Indicator for natural course (everone followed)
 	dta$followed_Any <- 1
-	dta$employment.years <- round(dta$employment.years)
 
+	# Index follow-up periods
 	setorder(dta, studyno, year)
 	dta[, I := 1:.N, by = studyno]
 
@@ -38,6 +39,7 @@ ice_gcomp <- function(
 		NULL
 	)
 
+	# Static covariates for discrete hazard and cumulative hazard
 	static_covariates.which <- c(
 		# "Employment status",
 		"Cumulative straight",
@@ -50,23 +52,10 @@ ice_gcomp <- function(
 		NULL
 	)
 
-	discrete.formula <- as.formula(paste(
-		"status",
-		"~",
-		"`Employment status` +",
-		"`Cumulative soluble` +",
-		"`Cumulative straight` +",
-		"`Cumulative synthetic` +",
-		"`Cumulative time off` +",
-		"Age +",
-		"`Duration of employment` +",
-		"Race +",
-		"Plant +",
-		"Sex",
-		NULL
-	))
-
+	# Intervention node name
 	intervene.which <- "Cumulative soluble"
+
+	# History to condition on for intervention
 	dynamic.which <- c(
 		"Employment status",
 		"Cumulative straight",
@@ -84,6 +73,24 @@ ice_gcomp <- function(
 	# Total number of outcomes
 	J <- max(times)
 	require(fastglm, quietly = T)
+
+	# Formula for discrete hazard regression
+	discrete.formula <- as.formula(paste(
+		"status",
+		"~",
+		"`Employment status` +",
+		"`Cumulative soluble` +",
+		"`Cumulative straight` +",
+		"`Cumulative synthetic` +",
+		"`Cumulative time off` +",
+		"Age +",
+		"`Duration of employment` +",
+		"Race +",
+		"Plant +",
+		"Sex",
+		NULL
+	))
+
 	h <- fastglm(
 		model.matrix(discrete.formula, data = dta)[with(dta, immortal == 0 & Censored == 0),],
 		dta[immortal == 0 & Censored == 0]$status,
@@ -100,22 +107,56 @@ ice_gcomp <- function(
 			newdata = model.matrix(discrete.formula, data = dta)[with(dta, immortal == 0),],
 			type = "response"))]
 
+	# dta[dta[,.(always_followed = as.numeric(all(get(paste0("followed_", a)) == 1))),
[…]

### 2023-05-25 run_g-formula.R

@@ -13,6 +13,7 @@ dat.reduced <- box_read(928445783979)
 N <- length(unique(dat.reduced[!is.na(I)]$studyno))
 message(sum(dat.reduced[!is.na(I)]$status))
 source(here("g-formula.R"))
+dat.reduced[,.(year1 = min(year), year2 = max(year)), I]
 
 followed.names <- c("followed_200", "followed_100", "followed_50",
 										"followed_25",  "followed_05",  "followed_025")

### 2023-06-12 reports/SER (2023)/nhl-ice-poster.tex
SER postr

% !TeX program = lualatex
%----------------------------------------------------------------------------------------
%  PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[20pt,final]{beamer}

\usepackage[scale=1]{beamerposter} % Use the beamerposter package for laying out the poster
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{titlelike}         {bg=yaleblue,fg=white}
\setbeamercolor{frametitle}        {bg=yaleblue!10,fg=yaleblue}
\setbeamercolor{block title}{fg=yaleblue,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
% \setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
% \setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
\setbeamercolor{block alerted title}{fg=white,bg=calyellow}
\setbeamercolor{block alerted body}{fg=black,bg=white}

\setbeamercolor{enumerate item}{fg=dblue!70}
\setbeamercolor{itemize item}{fg=dblue!70}
\setbeamercolor{itemize subitem}{fg=dblue!70}

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{42in} % A0 width: 46.8in
\setlength{\paperheight}{33.5in} % A0 height: 33.1in
\setlength{\sepwid}{0.02\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.3\paperwidth} % Width of one column
\setlength{\twocolwid}{2\onecolwid} % Width of two columns
\addtolength{\twocolwid}{\sepwid}
\setlength{\threecolwid}{3\onecolwid} % Width of three columns
\addtolength{\threecolwid}{2\sepwid}
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
\setlength\labelsep{\dimexpr\labelsep + 0.5em\relax}
\setlength{\parskip}{1em}
\setlength\columnsep{\sepwid}

\setbeamertemplate{itemize/enumerate body begin}{\normalsize}
\setbeamertemplate{itemize/enumerate subbody begin}{\normalsize}
\setbeamertemplate{itemize/enumerate subsubbody begin}{\normalsize}

% declare `cmex` to be arbitrary scalable
\DeclareFontShape{OMX}{cmex}{m}{n}{
  <-7.5> cmex7
  <7.5-8.5> cmex8
  <8.5-9.5> cmex9
  <9.5-> cmex10
}{}

\SetSymbolFont{largesymbols}{normal}{OMX}{cmex}{m}{n}
\SetSymbolFont{largesymbols}{bold}  {OMX}{cmex}{m}{n}

%-----------------------------------------------------------
% \renewcommand{\figurename}{Fig.}

\usepackage{multicol}
\setbeamerfont{caption}{size=\normalsize}
\usepackage{caption}
\captionsetup{labelformat=simple, labelsep=colon}

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables

\usepackage{bbm} % more BB
\input{\string~/HeadRs/common_supplement.tex}

\usepackage[sorting=none]{biblatex}
\renewcommand*{\bibfont}{\footnotesize}
\addbibresource{ser_poster.bib}

% ---------------------------------------------------------------------------
\setbeamertemplate{headline}{
 \leavevmode
  \begin{columns}
   \begin{column}{\linewidth} % line
    \vskip1cm
    \centering
    \usebeamercolor{title in headline}{\color{jblue}
        \Huge % CHANGE this line for the size of the title
        {\textbf{\inserttitle}}\\[0.5ex]}
    \usebeamercolor{author in headline}{\color{fg}
        \Large % CHANGE this line for the size of the author
        {\insertauthor}\\[1ex]}
    \usebeamercolor{institute in headline}{\color{fg}
        \large % CHANGE this line for the size of the institut
        {\insertinstitute}\\[1ex]}
    \vskip1cm
   \end{column}
   \vspace{1cm}
  \end{columns}
 \vspace{0.5in} % CHANGE this line for the space between your title and the horizontal rule
 \begin{beamercolorbox}[wd=47in,colsep=0.1cm]{cboxb}\end{beamercolorbox}
 \vspace{0.1in} % CHANGE this line for the space between your horizontal rule and your main body
}

%----------------------------------------------------------------------------------------
%  TITLE SECTION
%----------------------------------------------------------------------------------------
\title{\huge Risk of non-Hodgkin lymphoma under hypothetical interventions with guaranteed positivity} % Poster title
\author{Kevin T. Chen\textsuperscript{\small 1}, Sally Picciotto\textsuperscript{\small 2}, Ellen A. Eisen\textsuperscript{\small 2}} % Author(s)
\institute{University of California, Berkeley -- School of Public Health} % Institution(s)
%----------------------------------------------------------------------------------------

\begin{document}

% add logo
\addtobeamertemplate{headline}{}
{\begin{tikzpicture}[remember picture, overlay]
    \node [anchor=north west, inner sep=1.5cm]  at (current page.north west)
    {\includegraphics[height=9cm]{ucberkeleyseal_139_540.eps}};
  \end{tikzpicture}}
\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

  \vspace{0.01\paperheight}

  \begin{columns}[t,totalwidth=\onecolwid]

    \begin{column}{\sepwid}\end{column} % Empty spacer column

    \begin{column}{\onecolwid} % The first column
      \vbox to 0.78\paperheight{

        %----------------------------------------------------------------------------------------
        %  OBJECTIVES
        %----------------------------------------------------------------------------------------

        \begin{block}{Backgound}

          \begin{itemize}
            \item \textbf{Non-Hodgkin Lymphoma} (NHL) incidence was associated with
                  exposure to
                  \textbf{soluble metalworking fluid} (MWF) in a
                  Cox analysis of the
                  \textbf{United Auto Workers-General Motors} (UAW-GM) \textbf{cohort}
                  \nocite{Colbeth_2022}
            \item Unlike traditional regression analysis, \emph{causal inference} methods
                  \begin{itemize}
                    \item Can adjust for time-varying confounding affected by past exposure \nocite{Arrighi_1994}
                    \item Estimate population effects of hypothetical interventions
                  \end{itemize}
            \item Causal inference in statistics requires \textbf{positivity}, which is
                  \textbf{not always assessed or addressed} \nocite{Petersen_2012}
            \item Here, we specified \textbf{\emph{supportable} interventions} on soluble MWF exposure
                  in the UAW-GM cohort that \textbf{guarantee positivity}
            \item We estimated the effect of supportable interventions on
                  NHL risk in the UAW-GM cohort (1985-2015) using the
                  \textbf{hazard-extended iterative conditional expectation (ICE) parametric g-formula}
                  \nocite{Wen_2020,Young_2014}
            \item Unlike the classic parametric g-formula, ICE g-formula estimators do not require
                  parametric specification of the full joint distribution of the confounders,
                  exposure, and outcome
          \end{itemize}

        \end{block}

        \begin{block}{Target and supportable exposure limits}

          \begin{itemize}
            \item Suppose we want to know the effect of capping exposures at a \textbf{target exposure limit},
                  but estimation may not be supported by observed data
            \item Instead, we define \textbf{supportable exposure limits}
                  for every time $k$ and unique combination of confounder and exposure histories
                  $(\bar l_{k}, \bar a_{k - 1})$
                  \begin{itemize}
                    \item Limit at greatest observed exposure $\le$ \textbf{target limit}, if exists
                    \item No limit, if all observed exposures $>$ \textbf{target limit}
                  \end{itemize}
            \item Propensity scores for exposure at the supportable exposure limits
                  are guaranteed to be \textbf{strictly positive}
                  % \item Supportable exposure limits may be equal to, less than, or greater than the target exposure limits
            \item \textbf{Supportable intervention rule} for every
                  $(\bar l_{k}, \bar a_{k - 1})$, reduces exposures $a_k$ above the
                  \textbf{supportable exposure limit} to that limit, but allows exposures
                  below to vary naturally (Figures 1 and 2)
            \item Applying the supportable intervention rule to the observed data
                  induces the intervention distribution, which defines the
                  \textbf{stochastic dynamic intervention} with \textbf{guaranteed positvity}
          \end{itemize}

          \vspace{0.1\baselineskip}
          \begin{figure}
            \caption{Marginal distribution of nonzero exposure at $k = 2$
              before and after applying the supportable intervention rule}
            \begin{tikzpicture}[x=2.5pt,y=2.5pt]
              \input{resources/intervention-density.tex}
            \end{tikzpicture}
          \end{figure}

        \end{block}

      }\end{column} % End of the first column

    \begin{column}{\sepwid}\end{column} % Empty spacer column

    \begin{column}{\onecolwid} % Begin a column which is two columns wide (column 2)
      \vbox to 0.78\paperheight{

        \vspace{-0.5\baselineskip}
        \begin{figure}
          \caption{Distribution of nonzero exposure for three distinct confounder and
          exposure histories at $k = 2$ before and after applying the supportable intervention rule}
          \begin{tikzpicture}[x=2.5pt,y=2.5pt]
            \input{resources/intervention-density-witnin-combos.tex}
          \end{tikzpicture}
        \end{figure}

        \vspace{0.25\baselineskip}
        \begin{table}
          \caption{Demographic characteristics of the full cohort and the NHL cases}
          \small
          \begin{tabular}{p{0.3\linewidth}rlcrl}
            \toprule
                                & \multicolumn{2}{c}{Study population\phantom{0000}} &
                                & \multicolumn{2}{c}{NHL cases\phantom{00000}}                                                 \\
            \midrule
            $N$ (person-years)  & 33,134                                             & (794,733)     &  & 339  & (5,809)       \\
            Race                                                                                                               \\
            \hspace{1em}White   & 21,315                                             & (64\%)        &  & 250  & (74\%)        \\
            \hspace{1em}Black   & 6,250                                              & (19\%)        &  & 40   & (12\%)        \\
            \hspace{1em}Unknown & 5,569                                              & (17\%)        &  & 49   & (14\%)        \\
            Sex                                                                                                                \\
            \hspace{1em}Male    & 30,249                                             & (87\%)        &  & 206  & (89\%)        \\
            \hspace{1em}Female  & 4,499                                              & (13\%)        &  & 25   & (11\%)        \\
            % Plant                                                                                                                 \\
            % \hspace{1em}Plant 1    & 7,273                                              & (22\%)        &  & 70   & (21\%)        \\
            % \hspace{1em}Plant 2    & 14,251                                             & (43\%)        &  & 137  & (40\%)        \\
            % \hspace{1em}Plant 3    & 11,610                                             & (35\%)        &  & 132  & (39\%)        \\
            % Ever exposed to MWFs \\
            % \hspace{1em}Soluble & 29,010  & (88\%)    & 299  & (88\%) \\
            % \hspace{1em}Straight & 18,710  & (56\%)    & 197  & (58\%) \\
            % \hspace{1em}Synthetic & 11,824  & (36\%)  & 111  & (33\%) \\
            % Deceased by 2015         & 14,434 & (44\%)        &   & 53   & (16\%)            \\
            % % \hline
            % % Years of follow-up & 20 & (16.46, 20) &  & 13 & (6.83, 17) \\
            % Year of birth            & 1941   & (1927, 1950)  &   & 1935 & (1926, 1945)      \\
            % Year of hire             & 1967   & (1953, 1976)  &   & 1964 & (1953, 1971)      \\
            % Age at hire              & 23.6   & (20.0, 30.3)  &   & 25.3 & (20.2, 32.9)      \\
            % Year of leaving work$^*$ & 1981   & (1970, 1989)  &   & 1981 & (1971, 1989)      \\
            % Age at leaving work$^*$  & 45.2   & (31.8, 57.3)  &   & 53.0 & (36.4, 60.4)      \\
            Years at work       & 15.2                                               & (7.0, 26.6)   &  & 21.0 & (7.8, 29.9)   \\
            % Age at death$^\sharp$    & 73.4   & (64.4, 81.3)  &   & 73.0 & (66.3, 80.8)      \\
            Cumulative exposure$^\flat$
                                & 4.33                                               & (1.71, 10.69) &  & 5.43 & (2.19, 14.33) \\
            \bottomrule
            \multicolumn{6}{l}{\small Statistics shown are count (percent) or median (first and third quartiles).}             \\
            % \multicolumn{6}{l}{\small $^\sharp$ Among those who left work by 1995, when employment records ended.}                \\
            \multicolumn{6}{l}{\small $^\flat$ Among those who were ever-exposed; units in mg/m$^3\,\cdot\,$year.}             \\
            % \multicolumn{6}{l}{\small Abbreviations: NHL: non-Hodgkin lymphoma.}                                                  \\
            \bottomrule
          \end{tabular}
        \end{table}

        \vspace{1.5\baselineskip}
        \begin{block}{\normalsize Affiliations and acknowledgements \vspace*{0.2\baselineskip}}
          \vspace{-0.7\baselineskip}\small
          \begin{center}{
              \textsuperscript{1} Division of Epidemiology \& Biostatistics}
            \hspace{2em}
            \textsuperscript{2} Division of Environmental Health Sciences\\[6pt]
            Funding: CDC, NIOSH (R01OH011092) and NIOSH Training Grant (T42OH008429)
          \end{center}
        \end{block}

      }\end{column} % End of column 2

    \begin{column}{\sepwid}\end{column}

    \begin{column}{\onecolwid} % Begin a column which is two columns wide (column 2)
      \vbox to 0.78\paperheight{

        \begin{alertblock}{Main results}
          \vspace{-0.6\baselineskip}
          \begin{figure}
            \caption{Counterfactual number of cases averted under supportable intervention rules
              based on five different target exposure limits and no censoring,
              with 95\% bootstrap confidence intervals.}
            \begin{tikzpicture}[x=2.5pt,y=2.5pt]
              \input{resources/rd.tex}
            \end{tikzpicture}
          \end{figure}

          \begin{itemize}
            \item There would have been \textbf{502 NHL cases} if there was no censoring
            \item Stronger target exposure limits \textbf{monotonically reduced} NHL risk
            \item Setting the target exposure limit at the
                  \textbf{NIOSH recommended exposure limit}
                  0.5 mg/m\textsuperscript{3}
                  for total particulate mass derived from MWF
                  \textbf{would have averted 112 (95\% CI: 57, 181) NHL cases}
          \end{itemize}
        \end{alertblock}

        \begin{block}{Conclusions and discussion}
          \begin{itemize}
            \item \textbf{Stronger limits on exposure to soluble MWF provide stronger protections against NHL}
                  % \item Causal inference relies on assumptions\vspace*{-0.2\baselineskip}
                  %       \begin{multicols}{2}\begin{itemize}
                  %           \item Exchangeability
                  %           \item Positivity
                  %           \item Consistency
                  %           \item Correct model specification
                  %         \end{itemize}\end{multicols}
            \item During the anticipated rebound in domestic manufacturing,
                  protecting worker health should be a priority
            \item We evaluated supportable interventions with \textbf{guaranteed positivity} and therefore
                  \textbf{avoid extrapolation}
            \item We expect uniformly-enforced target exposure limits to have even
                  \textbf{stronger protective effects}
            \item The \textbf{classic parametric g-formula} estimator can also estimate
                  effects of supportable intervention rules, but
                  \textbf{requires many more parametric assumptions}
                  than ICE g-formula estimators \nocite{Taubman_2009}
          \end{itemize}
        \end{block}

        \vspace{3\baselineskip}

        \begin{block}{\normalsize References \vspace*{0.2\baselineskip}}
          \printbibliography
        \end{block}
        %     }\end{column} % End of column 2
        % \begin{column}{\sepwid}\end{column}
        % \begin{column}{\onecolwid}\vbox to 0.78\paperheight{%

        % \begin{block}{Overview of analysis steps}
        %   \begin{enumerate}\itemsep=6pt
        %     \item Fit a model for $h_{k, k - 1} = \mathbb E\left[Y_k \mid \bar l_{k - 1},
        %     \bar a_{k - 1}, Y_{k - 1} = C_k = 0\right]$.
        %     \item Predict $h^\text{int}_{k, k - 1}(a_{k - 1})$ for all possible $a_{k -1}$
        %     using the model from \mynum{1}.
        %     \item Estimate the counterfactual hazard $h^\text{int}_{K, K - 1}$
        %     $$\hat h^\text{int}_{K, K - 1} = \sum_{a_{K - 1}}
        %     \hat h^\text{int}_{k, k - 1}(a_{k - 1})
        %     \times f^\text{int}(a_{k - 1} \mid \bar l_{k - 1}, \bar a_{k - 2},
        %     Y_{k - 1} = C_{k - 1} = 0)$$
        %     \item Set $k = K - 2$. Iteratively:
        %           \vspace{2pt}\begin{enumerate}\itemsep=8pt
        %             \item Regress $\hat h^\text{int}_{K, k + 1}$ on $\bar L_k$
        %             and $\bar A_k$ among those with $Y_{k + 1} = C_{k + 1} = 0$.
        %             \item Predict $h^\text{int}_{K, k + 1} (a_k)$ for all possible $a_{k}$
        %             using the model from \mynum{a}.
        %             \item Estimate the counterfactual hazard for interval $[k, K]$
        %             \begin{align*}
        %               \hat h^\text{int}_{K, k} = \sum_{a_k}
        %               & \left(
        %                 \hat h^\text{int}_{K, k + 1} (a_k)
        %                 \times (1 - \hat h^\text{int}_{k + 1, k} (a_k)) +
        %                 \hat h^\text{int}_{k + 1, k} (a_k)
        %               \right) \\
        %               & \hspace{2em} \times f^\text{int}(a_{k} \mid
        %               \bar l_{k}, \bar a_{k - 1}, Y_{k} = C_{k} = 0)
        %             \end{align*}
        %             \item If $k > 1$, set $k \leftarrow k - 1$ and return to \mynum{a}.
        %           \end{enumerate}\vspace{2pt}
        %     \item Estimate $\mathbb E\left[ Y_K^\text{int} \right]$ using
        %     $n^{-1}\sum_i^n \hat h^\text{int}_{K, 0}$.
        %   \end{enumerate}

        % \end{block}

      }\end{column} % End of column 3

    \begin{column}{\sepwid}\end{column}

  \end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2023-06-12 reports/SER (2023)/resources/intervention-density-combined.tex
SER postr

% Created by tikzDevice version 0.12.3.1 on 2023-06-05 10:01:50
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (903.38,180.67);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (903.38,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 33.90, 45.85) rectangle (245.64,164.10);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 33.90, 45.85) rectangle (245.64,164.10);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 43.52, 51.22) rectangle ( 50.92, 54.00);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 50.92, 51.22) rectangle ( 58.33, 54.83);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 58.33, 51.22) rectangle ( 65.73, 58.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 65.73, 51.22) rectangle ( 73.14, 54.23);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 73.14, 51.22) rectangle ( 80.54, 55.10);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 80.54, 51.22) rectangle ( 87.94, 54.07);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 87.94, 51.22) rectangle ( 95.35, 54.09);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 95.35, 51.22) rectangle (102.75, 63.00);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (102.75, 51.22) rectangle (110.15, 58.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (110.15, 51.22) rectangle (117.56, 54.04);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.56, 51.22) rectangle (124.96, 55.71);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (124.96, 51.22) rectangle (132.36, 56.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (132.36, 51.22) rectangle (139.77, 54.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (139.77, 51.22) rectangle (147.17, 53.46);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (147.17, 51.22) rectangle (154.58, 59.90);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (154.58, 51.22) rectangle (161.98, 55.03);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (161.98, 51.22) rectangle (169.38, 53.02);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (169.38, 51.22) rectangle (176.79, 55.55);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (176.79, 51.22) rectangle (184.19, 55.39);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (184.19, 51.22) rectangle (191.59, 55.55);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (191.59, 51.22) rectangle (199.00, 53.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (199.00, 51.22) rectangle (206.40, 52.56);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (206.40, 51.22) rectangle (213.80, 54.54);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (213.80, 51.22) rectangle (221.21, 52.94);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (221.21, 51.22) rectangle (228.61, 60.40);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (228.61, 51.22) rectangle (236.02, 51.93);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 43.52, 51.22) rectangle ( 50.92, 63.05);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 50.92, 51.22) rectangle ( 58.33, 54.57);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 58.33, 51.22) rectangle ( 65.73, 59.70);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 65.73, 51.22) rectangle ( 73.14, 54.88);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 73.14, 51.22) rectangle ( 80.54, 55.88);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 80.54, 51.22) rectangle ( 87.94, 54.55);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 87.94, 51.22) rectangle ( 95.35, 55.13);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 95.35, 51.22) rectangle (102.75, 67.26);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (102.75, 51.22) rectangle (110.15, 69.47);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (110.15, 51.22) rectangle (117.56, 66.25);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.56, 51.22) rectangle (124.96, 52.97);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (124.96, 51.22) rectangle (132.36, 52.74);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (132.36, 51.22) rectangle (139.77, 52.09);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (139.77, 51.22) rectangle (147.17, 51.69);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (147.17, 51.22) rectangle (154.58, 54.31);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (154.58, 51.22) rectangle (161.98, 52.07);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (161.98, 51.22) rectangle (169.38, 51.69);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (169.38, 51.22) rectangle (176.79, 52.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (176.79, 51.22) rectangle (184.19, 52.14);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (184.19, 51.22) rectangle (191.59, 52.85);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (191.59, 51.22) rectangle (199.00, 51.97);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (199.00, 51.22) rectangle (206.40, 51.66);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (206.40, 51.22) rectangle (213.80, 52.15);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (213.80, 51.22) rectangle (221.21, 51.69);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (221.21, 51.22) rectangle (228.61, 54.97);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (228.61, 51.22) rectangle (236.02, 51.37);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.56, 45.85) -- (117.56,164.10);

\path[draw=drawColor,line width= 0.9pt,line join=round,line cap=round] ( 33.90, 45.85) rectangle (245.64,164.10);
\end{scope}
\begin{scope}
\path[clip] (251.14, 45.85) rectangle (462.89,164.10);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.14, 45.85) rectangle (462.89,164.10);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (260.77, 51.22) rectangle (268.17, 87.06);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (268.17, 51.22) rectangle (275.57, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (275.57, 51.22) rectangle (282.98, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (282.98, 51.22) rectangle (290.38, 63.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (290.38, 51.22) rectangle (297.78, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (297.78, 51.22) rectangle (305.19, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (305.19, 51.22) rectangle (312.59, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (312.59, 51.22) rectangle (319.99, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (319.99, 51.22) rectangle (327.40, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (327.40, 51.22) rectangle (334.80, 63.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (334.80, 51.22) rectangle (342.21, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (342.21, 51.22) rectangle (349.61, 63.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (349.61, 51.22) rectangle (357.01, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (357.01, 51.22) rectangle (364.42, 63.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (364.42, 51.22) rectangle (371.82, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (371.82, 51.22) rectangle (379.22, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (379.22, 51.22) rectangle (386.63, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (386.63, 51.22) rectangle (394.03, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (394.03, 51.22) rectangle (401.43, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (401.43, 51.22) rectangle (408.84, 63.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (408.84, 51.22) rectangle (416.24, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (416.24, 51.22) rectangle (423.65, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (423.65, 51.22) rectangle (431.05, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (431.05, 51.22) rectangle (438.45, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (438.45, 51.22) rectangle (445.86, 63.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (445.86, 51.22) rectangle (453.26, 51.22);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (260.77, 51.22) rectangle (268.17, 87.06);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (268.17, 51.22) rectangle (275.57, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (275.57, 51.22) rectangle (282.98, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (282.98, 51.22) rectangle (290.38, 63.17);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (290.38, 51.22) rectangle (297.78, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (297.78, 51.22) rectangle (305.19, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (305.19, 51.22) rectangle (312.59, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (312.59, 51.22) rectangle (319.99, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (319.99, 51.22) rectangle (327.40, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (327.40, 51.22) rectangle (334.80,110.95);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (334.80, 51.22) rectangle (342.21, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (342.21, 51.22) rectangle (349.61, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (349.61, 51.22) rectangle (357.01, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (357.01, 51.22) rectangle (364.42, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (364.42, 51.22) rectangle (371.82, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (371.82, 51.22) rectangle (379.22, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (379.22, 51.22) rectangle (386.63, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (386.63, 51.22) rectangle (394.03, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (394.03, 51.22) rectangle (401.43, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (401.43, 51.22) rectangle (408.84, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (408.84, 51.22) rectangle (416.24, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (416.24, 51.22) rectangle (423.65, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (423.65, 51.22) rectangle (431.05, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (431.05, 51.22) rectangle (438.45, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (438.45, 51.22) rectangle (445.86, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (445.86, 51.22) rectangle (453.26, 51.22);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (334.80, 45.85) -- (334.80,164.10);

\path[draw=drawColor,line width= 0.9pt,line join=round,line cap=round] (251.14, 45.85) rectangle (462.89,164.10);
\end{scope}
\begin{scope}
\path[clip] (468.39, 45.85) rectangle (680.13,164.10);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (468.39, 45.85) rectangle (680.13,164.10);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (478.01, 51.22) rectangle (485.41, 78.10);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (485.41, 51.22) rectangle (492.82, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (492.82, 51.22) rectangle (500.22, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (500.22, 51.22) rectangle (507.62, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (507.62, 51.22) rectangle (515.03, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (515.03, 51.22) rectangle (522.43, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (522.43, 51.22) rectangle (529.84, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (529.84, 51.22) rectangle (537.24, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (537.24, 51.22) rectangle (544.64, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (544.64, 51.22) rectangle (552.05, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (552.05, 51.22) rectangle (559.45,104.97);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (559.45, 51.22) rectangle (566.85, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (566.85, 51.22) rectangle (574.26, 78.10);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (574.26, 51.22) rectangle (581.66, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (581.66, 51.22) rectangle (589.07, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (589.07, 51.22) rectangle (596.47, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (596.47, 51.22) rectangle (603.87, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (603.87, 51.22) rectangle (611.28, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (611.28, 51.22) rectangle (618.68, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (618.68, 51.22) rectangle (626.08, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (626.08, 51.22) rectangle (633.49, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (633.49, 51.22) rectangle (640.89, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (640.89, 51.22) rectangle (648.29, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (648.29, 51.22) rectangle (655.70, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (655.70, 51.22) rectangle (663.10, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (663.10, 51.22) rectangle (670.51, 51.22);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (478.01, 51.22) rectangle (485.41,158.73);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (485.41, 51.22) rectangle (492.82, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (492.82, 51.22) rectangle (500.22, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (500.22, 51.22) rectangle (507.62, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (507.62, 51.22) rectangle (515.03, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (515.03, 51.22) rectangle (522.43, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (522.43, 51.22) rectangle (529.84, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (529.84, 51.22) rectangle (537.24, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (537.24, 51.22) rectangle (544.64, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (544.64, 51.22) rectangle (552.05, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (552.05, 51.22) rectangle (559.45, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (559.45, 51.22) rectangle (566.85, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (566.85, 51.22) rectangle (574.26, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (574.26, 51.22) rectangle (581.66, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (581.66, 51.22) rectangle (589.07, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (589.07, 51.22) rectangle (596.47, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (596.47, 51.22) rectangle (603.87, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (603.87, 51.22) rectangle (611.28, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (611.28, 51.22) rectangle (618.68, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (618.68, 51.22) rectangle (626.08, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (626.08, 51.22) rectangle (633.49, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (633.49, 51.22) rectangle (640.89, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (640.89, 51.22) rectangle (648.29, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (648.29, 51.22) rectangle (655.70, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (655.70, 51.22) rectangle (663.10, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (663.10, 51.22) rectangle (670.51, 51.22);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (552.05, 45.85) -- (552.05,164.10);

\path[draw=drawColor,line width= 0.9pt,line join=round,line cap=round] (468.39, 45.85) rectangle (680.13,164.10);
\end{scope}
\begin{scope}
\path[clip] (685.63, 45.85) rectangle (897.38,164.10);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (685.63, 45.85) rectangle (897.38,164.10);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (695.25, 51.22) rectangle (702.66, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (702.66, 51.22) rectangle (710.06, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (710.06, 51.22) rectangle (717.47, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (717.47, 51.22) rectangle (724.87, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (724.87, 51.22) rectangle (732.27, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (732.27, 51.22) rectangle (739.68, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (739.68, 51.22) rectangle (747.08, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (747.08, 51.22) rectangle (754.48, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (754.48, 51.22) rectangle (761.89, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (761.89, 51.22) rectangle (769.29, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (769.29, 51.22) rectangle (776.70, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (776.70, 51.22) rectangle (784.10, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (784.10, 51.22) rectangle (791.50, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (791.50, 51.22) rectangle (798.91, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (798.91, 51.22) rectangle (806.31, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (806.31, 51.22) rectangle (813.71, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (813.71, 51.22) rectangle (821.12, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (821.12, 51.22) rectangle (828.52, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (828.52, 51.22) rectangle (835.92, 57.94);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (835.92, 51.22) rectangle (843.33, 57.94);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (843.33, 51.22) rectangle (850.73, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (850.73, 51.22) rectangle (858.14, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (858.14, 51.22) rectangle (865.54, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (865.54, 51.22) rectangle (872.94, 57.94);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (872.94, 51.22) rectangle (880.35,138.57);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (880.35, 51.22) rectangle (887.75, 51.22);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (695.25, 51.22) rectangle (702.66, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (702.66, 51.22) rectangle (710.06, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (710.06, 51.22) rectangle (717.47, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (717.47, 51.22) rectangle (724.87, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (724.87, 51.22) rectangle (732.27, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (732.27, 51.22) rectangle (739.68, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (739.68, 51.22) rectangle (747.08, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (747.08, 51.22) rectangle (754.48, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (754.48, 51.22) rectangle (761.89, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (761.89, 51.22) rectangle (769.29, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (769.29, 51.22) rectangle (776.70, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (776.70, 51.22) rectangle (784.10, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (784.10, 51.22) rectangle (791.50, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (791.50, 51.22) rectangle (798.91, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (798.91, 51.22) rectangle (806.31, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (806.31, 51.22) rectangle (813.71, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (813.71, 51.22) rectangle (821.12, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (821.12, 51.22) rectangle (828.52, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (828.52, 51.22) rectangle (835.92, 57.94);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (835.92, 51.22) rectangle (843.33, 57.94);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (843.33, 51.22) rectangle (850.73, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (850.73, 51.22) rectangle (858.14, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (858.14, 51.22) rectangle (865.54, 51.22);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (865.54, 51.22) rectangle (872.94, 57.94);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (872.94, 51.22) rectangle (880.35,138.57);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (880.35, 51.22) rectangle (887.75, 51.22);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (769.29, 45.85) -- (769.29,164.10);

\path[draw=drawColor,line width= 0.9pt,line join=round,line cap=round] (685.63, 45.85) rectangle (897.38,164.10);
\end{scope}
\begin{scope}
\path[clip] ( 33.90,164.10) rectangle (245.64,180.67);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 33.90,164.10) rectangle (245.64,180.68);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (139.77,169.36) {Marginal distribution};
\end{scope}
\begin{scope}
\path[clip] (251.14,164.10) rectangle (462.89,180.67);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (251.14,164.10) rectangle (462.89,180.68);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (357.01,169.36) {Supported limit is at target limit};
\end{scope}
\begin{scope}
\path[clip] (468.39,164.10) rectangle (680.13,180.67);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (468.39,164.10) rectangle (680.13,180.68);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (574.26,169.36) {Supported limit is below target limit};
\end{scope}
\begin{scope}
\path[clip] (685.63,164.10) rectangle (897.38,180.67);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (685.63,164.10) rectangle (897.38,180.68);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (791.50,169.36) {No limit (none observed below target limit)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.52, 43.10) --
	( 43.52, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.75, 43.10) --
	(102.75, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.98, 43.10) --
	(161.98, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.21, 43.10) --
	(221.21, 45.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 43.52, 34.70) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (102.75, 34.70) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (161.98, 34.70) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (221.21, 34.70) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (260.77, 43.10) --
	(260.77, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (319.99, 43.10) --
	(319.99, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (379.22, 43.10) --
	(379.22, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (438.45, 43.10) --
	(438.45, 45.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (260.77, 34.70) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (319.99, 34.70) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (379.22, 34.70) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (438.45, 34.70) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (478.01, 43.10) --
	(478.01, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (537.24, 43.10) --
	(537.24, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (596.47, 43.10) --
	(596.47, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (655.70, 43.10) --
	(655.70, 45.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (478.01, 34.70) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (537.24, 34.70) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (596.47, 34.70) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (655.70, 34.70) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (695.25, 43.10) --
	(695.25, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (754.48, 43.10) --
	(754.48, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (813.71, 43.10) --
	(813.71, 45.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (872.94, 43.10) --
	(872.94, 45.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (695.25, 34.70) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (754.48, 34.70) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (813.71, 34.70) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (872.94, 34.70) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 48.12) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 75.00) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,101.88) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,128.75) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,155.63) {40};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15, 51.22) --
	( 33.90, 51.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15, 78.10) --
	( 33.90, 78.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,104.97) --
	( 33.90,104.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,131.85) --
	( 33.90,131.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,158.73) --
	( 33.90,158.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (465.64, 20.75) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 12.20,104.97) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (290.12,  0.00) rectangle (478.56,  8.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (290.12,  5.90) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (345.06,  5.00) rectangle (353.06, 13.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.8pt,fill=fillColor,fill opacity=0.20] (346.06,  6.00) rectangle (352.06, 12.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (398.62,  5.00) rectangle (406.62, 13.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.8pt,fill=fillColor,fill opacity=0.20] (399.62,  6.00) rectangle (405.62, 12.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (357.56,  5.90) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (411.12,  5.90) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (489.56,  0.00) rectangle (641.15,  8.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (489.56,  5.90) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (581.39,  5.00) rectangle (589.39, 13.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (585.39,  5.00) -- (585.39, 13.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (903.38,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (593.89,  5.90) {0.25 mg/m\textsuperscript{3}};
\end{scope}

### 2023-06-12 reports/SER (2023)/resources/intervention-density-combo1.tex
SER postr

% Created by tikzDevice version 0.12.3.1 on 2023-06-02 02:14:29
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (271.01,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 33.90, 40.85) rectangle (265.01,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 33.90, 40.85) rectangle (265.01,216.81);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 44.40, 48.84) rectangle ( 52.48,144.82);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 52.48, 48.84) rectangle ( 60.56, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 60.56, 48.84) rectangle ( 68.64, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 68.64, 48.84) rectangle ( 76.73, 80.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 76.73, 48.84) rectangle ( 84.81, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 84.81, 48.84) rectangle ( 92.89, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 92.89, 48.84) rectangle (100.97, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21, 80.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (125.21, 48.84) rectangle (133.29, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (133.29, 48.84) rectangle (141.37, 80.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (141.37, 48.84) rectangle (149.45, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (149.45, 48.84) rectangle (157.54, 80.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (157.54, 48.84) rectangle (165.62, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (165.62, 48.84) rectangle (173.70, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (173.70, 48.84) rectangle (181.78, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (181.78, 48.84) rectangle (189.86, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (189.86, 48.84) rectangle (197.94, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (197.94, 48.84) rectangle (206.02, 80.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (206.02, 48.84) rectangle (214.10, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (214.10, 48.84) rectangle (222.18, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (222.18, 48.84) rectangle (230.26, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (230.26, 48.84) rectangle (238.35, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (238.35, 48.84) rectangle (246.43, 80.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (246.43, 48.84) rectangle (254.51, 48.84);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 44.40, 48.84) rectangle ( 52.48,144.82);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 52.48, 48.84) rectangle ( 60.56, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 60.56, 48.84) rectangle ( 68.64, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 68.64, 48.84) rectangle ( 76.73, 80.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 76.73, 48.84) rectangle ( 84.81, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 84.81, 48.84) rectangle ( 92.89, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 92.89, 48.84) rectangle (100.97, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21,208.81);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (125.21, 48.84) rectangle (133.29, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (133.29, 48.84) rectangle (141.37, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (141.37, 48.84) rectangle (149.45, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (149.45, 48.84) rectangle (157.54, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (157.54, 48.84) rectangle (165.62, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (165.62, 48.84) rectangle (173.70, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (173.70, 48.84) rectangle (181.78, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (181.78, 48.84) rectangle (189.86, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (189.86, 48.84) rectangle (197.94, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (197.94, 48.84) rectangle (206.02, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (206.02, 48.84) rectangle (214.10, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (214.10, 48.84) rectangle (222.18, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (222.18, 48.84) rectangle (230.26, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (230.26, 48.84) rectangle (238.35, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (238.35, 48.84) rectangle (246.43, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (246.43, 48.84) rectangle (254.51, 48.84);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.9pt,line join=round,line cap=round] ( 33.90, 40.85) rectangle (265.01,216.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 45.75) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 81.74) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,117.73) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,153.72) {15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,189.72) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15, 48.84) --
	( 33.90, 48.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15, 84.84) --
	( 33.90, 84.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,120.83) --
	( 33.90,120.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,156.82) --
	( 33.90,156.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,192.81) --
	( 33.90,192.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.40, 38.10) --
	( 44.40, 40.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.05, 38.10) --
	(109.05, 40.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.70, 38.10) --
	(173.70, 40.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.35, 38.10) --
	(238.35, 40.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 44.40, 29.70) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (109.05, 29.70) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (173.70, 29.70) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (238.35, 29.70) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (149.45, 15.75) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 12.20,128.83) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 55.24,  0.00) rectangle (243.67,  3.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 55.24,  0.90) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (110.17,  0.00) rectangle (118.17,  8.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.8pt,fill=fillColor,fill opacity=0.20] (111.17,  1.00) rectangle (117.17,  7.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (163.74,  0.00) rectangle (171.74,  8.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.8pt,fill=fillColor,fill opacity=0.20] (164.74,  1.00) rectangle (170.74,  7.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (122.67,  0.90) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (176.24,  0.90) {Post intervention};
\end{scope}

### 2023-06-12 reports/SER (2023)/resources/intervention-density-combo2.tex
SER postr

--- 2023-06-12 reports/SER (2023)/resources/intervention-density-combo1.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-02 02:14:29
+% Created by tikzDevice version 0.12.3.1 on 2023-06-02 02:14:31
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 44.40, 48.84) rectangle ( 52.48,144.82);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 44.40, 48.84) rectangle ( 52.48, 48.84);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 52.48, 48.84) rectangle ( 60.56, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 52.48, 48.84) rectangle ( 60.56, 94.55);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 60.56, 48.84) rectangle ( 68.64, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 60.56, 48.84) rectangle ( 68.64,105.98);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 68.64, 48.84) rectangle ( 76.73, 80.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 68.64, 48.84) rectangle ( 76.73, 71.70);
 
@@
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 84.81, 48.84) rectangle ( 92.89, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 84.81, 48.84) rectangle ( 92.89, 71.70);
 
@@
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 94.55);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13, 71.70);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21, 80.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21, 48.84);
 
@@
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (133.29, 48.84) rectangle (141.37, 80.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (133.29, 48.84) rectangle (141.37, 48.84);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (141.37, 48.84) rectangle (149.45, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (141.37, 48.84) rectangle (149.45, 83.12);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (149.45, 48.84) rectangle (157.54, 80.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (149.45, 48.84) rectangle (157.54, 71.70);
 
@@
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (165.62, 48.84) rectangle (173.70, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (165.62, 48.84) rectangle (173.70, 60.27);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (173.70, 48.84) rectangle (181.78, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (173.70, 48.84) rectangle (181.78, 60.27);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (181.78, 48.84) rectangle (189.86, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (181.78, 48.84) rectangle (189.86, 60.27);
 
@@
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (197.94, 48.84) rectangle (206.02, 80.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (197.94, 48.84) rectangle (206.02, 48.84);
 
@@
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (214.10, 48.84) rectangle (222.18, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (214.10, 48.84) rectangle (222.18, 60.27);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (222.18, 48.84) rectangle (230.26, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (222.18, 48.84) rectangle (230.26, 60.27);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (230.26, 48.84) rectangle (238.35, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (230.26, 48.84) rectangle (238.35, 71.70);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (238.35, 48.84) rectangle (246.43, 80.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (238.35, 48.84) rectangle (246.43, 48.84);
 
@@
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 94.55);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13, 48.84);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13,208.81);
 
-\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21,208.81);
+\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21, 48.84);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 81.74) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 90.02) {5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,117.73) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,134.30) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,153.72) {15};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,189.72) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,178.58) {15};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15, 84.84) --
-	( 33.90, 84.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15, 93.12) --
+	( 33.90, 93.12);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,120.83) --
-	( 33.90,120.83);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,137.40) --
+	( 33.90,137.40);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,156.82) --
-	( 33.90,156.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,192.81) --
-	( 33.90,192.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,181.67) --
+	( 33.90,181.67);
 \end{scope}

### 2023-06-12 reports/SER (2023)/resources/intervention-density-combo3.tex
SER postr

% Created by tikzDevice version 0.12.3.1 on 2023-06-02 02:14:31
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (271.01,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 40.89, 40.85) rectangle (265.01,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.89, 40.85) rectangle (265.01,216.81);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 51.08, 48.84) rectangle ( 56.31, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 56.31, 48.84) rectangle ( 61.53, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 61.53, 48.84) rectangle ( 66.75, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 66.75, 48.84) rectangle ( 71.98, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 71.98, 48.84) rectangle ( 77.20, 54.00);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 77.20, 48.84) rectangle ( 82.43, 51.42);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 82.43, 48.84) rectangle ( 87.65, 82.39);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 87.65, 48.84) rectangle ( 92.87, 54.00);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 92.87, 48.84) rectangle ( 98.10, 97.87);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 98.10, 48.84) rectangle (103.32, 66.91);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (103.32, 48.84) rectangle (108.55, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (108.55, 48.84) rectangle (113.77, 64.33);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (113.77, 48.84) rectangle (119.00, 56.58);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (119.00, 48.84) rectangle (124.22, 69.49);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (124.22, 48.84) rectangle (129.44, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (129.44, 48.84) rectangle (134.67, 51.42);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (134.67, 48.84) rectangle (139.89, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (139.89, 48.84) rectangle (145.12, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (145.12, 48.84) rectangle (150.34, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (150.34, 48.84) rectangle (155.57, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (155.57, 48.84) rectangle (160.79, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (160.79, 48.84) rectangle (166.01, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (166.01, 48.84) rectangle (171.24, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (171.24, 48.84) rectangle (176.46, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (176.46, 48.84) rectangle (181.69, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (181.69, 48.84) rectangle (186.91, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (186.91, 48.84) rectangle (192.13, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (192.13, 48.84) rectangle (197.36, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (197.36, 48.84) rectangle (202.58, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (202.58, 48.84) rectangle (207.81, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (207.81, 48.84) rectangle (213.03, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (213.03, 48.84) rectangle (218.26, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (218.26, 48.84) rectangle (223.48, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (223.48, 48.84) rectangle (228.70, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (228.70, 48.84) rectangle (233.93, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (233.93, 48.84) rectangle (239.15, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (239.15, 48.84) rectangle (244.38, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (244.38, 48.84) rectangle (249.60, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (249.60, 48.84) rectangle (254.83, 48.84);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 51.08, 48.84) rectangle ( 56.31, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 56.31, 48.84) rectangle ( 61.53, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 61.53, 48.84) rectangle ( 66.75, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 66.75, 48.84) rectangle ( 71.98, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 71.98, 48.84) rectangle ( 77.20,208.81);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 77.20, 48.84) rectangle ( 82.43, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 82.43, 48.84) rectangle ( 87.65, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 87.65, 48.84) rectangle ( 92.87, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 92.87, 48.84) rectangle ( 98.10, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 98.10, 48.84) rectangle (103.32, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (103.32, 48.84) rectangle (108.55, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (108.55, 48.84) rectangle (113.77, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (113.77, 48.84) rectangle (119.00, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (119.00, 48.84) rectangle (124.22, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (124.22, 48.84) rectangle (129.44, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (129.44, 48.84) rectangle (134.67, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (134.67, 48.84) rectangle (139.89, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (139.89, 48.84) rectangle (145.12, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (145.12, 48.84) rectangle (150.34, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (150.34, 48.84) rectangle (155.57, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (155.57, 48.84) rectangle (160.79, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (160.79, 48.84) rectangle (166.01, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (166.01, 48.84) rectangle (171.24, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (171.24, 48.84) rectangle (176.46, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (176.46, 48.84) rectangle (181.69, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (181.69, 48.84) rectangle (186.91, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (186.91, 48.84) rectangle (192.13, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (192.13, 48.84) rectangle (197.36, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (197.36, 48.84) rectangle (202.58, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (202.58, 48.84) rectangle (207.81, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (207.81, 48.84) rectangle (213.03, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (213.03, 48.84) rectangle (218.26, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (218.26, 48.84) rectangle (223.48, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (223.48, 48.84) rectangle (228.70, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (228.70, 48.84) rectangle (233.93, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (233.93, 48.84) rectangle (239.15, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (239.15, 48.84) rectangle (244.38, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (244.38, 48.84) rectangle (249.60, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (249.60, 48.84) rectangle (254.83, 48.84);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.9pt,line join=round,line cap=round] ( 40.89, 40.85) rectangle (265.01,216.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94, 45.75) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94, 85.74) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94,125.73) {5.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94,165.72) {7.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94,205.71) {10.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14, 48.84) --
	( 40.89, 48.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14, 88.84) --
	( 40.89, 88.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14,128.83) --
	( 40.89,128.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14,168.82) --
	( 40.89,168.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14,208.81) --
	( 40.89,208.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.08, 38.10) --
	( 51.08, 40.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.32, 38.10) --
	(103.32, 40.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.57, 38.10) --
	(155.57, 40.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.81, 38.10) --
	(207.81, 40.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (260.05, 38.10) --
	(260.05, 40.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 51.08, 29.70) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (103.32, 29.70) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (155.57, 29.70) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (207.81, 29.70) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (260.05, 29.70) {4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (152.95, 15.75) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 12.20,128.83) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 58.74,  0.00) rectangle (247.17,  3.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 58.74,  0.90) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (113.67,  0.00) rectangle (121.67,  8.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{186,129,35}
\definecolor{fillColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.8pt,fill=fillColor,fill opacity=0.20] (114.67,  1.00) rectangle (120.67,  7.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (167.24,  0.00) rectangle (175.24,  8.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,60,97}
\definecolor{fillColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.8pt,fill=fillColor,fill opacity=0.20] (168.24,  1.00) rectangle (174.24,  7.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (126.17,  0.90) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (179.74,  0.90) {Post intervention};
\end{scope}

### 2023-06-12 reports/SER (2023)/resources/intervention-density-witnin-combos.tex
SER postr

% Created by tikzDevice version 0.12.3.1 on 2023-06-12 13:31:15
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,437.23);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (271.01,437.23);
\end{scope}
\begin{scope}
\path[clip] ( 33.90,319.44) rectangle (265.01,420.66);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 33.90,319.44) rectangle (265.01,420.66);
\definecolor{fillColor}{RGB}{163,207,235}

\path[fill=fillColor] ( 44.40,324.04) rectangle ( 52.48,354.71);

\path[fill=fillColor] ( 52.48,324.04) rectangle ( 60.56,324.04);

\path[fill=fillColor] ( 60.56,324.04) rectangle ( 68.64,324.04);

\path[fill=fillColor] ( 68.64,324.04) rectangle ( 76.73,334.26);

\path[fill=fillColor] ( 76.73,324.04) rectangle ( 84.81,324.04);

\path[fill=fillColor] ( 84.81,324.04) rectangle ( 92.89,324.04);

\path[fill=fillColor] ( 92.89,324.04) rectangle (100.97,324.04);

\path[fill=fillColor] (100.97,324.04) rectangle (109.05,324.04);

\path[fill=fillColor] (109.05,324.04) rectangle (117.13,324.04);

\path[fill=fillColor] (117.13,324.04) rectangle (125.21,375.16);

\path[fill=fillColor] (125.21,324.04) rectangle (133.29,324.04);

\path[fill=fillColor] (133.29,324.04) rectangle (141.37,324.04);

\path[fill=fillColor] (141.37,324.04) rectangle (149.45,324.04);

\path[fill=fillColor] (149.45,324.04) rectangle (157.54,324.04);

\path[fill=fillColor] (157.54,324.04) rectangle (165.62,324.04);

\path[fill=fillColor] (165.62,324.04) rectangle (173.70,324.04);

\path[fill=fillColor] (173.70,324.04) rectangle (181.78,324.04);

\path[fill=fillColor] (181.78,324.04) rectangle (189.86,324.04);

\path[fill=fillColor] (189.86,324.04) rectangle (197.94,324.04);

\path[fill=fillColor] (197.94,324.04) rectangle (206.02,324.04);

\path[fill=fillColor] (206.02,324.04) rectangle (214.10,324.04);

\path[fill=fillColor] (214.10,324.04) rectangle (222.18,324.04);

\path[fill=fillColor] (222.18,324.04) rectangle (230.26,324.04);

\path[fill=fillColor] (230.26,324.04) rectangle (238.35,324.04);

\path[fill=fillColor] (238.35,324.04) rectangle (246.43,324.04);

\path[fill=fillColor] (246.43,324.04) rectangle (254.51,324.04);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 3.2pt] ( 44.40,324.04) rectangle ( 52.48,354.71);

\path[draw=drawColor,line width= 3.2pt] ( 52.48,324.04) rectangle ( 60.56,324.04);

\path[draw=drawColor,line width= 3.2pt] ( 60.56,324.04) rectangle ( 68.64,324.04);

\path[draw=drawColor,line width= 3.2pt] ( 68.64,324.04) rectangle ( 76.73,334.26);

\path[draw=drawColor,line width= 3.2pt] ( 76.73,324.04) rectangle ( 84.81,324.04);

\path[draw=drawColor,line width= 3.2pt] ( 84.81,324.04) rectangle ( 92.89,324.04);

\path[draw=drawColor,line width= 3.2pt] ( 92.89,324.04) rectangle (100.97,324.04);

\path[draw=drawColor,line width= 3.2pt] (100.97,324.04) rectangle (109.05,324.04);

\path[draw=drawColor,line width= 3.2pt] (109.05,324.04) rectangle (117.13,324.04);

\path[draw=drawColor,line width= 3.2pt] (117.13,324.04) rectangle (125.21,334.26);

\path[draw=drawColor,line width= 3.2pt] (125.21,324.04) rectangle (133.29,324.04);

\path[draw=drawColor,line width= 3.2pt] (133.29,324.04) rectangle (141.37,334.26);

\path[draw=drawColor,line width= 3.2pt] (141.37,324.04) rectangle (149.45,324.04);

\path[draw=drawColor,line width= 3.2pt] (149.45,324.04) rectangle (157.54,334.26);

\path[draw=drawColor,line width= 3.2pt] (157.54,324.04) rectangle (165.62,324.04);

\path[draw=drawColor,line width= 3.2pt] (165.62,324.04) rectangle (173.70,324.04);

\path[draw=drawColor,line width= 3.2pt] (173.70,324.04) rectangle (181.78,324.04);

\path[draw=drawColor,line width= 3.2pt] (181.78,324.04) rectangle (189.86,324.04);

\path[draw=drawColor,line width= 3.2pt] (189.86,324.04) rectangle (197.94,324.04);

\path[draw=drawColor,line width= 3.2pt] (197.94,324.04) rectangle (206.02,334.26);

\path[draw=drawColor,line width= 3.2pt] (206.02,324.04) rectangle (214.10,324.04);

\path[draw=drawColor,line width= 3.2pt] (214.10,324.04) rectangle (222.18,324.04);

\path[draw=drawColor,line width= 3.2pt] (222.18,324.04) rectangle (230.26,324.04);

\path[draw=drawColor,line width= 3.2pt] (230.26,324.04) rectangle (238.35,324.04);

\path[draw=drawColor,line width= 3.2pt] (238.35,324.04) rectangle (246.43,334.26);

\path[draw=drawColor,line width= 3.2pt] (246.43,324.04) rectangle (254.51,324.04);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (125.21,319.44) -- (125.21,420.66);

\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round] ( 33.90,319.44) rectangle (265.01,420.66);
\end{scope}
\begin{scope}
\path[clip] ( 33.90,196.14) rectangle (265.01,297.37);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 33.90,196.14) rectangle (265.01,297.37);
\definecolor{fillColor}{RGB}{163,207,235}

\path[fill=fillColor] ( 44.40,200.74) rectangle ( 52.48,292.77);

\path[fill=fillColor] ( 52.48,200.74) rectangle ( 60.56,200.74);

\path[fill=fillColor] ( 60.56,200.74) rectangle ( 68.64,200.74);

\path[fill=fillColor] ( 68.64,200.74) rectangle ( 76.73,200.74);

\path[fill=fillColor] ( 76.73,200.74) rectangle ( 84.81,200.74);

\path[fill=fillColor] ( 84.81,200.74) rectangle ( 92.89,200.74);

\path[fill=fillColor] ( 92.89,200.74) rectangle (100.97,200.74);

\path[fill=fillColor] (100.97,200.74) rectangle (109.05,200.74);

\path[fill=fillColor] (109.05,200.74) rectangle (117.13,200.74);

\path[fill=fillColor] (117.13,200.74) rectangle (125.21,200.74);

\path[fill=fillColor] (125.21,200.74) rectangle (133.29,200.74);

\path[fill=fillColor] (133.29,200.74) rectangle (141.37,200.74);

\path[fill=fillColor] (141.37,200.74) rectangle (149.45,200.74);

\path[fill=fillColor] (149.45,200.74) rectangle (157.54,200.74);

\path[fill=fillColor] (157.54,200.74) rectangle (165.62,200.74);

\path[fill=fillColor] (165.62,200.74) rectangle (173.70,200.74);

\path[fill=fillColor] (173.70,200.74) rectangle (181.78,200.74);

\path[fill=fillColor] (181.78,200.74) rectangle (189.86,200.74);

\path[fill=fillColor] (189.86,200.74) rectangle (197.94,200.74);

\path[fill=fillColor] (197.94,200.74) rectangle (206.02,200.74);

\path[fill=fillColor] (206.02,200.74) rectangle (214.10,200.74);

\path[fill=fillColor] (214.10,200.74) rectangle (222.18,200.74);

\path[fill=fillColor] (222.18,200.74) rectangle (230.26,200.74);

\path[fill=fillColor] (230.26,200.74) rectangle (238.35,200.74);

\path[fill=fillColor] (238.35,200.74) rectangle (246.43,200.74);

\path[fill=fillColor] (246.43,200.74) rectangle (254.51,200.74);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 3.2pt] ( 44.40,200.74) rectangle ( 52.48,223.75);

\path[draw=drawColor,line width= 3.2pt] ( 52.48,200.74) rectangle ( 60.56,200.74);

\path[draw=drawColor,line width= 3.2pt] ( 60.56,200.74) rectangle ( 68.64,200.74);

\path[draw=drawColor,line width= 3.2pt] ( 68.64,200.74) rectangle ( 76.73,200.74);

\path[draw=drawColor,line width= 3.2pt] ( 76.73,200.74) rectangle ( 84.81,200.74);

\path[draw=drawColor,line width= 3.2pt] ( 84.81,200.74) rectangle ( 92.89,200.74);

\path[draw=drawColor,line width= 3.2pt] ( 92.89,200.74) rectangle (100.97,200.74);

\path[draw=drawColor,line width= 3.2pt] (100.97,200.74) rectangle (109.05,200.74);

\path[draw=drawColor,line width= 3.2pt] (109.05,200.74) rectangle (117.13,200.74);

\path[draw=drawColor,line width= 3.2pt] (117.13,200.74) rectangle (125.21,200.74);

\path[draw=drawColor,line width= 3.2pt] (125.21,200.74) rectangle (133.29,246.75);

\path[draw=drawColor,line width= 3.2pt] (133.29,200.74) rectangle (141.37,200.74);

\path[draw=drawColor,line width= 3.2pt] (141.37,200.74) rectangle (149.45,223.75);

\path[draw=drawColor,line width= 3.2pt] (149.45,200.74) rectangle (157.54,200.74);

\path[draw=drawColor,line width= 3.2pt] (157.54,200.74) rectangle (165.62,200.74);

\path[draw=drawColor,line width= 3.2pt] (165.62,200.74) rectangle (173.70,200.74);

\path[draw=drawColor,line width= 3.2pt] (173.70,200.74) rectangle (181.78,200.74);

\path[draw=drawColor,line width= 3.2pt] (181.78,200.74) rectangle (189.86,200.74);

\path[draw=drawColor,line width= 3.2pt] (189.86,200.74) rectangle (197.94,200.74);

\path[draw=drawColor,line width= 3.2pt] (197.94,200.74) rectangle (206.02,200.74);

\path[draw=drawColor,line width= 3.2pt] (206.02,200.74) rectangle (214.10,200.74);

\path[draw=drawColor,line width= 3.2pt] (214.10,200.74) rectangle (222.18,200.74);

\path[draw=drawColor,line width= 3.2pt] (222.18,200.74) rectangle (230.26,200.74);

\path[draw=drawColor,line width= 3.2pt] (230.26,200.74) rectangle (238.35,200.74);

\path[draw=drawColor,line width= 3.2pt] (238.35,200.74) rectangle (246.43,200.74);

\path[draw=drawColor,line width= 3.2pt] (246.43,200.74) rectangle (254.51,200.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (125.21,196.14) -- (125.21,297.37);

\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round] ( 33.90,196.14) rectangle (265.01,297.37);
\end{scope}
\begin{scope}
\path[clip] ( 33.90, 72.85) rectangle (265.01,174.07);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 33.90, 72.85) rectangle (265.01,174.07);
\definecolor{fillColor}{RGB}{163,207,235}

\path[fill=fillColor] ( 44.40, 77.45) rectangle ( 52.48, 77.45);

\path[fill=fillColor] ( 52.48, 77.45) rectangle ( 60.56, 77.45);

\path[fill=fillColor] ( 60.56, 77.45) rectangle ( 68.64, 77.45);

\path[fill=fillColor] ( 68.64, 77.45) rectangle ( 76.73, 77.45);

\path[fill=fillColor] ( 76.73, 77.45) rectangle ( 84.81, 77.45);

\path[fill=fillColor] ( 84.81, 77.45) rectangle ( 92.89, 77.45);

\path[fill=fillColor] ( 92.89, 77.45) rectangle (100.97, 77.45);

\path[fill=fillColor] (100.97, 77.45) rectangle (109.05, 77.45);

\path[fill=fillColor] (109.05, 77.45) rectangle (117.13, 77.45);

\path[fill=fillColor] (117.13, 77.45) rectangle (125.21, 77.45);

\path[fill=fillColor] (125.21, 77.45) rectangle (133.29, 77.45);

\path[fill=fillColor] (133.29, 77.45) rectangle (141.37, 77.45);

\path[fill=fillColor] (141.37, 77.45) rectangle (149.45, 77.45);

\path[fill=fillColor] (149.45, 77.45) rectangle (157.54, 77.45);

\path[fill=fillColor] (157.54, 77.45) rectangle (165.62, 77.45);

\path[fill=fillColor] (165.62, 77.45) rectangle (173.70, 77.45);

\path[fill=fillColor] (173.70, 77.45) rectangle (181.78, 77.45);

\path[fill=fillColor] (181.78, 77.45) rectangle (189.86, 77.45);

\path[fill=fillColor] (189.86, 77.45) rectangle (197.94, 83.20);

\path[fill=fillColor] (197.94, 77.45) rectangle (206.02, 83.20);

\path[fill=fillColor] (206.02, 77.45) rectangle (214.10, 77.45);

\path[fill=fillColor] (214.10, 77.45) rectangle (222.18, 77.45);

\path[fill=fillColor] (222.18, 77.45) rectangle (230.26, 77.45);

\path[fill=fillColor] (230.26, 77.45) rectangle (238.35, 83.20);

\path[fill=fillColor] (238.35, 77.45) rectangle (246.43,152.22);

\path[fill=fillColor] (246.43, 77.45) rectangle (254.51, 77.45);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 3.2pt] ( 44.40, 77.45) rectangle ( 52.48, 77.45);

\path[draw=drawColor,line width= 3.2pt] ( 52.48, 77.45) rectangle ( 60.56, 77.45);

\path[draw=drawColor,line width= 3.2pt] ( 60.56, 77.45) rectangle ( 68.64, 77.45);

\path[draw=drawColor,line width= 3.2pt] ( 68.64, 77.45) rectangle ( 76.73, 77.45);

\path[draw=drawColor,line width= 3.2pt] ( 76.73, 77.45) rectangle ( 84.81, 77.45);

\path[draw=drawColor,line width= 3.2pt] ( 84.81, 77.45) rectangle ( 92.89, 77.45);

\path[draw=drawColor,line width= 3.2pt] ( 92.89, 77.45) rectangle (100.97, 77.45);

\path[draw=drawColor,line width= 3.2pt] (100.97, 77.45) rectangle (109.05, 77.45);

\path[draw=drawColor,line width= 3.2pt] (109.05, 77.45) rectangle (117.13, 77.45);

\path[draw=drawColor,line width= 3.2pt] (117.13, 77.45) rectangle (125.21, 77.45);

\path[draw=drawColor,line width= 3.2pt] (125.21, 77.45) rectangle (133.29, 77.45);

\path[draw=drawColor,line width= 3.2pt] (133.29, 77.45) rectangle (141.37, 77.45);

\path[draw=drawColor,line width= 3.2pt] (141.37, 77.45) rectangle (149.45, 77.45);

\path[draw=drawColor,line width= 3.2pt] (149.45, 77.45) rectangle (157.54, 77.45);

\path[draw=drawColor,line width= 3.2pt] (157.54, 77.45) rectangle (165.62, 77.45);

\path[draw=drawColor,line width= 3.2pt] (165.62, 77.45) rectangle (173.70, 77.45);

\path[draw=drawColor,line width= 3.2pt] (173.70, 77.45) rectangle (181.78, 77.45);

\path[draw=drawColor,line width= 3.2pt] (181.78, 77.45) rectangle (189.86, 77.45);

\path[draw=drawColor,line width= 3.2pt] (189.86, 77.45) rectangle (197.94, 83.20);

\path[draw=drawColor,line width= 3.2pt] (197.94, 77.45) rectangle (206.02, 83.20);

\path[draw=drawColor,line width= 3.2pt] (206.02, 77.45) rectangle (214.10, 77.45);

\path[draw=drawColor,line width= 3.2pt] (214.10, 77.45) rectangle (222.18, 77.45);

\path[draw=drawColor,line width= 3.2pt] (222.18, 77.45) rectangle (230.26, 77.45);

\path[draw=drawColor,line width= 3.2pt] (230.26, 77.45) rectangle (238.35, 83.20);

\path[draw=drawColor,line width= 3.2pt] (238.35, 77.45) rectangle (246.43,152.22);

\path[draw=drawColor,line width= 3.2pt] (246.43, 77.45) rectangle (254.51, 77.45);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (125.21, 72.85) -- (125.21,174.07);

\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round] ( 33.90, 72.85) rectangle (265.01,174.07);
\end{scope}
\begin{scope}
\path[clip] ( 33.90,174.07) rectangle (265.01,190.64);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round,fill=fillColor] ( 33.90,174.07) rectangle (265.01,190.64);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (149.45,179.33) {No limit (all observed exposures $>$ target limit)};
\end{scope}
\begin{scope}
\path[clip] ( 33.90,297.37) rectangle (265.01,313.94);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round,fill=fillColor] ( 33.90,297.37) rectangle (265.01,313.94);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (149.45,302.62) {Supported exposure limit $<$ target limit};
\end{scope}
\begin{scope}
\path[clip] ( 33.90,420.66) rectangle (265.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round,fill=fillColor] ( 33.90,420.66) rectangle (265.01,437.23);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (149.45,425.92) {Supported exposure limit $=$ target limit};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 44.40, 70.10) --
	( 44.40, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (109.05, 70.10) --
	(109.05, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (173.70, 70.10) --
	(173.70, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (238.35, 70.10) --
	(238.35, 72.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 44.40, 61.70) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (109.05, 61.70) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (173.70, 61.70) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (238.35, 61.70) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,320.94) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,343.95) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,366.95) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,389.96) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,412.96) {40};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,324.04) --
	( 33.90,324.04);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,347.04) --
	( 33.90,347.04);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,370.05) --
	( 33.90,370.05);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,393.06) --
	( 33.90,393.06);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,416.06) --
	( 33.90,416.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,197.64) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,220.65) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,243.65) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,266.66) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,289.67) {40};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,200.74) --
	( 33.90,200.74);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,223.75) --
	( 33.90,223.75);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,246.75) --
	( 33.90,246.75);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,269.76) --
	( 33.90,269.76);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,292.77) --
	( 33.90,292.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 74.35) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 97.35) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,120.36) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,143.36) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,166.37) {40};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15, 77.45) --
	( 33.90, 77.45);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,100.45) --
	( 33.90,100.45);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,123.46) --
	( 33.90,123.46);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,146.46) --
	( 33.90,146.46);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 31.15,169.47) --
	( 33.90,169.47);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (149.45, 47.75) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 12.20,246.75) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 42.74, 23.00) rectangle (256.17, 35.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 42.74, 30.90) {Distribution:\ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (104.17, 28.00) rectangle (116.17, 40.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{163,207,235}
\definecolor{fillColor}{RGB}{163,207,235}

\path[draw=drawColor,line width= 1.2pt,fill=fillColor] (105.67, 29.50) rectangle (114.67, 38.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (202.60, 28.00) rectangle (214.60, 40.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 1.2pt] (204.10, 29.50) rectangle (213.10, 38.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (121.17, 30.90) {Post-intervention\ \ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (219.60, 30.90) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 71.16,  0.00) rectangle (227.75, 12.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 71.16,  7.90) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (163.49,  5.00) rectangle (175.49, 17.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (169.49,  5.00) -- (169.49, 17.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,437.23);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (180.49,  7.90) {0.25 mg/m\textsuperscript{3}};
\end{scope}

### 2023-06-12 reports/SER (2023)/resources/intervention-density.tex
SER postr

% Created by tikzDevice version 0.12.3.1 on 2023-06-08 17:09:01
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,195.13);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (271.01,195.13);
\end{scope}
\begin{scope}
\path[clip] ( 36.40, 72.85) rectangle (265.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 36.40, 72.85) rectangle (265.01,195.13);
\definecolor{fillColor}{RGB}{163,207,235}

\path[fill=fillColor] ( 46.79, 78.40) rectangle ( 58.33, 78.43);

\path[fill=fillColor] ( 58.33, 78.40) rectangle ( 69.88, 78.79);

\path[fill=fillColor] ( 69.88, 78.40) rectangle ( 81.43, 78.79);

\path[fill=fillColor] ( 81.43, 78.40) rectangle ( 92.97, 79.38);

\path[fill=fillColor] ( 92.97, 78.40) rectangle (104.52, 79.86);

\path[fill=fillColor] (104.52, 78.40) rectangle (116.06, 80.51);

\path[fill=fillColor] (116.06, 78.40) rectangle (127.61, 83.35);

\path[fill=fillColor] (127.61, 78.40) rectangle (139.16, 85.54);

\path[fill=fillColor] (139.16, 78.40) rectangle (150.70,103.29);

\path[fill=fillColor] (150.70, 78.40) rectangle (162.25,102.34);

\path[fill=fillColor] (162.25, 78.40) rectangle (173.80,189.57);

\path[fill=fillColor] (173.80, 78.40) rectangle (185.34,123.53);

\path[fill=fillColor] (185.34, 78.40) rectangle (196.89,106.28);

\path[fill=fillColor] (196.89, 78.40) rectangle (208.44, 88.77);

\path[fill=fillColor] (208.44, 78.40) rectangle (219.98, 85.04);

\path[fill=fillColor] (219.98, 78.40) rectangle (231.53, 78.97);

\path[fill=fillColor] (231.53, 78.40) rectangle (243.07, 79.17);

\path[fill=fillColor] (243.07, 78.40) rectangle (254.62, 78.43);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 3.2pt] ( 46.79, 78.40) rectangle ( 58.33, 78.43);

\path[draw=drawColor,line width= 3.2pt] ( 58.33, 78.40) rectangle ( 69.88, 78.73);

\path[draw=drawColor,line width= 3.2pt] ( 69.88, 78.40) rectangle ( 81.43, 78.76);

\path[draw=drawColor,line width= 3.2pt] ( 81.43, 78.40) rectangle ( 92.97, 79.20);

\path[draw=drawColor,line width= 3.2pt] ( 92.97, 78.40) rectangle (104.52, 79.47);

\path[draw=drawColor,line width= 3.2pt] (104.52, 78.40) rectangle (116.06, 79.85);

\path[draw=drawColor,line width= 3.2pt] (116.06, 78.40) rectangle (127.61, 82.26);

\path[draw=drawColor,line width= 3.2pt] (127.61, 78.40) rectangle (139.16, 83.65);

\path[draw=drawColor,line width= 3.2pt] (139.16, 78.40) rectangle (150.70, 93.74);

\path[draw=drawColor,line width= 3.2pt] (150.70, 78.40) rectangle (162.25, 93.20);

\path[draw=drawColor,line width= 3.2pt] (162.25, 78.40) rectangle (173.80,122.26);

\path[draw=drawColor,line width= 3.2pt] (173.80, 78.40) rectangle (185.34,132.11);

\path[draw=drawColor,line width= 3.2pt] (185.34, 78.40) rectangle (196.89,142.20);

\path[draw=drawColor,line width= 3.2pt] (196.89, 78.40) rectangle (208.44,112.28);

\path[draw=drawColor,line width= 3.2pt] (208.44, 78.40) rectangle (219.98,101.97);

\path[draw=drawColor,line width= 3.2pt] (219.98, 78.40) rectangle (231.53, 82.12);

\path[draw=drawColor,line width= 3.2pt] (231.53, 78.40) rectangle (243.07, 81.28);

\path[draw=drawColor,line width= 3.2pt] (243.07, 78.40) rectangle (254.62, 78.54);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (174.29, 72.85) -- (174.29,195.13);

\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round] ( 36.40, 72.85) rectangle (265.01,195.13);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45, 75.31) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,102.18) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,129.06) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,155.94) {0.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,182.82) {0.8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65, 78.40) --
	( 36.40, 78.40);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,105.28) --
	( 36.40,105.28);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,132.16) --
	( 36.40,132.16);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,159.04) --
	( 36.40,159.04);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,185.92) --
	( 36.40,185.92);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 46.79, 70.10) --
	( 46.79, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (137.13, 70.10) --
	(137.13, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (206.31, 70.10) --
	(206.31, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (259.48, 70.10) --
	(259.48, 72.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 46.79, 61.70) {0.001};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (137.13, 61.70) {0.05};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (206.31, 61.70) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (259.48, 61.70) {10};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (150.70, 47.75) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 12.20,133.99) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 43.99, 23.00) rectangle (257.42, 35.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 43.99, 30.90) {Distribution:\ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (105.42, 28.00) rectangle (117.42, 40.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{163,207,235}
\definecolor{fillColor}{RGB}{163,207,235}

\path[draw=drawColor,line width= 1.2pt,fill=fillColor] (106.92, 29.50) rectangle (115.92, 38.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (203.85, 28.00) rectangle (215.85, 40.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 1.2pt] (205.35, 29.50) rectangle (214.35, 38.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (122.42, 30.90) {Post-intervention\ \ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (220.85, 30.90) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 72.41,  0.00) rectangle (229.00, 12.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 72.41,  7.90) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (164.74,  5.00) rectangle (176.74, 17.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (170.74,  5.00) -- (170.74, 17.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (181.74,  7.90) {0.25 mg/m\textsuperscript{3}};
\end{scope}

### 2023-06-12 reports/SER (2023)/resources/rd.tex
SER postr

% Created by tikzDevice version 0.12.3.1 on 2023-06-01 11:24:54
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,162.61);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,162.61);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (271.01,162.61);
\end{scope}
\begin{scope}
\path[clip] ( 40.89, 26.85) rectangle (265.01,162.61);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.89, 26.85) rectangle (265.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (199.88,139.19) --
	(248.03,139.19) --
	(247.96,139.19) --
	(248.25,139.20) --
	(248.53,139.26) --
	(248.81,139.36) --
	(249.06,139.51) --
	(249.28,139.69) --
	(249.48,139.91) --
	(249.63,140.15) --
	(249.75,140.42) --
	(249.82,140.70) --
	(249.84,140.99) --
	(249.84,140.99) --
	(249.84,152.89) --
	(249.84,152.89) --
	(249.82,153.18) --
	(249.75,153.46) --
	(249.63,153.73) --
	(249.48,153.98) --
	(249.28,154.19) --
	(249.06,154.38) --
	(248.81,154.52) --
	(248.53,154.63) --
	(248.25,154.68) --
	(248.03,154.70) --
	(199.88,154.70) --
	(200.10,154.68) --
	(199.81,154.70) --
	(199.52,154.66) --
	(199.24,154.58) --
	(198.97,154.46) --
	(198.74,154.29) --
	(198.53,154.09) --
	(198.35,153.86) --
	(198.22,153.60) --
	(198.12,153.32) --
	(198.08,153.04) --
	(198.07,152.89) --
	(198.07,140.99) --
	(198.08,141.14) --
	(198.08,140.85) --
	(198.12,140.56) --
	(198.22,140.29) --
	(198.35,140.03) --
	(198.53,139.80) --
	(198.74,139.60) --
	(198.97,139.43) --
	(199.24,139.31) --
	(199.52,139.22) --
	(199.81,139.19) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 40.89, 26.85) rectangle (265.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (223.95,144.19) {98 (45, 161)};
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (197.88,113.08) --
	(250.03,113.08) --
	(249.96,113.08) --
	(250.25,113.09) --
	(250.53,113.15) --
	(250.81,113.25) --
	(251.06,113.40) --
	(251.28,113.58) --
	(251.48,113.80) --
	(251.63,114.05) --
	(251.75,114.31) --
	(251.81,114.60) --
	(251.84,114.89) --
	(251.84,114.89) --
	(251.84,126.78) --
	(251.84,126.78) --
	(251.81,127.07) --
	(251.75,127.36) --
	(251.63,127.62) --
	(251.48,127.87) --
	(251.28,128.09) --
	(251.06,128.27) --
	(250.81,128.42) --
	(250.53,128.52) --
	(250.25,128.58) --
	(250.03,128.59) --
	(197.88,128.59) --
	(198.10,128.58) --
	(197.81,128.59) --
	(197.52,128.55) --
	(197.24,128.47) --
	(196.97,128.35) --
	(196.74,128.18) --
	(196.53,127.98) --
	(196.35,127.75) --
	(196.22,127.49) --
	(196.12,127.22) --
	(196.08,126.93) --
	(196.07,126.78) --
	(196.07,114.89) --
	(196.08,115.03) --
	(196.08,114.74) --
	(196.12,114.45) --
	(196.22,114.18) --
	(196.35,113.92) --
	(196.53,113.69) --
	(196.74,113.49) --
	(196.97,113.32) --
	(197.24,113.20) --
	(197.52,113.12) --
	(197.81,113.08) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 40.89, 26.85) rectangle (265.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (223.95,118.08) {106 (51, 173)};
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (197.88, 86.97) --
	(250.03, 86.97) --
	(249.96, 86.97) --
	(250.25, 86.99) --
	(250.53, 87.04) --
	(250.81, 87.15) --
	(251.06, 87.29) --
	(251.28, 87.48) --
	(251.48, 87.69) --
	(251.63, 87.94) --
	(251.75, 88.21) --
	(251.81, 88.49) --
	(251.84, 88.78) --
	(251.84, 88.78) --
	(251.84,100.67) --
	(251.84,100.67) --
	(251.81,100.96) --
	(251.75,101.25) --
	(251.63,101.51) --
	(251.48,101.76) --
	(251.28,101.98) --
	(251.06,102.16) --
	(250.81,102.31) --
	(250.53,102.41) --
	(250.25,102.47) --
	(250.03,102.48) --
	(197.88,102.48) --
	(198.10,102.47) --
	(197.81,102.48) --
	(197.52,102.45) --
	(197.24,102.36) --
	(196.97,102.24) --
	(196.74,102.07) --
	(196.53,101.87) --
	(196.35,101.64) --
	(196.22,101.38) --
	(196.12,101.11) --
	(196.08,100.82) --
	(196.07,100.67) --
	(196.07, 88.78) --
	(196.08, 88.92) --
	(196.08, 88.63) --
	(196.12, 88.35) --
	(196.22, 88.07) --
	(196.35, 87.81) --
	(196.53, 87.58) --
	(196.74, 87.38) --
	(196.97, 87.21) --
	(197.24, 87.09) --
	(197.52, 87.01) --
	(197.81, 86.97) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 40.89, 26.85) rectangle (265.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (223.95, 91.97) {112 (57, 181)};
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (197.88, 60.86) --
	(250.03, 60.86) --
	(249.96, 60.87) --
	(250.25, 60.88) --
	(250.53, 60.94) --
	(250.81, 61.04) --
	(251.06, 61.18) --
	(251.28, 61.37) --
	(251.48, 61.59) --
	(251.63, 61.83) --
	(251.75, 62.10) --
	(251.81, 62.38) --
	(251.84, 62.67) --
	(251.84, 62.67) --
	(251.84, 74.57) --
	(251.84, 74.57) --
	(251.81, 74.86) --
	(251.75, 75.14) --
	(251.63, 75.41) --
	(251.48, 75.65) --
	(251.28, 75.87) --
	(251.06, 76.05) --
	(250.81, 76.20) --
	(250.53, 76.30) --
	(250.25, 76.36) --
	(250.03, 76.37) --
	(197.88, 76.37) --
	(198.10, 76.36) --
	(197.81, 76.37) --
	(197.52, 76.34) --
	(197.24, 76.26) --
	(196.97, 76.13) --
	(196.74, 75.97) --
	(196.53, 75.77) --
	(196.35, 75.53) --
	(196.22, 75.28) --
	(196.12, 75.00) --
	(196.08, 74.71) --
	(196.07, 74.57) --
	(196.07, 62.67) --
	(196.08, 62.82) --
	(196.08, 62.53) --
	(196.12, 62.24) --
	(196.22, 61.96) --
	(196.35, 61.70) --
	(196.53, 61.47) --
	(196.74, 61.27) --
	(196.97, 61.11) --
	(197.24, 60.98) --
	(197.52, 60.90) --
	(197.81, 60.87) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 40.89, 26.85) rectangle (265.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (223.95, 65.86) {118 (59, 192)};
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (197.88, 34.76) --
	(250.03, 34.76) --
	(249.96, 34.76) --
	(250.25, 34.77) --
	(250.53, 34.83) --
	(250.81, 34.93) --
	(251.06, 35.08) --
	(251.28, 35.26) --
	(251.48, 35.48) --
	(251.63, 35.72) --
	(251.75, 35.99) --
	(251.81, 36.27) --
	(251.84, 36.56) --
	(251.84, 36.56) --
	(251.84, 48.46) --
	(251.84, 48.46) --
	(251.81, 48.75) --
	(251.75, 49.03) --
	(251.63, 49.30) --
	(251.48, 49.54) --
	(251.28, 49.76) --
	(251.06, 49.95) --
	(250.81, 50.09) --
	(250.53, 50.19) --
	(250.25, 50.25) --
	(250.03, 50.27) --
	(197.88, 50.27) --
	(198.10, 50.25) --
	(197.81, 50.26) --
	(197.52, 50.23) --
	(197.24, 50.15) --
	(196.97, 50.02) --
	(196.74, 49.86) --
	(196.53, 49.66) --
	(196.35, 49.42) --
	(196.22, 49.17) --
	(196.12, 48.89) --
	(196.08, 48.60) --
	(196.07, 48.46) --
	(196.07, 36.56) --
	(196.08, 36.71) --
	(196.08, 36.42) --
	(196.12, 36.13) --
	(196.22, 35.85) --
	(196.35, 35.60) --
	(196.53, 35.36) --
	(196.74, 35.16) --
	(196.97, 35.00) --
	(197.24, 34.87) --
	(197.52, 34.79) --
	(197.81, 34.76) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 40.89, 26.85) rectangle (265.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (223.95, 39.76) {129 (66, 214)};
\definecolor{drawColor}{RGB}{0,60,97}

\path[draw=drawColor,line width= 1.6pt,line join=round] (156.42,144.98) --
	(156.42,148.90);

\path[draw=drawColor,line width= 1.6pt,line join=round] (156.42,146.94) --
	( 84.79,146.94);

\path[draw=drawColor,line width= 1.6pt,line join=round] ( 84.79,144.98) --
	( 84.79,148.90);

\path[draw=drawColor,line width= 1.6pt,line join=round] (164.09,118.88) --
	(164.09,122.79);

\path[draw=drawColor,line width= 1.6pt,line join=round] (164.09,120.83) --
	( 88.92,120.83);

\path[draw=drawColor,line width= 1.6pt,line join=round] ( 88.92,118.88) --
	( 88.92,122.79);

\path[draw=drawColor,line width= 1.6pt,line join=round] (169.20, 92.77) --
	(169.20, 96.68);

\path[draw=drawColor,line width= 1.6pt,line join=round] (169.20, 94.73) --
	( 92.17, 94.73);

\path[draw=drawColor,line width= 1.6pt,line join=round] ( 92.17, 92.77) --
	( 92.17, 96.68);

\path[draw=drawColor,line width= 1.6pt,line join=round] (175.75, 66.66) --
	(175.75, 70.58);

\path[draw=drawColor,line width= 1.6pt,line join=round] (175.75, 68.62) --
	( 93.91, 68.62);

\path[draw=drawColor,line width= 1.6pt,line join=round] ( 93.91, 66.66) --
	( 93.91, 70.58);

\path[draw=drawColor,line width= 1.6pt,line join=round] (189.54, 40.55) --
	(189.54, 44.47);

\path[draw=drawColor,line width= 1.6pt,line join=round] (189.54, 42.51) --
	( 98.17, 42.51);

\path[draw=drawColor,line width= 1.6pt,line join=round] ( 98.17, 40.55) --
	( 98.17, 44.47);
\definecolor{fillColor}{RGB}{0,60,97}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.65,146.94) circle (  1.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.54,120.83) circle (  1.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.15, 94.73) circle (  1.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.92, 68.62) circle (  1.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.90, 42.51) circle (  1.86);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,draw opacity=0.70,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 57.26, 26.85) -- ( 57.26,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.9pt,line join=round,line cap=round] ( 40.89, 26.85) rectangle (265.01,162.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94, 39.41) {0.05};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94, 65.52) {0.25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94, 91.63) {0.50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94,117.74) {1.00};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 35.94,143.84) {2.00};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,162.61);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14, 42.51) --
	( 40.89, 42.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14, 68.62) --
	( 40.89, 68.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14, 94.73) --
	( 40.89, 94.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14,120.83) --
	( 40.89,120.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.14,146.94) --
	( 40.89,146.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,162.61);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.26, 24.10) --
	( 57.26, 26.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.00, 24.10) --
	(119.00, 26.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (180.74, 24.10) --
	(180.74, 26.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (242.48, 24.10) --
	(242.48, 26.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 57.26, 15.70) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (119.00, 15.70) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (180.74, 15.70) {200};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (242.48, 15.70) {300};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (152.95,  1.75) {Cases averted};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,162.61);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 12.20, 94.73) {Target limit (mg/m$^3$)};
\end{scope}

### 2023-06-12 reports/paper/paper.qmd
SER postr

@@
   chunk_output_type: inline
+editor: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-**Manuscript title:** Hypothetical limits on workplace exposure for reducing non-Hodgkin lymphoma: An application of the hazard-extended iterative conditional expectation parametric g-formula
+**Manuscript title:** Hypothetical limits on workplace exposure for
+reducing non-Hodgkin lymphoma: An application of the hazard-extended
+iterative conditional expectation parametric g-formula
 
-**Authors:** Kevin T. Chen^a,b,c^, Sally Picciotto^b^, Ellen A. Eisen^b^
+**Authors:** Kevin T. Chen^a^, Sally Picciotto^b^, Ellen A. Eisen^b^
 
-^a^ University of California, Berkeley School of Public Health, Division of Epidemiology \& Biostatistics
-
-^b^ University of California, Berkeley School of Public Health, Division of Environmental Health Sciences
-
-^c^ University of California, Berkeley Department of Statistics
+^a^ University of California, Berkeley School of Public Health, Division
+of Epidemiology & Biostatistics
 
@@
 Berkeley, CA 94720-7360\
-kevchen@berkeley.edu\
+kevchen\@berkeley.edu\
 (510) 387-3327
 
-**Running head suggestion:** Limits on metalworking fluid exposure to prevent NHL.
+**Running head suggestion:** Limits on metalworking fluid exposure to
+prevent NHL.
 
@@
 
-**Sources of financial support:** This work was supported by Training Grant T42OH008429 and Research Project Grant R01OH011092, both funded by the National Institute for Occupational Safety and Health (NIOSH) / Centers for Disease Control and Prevention (CDC).
+**Sources of financial support:** This work was supported by Training
+Grant T42OH008429 and Research Project Grant R01OH011092, both funded by
+the National Institute for Occupational Safety and Health (NIOSH) /
+Centers for Disease Control and Prevention (CDC).
 
-**Data and computing code:** Code for reproducing analyses and reports are available on [Github](https://github.com/kvntchn/gm-nhl-ice). Data are available upon reasonable request.
+**Data and computing code:** Code for reproducing analyses and reports
+are available on [Github](https://github.com/kvntchn/gm-nhl-ice). Data
+are available upon reasonable request.
 
-**Keywords:** Metalworking fluid, occupational exposure, non-Hodgkin lymphoma, cancer, causal inference, g-formula, healthy-worker effect, United States
+**Keywords:** Metalworking fluid, occupational exposure, non-Hodgkin
+lymphoma, cancer, causal inference, g-formula, healthy-worker effect,
+United States
 
@@
 
-**Background:** Non-Hodgkin lymphoma (NHL) incidence has increased substantially in the US since 1960 and was recently linked to workplace exposure to soluble metalworking fluids (MWF) in a standard survival analysis of the United Auto Workers-General Motors (UAW-GM) cohort.
-To further explore this association, we estimate the effects of hypothetical limits on soluble MWF exposure in relation to NHL risk in the same cohort of autoworkers.
+**Background:** Non-Hodgkin lymphoma (NHL) incidence has increased
+substantially in the US since 1960 and was recently linked to workplace
+exposure to soluble metalworking fluids (MWF) in a standard survival
+analysis of the United Auto Workers-General Motors (UAW-GM) cohort. To
+further explore this association, we estimate the effects of
+hypothetical limits on soluble MWF exposure in relation to NHL risk in
+the same cohort of autoworkers.
 
-**Methods:** We estimated counterfactual risk of NHL between 1985 and 2015 in the UAW-GM cohort of autoworkers at three Michigan plants (n = 33,134) under hypothetical limits on annual average daily exposure to soluble MWF.
-We applied the hazard-extended ICE parametric g-formula, an estimator capable of adjusting for time-varying confounding affected by past exposure.
+**Methods:** We estimated counterfactual risk of NHL between 1985 and
+2015 in the UAW-GM cohort of autoworkers at three Michigan plants (n =
+33,134) under hypothetical target exposure limits for soluble MWF. We
+applied the hazard-extended iterative conditional expectation parametric
+g-formula, an estimator capable of adjusting for time-varying
+confounding affected by past exposure.
 
 **Results:** 339 NHL cases occurred over the 30-year follow-up period.
-Stronger hypothetical limits on soluble MWF exposure resulted in monotonic reductions in NHL risk.
-Capping annual average daily exposure at 2 mg/m^3^ would have prevented 98 (95% CI: 45, 161) cases of NHL.
-Capping at 0.5 mg/m^3^, the NIOSH recommended exposure limit, would have prevented 112 (95% CI: 57, 181) cases.
-Finally, capping at 0.05 mg/m^3^ would have prevented 129 (95% CI: 66, 214) cases.
+Stronger target limits on soluble MWF exposure resulted in monotonic
+reductions in NHL risk. Setting the target exposure limit at 2 mg/m^3^
+would have prevented 98 (95% CI: 45, 161) cases of NHL. A target
+exposure limit of 0.5 mg/m^3^, the NIOSH recommended exposure limit,
+would have prevented 112 (95% CI: 57, 181) cases. Finally, a target
+exposure limit of 0.05 mg/m^3^ would have prevented 129 (95% CI: 66,
+214) cases.
 
-**Conclusion:** Limits on soluble MWF exposure would have prevented cases of NHL in the UAW-GM cohort.
-Although MWF use is expected to decline as the automotive industry turns to electric vehicles, a boom in electric vehicle manufacturing could nonetheless lead to global increases in worker exposure to MWF.
-Maintaining limits on exposure to MWF may protect workers against risk of NHL.
+**Conclusion:** Limits on soluble MWF exposure would have prevented
+cases of NHL in the UAW-GM cohort. Although MWF use is expected to
+decline as the automotive industry turns to electric vehicles, a boom in
+domestic vehicle manufacturing could nonetheless lead to global
+increases in worker exposure to MWF in the US. Maintaining or
+strengthening exposure limits for MWF may protect workers from NHL.
 
@@
 # Introduction
+
+Non-Hodgkin Lymphoma (NHL) incidence in the United States doubled
+between 1973 and 1994, before plateauing at around 19 per 100,000
+persons per year, making it the seventh most common cancer in the
+country [@seer_1994; @Ekstrom-Smedby_2006]. The strongest known risk
+factor of NHL is immunosuppression, both congenital and acquired
+[@Filipovich_1992; @Chiu_2015]. Modulation of immune function
+contributes to the pathogenesis of NHL directly by perturbing lymphocyte
+function or indirectly by reducing immunosurveillance against neoplasms.
+Immunodeficiency may also interact with infection with Epstein-Barr
+Virus, resulting in uncontrolled B-cell proliferation [@Oertel_2002].
+Acquired immunodeficiency through infection with human immunodeficiency
+virus (HIV) can lead to genetic lesions and dysregulation while
+increasing vulnerability to infection by other oncogenic agents
+[@Grulich_1999; @Alexander_2007]. However, since immunodeficiency and
+infection with HIV are rare, they cannot fully explain the historic rise
+or present burden of NHL [@Shiels_2013]. The rise in NHL incidence
+coincided with a period of rapid and extensive chemicalization in
+industry, agriculture and warfare; environmental and occupational
+exposures may play an important explanatory role in the epidemiology of
+NHL [@Nelson_2005; @Romero_2021].
+
+Pesticide exposure among workers in agricultural settings was a common
+target of NHL research in recent decades. A meta-analysis of 44 articles
+published between 1980 and 2014 found statistically significant
+associations between NHL and exposure to several classes of pesticides
+including carbamate, organophosporus, triazine, and organochlorine
+[@Schinasi_2014]. Occupational exposures associated with NHL are not
+limited to the agricultural sector, however. Occupational groups
+associated with NHL risk also include metal processors, health workers,
+salespeople, machinists, and electricians [@Fritschi_2005a;
+@Mester_2006; @Ekstrom-Smedby_2006]. Workers in these occupational
+groups often come into contact with industrial chemicals such as
+gasoline, solvents, coolants, and lubricants such as metalworking fluids
+(MWF).
+
+Metalworking fluids are complex mixtures of oil, water, and chemical
+additives that optimize metal machining operations. During shaping,
+grinding, and cutting operations, MWFs are misted, poured, or blasted at
+high pressure onto work surfaces to remove debris, cool metal, improve
+efficiency, and prevent deterioration of tools. Although MWFs are
+essential to manufacturing processes, they also present a potential
+health hazard to exposed workers through inhalation or ingestion of MWF
+particulate mass.
+
+There are three general types of MWF: straight, soluble, and synthetic.
+The type of MWF applied has changed over the decades in response to
+engineering, economic, and health considerations. Straight MWF, the
+oldest class of MWF, is comprised mostly of mineral oils, which were
+classified as carcinogenic by the International Agency for Research on
+Cancer (IARC) in 1973, citing studies of occupational exposures among
+workers in oil, textile, and metal industries [@IARC_1973]. In the same
+decade, additional factors including the high cost of oil and the
+introduction of performance-enhancing water-soluble chemical additives
+spurred the gradual replacement of straight MWF with water-based soluble
+and synthetic MWF for many, but not all metalworking operations
+[@Childers_2005]. Although water-based MWFs contain little to no mineral
+oil, they contain a richer cocktail of additives including chromates,
+cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and
+triazines: classes of chemicals with known or plausible carcinogenicity
+[@IARC_1987; @IARC_2014; @IARC_2017]. As the US prepares for a boom in
+domestic automotive manufacturing, occupational exposure to MWF will
+remain an important concern for worker health [@Armbrust_2021;
+@Carr_2022; @Keilman_2023].
+
+One challenge in estimating the causal effects of occupational exposures
+on worker health is the Healthy Worker Survivor Effect (HWSE), the
+process by which healthier individuals remain at work where they
+accumulate more exposure while those more susceptible to the deleterious
+health effects leave work [@Arrighi_1994]. A well-known analytical
+method for causal inference in observational studies where the HWSE or
+other forms of time-varying confounding affected by past exposure may be
+operating is the parametric g-formula [@Robins_1986; @Taubman_2009;
+@Richardson_2013]. A central requirement necessary for causal
+interpretation of any analysis is positivity (overlap) ie adequate
+variation in the exposure of interest within strata formed by confounder
+and exposure history [@Petersen_2012]. Here, we specify hypothetical
+interventions on exposure to soluble MWF in the United Auto
+Workers-General Motors (UAW-GM) occupational cohort whose effects can be
+estimated with guaranteed positivity. In particular, we estimate the
+cumulative incidence of NHL between 1985 and 2015 under well-supported
+(supportable) interventions by applying the the hazard-extended
+iterative conditional expectation (ICE) parametric g-formula
+[@Arrighi_1994; @Wen_2021].
 
@@
 
-<!-- Here, we describe the hazard-extended ICE parametric g-formula, an extension of the ICE parametric g-formula for causal survival analyses, and apply it to estimate counterfactual cumulative incidences of non-Hodgkin lymphoma under hypothetical interventions on annual average daily exposure to soluble metalworking fluids (MWF) in the UAW-GM autoworkers cohort between 1984 and 2005.
-The interventions we evaluate are modified longitudinal treatment policies which depend on the natural value of exposure [@Taubman_2009;@Richardson_2013;@Haneuse_2013;@Young_2014;@Diaz_2021].
--->
-
 <!-- In recent years, there has been a surge in optimism for growth in American manufacturing [@Carr_2022;@Armbrust_2021].
@@
 
-Non-Hodgkin Lymphoma (NHL) incidence in the United States doubled between 1973 and 1994, before plateauing at around 19 per 100,000 persons per year, making it the seventh most common cancer in the country [@seer_1994;@Ekstrom-Smedby_2006].
-The strongest known risk factor of NHL is immunosuppression, both congenital and acquired [@Filipovich_1992;@Chiu_2015].
-Modulation of immune function contributes to the pathogenesis of NHL directly by perturbing lymphocyte function or indirectly by reducing immunosurveillance against neoplasms.
-Immunodeficiency may also interact with infection with Epstein-Barr Virus, resulting in uncontrolled B-cell proliferation [@Oertel_2002].
-Acquired immunodeficiency through infection with human immunodeficiency virus (HIV) can lead to genetic lesions and dysregulation while increasing vulnerability to infection by other oncogenic agents [@Grulich_1999;@Alexander_2007].
-However, since immunodeficiency and infection with HIV are rare, they cannot fully explain the historic rise or present burden of NHL [@Shiels_2013].
-The rise in NHL incidence coincided with a period of rapid and extensive chemicalization in industry, agriculture and warfare, suggesting that environmental and occupational exposures may have an important explanatory role in the epidemiology of NHL [@Nelson_2005;@Romero_2021].
-
-Pesticide exposure in agricultural occupational settings was a common target of NHL research in recent decades.
-A meta-analysis of 44 articles published between 1980 and 2014 found statistically significant associations between NHL and exposure to several classes of pesticides including carbamate, organophosporus, triazine, and organochlorine [@Schinasi_2014].
-Occupations associated with NHL are not limited to the agricultural sector, however.
-Metal processors, health workers, salespeople, machinists, and electricians have all been identified as occupational groups with higher risk of NHL [@Fritschi_2005a; @Mester_2006; @Ekstrom-Smedby_2006].
-Workers in these occupational groups often come into contact with industrial chemicals such as gasoline, solvents, coolants, and lubricants such as metalworking fluids.
-
-Metalworking fluids (MWF) are complex mixtures of oil, water, and chemical additives that optimize metal machining operations.
-During shaping, grinding, and cutting operations, MWF are misted, poured, or blasted at high pressure onto work surfaces to remove debris, cool metal, improve efficiency, and prevent deterioration of tools.
-Although MWFs provide essential engineering benefits to manufacturing processes, they may also present a potential health hazard to exposed workers, who may inhale or ingest aerosolized MWFs.
-There are three general types of MWF: straight, soluble, and synthetic.
-The type of MWF applied has changed over the decades in response to engineering, economic, and health considerations.
-
-Straight MWF, the oldest class of MWF, is comprised mostly of mineral oils, which were classified as carcinogenic by the International Agency for Research on Cancer (IARC) in 1973, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973].
-In the same decade, additional factors including the high cost of oil and the introduction of performance-enhancing water-soluble chemical additives spurred the gradual replacement of straight MWF with water-based soluble and synthetic MWFs for many, but not all metalworking operations [@Childers_2005].
-Although water-based MWF contain little to no mineral oil, they contain a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987;@IARC_2014;@IARC_2017].
-With policy makers and companies anticipating a boom in domestic manufacturing, occupational exposure to MWFs will remain an important concern for worker health in the US [@Armbrust_2021;@Carr_2022;@Keilman_2023].
-
-Here, we assess the effect of hypothetical MWF exposure limits on cumulative incidence of NHL from 1985 to 2014 in the United Auto Workers-General Motors (UAW-GM) occupational cohort study.
-A recent study of cancer incidence in this cohort linked NHL with exposure to soluble MWF in a Cox proportional hazards regression [@Colbeth_2023].
-Standard regression methods are vulnerable to downward bias due to the healthy worker survivor effect (HWSE), the process by which healthier individuals remain at work where they accumulate more occupational exposure.
-Therefore, we further explored this association using an estimator capable of adjusting for the HWSE and other sources of time-varying confounding and censoring affected by past exposure: the hazard-extended iterative conditional expectation (ICE) parametric g-formula [@Arrighi_1994;@Wen_2021].
-Like other causal estimators in statistics, the hazard-extended ICE g-formula yields marginal effect estimates of hypothetical interventions, which may be more interpretable under a population health framework than conditional measures.
-
-<!-- The healthy worker survivor effect (HWSE) is a key concern in occupational studies.
-The HWSE is the dynamic selection process by which healthier individuals remain at work, where they accumulate more occupational exposure, and less healthy individuals leave work [@Arrighi_1994].
-Standard analyses of occupational cohorts affected by the HWSE result in a downward bias on the exposure-outcome associations of interest, as less healthy workers typically accrue less exposure than healthier workers.
-One analytic approach for addressing potential bias due to the HWSE and other time-varying confounders affected by past exposure is the application of longitudinal causal estimators such as the parametric g-formula [@Taubman_2009].
--->
-
 # Methods
 
-We estimated NHL cumulative incidence from 1985 to 2014 under hypothetical limits on annual average daily exposure to soluble MWF by applying the hazard-extended ICE parametric g-formula estimator [@Wen_2020].
-First, we estimated the expected number of NHL cases that we would observe if there were no censoring by competing risks.
-Then, we contrasted this counterfactual cumulative incidence to that under interventions enforcing one of five hypothetical exposure limits in addition to no censoring, when positivity allows.
-The five limits we evaluated were (1) 2.0 mg/m^3^, (2) 1.0 mg/m^3^, (3) 0.5 mg/m^3^, (4) 0.25 mg/m^3^, and
-(5) 0.05 mg/m^3^.
-The National Institute for Occupational Safety and Health (NIOSH) Recommended Exposure Limit (REL) for total particulate mass (PM) composed of MWFs is 0.5 mg/m^3^ [@niosh_1998].
-These interventions reduce exposures above the hypothetical limit, but allow exposures below the limit to vary according to their natural distribution.
-To prevent extrapolation, interventions considered reduce above-limit exposures to the highest limit-abiding exposure observed among other workers in the study population with the same confounder and exposure history at that time.
-If no such peers existed, the above-limit exposures among those workers would retain their natural distribution.
-
-<!-- These interventions are known as threshold interventions that depend on the natural value of exposure.
-In general, threshold interventions set exposure to the hypothetical limit of interest when the natural value of exposure is beyond the threshold.
-Otherwise, these interventions leave exposure at the natural value.
-Such interventions are analogous to longitudinal stochastic interventions where the intervention distribution of exposure is the distribution of exposure induced by the threshold intervention rule [@Taubman_2009;@Young_2014;@Diaz_2021].
--->
+We estimated NHL cumulative incidence from 1985 to 2015 under
+supportable interventions on average daily exposure to soluble MWF by
+applying the hazard-extended ICE parametric g-formula estimator
+[@Wen_2020]. First, we estimated the expected number of NHL cases that
+we would observe if there were no censoring by competing risks. Then, we
+contrasted this case count to that under supportable interventions based
+on five hypothetical target exposure limits and no competing risks. The
+five target exposure limits were (1) 2.0, (2) 1.0, (3) 0.5, (4) 0.25,
+and (5) 0.05 mg/m^3^. The National Institute for Occupational Safety and
+Health (NIOSH) recommended exposure limit (REL) for total particulate
+mass (PM) composed of MWF is 0.5 mg/m^3^ [@niosh_1998]. For each target
+exposure limit, period of follow-up, and unique combination of
+confounder and exposure histories, we also defined a supportable
+exposure limit, which was the maximum observed value of exposure at or
+below the target exposure limit or no limit when all of the observed
+values were above the target limit. For each target exposure limit, we
+specified an intervention rule that reduced exposures above the
+supportable exposure limit to that limit, but allowed exposures at or
+below the limit to vary according to their natural distribution.
+Applying this intervention rule to the observed distribution of exposure
+produced the intervention distribution that defined the stochastic
+dynamic intervention with guaranteed positivity.
 
@@
 
-We used data from the UAW-GM cohort, which included all hourly workers at three automobile manufacturing plants in Michigan who had worked at least three years by 1985.
-Past papers provide detailed descriptions of the cohort [@Eisen_1992;@Eisen_2001].
-The large size of the study population and rich time-varying, quantitative MWF exposure data provide an opportunity to study a relatively rare cancer and evaluate realistic interventions on MWF exposure in a longitudinal cohort setting.
-The present study population (N = 33,134) was restricted to the autoworkers who were at work in 1941 or not yet hired, missing no more than half of their employment history, and still alive at the start of follow-up.
-Autoworkers in the study population were followed for NHL incidence from January 1, 1985 until NHL diagnosis, death, December 31, 2014 (20 years after the end of employment record availability), or the oldest observed age at death (108 years), whichever came earlier.
+We used data from the UAW-GM cohort, which included all hourly workers
+at three automobile manufacturing plants in Michigan who had worked at
+least three years by 1985. Past papers provide detailed descriptions of
+the cohort [@Eisen_1992; @Eisen_2001]. The large size of the study
+population and rich time-varying, quantitative MWF exposure data provide
+an opportunity to study this relatively rare cancer and evaluate
+realistic interventions on MWF exposure in a longitudinal cohort
+setting. The present study population (N = 33,134) was restricted to the
+autoworkers who were at work in 1941 or not yet hired, missing no more
+than half of their employment history, and still alive at the start of
+follow-up. Autoworkers in the study population were followed for NHL
+incidence from January 1, 1985 until NHL diagnosis, death, December 31,
+2014 (30 years after the end of employment record availability), or the
+oldest observed age at death (108 years), whichever came earlier.
 
@@
 
-We identified incident cancers in the UAW-GM cohort that occurred between 1985 and 2014 by linkage to the Michigan Cancer Registry (MCR).
-Workers at Plants 1 and 2, located in the greater Detroit metropolitan area, were also linked to the Detroit Regional Registry of the Surveillance, Epidemiology, and End Results (SEER) Program.
-Cancer types were distinguished using site and histology codes conforming to the International classification of Diseases for Oncology, 3^rd^ edition (ICD-O-3).
-Non-Hodgkin lymphoma was defined by cancers with any of the following ICD-O-3 Histology codes: 9590-9597, 9670-9671, 9673, 9675, 9678-9680, 9684, 9687-9691, 9695, 9698-9702, 9705, 9708-9709, 9712, 9714-9719, 9724-9729, 9735, 9737-9738, 9811-9818, 9823, 9827, 9837.
-Details regarding cancer incidence follow-up are described elsewhere [@Colbeth_2023].
-Vital status was ascertained from company records and by linkage to Social Security Administration, National Death Index, and state mortality files.
+We identified incident cancers in the UAW-GM cohort between 1985 and
+2014 by linkage to the Michigan Cancer Registry (MCR). Workers at Plants
+1 and 2, located in the greater Detroit metropolitan area, were also
+linked to the Detroit Regional Registry of the Surveillance,
+Epidemiology, and End Results (SEER) Program. Cancer types were
+distinguished using site and histology codes conforming to the
+International classification of Diseases for Oncology, 3^rd^ edition
+(ICD-O-3). Non-Hodgkin lymphoma was defined by cancers with any of the
+following ICD-O-3 histology codes: 9590-9597, 9670-9671, 9673, 9675,
+9678-9680, 9684, 9687-9691, 9695, 9698-9702, 9705, 9708-9709, 9712,
+9714-9719, 9724-9729, 9735, 9737-9738, 9811-9818, 9823, 9827, 9837.
+Details regarding cancer incidence follow-up are described elsewhere
+[@Colbeth_2023]. Vital status was ascertained from company records and
+by linkage to Social Security Administration, National Death Index, and
+state mortality files.
 
-Covariates including year of hire, sex, race, and plant location were obtained from company records.
-Race was missing for about 16% of the cohort, most commonly among workers hired before 1960 in Plant 2.
-In analyses, missing race was considered a distinct category.
-All covariates were coded as categorical variables.
-Cut-points for categorizing continuous covariates were determined according to the quantiles among cases.
+Potential confounders including year of hire, sex, race, time off,
+employment status, and plant location were obtained from company
+records. Race was missing for about 16% of the cohort, most commonly
+among workers hired before 1960 in Plant 2. In analyses, missing race
+was considered a distinct category. All potential confounders were coded
+as categorical variables. Cut-points for categorizing continuous
+covariates were determined according to the quantiles among cases.
 
@@
 
-Quantitative measurement of time-varying MWF exposure is a distinguishing strength of the UAW-GM cohort study relative to other occupational cohort studies.
-Exposure assessment was based on direct air sampling as well as company records.
-Company industrial hygienists collected several hundred personal and area samples for total particulate matter (mg/m^3^) composed of MWF over many decades.
-Research industrial hygienists collected additional air sampling data when the cohort study was launched in the mid 1980s.
-These additional data were combined with the historical data and company records to construct a job-exposure matrix of quantitative 8-hour time-weighted average daily exposure estimates to soluble, straight, and synthetic MWFs for each combination of job, department, and plant over time.
-Workers' time-weighted annual average daily exposure to each MWF type was determined by combining this job-exposure matrix with employment records, which recorded time-varying job type, department, and plant for each employee from hire to termination or 1994, whichever came sooner.
-For employment records that were at least half complete, gaps in the record were interpolated by carrying forward the last known job type.
-The exposure assessment is described in detail elsewhere [@Hallock_1994;@Woskie_1994;@Woskie_2003].
+Quantitative measurement of time-varying MWF exposure is a
+distinguishing strength of the UAW-GM cohort study relative to other
+occupational cohort studies. Exposure assessment was based on direct air
+sampling as well as company records. Company industrial hygienists
+collected several hundred personal and area samples for total
+particulate matter (mg/m^3^) composed of MWF over many decades. Research
+industrial hygienists collected additional air sampling data when the
+cohort study was launched in the mid 1980s. These additional data
+combined with historical data and company records constituted a
+job-exposure matrix of quantitative 8-hour time-weighted average daily
+exposure estimates to soluble, straight, and synthetic MWF for each
+combination of job, department, and plant over time. Workers' average
+daily exposure to each MWF type was determined by combining this
+job-exposure matrix with employment records, which recorded time-varying
+job type, department, and plant for each employee from hire to
+termination or 1995, whichever came sooner. For employment records that
+were at least half complete, gaps in the record were interpolated by
+carrying forward the last known job type. The exposure assessment is
+described in detail elsewhere [@Hallock_1994; @Woskie_1994;
+@Woskie_2003].
 
-Previous analyses of NHL applied exposure lags of 1 to 20 years to account for disease latency; we lagged cumulative MWF exposures by 20 years and therefore ended follow-up on January 1, 2015 [@Smith_2007;@Karipidis_2007;@Zhang_2019].
-In analyses, MWF exposure at start of follow-up was summarized as the cumulative sum of annual exposure intensities.
-Exposure was coded as categorical variables with cut-points at zero and the quintiles of exposure among cases.
-In analyses, we estimated the effects of interventions on soluble MWF while treating exposure to straight and synthetic MWFs as potential confounders.
+Previous analyses of NHL applied exposure lags of 1 to 20 years to
+account for disease latency; we lagged cumulative MWF exposures by 20
+years and therefore ended follow-up on January 1, 2015 [@Smith_2007;
+@Karipidis_2007; @Zhang_2019]. In analyses, MWF exposure history at
+start of follow-up was summarized as the cumulative sum of annual
+exposure intensities. Exposure was coded as categorical variables with
+cut-points at zero and the quintiles of nonzero exposure among cases. We
+estimated the effects of interventions on soluble MWF, the type of MWF
+used most widely and in the greatest quantities. We treated exposure to
+straight and synthetic MWF as potential confounders.
 
@@
 
-We split the 30-year follow-up period into ten time periods based on the deciles of the dates of diagnosis of NHL.
-The number of years per period range from two  to four years.
-The hazard-extended ICE parametric g-formula involves two stages.
-In the first, we estimate counterfactual discrete hazards over the person-periods.
-In the second, we pool those estimates to estimate counterfactual risk over the entire follow-up period.
-During pooling, we iteratively combine estimates of the counterfactual hazard starting with the last two periods, then the last three, then the last four, and so forth.
-In each iteration, we perform model-based standardization over exposure and covariate histories before combining the counterfactual discrete hazard with that pooled over subsequent periods.
-This iterative process results in a sequentially standardized estimate of NHL cumulative incidence over the entire follow-up period under the post-intervention distribution of exposure.
+We split the 30-year follow-up period into ten time periods based on the
+deciles of the dates of diagnosis of NHL. The number of years per period
+ranged from two to four years. The hazard-extended ICE parametric
+g-formula involved two stages. In the first, we estimated counterfactual
+discrete hazards over the person-periods. In the second, we pooled those
+estimates to estimate the counterfactual risk over the entire follow-up
+period. During pooling, we iteratively combined estimates of the
+counterfactual hazard starting with the last two periods, then the last
+three, then the last four, and so forth. In each iteration, we performed
+model-based standardization over exposure and covariate histories before
+combining the counterfactual discrete hazard with the risk over
+subsequent periods. This iterative process resulted in a sequentially
+standardized estimate of the counterfactual cumulative incidence of NHL
+when the intervention of interest is enforced over all follow-up
+periods. We took exposure to straight and synthetic MWF, employment
+status, cumulative time off, age, duration of employment, sex
+(male/female), race (Black/white/unknown), and plant (Plant 1/Plant
+2/Plant 3) to be potential confounders. Exposure to MWF, employment
+status, time off, and duration of employment were lagged 20 years. An
+overview of the general steps of the estimation procedure are presented
+below. Note that we refer to discrete hazards simply as hazards.
 
-At the start of follow-up and in the first stage of estimation, we summarized history of exposure to soluble MWF as the cumulative sum of average daily exposure.
-In the first stage, we fitted a pooled logistic regression for NHL over at-risk person-periods given cumulative exposure to straight, soluble, and synthetic MWFs, employment status, cumulative time off, age, duration of employment, sex (male/female), race (Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3).
-Exposure to MWFs, employment status, time off, and duration of employment were lagged 20 years.
-All continuous variables were represented as categorical variables with cut points determined by the quantiles of nonzero values among NHL cases.
-In the second stage, we conducted model-based standardization using logistic regression on the entire set of exposure and covariate histories.
-An overview of the general steps of the estimation procedure are presented below.
-Note that we refer to discrete hazards simply as hazards.
+1.  Fit a pooled logistic regression of NHL on covariates and exposure
+    over all at-risk person-periods.
 
-1.  Fit a pooled logistic regression of NHL on covariates
-		and exposure over all at-risk person-periods.
-2.  Predict the hazard for each person-period for each possible level of exposure
-		using the model from step 1.
-3.  Within strata formed by unique combinations of covariates, obtain the
-    post-intervention distribution of exposure by applying the intervention rule
-    to the observed exposure distribution.
+2.  Predict the hazard for each person-period for each possible level of
+    exposure using the model from step 1.
+
+3.  Within strata formed by unique combinations of covariates, obtain
+    the intervention distribution of exposure by applying the
+    intervention rule to the observed exposure distribution.
+
 4.  Within strata, estimate the counterfactual hazard for each
-		person-period by taking a weighted sum of the predicted hazards from step 2.
+    person-period by taking a weighted sum of the predicted hazards from
+    step 2.
+
 5.  Starting at the penultimate period of follow-up, estimate the pooled
@@
 
-    a)  Regress the counterfactual hazard pooled over all subsequent periods on
-        exposure and covariate history at the current period.
-    b)  Predict the pooled hazard for each person at risk at the start of the
-    		period and each possible level of exposure using the model from (a).
-    		Retrieve the predicted hazards from step 2. For each person and level
-    		of exposure, multiply the predicted pooled hazard by one minus the 
-    		corresponding predicted hazard and add the predicted hazard to the
-    		product.
-    c)  Within strata formed by exposure and covariate history, obtain the
-        post-intervention distribution of exposure by applying the 
+    a)  Regress the counterfactual hazard pooled over all subsequent
+        periods on exposure and covariate history at the current period.
+    b)  Predict the pooled hazard for each person at risk at the start
+        of the period and each possible level of exposure using the
+        model from (a). Retrieve the predicted hazards from step 2. For
+        each person and level of exposure, multiply the predicted pooled
+        hazard by one minus the corresponding predicted hazard and add
+        the predicted hazard to the product.
+    c)  Within strata formed by exposure and covariate history, obtain
+        the intervention distribution of exposure by applying the
         intervention rule to the observed exposure distribution.
-    d)  Within strata, estimate the counterfactual hazard pooled over the present
-    		and subsequent periods for each person by taking a weighted sum of the
-    		predicted pooled hazards from (b).
-    e)  If the present period is not first period, set the reference period to the
-    		preceding period and return to (a).
+    d)  Within strata, estimate the counterfactual hazard pooled over
+        the present and subsequent periods for each person by taking a
+        weighted sum of the predicted pooled hazards from (b).
+    e)  If the present period is not first period, set the reference
+        period to the preceding period and return to (a).
 
-6.  Compute the counterfactual risk by averaging the counterfactual hazard over
-		the entire follow-up period across all persons.
+6.  Compute the counterfactual risk by averaging the counterfactual
+    hazard over the entire follow-up period across all persons.
 
-To account for censoring, fit the models in step 1 and step 5a among those who were
-not censored and obtain predicted hazards for all at-risk person-periods, including
-those that were censored.
+To account for censoring, fit the models in step 1 and step 5a among
+those who were not censored and obtain predicted hazards for all at-risk
+person-periods, including those that were censored.
 
-We estimated cumulative incidence under the observed distribution of soluble MWF exposure (natural course) and under the six interventions.
-We contrasted the cumulative incidence under intervention to that under the natural course by computing the number of cases averted and the cumulative incidence ratios.
-Confidence intervals were computed using the basic nonparametric bootstrap with 1000 Monte Carlo samples from the population at the start of follow-up.
-All the necessary script used to reproduce the analyses are available on [GitHub](https://github.com/kvntchn/gm-nhl-ice).
+We estimated cumulative incidence under the observed distribution of
+soluble MWF exposure (natural course) and under the five supportable
+exposure limits. We contrasted the cumulative incidence under
+supportable limits to that under the natural course by computing the
+number of cases averted and the cumulative incidence ratios. Confidence
+intervals were computed using the basic nonparametric bootstrap with
+1000 Monte Carlo samples from the population at the start of follow-up.
+All the necessary script used to reproduce the analyses are available on
+[GitHub](https://github.com/kvntchn/gm-nhl-ice).
 
@@
 
-Table 1 presents summary statistics of exposure and covariates for the full study population and for those diagnosed with NHL between 1985 and 2005.
-The cohort is predominantly white (66%) and male (87%).
-The median year of hire among those diagnosed with NHL was 1959 whereas the median year of hire in the full study population was almost a decade later.
-Age at hire was approximately the same among those with NHL and the full study population.
-Median lagged cumulative exposure to all three MWF types was higher among NHL cases.
-Soluble MWFs were the most widely used MWF type, with approximately 90% of workers ever exposed.
-Median cumulative exposure among the exposed was 6.5 times higher for soluble than for straight MWFs.
-Figure 1 shows median annual average daily exposure to the three MWF types among exposed workers over calendar time.
-Exposure to MWF generally followed a downward trend over time.
+Table 1 presents summary statistics of exposure and covariates for the
+full study population and for those diagnosed with NHL between 1985 and
+2005. The cohort is predominantly white (66%) and male (87%). The median
+year of hire among those diagnosed with NHL was 1959 whereas the median
+year of hire in the full study population was almost a decade later. Age
+at hire was approximately the same among those with NHL and the full
+study population. Median lagged cumulative exposure to all three MWF
+types was higher among NHL cases. Soluble MWF were the most widely used
+MWF type, with approximately 90% of workers ever exposed. Median
+cumulative exposure among the exposed was 6.5 times higher for soluble
+than for straight MWF. Figure 1 shows median annual average daily
+exposure to the three MWF types among exposed workers over calendar
+time. Exposure to MWF generally followed a downward trend over time.
 
@@
     i = grep("Cumulative exposure", rownames(tab1)), j = 1,
-    value = as_paragraph("Cumulative exposure to MWFs (mg/m",
+    value = as_paragraph("Cumulative exposure to MWF (mg/m",
                          as_sup("3"), "-years)")) |>
@@
 ```
+
 \
 
-![Figure 1. Median annual average daily exposure to soluble, straight, and synthetic metalworking fluids among exposed workers over time.](../../resources/images/exposure.png){width=6.5in}
+![Figure 1. Median annual average daily exposure to soluble, straight,
+and synthetic metalworking fluids among exposed workers over
+time.](../../resources/images/exposure.png){width="6.5in"}
 
@@
 ```
+
 ```{r}
@@
 
-The observed number of NHL cases over the 20-year follow-up period was 231 (corresponding to a 20-year risk of 6.65 per 1000).
-Table 2 presents the hazard-extended ICE parametric g-formula estimates of the counterfactual number of cases, number of cases averted, and cumulative incidence ratios contrasting hypothetical limits on exposure to soluble MWF to no limit, after elimination of competing risks.
-Under an intervention eliminating competing risks, the estimated number of cases under no limit on MWF exposure was 332 (285, 380).
-Stronger limits on annual average daily exposure to soluble MWFs resulted in monotonically stronger reductions in the cumulative incidence of NHL.
-Capping annual average daily exposure to soluble MWFs at 0.5 mg/m^3^, 0.25 mg/m^3^, and 0.05 mg/m^3^ resulted in 44 (-6, 91), 52 (-5, 106), and 71 (12, 129) fewer NHL cases, respectively.
-These correspond to cumulative incidence ratios 0.87 (0.73, 1.02), 0.84 (0.68, 1.01), and 0.79 (0.61, 0.97).
+The observed number of NHL cases over the 30-year follow-up period was
+339. Table 2 presents the hazard-extended ICE parametric g-formula
+estimates of the counterfactual number of cases, number of cases
+averted, and cumulative incidence ratios contrasting hypothetical
+interventions on exposure to soluble MWF based on different target
+exposure limits and no competing risks. Under an intervention
+eliminating competing risks, the estimated number of cases was 502 (95%
+CI: 439, 555). Interventions based on stronger limits on average daily
+exposure to soluble MWF resulted in monotonically stronger reductions in
+the estimated cumulative incidence of NHL. Setting the target exposure
+limit at the NIOSH REL 0.5 mg/m^3^ would have averted 112 (95% CI: 57,
+181) NHL cases.
 
 ```{r, eval=F}
-tikzDevice::tikz(here::here("reports/ACIC (2022)/poster/resources/rr.tex"),
-                 width = 4, height = 1.75,
-                 standAlone = T)
-contrasts.tab[grepl("sol|natural\\.Any", variable) & !grepl(
-  "[a-z]", label),] |> ggplot(
-    aes(x = factor(label, rev(c("0.5", "0.25", "0.05"))),
-        y = rd, ymin = rd_lower, ymax = rd_upper)
+tikzDevice::tikz(here::here("reports/private/SER (2023)/resources/rd.tex"),
+                 width = 3.75, height = 2.25,
+								 documentDeclaration = "\\documentclass{beamer}",
+                 bareBones = T)
+contrasts.tab[,.(
+     label,
+     # `Person-years intervened (%)` = clean_percent_py(variable),
+     `Cases averted`    = rd * N,
+     rd_lower,
+     rd_upper,
+     result = paste0(
+     	round(rd * N),
+     	" (", round(rd_lower), ", ", round(rd_upper), ")")
+   )][c(6, 3, 2, 5, 4, 1),] -> gg.tab 
+gg.tab[label != "None"] |> ggplot(
+    aes(x = factor(
+    	label,
+    	levels = c("0.05", "0.25", "0.5", "1.0", "2.0",  "None"),
+    	labels = c("0.05", "0.25", "0.50", "1.00", "2.00",  "None")),
+        y = `Cases averted`, ymin = rd_lower, ymax = rd_upper)
   ) +
-  geom_errorbar(linewidth = 0.5, width = 0.15, color = '#102451') +
-  geom_point(size = 0.9, color = '#102451') + 
-  geom_hline(yintercept = 1, lty = 2, color = '#102451', alpha = 0.7) +
+	geom_label(aes(y = 270, label = result), size = 8/.pt, 
+						 label.padding = unit(5, "pt")) +
+  geom_errorbar(linewidth = 4 / .pt, width = 0.15, color = '#003c61') +
+  geom_point(size = 4 / .pt, color = '#003c61') + 
+  geom_hline(yintercept = 0, lty = 2, , alpha = 0.7) +
   labs(
     y = "Cases averted",
-    x = "Hypothetical limit (mg/m$^3$)") +
+    x = "Target limit (mg/m$^3$)") +
   mytheme +
-  coord_flip(ylim = c(-15, 130)) +
-  theme(panel.grid = element_blank())
+  coord_flip(ylim = c(-10, 320)) +
+  theme(panel.grid = element_blank(),
+  			axis.text = element_text(size = 9, colour = 'black'),
+  			panel.border = element_rect(colour = "black", size = 0.75),
+  			axis.title.y = element_text(size = 9, margin = margin(r = 6)),
+  			axis.title.x = element_text(size = 9, margin = margin(t = 6)),
+  			plot.margin = margin(l = 6, r = 6)
+  )
 dev.off()
-
-lualatex(directory = here::here("reports/ACIC (2022)/poster/resources"))
 ```
@@
 
-Although NIOSH concluded that there exists substantial evidence linking MWF exposure to several different cancers, their REL of 0.5 mg/m^3^ for total particulate matter derived from any type of MWF targeted risk of acute respiratory disorders rather than on cancer [@niosh_1998;@Mirer_2003].
-Hence, they may be inadequate for protecting against cancer risk.
-Using the hazard-extended ICE parametric g-formula, We estimated the counterfactual expected number of NHL cases from 1985 to 2005 in the UAW-GM cohort if annual average daily exposure to soluble MWF were limited to the NIOSH REL, half the REL, and a tenth of the REL and found a monotonic exposure-dependent relationship with lower cumulative incidence estimates arising from stronger limits.
+Although NIOSH concluded that there exists substantial evidence linking
+MWF exposure to several different cancers, their REL of 0.5 mg/m^3^ for
+total particulate matter derived from any type of MWF targeted risk of
+respiratory disorders rather than cancer [@niosh_1998; @Mirer_2003].
+Exposure limits stronger than the NIOSH REL may provide additional
+health protections not previously considered by policy makers. Using the
+hazard-extended ICE parametric g-formula, We estimated the
+counterfactual expected number of NHL cases from 1985 to 2015 in the
+UAW-GM cohort if we enforced exposure limits based on five different
+target exposure limits and found a monotonic exposure-dependent
+relationship where stronger target exposure limits yielded lower NHL
+case count estimates.
 
-The g-formula is a well-known approach in causal inference used for the identification of causal effects in the presence of time-varying confounding affected by past exposure [@Robins_1986].
-Standard representations of the g-formula include (1) a non-iterated expectation over the joint density of covariates, (2) the ICE over time, and (3) an inverse probability weighted expectation.
-The parametric g-formula is a plug in estimator for the g-formula under its first, non-iterative, representation.
-It involves the parametric modeling of the full joint distribution of the outcome, exposure, and covariates under study for each time point [@Taubman_2009;@Young_2014].
-Counterfactual quantities under hypothetical interventions of interest are computed from Monte Carlo samples from distributions implied by the fitted parametric models.
-In longitudinal settings, this approach often requires specifying and fitting large number of models in order to satisfy the exchangeability assumptions necessary for causal identification.
+The g-formula is a well-known approach in causal inference used for the
+identification and estimation of causal effects in the presence of
+time-varying confounding affected by past exposure [@Robins_1986].
+Standard representations of the g-formula include (1) a non-iterated
+expectation over the joint density of covariates, (2) the ICE over time,
+and (3) an inverse probability weighted expectation. The parametric
+g-formula is a plug in estimator for the g-formula under its first,
+non-iterative, representation. It involves the parametric modeling of
+the full joint distribution of the outcome, exposure, and covariates
+under study for each time point [@Taubman_2009; @Young_2014].
+Counterfactual quantities under hypothetical interventions of interest
+are computed from Monte Carlo samples from distributions implied by the
+fitted parametric models. In longitudinal settings, this approach often
+requires specifying and fitting large number of models in order to
+satisfy the exchangeability assumptions necessary for causal
+identification.
 <!-- Since applications of the parametric g-formula are often context-laden, there are no unified guidelines for model specification. -->
 
-Parametric estimators using the ICE representation of the g-formula require modeling only the conditional outcome distributions, so they require fewer parametric assumptions than non-iterative parametric g-formula estimators.
-Counterfactual outcome estimates over the follow-up period are computed from interval-specific conditional estimates by applying the tower rule of expectation.
-Under the assumptions of conditional exchangeability at all time points, positivity, counterfactual consistency, and correct model specification, the hazard-extended parametric g-formula yields unbiased estimates of counterfactual risk with greater statistical efficiency than both propensity score-based estimators and the classical ICE g-formula.
+Parametric estimators using the ICE representation of the g-formula
+require modeling only the conditional outcome distributions, so they
+require fewer parametric assumptions than non-iterative parametric
+g-formula estimators. Counterfactual outcome estimates over the
+follow-up period are computed from interval-specific conditional
+estimates by applying the tower rule of expectation. Under the
+assumptions of conditional exchangeability at all time points,
+positivity, counterfactual consistency, and correct model specification,
+the hazard-extended parametric g-formula yields unbiased estimates of
+counterfactual risk with greater statistical efficiency than both
+propensity score-based estimators and the classical ICE g-formula.
 
-Under the assumptions of conditional exchangeability, positivity, consistency, and correct model specification, our estimates are unbiased for the true counterfactual risk under the hypothetical interventions.
-Conditional exchangeability means that for all time points, there is no confounding of the relationship between exposure/censoring and both future exposure/censoring and NHL status given the observed past, including past exposure and covariates [@Richardson_2013;@Diaz_2021].
-A major threat to conditional exchangeability in longitudinal occupational studies is the HWSE.
-We limit potential bias due to the HWSE by conditioning on cumulative exposure, employment status, and cumulative time off history at each time point.
-Cumulative time off and employment status are reasonable mediators of the causal paths linking past health to future exposure and health, but adjustment for these variables may not be sufficient for eliminating bias due to the HWSE.
-Declines in a worker's health may lead to reductions in work-related exposure without affecting employment status or time off work [@Garcia_2017].
-We expect the absence of time-varying measures of worker health over the life course to result in bias toward the null.
+Conditional exchangeability means that for all time points, there is no
+confounding of the relationship between exposure/censoring and both
+future exposure/censoring and NHL status given the observed past,
+including past exposure and covariates [@Richardson_2013; @Diaz_2021]. A
+major threat to conditional exchangeability in longitudinal occupational
+studies is the HWSE. We limit potential bias due to the HWSE by
+conditioning on cumulative exposure, employment status, and cumulative
+time off history at each time point. Cumulative time off and employment
+status are reasonable mediators of the causal paths linking past health
+to future exposure and health, but adjustment for these variables may
+not be sufficient for eliminating bias due to the HWSE. Declines in a
+worker's health may lead to reductions in work-related exposure without
+affecting employment status or time off work [@Garcia_2017]. We expect
+the absence of time-varying measures of worker health over the life
+course to result in bias toward the null.
 
-Positivity refers to the need for adequate variation in future exposure among strata formed by observed covariate and intervention-compliant exposure histories.
-Even under conditional exchangeability, where exposures within these strata may be considered the result of experimental assignment, expected counterfactual outcomes under different exposures may not be estimable if there is excessive sparsity in the observed distribution of exposures [@Maldonado_2002].
-We investigated static and dynamic stochastic interventions on soluble MWF exposure that intervened only when annual average daily exposure exceeded the hypothetical limit under consideration.
-Hence, our parameters of interest achieve positivity more easily than those for static deterministic interventions e.g.
-setting all to a single level of exposure.
-Nonetheless, violations in positivity were still of concern due to the high dimensionality of covariates, as is common in longitudinal settings.
-We addressed sparsity by summarizing the 20 years of follow-up over a coarser timescale with only 8 follow-up periods and by representing covariates using fewer categories.
-Coarsening limits the comprehensiveness of confounding control, but improves positivity.
-In practice, causal inference using observational data must always balance positivity, covariate adjustment, and model specification [@Petersen_2012].
+Positivity refers to the need for adequate variation in future exposure
+among strata formed by observed covariate and intervention-compliant
+exposure histories. Even under conditional exchangeability, where
+exposures within these strata may be considered the result of
+experimental assignment, expected counterfactual outcomes under
+different exposures may not be estimable if there is excessive sparsity
+in the observed distribution of exposures [@Maldonado_2002]. We
+investigated static and dynamic stochastic interventions on soluble MWF
+exposure that intervened only when average daily exposure exceeded the
+hypothetical limit under consideration. Hence, our parameters of
+interest achieve positivity more easily than those for static
+deterministic interventions e.g. setting all to a single level of
+exposure. Nonetheless, violations in positivity were still of concern
+due to the high dimensionality of covariates, as is common in
+longitudinal settings. We addressed sparsity by summarizing the 20 years
+of follow-up over a coarser timescale with only 8 follow-up periods and
+by representing covariates using fewer categories. Coarsening limits the
+comprehensiveness of confounding control, but improves positivity. In
+practice, causal inference using observational data must always balance
+positivity, covariate adjustment, and model specification
+[@Petersen_2012].
 <!-- When estimating causal effects using estimators that do not require exposure modeling, as is the case with ICE g-formula methods, concerns over potential bias due to practical violations in positivity may be relaxed if correct model specification, discussed below, is attained.
@@
 
-The consistency assumption, also known as the no-multiple-versions-of-treatment or stable unit treatment value assumption, is that counterfactual outcomes under each possible exposure value take on a unique value [@Cole_2009;@VanderWeele_2013].
-This assumption would be violated if there were multiple versions of treatment causally associated with different outcomes.
-This basic notion of consistency is violated in our analysis because our exposure of interest is a complex mixture of diverse components with substantial variation over time due to changes in formulation as well as the natural physical, chemical, and biological changes in the MWF over the course of its use and reuse [@Howell_2006].
-However, causal effect estimates under violations in the consistency assumption are still valid and unbiased if there is adequate adjustment for confounders of the exposure-version relationship [@VanderWeele_2013].
-This may be thought of as conditional consistency within strata, in which there is only one version of treatment.
-Our analysis indexed time periods over calendar time and adjusted for age, year of hire, and plant.
-In this way, we limited potential for bias due to variation in MWF composition.
+The consistency assumption, also known as the
+no-multiple-versions-of-treatment or stable unit treatment value
+assumption, is that counterfactual outcomes under each possible exposure
+value take on a unique value [@Cole_2009; @VanderWeele_2013]. This
+assumption would be violated if there were multiple versions of
+treatment causally associated with different outcomes. This basic notion
+of consistency is violated in our analysis because our exposure of
+interest is a complex mixture of diverse components with substantial
+variation over time due to changes in formulation as well as the natural
+physical, chemical, and biological changes in the MWF over the course of
+its use and reuse [@Howell_2006]. However, causal effect estimates under
+violations in the consistency assumption are still valid and unbiased if
+there is adequate adjustment for confounders of the exposure-version
+relationship [@VanderWeele_2013]. This may be thought of as conditional
+consistency within strata, in which there is only one version of
+treatment. Our analysis indexed time periods over calendar time and
+adjusted for age, year of hire, and plant. In this way, we limited
+potential for bias due to variation in MWF composition.
 
-Correct model specification is a standard assumption in all parametric and semi-parametric analyses.
-The estimator we applied offers greater statistical efficiency than the classical ICE parametric g-formula estimator because it leverages greater parametric smoothing.
-In causal analyses of longitudinal cohort studies, both the hazard-extended and classical ICE parametric g-formula estimators are less common than the NICE parametric g-formula [@Keil_2014].
-However, a major limitation of the NICE g-formula is the g-null paradox: the guaranteed misspecification of parametric models resulting in the false rejection of the null hypothesis when the null is true and when there is time-varying confounding affected by past exposure [@Naimi_2015;@McGrath_2022].
-As with all ICE g-formula estimators, the estimator we applied is not subject to the g-null paradox.
-Furthermore, simulation studies show that the variance of the hazard-extended ICE parametric g-formula is similar to that of the NICE parametric g-formula, so we expect the former to be no less conservative than the latter [@Wen_2020].
+Correct model specification is a standard assumption in all parametric
+and semi-parametric analyses. The estimator we applied offers greater
+statistical efficiency than the classical ICE parametric g-formula
+estimator because it leverages greater parametric smoothing. In causal
+analyses of longitudinal cohort studies, both the hazard-extended and
+classical ICE parametric g-formula estimators are less common than the
+NICE parametric g-formula [@Keil_2014]. However, a major limitation of
+the NICE g-formula is the g-null paradox: the guaranteed
+misspecification of parametric models resulting in the false rejection
+of the null hypothesis when the null is true and when there is
+time-varying confounding affected by past exposure [@Naimi_2015;
+@McGrath_2022]. As with all ICE g-formula estimators, the estimator we
+applied is not subject to the g-null paradox. Furthermore, simulation
+studies show that the variance of the hazard-extended ICE parametric
+g-formula is similar to that of the NICE parametric g-formula, so we
+expect the former to be no less conservative than the latter
+[@Wen_2020].
 
@@
 
-Much of the existing epidemiologic literature linking occupational and environmental exposures to NHL report findings from case-control studies where exposures are measured crudely as binary indicators of exposure or membership in a particular occupational group [@Cano_2001;@Costantini_2001;@Karunanayake_2008;@t-Mannetje_2016].
-Associations between occupations and NHL risk vary considerably, but one study of working men in Kansas and Nebraska found strong associations between NHL risk and occupations involving metalworking and motor vehicles [@Zheng_2002].
-Both of these occupations may entail exposure to soluble MWFs, which contain a number of additives of concern for human health and for NHL risk in particular.
-Organic compounds containing phosphorous, chlorine, sulfur, nitrogen, and boron are commonly added to soluble MWF to control microbial growth, improve performance under high heat/pressure, and inhibit corrosion [@Evans_2020].
-Organophosphorus compounds include organophosphate pesticides, which have been linked to cancer risk in epidemiologic and animal studies.
-Some were classified as possibly carcinogenic by the IARC [@IARC_2017].
-Studies of occupational exposure to chlorinated solvents and pesticides have also been linked to NHL risk [@Cocco_2008;@Purdue_2011;@Cocco_2013;@Vlaanderen_2013;@Callahan_2018].
-In 2014, the IARC classified trichloroethylene, tetrachloroethylene, and other chlorinated agents as Group 1 carcinogens [@IARC_2014].
-Chlorinated solvents are commonly used as degreasers in industrial settings, but their use in the plants under study here was rare [@Shrestha_2016].
-The structural characteristics shared by MWF additives and known/suspected carcinogens suggest potential similarities in their behavior in biological systems.
+Much of the existing epidemiologic literature linking occupational and
+environmental exposures to NHL report findings from case-control studies
+where exposures are measured crudely as binary indicators of exposure or
+membership in a particular occupational group [@Cano_2001;
+@Costantini_2001; @Karunanayake_2008; @t-Mannetje_2016]. Associations
+between occupations and NHL risk vary considerably, but one study of
+working men in Kansas and Nebraska found strong associations between NHL
+risk and occupations involving metalworking and motor vehicles
+[@Zheng_2002]. Both of these occupations may entail exposure to soluble
+MWF, which contain a number of additives of concern for human health and
+for NHL risk in particular. Organic compounds containing phosphorous,
+chlorine, sulfur, nitrogen, and boron are commonly added to soluble MWF
+to control microbial growth, improve performance under high
+heat/pressure, and inhibit corrosion [@Evans_2020]. Organophosphorus
+compounds include organophosphate pesticides, which have been linked to
+cancer risk in epidemiologic and animal studies. Some were classified as
+possibly carcinogenic by the IARC [@IARC_2017]. Studies of occupational
+exposure to chlorinated solvents and pesticides have also been linked to
+NHL risk [@Cocco_2008; @Purdue_2011; @Cocco_2013; @Vlaanderen_2013;
+@Callahan_2018]. In 2014, the IARC classified trichloroethylene,
+tetrachloroethylene, and other chlorinated agents as Group 1 carcinogens
+[@IARC_2014]. Chlorinated solvents are commonly used as degreasers in
+industrial settings, but their use in the plants under study here was
+rare [@Shrestha_2016]. The structural characteristics shared by MWF
+additives and known/suspected carcinogens suggest potential similarities
+in their behavior in biological systems.
 
-This study investigated the effect of hypothetical limits on MWF exposure by comparing the standardized distributions of NHL under various distributions of cumulative exposure induced by applying upper bounds to annual average daily exposure to soluble MWF.
-We selected these hypothetical limits based on the NIOSH REL of 0.5 mg/m^3^ [@niosh_1998].
-In the real world, there is no enforcement of the REL, but we nonetheless observed annual average daily exposures below the REL in these GM plants for many years.
-If the REL were enforced in the real world, we would not expect reductions in exposure for these low-exposure person-years.
-Hence, contrasting the counterfactual scenario where all workers experienced annual average daily exposure at the REL to one where all workers experienced annual average daily exposure at some higher level would result in an overestimate of the expected real-world benefit of REL enforcement.
+This study investigated the effect of hypothetical limits on MWF
+exposure by comparing the standardized distributions of NHL under
+various distributions of cumulative exposure induced by applying upper
+bounds to average daily exposure to soluble MWF. We selected these
+hypothetical limits based on the NIOSH REL of 0.5 mg/m^3^ [@niosh_1998].
+In the real world, there is no enforcement of the REL, but we
+nonetheless observed average daily exposures below the REL in these GM
+plants for many years. If the REL were enforced in the real world, we
+would not expect reductions in exposure for these low-exposure
+person-years. Hence, contrasting the counterfactual scenario where all
+workers experienced average daily exposure at the REL to one where all
+workers experienced average daily exposure at some higher level would
+result in an overestimate of the expected real-world benefit of REL
+enforcement.
 
 <!-- The interventions we considered are stochastic interventions resulting in post-intervention distributions of exposure that better reflect what we would expect if exposure limits were enforced in the real world.
-The interventions which ignore exposure to straight and synthetic MWFs are static.
+The interventions which ignore exposure to straight and synthetic MWF are static.
 The interventions which reduce exposure to soluble MWF by a quantity determined by exposure to other MWF are dynamic.
 The dynamic stochastic interventions respect the fact that the REL is for total MWF, not just soluble MWF.
-If an individual experienced a large amount of exposure to straight and synthetic MWF in one year, then their exposure to soluble MWF should be bounded at a lower level so that the sum of their exposure to soluble, straight, and synthetic MWFs is no greater than the hypothetical limit.
+If an individual experienced a large amount of exposure to straight and synthetic MWF in one year, then their exposure to soluble MWF should be bounded at a lower level so that the sum of their exposure to soluble, straight, and synthetic MWF is no greater than the hypothetical limit.
 -->
@@
 
-Associations between several occupations and risk of NHL have been reported previously, but none evaluated the potential effect of hypothetical limits on occupational exposures [@Ekstrom-Smedby_2006;@Chiu_2015;@t-Mannetje_2016;@Callahan_2018].
-We found evidence that exposure to soluble MWF was associated with NHL incidence after adjustment for time-varying confounding affected by prior exposure using the hazard-extended ICE parametric g-formula.
-Reducing cumulative exposure to soluble MWF by enforcing hypothetical, but realistic, interventions on annual average daily exposure would reduce NHL incidence.
+Associations between several occupations and risk of NHL have been
+reported previously, but none evaluated the potential effect of
+hypothetical limits on occupational exposures [@Ekstrom-Smedby_2006;
+@Chiu_2015; @t-Mannetje_2016; @Callahan_2018]. We found evidence that
+exposure to soluble MWF was associated with NHL incidence after
+adjustment for time-varying confounding affected by prior exposure using
+the hazard-extended ICE parametric g-formula. Reducing cumulative
+exposure to soluble MWF by enforcing hypothetical, but realistic,
+interventions on average daily exposure would reduce NHL incidence.
 \newpage
@@
 
-<div id="refs"></div>
+::: {#refs}
+:::

### 2023-06-12 illustrate-intervention-distribution.R

@@ -1,0 +1,293 @@
+# Figures for illustrating intervention ####
+# Kevin Chen
+# May 25, 2023
+
+library(here)
+library(boxr); box_auth()
+
+source("~/HeadRs/00-my-theme.R")
+options(
+	tikzLualatexPackages = c(
+		# "\\usepackage[utf8]{inputenc}",
+		"\\usepackage{amssymb}",
+		"\\usepackage{tikz}\n",
+		"\\RequirePackage[T1]{fontenc}\n",
+		"\\RequirePackage{lmodern}",
+		"\\usepackage[active,tightpage,psfixbb]{preview}\n",
+		"\\PreviewEnvironment{pgfpicture}\n",
+		"\\setlength\\PreviewBorder{0pt}\n",
+		# "\\input{\\string~/HeadRs/common_supplement.tex}\n",
+		# "\\input{\\string~/HeadRs/stathead.sty}\n",
+		NULL
+	)
+)
+
+# # Shape data
+# source(here::here("shape-data.R"))
+# dat <- box_read(1179471733155)
+# dat <- dat[yin.gm >= 1965]
+dat.reduced <- box_read(928445783979)
+N <- length(unique(dat.reduced[!is.na(I)]$studyno))
+message(sum(dat.reduced[!is.na(I)]$status))
+source(here("g-formula.R"))
+dat.reduced[,.(year1 = min(year), year2 = max(year)), I]
+
+followed.names <- c("followed_200", "followed_100", "followed_50",
+										"followed_25",  "followed_05",  "followed_025")
+covariates.which <- c(
+	followed.names,
+	"studyno", "I", "year", "immortal",
+	"status", "Censored", "Other event", "All causes",
+	"age.year2", "Age", "Age at hire",
+	"year2", "Year",
+	"straight", "soluble", "synthetic",
+	"Straight", "Soluble", "Synthetic",
+	"Cumulative straight", "Cumulative synthetic",
+	"Cumulative soluble", "Cumulative soluble shifted",
+	"Baseline cumulative soluble",
+	"Baseline cumulative straight",
+	"Baseline cumulative synthetic",
+	"cum_straight", "cum_soluble", "cum_synthetic",
+	"Employment status",
+	"Duration of employment", "employment.years",
+	"Cumulative time off", "cum_off",
+	"Year of hire", "yin.gm", "Sex", "Race", "Plant", 'py')
+
+dat.reduced[,`:=`(
[…]

### 2023-06-30 reports/SER (2023)/resources/intervention-density.tex
update paper

@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-08 17:09:01
+% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:02:21
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 36.40, 72.85) rectangle (265.01,195.13);
+\path[clip] ( 34.23, 80.08) rectangle (265.01,189.13);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 36.40, 72.85) rectangle (265.01,195.13);
+\path[fill=fillColor] ( 34.23, 80.08) rectangle (265.01,189.13);
 \definecolor{fillColor}{RGB}{163,207,235}
 
-\path[fill=fillColor] ( 46.79, 78.40) rectangle ( 58.33, 78.43);
+\path[fill=fillColor] ( 44.72, 85.04) rectangle ( 56.38, 85.06);
 
-\path[fill=fillColor] ( 58.33, 78.40) rectangle ( 69.88, 78.79);
+\path[fill=fillColor] ( 56.38, 85.04) rectangle ( 68.04, 85.38);
 
-\path[fill=fillColor] ( 69.88, 78.40) rectangle ( 81.43, 78.79);
+\path[fill=fillColor] ( 68.04, 85.04) rectangle ( 79.69, 85.38);
 
-\path[fill=fillColor] ( 81.43, 78.40) rectangle ( 92.97, 79.38);
+\path[fill=fillColor] ( 79.69, 85.04) rectangle ( 91.35, 85.91);
 
-\path[fill=fillColor] ( 92.97, 78.40) rectangle (104.52, 79.86);
+\path[fill=fillColor] ( 91.35, 85.04) rectangle (103.00, 86.33);
 
-\path[fill=fillColor] (104.52, 78.40) rectangle (116.06, 80.51);
+\path[fill=fillColor] (103.00, 85.04) rectangle (114.66, 86.91);
 
-\path[fill=fillColor] (116.06, 78.40) rectangle (127.61, 83.35);
+\path[fill=fillColor] (114.66, 85.04) rectangle (126.31, 89.45);
 
-\path[fill=fillColor] (127.61, 78.40) rectangle (139.16, 85.54);
+\path[fill=fillColor] (126.31, 85.04) rectangle (137.97, 91.40);
 
-\path[fill=fillColor] (139.16, 78.40) rectangle (150.70,103.29);
+\path[fill=fillColor] (137.97, 85.04) rectangle (149.62,107.23);
 
-\path[fill=fillColor] (150.70, 78.40) rectangle (162.25,102.34);
+\path[fill=fillColor] (149.62, 85.04) rectangle (161.28,106.39);
 
-\path[fill=fillColor] (162.25, 78.40) rectangle (173.80,189.57);
+\path[fill=fillColor] (161.28, 85.04) rectangle (172.93,184.17);
 
-\path[fill=fillColor] (173.80, 78.40) rectangle (185.34,123.53);
+\path[fill=fillColor] (172.93, 85.04) rectangle (184.59,125.28);
 
-\path[fill=fillColor] (185.34, 78.40) rectangle (196.89,106.28);
+\path[fill=fillColor] (184.59, 85.04) rectangle (196.25,109.90);
 
-\path[fill=fillColor] (196.89, 78.40) rectangle (208.44, 88.77);
+\path[fill=fillColor] (196.25, 85.04) rectangle (207.90, 94.28);
 
-\path[fill=fillColor] (208.44, 78.40) rectangle (219.98, 85.04);
+\path[fill=fillColor] (207.90, 85.04) rectangle (219.56, 90.96);
 
-\path[fill=fillColor] (219.98, 78.40) rectangle (231.53, 78.97);
+\path[fill=fillColor] (219.56, 85.04) rectangle (231.21, 85.54);
 
-\path[fill=fillColor] (231.53, 78.40) rectangle (243.07, 79.17);
+\path[fill=fillColor] (231.21, 85.04) rectangle (242.87, 85.72);
 
-\path[fill=fillColor] (243.07, 78.40) rectangle (254.62, 78.43);
+\path[fill=fillColor] (242.87, 85.04) rectangle (254.52, 85.06);
 \definecolor{drawColor}{RGB}{186,129,35}
 
-\path[draw=drawColor,line width= 3.2pt] ( 46.79, 78.40) rectangle ( 58.33, 78.43);
+\path[draw=drawColor,line width= 3.2pt] ( 44.72, 85.04) rectangle ( 56.38, 85.06);
 
-\path[draw=drawColor,line width= 3.2pt] ( 58.33, 78.40) rectangle ( 69.88, 78.73);
+\path[draw=drawColor,line width= 3.2pt] ( 56.38, 85.04) rectangle ( 68.04, 85.33);
 
-\path[draw=drawColor,line width= 3.2pt] ( 69.88, 78.40) rectangle ( 81.43, 78.76);
+\path[draw=drawColor,line width= 3.2pt] ( 68.04, 85.04) rectangle ( 79.69, 85.35);
 
-\path[draw=drawColor,line width= 3.2pt] ( 81.43, 78.40) rectangle ( 92.97, 79.20);
+\path[draw=drawColor,line width= 3.2pt] ( 79.69, 85.04) rectangle ( 91.35, 85.74);
 
-\path[draw=drawColor,line width= 3.2pt] ( 92.97, 78.40) rectangle (104.52, 79.47);
+\path[draw=drawColor,line width= 3.2pt] ( 91.35, 85.04) rectangle (103.00, 85.99);
 
-\path[draw=drawColor,line width= 3.2pt] (104.52, 78.40) rectangle (116.06, 79.85);
+\path[draw=drawColor,line width= 3.2pt] (103.00, 85.04) rectangle (114.66, 86.33);
 
-\path[draw=drawColor,line width= 3.2pt] (116.06, 78.40) rectangle (127.61, 82.26);
+\path[draw=drawColor,line width= 3.2pt] (114.66, 85.04) rectangle (126.31, 88.47);
 
-\path[draw=drawColor,line width= 3.2pt] (127.61, 78.40) rectangle (139.16, 83.65);
+\path[draw=drawColor,line width= 3.2pt] (126.31, 85.04) rectangle (137.97, 89.72);
 
-\path[draw=drawColor,line width= 3.2pt] (139.16, 78.40) rectangle (150.70, 93.74);
+\path[draw=drawColor,line width= 3.2pt] (137.97, 85.04) rectangle (149.62, 98.72);
 
-\path[draw=drawColor,line width= 3.2pt] (150.70, 78.40) rectangle (162.25, 93.20);
+\path[draw=drawColor,line width= 3.2pt] (149.62, 85.04) rectangle (161.28, 98.23);
 
-\path[draw=drawColor,line width= 3.2pt] (162.25, 78.40) rectangle (173.80,122.26);
+\path[draw=drawColor,line width= 3.2pt] (161.28, 85.04) rectangle (172.93,124.15);
 
-\path[draw=drawColor,line width= 3.2pt] (173.80, 78.40) rectangle (185.34,132.11);
+\path[draw=drawColor,line width= 3.2pt] (172.93, 85.04) rectangle (184.59,132.93);
 
-\path[draw=drawColor,line width= 3.2pt] (185.34, 78.40) rectangle (196.89,142.20);
+\path[draw=drawColor,line width= 3.2pt] (184.59, 85.04) rectangle (196.25,141.93);
 
-\path[draw=drawColor,line width= 3.2pt] (196.89, 78.40) rectangle (208.44,112.28);
+\path[draw=drawColor,line width= 3.2pt] (196.25, 85.04) rectangle (207.90,115.25);
 
-\path[draw=drawColor,line width= 3.2pt] (208.44, 78.40) rectangle (219.98,101.97);
+\path[draw=drawColor,line width= 3.2pt] (207.90, 85.04) rectangle (219.56,106.06);
 
-\path[draw=drawColor,line width= 3.2pt] (219.98, 78.40) rectangle (231.53, 82.12);
+\path[draw=drawColor,line width= 3.2pt] (219.56, 85.04) rectangle (231.21, 88.35);
 
-\path[draw=drawColor,line width= 3.2pt] (231.53, 78.40) rectangle (243.07, 81.28);
+\path[draw=drawColor,line width= 3.2pt] (231.21, 85.04) rectangle (242.87, 87.60);
 
-\path[draw=drawColor,line width= 3.2pt] (243.07, 78.40) rectangle (254.62, 78.54);
+\path[draw=drawColor,line width= 3.2pt] (242.87, 85.04) rectangle (254.52, 85.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (174.29, 72.85) -- (174.29,195.13);
+\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (173.43, 80.08) -- (173.43,189.13);
 
-\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round] ( 36.40, 72.85) rectangle (265.01,195.13);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.23, 80.08) rectangle (265.01,189.13);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45, 75.31) {0.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28, 82.28) {0.0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,102.18) {0.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,106.25) {0.2};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,129.06) {0.4};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,130.22) {0.4};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,155.94) {0.6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,154.19) {0.6};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,182.82) {0.8};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,178.16) {0.8};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65, 78.40) --
-	( 36.40, 78.40);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48, 85.04) --
+	( 34.23, 85.04);
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,105.28) --
-	( 36.40,105.28);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,109.01) --
+	( 34.23,109.01);
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,132.16) --
-	( 36.40,132.16);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,132.98) --
+	( 34.23,132.98);
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,159.04) --
-	( 36.40,159.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,156.95) --
+	( 34.23,156.95);
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,185.92) --
-	( 36.40,185.92);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,180.92) --
+	( 34.23,180.92);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] ( 46.79, 70.10) --
-	( 46.79, 72.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 44.72, 77.33) --
+	( 44.72, 80.08);
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] (137.13, 70.10) --
-	(137.13, 72.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (135.92, 77.33) --
+	(135.92, 80.08);
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] (206.31, 70.10) --
-	(206.31, 72.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (205.75, 77.33) --
+	(205.75, 80.08);
 
-\path[draw=drawColor,line width= 3.2pt,line join=round] (259.48, 70.10) --
-	(259.48, 72.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (259.43, 77.33) --
+	(259.43, 80.08);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 46.79, 61.70) {0.001};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 44.72, 69.62) {0.001};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (137.13, 61.70) {0.05};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (135.92, 69.62) {0.05};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (206.31, 61.70) {1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (205.75, 69.62) {1};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (259.48, 61.70) {10};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (259.43, 69.62) {10};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (150.70, 47.75) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (149.62, 56.56) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 12.20,133.99) {Density};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 11.51,134.60) {Density};
 \end{scope}
@@
 
-\path[fill=fillColor] ( 43.99, 23.00) rectangle (257.42, 35.00);
+\path[fill=fillColor] ( 62.32, 26.00) rectangle (236.93, 44.00);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 43.99, 30.90) {Distribution:\ \ \ };
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 62.32, 32.25) {Distribution:\ \ \ };
 \end{scope}
@@
 
-\path[fill=fillColor] (105.42, 28.00) rectangle (117.42, 40.00);
+\path[fill=fillColor] (114.49, 31.00) rectangle (122.49, 39.00);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.2pt,fill=fillColor] (106.92, 29.50) rectangle (115.92, 38.50);
+\path[draw=drawColor,line width= 0.8pt,fill=fillColor] (115.49, 32.00) rectangle (121.49, 38.00);
 \end{scope}
@@
 
-\path[fill=fillColor] (203.85, 28.00) rectangle (215.85, 40.00);
+\path[fill=fillColor] (194.42, 31.00) rectangle (202.42, 39.00);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.2pt] (205.35, 29.50) rectangle (214.35, 38.50);
+\path[draw=drawColor,line width= 0.8pt] (195.42, 32.00) rectangle (201.42, 38.00);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (122.42, 30.90) {Post-intervention\ \ \ \ };
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (124.49, 32.25) {Post-intervention\ \ \ \ };
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (220.85, 30.90) {Observed};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (204.42, 32.25) {Observed};
 \end{scope}
@@
 
-\path[fill=fillColor] ( 72.41,  0.00) rectangle (229.00, 12.00);
+\path[fill=fillColor] ( 83.80,  6.00) rectangle (215.44, 24.00);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 72.41,  7.90) {Target exposure limit:};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 83.80, 12.25) {Target exposure limit:};
 \end{scope}
@@
 
-\path[fill=fillColor] (164.74,  5.00) rectangle (176.74, 17.00);
+\path[fill=fillColor] (163.43, 11.00) rectangle (171.43, 19.00);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (170.74,  5.00) -- (170.74, 17.00);
+\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (167.43, 11.00) -- (167.43, 19.00);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (181.74,  7.90) {0.25 mg/m\textsuperscript{3}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (173.43, 12.25) {0.25 mg/m\textsuperscript{3}};
 \end{scope}

### 2023-06-30 reports/paper/paper.qmd
update paper

@@
 
-**Manuscript title:** Hypothetical limits on workplace exposure for
-reducing non-Hodgkin lymphoma: An application of the hazard-extended
-iterative conditional expectation parametric g-formula
+**Manuscript title:** Hypothetical interventions on workplace exposure
+with guaranteed positivity
 
@@
 of Epidemiology & Biostatistics
+
+^b^ University of California, Berkeley School of Public Health, Division
+of Environmental Health Sciences
 
@@
 
-**Running head suggestion:** Limits on metalworking fluid exposure to
-prevent NHL.
+**Running head suggestion:** Supportable interventions for reducing NHL
+risk.
 
@@
 **Keywords:** Metalworking fluid, occupational exposure, non-Hodgkin
-lymphoma, cancer, causal inference, g-formula, healthy-worker effect,
-United States
+lymphoma, cancer, positivity, overlap, causal inference, g-formula,
+iterated conditional expectation, healthy-worker effect
+
+**Word count** **(Limit: 1500 to 4000 words):** 3812
 
@@
 exposure to soluble metalworking fluids (MWF) in a standard survival
-analysis of the United Auto Workers-General Motors (UAW-GM) cohort. To
-further explore this association, we estimate the effects of
-hypothetical limits on soluble MWF exposure in relation to NHL risk in
-the same cohort of autoworkers.
+analysis of the United Auto Workers-General Motors (UAW-GM) cohort.
+Here, we estimate the effects of hypothetical interventions on soluble
+MWF exposure in relation to NHL risk in the same cohort of autoworkers.
+Estimation of causal effects requires positivity, which we guarantee by
+investigating causal contrasts that are supportable by the data.
 
@@
 2015 in the UAW-GM cohort of autoworkers at three Michigan plants (n =
-33,134) under hypothetical target exposure limits for soluble MWF. We
-applied the hazard-extended iterative conditional expectation parametric
-g-formula, an estimator capable of adjusting for time-varying
-confounding affected by past exposure.
+33,134) under supportable interventions on exposure to soluble MWF. The
+supportable intervention reduces annual daily average exposures above
+the target limit to that limit when the target limit is supported by
+data. Otherwise, the supportable intervention reduces exposure to the
+highest level of exposure below the target limit or not at all,
+depending on support.
 
@@
 Stronger target limits on soluble MWF exposure resulted in monotonic
-reductions in NHL risk. Setting the target exposure limit at 2 mg/m^3^
-would have prevented 98 (95% CI: 45, 161) cases of NHL. A target
-exposure limit of 0.5 mg/m^3^, the NIOSH recommended exposure limit,
-would have prevented 112 (95% CI: 57, 181) cases. Finally, a target
-exposure limit of 0.05 mg/m^3^ would have prevented 129 (95% CI: 66,
-214) cases.
+reductions in NHL risk. Setting the target exposure limit at 0.5
+mg/m^3^, the NIOSH recommended exposure limit, would have prevented 112
+(95% CI: 57, 181) cases.
 
-**Conclusion:** Limits on soluble MWF exposure would have prevented
-cases of NHL in the UAW-GM cohort. Although MWF use is expected to
-decline as the automotive industry turns to electric vehicles, a boom in
-domestic vehicle manufacturing could nonetheless lead to global
-increases in worker exposure to MWF in the US. Maintaining or
-strengthening exposure limits for MWF may protect workers from NHL.
+**Conclusion:** Stronger limits on exposure to soluble MWF provide
+stronger protections against NHL. We expect the effects of enforcing the
+target exposure limits uniformly to have even stronger protective
+effects. Strengthening exposure limits for MWF may protect workers from
+NHL during the anticipated boom in domestic manufacturing.
 
@@
 factor of NHL is immunosuppression, both congenital and acquired
-[@Filipovich_1992; @Chiu_2015]. Modulation of immune function
-contributes to the pathogenesis of NHL directly by perturbing lymphocyte
-function or indirectly by reducing immunosurveillance against neoplasms.
-Immunodeficiency may also interact with infection with Epstein-Barr
-Virus, resulting in uncontrolled B-cell proliferation [@Oertel_2002].
-Acquired immunodeficiency through infection with human immunodeficiency
-virus (HIV) can lead to genetic lesions and dysregulation while
-increasing vulnerability to infection by other oncogenic agents
-[@Grulich_1999; @Alexander_2007]. However, since immunodeficiency and
+[@Filipovich_1992; @Chiu_2015]. However, since immunodeficiency and
 infection with HIV are rare, they cannot fully explain the historic rise
@@
 Metalworking fluids are complex mixtures of oil, water, and chemical
-additives that optimize metal machining operations. During shaping,
+additives that optimize metal machining operations. There are three
+general types of MWF: straight, soluble, and synthetic. During shaping,
 grinding, and cutting operations, MWFs are misted, poured, or blasted at
@@
 health hazard to exposed workers through inhalation or ingestion of MWF
-particulate mass.
-
-There are three general types of MWF: straight, soluble, and synthetic.
-The type of MWF applied has changed over the decades in response to
-engineering, economic, and health considerations. Straight MWF, the
-oldest class of MWF, is comprised mostly of mineral oils, which were
-classified as carcinogenic by the International Agency for Research on
-Cancer (IARC) in 1973, citing studies of occupational exposures among
-workers in oil, textile, and metal industries [@IARC_1973]. In the same
-decade, additional factors including the high cost of oil and the
-introduction of performance-enhancing water-soluble chemical additives
-spurred the gradual replacement of straight MWF with water-based soluble
-and synthetic MWF for many, but not all metalworking operations
-[@Childers_2005]. Although water-based MWFs contain little to no mineral
-oil, they contain a richer cocktail of additives including chromates,
-cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and
-triazines: classes of chemicals with known or plausible carcinogenicity
-[@IARC_1987; @IARC_2014; @IARC_2017]. As the US prepares for a boom in
-domestic automotive manufacturing, occupational exposure to MWF will
-remain an important concern for worker health [@Armbrust_2021;
-@Carr_2022; @Keilman_2023].
+particulate mass. In response to health concerns and the rising cost of
+oil, soluble MWF were developed to replace straight MWF and are now the
+most commonly used type [@Byers_2006].
 
@@
 accumulate more exposure while those more susceptible to the deleterious
-health effects leave work [@Arrighi_1994]. A well-known analytical
-method for causal inference in observational studies where the HWSE or
-other forms of time-varying confounding affected by past exposure may be
+health effects of exposure leave work [@Arrighi_1994]. An early causal
+inference method in statistics developed to estimate causal effects in
+longitudinal observational studies where the HWSE or other forms of
+time-varying confounding/selection bias affected by past exposure may be
 operating is the parametric g-formula [@Robins_1986; @Taubman_2009;
-@Richardson_2013]. A central requirement necessary for causal
-interpretation of any analysis is positivity (overlap) ie adequate
-variation in the exposure of interest within strata formed by confounder
-and exposure history [@Petersen_2012]. Here, we specify hypothetical
-interventions on exposure to soluble MWF in the United Auto
-Workers-General Motors (UAW-GM) occupational cohort whose effects can be
-estimated with guaranteed positivity. In particular, we estimate the
-cumulative incidence of NHL between 1985 and 2015 under well-supported
-(supportable) interventions by applying the the hazard-extended
+@Richardson_2013]. A central requirement necessary for causal inference
+is positivity (overlap) ie adequate variation in the exposure of
+interest within strata formed by confounder and exposure histories
+[@Petersen_2012].
+
+Common approaches for addressing violations in positivity are
+model-based smoothing when using outcome-regression techniques, weight
+truncation when using propensity methods, or a combination of both.
+Another approach is to consider only those causal contrasts that are
+supported by the observed data ie have strictly positive propensity
+score. Here, we defined supportable interventions on exposure to soluble
+MWF in the United Auto Workers-General Motors (UAW-GM) occupational
+cohort whose effects can be estimated with guaranteed positivity. We
+estimated the cumulative incidence of NHL between 1985 and 2015 under
+supportable interventions based on selected target exposure limits on
+annual average daily exposure by applying the the hazard-extended
 iterative conditional expectation (ICE) parametric g-formula
-[@Arrighi_1994; @Wen_2021].
+[@Arrighi_1994; @Wen_2020].
 
@@
 We estimated NHL cumulative incidence from 1985 to 2015 under
-supportable interventions on average daily exposure to soluble MWF by
-applying the hazard-extended ICE parametric g-formula estimator
-[@Wen_2020]. First, we estimated the expected number of NHL cases that
-we would observe if there were no censoring by competing risks. Then, we
-contrasted this case count to that under supportable interventions based
-on five hypothetical target exposure limits and no competing risks. The
-five target exposure limits were (1) 2.0, (2) 1.0, (3) 0.5, (4) 0.25,
-and (5) 0.05 mg/m^3^. The National Institute for Occupational Safety and
-Health (NIOSH) recommended exposure limit (REL) for total particulate
-mass (PM) composed of MWF is 0.5 mg/m^3^ [@niosh_1998]. For each target
-exposure limit, period of follow-up, and unique combination of
-confounder and exposure histories, we also defined a supportable
-exposure limit, which was the maximum observed value of exposure at or
-below the target exposure limit or no limit when all of the observed
-values were above the target limit. For each target exposure limit, we
-specified an intervention rule that reduced exposures above the
-supportable exposure limit to that limit, but allowed exposures at or
-below the limit to vary according to their natural distribution.
-Applying this intervention rule to the observed distribution of exposure
-produced the intervention distribution that defined the stochastic
-dynamic intervention with guaranteed positivity.
+supportable interventions on on annual average daily exposure to soluble
+MWF based on several target exposure limits. First, we estimated the
+expected number of NHL cases that we would observe if there were no
+censoring by censoring and no target exposure limit. Then, we contrasted
+this case count to that under supportable interventions based on five
+hypothetical target exposure limits and no censoring. The five target
+exposure limits were (1) 2.0, (2) 1.0, (3) 0.5, (4) 0.25, and (5) 0.05
+mg/m^3^. The National Institute for Occupational Safety and Health
+(NIOSH) recommended exposure limit (REL) for time-weighted average total
+particulate mass (PM) composed of MWF is 0.5 mg/m^3^ [@niosh_1998].
+
+For each target exposure limit, period of follow-up, and strata defined
+by unique combinations of confounder and exposure histories, we found a
+supportable exposure limit, which was the maximum observed value of
+exposure at or below the target exposure limit. If all of the observed
+values were above the target limit, no limit was enforced for that
+stratum. The supportable intervention rule then reduces exposures above
+the supportable exposure limit to that limit, but allowed exposures at
+or below the limit to vary according to their observed distribution.
+Applying the supportable intervention rule to the observed distribution
+of exposure produces the intervention distribution that defines the
+corresponding stochastic dynamic intervention with guaranteed
+positivity. We estimated the effect of supportable intervention rules
+based on selected target exposure limits, expressed as stochastic
+dynamic interventions, using the hazard-extended ICE parametric
+g-formula [@Wen_2020].
+
+Figure 1 presents three example scenarios where the target exposure
+limit is 0.25 mg/m^3^ in all cases, but the supportable exposure limit
+differs depending on what the observed data supports. In Figure 1a, the
+supportable exposure limit is equal to the target exposure limit as some
+individuals with that particular set of potential confounder and
+exposure histories were observed to have experienced exposure at that
+level. In Figure 1b, the supportable exposure limit is below the target
+exposure limit. In Figure 1c, there is no limit on exposure because no
+individuals in that stratum experienced exposure below the target
+exposure limit.
+
+::: {#fig-rules layout-ncol="2"}
+![](resources/images/intervention-density-witnin-combos-a.png){#fig-1a
+width="3.5in"}
+![](resources/images/intervention-density-witnin-combos-b.png){#fig-1b
+width="3.5in"}
+![](resources/images/intervention-density-witnin-combos-c.png){#fig-1c
+width="3.5in"}
+
+Observed and post intervention distribution of nonzero exposure for
+three distinct confounder and exposure histories before and after
+applying the supportable intervention rule.
+:::
 
@@
 the cohort [@Eisen_1992; @Eisen_2001]. The large size of the study
-population and rich time-varying, quantitative MWF exposure data provide
-an opportunity to study this relatively rare cancer and evaluate
-realistic interventions on MWF exposure in a longitudinal cohort
-setting. The present study population (N = 33,134) was restricted to the
-autoworkers who were at work in 1941 or not yet hired, missing no more
-than half of their employment history, and still alive at the start of
-follow-up. Autoworkers in the study population were followed for NHL
-incidence from January 1, 1985 until NHL diagnosis, death, December 31,
-2014 (30 years after the end of employment record availability), or the
-oldest observed age at death (108 years), whichever came earlier.
+population and rich time-varying, quantitative MWF exposure data enable
+the study of this relatively rare cancer and evaluate realistic
+interventions on MWF exposure in a longitudinal cohort setting. The
+present study population (N = 33,134) was restricted to the autoworkers
+who were at work in 1941 or not yet hired, missing no more than half of
+their employment history, and still alive at the start of follow-up.
+Autoworkers in the study population were followed for NHL incidence from
+January 1, 1985 until NHL diagnosis, death, December 31, 2014 (30 years
+after the end of employment record availability), or the oldest observed
+age at death (108 years), whichever came earlier.
 
-## Outcome and covariates
+## Outcome and potential confounders
 
@@
 Details regarding cancer incidence follow-up are described elsewhere
-[@Colbeth_2023]. Vital status was ascertained from company records and
+[@Colbeth_2022]. Vital status was ascertained from company records and
 by linkage to Social Security Administration, National Death Index, and
@@
 exposure estimates to soluble, straight, and synthetic MWF for each
-combination of job, department, and plant over time. Workers' average
-daily exposure to each MWF type was determined by combining this
+combination of job, department, and plant over time. Workers' annual
+average daily exposure to each MWF type was determined by combining this
 job-exposure matrix with employment records, which recorded time-varying
@@
 @Karipidis_2007; @Zhang_2019]. In analyses, MWF exposure history at
-start of follow-up was summarized as the cumulative sum of annual
+start of follow-up was summarized as the cumulative sum of average
 exposure intensities. Exposure was coded as categorical variables with
@@
 estimated the effects of interventions on soluble MWF, the type of MWF
-used most widely and in the greatest quantities. We treated exposure to
-straight and synthetic MWF as potential confounders.
+used most widely and in the greatest quantities while treating
+co-exposure to straight and synthetic MWFs as potential confounders.
 
@@
 ranged from two to four years. The hazard-extended ICE parametric
-g-formula involved two stages. In the first, we estimated counterfactual
-discrete hazards over the person-periods. In the second, we pooled those
+g-formula involves two stages. In the first, we estimate counterfactual
+discrete hazards over the person-periods. In the second, we pool those
 estimates to estimate the counterfactual risk over the entire follow-up
-period. During pooling, we iteratively combined estimates of the
-counterfactual hazard starting with the last two periods, then the last
-three, then the last four, and so forth. In each iteration, we performed
-model-based standardization over exposure and covariate histories before
-combining the counterfactual discrete hazard with the risk over
-subsequent periods. This iterative process resulted in a sequentially
-standardized estimate of the counterfactual cumulative incidence of NHL
-when the intervention of interest is enforced over all follow-up
-periods. We took exposure to straight and synthetic MWF, employment
-status, cumulative time off, age, duration of employment, sex
-(male/female), race (Black/white/unknown), and plant (Plant 1/Plant
-2/Plant 3) to be potential confounders. Exposure to MWF, employment
-status, time off, and duration of employment were lagged 20 years. An
-overview of the general steps of the estimation procedure are presented
-below. Note that we refer to discrete hazards simply as hazards.
+period. During pooling, we iteratively combine estimates of the
+counterfactual hazard to obtain a pooled estimate over an increasing
+number of periods starting from the last period. In each iteration, we
+perform model-based standardization over exposure and covariate
+histories before combining the counterfactual discrete hazard estimate
+with the estimated hazard pooled over subsequent periods. This iterative
+process results in a sequentially standardized estimate of the
+counterfactual cumulative incidence of NHL when the intervention of
+interest is enforced over all follow-up periods.
 
-1.  Fit a pooled logistic regression of NHL on covariates and exposure
-    over all at-risk person-periods.
+We investigated supportable interventions that guarantee positivity:
+every value of exposure that could be assigned under the our stochastic
+dynamic intervention has a strictly positive propensity score. We took
+exposure to straight and synthetic MWF, employment status, cumulative
+time off, age, duration of employment, sex (male/female), race
+(Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3) to be
+potential confounders. Exposure to MWF, employment status, time off, and
+duration of employment were lagged 20 years. An overview of the general
+steps of the estimation procedure are presented below. Note that we
+refer to discrete hazards simply as hazards.
+
+1.  Fit a pooled logistic regression of NHL on potential confounders and
+    exposure over all at-risk person-periods.
 
@@
 
-3.  Within strata formed by unique combinations of covariates, obtain
-    the intervention distribution of exposure by applying the
-    intervention rule to the observed exposure distribution.
+3.  Within strata formed by unique combinations of potential confounders
+    and exposure, obtain the intervention distribution of exposure by
+    applying the supportable intervention rule to the observed exposure
+    distribution.
 
@@
     a)  Regress the counterfactual hazard pooled over all subsequent
-        periods on exposure and covariate history at the current period.
+        periods on all past potential confounders and exposures.
     b)  Predict the pooled hazard for each person at risk at the start
@@
         each person and level of exposure, multiply the predicted pooled
-        hazard by one minus the corresponding predicted hazard and add
-        the predicted hazard to the product.
-    c)  Within strata formed by exposure and covariate history, obtain
-        the intervention distribution of exposure by applying the
-        intervention rule to the observed exposure distribution.
+        hazard by one minus the corresponding predicted hazard. Then,
+        add the predicted hazard to the product.
+    c)  Within strata formed by potential confounder and exposure
+        histories, obtain the intervention distribution of exposure by
+        applying the intervention rule to the observed exposure
+        distribution.
     d)  Within strata, estimate the counterfactual hazard pooled over
@@
 
-6.  Compute the counterfactual risk by averaging the counterfactual
-    hazard over the entire follow-up period across all persons.
+6.  Compute the counterfactual risk by averaging the pooled
+    counterfactual hazards across all persons.
 
@@
 
-We estimated cumulative incidence under the observed distribution of
-soluble MWF exposure (natural course) and under the five supportable
-exposure limits. We contrasted the cumulative incidence under
-supportable limits to that under the natural course by computing the
-number of cases averted and the cumulative incidence ratios. Confidence
-intervals were computed using the basic nonparametric bootstrap with
-1000 Monte Carlo samples from the population at the start of follow-up.
-All the necessary script used to reproduce the analyses are available on
-[GitHub](https://github.com/kvntchn/gm-nhl-ice).
-
-# Results
+We estimated cumulative incidence under no intervention on soluble MWF
+and under the supportable interventions based on the five target
+exposure limits. We contrasted the cumulative incidence under the
+supportable interventions to that under no intervention on exposure by
+computing the number of cases averted and the cumulative incidence
+ratios. Confidence intervals were computed using the basic nonparametric
+bootstrap with 1000 Monte Carlo samples from the population at the start
+of follow-up. All the necessary script used to reproduce the analyses
+are available on [GitHub](https://github.com/kvntchn/gm-nhl-ice).
 
@@
   # hspace.which <- grepl("\\\\hspace\\{.*\\}", rownames(tab1))
-  rownames(tab1) <- gsub("\\\\hspace\\{.*\\}|\\\\hline |\\$.*\\$| among deceased", "", rownames(tab1))
+	rownames(tab1) <- gsub(
+		"\\\\hspace\\{.*\\}|\\\\hline |\\$.*\\$| among deceased",
+		"",
+		rownames(tab1))
 
@@
 
-Table 1 presents summary statistics of exposure and covariates for the
-full study population and for those diagnosed with NHL between 1985 and
-2005. The cohort is predominantly white (66%) and male (87%). The median
-year of hire among those diagnosed with NHL was 1959 whereas the median
-year of hire in the full study population was almost a decade later. Age
-at hire was approximately the same among those with NHL and the full
-study population. Median lagged cumulative exposure to all three MWF
-types was higher among NHL cases. Soluble MWF were the most widely used
-MWF type, with approximately 90% of workers ever exposed. Median
-cumulative exposure among the exposed was 6.5 times higher for soluble
-than for straight MWF. Figure 1 shows median annual average daily
-exposure to the three MWF types among exposed workers over calendar
-time. Exposure to MWF generally followed a downward trend over time.
+# Results
+
+Table 1 presents summary statistics for the full study population and
+among those diagnosed with NHL between 1985 and 2015. The cohort is
+predominantly white (64%) and male (86%). Year of hire and age at hire
+were approximately the same among those with NHL and the full study
+population. Median lagged cumulative exposure to all three types of MWF
+was higher among NHL cases. Soluble MWF were the most widely used type,
+with approximately 88% of workers ever exposed. Median cumulative
+exposure among the exposed was 6 times higher for soluble than for
+straight MWF. Figure 2 shows median annual average daily exposure to the
+three MWF types among exposed workers over calendar time. Exposure to
+MWF generally followed a downward trend over time.
 
@@
 # tab1 <- tab1[tab1.which,]
-tab1[c(1:13, 15, 14, 16:27, 29, 28, 30),-grep("hspace.logical", colnames(tab1))] |> 
+tab1.sub <- tab1[c(1:13, 15, 14, 16:27, 29, 28, 30),]
+tab1.sub <- tab1.sub[-c(17, 21, 26),]
+tab1.sub_hspace <- tab1.sub$hspace.logical
+tab1.sub <- tab1.sub[,-grep('hspace.logical', names(tab1.sub))]
+```
+
+```{r}
+tab1.sub |> 
   data.frame() |> flextable() |>
@@
   hline_top() |> hline_bottom() |>
-  hline(which((grepl("[0-9]\\)", tab1$spread))[-1])[1]) |> width(4, 0.1) |>
+  hline(which((grepl("[0-9]\\)", tab1.sub$spread))[-1])[1]) |> width(4, 0.1) |>
   width(1, 2.2) |> width(c(3, 6), 1.1) |> width(c(2, 5), 0.65) |>
   flextable::compose(
-    i = grep("Cumulative exposure", rownames(tab1)), j = 1,
+    i = grep("Cumulative exposure", rownames(tab1.sub)), j = 1,
     value = as_paragraph("Cumulative exposure to MWF (mg/m",
@@
   flextable::align(j = 2:6, align = "center", part = "all") |>
-  footnote(i = grep("Plant$", rownames(tab1)), j = 1, value = as_paragraph(
+  footnote(i = grep("Plant$", rownames(tab1.sub)), j = 1, value = as_paragraph(
     " Plant of longest employment duration among those who worked at multiple plants"),
     ref_symbols = "a", inline = T) |>
-  footnote(i = grep("Ever exposed|time off", rownames(tab1)), j = 1, value = as_paragraph(
+  footnote(i = grep("Ever exposed|time off", rownames(tab1.sub)), j = 1, value = as_paragraph(
     " Lagged 10 years"),
     ref_symbols = "b", inline = T) |>
-  footnote(i = grep("work", rownames(tab1)), j = 1, value = as_paragraph(
+  footnote(i = grep("work", rownames(tab1.sub)), j = 1, value = as_paragraph(
     " Among those who left work by December 31, 1994"),
     ref_symbols = "c", inline = T) |>
-  # footnote(i = grep("death", rownames(tab1)), j = 1, value = as_paragraph(
+  # footnote(i = grep("death", rownames(tab1.sub)), j = 1, value = as_paragraph(
   #   " Among deceased"),
   #   ref_symbols = "d", inline = T) |>
-  footnote(i = grep("Cumulative exposure", rownames(tab1)), j = 1, value = as_paragraph(
+  footnote(i = grep("Cumulative exposure", rownames(tab1.sub)), j = 1, value = as_paragraph(
     " Among ever-exposed individuals, lagged 10 years."),
@@
   padding(
-    i = which(tab1$hspace.logical),
+    i = which(tab1.sub_hspace),
     j = 1,
@@
   ) |>
-  merge_at(i = grep("Cumulative exposure", rownames(tab1))) |>
+  merge_at(i = grep("Cumulative exposure", rownames(tab1.sub))) |>
   hline_bottom(part = "footer") |> font(fontname = 'arial') |>
-  set_caption(caption = "Summary of population characteristics. Statistics shown above the horizontal line are count (%). Those shown below are median (quartile 1, quartile 3).")
+	set_caption(
+		caption = paste0(
+			"Summary of population characteristics. Statistics shown above ",
+			"the horizontal line are count (%). Those shown below are median ",
+			"(quartile 1, quartile 3).")
+	)
 ```
@@
 
-![Figure 1. Median annual average daily exposure to soluble, straight,
+![Figure 2. Median annual average daily exposure to soluble, straight,
 and synthetic metalworking fluids among exposed workers over
@@
 estimates of the counterfactual number of cases, number of cases
-averted, and cumulative incidence ratios contrasting hypothetical
+averted, and cumulative incidence ratios contrasting supportable
 interventions on exposure to soluble MWF based on different target
-exposure limits and no competing risks. Under an intervention
-eliminating competing risks, the estimated number of cases was 502 (95%
-CI: 439, 555). Interventions based on stronger limits on average daily
-exposure to soluble MWF resulted in monotonically stronger reductions in
-the estimated cumulative incidence of NHL. Setting the target exposure
-limit at the NIOSH REL 0.5 mg/m^3^ would have averted 112 (95% CI: 57,
-181) NHL cases.
+exposure limits and no censoring. Under an intervention eliminating
+censoring, the estimated number of cases was 502 (95% CI: 439, 555).
+Interventions based on stronger target exposure limits on soluble MWF
+resulted in monotonically stronger reductions in the estimated
+cumulative incidence of NHL. Setting the target exposure limit at the
+NIOSH REL 0.5 mg/m^3^ would have averted 112 (95% CI: 57, 181) NHL
+cases.
 
@@
     j = 1,
-    value = as_paragraph("Exposure limit for soluble MWF (mg/m", as_sup("3"), ")"),
+    value = as_paragraph("Target exposure limit (mg/m", as_sup("3"), ")"),
     part = "header"
@@
   hline_bottom(part = "footer") |>
-  set_caption(caption = "Counterfactual number of cases, number of cases averted, and cumulative incidence ratio estimates contrasting hypothetical limits on soluble MWF exposure to no intervention on exposure.")
+	set_caption(caption = paste0(
+		"Estimates of the counterfactual number of cases, ",
+		"number of cases averted ",
+		"and cumulative incidence ratios ",
+		"contrasting supportable ",
+		"interventions on annual average daily exposure to soluble MWF ",
+		"to no intervention on exposure."
+	))
 
@@
 Although NIOSH concluded that there exists substantial evidence linking
-MWF exposure to several different cancers, their REL of 0.5 mg/m^3^ for
-total particulate matter derived from any type of MWF targeted risk of
-respiratory disorders rather than cancer [@niosh_1998; @Mirer_2003].
-Exposure limits stronger than the NIOSH REL may provide additional
-health protections not previously considered by policy makers. Using the
-hazard-extended ICE parametric g-formula, We estimated the
+MWF exposure to several different cancers including larynx, rectum,
+pancreas, skin, scrotum, and bladder cancer, their REL of 0.5 mg/m^3^
+for total particulate matter derived from any type of MWF targeted risk
+of nonmalignant health conditions [@niosh_1998; @Mirer_2003]. Exposure
+limits stronger than the NIOSH REL may provide valuable health
+protections not previously considered by policy makers. Using the
+hazard-extended ICE parametric g-formula, we estimated the
 counterfactual expected number of NHL cases from 1985 to 2015 in the
-UAW-GM cohort if we enforced exposure limits based on five different
-target exposure limits and found a monotonic exposure-dependent
-relationship where stronger target exposure limits yielded lower NHL
-case count estimates.
+UAW-GM cohort if we enforced supportable interventions on soluble MWF
+based on five different target exposure limits and found a monotonic
+exposure-dependent relationship where stronger target exposure limits
+yielded lower NHL case count estimates.
 
-The g-formula is a well-known approach in causal inference used for the
-identification and estimation of causal effects in the presence of
-time-varying confounding affected by past exposure [@Robins_1986].
-Standard representations of the g-formula include (1) a non-iterated
-expectation over the joint density of covariates, (2) the ICE over time,
-and (3) an inverse probability weighted expectation. The parametric
-g-formula is a plug in estimator for the g-formula under its first,
-non-iterative, representation. It involves the parametric modeling of
-the full joint distribution of the outcome, exposure, and covariates
-under study for each time point [@Taubman_2009; @Young_2014].
-Counterfactual quantities under hypothetical interventions of interest
-are computed from Monte Carlo samples from distributions implied by the
-fitted parametric models. In longitudinal settings, this approach often
-requires specifying and fitting large number of models in order to
-satisfy the exchangeability assumptions necessary for causal
-identification.
+The g-formula is a well-known approach in causal inference used for
+estimating causal effects in the presence of time-varying confounding
+affected by past exposure [@Robins_1986]. Standard representations of
+the g-formula include (1) a non-iterated expectation over the joint
+density of covariates, (2) the ICE over time, and (3) an inverse
+probability weighted expectation. The classic parametric g-formula is a
+plug in estimator for the g-formula under its first, non-iterative,
+representation. It involves the parametric modeling of the full joint
+distribution of the confounders, exposure, and outcome for each time
+point [@Taubman_2009; @Young_2014]. Counterfactual quantities under
+hypothetical interventions of interest are computed from Monte Carlo
+samples from distributions implied by the fitted parametric models. In
+longitudinal settings, this approach often requires specifying and
+fitting large number of models in order to satisfy the exchangeability
+assumptions necessary for causal identification. Despite this
+limitation, analysts often choose the parametric g-formula because of
+the intuitive way it handles interventions on the natural value of
+exposure. However, these causal estimands are not unique to the
+parametric g-formula. The distribution of exposure produced by
+marginalizing intervention rules over the observed distribution of
+exposure within strata formed by potential confounder and exposure
+histories defines a corresponding stochastic dynamic intervention, whose
+effects may be estimated using various estimators [@Wen_2020;
+@Bang_2005; @van-der-Laan_2011; @Wen_2023; @Diaz_2021]. Estimating
+causal effects of this implied stochastic dynamic intervention is
+analogous to that of interventions on the natural value of exposure
+[@Young_2014].
 <!-- Since applications of the parametric g-formula are often context-laden, there are no unified guidelines for model specification. -->
 
-Parametric estimators using the ICE representation of the g-formula
-require modeling only the conditional outcome distributions, so they
-require fewer parametric assumptions than non-iterative parametric
-g-formula estimators. Counterfactual outcome estimates over the
-follow-up period are computed from interval-specific conditional
-estimates by applying the tower rule of expectation. Under the
-assumptions of conditional exchangeability at all time points,
-positivity, counterfactual consistency, and correct model specification,
-the hazard-extended parametric g-formula yields unbiased estimates of
-counterfactual risk with greater statistical efficiency than both
-propensity score-based estimators and the classical ICE g-formula.
+Estimators using the ICE representation of the g-formula are capable of
+estimating effects of stochastic dynamic interventions. These ICE
+g-formula estimators require modeling only the conditional distributions
+of the outcome at each time. Hence, they require fewer parametric
+assumptions than the classic parametric g-formula. Counterfactual
+outcome estimates over the follow-up period are computed from
+interval-specific conditional estimates by applying the tower rule of
+expectation. Under the assumptions of conditional exchangeability at all
+time points, positivity, counterfactual consistency, and correct model
+specification, the hazard-extended parametric g-formula yields unbiased
+estimates of counterfactual risk with greater statistical efficiency
+than both propensity score-based estimators and the non-extended ICE
+g-formula.
 
-Conditional exchangeability means that for all time points, there is no
-confounding of the relationship between exposure/censoring and both
-future exposure/censoring and NHL status given the observed past,
-including past exposure and covariates [@Richardson_2013; @Diaz_2021]. A
-major threat to conditional exchangeability in longitudinal occupational
-studies is the HWSE. We limit potential bias due to the HWSE by
-conditioning on cumulative exposure, employment status, and cumulative
-time off history at each time point. Cumulative time off and employment
-status are reasonable mediators of the causal paths linking past health
-to future exposure and health, but adjustment for these variables may
-not be sufficient for eliminating bias due to the HWSE. Declines in a
-worker's health may lead to reductions in work-related exposure without
-affecting employment status or time off work [@Garcia_2017]. We expect
-the absence of time-varying measures of worker health over the life
-course to result in bias toward the null.
-
-Positivity refers to the need for adequate variation in future exposure
-among strata formed by observed covariate and intervention-compliant
-exposure histories. Even under conditional exchangeability, where
-exposures within these strata may be considered the result of
-experimental assignment, expected counterfactual outcomes under
-different exposures may not be estimable if there is excessive sparsity
-in the observed distribution of exposures [@Maldonado_2002]. We
-investigated static and dynamic stochastic interventions on soluble MWF
-exposure that intervened only when average daily exposure exceeded the
-hypothetical limit under consideration. Hence, our parameters of
-interest achieve positivity more easily than those for static
-deterministic interventions e.g. setting all to a single level of
-exposure. Nonetheless, violations in positivity were still of concern
-due to the high dimensionality of covariates, as is common in
-longitudinal settings. We addressed sparsity by summarizing the 20 years
-of follow-up over a coarser timescale with only 8 follow-up periods and
-by representing covariates using fewer categories. Coarsening limits the
-comprehensiveness of confounding control, but improves positivity. In
-practice, causal inference using observational data must always balance
-positivity, covariate adjustment, and model specification
-[@Petersen_2012].
-<!-- When estimating causal effects using estimators that do not require exposure modeling, as is the case with ICE g-formula methods, concerns over potential bias due to practical violations in positivity may be relaxed if correct model specification, discussed below, is attained.
--->
+Correct model specification is a standard assumption in all parametric
+and semi-parametric analyses. In causal analyses of longitudinal cohort
+studies, ICE g-formula estimators are less common than the classic
+parametric g-formula [@Keil_2014]. However, a major limitation of the
+classic g-formula is the g-null paradox: the guaranteed misspecification
+of parametric models resulting in the false rejection of the null
+hypothesis when the null is true and when there is time-varying
+confounding affected by past exposure [@Naimi_2015; @McGrath_2022]. As
+with all ICE g-formula estimators, the estimator we applied is not
+subject to the g-null paradox. Furthermore, since ICE g-formula
+estimators require fewer parametric modeling requirements than the
+classic parametric g-formula, correct model specification may be
+achieved more readily.
 
@@
 
-Correct model specification is a standard assumption in all parametric
-and semi-parametric analyses. The estimator we applied offers greater
-statistical efficiency than the classical ICE parametric g-formula
-estimator because it leverages greater parametric smoothing. In causal
-analyses of longitudinal cohort studies, both the hazard-extended and
-classical ICE parametric g-formula estimators are less common than the
-NICE parametric g-formula [@Keil_2014]. However, a major limitation of
-the NICE g-formula is the g-null paradox: the guaranteed
-misspecification of parametric models resulting in the false rejection
-of the null hypothesis when the null is true and when there is
-time-varying confounding affected by past exposure [@Naimi_2015;
-@McGrath_2022]. As with all ICE g-formula estimators, the estimator we
-applied is not subject to the g-null paradox. Furthermore, simulation
-studies show that the variance of the hazard-extended ICE parametric
-g-formula is similar to that of the NICE parametric g-formula, so we
-expect the former to be no less conservative than the latter
-[@Wen_2020].
+Positivity refers to the need for adequate variation in future exposure
+among strata formed by observed covariate and intervention-compliant
+exposure histories. Even under conditional exchangeability, where
+exposures within these strata may be considered the result of
+experimental assignment, expected counterfactual outcomes under
+different exposures may not be estimable if there is excessive sparsity
+in the observed distribution of exposures [@Maldonado_2002]. Rather than
+address potential violations in positivity analytically, we investigated
+stochastic dynamic interventions on soluble MWF exposure based on
+intervention distributions which are nonzero only where the propensity
+score is strictly positive. Hence, our supportable interventions
+guarantee positivity. Interventions that guarantee positivity have been
+suggested in the past, and have also been called "realistic"
+interventions [@Petersen_2012].
+
+Conditional exchangeability means that for all time points, there is no
+confounding of the relationship between exposure/censoring and both
+future exposure/censoring and NHL status given the observed past,
+including past exposure and confounders [@Richardson_2013; @Diaz_2021].
+A major threat to conditional exchangeability in longitudinal
+occupational studies is the HWSE. We limit potential bias due to the
+HWSE by conditioning on cumulative exposure, employment status, and
+cumulative time off history at each time point. Cumulative time off and
+employment status are reasonable mediators of the causal paths linking
+past health to future exposure and health, but adjustment for these
+variables may not be sufficient for eliminating bias due to the HWSE.
+Declines in a worker's health may lead to reductions in work-related
+exposure without affecting employment status or time off work
+[@Garcia_2017]. We expect the absence of time-varying measures of worker
+health over the life course to result in bias toward the null.
+
+<!-- There are three general types of MWF: straight, soluble, and synthetic.
+The type of MWF applied has changed over the decades in response to engineering, economic, and health considerations.
+Straight MWF, the oldest class of MWF, is comprised mostly of mineral oils, which were classified as carcinogenic by the International Agency for Research on Cancer (IARC) in 1973, citing studies of occupational exposures among workers in oil, textile, and metal industries [@IARC_1973].
+In the same decade, additional factors including the high cost of oil and the introduction of performance-enhancing water-soluble chemical additives spurred the gradual replacement of straight MWF with water-based soluble and synthetic MWF for many, but not all metalworking operations [@Childers_2005].
+Although water-based MWFs contain little to no mineral oil, they contain a richer cocktail of additives including chromates, cycloalkanes, phenols, organochlorines, nitrites, sulfonates, and triazines: classes of chemicals with known or plausible carcinogenicity [@IARC_1987; @IARC_2014; @IARC_2017].
+As the US prepares for a boom in domestic automotive manufacturing, occupational exposure to MWF will remain an important concern for worker health [@Armbrust_2021; @Carr_2022; @Keilman_2023].
+-->
 
@@
 environmental exposures to NHL report findings from case-control studies
-where exposures are measured crudely as binary indicators of exposure or
+where exposures are measured as binary indicators of exposure or as
 membership in a particular occupational group [@Cano_2001;
@@
 
-This study investigated the effect of hypothetical limits on MWF
-exposure by comparing the standardized distributions of NHL under
-various distributions of cumulative exposure induced by applying upper
-bounds to average daily exposure to soluble MWF. We selected these
-hypothetical limits based on the NIOSH REL of 0.5 mg/m^3^ [@niosh_1998].
-In the real world, there is no enforcement of the REL, but we
-nonetheless observed average daily exposures below the REL in these GM
-plants for many years. If the REL were enforced in the real world, we
-would not expect reductions in exposure for these low-exposure
-person-years. Hence, contrasting the counterfactual scenario where all
-workers experienced average daily exposure at the REL to one where all
-workers experienced average daily exposure at some higher level would
-result in an overestimate of the expected real-world benefit of REL
-enforcement.
+<!-- Modulation of immune function contributes to the pathogenesis of NHL directly by perturbing lymphocyte function or indirectly by reducing immunosurveillance against neoplasms.
+Immunodeficiency may also interact with infection with Epstein-Barr Virus, resulting in uncontrolled B-cell proliferation [@Oertel_2002].
+Acquired immunodeficiency through infection with human immunodeficiency virus (HIV) can lead to genetic lesions and dysregulation while increasing vulnerability to infection by other oncogenic agents [@Grulich_1999; @Alexander_2007].
+-->
 
-<!-- The interventions we considered are stochastic interventions resulting in post-intervention distributions of exposure that better reflect what we would expect if exposure limits were enforced in the real world.
-The interventions which ignore exposure to straight and synthetic MWF are static.
-The interventions which reduce exposure to soluble MWF by a quantity determined by exposure to other MWF are dynamic.
-The dynamic stochastic interventions respect the fact that the REL is for total MWF, not just soluble MWF.
-If an individual experienced a large amount of exposure to straight and synthetic MWF in one year, then their exposure to soluble MWF should be bounded at a lower level so that the sum of their exposure to soluble, straight, and synthetic MWF is no greater than the hypothetical limit.
--->
+This study investigated the effect of supportable interventions on MWF
+exposure with guaranteed positivity. We compared the standardized risk
+of NHL under post-intervention distributions of exposure based on a
+range of target limits on annual average daily exposure to soluble MWF.
+We selected a range of hypothetical target exposure limits near the
+NIOSH REL of 0.5 mg/m^3^ [@niosh_1998]. If the target exposure limits
+were enforced uniformly rather than in a data-supportable way, we would
+expect even larger reductions in NHL risk relative to no intervention on
+exposure. The supportable interventions we evaluated here provide a more
+conservative estimate of the potential health benefit of enforcing
+stronger limits on MWF exposure in the real world because they
+explicitly restrict the causal contrasts we can evaluate to those
+supported by the observed data.
 
@@
 Associations between several occupations and risk of NHL have been
-reported previously, but none evaluated the potential effect of
-hypothetical limits on occupational exposures [@Ekstrom-Smedby_2006;
-@Chiu_2015; @t-Mannetje_2016; @Callahan_2018]. We found evidence that
-exposure to soluble MWF was associated with NHL incidence after
-adjustment for time-varying confounding affected by prior exposure using
-the hazard-extended ICE parametric g-formula. Reducing cumulative
-exposure to soluble MWF by enforcing hypothetical, but realistic,
-interventions on average daily exposure would reduce NHL incidence.
-\newpage
+reported previously, but none to our knowledge evaluated the potential
+effect of realistic limits on occupational exposures
+[@Ekstrom-Smedby_2006; @Chiu_2015; @t-Mannetje_2016; @Callahan_2018]. We
+found evidence that limiting exposure to soluble MWF would reduce NHL
+incidence in an analysis that guarantees positivity and adjusts for time-varying confounding affected by past exposure. \newpage
 

### 2023-06-30 reports/paper/resources/intervention-density-witnin-combos-a.tex
update paper

% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:02:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\end{document}
re}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (252.94,180.67);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,110.79);

\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

\path[fill=fillColor] ( 62.31, 37.60) rectangle ( 69.61, 37.60);

\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 62.00);

\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);

\path[fill=fillColor] ( 84.20, 37.60) rectangle ( 91.50, 37.60);

\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 37.60);

\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);

\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);

\path[fill=fillColor] (113.39, 37.60) rectangle (120.69,159.58);

\path[fill=fillColor] (120.69, 37.60) rectangle (127.99, 37.60);

\path[fill=fillColor] (127.99, 37.60) rectangle (135.29, 37.60);

\path[fill=fillColor] (135.29, 37.60) rectangle (142.58, 37.60);

\path[fill=fillColor] (142.58, 37.60) rectangle (149.88, 37.60);

\path[fill=fillColor] (149.88, 37.60) rectangle (157.18, 37.60);

\path[fill=fillColor] (157.18, 37.60) rectangle (164.48, 37.60);

\path[fill=fillColor] (164.48, 37.60) rectangle (171.78, 37.60);

\path[fill=fillColor] (171.78, 37.60) rectangle (179.07, 37.60);

\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 37.60);

\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);

\path[fill=fillColor] (193.67, 37.60) rectangle (200.97, 37.60);

\path[fill=fillColor] (200.97, 37.60) rectangle (208.27, 37.60);

\path[fill=fillColor] (208.27, 37.60) rectangle (215.56, 37.60);

\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);

\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);

\path[fill=fillColor] (230.16, 37.60) rectangle (237.46, 37.60);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01,110.79);

\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 62.31, 37.60) rectangle ( 69.61, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 62.00);

\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 84.20, 37.60) rectangle ( 91.50, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);

\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);

\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 62.00);

\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);

\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 62.00);

\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 37.60);

\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 62.00);

\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);

\path[draw=drawColor,line width= 0.4pt] (157.18, 37.60) rectangle (164.48, 37.60);

\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);

\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);

\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);

\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 62.00);

\path[draw=drawColor,line width= 0.4pt] (193.67, 37.60) rectangle (200.97, 37.60);

\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);

\path[draw=drawColor,line width= 0.4pt] (208.27, 37.60) rectangle (215.56, 37.60);

\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 37.60);

\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 62.00);

\path[draw=drawColor,line width= 0.4pt] (230.16, 37.60) rectangle (237.46, 37.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.50) -- (120.69,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.22, 31.50) rectangle (246.94,165.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 62.29) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 89.74) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,117.18) {15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,144.62) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
	( 38.22, 37.60);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 65.05) --
	( 38.22, 65.05);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 92.49) --
	( 38.22, 92.49);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,119.93) --
	( 38.22,119.93);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,147.38) --
	( 38.22,147.38);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.75) --
	( 47.71, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.75) --
	(106.10, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.75) --
	(164.48, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.75) --
	(222.86, 31.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 47.71, 21.04) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.10, 21.04) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.48, 21.04) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (222.86, 21.04) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.58,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.59) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,143.84) rectangle (244.lor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (155.18,142.55) rectangle (244.94,168.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (155.18,161.56) {Distribution:\ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (155.18,150.55) rectangle (163.18,158.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (155.18,150.55) rectangle (163.18,158.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (155.18,142.55) rectangle (163.18,150.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (155.68,143.05) rectangle (162.68,150.05);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.18,151.79) {Post-intervention\ \ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.18,143.79) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (155.18,123.02) rectangle (231.18,140.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (155.18,134.03) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (155.18,123.02) rectangle (163.18,131.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (159.18,123.02) -- (159.18,131.02);
\end{scope}
\end{tikzpicture}

\end{document}
}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.22,170.34) {a)};
\end{scope}
\end{tikzpicture}

\end{document}

### 2023-06-30 reports/paper/resources/intervention-density-witnin-combos-b.tex
update paper

--- 2023-06-30 reports/paper/resources/intervention-density-witnin-combos-a.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:02:22
+% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:08
 % !TEX encoding = UTF-8 Unicode
@@
 
-\end{document}
-re}[x=1pt,y=1pt]
+\begin{tikzpicture}[x=1pt,y=1pt]
 \definecolor{fillColor}{RGB}{255,255,255}
@@
 
-\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,110.79);
+\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,159.58);
 
@@
 
-\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 62.00);
+\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 37.60);
 
@@
 
-\path[fill=fillColor] (113.39, 37.60) rectangle (120.69,159.58);
+\path[fill=fillColor] (113.39, 37.60) rectangle (120.69, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01,110.79);
+\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 68.10);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 62.00);
+\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 98.59);
 
-\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 68.10);
 
-\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 37.60);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 62.29) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 65.34) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 89.74) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 95.83) {20};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,117.18) {15};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,126.33) {30};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,144.62) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,156.82) {40};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 65.05) --
-	( 38.22, 65.05);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 68.10) --
+	( 38.22, 68.10);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 92.49) --
-	( 38.22, 92.49);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 98.59) --
+	( 38.22, 98.59);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,119.93) --
-	( 38.22,119.93);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,129.08) --
+	( 38.22,129.08);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,147.38) --
-	( 38.22,147.38);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,159.58) --
+	( 38.22,159.58);
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,143.84) rectangle (244.lor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (155.18,142.55) rectangle (244.94,168.08);
+\path[fill=fillColor] (168.95,143.84) rectangle (244.95,163.87);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (155.18,161.56) {Distribution:\ \ \ };
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,157.35) {Target exposure limit:};
 \end{scope}
@@
 
-\path[fill=fillColor] (155.18,150.55) rectangle (163.18,158.55);
+\path[fill=fillColor] (168.95,146.34) rectangle (176.95,154.34);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.34) -- (172.95,154.34);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.59) {0.25 mg/m$^3$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (168.95,113.81) rectangle (240.85,141.84);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.32) {Distribution:};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
 \end{scope}
@@
 
-\path[fill=fillColor] (155.18,150.55) rectangle (163.18,158.55);
+\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
 \end{scope}
@@
 
-\path[fill=fillColor] (155.18,142.55) rectangle (163.18,150.55);
+\path[fill=fillColor] (168.95,116.31) rectangle (176.95,124.31);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt] (155.68,143.05) rectangle (162.68,150.05);
+\path[draw=drawColor,line width= 0.4pt] (169.45,116.81) rectangle (176.45,123.81);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.18,151.79) {Post-intervention\ \ \ \ };
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,125.55) {Post-intervention};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.18,143.79) {Observed};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (155.18,123.02) rectangle (231.18,140.55);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (155.18,134.03) {Target exposure limit:};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (155.18,123.02) rectangle (163.18,131.02);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (159.18,123.02) -- (159.18,131.02);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.36,170.34) {b)};
 \end{scope}
@@
 \end{document}
-}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.22,170.34) {a)};
-\end{scope}
-\end{tikzpicture}
-
-\end{document}

### 2023-06-30 reports/paper/resources/intervention-density-witnin-combos-c.tex
update paper

--- 2023-06-30 reports/paper/resources/intervention-density-witnin-combos-b.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:08
+% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:09
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,159.58);
+\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
 
@@
 
-\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 46.98);
 
-\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);
+\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 46.98);
 
@@
 
-\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);
+\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 46.98);
 
-\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);
+\path[fill=fillColor] (222.86, 37.60) rectangle (230.16,159.58);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 68.10);
+\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 98.59);
+\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 68.10);
+\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 46.98);
 
-\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 46.98);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 46.98);
 
-\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16,159.58);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 65.34) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 72.38) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 95.83) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,109.91) {20};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,126.33) {30};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,156.82) {40};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,147.44) {30};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 68.10) --
-	( 38.22, 68.10);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 75.13) --
+	( 38.22, 75.13);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 98.59) --
-	( 38.22, 98.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,112.66) --
+	( 38.22,112.66);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,129.08) --
-	( 38.22,129.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,159.58) --
-	( 38.22,159.58);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,150.19) --
+	( 38.22,150.19);
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,143.84) rectangle (244.95,163.87);
+\path[fill=fillColor] ( 42.31,143.84) rectangle (118.31,163.87);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,157.35) {Target exposure limit:};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 42.31,157.35) {Target exposure limit:};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,146.34) rectangle (176.95,154.34);
+\path[fill=fillColor] ( 42.31,146.34) rectangle ( 50.31,154.34);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.34) -- (172.95,154.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] ( 46.31,146.34) -- ( 46.31,154.34);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.59) {0.25 mg/m$^3$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,147.59) {0.25 mg/m$^3$};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,113.81) rectangle (240.85,141.84);
+\path[fill=fillColor] ( 42.31,113.81) rectangle (114.21,141.84);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.32) {Distribution:};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 42.31,135.32) {Distribution:};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
+\path[fill=fillColor] ( 42.31,124.31) rectangle ( 50.31,132.31);
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,116.31) rectangle (176.95,124.31);
+\path[fill=fillColor] ( 42.31,116.31) rectangle ( 50.31,124.31);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt] (169.45,116.81) rectangle (176.45,123.81);
+\path[draw=drawColor,line width= 0.4pt] ( 42.81,116.81) rectangle ( 49.81,123.81);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,125.55) {Post-intervention};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,125.55) {Post-intervention};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,117.55) {Observed};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.36,170.34) {b)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.08,170.34) {c)};
 \end{scope}

### 2023-06-30 illustrate-intervention-distribution.R

@@ -152,37 +152,39 @@ soluble_combo_distributions <- rbindlist(list(
 ), idcol = T)
 
 soluble_combo_distributions[,.id := factor(.id, labels = c(
-	"Supported exposure limit $=$ target limit",
-	"Supported exposure limit $<$ target limit",
-	"No limit (all observed exposures $>$ target limit)"
+	"Target exposure limit is supported",
+	"Supportable exposure limit below target",
+	"None below target exposure limit"
 ))]
 
 
 
 mytheme <- theme_bw() +
-		theme(legend.position = 'bottom',
-					legend.box = 'vertical',
-					legend.margin = margin(t = -5, b = 5),
-					panel.grid = element_blank(),
-					panel.border = element_rect(color = "black", linewidth = 8 / .pt),
-					strip.background = element_rect(color = 'black', fill="lightgrey", linewidth = 8 / .pt),
-					legend.key.size = unit(12, 'pt'),
-					legend.title = element_text(size = 9, colour = 'black'),
-					legend.text = element_text(size = 9, colour = 'black'),
-					legend.spacing.x = unit(5, 'pt'),
-					axis.text = element_text(size = 9, colour = 'black'),
-					axis.ticks = element_line(linewidth = 8 / .pt),
-					axis.title.y = element_text(size = 9, margin = margin(r = 6)),
-					axis.title.x = element_text(size = 9, margin = margin(t = 6)),
-					plot.margin = margin(l = 6, r = 6)
-		)
+	theme(legend.position = 'bottom',
+				legend.box = 'vertical',
+				legend.margin = margin(t = 5, b = 5),
+				panel.grid = element_blank(),
+				panel.border = element_rect(color = "black", linewidth = 1 / .pt),
+				strip.background = element_rect(
+					color = 'black', fill="lightgrey", linewidth = 1 / .pt),
+				axis.ticks = element_line(linewidth = 1 / .pt),
+				legend.key.size = unit(8, 'pt'),
+				legend.spacing.x = unit(2, 'pt'),
+				legend.spacing.y = unit(2, 'pt'),
+				legend.title = element_text(size = 8, colour = 'black'),
+				legend.text  = element_text(size = 8, colour = 'black'),
+				axis.text    = element_text(size = 8, colour = 'black'),
[…]

### 2023-08-05 reports/SER (2023)/resources/intervention-density.tex
New intervention

@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:02:21
+% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:49:02
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[fill=fillColor] (172.93, 85.04) rectangle (184.59,125.28);
+\path[fill=fillColor] (172.93, 85.04) rectangle (184.59,134.47);
 
-\path[fill=fillColor] (184.59, 85.04) rectangle (196.25,109.90);
+\path[fill=fillColor] (184.59, 85.04) rectangle (196.25,107.84);
 
-\path[fill=fillColor] (196.25, 85.04) rectangle (207.90, 94.28);
+\path[fill=fillColor] (196.25, 85.04) rectangle (207.90, 91.09);
 
-\path[fill=fillColor] (207.90, 85.04) rectangle (219.56, 90.96);
+\path[fill=fillColor] (207.90, 85.04) rectangle (219.56, 87.76);
 
-\path[fill=fillColor] (219.56, 85.04) rectangle (231.21, 85.54);
+\path[fill=fillColor] (219.56, 85.04) rectangle (231.21, 85.25);
 
-\path[fill=fillColor] (231.21, 85.04) rectangle (242.87, 85.72);
+\path[fill=fillColor] (231.21, 85.04) rectangle (242.87, 85.35);
 
-\path[fill=fillColor] (242.87, 85.04) rectangle (254.52, 85.06);
+\path[fill=fillColor] (242.87, 85.04) rectangle (254.52, 85.04);
 \definecolor{drawColor}{RGB}{186,129,35}
@@
 
-\path[draw=drawColor,line width= 3.2pt] (114.66, 85.04) rectangle (126.31, 88.47);
+\path[draw=drawColor,line width= 3.2pt] (114.66, 85.04) rectangle (126.31, 88.48);
 
@@
 
-\path[draw=drawColor,line width= 3.2pt] (161.28, 85.04) rectangle (172.93,124.15);
+\path[draw=drawColor,line width= 3.2pt] (161.28, 85.04) rectangle (172.93,124.16);
 
-\path[draw=drawColor,line width= 3.2pt] (172.93, 85.04) rectangle (184.59,132.93);
+\path[draw=drawColor,line width= 3.2pt] (172.93, 85.04) rectangle (184.59,132.94);
 
-\path[draw=drawColor,line width= 3.2pt] (184.59, 85.04) rectangle (196.25,141.93);
+\path[draw=drawColor,line width= 3.2pt] (184.59, 85.04) rectangle (196.25,141.94);
 
-\path[draw=drawColor,line width= 3.2pt] (196.25, 85.04) rectangle (207.90,115.25);
+\path[draw=drawColor,line width= 3.2pt] (196.25, 85.04) rectangle (207.90,115.26);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,106.25) {0.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,106.26) {0.2};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,130.22) {0.4};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,130.23) {0.4};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,154.19) {0.6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,154.21) {0.6};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,178.16) {0.8};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,178.18) {0.8};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,132.98) --
-	( 34.23,132.98);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,132.99) --
+	( 34.23,132.99);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,156.95) --
-	( 34.23,156.95);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,156.96) --
+	( 34.23,156.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,180.92) --
-	( 34.23,180.92);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,180.94) --
+	( 34.23,180.94);
 \end{scope}

### 2023-08-05 reports/paper/paper.qmd
New intervention

@@
 
-**Keywords:** Metalworking fluid, occupational exposure, non-Hodgkin
-lymphoma, cancer, positivity, overlap, causal inference, g-formula,
+**Keywords:** Positivity, overlap, causal inference, g-formula,
+metalworking fluid, occupational exposure, non-Hodgkin lymphoma, cancer,
 iterated conditional expectation, healthy-worker effect
 
-**Word count** **(Limit: 1500 to 4000 words):** 3812
+**Word count** **(Limit: 1500 to 4000 words):** 3812 (approx)
 
@@
 **Background:** Non-Hodgkin lymphoma (NHL) incidence has increased
-substantially in the US since 1960 and was recently linked to workplace
-exposure to soluble metalworking fluids (MWF) in a standard survival
-analysis of the United Auto Workers-General Motors (UAW-GM) cohort.
-Here, we estimate the effects of hypothetical interventions on soluble
-MWF exposure in relation to NHL risk in the same cohort of autoworkers.
-Estimation of causal effects requires positivity, which we guarantee by
-investigating causal contrasts that are supportable by the data.
+substantially in the US and was recently linked to workplace exposure to
+soluble metalworking fluids (MWF) in a standard survival analysis of the
+United Auto Workers-General Motors (UAW-GM) cohort. Here, we estimate
+the effects of hypothetical interventions on soluble MWF exposure in
+relation to NHL risk in the same cohort of autoworkers. Estimation of
+causal effects requires positivity, which we guarantee by investigating
+causal contrasts that are supportable by the data.
 
@@
 2015 in the UAW-GM cohort of autoworkers at three Michigan plants (n =
-33,134) under supportable interventions on exposure to soluble MWF. The
-supportable intervention reduces annual daily average exposures above
-the target limit to that limit when the target limit is supported by
+33,134) under hypothetical supportable interventions on exposure to
+soluble MWF. A supportable intervention reduces annual daily average
+exposures above a specific target limit to that limit when supported by
 data. Otherwise, the supportable intervention reduces exposure to the
-highest level of exposure below the target limit or not at all,
-depending on support.
+highest level below the target limit or not at all, depending on
+support.
 
@@
 
-**Conclusion:** Stronger limits on exposure to soluble MWF provide
+**Conclusion:** More stringent limits on exposure to soluble MWF provide
 stronger protections against NHL. We expect the effects of enforcing the
@@
 Metalworking fluids are complex mixtures of oil, water, and chemical
-additives that optimize metal machining operations. There are three
-general types of MWF: straight, soluble, and synthetic. During shaping,
-grinding, and cutting operations, MWFs are misted, poured, or blasted at
-high pressure onto work surfaces to remove debris, cool metal, improve
-efficiency, and prevent deterioration of tools. Although MWFs are
-essential to manufacturing processes, they also present a potential
-health hazard to exposed workers through inhalation or ingestion of MWF
-particulate mass. In response to health concerns and the rising cost of
-oil, soluble MWF were developed to replace straight MWF and are now the
-most commonly used type [@Byers_2006].
+additives that cool and lubricate metal machining operations. There are
+three general types of MWF: straight, soluble, and synthetic. During
+shaping, grinding, and cutting operations, MWFs are misted, poured, or
+blasted at high pressure onto work surfaces to remove debris, cool
+metal, improve efficiency, and prevent deterioration of tools. Although
+MWFs are essential to manufacturing processes, they also present a
+potential health hazard to exposed workers through inhalation or
+ingestion of MWF particulate mass. In response to health concerns
+related to the carcinogenicity of polycyclic aromatic hydrocarbons
+(PAHs) in mineral oil as well as the rising global cost of oil products,
+water-based soluble MWF, which usually contain about 40-70% oil by
+weight, were developed to replace oil-based straight MWF [@IARC_1973;
+@IARC_1987; @Childers_2006]. Today, soluble MWF is the most common type
+of MWF in metal machining operations [@Byers_2006].
 
@@
 @Richardson_2013]. A central requirement necessary for causal inference
-is positivity (overlap) ie adequate variation in the exposure of
-interest within strata formed by confounder and exposure histories
-[@Petersen_2012].
+from observational data is positivity (overlap) ie adequate variation in
+the exposure of interest within strata formed by confounder and exposure
+histories [@Petersen_2012].
 
 Common approaches for addressing violations in positivity are
-model-based smoothing when using outcome-regression techniques, weight
+model-based smoothing when using outcome regression methods, weight
 truncation when using propensity methods, or a combination of both.
-Another approach is to consider only those causal contrasts that are
-supported by the observed data ie have strictly positive propensity
-score. Here, we defined supportable interventions on exposure to soluble
-MWF in the United Auto Workers-General Motors (UAW-GM) occupational
-cohort whose effects can be estimated with guaranteed positivity. We
-estimated the cumulative incidence of NHL between 1985 and 2015 under
-supportable interventions based on selected target exposure limits on
-annual average daily exposure by applying the the hazard-extended
-iterative conditional expectation (ICE) parametric g-formula
-[@Arrighi_1994; @Wen_2020].
+Another approach is to only consider causal contrasts that are supported
+by the observed data ie those involving hypothetical interventions with
+propensity score strictly greater than zero. Here, we defined
+hypothetical supportable interventions on exposure to soluble MWF in the
+United Auto Workers-General Motors (UAW-GM) occupational cohort and
+estimated their effects on NHL incidence between 1985 and 2015 relative
+to no exposure intervention while guaranteeing positivity.
 
@@
 
-We estimated NHL cumulative incidence from 1985 to 2015 under
-supportable interventions on on annual average daily exposure to soluble
-MWF based on several target exposure limits. First, we estimated the
-expected number of NHL cases that we would observe if there were no
-censoring by censoring and no target exposure limit. Then, we contrasted
-this case count to that under supportable interventions based on five
-hypothetical target exposure limits and no censoring. The five target
-exposure limits were (1) 2.0, (2) 1.0, (3) 0.5, (4) 0.25, and (5) 0.05
-mg/m^3^. The National Institute for Occupational Safety and Health
-(NIOSH) recommended exposure limit (REL) for time-weighted average total
-particulate mass (PM) composed of MWF is 0.5 mg/m^3^ [@niosh_1998].
+We estimated the cumulative incidence of NHL between 1985 and 2015 under
+supportable interventions based on selected target exposure limits on
+annual average daily exposure to soluble MWF by applying the the
+hazard-extended iterative conditional expectation (ICE) parametric
+g-formula [@Wen_2020]. First, we estimated the expected number of NHL
+cases that we would observe if there were no censoring and no limit on
+exposure. Then, we contrasted this case count to that under supportable
+interventions based on five hypothetical target exposure limits and no
+censoring. The five target exposure limits were (1) 2.0, (2) 1.0, (3)
+0.5, (4) 0.25, and (5) 0.05 mg/m^3^. The National Institute for
+Occupational Safety and Health (NIOSH) recommended exposure limit (REL)
+for time-weighted average total particulate mass (PM) composed of MWF is
+0.5 mg/m^3^ [@niosh_1998].
 
-For each target exposure limit, period of follow-up, and strata defined
+For each target exposure limit, period of follow-up, and stratum defined
 by unique combinations of confounder and exposure histories, we found a
 supportable exposure limit, which was the maximum observed value of
-exposure at or below the target exposure limit. If all of the observed
-values were above the target limit, no limit was enforced for that
-stratum. The supportable intervention rule then reduces exposures above
-the supportable exposure limit to that limit, but allowed exposures at
-or below the limit to vary according to their observed distribution.
-Applying the supportable intervention rule to the observed distribution
-of exposure produces the intervention distribution that defines the
-corresponding stochastic dynamic intervention with guaranteed
-positivity. We estimated the effect of supportable intervention rules
-based on selected target exposure limits, expressed as stochastic
-dynamic interventions, using the hazard-extended ICE parametric
-g-formula [@Wen_2020].
+exposure at or below the target exposure limit, if such a value exists.
+If all of the observed values were above the target limit, the
+supportable limit was simply the maximum observed value. The supportable
+intervention rule then reduces exposures above the supportable exposure
+limit to that limit, but allows exposures at or below the limit to vary
+according to their observed distribution. Applying the supportable
+intervention rule to the observed distribution of exposure produces the
+intervention distribution that defines the corresponding stochastic
+dynamic intervention with guaranteed positivity. We estimated the effect
+of supportable intervention rules based on the selected target exposure
+limits, expressed as stochastic dynamic interventions, using the
+hazard-extended ICE parametric g-formula [@Wen_2020].
 
@@
 
-We used data from the UAW-GM cohort, which included all hourly workers
-at three automobile manufacturing plants in Michigan who had worked at
-least three years by 1985. Past papers provide detailed descriptions of
-the cohort [@Eisen_1992; @Eisen_2001]. The large size of the study
-population and rich time-varying, quantitative MWF exposure data enable
-the study of this relatively rare cancer and evaluate realistic
+We used data from the UAW-GM cohort study, which included all hourly
+workers at three automobile manufacturing plants in Michigan who had
+worked at least three years by 1985. Past papers provide detailed
+descriptions of the cohort [@Eisen_1992; @Eisen_2001]. The large size of
+the study population and rich time-varying, quantitative MWF exposure
+data enable the study of a relatively rare cancer and evaluate realistic
 interventions on MWF exposure in a longitudinal cohort setting. The
@@
 who were at work in 1941 or not yet hired, missing no more than half of
-their employment history, and still alive at the start of follow-up.
-Autoworkers in the study population were followed for NHL incidence from
-January 1, 1985 until NHL diagnosis, death, December 31, 2014 (30 years
-after the end of employment record availability), or the oldest observed
-age at death (108 years), whichever came earlier.
+their employment history, and still alive at the start of follow-up for
+cancer incidence on January 1, 1941. Autoworkers in the study population
+were followed until NHL diagnosis, death, December 31, 2014, or the
+oldest observed age at death, whichever came earlier.
 
@@
 
-Potential confounders including year of hire, sex, race, time off,
+Potential confounders including year of hire, sex, race, time off work,
 employment status, and plant location were obtained from company
@@
 distinguishing strength of the UAW-GM cohort study relative to other
-occupational cohort studies. Exposure assessment was based on direct air
-sampling as well as company records. Company industrial hygienists
-collected several hundred personal and area samples for total
-particulate matter (mg/m^3^) composed of MWF over many decades. Research
-industrial hygienists collected additional air sampling data when the
-cohort study was launched in the mid 1980s. These additional data
-combined with historical data and company records constituted a
-job-exposure matrix of quantitative 8-hour time-weighted average daily
-exposure estimates to soluble, straight, and synthetic MWF for each
-combination of job, department, and plant over time. Workers' annual
-average daily exposure to each MWF type was determined by combining this
+environmental or occupational health studies. Exposure assessment was
+based on direct air sampling as well as company records. Company
+industrial hygienists collected several hundred personal and area
+samples for total particulate mass (mg/m^3^) composed of MWF over many
+decades. Research industrial hygienists collected additional air
+sampling data when the cohort study was launched in the mid 1980s
+[@Woskie_1994; @Woskie_1994a]. These additional data combined with
+historical data and company records constituted a job-exposure matrix of
+quantitative 8-hour time-weighted average daily exposure estimates to
+soluble, straight, and synthetic MWF for each combination of job,
+department, and plant over time [@Hallock_1994]. Workers' annual average
+daily exposure to each MWF type was determined by combining this
 job-exposure matrix with employment records, which recorded time-varying
@@
 
-Previous analyses of NHL applied exposure lags of 1 to 20 years to
-account for disease latency; we lagged cumulative MWF exposures by 20
-years and therefore ended follow-up on January 1, 2015 [@Smith_2007;
-@Karipidis_2007; @Zhang_2019]. In analyses, MWF exposure history at
-start of follow-up was summarized as the cumulative sum of average
-exposure intensities. Exposure was coded as categorical variables with
-cut-points at zero and the quintiles of nonzero exposure among cases. We
-estimated the effects of interventions on soluble MWF, the type of MWF
-used most widely and in the greatest quantities while treating
-co-exposure to straight and synthetic MWFs as potential confounders.
+In previous analyses of NHL, exposure lags of 1 to 20 years were applied
+to account for disease latency; we lagged cumulative MWF exposures by 20
+years [@Smith_2007; @Karipidis_2007; @Zhang_2019]. In analyses, MWF
+exposure history at start of follow-up was summarized as the cumulative
+sum of average exposure intensities. Exposure was coded as categorical
+variables with cut-points at zero and the quintiles of nonzero exposure
+among cases. We estimated the effects of hypothetical interventions on
+soluble MWF, the type of MWF used most widely and in the greatest
+quantities while treating co-exposure to straight and synthetic MWFs as
+potential confounders.
 
@@
 deciles of the dates of diagnosis of NHL. The number of years per period
-ranged from two to four years. The hazard-extended ICE parametric
-g-formula involves two stages. In the first, we estimate counterfactual
-discrete hazards over the person-periods. In the second, we pool those
-estimates to estimate the counterfactual risk over the entire follow-up
-period. During pooling, we iteratively combine estimates of the
-counterfactual hazard to obtain a pooled estimate over an increasing
-number of periods starting from the last period. In each iteration, we
-perform model-based standardization over exposure and covariate
-histories before combining the counterfactual discrete hazard estimate
-with the estimated hazard pooled over subsequent periods. This iterative
-process results in a sequentially standardized estimate of the
-counterfactual cumulative incidence of NHL when the intervention of
-interest is enforced over all follow-up periods.
+ranged from two to four. The hazard-extended ICE parametric g-formula
+involves two stages. In the first, we estimate counterfactual discrete
+hazards over the person-periods. In the second, we pool those estimates
+to estimate the counterfactual risk over the entire follow-up period.
+During pooling, we iteratively combine estimates of the counterfactual
+hazard to obtain a pooled estimate over an increasing number of periods
+starting from the last period. In each iteration, we perform model-based
+standardization over exposure and covariate histories before combining
+the counterfactual discrete hazard estimate with the estimated hazard
+pooled over subsequent periods. This iterative process results in a
+sequentially standardized estimate of the counterfactual cumulative
+incidence of NHL when the intervention of interest is enforced over all
+follow-up periods.
 
@@
 every value of exposure that could be assigned under the our stochastic
-dynamic intervention has a strictly positive propensity score. We took
-exposure to straight and synthetic MWF, employment status, cumulative
-time off, age, duration of employment, sex (male/female), race
-(Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3) to be
+dynamic intervention has propensity score strictly greater than zero. We
+treated co-exposure to straight and synthetic MWF, employment status,
+cumulative time off, age, duration of employment, sex (male/female),
+race (Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3) as
 potential confounders. Exposure to MWF, employment status, time off, and
@@
 
-1.  Fit a pooled logistic regression of NHL on potential confounders and
-    exposure over all at-risk person-periods.
+1.  Fit a pooled logistic regression model for NHL on potential
+    confounders and exposure over all at-risk person-periods.
 
@@
 We estimated cumulative incidence under no intervention on soluble MWF
-and under the supportable interventions based on the five target
-exposure limits. We contrasted the cumulative incidence under the
+and under the supportable interventions based on the five selected
+target exposure limits. We contrasted the cumulative incidence under the
 supportable interventions to that under no intervention on exposure by
@@
 bootstrap with 1000 Monte Carlo samples from the population at the start
-of follow-up. All the necessary script used to reproduce the analyses
+of follow-up. All the necessary scripts used to reproduce the analyses
 are available on [GitHub](https://github.com/kvntchn/gm-nhl-ice).
@@
 with approximately 88% of workers ever exposed. Median cumulative
-exposure among the exposed was 6 times higher for soluble than for
-straight MWF. Figure 2 shows median annual average daily exposure to the
-three MWF types among exposed workers over calendar time. Exposure to
-MWF generally followed a downward trend over time.
+exposure among the exposed was approximately 6 times higher for soluble
+than for straight MWF. Figure 2 shows median annual average daily
+exposure to the three MWF types among exposed workers over calendar
+time. Exposure to MWF generally followed a downward trend over time.
 
@@
   footnote(i = grep("Ever exposed|time off", rownames(tab1.sub)), j = 1, value = as_paragraph(
-    " Lagged 10 years"),
+    " Lagged 20 years"),
     ref_symbols = "b", inline = T) |>
-  footnote(i = grep("work", rownames(tab1.sub)), j = 1, value = as_paragraph(
-    " Among those who left work by December 31, 1994"),
-    ref_symbols = "c", inline = T) |>
+  # footnote(i = grep("work", rownames(tab1.sub)), j = 1, value = as_paragraph(
+  #   " Among those who left work by December 31, 1994"),
+  #   ref_symbols = "c", inline = T) |>
   # footnote(i = grep("death", rownames(tab1.sub)), j = 1, value = as_paragraph(
@@
   footnote(i = grep("Cumulative exposure", rownames(tab1.sub)), j = 1, value = as_paragraph(
-    " Among ever-exposed individuals, lagged 10 years."),
+    " Among ever-exposed individuals, lagged 20 years."),
     ref_symbols = "d", inline = T) |>
@@
 The observed number of NHL cases over the 30-year follow-up period was
-339. Table 2 presents the hazard-extended ICE parametric g-formula
-estimates of the counterfactual number of cases, number of cases
-averted, and cumulative incidence ratios contrasting supportable
-interventions on exposure to soluble MWF based on different target
-exposure limits and no censoring. Under an intervention eliminating
-censoring, the estimated number of cases was 502 (95% CI: 439, 555).
-Interventions based on stronger target exposure limits on soluble MWF
-resulted in monotonically stronger reductions in the estimated
-cumulative incidence of NHL. Setting the target exposure limit at the
-NIOSH REL 0.5 mg/m^3^ would have averted 112 (95% CI: 57, 181) NHL
-cases.
+339. Table 2 presents estimates of the counterfactual number of cases,
+number of cases averted, and cumulative incidence ratios contrasting
+supportable interventions on exposure to soluble MWF based on different
+target exposure limits and no censoring. Under an intervention
+eliminating censoring, the estimated number of cases was 502 (95% CI:
+439, 555). Interventions based on stronger target exposure limits on
+soluble MWF resulted in monotonically stronger reductions in the
+estimated cumulative incidence of NHL. Setting the target exposure limit
+at the NIOSH REL 0.5 mg/m^3^ would have averted 112 (95% CI: 57, 181)
+NHL cases.
 
@@
 pancreas, skin, scrotum, and bladder cancer, their REL of 0.5 mg/m^3^
-for total particulate matter derived from any type of MWF targeted risk
-of nonmalignant health conditions [@niosh_1998; @Mirer_2003]. Exposure
-limits stronger than the NIOSH REL may provide valuable health
-protections not previously considered by policy makers. Using the
-hazard-extended ICE parametric g-formula, we estimated the
+for total particulate mass derived from any type of MWF was based on
+nonmalignant respiratory health effects [@niosh_1998; @Mirer_2003].
+Exposure limits stronger than the NIOSH REL may provide valuable health
+protections not previously taken into account by policy makers. Using
+the hazard-extended ICE parametric g-formula, we estimated the
 counterfactual expected number of NHL cases from 1985 to 2015 in the
-UAW-GM cohort if we enforced supportable interventions on soluble MWF
-based on five different target exposure limits and found a monotonic
-exposure-dependent relationship where stronger target exposure limits
-yielded lower NHL case count estimates.
+UAW-GM cohort if we enforced hypothetical supportable interventions on
+soluble MWF based on five different target exposure limits and found a
+monotonic exposure-dependent relationship where stronger target exposure
+limits yielded lower NHL case count estimates.
 
@@
 probability weighted expectation. The classic parametric g-formula is a
-plug in estimator for the g-formula under its first, non-iterative,
+plug-in estimator for the g-formula under its first, non-iterative,
 representation. It involves the parametric modeling of the full joint
@@
 guarantee positivity. Interventions that guarantee positivity have been
-suggested in the past, and have also been called "realistic"
+suggested in the past and have also been called "realistic"
 interventions [@Petersen_2012].
@@
 [@Zheng_2002]. Both of these occupations may entail exposure to soluble
-MWF, which contain a number of additives of concern for human health and
-for NHL risk in particular. Organic compounds containing phosphorous,
-chlorine, sulfur, nitrogen, and boron are commonly added to soluble MWF
-to control microbial growth, improve performance under high
-heat/pressure, and inhibit corrosion [@Evans_2020]. Organophosphorus
-compounds include organophosphate pesticides, which have been linked to
-cancer risk in epidemiologic and animal studies. Some were classified as
-possibly carcinogenic by the IARC [@IARC_2017]. Studies of occupational
-exposure to chlorinated solvents and pesticides have also been linked to
-NHL risk [@Cocco_2008; @Purdue_2011; @Cocco_2013; @Vlaanderen_2013;
-@Callahan_2018]. In 2014, the IARC classified trichloroethylene,
-tetrachloroethylene, and other chlorinated agents as Group 1 carcinogens
-[@IARC_2014]. Chlorinated solvents are commonly used as degreasers in
-industrial settings, but their use in the plants under study here was
-rare [@Shrestha_2016]. The structural characteristics shared by MWF
-additives and known/suspected carcinogens suggest potential similarities
-in their behavior in biological systems.
+MWF, which contain mineral oils and a number of chemical additives of
+concern for human health and for NHL risk in particular. Organic
+compounds containing phosphorous, chlorine, sulfur, nitrogen, and boron
+are commonly added to soluble MWF to control microbial growth, improve
+performance under high heat/pressure, and inhibit corrosion
+[@Evans_2020]. Organophosphorus compounds include organophosphate
+pesticides, which have been linked to cancer risk in epidemiologic and
+animal studies. Some were classified as possibly carcinogenic by the
+IARC [@IARC_2017]. Studies of occupational exposure to chlorinated
+solvents and pesticides have also been linked to NHL risk [@Cocco_2008;
+@Purdue_2011; @Cocco_2013; @Vlaanderen_2013; @Callahan_2018]. In 2014,
+the IARC classified trichloroethylene, tetrachloroethylene, and other
+chlorinated agents as Group 1 carcinogens [@IARC_2014]. Chlorinated
+solvents are commonly used as degreasers in industrial settings, but
+their use in the plants under study here was rare [@Shrestha_2016]. The
+structural characteristics shared by MWF additives and known/suspected
+carcinogens suggest potential similarities in their behavior in
+biological systems.
 
@@
 stronger limits on MWF exposure in the real world because they
-explicitly restrict the causal contrasts we can evaluate to those
-supported by the observed data.
+explicitly restrict the causal contrasts to those supported by the
+observed data.
 
@@
 found evidence that limiting exposure to soluble MWF would reduce NHL
-incidence in an analysis that guarantees positivity and adjusts for time-varying confounding affected by past exposure. \newpage
+incidence in an analysis that guarantees positivity and adjusts for
+time-varying confounding affected by past exposure. \newpage
 

### 2023-08-05 reports/paper/resources/intervention-density-witnin-combos-a.tex
New intervention

@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:02:22
+% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:49:59
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.18,143.79) {Observed};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (155.18,123.02) rectangle (231.18,140.55);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (155.18,134.03) {Target exposure limit:};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (155.18,123.02) rectangle (163.18,131.02);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (159.18,123.02) -- (159.18,131.02);
-\end{scope}
-\end{tikzpicture}
-
-\end{document}
-}
 \path[clip] (  0.00,  0.00) rectangle (252.94,180.67);

### 2023-08-05 reports/paper/resources/intervention-density-witnin-combos-c.tex
New intervention

@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:09
+% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:50:47
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 46.98);
+\path[fill=fillColor] (179.07, 37.60) rectangle (186.37,159.58);
 
-\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 46.98);
+\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);
 
@@
 
-\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 46.98);
+\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);
 
-\path[fill=fillColor] (222.86, 37.60) rectangle (230.16,159.58);
+\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 46.98);
+\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 45.22);
 
-\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 46.98);
+\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 45.22);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 46.98);
+\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 45.22);
 
-\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16,159.58);
+\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16,136.71);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 72.38) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 65.34) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,109.91) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 95.83) {20};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,147.44) {30};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,126.33) {30};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,156.82) {40};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 75.13) --
-	( 38.22, 75.13);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 68.10) --
+	( 38.22, 68.10);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,112.66) --
-	( 38.22,112.66);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 98.59) --
+	( 38.22, 98.59);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,150.19) --
-	( 38.22,150.19);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,129.08) --
+	( 38.22,129.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,159.58) --
+	( 38.22,159.58);
 \end{scope}

### 2023-08-05 g-formula.R

@@ -130,17 +130,24 @@ ice_gcomp <- function(
 			# Get non-followers
 			dta.probs_not_followed <- dta[
 				get(paste0("followed_", a)) == 0 & I == k,
-				dynamic.which, with = F]
+				c(dynamic.which, intervene.which), with = F]
+
+			# Get lowest exposure among non-followers
+			dta.probs_not_followed[,`:=`(
+				Exposure = levels(get(intervene.which))[
+					min(as.numeric(get(intervene.which)))]
+			), eval(dynamic.which)]
 
 			# Add rule-abiding exposure if positivity allows
-			dta.probs_not_followed <- dta.probs_not_followed[
-					dta.probs_barely_followed,
+			dta.probs_not_followed <- dta.probs_barely_followed[
+				dta.probs_not_followed,
 					on = dynamic.which
 				]
+			dta.probs_not_followed[is.na(Exposure), Exposure := i.Exposure]
 
 			# Combine distribution to get the intervention distribution
 			dta.probs <- rbindlist(list(
-				dta.probs_followed, dta.probs_not_followed
+				dta.probs_followed, dta.probs_not_followed[,names(dta.probs_followed), with = F]
 			))
 
 			# Get counts within exposure levels
@@ -348,17 +355,24 @@ ice_gcomp <- function(
 			# Get non-followers
 			dta.probs_not_followed <- dta.wide[
 				followed == 0 ,
-				dynamic.which, with = F]
+				c(dynamic.which, intervene.which.k), with = F]
+
+			# Get lowest exposure among non-followers
+			dta.probs_not_followed[,`:=`(
+				Exposure = levels(get(intervene.which.k))[
+					min(as.numeric(get(intervene.which.k)))]
+			), eval(dynamic.which)]
 
 			# Add rule-abiding exposure if positivity allows
-			dta.probs_not_followed <- dta.probs_not_followed[
-					dta.probs_barely_followed,
+			dta.probs_not_followed <- dta.probs_barely_followed[
+					dta.probs_not_followed,
 					on = dynamic.which
 				]
+			dta.probs_not_followed[is.na(Exposure), Exposure := i.Exposure]
 
 			# Combine distribution to get the intervention distribution
 			dta.probs <- rbindlist(list(
-				dta.probs_followed, dta.probs_not_followed
+				dta.probs_followed, dta.probs_not_followed[,names(dta.probs_followed), with = F]
 			))
 
 			dta.probs <- lapply(

### 2023-08-05 illustrate-intervention-distribution.R

@@ -120,7 +120,7 @@ a <- 0.25
 post_intervention <- dta.wide[,.(soluble = {
 	if (sum(get(paste0('soluble_', k)) <= a) > 0) {
 		max(get(paste0('soluble_', k))[get(paste0('soluble_', k)) <= a])
-	} else {NaN}
+	} else {min(get(paste0('soluble_', k)))}
 }), eval(dynamic.which)]
 
 soluble_distribution <- post_intervention[
@@ -138,13 +138,6 @@ soluble_combos <- dta.wide[, c('studyno', dynamic.which), with = F][
 	soluble_distribution, on = 'studyno'
 ]
 
-i <- 0; foo <- a
-while (i <= ncol(soluble_combos) & foo > a - 0.2) {
-	i <- i + 1
-	foo <- soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][i,], on = dynamic.which]
-	foo <- max(foo$`Post-intervention`)
-}
-
 soluble_combo_distributions <- rbindlist(list(
 	soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][1,], on = dynamic.which],
 	soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][8,], on = dynamic.which],
@@ -154,10 +147,8 @@ soluble_combo_distributions <- rbindlist(list(
 soluble_combo_distributions[,.id := factor(.id, labels = c(
 	"Target exposure limit is supported",
 	"Supportable exposure limit below target",
-	"None below target exposure limit"
+	"Supportable exposure limit above target"
 ))]
-
-
 
 mytheme <- theme_bw() +
 	theme(legend.position = 'bottom',

### 2023-08-05 run_g-formula.R

@@ -113,6 +113,7 @@ B <- 1e3
 # 	B = B,
 # 	interventions = list("Any", "200", "100", "50", "25", "05"))
 # # })
+# # 9.33 hours since get.bs() was called.
 # saveRDS(estimates.bs, here::here("resources", paste0("estimates.bs.rds")))
 
 # Examine BS sampling distribution ####

### 2023-08-28 reports/paper/paper.qmd
Reduce abstract length

@@
 
-**Authors:** Kevin T. Chen^a^, Sally Picciotto^b^, Ellen A. Eisen^b^
+**Authors:** Kevin T. Chen\^a, b\^, Sally Picciotto^c^, Ellen A.
+Eisen^c^
 
@@
 
-^b^ University of California, Berkeley School of Public Health, Division
+^b^ University of California, Berkeley Department of Statistics
+
+^c^ University of California, Berkeley School of Public Health, Division
 of Environmental Health Sciences
@@
 kevchen\@berkeley.edu\
-(510) 387-3327
+(510) 816-3408
 
-**Running head suggestion:** Supportable interventions for reducing NHL
-risk.
+**Running head suggestion:** Hypothetical interventions with guaranteed positivity
 
@@
 **Sources of financial support:** This work was supported by Training
-Grant T42OH008429 and Research Project Grant R01OH011092, both funded by
+Grant T42OH008429 and Research Project Grant R01OH011092, both from
 the National Institute for Occupational Safety and Health (NIOSH) /
@@
 
-**Word count** **(Limit: 1500 to 4000 words):** 3812 (approx)
+**Word count** **(Limit: 1500 to 4000 words):** 3842 (approx)
 
@@
 
-**Methods:** We estimated counterfactual risk of NHL between 1985 and
-2015 in the UAW-GM cohort of autoworkers at three Michigan plants (n =
-33,134) under hypothetical supportable interventions on exposure to
-soluble MWF. A supportable intervention reduces annual daily average
-exposures above a specific target limit to that limit when supported by
-data. Otherwise, the supportable intervention reduces exposure to the
-highest level below the target limit or not at all, depending on
-support.
+**Methods:** We defined hypothetical supportable interventions that
+reduce annual daily average exposures above a specific target limit to
+that limit when supported by data. When the target limit is not
+supported, the intervention reduces exposure to the nearest supported
+level of exposure. We estimated counterfactual risk of NHL between 1985
+and 2015 in the UAW-GM cohort of autoworkers at three Michigan plants (n
+= 33,134) under hypothetical supportable interventions on exposure to
+soluble MWF.
 
@@
 reductions in NHL risk. Setting the target exposure limit at 0.5
-mg/m^3^, the NIOSH recommended exposure limit, would have prevented 112
-(95% CI: 57, 181) cases.
+mg/m^3^, the NIOSH recommended exposure limit, would have prevented 124
+(95% CI: 66, 202) cases.
 
 **Conclusion:** More stringent limits on exposure to soluble MWF provide
-stronger protections against NHL. We expect the effects of enforcing the
-target exposure limits uniformly to have even stronger protective
-effects. Strengthening exposure limits for MWF may protect workers from
-NHL during the anticipated boom in domestic manufacturing.
+stronger protections against NHL. We expect that uniformly enforcing the
+target exposure limits, regardless of data support, would have even
+stronger protective effects. Strengthening exposure limits for MWF may
+protect workers from NHL during the anticipated boom in domestic
+manufacturing.
 
@@
 Non-Hodgkin Lymphoma (NHL) incidence in the United States doubled
-between 1973 and 1994, before plateauing at around 19 per 100,000
-persons per year, making it the seventh most common cancer in the
-country [@seer_1994; @Ekstrom-Smedby_2006]. The strongest known risk
-factor of NHL is immunosuppression, both congenital and acquired
+between 1973 and 1994 before plateauing at around 19 per 100,000 persons
+per year, making it the seventh most common cancer in the country
+[@seer_1994; @Ekstrom-Smedby_2006]. The strongest known risk factor of
+NHL is immunosuppression, both congenital and acquired
 [@Filipovich_1992; @Chiu_2015]. However, since immunodeficiency and
@@
 accumulate more exposure while those more susceptible to the deleterious
-health effects of exposure leave work [@Arrighi_1994]. An early causal
-inference method in statistics developed to estimate causal effects in
-longitudinal observational studies where the HWSE or other forms of
-time-varying confounding/selection bias affected by past exposure may be
-operating is the parametric g-formula [@Robins_1986; @Taubman_2009;
+health effects of exposure leave work [@Arrighi_1994]. The parametric
+g-formula is an early causal inference method in statistics developed to
+estimate causal effects in longitudinal observational studies where the
+HWSE or other forms of time-varying confounding/selection bias affected
+by past exposure may be operating [@Robins_1986; @Taubman_2009;
 @Richardson_2013]. A central requirement necessary for causal inference
-from observational data is positivity (overlap) ie adequate variation in
-the exposure of interest within strata formed by confounder and exposure
-histories [@Petersen_2012].
+from observational data is positivity (overlap), *i.e.,* adequate
+variation in the exposure of interest within strata formed by confounder
+and exposure histories [@Petersen_2012].
 
@@
 Another approach is to only consider causal contrasts that are supported
-by the observed data ie those involving hypothetical interventions with
-propensity score strictly greater than zero. Here, we defined
+by the observed data, *i.e.,* those involving hypothetical interventions
+with propensity score strictly greater than zero. Here, we defined
 hypothetical supportable interventions on exposure to soluble MWF in the
@@
 supportable interventions based on selected target exposure limits on
-annual average daily exposure to soluble MWF by applying the the
+annual average daily exposure to soluble MWF by applying the
 hazard-extended iterative conditional expectation (ICE) parametric
@@
 If all of the observed values were above the target limit, the
-supportable limit was simply the maximum observed value. The supportable
+supportable limit was the minimum observed value. The supportable
 intervention rule then reduces exposures above the supportable exposure
@@
 level. In Figure 1b, the supportable exposure limit is below the target
-exposure limit. In Figure 1c, there is no limit on exposure because no
-individuals in that stratum experienced exposure below the target
-exposure limit.
+exposure limit. In Figure 1c, the supportable exposure limit, the
+minimum observed level of exposure in that stratum, is greater than the
+target exposure limit.
 
@@
 the study population and rich time-varying, quantitative MWF exposure
-data enable the study of a relatively rare cancer and evaluate realistic
-interventions on MWF exposure in a longitudinal cohort setting. The
-present study population (N = 33,134) was restricted to the autoworkers
-who were at work in 1941 or not yet hired, missing no more than half of
-their employment history, and still alive at the start of follow-up for
-cancer incidence on January 1, 1941. Autoworkers in the study population
-were followed until NHL diagnosis, death, December 31, 2014, or the
-oldest observed age at death, whichever came earlier.
+data enable the study of a relatively rare cancer and evaluation of
+realistic interventions on MWF exposure in a longitudinal cohort
+setting. The present study population (N = 33,134) was restricted to the
+autoworkers who were at work in 1941 or not yet hired, missing no more
+than half of their employment history, and still alive at the start of
+follow-up for cancer incidence on January 1, 1985. Autoworkers in the
+study population were followed until NHL diagnosis, death, December 31,
+2014, or the oldest observed age at death, whichever came earlier.
 
@@
 [@Woskie_1994; @Woskie_1994a]. These additional data combined with
-historical data and company records constituted a job-exposure matrix of
-quantitative 8-hour time-weighted average daily exposure estimates to
-soluble, straight, and synthetic MWF for each combination of job,
-department, and plant over time [@Hallock_1994]. Workers' annual average
-daily exposure to each MWF type was determined by combining this
-job-exposure matrix with employment records, which recorded time-varying
-job type, department, and plant for each employee from hire to
-termination or 1995, whichever came sooner. For employment records that
-were at least half complete, gaps in the record were interpolated by
-carrying forward the last known job type. The exposure assessment is
-described in detail elsewhere [@Hallock_1994; @Woskie_1994;
-@Woskie_2003].
+historical data and company records were used to construct a
+job-exposure matrix of quantitative 8-hour time-weighted average daily
+exposure estimates to soluble, straight, and synthetic MWF for each
+combination of job, department, and plant over time [@Hallock_1994].
+Workers' annual average daily exposure to each MWF type was determined
+by combining this job-exposure matrix with employment records, which
+recorded time-varying job type, department, and plant for each employee
+from hire to termination or 1995, whichever came sooner. For employment
+records that were at least half complete, gaps in the record were
+interpolated by carrying forward the last known job type. The exposure
+assessment is described in detail elsewhere [@Hallock_1994;
+@Woskie_1994; @Woskie_2003].
 
@@
 We investigated supportable interventions that guarantee positivity:
-every value of exposure that could be assigned under the our stochastic
+every value of exposure that could be assigned under our stochastic
 dynamic intervention has propensity score strictly greater than zero. We
@@
 estimated cumulative incidence of NHL. Setting the target exposure limit
-at the NIOSH REL 0.5 mg/m^3^ would have averted 112 (95% CI: 57, 181)
+at the NIOSH REL 0.5 mg/m^3^ would have averted 124 (95% CI: 66, 202)
 NHL cases.
@@
 classic parametric g-formula, correct model specification may be
-achieved more readily.
+achieved (or approximated) more readily.
 

### 2023-08-28 illustrate-intervention-distribution.R

@@ -161,7 +161,7 @@ mytheme <- theme_bw() +
 				axis.ticks = element_line(linewidth = 1 / .pt),
 				legend.key.size = unit(8, 'pt'),
 				legend.spacing.x = unit(2, 'pt'),
-				legend.spacing.y = unit(2, 'pt'),
+				legend.spacing.y = unit(2.5, 'pt'),
 				legend.title = element_text(size = 8, colour = 'black'),
 				legend.text  = element_text(size = 8, colour = 'black'),
 				axis.text    = element_text(size = 8, colour = 'black'),
@@ -251,7 +251,6 @@ for (i in 1:3) {
 				legend.margin = margin(t = 0, r = 0, b = 2.5, l = 0),
 				legend.box.margin = margin(t = 0, r = 2, b = 0, l = 2),
 				plot.margin = margin(t = 15, l = 12, 6, 6)
-				# legend.background = element_rect(color = 'black')
 			),
 		labels = paste0(letters[i], ")"), label_fontface = "plain", label_size = 10,
 		hjust = -0.25, vjust = 1.5

### 2023-08-31 reports/paper/paper.qmd
remove names

@@
 
-**Authors:** Kevin T. Chen\^a, b\^, Sally Picciotto^c^, Ellen A.
-Eisen^c^
+**Authors:** Kevin T. Chen^a,b^, Sally Picciotto^c^, Ellen A. Eisen^c^
 
@@
 
-**Running head suggestion:** Hypothetical interventions with guaranteed positivity
-
 **Conflicts of interests:** Authors declare no conflicts of interest.
@@
 **Sources of financial support:** This work was supported by Training
-Grant T42OH008429 and Research Project Grant R01OH011092, both from
-the National Institute for Occupational Safety and Health (NIOSH) /
-Centers for Disease Control and Prevention (CDC).
+Grant T42OH008429 and Research Project Grant R01OH011092, both from the
+National Institute for Occupational Safety and Health (NIOSH) / Centers
+for Disease Control and Prevention (CDC).
 
@@
 
-**Word count** **(Limit: 1500 to 4000 words):** 3842 (approx)
+**Word count** **(Limit: 4000 words):** 3842
 
@@
 
-(Limit: 250 words)
+(Limit: 200 words)
 
-**Background:** Non-Hodgkin lymphoma (NHL) incidence has increased
-substantially in the US and was recently linked to workplace exposure to
-soluble metalworking fluids (MWF) in a standard survival analysis of the
-United Auto Workers-General Motors (UAW-GM) cohort. Here, we estimate
-the effects of hypothetical interventions on soluble MWF exposure in
-relation to NHL risk in the same cohort of autoworkers. Estimation of
-causal effects requires positivity, which we guarantee by investigating
-causal contrasts that are supportable by the data.
-
-**Methods:** We defined hypothetical supportable interventions that
-reduce annual daily average exposures above a specific target limit to
-that limit when supported by data. When the target limit is not
-supported, the intervention reduces exposure to the nearest supported
-level of exposure. We estimated counterfactual risk of NHL between 1985
-and 2015 in the UAW-GM cohort of autoworkers at three Michigan plants (n
-= 33,134) under hypothetical supportable interventions on exposure to
-soluble MWF.
-
-**Results:** 339 NHL cases occurred over the 30-year follow-up period.
-Stronger target limits on soluble MWF exposure resulted in monotonic
-reductions in NHL risk. Setting the target exposure limit at 0.5
-mg/m^3^, the NIOSH recommended exposure limit, would have prevented 124
-(95% CI: 66, 202) cases.
-
-**Conclusion:** More stringent limits on exposure to soluble MWF provide
-stronger protections against NHL. We expect that uniformly enforcing the
-target exposure limits, regardless of data support, would have even
-stronger protective effects. Strengthening exposure limits for MWF may
-protect workers from NHL during the anticipated boom in domestic
-manufacturing.
+Non-Hodgkin lymphoma (NHL) incidence was recently linked to exposure to
+metalworking fluid (MWF) in a standard survival analysis of the United
+Auto Workers-General Motors cohort. To provide results more directly
+relevant to guiding exposure limits, we estimated the counterfactual
+risks of NHL under hypothetical supportable interventions on exposure to
+MWF in the same cohort (n = 33,134) for 1985-2015 using the
+hazard-extended iterative conditional expectation g-formula. We
+addressed potential bias due to the healthy worker survivor effect while
+investigating stochastic dynamic interventions that avoid extrapolation
+beyond observed conditional exposure distributions, thus guaranteeing
+positivity by design. These interventions reduced exposures above
+specified target limits to the nearest supported level of exposure but
+allowed exposures below the limit to vary naturally. 339 NHL cases
+occurred over the 30-year follow-up period. Stronger target limits on
+MWF exposure resulted in monotonic reductions in NHL risk. Setting the
+target exposure limit at 0.5 mg/m^3^, the NIOSH recommended exposure
+limit, would have prevented 124 (95% CI: 66, 202) cases. We expect that
+uniformly enforcing the target exposure limits, regardless of data
+support, would have yielded even stronger protective effects.
+Strengthening protections against exposure to MWF may protect workers
+from NHL during the anticipated boom in domestic manufacturing.
 

### 2023-08-31 g-formula.R

@@ -1,5 +1,4 @@
 # Parametric g-formula ####
-# Kevin Chen
 # November 3, 2020
 
 library(here)

### 2023-08-31 get-data.R

@@ -1,5 +1,4 @@
 # Get data for cancer incidence ####
-# Kevin Chen
 # November 3, 2020
 
 library(here)

### 2023-08-31 illustrate-intervention-distribution.R

@@ -1,5 +1,4 @@
 # Figures for illustrating intervention ####
-# Kevin Chen
 # May 25, 2023
 
 library(here)

### 2023-08-31 run_g-formula.R

@@ -1,5 +1,4 @@
 # Run parametric g-formula ####
-# Kevin Chen
 # November 3, 2020
 
 library(here)

### 2023-08-31 shape-data.R

@@ -1,5 +1,4 @@
 # Shaping data for parametric g-formula and the sdr lmtp ####
-# Kevin Chen
 # November 3, 2020
 
 library(here)

### 2023-08-31 reports/paper/paper.qmd
move files

@@
 ```
-
-**Type of manuscript:** Original Research Article
-
-**Manuscript title:** Hypothetical interventions on workplace exposure
-with guaranteed positivity
-
-**Authors:** Kevin T. Chen^a,b^, Sally Picciotto^c^, Ellen A. Eisen^c^
-
-^a^ University of California, Berkeley School of Public Health, Division
-of Epidemiology & Biostatistics
-
-^b^ University of California, Berkeley Department of Statistics
-
-^c^ University of California, Berkeley School of Public Health, Division
-of Environmental Health Sciences
-
-**Corresponding author:**\
-Kevin T. Chen\
-2121 Berkeley Way\
-Room 5302, Desk 5305-1\
-Berkeley, CA 94720-7360\
-kevchen\@berkeley.edu\
-(510) 816-3408
-
-**Conflicts of interests:** Authors declare no conflicts of interest.
-
-**Sources of financial support:** This work was supported by Training
-Grant T42OH008429 and Research Project Grant R01OH011092, both from the
-National Institute for Occupational Safety and Health (NIOSH) / Centers
-for Disease Control and Prevention (CDC).
-
-**Data and computing code:** Code for reproducing analyses and reports
-are available on [Github](https://github.com/kvntchn/gm-nhl-ice). Data
-are available upon reasonable request.
-
-**Keywords:** Positivity, overlap, causal inference, g-formula,
-metalworking fluid, occupational exposure, non-Hodgkin lymphoma, cancer,
-iterated conditional expectation, healthy-worker effect
-
-**Word count** **(Limit: 4000 words):** 3842
-
-\newpage
 

### 2025-04-14 reports/paper/paper.qmd
prepare for revisions

@@
 Non-Hodgkin Lymphoma (NHL) incidence in the United States doubled
-between 1973 and 1994 before plateauing at around 19 per 100,000 persons
-per year, making it the seventh most common cancer in the country
-[@seer_1994; @Ekstrom-Smedby_2006]. The strongest known risk factor of
-NHL is immunosuppression, both congenital and acquired
-[@Filipovich_1992; @Chiu_2015]. However, since immunodeficiency and
-infection with HIV are rare, they cannot fully explain the historic rise
-or present burden of NHL [@Shiels_2013]. The rise in NHL incidence
-coincided with a period of rapid and extensive chemicalization in
-industry, agriculture and warfare; environmental and occupational
-exposures may play an important explanatory role in the epidemiology of
-NHL [@Nelson_2005; @Romero_2021].
+between 1973 and 1994 before plateauing at around 19 per 100,000
+persons per year, making it the seventh most common cancer in the
+country [@seer_1994; @Ekstrom-Smedby_2006]. The strongest known risk
+factors of NHL are autoimmune disease and immunosuppression
+[@Filipovich_1992; @Chiu_2015]. The relationship between autoimmune
+diseases NHL is specific in that each disease is associated with a
+particular subtype of NHL [@Thandra_2021]. Immunosuppression and
+infection with HIV are strongly associated with Burkitt lymphoma
+[@Thandra_2021]. These risk factors cannot fully explain the historic
+rise or present burden of NHL, however [@Shiels_2013]. Since the
+rise in NHL incidence coincided with a period of rapid and extensive
+chemicalization in industry, agriculture and warfare; environmental
+and occupational exposures may play an important explanatory role in
+the epidemiology of NHL [@Nelson_2005; @Romero_2021]. Existing
+epidemiologic studies suggest that occupational exposures may increase
+the risk of NHL without subtype specificity [@Thandra_2021].
 
@@
 
-Common approaches for addressing violations in positivity are
-model-based smoothing when using outcome regression methods, weight
-truncation when using propensity methods, or a combination of both.
-Another approach is to only consider causal contrasts that are supported
-by the observed data, *i.e.,* those involving hypothetical interventions
-with propensity score strictly greater than zero. Here, we defined
-hypothetical supportable interventions on exposure to soluble MWF in the
-United Auto Workers-General Motors (UAW-GM) occupational cohort and
-estimated their effects on NHL incidence between 1985 and 2015 relative
-to no exposure intervention while guaranteeing positivity.
+When positivity is not satisfied, causal inference methods that rely
+only on models for the counterfactual outcome, and not the treatment
+mechanism, may still yield valid causal estimates, if the models are
+correctly specified. We evaluated how hypothetical interventions on
+exposure to soluble MWF would affect the incidence of NHL between 1985
+and 2015 in the United Auto Workers-General Motors (UAW-GM)
+occupational cohort using the iterative conditional expectation (ICE)
+parametric g-formula, which relies on models for the outcome only. To
+further address potential violations in positivity, we defined and
+evaluated hypothetical interventions resulting in post-intervention
+exposure histories whose propensity score is strictly greater than 
+zero _i.e._, exposure histories that can be found in the observed
+data. We call these hypothetical interventions "supportable".
 
@@
 annual average daily exposure to soluble MWF by applying the
-hazard-extended iterative conditional expectation (ICE) parametric
-g-formula [@Wen_2020]. First, we estimated the expected number of NHL
+hazard-extended ICE parametric  we estimated the expected number of NHL
 cases that we would observe if there were no censoring and no limit on

### 2025-04-14 shape-data.R

@@ -55,7 +55,7 @@ dat[,`:=`(
 	off = shift(off, exposure.lag, 0),
 	cum_off = shift(cum_off, exposure.lag, 0)
 )]
-# dat <- dat[yin <= as.Date("1983-01-01") & year >= 1985 & year <= 1994 + exposure.lag]
+dat <- dat[yin >= as.Date("1985-01-01") - exposure.lag * 365.25]
 # Get data analytic ####
 get.coxph(
 	cohort_name = "dat",
@@ -69,13 +69,17 @@ dat <- copy(nhl.dat)
 cancer <- box_read('512727972584')
 setDT(cancer)
 
-nhl_morphology <- merge(dat[status == 1, .(studyno, yoi)],
-												unique(cancer[morph %in% c(
-													9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687:9691, 9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729, 9735, 9737:9738, 9811:9818, 9823, 9827, 9837,
-													9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687, 9688, 9689:9691, 9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729, 9735, 9737, 9738,
-													9811:9818, 9823, 9827, 9837
-												),.(studyno, yoi = ddiag, morph)]),
-												by = c("studyno", "yoi"))
+nhl_morphology <- merge(
+	dat[status == 1, .(studyno, yoi)],
+	unique(cancer[morph %in% c(
+		9590:9597, 9670:9671, 9673, 9675, 9678:9680, 9684, 9687:9691,
+		9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729,
+		9735, 9737:9738, 9811:9818, 9823, 9827, 9837, 9590:9597,
+		9670:9671, 9673, 9675, 9678:9680, 9684, 9687, 9688, 9689:9691,
+		9695, 9698:9702, 9705, 9708:9709, 9712, 9714:9719, 9724:9729,
+		9735, 9737, 9738, 9811:9818, 9823, 9827, 9837
+	),.(studyno, yoi = ddiag, morph)]),
+	by = c("studyno", "yoi"))
 
 dat <- merge(
 	dat, nhl_morphology[,.(studyno, morph = as.integer(morph))],
[…]

### 2025-04-15 reports/paper/paper.qmd
some revisions

@@
 ---
-# fontsize: 11pt
-# mainfont: arial
+# title: Hypothetical interventions on workplace exposure with guaranteed positivity
+fontsize: 11pt
+header-includes:
+- \allowdisplaybreaks
+- \usepackage{setspace}\setstretch{1.1}
+- \usepackage{etoolbox}
+  \newcommand{\zerodisplayskips}{
+    \setlength{\abovedisplayskip}{2pt}
+    \setlength{\belowdisplayskip}{2pt}
+    \setlength{\abovedisplayshortskip}{1pt}
+    \setlength{\belowdisplayshortskip}{1pt}}
+  \appto{\normalsize}{\zerodisplayskips}
+  \appto{\small}{\zerodisplayskips}
+  \appto{\footnotesize}{\zerodisplayskips}
+- \usepackage{pgf}\usepackage{pgfplots}\usepackage{tikz}
+- \usetikzlibrary{graphs, arrows, automata, shadings}
+- \setlength{\floatsep}{0pt}
+- \usepackage{enumitem}\setlist[enumerate]{leftmargin=*}
+- \usepackage{verbatim}
+- \makeatletter
+  \patchcmd{\@verbatim}{\verbatim@font}{\singlespacing\small\verbatim@font}{}{}
+- \RedeclareSectionCommand[runin=false, beforeskip=-1sp,
+  afterskip=-0.1\baselineskip]{section}
+- \RedeclareSectionCommand[runin=false, beforeskip=-1sp,
+  afterskip=-0.1\baselineskip]{subsection}
+- \newcommand\blfootnote[1]{
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}
+  \addtocounter{footnote}{-1}
+  \endgroup}
+- \setlength{\columnsep}{2em}
+- \setlength{\tabcolsep}{2pt}
+- \usepackage{dsfont}
+- \usepackage[section]{placeins}
+latex-output-dir: '..'
 format:
- # html: default
- docx:
-    number-sections: false
-    global-numbering: true
-    reference-doc: "../../../../HeadRs/rmd_templates/style-guide-arial-11.docx"
+  pdf:
+    documentclass: scrartcl
+    # classoption: twocolumn
+    geometry: 
+      - margin=1.1in
+      - footskip=0.35in
+    keep-tex: true
+  # docx:
+  #   number-sections: false
+  #   global-numbering: true
+  #   reference-doc: "../../../../HeadRs/rmd_templates/style-guide-serif.docx"
+tbl-cap-location: top
 bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
-csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
 notes-after-punctuation: true
+csl: "`r path.expand('~/HeadRs/csl/de-gruyter.csl')`"
+fig-cap-location: top
+crossref:
+  lof-title: "List of figures"
+  lot-title: "List of tables"
+  custom:
+    - kind: float
+      key: suppfig
+      latex-env: suppfig
+      reference-prefix: Figure S
+      space-before-numbering: false
+      latex-list-of-description: Supplemental Figure
+      caption-location: top
+    - kind: float
+      key: supptbl
+      latex-env: supptbl
+      reference-prefix: Table S
+      space-before-numbering: false
+      latex-list-of-description: Supplemental Table
+      caption-location: top
 execute:
@@
   chunk_output_type: inline
-editor: 
-  markdown: 
-    wrap: 72
 ---
@@
 knitr::opts_chunk$set(echo=F, results = 'asis')
-library(bibtex)
-biblio <- bibtex::read.bib('~/Box Sync/papers/EnvEpi.bib')
+source("~/headrs/00-my-theme.R")
+library(xtable)
 library(flextable)
+set_flextable_defaults(font.size = 10, font.family = "Helvetica Neue")
 library(data.table)
@@
 
-# Abstract
+# Hypothetical interventions on workplace exposure with guaranteed positivity
 
-(Limit: 200 words)
+## Abstract
 
@@
 
-\newpage
+{{< pagebreak >}}
 
-# Introduction
+## Introduction
 
@@
 
-# Methods
+## Methods
 
@@
 
-::: {#fig-rules layout-ncol="2"}
-![](resources/images/intervention-density-witnin-combos-a.png){#fig-1a
-width="3.5in"}
-![](resources/images/intervention-density-witnin-combos-b.png){#fig-1b
-width="3.5in"}
-![](resources/images/intervention-density-witnin-combos-c.png){#fig-1c
-width="3.5in"}
-
-Observed and post intervention distribution of nonzero exposure for
-three distinct confounder and exposure histories before and after
-applying the supportable intervention rule.
-:::
-
-## Study population
+### Study population
 
@@
 
-## Outcome and potential confounders
+### Outcome and potential confounders
 
@@
 
-## Exposure
+### Exposure
 
@@
 
-## Hazard-extended ICE parametric g-formula
+### Hazard-extended ICE parametric g-formula
 
@@
 supportable interventions to that under no intervention on exposure by
-computing the number of cases averted and the cumulative incidence
+computing the risk difference per 10,000 and the cumulative incidence
 ratios. Confidence intervals were computed using the basic nonparametric
@@
 
-```{r}
-source(here::here("../gm-wrangling/wrangling/table1.R"))
-clean.tab1 <- function(tab1) {
-  # hspace.which <- grepl("\\\\hspace\\{.*\\}", rownames(tab1))
-	rownames(tab1) <- gsub(
-		"\\\\hspace\\{.*\\}|\\\\hline |\\$.*\\$| among deceased",
-		"",
-		rownames(tab1))
-
-  tab1[!grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2]  <-  paste0(
-    "(",
-    tab1[!grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2],
-    ")"
-  )
-
-  tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2] <- paste0(
-    "(", tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2], ", ",
-    tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 3],
-    ")"
-  )
-
-  return(tab1[,1:2])
-}
-full.tab1 <- readRDS(here::here("resources", "tab1.rds"))
-nhl.tab1 <- readRDS(here::here("resources", "nhl.tab1.rds"))
-
-tab1.clean <- clean.tab1(full.tab1)
-nhl.tab1.clean <- clean.tab1(nhl.tab1)
-
-tab1 <- cbind(hspace.logical = grepl("\\\\hspace\\{.*\\}", rownames(full.tab1)),
-              variable = rownames(tab1.clean), tab1.clean, NA, nhl.tab1.clean)
-
-tab1 <- tab1[!grepl("Years of follow-up", rownames(tab1)),]
-tab1$variable[1] <- "N (person-years)"
-```
-
-# Results
+## Results
 
@@
 
-```{r}
-# tab1 <- tab1[tab1.which,]
-tab1.sub <- tab1[c(1:13, 15, 14, 16:27, 29, 28, 30),]
-tab1.sub <- tab1.sub[-c(17, 21, 26),]
-tab1.sub_hspace <- tab1.sub$hspace.logical
-tab1.sub <- tab1.sub[,-grep('hspace.logical', names(tab1.sub))]
-```
-
-```{r}
-tab1.sub |> 
-  data.frame() |> flextable() |>
-  delete_part(part = "header") |>
-  add_header_row(values = c("", "Study population", "", "NHL cases"),
-                 colwidths = c(1, 2, 1, 2)) |>
-  hline_top(part = "header") |>
-  hline_top() |> hline_bottom() |>
-  hline(which((grepl("[0-9]\\)", tab1.sub$spread))[-1])[1]) |> width(4, 0.1) |>
-  width(1, 2.2) |> width(c(3, 6), 1.1) |> width(c(2, 5), 0.65) |>
-  flextable::compose(
-    i = grep("Cumulative exposure", rownames(tab1.sub)), j = 1,
-    value = as_paragraph("Cumulative exposure to MWF (mg/m",
-                         as_sup("3"), "-years)")) |>
-  flextable::align(j = 2:6, align = "center", part = "all") |>
-  footnote(i = grep("Plant$", rownames(tab1.sub)), j = 1, value = as_paragraph(
-    " Plant of longest employment duration among those who worked at multiple plants"),
-    ref_symbols = "a", inline = T) |>
-  footnote(i = grep("Ever exposed|time off", rownames(tab1.sub)), j = 1, value = as_paragraph(
-    " Lagged 20 years"),
-    ref_symbols = "b", inline = T) |>
-  # footnote(i = grep("work", rownames(tab1.sub)), j = 1, value = as_paragraph(
-  #   " Among those who left work by December 31, 1994"),
-  #   ref_symbols = "c", inline = T) |>
-  # footnote(i = grep("death", rownames(tab1.sub)), j = 1, value = as_paragraph(
-  #   " Among deceased"),
-  #   ref_symbols = "d", inline = T) |>
-  footnote(i = grep("Cumulative exposure", rownames(tab1.sub)), j = 1, value = as_paragraph(
-    " Among ever-exposed individuals, lagged 20 years."),
-    ref_symbols = "d", inline = T) |>
-  add_footer_row(values = "NHL: non-Hodgkin lymphoma.", colwidths = 6) |>
-  padding(padding = 1.5, part = "all") |>
-  padding(
-    i = which(tab1.sub_hspace),
-    j = 1,
-    padding.left = 20
-  ) |>
-  merge_at(i = grep("Cumulative exposure", rownames(tab1.sub))) |>
-  hline_bottom(part = "footer") |> font(fontname = 'arial') |>
-	set_caption(
-		caption = paste0(
-			"Summary of population characteristics. Statistics shown above ",
-			"the horizontal line are count (%). Those shown below are median ",
-			"(quartile 1, quartile 3).")
-	)
-```
-
-\
-
-![Figure 2. Median annual average daily exposure to soluble, straight,
-and synthetic metalworking fluids among exposed workers over
-time.](../../resources/images/exposure.png){width="6.5in"}
-
-```{r}
-load(here::here("resources", paste0("estimates.rdata")))
-estimates.bs <- readRDS(here::here("resources", paste0("estimates.bs.rds")))
-```
-
-```{r}
-# Risk ratios
-do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
-  x/estimates.bs[,2]
-})) %>% melt(measure.vars = names(.)) -> rr.bs
-
-# Risk differences
-do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
-  x - estimates.bs[,2]
-})) %>% melt(measure.vars = names(.)) -> rd.bs
-
-estimates.bs[,-1] %>% melt(measure.vars = names(.)) -> risk.bs
-
-# Collect point estimates
-point_estimates <- data.table(
-  variable = c(
-    "200", "100", "50", "25", "05", "Any"),
-  estimate =  c(sapply(estimates[2:6], mean),
-                mean(estimates[[1]]))
-)
-```
-
-```{r}
-# Calculate risk ratios for each bootstrap sample
-rr <- merge(
-  rr.bs,
-  point_estimates[,.(
-    variable = paste0(variable, ".Any"),
-    estimate = estimate/estimate[variable == "Any"]
-  )],
-  all.x = F,
-  by = "variable")
-
-# Get lower and upper 2.5th %tiles
-rr <- rr[,.(
-  rr = estimate[1],
-  rr_lower = 2 * estimate[1] - quantile(value, 1 - 0.025),
-  rr_upper = 2 * estimate[1] - quantile(value, 0.025)
-  ),
-variable]
-```
-
-```{r}
-# Calculate risk differences for each bootstrap sample
-rd <- merge(
-  rd.bs,
-  point_estimates[,.(
-    variable = paste0(variable, ".Any"),
-    estimate = estimate - estimate[variable == "Any"]
-  )],
-  all.x = F,
-  by = "variable")
-
-# Get lower and upper 2.5th %tiles
-N <- 33134
-rd <- rd[,.(
-  rd = - estimate[1],
-  rd_lower = - (2 * estimate[1] - quantile(value, 0.025)) * N,
-  rd_upper = - (2 * estimate[1] - quantile(value, 1 - 0.025)) * N
-  # wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
-  # wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
-),
-variable]
-```
-
-```{r}
-# Combine differences and ratios
-contrasts.tab <- merge(rr, rd, by = 'variable')
-```
-
-```{r}
-# Collect risks
-risks <- merge(
-  risk.bs,
-  point_estimates,
-  all.x = F,
-  by = "variable")
-
-# Get lower and upper 2.5th %tiles
-risks <- risks[,.(estimate = estimate[1],
-      lower = 2 * mean(value) - quantile(value, 1 - 0.025),
-      upper = 2 * mean(value) - quantile(value, 0.025)
-      # wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
-      # wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
-      ),
-   .(variable.risks = variable)]
-```
-
-```{r}
-intervention.labels <- data.table(
-  variable = c(
-    "200", "100", "50", "25", "05", "Any"
-  ),
-  label = c(
-    "2.0", "1.0", "0.5", "0.25", "0.05", "None"
-  )
-)
-
-# Add intervention labels
-contrasts.tab <- merge(
-  contrasts.tab, intervention.labels[,.(variable = paste0(variable, ".Any"), label)],
-  all = T,
-  by = "variable"
-)
-
-```
-
-```{r}
-clean_percent_py <- function(variable, digits = 1, scale = 100) {
-  sprintf(paste0("%.", digits, "f"), round(
-    intervened_py[match(
-       sapply(variable, gsub, pattern = ".Any", replacement = ""),
-       variable.dat
-  ), percent_py_intervened] * scale,
-  digits))
-}
-
-clean_risk <- function(variable, digits = 2, scale = 1000) {
-  sprintf(paste0("%.", digits, "f"), round(risks[match(
-       sapply(variable, gsub, pattern = ".Any", replacement = ""),
-       variable.risks
-  ), estimate] * scale, digits))
-}
-
-clean_risk.ci <- function(variable, digits = 2, scale = 1000) {
-       x <- risks[match(
-       sapply(variable, gsub, pattern = ".Any", replacement = ""),
-       variable.risks
-       ),.(lower, upper)]
-       ifelse(!is.na(x$lower), paste0(
-         "(",
-         sprintf(paste0("%.", digits, "f"), round(x$lower * scale, digits)),
-         ", ", 
-         sprintf(paste0("%.", digits, "f"), round(x$upper * scale, digits)),
-         ")"), NA)
-}
-
-clean_rr.ci <- function(estimate, lower, upper, digits = 2) {
-  ifelse(!is.na(lower), paste0(
-    "(",
-    sprintf(paste0("%.", digits, "f"), round(lower, digits)),
-    ", ",
-    sprintf(paste0("%.", digits, "f"), round(upper, digits)),
-    ")"), NA)
-}
-
-mwf.flextable <- function(x, n_col = 7) {
-  flextable::compose(x, j = c(3, n_col), value = as_paragraph(rep("(95% CI)", 2)),
-    part = "header"
-  ) |>
-  border_remove() |>
-  hline_top(part = "header") |>
-  hline_top() |> hline_bottom() |>
-  flextable::align(j = 2:n_col, align = "center", part = "all") |>
-  padding(padding = 1.5, part = "all")
-}
-```
-
 The observed number of NHL cases over the 30-year follow-up period was
 339. Table 2 presents estimates of the counterfactual number of cases,
-number of cases averted, and cumulative incidence ratios contrasting
+risk difference per 10,000, and cumulative incidence ratios contrasting
 supportable interventions on exposure to soluble MWF based on different
@@
 
-```{r, eval=F}
-tikzDevice::tikz(here::here("reports/private/SER (2023)/resources/rd.tex"),
-                 width = 3.75, height = 2.25,
-								 documentDeclaration = "\\documentclass{beamer}",
-                 bareBones = T)
-contrasts.tab[,.(
-     label,
-     # `Person-years intervened (%)` = clean_percent_py(variable),
-     `Cases averted`    = rd * N,
-     rd_lower,
-     rd_upper,
-     result = paste0(
-     	round(rd * N),
-     	" (", round(rd_lower), ", ", round(rd_upper), ")")
-   )][c(6, 3, 2, 5, 4, 1),] -> gg.tab 
-gg.tab[label != "None"] |> ggplot(
-    aes(x = factor(
-    	label,
-    	levels = c("0.05", "0.25", "0.5", "1.0", "2.0",  "None"),
-    	labels = c("0.05", "0.25", "0.50", "1.00", "2.00",  "None")),
-        y = `Cases averted`, ymin = rd_lower, ymax = rd_upper)
-  ) +
-	geom_label(aes(y = 270, label = result), size = 8/.pt, 
-						 label.padding = unit(5, "pt")) +
-  geom_errorbar(linewidth = 4 / .pt, width = 0.15, color = '#003c61') +
-  geom_point(size = 4 / .pt, color = '#003c61') + 
-  geom_hline(yintercept = 0, lty = 2, , alpha = 0.7) +
-  labs(
-    y = "Cases averted",
-    x = "Target limit (mg/m$^3$)") +
-  mytheme +
-  coord_flip(ylim = c(-10, 320)) +
-  theme(panel.grid = element_blank(),
-  			axis.text = element_text(size = 9, colour = 'black'),
-  			panel.border = element_rect(colour = "black", size = 0.75),
-  			axis.title.y = element_text(size = 9, margin = margin(r = 6)),
-  			axis.title.x = element_text(size = 9, margin = margin(t = 6)),
-  			plot.margin = margin(l = 6, r = 6)
-  )
-dev.off()
-```
-
-```{r}
-contrasts.tab[,.(
-     label,
-     # `Person-years intervened (%)` = clean_percent_py(variable),
-     `Cases`  = clean_risk(variable, 0, N),
-     `(95% CI)`      = clean_risk.ci(variable, 0, N),
-     `Cases averted`    = round(rd * N),
-     `(95% CI1)`        = paste0(
-       "(",
-       round(rd_lower), ", ",
-       round(rd_upper), ")"),
-     CIR              = sprintf("%.2f", round(rr, 2)),
-     `(95% CI2)`   = clean_rr.ci(rr, rr_lower, rr_upper)
-   )][c(6, 3, 2, 5, 4, 1),] -> sol.tab
-sol.tab[label == "None", 4:7] <- NA
-
-# save(sol.tab, mwf.flextable, file = here::here('resources', 'sol.tab.rdata'))
-
-sol.tab |> flextable() |>
-  flextable::compose(
-    j = 1,
-    value = as_paragraph("Target exposure limit (mg/m", as_sup("3"), ")"),
-    part = "header"
-  ) |>
-  set_header_labels(
-    `(95% CI1)` = "(95% CI)",
-    `(95% CI2)` = "(95% CI)"
-  ) |> mwf.flextable() |>
-  width(width = c(1.1, 0.5, 0.9, 0.55, 0.9, 0.5, 0.9)) |>
-  add_footer_row(values = paste(
-    "CIR: cumulative incidence ratio. MWF: metalworking fluid",
-    sep = "\n"), colwidths = 7) |>
-  hline_bottom(part = "footer") |>
-	set_caption(caption = paste0(
-		"Estimates of the counterfactual number of cases, ",
-		"number of cases averted ",
-		"and cumulative incidence ratios ",
-		"contrasting supportable ",
-		"interventions on annual average daily exposure to soluble MWF ",
-		"to no intervention on exposure."
-	))
-
-```
-
-# Discussion
+## Discussion
 
@@
 
-# Conclusions
+## Conclusions
 
@@
 
-# Citations
+## References
 
@@
 :::
+
+{{< pagebreak >}}
+
+## Tables and figures
+
+:::{#fig-rules layout-ncol=2}
+![](resources/intervention-density-witnin-combos-a.pdf){#fig-1a}
+
+![](resources/intervention-density-witnin-combos-b.pdf){#fig-1b}
+
+![](resources/intervention-density-witnin-combos-c.pdf){#fig-1c}
+
+Observed and post intervention distribution of nonzero exposure for
+three distinct confounder and exposure histories before and after
+applying the supportable intervention rule.
+:::
+
+```{r}
+source(here::here("../gm-wrangling/wrangling/table1.R"))
+clean.tab1 <- function(tab1) {
+  # hspace.which <- grepl("\\\\hspace\\{.*\\}", rownames(tab1))
+	rownames(tab1) <- gsub(
+		"\\\\hspace\\{.*\\}|\\\\hline |\\$.*\\$| among deceased",
+		"",
+		rownames(tab1))
+
+  tab1[!grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2]  <-  paste0(
+    "(",
+    tab1[!grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2],
+    ")"
+  )
+
+  tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2] <- paste0(
+    "(", tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 2], ", ",
+    tab1[grepl("median", tab1[,4]) & !is.na(tab1[,1]), 3],
+    ")"
+  )
+
+  return(tab1[,1:2])
+}
+full.tab1 <- readRDS(here::here("resources", "tab1.rds"))
+nhl.tab1 <- readRDS(here::here("resources", "nhl.tab1.rds"))
+
+tab1.clean <- clean.tab1(full.tab1)
+nhl.tab1.clean <- clean.tab1(nhl.tab1)
+
+tab1 <- cbind(hspace.logical = grepl("\\\\hspace\\{.*\\}", rownames(full.tab1)),
+              variable = rownames(tab1.clean), tab1.clean, NA, nhl.tab1.clean)
+
+tab1 <- tab1[!grepl("Years of follow-up", rownames(tab1)),]
+tab1$variable[1] <- "N (person-years)"
+```
+
+```{r}
+# tab1 <- tab1[tab1.which,]
+tab1.sub <- tab1[c(1:13, 15, 14, 16:27, 29, 28, 30),]
+tab1.sub <- tab1.sub[-c(17, 21, 26),]
+tab1.sub_hspace <- tab1.sub$hspace.logical
+tab1.sub <- tab1.sub[,-grep('hspace.logical', names(tab1.sub))]
+```
+
+:::{#tbl-1}
+```{r}
+if (!knitr::is_latex_output()) {
+tab1.sub |> 
+  data.frame() |> flextable() |>
+  delete_part(part = "header") |>
+  add_header_row(values = c("", "Study population", "", "NHL cases"),
+                 colwidths = c(1, 2, 1, 2)) |>
+  hline_top(part = "header") |>
+  hline_top() |> hline_bottom() |>
+  hline(which((grepl("[0-9]\\)", tab1.sub$spread))[-1])[1]) |> width(4, 0.1) |>
+  width(1, 2.2) |> width(c(3, 6), 1.1) |> width(c(2, 5), 0.65) |>
+  flextable::compose(
+    i = grep("Cumulative exposure", rownames(tab1.sub)), j = 1,
+    value = as_paragraph("Cumulative exposure to MWF (mg/m",
+                         as_sup("3"), "-years)")) |>
+  flextable::align(j = 2:6, align = "center", part = "all") |>
+  footnote(i = grep("Plant$", rownames(tab1.sub)), j = 1, value = as_paragraph(
+    " Plant of longest employment duration among those who worked at multiple plants"),
+    ref_symbols = "a", inline = T) |>
+  footnote(i = grep("Ever exposed|time off", rownames(tab1.sub)), j = 1, value = as_paragraph(
+    " Lagged 20 years"),
+    ref_symbols = "b", inline = T) |>
+  # footnote(i = grep("work", rownames(tab1.sub)), j = 1, value = as_paragraph(
+  #   " Among those who left work by December 31, 1994"),
+  #   ref_symbols = "c", inline = T) |>
+  # footnote(i = grep("death", rownames(tab1.sub)), j = 1, value = as_paragraph(
+  #   " Among deceased"),
+  #   ref_symbols = "d", inline = T) |>
+  footnote(i = grep("Cumulative exposure", rownames(tab1.sub)), j = 1, value = as_paragraph(
+    " Among ever-exposed individuals, lagged 20 years."),
+    ref_symbols = "d", inline = T) |>
+  add_footer_row(values = "NHL: non-Hodgkin lymphoma.", colwidths = 6) |>
+  padding(padding = 1.5, part = "all") |>
+  padding(
+    i = which(tab1.sub_hspace),
+    j = 1,
+    padding.left = 20
+  ) |>
+  merge_at(i = grep("Cumulative exposure", rownames(tab1.sub))) |>
+  hline_bottom(part = "footer")
+} else {
+	rownames(tab1.sub) <- NULL
+	tab1.sub <- tab1.sub[,-4]
+	tab1.sub[tab1.sub_hspace, "variable"] <- paste0(
+		"\\hspace{2em}", tab1.sub[tab1.sub_hspace, "variable"])
+	tab1.sub$spread <- sanitize(tab1.sub$spread)
+	tab1.sub$spread.1 <- sanitize(tab1.sub$spread.1)
+	names(tab1.sub) <- c(
+		"%",
+		"Count", "(\\%)",
+		"Count", "(\\%)")
+	print(xtable(tab1.sub,
+							 align = "clrlrl"),
+				add.to.row = list(
+					pos = list(-1, 1, 16),
+					command = c(
+						paste0(
+							"\\toprule & \\multicolumn{2}{c}{Study population}", 
+							" & \\multicolumn{2}{c}{NHL Cases} \\\\ \n",
+							"\\cmidrule(lr){2-3}\\cmidrule(lr){4-5}\n"),
+						"\\midrule & Count & (\\%)     & Count & (\\%) \\\\\n\\midrule\n",
+						"\\midrule & Median & (Q1, Q3) & Median & (Q1, Q3) \\\\\n\\midrule\n"
+					)
+				),
+				hline.after = nrow(tab1.sub)
+	)
+}
+
+```
+
+Summary of population characteristics. Statistics shown above
+the horizontal line are count (%). Those shown below are median
+(quartile 1, quartile 3).
+
+:::
+
+\
+
+:::{#fig-exposure}
+![](../../resources/images/exposure.png){width="6.5in"}
+
+Median annual average daily exposure to soluble, straight,
+and synthetic metalworking fluids among exposed workers over
+time.
+:::
+
+```{r}
+load(here::here("resources", paste0("estimates.rdata")))
+estimates.bs <- readRDS(here::here("resources", paste0("estimates.bs.rds")))
+```
+
+```{r}
+# Risk ratios
+do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
+  x/estimates.bs[,2]
+})) %>% melt(measure.vars = names(.)) -> rr.bs
+
+# Risk differences
+do.call(cbind, lapply(estimates.bs[,-(1:2)], function(x) {
+  x - estimates.bs[,2]
+})) %>% melt(measure.vars = names(.)) -> rd.bs
+
+estimates.bs[,-1] %>% melt(measure.vars = names(.)) -> risk.bs
+
+# Collect point estimates
+point_estimates <- data.table(
+  variable = c(
+    "200", "100", "50", "25", "05", "Any"),
+  estimate =  c(sapply(estimates[2:6], mean),
+                mean(estimates[[1]]))
+)
+```
+
+```{r}
+# Calculate risk ratios for each bootstrap sample
+rr <- merge(
+  rr.bs,
+  point_estimates[,.(
+    variable = paste0(variable, ".Any"),
+    estimate = estimate/estimate[variable == "Any"]
+  )],
+  all.x = F,
+  by = "variable")
+
+# Get lower and upper 2.5th %tiles
+rr <- rr[,.(
+  rr = estimate[1],
+  rr_lower = 2 * estimate[1] - quantile(value, 1 - 0.025),
+  rr_upper = 2 * estimate[1] - quantile(value, 0.025)
+  ),
+variable]
+```
+
+```{r}
+# Calculate risk differences for each bootstrap sample
+rd <- merge(
+  rd.bs,
+  point_estimates[,.(
+    variable = paste0(variable, ".Any"),
+    estimate = estimate - estimate[variable == "Any"]
+  )],
+  all.x = F,
+  by = "variable")
+
+# Get lower and upper 2.5th %tiles
+N <- 33134
+rd <- rd[,.(
+  rd = - estimate[1],
+  rd_lower = - (2 * estimate[1] - quantile(value, 0.025)) * N,
+  rd_upper = - (2 * estimate[1] - quantile(value, 1 - 0.025)) * N
+  # wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
+  # wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
+),
+variable]
+```
+
+```{r}
+# Combine differences and ratios
+contrasts.tab <- merge(rr, rd, by = 'variable')
+```
+
+```{r}
+# Collect risks
+risks <- merge(
+  risk.bs,
+  point_estimates,
+  all.x = F,
+  by = "variable")
+
+# Get lower and upper 2.5th %tiles
+risks <- risks[,.(estimate = estimate[1],
+      lower = 2 * mean(value) - quantile(value, 1 - 0.025),
+      upper = 2 * mean(value) - quantile(value, 0.025)
+      # wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
+      # wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
+      ),
+   .(variable.risks = variable)]
+```
+
+```{r}
+intervention.labels <- data.table(
+  variable = c(
+    "200", "100", "50", "25", "05", "Any"
+  ),
+  label = c(
+    "2.0", "1.0", "0.5", "0.25", "0.05", "None"
+  )
+)
+
+# Add intervention labels
+contrasts.tab <- merge(
+  contrasts.tab, intervention.labels[,.(variable = paste0(variable, ".Any"), label)],
+  all = T,
+  by = "variable"
+)
+
+```
+
+```{r}
+clean_percent_py <- function(variable, digits = 1, scale = 100) {
+  sprintf(paste0("%.", digits, "f"), round(
+    intervened_py[match(
+       sapply(variable, gsub, pattern = ".Any", replacement = ""),
+       variable.dat
+  ), percent_py_intervened] * scale,
+  digits))
+}
+
+clean_risk <- function(variable, digits = 2, scale = 1000) {
+  sprintf(paste0("%.", digits, "f"), round(risks[match(
+       sapply(variable, gsub, pattern = ".Any", replacement = ""),
+       variable.risks
+  ), estimate] * scale, digits))
+}
+
+clean_risk.ci <- function(variable, digits = 2, scale = 1000) {
+       x <- risks[match(
+       sapply(variable, gsub, pattern = ".Any", replacement = ""),
+       variable.risks
+       ),.(lower, upper)]
+       ifelse(!is.na(x$lower), paste0(
+         "(",
+         sprintf(paste0("%.", digits, "f"), round(x$lower * scale, digits)),
+         ", ", 
+         sprintf(paste0("%.", digits, "f"), round(x$upper * scale, digits)),
+         ")"), NA)
+}
+
+clean_rr.ci <- function(estimate, lower, upper, digits = 2) {
+  ifelse(!is.na(lower), paste0(
+    "(",
+    sprintf(paste0("%.", digits, "f"), round(lower, digits)),
+    ", ",
+    sprintf(paste0("%.", digits, "f"), round(upper, digits)),
+    ")"), NA)
+}
+
+mwf.flextable <- function(x, n_col = 7) {
+  flextable::compose(x, j = c(3, n_col), value = as_paragraph(rep("(95% CI)", 2)),
+    part = "header"
+  ) |>
+  border_remove() |>
+  hline_top(part = "header") |>
+  hline_top() |> hline_bottom() |>
+  flextable::align(j = 2:n_col, align = "center", part = "all") |>
+  padding(padding = 1.5, part = "all")
+}
+```
+
+```{r}
+contrasts.tab[,.(
+     label,
+     # `Person-years intervened (%)` = clean_percent_py(variable),
+     `Cases`  = clean_risk(variable, 0, N),
+     `(95% CI)`      = clean_risk.ci(variable, 0, N),
+     `RD`    = round(rd * 10000),
+     `(95% CI1)`        = paste0(
+       "(",
+       round(rd_lower), ", ",
+       round(rd_upper), ")"),
+     CIR              = sprintf("%.2f", round(rr, 2)),
+     `(95% CI2)`   = clean_rr.ci(rr, rr_lower, rr_upper)
+   )][c(6, 3, 2, 5, 4, 1),] -> sol.tab
+sol.tab[label == "None", 4:7] <- NA
+
+# save(sol.tab, mwf.flextable, file = here::here('resources', 'sol.tab.rdata'))
+```
+
+::: {#tbl-rd}
+```{r}
+if (!knitr::is_latex_output()) {
+sol.tab |> flextable() |>
+  flextable::compose(
+    j = 1,
+    value = as_paragraph("Target exposure limit (mg/m", as_sup("3"), ")"),
+    part = "header"
+  ) |>
+  set_header_labels(
+    `(95% CI1)` = "(95% CI)",
+    `(95% CI2)` = "(95% CI)"
+  ) |> mwf.flextable() |>
+  width(width = c(1.1, 0.5, 0.9, 0.55, 0.9, 0.5, 0.9)) |>
+  add_footer_row(values = paste(
+    "CIR: cumulative incidence ratio. MWF: metalworking fluid",
+    sep = "\n"), colwidths = 7) |>
+  hline_bottom(part = "footer")
+} else {
+	names(sol.tab) <- gsub("CI.*)", "CI)", names(sol.tab))
+	names(sol.tab) <- sanitize(names(sol.tab))
+	names(sol.tab)[1] <- "Target exposure limit (mg/m\\textsuperscript{3})"
+	xtable(sol.tab, align = c("clrlrlrl"))
+}
+```
+
+Estimates of the counterfactual number of cases, number of cases 
+averted, and cumulative incidence ratios (CIR) contrasting supportable 
+interventions on annual average daily exposure to soluble MWF
+to no intervention on exposure.
+:::

### 2025-04-15 reports/paper/paper.tex
some revisions

% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  11pt,
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage[margin=1.1in,footskip=0.35in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\KOMAoption{captions}{tableheading,figureheading}
\allowdisplaybreaks
\usepackage{setspace}\setstretch{1.1}
\usepackage{etoolbox} \newcommand{\zerodisplayskips}{ \setlength{\abovedisplayskip}{2pt} \setlength{\belowdisplayskip}{2pt} \setlength{\abovedisplayshortskip}{1pt} \setlength{\belowdisplayshortskip}{1pt}} \appto{\normalsize}{\zerodisplayskips} \appto{\small}{\zerodisplayskips} \appto{\footnotesize}{\zerodisplayskips}
\usepackage{pgf}\usepackage{pgfplots}\usepackage{tikz}
\usetikzlibrary{graphs, arrows, automata, shadings}
\setlength{\floatsep}{0pt}
\usepackage{enumitem}\setlist[enumerate]{leftmargin=*}
\usepackage{verbatim}
\makeatletter \patchcmd{\@verbatim}{\verbatim@font}{\singlespacing\small\verbatim@font}{}{}
\RedeclareSectionCommand[runin=false, beforeskip=-1sp, afterskip=-0.1\baselineskip]{section}
\RedeclareSectionCommand[runin=false, beforeskip=-1sp, afterskip=-0.1\baselineskip]{subsection}
\newcommand\blfootnote[1]{ \begingroup \renewcommand\thefootnote{}\footnote{#1} \addtocounter{footnote}{-1} \endgroup}
\setlength{\columnsep}{2em}
\setlength{\tabcolsep}{2pt}
\usepackage{dsfont}
\usepackage[section]{placeins}
\makeatletter
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{plain}
\@ifundefined{c@chapter}{\newfloat{suppfig}{h}{losuppfig}}{\newfloat{suppfig}{h}{losuppfig}[chapter]}
\floatname{suppfig}{Figure S}
\floatstyle{plaintop}
\restylefloat{suppfig}
\newcommand*\quartosuppfigref[1]{Figure \hyperref[#1]{S\ref{#1}}}
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\DeclareCaptionLabelFormat{quartosuppfigreflabelformat}{#1#2}
\captionsetup[suppfig]{labelformat=quartosuppfigreflabelformat}
\newcommand*\listofsuppfigs{\listof{suppfig}{List of Supplemental Figures}}
\makeatother
\makeatletter
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{plain}
\@ifundefined{c@chapter}{\newfloat{supptbl}{h}{losupptbl}}{\newfloat{supptbl}{h}{losupptbl}[chapter]}
\floatname{supptbl}{Table S}
\floatstyle{plaintop}
\restylefloat{supptbl}
\newcommand*\quartosupptblref[1]{Table \hyperref[#1]{S\ref{#1}}}
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\DeclareCaptionLabelFormat{quartosupptblreflabelformat}{#1#2}
\captionsetup[supptbl]{labelformat=quartosupptblreflabelformat}
\newcommand*\listofsupptbls{\listof{supptbl}{List of Supplemental Tables}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of figures}
\else
  \newcommand\listfigurename{List of figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of tables}
\else
  \newcommand\listtablename{List of tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}
\begin{document}

\section{Hypothetical interventions on workplace exposure with
guaranteed
positivity}\label{hypothetical-interventions-on-workplace-exposure-with-guaranteed-positivity}

\subsection{Abstract}\label{abstract}

Non-Hodgkin lymphoma (NHL) incidence was recently linked to exposure to
metalworking fluid (MWF) in a standard survival analysis of the United
Auto Workers-General Motors cohort. To provide results more directly
relevant to guiding exposure limits, we estimated the counterfactual
risks of NHL under hypothetical supportable interventions on exposure to
MWF in the same cohort (n = 33,134) for 1985-2015 using the
hazard-extended iterative conditional expectation g-formula. We
addressed potential bias due to the healthy worker survivor effect while
investigating stochastic dynamic interventions that avoid extrapolation
beyond observed conditional exposure distributions, thus guaranteeing
positivity by design. These interventions reduced exposures above
specified target limits to the nearest supported level of exposure but
allowed exposures below the limit to vary naturally. 339 NHL cases
occurred over the 30-year follow-up period. Stronger target limits on
MWF exposure resulted in monotonic reductions in NHL risk. Setting the
target exposure limit at 0.5 mg/m\textsuperscript{3}, the NIOSH
recommended exposure limit, would have prevented 124 (95\% CI: 66, 202)
cases. We expect that uniformly enforcing the target exposure limits,
regardless of data support, would have yielded even stronger protective
effects. Strengthening protections against exposure to MWF may protect
workers from NHL during the anticipated boom in domestic manufacturing.

\newpage{}

\subsection{Introduction}\label{introduction}

Non-Hodgkin Lymphoma (NHL) incidence in the United States doubled
between 1973 and 1994 before plateauing at around 19 per 100,000 persons
per year, making it the seventh most common cancer in the country
{[}1,2{]}. The strongest known risk factors of NHL are autoimmune
disease and immunosuppression {[}3,4{]}. The relationship between
autoimmune diseases NHL is specific in that each disease is associated
with a particular subtype of NHL {[}5{]}. Immunosuppression and
infection with HIV are strongly associated with Burkitt lymphoma
{[}5{]}. These risk factors cannot fully explain the historic rise or
present burden of NHL, however {[}6{]}. Since the rise in NHL incidence
coincided with a period of rapid and extensive chemicalization in
industry, agriculture and warfare; environmental and occupational
exposures may play an important explanatory role in the epidemiology of
NHL {[}7,8{]}. Existing epidemiologic studies suggest that occupational
exposures may increase the risk of NHL without subtype specificity
{[}5{]}.

Pesticide exposure among workers in agricultural settings was a common
target of NHL research in recent decades. A meta-analysis of 44 articles
published between 1980 and 2014 found statistically significant
associations between NHL and exposure to several classes of pesticides
including carbamate, organophosporus, triazine, and organochlorine
{[}9{]}. Occupational exposures associated with NHL are not limited to
the agricultural sector, however. Occupational groups associated with
NHL risk also include metal processors, health workers, salespeople,
machinists, and electricians {[}2,10,11{]}. Workers in these
occupational groups often come into contact with industrial chemicals
such as gasoline, solvents, coolants, and lubricants such as
metalworking fluids (MWF).

Metalworking fluids are complex mixtures of oil, water, and chemical
additives that cool and lubricate metal machining operations. There are
three general types of MWF: straight, soluble, and synthetic. During
shaping, grinding, and cutting operations, MWFs are misted, poured, or
blasted at high pressure onto work surfaces to remove debris, cool
metal, improve efficiency, and prevent deterioration of tools. Although
MWFs are essential to manufacturing processes, they also present a
potential health hazard to exposed workers through inhalation or
ingestion of MWF particulate mass. In response to health concerns
related to the carcinogenicity of polycyclic aromatic hydrocarbons
(PAHs) in mineral oil as well as the rising global cost of oil products,
water-based soluble MWF, which usually contain about 40-70\% oil by
weight, were developed to replace oil-based straight MWF {[}12--14{]}.
Today, soluble MWF is the most common type of MWF in metal machining
operations {[}15{]}.

One challenge in estimating the causal effects of occupational exposures
on worker health is the Healthy Worker Survivor Effect (HWSE), the
process by which healthier individuals remain at work where they
accumulate more exposure while those more susceptible to the deleterious
health effects of exposure leave work {[}16{]}. The parametric g-formula
is an early causal inference method in statistics developed to estimate
causal effects in longitudinal observational studies where the HWSE or
other forms of time-varying confounding/selection bias affected by past
exposure may be operating {[}17--19{]}. A central requirement necessary
for causal inference from observational data is positivity (overlap),
\emph{i.e.,} adequate variation in the exposure of interest within
strata formed by confounder and exposure histories {[}20{]}.

When positivity is not satisfied, causal inference methods that rely
only on models for the counterfactual outcome, and not the treatment
mechanism, may still yield valid causal estimates, if the models are
correctly specified. We evaluated how hypothetical interventions on
exposure to soluble MWF would affect the incidence of NHL between 1985
and 2015 in the United Auto Workers-General Motors (UAW-GM) occupational
cohort using the iterative conditional expectation (ICE) parametric
g-formula, which relies on models for the outcome only. To further
address potential violations in positivity, we defined and evaluated
hypothetical interventions resulting in post-intervention exposure
histories whose propensity score is strictly greater than zero
\emph{i.e.}, exposure histories that can be found in the observed data.
We call these hypothetical interventions ``supportable''.

\subsection{Methods}\label{methods}

We estimated the cumulative incidence of NHL between 1985 and 2015 under
supportable interventions based on selected target exposure limits on
annual average daily exposure to soluble MWF by applying the
hazard-extended ICE parametric we estimated the expected number of NHL
cases that we would observe if there were no censoring and no limit on
exposure. Then, we contrasted this case count to that under supportable
interventions based on five hypothetical target exposure limits and no
censoring. The five target exposure limits were (1) 2.0, (2) 1.0, (3)
0.5, (4) 0.25, and (5) 0.05 mg/m\textsuperscript{3}. The National
Institute for Occupational Safety and Health (NIOSH) recommended
exposure limit (REL) for time-weighted average total particulate mass
(PM) composed of MWF is 0.5 mg/m\textsuperscript{3} {[}21{]}.

For each target exposure limit, period of follow-up, and stratum defined
by unique combinations of confounder and exposure histories, we found a
supportable exposure limit, which was the maximum observed value of
exposure at or below the target exposure limit, if such a value exists.
If all of the observed values were above the target limit, the
supportable limit was the minimum observed value. The supportable
intervention rule then reduces exposures above the supportable exposure
limit to that limit, but allows exposures at or below the limit to vary
according to their observed distribution. Applying the supportable
intervention rule to the observed distribution of exposure produces the
intervention distribution that defines the corresponding stochastic
dynamic intervention with guaranteed positivity. We estimated the effect
of supportable intervention rules based on the selected target exposure
limits, expressed as stochastic dynamic interventions, using the
hazard-extended ICE parametric g-formula {[}22{]}.

Figure 1 presents three example scenarios where the target exposure
limit is 0.25 mg/m\textsuperscript{3} in all cases, but the supportable
exposure limit differs depending on what the observed data supports. In
Figure 1a, the supportable exposure limit is equal to the target
exposure limit as some individuals with that particular set of potential
confounder and exposure histories were observed to have experienced
exposure at that level. In Figure 1b, the supportable exposure limit is
below the target exposure limit. In Figure 1c, the supportable exposure
limit, the minimum observed level of exposure in that stratum, is
greater than the target exposure limit.

\subsubsection{Study population}\label{study-population}

We used data from the UAW-GM cohort study, which included all hourly
workers at three automobile manufacturing plants in Michigan who had
worked at least three years by 1985. Past papers provide detailed
descriptions of the cohort {[}23,24{]}. The large size of the study
population and rich time-varying, quantitative MWF exposure data enable
the study of a relatively rare cancer and evaluation of realistic
interventions on MWF exposure in a longitudinal cohort setting. The
present study population (N = 33,134) was restricted to the autoworkers
who were at work in 1941 or not yet hired, missing no more than half of
their employment history, and still alive at the start of follow-up for
cancer incidence on January 1, 1985. Autoworkers in the study population
were followed until NHL diagnosis, death, December 31, 2014, or the
oldest observed age at death, whichever came earlier.

\subsubsection{Outcome and potential
confounders}\label{outcome-and-potential-confounders}

We identified incident cancers in the UAW-GM cohort between 1985 and
2014 by linkage to the Michigan Cancer Registry (MCR). Workers at Plants
1 and 2, located in the greater Detroit metropolitan area, were also
linked to the Detroit Regional Registry of the Surveillance,
Epidemiology, and End Results (SEER) Program. Cancer types were
distinguished using site and histology codes conforming to the
International classification of Diseases for Oncology,
3\textsuperscript{rd} edition (ICD-O-3). Non-Hodgkin lymphoma was
defined by cancers with any of the following ICD-O-3 histology codes:
9590-9597, 9670-9671, 9673, 9675, 9678-9680, 9684, 9687-9691, 9695,
9698-9702, 9705, 9708-9709, 9712, 9714-9719, 9724-9729, 9735, 9737-9738,
9811-9818, 9823, 9827, 9837. Details regarding cancer incidence
follow-up are described elsewhere {[}25{]}. Vital status was ascertained
from company records and by linkage to Social Security Administration,
National Death Index, and state mortality files.

Potential confounders including year of hire, sex, race, time off work,
employment status, and plant location were obtained from company
records. Race was missing for about 16\% of the cohort, most commonly
among workers hired before 1960 in Plant 2. In analyses, missing race
was considered a distinct category. All potential confounders were coded
as categorical variables. Cut-points for categorizing continuous
covariates were determined according to the quantiles among cases.

\subsubsection{Exposure}\label{exposure}

Quantitative measurement of time-varying MWF exposure is a
distinguishing strength of the UAW-GM cohort study relative to other
environmental or occupational health studies. Exposure assessment was
based on direct air sampling as well as company records. Company
industrial hygienists collected several hundred personal and area
samples for total particulate mass (mg/m\textsuperscript{3}) composed of
MWF over many decades. Research industrial hygienists collected
additional air sampling data when the cohort study was launched in the
mid 1980s {[}26,27{]}. These additional data combined with historical
data and company records were used to construct a job-exposure matrix of
quantitative 8-hour time-weighted average daily exposure estimates to
soluble, straight, and synthetic MWF for each combination of job,
department, and plant over time {[}28{]}. Workers' annual average daily
exposure to each MWF type was determined by combining this job-exposure
matrix with employment records, which recorded time-varying job type,
department, and plant for each employee from hire to termination or
1995, whichever came sooner. For employment records that were at least
half complete, gaps in the record were interpolated by carrying forward
the last known job type. The exposure assessment is described in detail
elsewhere {[}26,28,29{]}.

In previous analyses of NHL, exposure lags of 1 to 20 years were applied
to account for disease latency; we lagged cumulative MWF exposures by 20
years {[}30--32{]}. In analyses, MWF exposure history at start of
follow-up was summarized as the cumulative sum of average exposure
intensities. Exposure was coded as categorical variables with cut-points
at zero and the quintiles of nonzero exposure among cases. We estimated
the effects of hypothetical interventions on soluble MWF, the type of
MWF used most widely and in the greatest quantities while treating
co-exposure to straight and synthetic MWFs as potential confounders.

\subsubsection{Hazard-extended ICE parametric
g-formula}\label{hazard-extended-ice-parametric-g-formula}

We split the 30-year follow-up period into ten time periods based on the
deciles of the dates of diagnosis of NHL. The number of years per period
ranged from two to four. The hazard-extended ICE parametric g-formula
involves two stages. In the first, we estimate counterfactual discrete
hazards over the person-periods. In the second, we pool those estimates
to estimate the counterfactual risk over the entire follow-up period.
During pooling, we iteratively combine estimates of the counterfactual
hazard to obtain a pooled estimate over an increasing number of periods
starting from the last period. In each iteration, we perform model-based
standardization over exposure and covariate histories before combining
the counterfactual discrete hazard estimate with the estimated hazard
pooled over subsequent periods. This iterative process results in a
sequentially standardized estimate of the counterfactual cumulative
incidence of NHL when the intervention of interest is enforced over all
follow-up periods.

We investigated supportable interventions that guarantee positivity:
every value of exposure that could be assigned under our stochastic
dynamic intervention has propensity score strictly greater than zero. We
treated co-exposure to straight and synthetic MWF, employment status,
cumulative time off, age, duration of employment, sex (male/female),
race (Black/white/unknown), and plant (Plant 1/Plant 2/Plant 3) as
potential confounders. Exposure to MWF, employment status, time off, and
duration of employment were lagged 20 years. An overview of the general
steps of the estimation procedure are presented below. Note that we
refer to discrete hazards simply as hazards.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Fit a pooled logistic regression model for NHL on potential
  confounders and exposure over all at-risk person-periods.
\item
  Predict the hazard for each person-period for each possible level of
  exposure using the model from step 1.
\item
  Within strata formed by unique combinations of potential confounders
  and exposure, obtain the intervention distribution of exposure by
  applying the supportable intervention rule to the observed exposure
  distribution.
\item
  Within strata, estimate the counterfactual hazard for each
  person-period by taking a weighted sum of the predicted hazards from
  step 2.
\item
  Starting at the penultimate period of follow-up, estimate the pooled
  counterfactual hazard:

  \begin{enumerate}
  \def\labelenumii{\alph{enumii})}
  \tightlist
  \item
    Regress the counterfactual hazard pooled over all subsequent periods
    on all past potential confounders and exposures.
  \item
    Predict the pooled hazard for each person at risk at the start of
    the period and each possible level of exposure using the model from
    (a). Retrieve the predicted hazards from step 2. For each person and
    level of exposure, multiply the predicted pooled hazard by one minus
    the corresponding predicted hazard. Then, add the predicted hazard
    to the product.
  \item
    Within strata formed by potential confounder and exposure histories,
    obtain the intervention distribution of exposure by applying the
    intervention rule to the observed exposure distribution.
  \item
    Within strata, estimate the counterfactual hazard pooled over the
    present and subsequent periods for each person by taking a weighted
    sum of the predicted pooled hazards from (b).
  \item
    If the present period is not first period, set the reference period
    to the preceding period and return to (a).
  \end{enumerate}
\item
  Compute the counterfactual risk by averaging the pooled counterfactual
  hazards across all persons.
\end{enumerate}

To account for censoring, fit the models in step 1 and step 5a among
those who were not censored and obtain predicted hazards for all at-risk
person-periods, including those that were censored.

We estimated cumulative incidence under no intervention on soluble MWF
and under the supportable interventions based on the five selected
target exposure limits. We contrasted the cumulative incidence under the
supportable interventions to that under no intervention on exposure by
computing the risk difference per 10,000 and the cumulative incidence
ratios. Confidence intervals were computed using the basic nonparametric
bootstrap with 1000 Monte Carlo samples from the population at the start
of follow-up. All the necessary scripts used to reproduce the analyses
are available on \href{https://github.com/kvntchn/gm-nhl-ice}{GitHub}.

\subsection{Results}\label{results}

Table 1 presents summary statistics for the full study population and
among those diagnosed with NHL between 1985 and 2015. The cohort is
predominantly white (64\%) and male (86\%). Year of hire and age at hire
were approximately the same among those with NHL and the full study
population. Median lagged cumulative exposure to all three types of MWF
was higher among NHL cases. Soluble MWF were the most widely used type,
with approximately 88\% of workers ever exposed. Median cumulative
exposure among the exposed was approximately 6 times higher for soluble
than for straight MWF. Figure 2 shows median annual average daily
exposure to the three MWF types among exposed workers over calendar
time. Exposure to MWF generally followed a downward trend over time.

The observed number of NHL cases over the 30-year follow-up period was
339. Table 2 presents estimates of the counterfactual number of cases,
risk difference per 10,000, and cumulative incidence ratios contrasting
supportable interventions on exposure to soluble MWF based on different
target exposure limits and no censoring. Under an intervention
eliminating censoring, the estimated number of cases was 502 (95\% CI:
439, 555). Interventions based on stronger target exposure limits on
soluble MWF resulted in monotonically stronger reductions in the
estimated cumulative incidence of NHL. Setting the target exposure limit
at the NIOSH REL 0.5 mg/m\textsuperscript{3} would have averted 124
(95\% CI: 66, 202) NHL cases.

\subsection{Discussion}\label{discussion}

Although NIOSH concluded that there exists substantial evidence linking
MWF exposure to several different cancers including larynx, rectum,
pancreas, skin, scrotum, and bladder cancer, their REL of 0.5
mg/m\textsuperscript{3} for total particulate mass derived from any type
of MWF was based on nonmalignant respiratory health effects {[}21,33{]}.
Exposure limits stronger than the NIOSH REL may provide valuable health
protections not previously taken into account by policy makers. Using
the hazard-extended ICE parametric g-formula, we estimated the
counterfactual expected number of NHL cases from 1985 to 2015 in the
UAW-GM cohort if we enforced hypothetical supportable interventions on
soluble MWF based on five different target exposure limits and found a
monotonic exposure-dependent relationship where stronger target exposure
limits yielded lower NHL case count estimates.

The g-formula is a well-known approach in causal inference used for
estimating causal effects in the presence of time-varying confounding
affected by past exposure {[}17{]}. Standard representations of the
g-formula include (1) a non-iterated expectation over the joint density
of covariates, (2) the ICE over time, and (3) an inverse probability
weighted expectation. The classic parametric g-formula is a plug-in
estimator for the g-formula under its first, non-iterative,
representation. It involves the parametric modeling of the full joint
distribution of the confounders, exposure, and outcome for each time
point {[}18,34{]}. Counterfactual quantities under hypothetical
interventions of interest are computed from Monte Carlo samples from
distributions implied by the fitted parametric models. In longitudinal
settings, this approach often requires specifying and fitting large
number of models in order to satisfy the exchangeability assumptions
necessary for causal identification. Despite this limitation, analysts
often choose the parametric g-formula because of the intuitive way it
handles interventions on the natural value of exposure. However, these
causal estimands are not unique to the parametric g-formula. The
distribution of exposure produced by marginalizing intervention rules
over the observed distribution of exposure within strata formed by
potential confounder and exposure histories defines a corresponding
stochastic dynamic intervention, whose effects may be estimated using
various estimators {[}22,35--38{]}. Estimating causal effects of this
implied stochastic dynamic intervention is analogous to that of
interventions on the natural value of exposure {[}34{]}.

Estimators using the ICE representation of the g-formula are capable of
estimating effects of stochastic dynamic interventions. These ICE
g-formula estimators require modeling only the conditional distributions
of the outcome at each time. Hence, they require fewer parametric
assumptions than the classic parametric g-formula. Counterfactual
outcome estimates over the follow-up period are computed from
interval-specific conditional estimates by applying the tower rule of
expectation. Under the assumptions of conditional exchangeability at all
time points, positivity, counterfactual consistency, and correct model
specification, the hazard-extended parametric g-formula yields unbiased
estimates of counterfactual risk with greater statistical efficiency
than both propensity score-based estimators and the non-extended ICE
g-formula.

Correct model specification is a standard assumption in all parametric
and semi-parametric analyses. In causal analyses of longitudinal cohort
studies, ICE g-formula estimators are less common than the classic
parametric g-formula {[}39{]}. However, a major limitation of the
classic g-formula is the g-null paradox: the guaranteed misspecification
of parametric models resulting in the false rejection of the null
hypothesis when the null is true and when there is time-varying
confounding affected by past exposure {[}40,41{]}. As with all ICE
g-formula estimators, the estimator we applied is not subject to the
g-null paradox. Furthermore, since ICE g-formula estimators require
fewer parametric modeling requirements than the classic parametric
g-formula, correct model specification may be achieved (or approximated)
more readily.

The consistency assumption, also known as the
no-multiple-versions-of-treatment or stable unit treatment value
assumption, is that counterfactual outcomes under each possible exposure
value take on a unique value {[}42,43{]}. This assumption would be
violated if there were multiple versions of treatment causally
associated with different outcomes. This basic notion of consistency is
violated in our analysis because our exposure of interest is a complex
mixture of diverse components with substantial variation over time due
to changes in formulation as well as the natural physical, chemical, and
biological changes in the MWF over the course of its use and reuse
{[}44{]}. However, causal effect estimates under violations in the
consistency assumption are still valid and unbiased if there is adequate
adjustment for confounders of the exposure-version relationship
{[}43{]}. This may be thought of as conditional consistency within
strata, in which there is only one version of treatment. Our analysis
indexed time periods over calendar time and adjusted for age, year of
hire, and plant. In this way, we limited potential for bias due to
variation in MWF composition.

Positivity refers to the need for adequate variation in future exposure
among strata formed by observed covariate and intervention-compliant
exposure histories. Even under conditional exchangeability, where
exposures within these strata may be considered the result of
experimental assignment, expected counterfactual outcomes under
different exposures may not be estimable if there is excessive sparsity
in the observed distribution of exposures {[}45{]}. Rather than address
potential violations in positivity analytically, we investigated
stochastic dynamic interventions on soluble MWF exposure based on
intervention distributions which are nonzero only where the propensity
score is strictly positive. Hence, our supportable interventions
guarantee positivity. Interventions that guarantee positivity have been
suggested in the past and have also been called ``realistic''
interventions {[}20{]}.

Conditional exchangeability means that for all time points, there is no
confounding of the relationship between exposure/censoring and both
future exposure/censoring and NHL status given the observed past,
including past exposure and confounders {[}19,38{]}. A major threat to
conditional exchangeability in longitudinal occupational studies is the
HWSE. We limit potential bias due to the HWSE by conditioning on
cumulative exposure, employment status, and cumulative time off history
at each time point. Cumulative time off and employment status are
reasonable mediators of the causal paths linking past health to future
exposure and health, but adjustment for these variables may not be
sufficient for eliminating bias due to the HWSE. Declines in a worker's
health may lead to reductions in work-related exposure without affecting
employment status or time off work {[}46{]}. We expect the absence of
time-varying measures of worker health over the life course to result in
bias toward the null.

Much of the existing epidemiologic literature linking occupational and
environmental exposures to NHL report findings from case-control studies
where exposures are measured as binary indicators of exposure or as
membership in a particular occupational group {[}47--50{]}. Associations
between occupations and NHL risk vary considerably, but one study of
working men in Kansas and Nebraska found strong associations between NHL
risk and occupations involving metalworking and motor vehicles {[}51{]}.
Both of these occupations may entail exposure to soluble MWF, which
contain mineral oils and a number of chemical additives of concern for
human health and for NHL risk in particular. Organic compounds
containing phosphorous, chlorine, sulfur, nitrogen, and boron are
commonly added to soluble MWF to control microbial growth, improve
performance under high heat/pressure, and inhibit corrosion {[}52{]}.
Organophosphorus compounds include organophosphate pesticides, which
have been linked to cancer risk in epidemiologic and animal studies.
Some were classified as possibly carcinogenic by the IARC {[}53{]}.
Studies of occupational exposure to chlorinated solvents and pesticides
have also been linked to NHL risk {[}54--58{]}. In 2014, the IARC
classified trichloroethylene, tetrachloroethylene, and other chlorinated
agents as Group 1 carcinogens {[}59{]}. Chlorinated solvents are
commonly used as degreasers in industrial settings, but their use in the
plants under study here was rare {[}60{]}. The structural
characteristics shared by MWF additives and known/suspected carcinogens
suggest potential similarities in their behavior in biological systems.

This study investigated the effect of supportable interventions on MWF
exposure with guaranteed positivity. We compared the standardized risk
of NHL under post-intervention distributions of exposure based on a
range of target limits on annual average daily exposure to soluble MWF.
We selected a range of hypothetical target exposure limits near the
NIOSH REL of 0.5 mg/m\textsuperscript{3} {[}21{]}. If the target
exposure limits were enforced uniformly rather than in a
data-supportable way, we would expect even larger reductions in NHL risk
relative to no intervention on exposure. The supportable interventions
we evaluated here provide a more conservative estimate of the potential
health benefit of enforcing stronger limits on MWF exposure in the real
world because they explicitly restrict the causal contrasts to those
supported by the observed data.

\subsection{Conclusions}\label{conclusions}

Associations between several occupations and risk of NHL have been
reported previously, but none to our knowledge evaluated the potential
effect of realistic limits on occupational exposures {[}2,4,50,58{]}. We
found evidence that limiting exposure to soluble MWF would reduce NHL
incidence in an analysis that guarantees positivity and adjusts for
time-varying confounding affected by past exposure. \newpage

\subsection{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-seer_1994}
\CSLLeftMargin{1. }%
\CSLRightInline{Institute NC. SEER cancer statistics review 1973-1994:
Trends in SEER incidence and US mortality, by race and sex. National
Cancer Institute; 1994. }

\bibitem[\citeproctext]{ref-Ekstrom-Smedby_2006}
\CSLLeftMargin{2. }%
\CSLRightInline{Ekström-Smedby K. Epidemiology and etiology of
non-{Hodgkin} lymphoma--a review. Acta oncologica. 2006;45(3):258--71. }

\bibitem[\citeproctext]{ref-Filipovich_1992}
\CSLLeftMargin{3. }%
\CSLRightInline{Filipovich A, Mathur A, Kamat D, Shapiro R. Primary
immunodeficiencies: Genetic risk factors for lymphoma. Cancer research.
1992;52(19\_Supplement):5465s--5467s. }

\bibitem[\citeproctext]{ref-Chiu_2015}
\CSLLeftMargin{4. }%
\CSLRightInline{Chiu BCH, Hou N. Epidemiology and etiology of
non-{Hodgkin} lymphoma. Evens AM, Blum KA, editors. Vol. 165. Springer;
2015. }

\bibitem[\citeproctext]{ref-Thandra_2021}
\CSLLeftMargin{5. }%
\CSLRightInline{Thandra KC, Barsouk A, Saginala K, Padala SA, Barsouk A,
Rawla P. Epidemiology of non-{Hodgkin}'s lymphoma. Medical Sciences.
2021;9(1):5. }

\bibitem[\citeproctext]{ref-Shiels_2013}
\CSLLeftMargin{6. }%
\CSLRightInline{Shiels MS, Engels EA, Linet MS, Clarke CA, Li J, Hall
HI, et al. The epidemic of non-{Hodgkin} lymphoma in the {United
States}: Disentangling the effect of HIV, 1992--2009. Cancer
Epidemiology and Prevention Biomarkers. 2013;22(6):1069--78. }

\bibitem[\citeproctext]{ref-Nelson_2005}
\CSLLeftMargin{7. }%
\CSLRightInline{Nelson NJ. Studies examine whether persistent organic
agents may be responsible for rise in lymphoma rates. Journal of the
National Cancer Institute. 2005;97(20):1490--1. }

\bibitem[\citeproctext]{ref-Romero_2021}
\CSLLeftMargin{8. }%
\CSLRightInline{Romero AM. Economic poisoning: Industrial waste and the
chemicalization of american agriculture {[}Internet{]}. University of
California Press; 2021. Available from:
\url{https://doi.org/10.1525/9780520381575}}

\bibitem[\citeproctext]{ref-Schinasi_2014}
\CSLLeftMargin{9. }%
\CSLRightInline{Schinasi L, Leon ME. Non-{Hodgkin} lymphoma and
occupational exposure to agricultural pesticide chemical groups and
active ingredients: A systematic review and meta-analysis. International
Journal of Environmental Research and Public Health {[}Internet{]}.
2014;11(4):4449--527. Available from:
\url{https://www.mdpi.com/1660-4601/11/4/4449}}

\bibitem[\citeproctext]{ref-Fritschi_2005a}
\CSLLeftMargin{10. }%
\CSLRightInline{Fritschi L, Benke G, Hughes AM, Kricker A, Vajdic CM,
Grulich A, et al. Risk of non-{Hodgkin} lymphoma associated with
occupational exposure to solvents, metals, organic dusts and PCBs
(australia). Cancer Causes \& Control. 2005;16(5):599--607. }

\bibitem[\citeproctext]{ref-Mester_2006}
\CSLLeftMargin{11. }%
\CSLRightInline{Mester B, Nieters A, Deeg E, Elsner G, Becker N, Seidler
A. Occupation and malignant lymphoma: A population based case control
study in germany. Occupational and environmental medicine.
2006;63(1):17--26. }

\bibitem[\citeproctext]{ref-IARC_1973}
\CSLLeftMargin{12. }%
\CSLRightInline{IARC. IARC monographs on the evaluation of carcinogenic
risk of the chemical to man: Certain polycyclic aromatic hydrocarbons
and heterocyclic compounds. Vol. 3. World Health Organization
International Agency for Research on Cancer; 1973. }

\bibitem[\citeproctext]{ref-IARC_1987}
\CSLLeftMargin{13. }%
\CSLRightInline{IARC. IARC monographs on the evaluation of the
carcinogenic risk of chemicals to humans: Overall evaluations of
carcinogenicity: An updating of IARC monographs. Vols. 1-42, World
Health Organization. World Health Organization International Agency for
Research on Cancer; 1987. }

\bibitem[\citeproctext]{ref-Childers_2006}
\CSLLeftMargin{14. }%
\CSLRightInline{Childers J. The chemistry of metalworking fluids. In:
Metalworking fluids. CRC Press; 2006. }

\bibitem[\citeproctext]{ref-Byers_2006}
\CSLLeftMargin{15. }%
\CSLRightInline{Byers JP. Metalworking fluids. CRC Press; 2006. }

\bibitem[\citeproctext]{ref-Arrighi_1994}
\CSLLeftMargin{16. }%
\CSLRightInline{Arrighi HM, Hertz-Picciotto I. The evolving concept of
the healthy worker survivor effect. Epidemiology {[}Internet{]}.
1994;5(2):189--96. Available from:
\url{http://www.jstor.org/stable/3702361}}

\bibitem[\citeproctext]{ref-Robins_1986}
\CSLLeftMargin{17. }%
\CSLRightInline{Robins J.
\href{https://doi.org/10.1016/0270-0255(86)90088-6}{A new approach to
causal inference in mortality studies with a sustained exposure
period---application to control of the healthy worker survivor effect}.
Mathematical Modelling. 1986;7(9):1393--512. }

\bibitem[\citeproctext]{ref-Taubman_2009}
\CSLLeftMargin{18. }%
\CSLRightInline{Taubman SL, Robins JM, Mittleman MA, Hernán MA.
Intervening on risk factors for coronary heart disease: An application
of the parametric g-formula. International journal of epidemiology.
2009;38(6):1599--611. }

\bibitem[\citeproctext]{ref-Richardson_2013}
\CSLLeftMargin{19. }%
\CSLRightInline{Richardson TS, Robins JM. Single world intervention
graphs (SWIGs): A unification of the counterfactual and graphical
approaches to causality. Center for the Statistics and the Social
Sciences, University of Washington Series Working Paper.
2013;128(30):2013. }

\bibitem[\citeproctext]{ref-Petersen_2012}
\CSLLeftMargin{20. }%
\CSLRightInline{Petersen ML, Porter P, Gruber S, Wang Y, van der Laan
MJ. Diagnosing and responding to violations in the positivity
assumption. Statistical Methods in Medical Research {[}Internet{]}.
2012;21(1):31--54. Available from:
\url{https://doi.org/10.1177/0962280210386207}}

\bibitem[\citeproctext]{ref-niosh_1998}
\CSLLeftMargin{21. }%
\CSLRightInline{Rosenstock L, editor. What you need to know about
occupational exposure to metalworking fluids. Department of Health;
Human Services (NIOSH); 1998. }

\bibitem[\citeproctext]{ref-Wen_2020}
\CSLLeftMargin{22. }%
\CSLRightInline{Wen L, Young JG, Robins JM, Hernán MA. Parametric
g-formula implementations for causal survival analyses. Biometrics.
2020; }

\bibitem[\citeproctext]{ref-Eisen_1992}
\CSLLeftMargin{23. }%
\CSLRightInline{Eisen EA, Tolbert PE, Monson RR, Smith TJ. Mortality
studies of machining fluid exposure in the automobile industry {I}: A
standardized mortality ratio analysis. American journal of industrial
medicine. 1992;22(6):809--24. }

\bibitem[\citeproctext]{ref-Eisen_2001}
\CSLLeftMargin{24. }%
\CSLRightInline{Eisen EA, Bardin J, Gore R, Woskie SR, Hallock MF,
Monson RR. Exposure-response models based on extended follow-up of a
cohort mortality study in the automobile industry. Scandinavian journal
of work, environment \& health. 2001;27(4):240--9. }

\bibitem[\citeproctext]{ref-Colbeth_2022}
\CSLLeftMargin{25. }%
\CSLRightInline{Colbeth HL, Chen KT, Picciotto S, Costello S, Eisen EA.
Exposure to metalworking fluids and cancer incidence in the united auto
workers--general motors cohort. American Journal of Epidemiology. 2022;
}

\bibitem[\citeproctext]{ref-Woskie_1994}
\CSLLeftMargin{26. }%
\CSLRightInline{Woskie SR, Smith TJ, Hallock MF, Hammond SK, Rosenthal
F, Eisen EA, et al. Size-selective pulmonary dose indices for
metal-working fluid aerosols in machining and grinding operations in the
automobile manufacturing industry. American Industrial Hygiene
Association Journal. 1994;55(1):20--9. }

\bibitem[\citeproctext]{ref-Woskie_1994a}
\CSLLeftMargin{27. }%
\CSLRightInline{Woskie SR, Smith TJ, Hammond SK, Hallock MH. Factors
affecting worker exposures to metal-working fluids during automotive
component manufacturing. Applied Occupational and Environmental Hygiene.
1994;9(9):612--21. }

\bibitem[\citeproctext]{ref-Hallock_1994}
\CSLLeftMargin{28. }%
\CSLRightInline{Hallock MF, Smith TJ, Woskie SR, Hammond SK. Estimation
of historical exposures to machining fluids in the automotive industry.
American Journal of Industrial Medicine {[}Internet{]}.
1994;26(5):621--34. Available from:
\url{http://dx.doi.org/10.1002/ajim.4700260505}}

\bibitem[\citeproctext]{ref-Woskie_2003}
\CSLLeftMargin{29. }%
\CSLRightInline{Woskie SR, Virji MA, Hallock M, Smith TJ, Hammond SK.
Summary of the findings from the exposure assessments for metalworking
fluid mortality and morbidity studies. Applied occupational and
environmental hygiene. 2003;18(11):855--64. }

\bibitem[\citeproctext]{ref-Smith_2007}
\CSLLeftMargin{30. }%
\CSLRightInline{Smith MT, Jones RM, Smith AH. Benzene exposure and risk
of non-{Hodgkin} lymphoma. Cancer epidemiology, biomarkers \&
prevention. 2007;16(3):385--91. }

\bibitem[\citeproctext]{ref-Karipidis_2007}
\CSLLeftMargin{31. }%
\CSLRightInline{Karipidis KK, Benke G, Sim MR, Kauppinen T, Kricker A,
Hughes AM, et al. Occupational exposure to ionizing and non-ionizing
radiation and risk of non-{Hodgkin} lymphoma. International archives of
occupational and environmental health. 2007;80(8):663--70. }

\bibitem[\citeproctext]{ref-Zhang_2019}
\CSLLeftMargin{32. }%
\CSLRightInline{Zhang L, Rana I, Shaffer RM, Taioli E, Sheppard L.
Exposure to glyphosate-based herbicides and risk for non-{Hodgkin}
lymphoma: A meta-analysis and supporting evidence. Mutation
Research/Reviews in Mutation Research. 2019;781:186--206. }

\bibitem[\citeproctext]{ref-Mirer_2003}
\CSLLeftMargin{33. }%
\CSLRightInline{Mirer F. Updated epidemiology of workers exposed to
metalworking fluids provides sufficient evidence for carcinogenicity.
Applied occupational and environmental hygiene. 2003;18(11):902--12. }

\bibitem[\citeproctext]{ref-Young_2014}
\CSLLeftMargin{34. }%
\CSLRightInline{Young JG, Hernán MA, Robins JM. Identification,
estimation and approximation of risk under interventions that depend on
the natural value of treatment using observational data. Epidemiologic
methods. 2014;3(1):1--19. }

\bibitem[\citeproctext]{ref-Bang_2005}
\CSLLeftMargin{35. }%
\CSLRightInline{Bang H, Robins JM. Doubly robust estimation in missing
data and causal inference models. Biometrics. 2005;61(4):962--73. }

\bibitem[\citeproctext]{ref-van-der-Laan_2011}
\CSLLeftMargin{36. }%
\CSLRightInline{van der Laan MJ, Rose S. Targeted learning: Causal
inference for observational and experimental data. Springer Science \&
Business Media; 2011. }

\bibitem[\citeproctext]{ref-Wen_2023}
\CSLLeftMargin{37. }%
\CSLRightInline{Wen L, Marcus JL, Young JG. Intervention treatment
distributions that depend on the observed treatment process and model
double robustness in causal survival analysis. Statistical Methods in
Medical Research. 2023;09622802221146311. }

\bibitem[\citeproctext]{ref-Diaz_2021}
\CSLLeftMargin{38. }%
\CSLRightInline{Dı́az I, Williams N, Hoffman KL, Schenck EJ.
Nonparametric causal effects based on longitudinal modified treatment
policies. Journal of the American Statistical Association. 2021;1--16. }

\bibitem[\citeproctext]{ref-Keil_2014}
\CSLLeftMargin{39. }%
\CSLRightInline{Keil AP, Edwards JK, Richardson DB, Naimi AI, Cole SR.
The parametric g-formula for time-to-event data: Intuition and a worked
example. Epidemiology {[}Internet{]}. 2014;25(6). Available from:
\url{https://journals.lww.com/epidem/Fulltext/2014/11000/The_Parametric_g_Formula_for_Time_to_event_Data_.16.aspx}}

\bibitem[\citeproctext]{ref-Naimi_2015}
\CSLLeftMargin{40. }%
\CSLRightInline{Naimi AI, Tchetgen Tchetgen EJ. Invited commentary:
Estimating population impact in the presence of competing events.
American journal of epidemiology. 2015;181(8):571--4. }

\bibitem[\citeproctext]{ref-McGrath_2022}
\CSLLeftMargin{41. }%
\CSLRightInline{McGrath S, Young JG, Hernán MA. Revisiting the g-null
paradox. Epidemiology. 2022;33(1):114--20. }

\bibitem[\citeproctext]{ref-Cole_2009}
\CSLLeftMargin{42. }%
\CSLRightInline{Cole SR, Frangakis CE. The consistency statement in
causal inference: A definition or an assumption? Epidemiology.
2009;20(1):3--5. }

\bibitem[\citeproctext]{ref-VanderWeele_2013}
\CSLLeftMargin{43. }%
\CSLRightInline{VanderWeele TJ, Shpitser I. On the definition of a
confounder. Annals of statistics. 2013;41(1):196. }

\bibitem[\citeproctext]{ref-Howell_2006}
\CSLLeftMargin{44. }%
\CSLRightInline{Howell JK, Lucke WE, White EM. Metalworking fluids. In:
Byers JP, editor. CRC Press; 2006. }

\bibitem[\citeproctext]{ref-Maldonado_2002}
\CSLLeftMargin{45. }%
\CSLRightInline{Maldonado G, Greenland S. Estimating causal effects.
International journal of epidemiology. 2002;31(2):422--9. }

\bibitem[\citeproctext]{ref-Garcia_2017}
\CSLLeftMargin{46. }%
\CSLRightInline{Garcia E, Picciotto S, Costello S, Bradshaw PT, Eisen
EA. Assessment of the healthy worker survivor effect in cancer studies
of the {United Autoworkers-General Motors Cohort}. Occupational and
environmental medicine. 2017;74(4):294--300. }

\bibitem[\citeproctext]{ref-Cano_2001}
\CSLLeftMargin{47. }%
\CSLRightInline{Cano MI, Pollán M. Non-{Hodgkin}'s lymphomas and
occupation in sweden. International archives of occupational and
environmental health. 2001;74(6):443--9. }

\bibitem[\citeproctext]{ref-Costantini_2001}
\CSLLeftMargin{48. }%
\CSLRightInline{Costantini AS, Miligi L, Kriebel D, Ramazzotti V,
Rodella S, Scarpi E, et al. A multicenter case-control study in italy on
hematolymphopoietic neoplasms and occupation. Epidemiology. 2001;78--87.
}

\bibitem[\citeproctext]{ref-Karunanayake_2008}
\CSLLeftMargin{49. }%
\CSLRightInline{Karunanayake CP, McDuffie HH, Dosman JA, Spinelli JJ,
Pahwa P. Occupational exposures and non-{Hodgkin}'s lymphoma: Canadian
case-control study. Environmental Health. 2008;7(1):1--9. }

\bibitem[\citeproctext]{ref-t-Mannetje_2016}
\CSLLeftMargin{50. }%
\CSLRightInline{`t Mannetje A, De Roos AJ, Boffetta P, Vermeulen R,
Benke G, Fritschi L, et al. Occupation and risk of non-{Hodgkin}
lymphoma and its subtypes: A pooled analysis from the InterLymph
consortium. Environmental health perspectives. 2016;124(4):396--405. }

\bibitem[\citeproctext]{ref-Zheng_2002}
\CSLLeftMargin{51. }%
\CSLRightInline{Zheng T, Blair A, Zhang Y, Weisenburger DD, Zahm SH.
Occupation and risk of non-{Hodgkin}'s lymphoma and chronic lymphocytic
leukemia. Journal of occupational and environmental medicine.
2002;44(5):469--74. }

\bibitem[\citeproctext]{ref-Evans_2020}
\CSLLeftMargin{52. }%
\CSLRightInline{Evans R, Hooijman J, van der Veer J. High-speed
machining. In: Gupta K, Davim P, editors. Academic Press; 2020. }

\bibitem[\citeproctext]{ref-IARC_2017}
\CSLLeftMargin{53. }%
\CSLRightInline{IARC. IARC monographs on the evaluation of carcinogenic
risk of the chemical to humans: Some organophosphate insecticides and
herbicides. Vol. 112. World Health Organization International Agency for
Research on Cancer; 2017. }

\bibitem[\citeproctext]{ref-Cocco_2008}
\CSLLeftMargin{54. }%
\CSLRightInline{Cocco P, Brennan P, Ibba A, Sanjosè Llongueras S de,
Maynadié M, Nieters A, et al. Plasma polychlorobiphenyl and
organochlorine pesticide level and risk of major lymphoma subtypes.
Occupational and Environmental Medicine. 2008;65(2):132--40. }

\bibitem[\citeproctext]{ref-Purdue_2011}
\CSLLeftMargin{55. }%
\CSLRightInline{Purdue MP, Bakke B, Stewart P, De Roos AJ, Schenk M,
Lynch CF, et al. A case-control study of occupational exposure to
trichloroethylene and non-{Hodgkin} lymphoma. Environmental health
perspectives. 2011;119(2):232--8. }

\bibitem[\citeproctext]{ref-Cocco_2013}
\CSLLeftMargin{56. }%
\CSLRightInline{Cocco P, Vermeulen R, Flore V, Nonne T, Campagna M,
Purdue M, et al. Occupational exposure to trichloroethylene and risk of
non-{Hodgkin} lymphoma and its major subtypes: A pooled IinterLlymph
analysis. Occupational and environmental medicine. 2013;70(11):795--802.
}

\bibitem[\citeproctext]{ref-Vlaanderen_2013}
\CSLLeftMargin{57. }%
\CSLRightInline{Vlaanderen J, Straif K, Pukkala E, Kauppinen T, Kyyrönen
P, Martinsen JI, et al. Occupational exposure to trichloroethylene and
perchloroethylene and the risk of lymphoma, liver, and kidney cancer in
four nordic countries. Occupational and environmental medicine.
2013;70(6):393--401. }

\bibitem[\citeproctext]{ref-Callahan_2018}
\CSLLeftMargin{58. }%
\CSLRightInline{Callahan CL, Stewart PA, Friesen MC, Locke S, De Roos
AJ, Cerhan JR, et al. Case-control investigation of occupational
exposure to chlorinated solvents and non-{Hodgkin}'s lymphoma.
Occupational and environmental medicine. 2018;75(6):415--20. }

\bibitem[\citeproctext]{ref-IARC_2014}
\CSLLeftMargin{59. }%
\CSLRightInline{IARC. IARC monographs on the evaluation of carcinogenic
risks to humans: Trichloroethylene, tetrachloroethylene, and some other
chlorinated agents. Vol. 106, World Health Organization. World Health
Organization International Agency for Research on Cancer; 2014. }

\bibitem[\citeproctext]{ref-Shrestha_2016}
\CSLLeftMargin{60. }%
\CSLRightInline{Shrestha D, Liu S, Hammond SK, LaValley MP, Weiner DE,
Eisen EA, et al. Risk of renal cell carcinoma following exposure to
metalworking fluids among autoworkers. Occupational and environmental
medicine. 2016;73(10):656--62. }

\end{CSLReferences}

\newpage{}

\subsection{Tables and figures}\label{tables-and-figures}

\begin{figure}

\caption{\label{fig-rules}Observed and post intervention distribution of
nonzero exposure for three distinct confounder and exposure histories
before and after applying the supportable intervention rule.}

\begin{minipage}{0.50\linewidth}

\subcaption{\label{fig-1a}}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{resources/intervention-density-witnin-combos-a.pdf}}

}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\subcaption{\label{fig-1b}}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{resources/intervention-density-witnin-combos-b.pdf}}

}

\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}

\subcaption{\label{fig-1c}}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{resources/intervention-density-witnin-combos-c.pdf}}

}

\end{minipage}%

\end{figure}%

\begin{table}

\caption{\label{tbl-1}Summary of population characteristics. Statistics
shown above the horizontal line are count (\%). Those shown below are
median (quartile 1, quartile 3).}

\centering{

\begin{tabular}{lrlrl}
  \toprule & \multicolumn{2}{c}{Study population} & \multicolumn{2}{c}{NHL Cases} \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}
% & Count & (\%) & Count & (\%) \\ 
 N (person-years) & 33,134 & (794,733) & 339 & (5,809) \\ 
   \midrule & Count & (\%)     & Count & (\%) \\
\midrule
Race &  &  &  &  \\ 
  \hspace{2em}White & 21,315 & (64\%) & 250 & (74\%) \\ 
  \hspace{2em}Black & 6,250 & (19\%) & 40 & (12\%) \\ 
  \hspace{2em}Unknown & 5,569 & (17\%) & 49 & (14\%) \\ 
  Sex &  &  &  &  \\ 
  \hspace{2em}Male & 28,640 & (86\%) & 297 & (88\%) \\ 
  \hspace{2em}Female & 4,494 & (14\%) & 42 & (12\%) \\ 
  Plant &  &  &  &  \\ 
  \hspace{2em}Plant 1 & 7,273 & (22\%) & 70 & (21\%) \\ 
  \hspace{2em}Plant 2 & 14,251 & (43\%) & 137 & (40\%) \\ 
  \hspace{2em}Plant 3 & 11,610 & (35\%) & 132 & (39\%) \\ 
  Ever exposed to MWFs &  &  &  &  \\ 
  \hspace{2em}Soluble & 29,010 & (88\%) & 299 & (88\%) \\ 
  \hspace{2em}Straight & 18,710 & (56\%) & 197 & (58\%) \\ 
  \hspace{2em}Synthetic & 11,824 & (36\%) & 111 & (33\%) \\ 
   \midrule & Median & (Q1, Q3) & Median & (Q1, Q3) \\
\midrule
Year of birth & 1941 & (1927, 1950) & 1935 & (1926, 1945) \\ 
  Year of hire & 1967 & (1953, 1976) & 1964 & (1953, 1971) \\ 
  Age at hire (years) & 23.6 & (20.0, 30.3) & 25.3 & (20.2, 32.9) \\ 
  Age at leaving work (years) & 45.2 & (31.8, 57.3) & 53.0 & (36.4, 60.4) \\ 
  Years at work & 15.2 & (7.0, 26.6) & 21.0 & (7.8, 29.9) \\ 
  Year of death & 2001 & (1994, 2009) & 2004 & (1998, 2010) \\ 
  Age at death (years) & 73.4 & (64.4, 81.3) & 73.0 & (66.3, 80.8) \\ 
  Cumulative exposurey) &  &  &  &  \\ 
  \hspace{2em}Soluble  & 4.33 & (1.71, 10.69) & 5.43 & (2.19, 14.33) \\ 
  \hspace{2em}Straight  & 0.67 & (0.21, 2.38) & 0.77 & (0.18, 3.52) \\ 
  \hspace{2em}Synthetic  & 0.44 & (0.15, 1.58) & 0.69 & (0.18, 1.91) \\ 
   \bottomrule
\end{tabular}

}

\end{table}%

\hfill\break

\begin{figure}

\caption{\label{fig-exposure}Median annual average daily exposure to
soluble, straight, and synthetic metalworking fluids among exposed
workers over time.}

\centering{

\includegraphics[width=6.5in,height=\textheight,keepaspectratio]{../../resources/images/exposure.png}

}

\end{figure}%

\begin{table}

\caption{\label{tbl-rd}Estimates of the counterfactual number of cases,
number of cases averted, and cumulative incidence ratios (CIR)
contrasting supportable interventions on annual average daily exposure
to soluble MWF to no intervention on exposure.}

\centering{

\begin{tabular}{lrlrlrl}
  \toprule
Target exposure limit (mg/m\textsuperscript{3}) & Cases & (95\% CI) & RD & (95\% CI) & CIR & (95\% CI) \\ 
  \midrule
None & 308 & (439, 555) &  &  &  &  \\ 
  2.0 & 280 & (317, 464) & 8.00 & (-103, 18) & 0.91 & (0.89, 1.13) \\ 
  1.0 & 277 & (306, 457) & 9.00 & (-110, 20) & 0.90 & (0.89, 1.13) \\ 
  0.5 & 268 & (296, 450) & 12.00 & (-102, 34) & 0.87 & (0.83, 1.09) \\ 
  0.25 & 260 & (286, 445) & 15.00 & (-99, 46) & 0.84 & (0.78, 1.06) \\ 
  0.05 & 238 & (262, 439) & 21.00 & (-79, 88) & 0.77 & (0.65, 0.97) \\ 
   \bottomrule
\end{tabular}

}

\end{table}%

\end{document}

### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-a.tex
some revisions

@@
-% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:49:59
+% Created by tikzDevice version 0.12.6 on 2025-04-14 23:48:19
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
+\path[clip] ( 39.16, 31.76) rectangle (246.94,165.67);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
+\path[fill=fillColor] ( 39.16, 31.76) rectangle (246.95,165.67);
 \definecolor{fillColor}{RGB}{211,211,211}
 
-\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,110.79);
+\path[fill=fillColor] ( 48.60, 37.85) rectangle ( 55.87, 37.85);
 
-\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[fill=fillColor] ( 55.87, 37.85) rectangle ( 63.13, 47.21);
 
-\path[fill=fillColor] ( 62.31, 37.60) rectangle ( 69.61, 37.60);
+\path[fill=fillColor] ( 63.13, 37.85) rectangle ( 70.40, 37.85);
 
-\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 62.00);
+\path[fill=fillColor] ( 70.40, 37.85) rectangle ( 77.66, 47.21);
 
-\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[fill=fillColor] ( 77.66, 37.85) rectangle ( 84.93, 47.21);
 
-\path[fill=fillColor] ( 84.20, 37.60) rectangle ( 91.50, 37.60);
+\path[fill=fillColor] ( 84.93, 37.85) rectangle ( 92.19, 37.85);
 
-\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 37.60);
+\path[fill=fillColor] ( 92.19, 37.85) rectangle ( 99.46, 47.21);
 
-\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);
+\path[fill=fillColor] ( 99.46, 37.85) rectangle (106.72,159.59);
 
-\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);
+\path[fill=fillColor] (106.72, 37.85) rectangle (113.99, 37.85);
 
-\path[fill=fillColor] (113.39, 37.60) rectangle (120.69,159.58);
+\path[fill=fillColor] (113.99, 37.85) rectangle (121.26, 37.85);
 
-\path[fill=fillColor] (120.69, 37.60) rectangle (127.99, 37.60);
+\path[fill=fillColor] (121.26, 37.85) rectangle (128.52, 37.85);
 
-\path[fill=fillColor] (127.99, 37.60) rectangle (135.29, 37.60);
+\path[fill=fillColor] (128.52, 37.85) rectangle (135.79, 37.85);
 
-\path[fill=fillColor] (135.29, 37.60) rectangle (142.58, 37.60);
+\path[fill=fillColor] (135.79, 37.85) rectangle (143.05, 37.85);
 
-\path[fill=fillColor] (142.58, 37.60) rectangle (149.88, 37.60);
+\path[fill=fillColor] (143.05, 37.85) rectangle (150.32, 37.85);
 
-\path[fill=fillColor] (149.88, 37.60) rectangle (157.18, 37.60);
+\path[fill=fillColor] (150.32, 37.85) rectangle (157.58, 37.85);
 
-\path[fill=fillColor] (157.18, 37.60) rectangle (164.48, 37.60);
+\path[fill=fillColor] (157.58, 37.85) rectangle (164.85, 37.85);
 
-\path[fill=fillColor] (164.48, 37.60) rectangle (171.78, 37.60);
+\path[fill=fillColor] (164.85, 37.85) rectangle (172.11, 37.85);
 
-\path[fill=fillColor] (171.78, 37.60) rectangle (179.07, 37.60);
+\path[fill=fillColor] (172.11, 37.85) rectangle (179.38, 37.85);
 
-\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[fill=fillColor] (179.38, 37.85) rectangle (186.64, 37.85);
 
-\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);
+\path[fill=fillColor] (186.64, 37.85) rectangle (193.91, 37.85);
 
-\path[fill=fillColor] (193.67, 37.60) rectangle (200.97, 37.60);
+\path[fill=fillColor] (193.91, 37.85) rectangle (201.17, 37.85);
 
-\path[fill=fillColor] (200.97, 37.60) rectangle (208.27, 37.60);
+\path[fill=fillColor] (201.17, 37.85) rectangle (208.44, 37.85);
 
-\path[fill=fillColor] (208.27, 37.60) rectangle (215.56, 37.60);
+\path[fill=fillColor] (208.44, 37.85) rectangle (215.70, 37.85);
 
-\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);
+\path[fill=fillColor] (215.70, 37.85) rectangle (222.97, 37.85);
 
-\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);
+\path[fill=fillColor] (222.97, 37.85) rectangle (230.23, 37.85);
 
-\path[fill=fillColor] (230.16, 37.60) rectangle (237.46, 37.60);
+\path[fill=fillColor] (230.23, 37.85) rectangle (237.50, 37.85);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01,110.79);
+\path[draw=drawColor,line width= 0.4pt] ( 48.60, 37.85) rectangle ( 55.87, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 55.87, 37.85) rectangle ( 63.13, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] ( 62.31, 37.60) rectangle ( 69.61, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 63.13, 37.85) rectangle ( 70.40, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 62.00);
+\path[draw=drawColor,line width= 0.4pt] ( 70.40, 37.85) rectangle ( 77.66, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 77.66, 37.85) rectangle ( 84.93, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] ( 84.20, 37.60) rectangle ( 91.50, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 84.93, 37.85) rectangle ( 92.19, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 92.19, 37.85) rectangle ( 99.46, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 99.46, 37.85) rectangle (106.72, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (106.72, 37.85) rectangle (113.99, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (113.99, 37.85) rectangle (121.26, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (121.26, 37.85) rectangle (128.52, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (128.52, 37.85) rectangle (135.79, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (135.79, 37.85) rectangle (143.05, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (143.05, 37.85) rectangle (150.32, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (150.32, 37.85) rectangle (157.58, 94.04);
 
-\path[draw=drawColor,line width= 0.4pt] (157.18, 37.60) rectangle (164.48, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (157.58, 37.85) rectangle (164.85, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (164.85, 37.85) rectangle (172.11, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (172.11, 37.85) rectangle (179.38, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (179.38, 37.85) rectangle (186.64, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (186.64, 37.85) rectangle (193.91, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] (193.67, 37.60) rectangle (200.97, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (193.91, 37.85) rectangle (201.17, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (201.17, 37.85) rectangle (208.44, 56.58);
 
-\path[draw=drawColor,line width= 0.4pt] (208.27, 37.60) rectangle (215.56, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (208.44, 37.85) rectangle (215.70, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (215.70, 37.85) rectangle (222.97, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (222.97, 37.85) rectangle (230.23, 47.21);
 
-\path[draw=drawColor,line width= 0.4pt] (230.16, 37.60) rectangle (237.46, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (230.23, 37.85) rectangle (237.50, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.50) -- (120.69,165.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (121.26, 31.76) -- (121.26,165.67);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.22, 31.50) rectangle (246.94,165.68);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.16, 31.76) rectangle (246.95,165.67);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21, 35.09) {0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 62.29) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21, 74.89) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 89.74) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21,114.69) {20};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,117.18) {15};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,144.62) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21,154.49) {30};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
-	( 38.22, 37.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41, 37.85) --
+	( 39.16, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 65.05) --
-	( 38.22, 65.05);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41, 77.65) --
+	( 39.16, 77.65);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 92.49) --
-	( 38.22, 92.49);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41,117.45) --
+	( 39.16,117.45);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,119.93) --
-	( 38.22,119.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,147.38) --
-	( 38.22,147.38);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41,157.25) --
+	( 39.16,157.25);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.75) --
-	( 47.71, 31.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 48.60, 29.01) --
+	( 48.60, 31.76);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.75) --
-	(106.10, 31.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (106.72, 29.01) --
+	(106.72, 31.76);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.75) --
-	(164.48, 31.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (164.85, 29.01) --
+	(164.85, 31.76);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.75) --
-	(222.86, 31.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (222.97, 29.01) --
+	(222.97, 31.76);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 47.71, 21.04) {0.0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 48.60, 21.30) {0.0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.10, 21.04) {0.2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.72, 21.30) {0.2};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.48, 21.04) {0.4};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.85, 21.30) {0.4};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (222.86, 21.04) {0.6};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (222.97, 21.30) {0.6};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.58,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (143.05,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.59) {Density};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.72) {Density};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,143.84) rectangle (244.95,163.87);
+\path[fill=fillColor] (170.95,144.14) rectangle (246.94,167.67);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,157.35) {Target exposure limit:};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (170.95,161.15) {Target exposure limit:};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,146.34) rectangle (176.95,154.34);
+\path[fill=fillColor] (170.95,146.64) rectangle (178.95,154.64);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.34) -- (172.95,154.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (174.95,146.64) -- (174.95,154.64);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.59) {0.25 mg/m$^3$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.45,147.89) {0.25 mg/m$^3$};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,113.81) rectangle (240.85,141.84);
+\path[fill=fillColor] (170.95,110.11) rectangle (246.35,141.64);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.32) {Distribution:};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (170.95,135.12) {Distribution:};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
+\path[fill=fillColor] (170.95,120.61) rectangle (178.95,128.61);
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,116.31) rectangle (176.95,124.31);
+\path[fill=fillColor] (170.95,112.61) rectangle (178.95,120.61);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt] (169.45,116.81) rectangle (176.45,123.81);
+\path[draw=drawColor,line width= 0.4pt] (171.45,113.11) rectangle (178.45,120.11);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,125.55) {Post-intervention};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.45,121.85) {Post-intervention};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.22,170.34) {a)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.45,113.85) {Observed};
 \end{scope}

### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-b.tex
New intervention
some revisions

@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:08
+% Created by tikzDevice version 0.12.6 on 2025-04-14 23:49:03
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
+\path[clip] ( 39.16, 31.76) rectangle (246.94,165.67);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
+\path[fill=fillColor] ( 39.16, 31.76) rectangle (246.95,165.67);
 \definecolor{fillColor}{RGB}{211,211,211}
 
-\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,159.58);
+\path[fill=fillColor] ( 48.60, 37.85) rectangle ( 55.87, 37.85);
 
-\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[fill=fillColor] ( 55.87, 37.85) rectangle ( 63.13, 37.85);
 
-\path[fill=fillColor] ( 62.31, 37.60) rectangle ( 69.61, 37.60);
+\path[fill=fillColor] ( 63.13, 37.85) rectangle ( 70.40, 37.85);
 
-\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 37.60);
+\path[fill=fillColor] ( 70.40, 37.85) rectangle ( 77.66, 37.85);
 
-\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[fill=fillColor] ( 77.66, 37.85) rectangle ( 84.93, 37.85);
 
-\path[fill=fillColor] ( 84.20, 37.60) rectangle ( 91.50, 37.60);
+\path[fill=fillColor] ( 84.93, 37.85) rectangle ( 92.19, 37.85);
 
-\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 37.60);
+\path[fill=fillColor] ( 92.19, 37.85) rectangle ( 99.46, 37.85);
 
-\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);
+\path[fill=fillColor] ( 99.46, 37.85) rectangle (106.72, 37.85);
 
-\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);
+\path[fill=fillColor] (106.72, 37.85) rectangle (113.99, 37.85);
 
-\path[fill=fillColor] (113.39, 37.60) rectangle (120.69, 37.60);
+\path[fill=fillColor] (113.99, 37.85) rectangle (121.26,159.59);
 
-\path[fill=fillColor] (120.69, 37.60) rectangle (127.99, 37.60);
+\path[fill=fillColor] (121.26, 37.85) rectangle (128.52, 37.85);
 
-\path[fill=fillColor] (127.99, 37.60) rectangle (135.29, 37.60);
+\path[fill=fillColor] (128.52, 37.85) rectangle (135.79, 37.85);
 
-\path[fill=fillColor] (135.29, 37.60) rectangle (142.58, 37.60);
+\path[fill=fillColor] (135.79, 37.85) rectangle (143.05, 37.85);
 
-\path[fill=fillColor] (142.58, 37.60) rectangle (149.88, 37.60);
+\path[fill=fillColor] (143.05, 37.85) rectangle (150.32, 37.85);
 
-\path[fill=fillColor] (149.88, 37.60) rectangle (157.18, 37.60);
+\path[fill=fillColor] (150.32, 37.85) rectangle (157.58, 37.85);
 
-\path[fill=fillColor] (157.18, 37.60) rectangle (164.48, 37.60);
+\path[fill=fillColor] (157.58, 37.85) rectangle (164.85, 37.85);
 
-\path[fill=fillColor] (164.48, 37.60) rectangle (171.78, 37.60);
+\path[fill=fillColor] (164.85, 37.85) rectangle (172.11, 37.85);
 
-\path[fill=fillColor] (171.78, 37.60) rectangle (179.07, 37.60);
+\path[fill=fillColor] (172.11, 37.85) rectangle (179.38, 37.85);
 
-\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[fill=fillColor] (179.38, 37.85) rectangle (186.64, 37.85);
 
-\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);
+\path[fill=fillColor] (186.64, 37.85) rectangle (193.91, 37.85);
 
-\path[fill=fillColor] (193.67, 37.60) rectangle (200.97, 37.60);
+\path[fill=fillColor] (193.91, 37.85) rectangle (201.17, 37.85);
 
-\path[fill=fillColor] (200.97, 37.60) rectangle (208.27, 37.60);
+\path[fill=fillColor] (201.17, 37.85) rectangle (208.44, 37.85);
 
-\path[fill=fillColor] (208.27, 37.60) rectangle (215.56, 37.60);
+\path[fill=fillColor] (208.44, 37.85) rectangle (215.70, 37.85);
 
-\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);
+\path[fill=fillColor] (215.70, 37.85) rectangle (222.97, 37.85);
 
-\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);
+\path[fill=fillColor] (222.97, 37.85) rectangle (230.23, 37.85);
 
-\path[fill=fillColor] (230.16, 37.60) rectangle (237.46, 37.60);
+\path[fill=fillColor] (230.23, 37.85) rectangle (237.50, 37.85);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 68.10);
+\path[draw=drawColor,line width= 0.4pt] ( 48.60, 37.85) rectangle ( 55.87, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 55.87, 37.85) rectangle ( 63.13, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 62.31, 37.60) rectangle ( 69.61, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 63.13, 37.85) rectangle ( 70.40, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 70.40, 37.85) rectangle ( 77.66, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 77.66, 37.85) rectangle ( 84.93, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 84.20, 37.60) rectangle ( 91.50, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 84.93, 37.85) rectangle ( 92.19, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 92.19, 37.85) rectangle ( 99.46, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 99.46, 37.85) rectangle (106.72, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (106.72, 37.85) rectangle (113.99, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (113.99, 37.85) rectangle (121.26,159.59);
 
-\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 98.59);
+\path[draw=drawColor,line width= 0.4pt] (121.26, 37.85) rectangle (128.52, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (128.52, 37.85) rectangle (135.79, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 68.10);
+\path[draw=drawColor,line width= 0.4pt] (135.79, 37.85) rectangle (143.05, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (143.05, 37.85) rectangle (150.32, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (150.32, 37.85) rectangle (157.58, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (157.18, 37.60) rectangle (164.48, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (157.58, 37.85) rectangle (164.85, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (164.85, 37.85) rectangle (172.11, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (172.11, 37.85) rectangle (179.38, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (179.38, 37.85) rectangle (186.64, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (186.64, 37.85) rectangle (193.91, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (193.67, 37.60) rectangle (200.97, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (193.91, 37.85) rectangle (201.17, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (201.17, 37.85) rectangle (208.44, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (208.27, 37.60) rectangle (215.56, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (208.44, 37.85) rectangle (215.70, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (215.70, 37.85) rectangle (222.97, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (222.97, 37.85) rectangle (230.23, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt] (230.16, 37.60) rectangle (237.46, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (230.23, 37.85) rectangle (237.50, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.50) -- (120.69,165.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (121.26, 31.76) -- (121.26,165.67);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.22, 31.50) rectangle (246.94,165.68);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.16, 31.76) rectangle (246.95,165.67);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21, 35.09) {0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 65.34) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21, 65.53) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 95.83) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21, 95.96) {20};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,126.33) {30};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21,126.40) {30};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,156.82) {40};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21,156.83) {40};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
-	( 38.22, 37.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41, 37.85) --
+	( 39.16, 37.85);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 68.10) --
-	( 38.22, 68.10);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41, 68.28) --
+	( 39.16, 68.28);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 98.59) --
-	( 38.22, 98.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41, 98.72) --
+	( 39.16, 98.72);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,129.08) --
-	( 38.22,129.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41,129.15) --
+	( 39.16,129.15);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,159.58) --
-	( 38.22,159.58);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41,159.59) --
+	( 39.16,159.59);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.36,170.34) {b)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.45,113.85) {Observed};
 \end{scope}

### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-c.tex
some revisions

--- 2023-06-30 reports/paper/resources/intervention-density-witnin-combos-c.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:09
+% Created by tikzDevice version 0.12.6 on 2025-04-14 23:49:06
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
+\path[clip] ( 25.28, 31.76) rectangle (246.94,165.67);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
-\definecolor{fillColor}{RGB}{211,211,211}
-
-\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
-
-\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
-
-\path[fill=fillColor] ( 62.31, 37.60) rectangle ( 69.61, 37.60);
-
-\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 37.60);
-
-\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
-
-\path[fill=fillColor] ( 84.20, 37.60) rectangle ( 91.50, 37.60);
-
-\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 37.60);
-
-\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);
-
-\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);
-
-\path[fill=fillColor] (113.39, 37.60) rectangle (120.69, 37.60);
-
-\path[fill=fillColor] (120.69, 37.60) rectangle (127.99, 37.60);
-
-\path[fill=fillColor] (127.99, 37.60) rectangle (135.29, 37.60);
-
-\path[fill=fillColor] (135.29, 37.60) rectangle (142.58, 37.60);
-
-\path[fill=fillColor] (142.58, 37.60) rectangle (149.88, 37.60);
-
-\path[fill=fillColor] (149.88, 37.60) rectangle (157.18, 37.60);
-
-\path[fill=fillColor] (157.18, 37.60) rectangle (164.48, 37.60);
-
-\path[fill=fillColor] (164.48, 37.60) rectangle (171.78, 37.60);
-
-\path[fill=fillColor] (171.78, 37.60) rectangle (179.07, 37.60);
-
-\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 46.98);
-
-\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 46.98);
-
-\path[fill=fillColor] (193.67, 37.60) rectangle (200.97, 37.60);
-
-\path[fill=fillColor] (200.97, 37.60) rectangle (208.27, 37.60);
-
-\path[fill=fillColor] (208.27, 37.60) rectangle (215.56, 37.60);
-
-\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 46.98);
-
-\path[fill=fillColor] (222.86, 37.60) rectangle (230.16,159.58);
-
-\path[fill=fillColor] (230.16, 37.60) rectangle (237.46, 37.60);
+\path[fill=fillColor] ( 25.28, 31.76) rectangle (246.94,165.67);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (136.11, 31.76) -- (136.11,165.67);
 
-\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 25.28, 31.76) rectangle (246.94,165.67);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.4pt] ( 62.31, 37.60) rectangle ( 69.61, 37.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.28, 29.01) --
+	( 25.28, 31.76);
 
-\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 37.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 80.69, 29.01) --
+	( 80.69, 31.76);
 
-\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (136.11, 29.01) --
+	(136.11, 31.76);
 
-\path[draw=drawColor,line width= 0.4pt] ( 84.20, 37.60) rectangle ( 91.50, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (157.18, 37.60) rectangle (164.48, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 46.98);
-
-\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 46.98);
-
-\path[draw=drawColor,line width= 0.4pt] (193.67, 37.60) rectangle (200.97, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (208.27, 37.60) rectangle (215.56, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 46.98);
-
-\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16,159.58);
-
-\path[draw=drawColor,line width= 0.4pt] (230.16, 37.60) rectangle (237.46, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.50) -- (120.69,165.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.22, 31.50) rectangle (246.94,165.68);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (191.53, 29.01) --
+	(191.53, 31.76);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 25.28, 21.30) {0.200};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 72.38) {10};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 80.69, 21.30) {0.225};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,109.91) {20};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (136.11, 21.30) {0.250};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,147.44) {30};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
-	( 38.22, 37.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 75.13) --
-	( 38.22, 75.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,112.66) --
-	( 38.22,112.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,150.19) --
-	( 38.22,150.19);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.75) --
-	( 47.71, 31.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.75) --
-	(106.10, 31.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.75) --
-	(164.48, 31.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.75) --
-	(222.86, 31.50);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (191.53, 21.30) {0.275};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 47.71, 21.04) {0.0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.10, 21.04) {0.2};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.48, 21.04) {0.4};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (222.86, 21.04) {0.6};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (136.11,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.58,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.72) {Density};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 27.49,127.13) rectangle (103.49,150.66);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.59) {Density};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 27.49,144.14) {Target exposure limit:};
 \end{scope}
@@
 
-\path[fill=fillColor] ( 42.31,143.84) rectangle (118.31,163.87);
+\path[fill=fillColor] ( 27.49,129.63) rectangle ( 35.49,137.63);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 42.31,157.35) {Target exposure limit:};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 42.31,146.34) rectangle ( 50.31,154.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] ( 31.49,129.63) -- ( 31.49,137.63);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] ( 46.31,146.34) -- ( 46.31,154.34);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,147.59) {0.25 mg/m$^3$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 42.31,113.81) rectangle (114.21,141.84);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 42.31,135.32) {Distribution:};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 42.31,124.31) rectangle ( 50.31,132.31);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{fillColor}{RGB}{211,211,211}
-
-\path[fill=fillColor] ( 42.31,124.31) rectangle ( 50.31,132.31);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 42.31,116.31) rectangle ( 50.31,124.31);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt] ( 42.81,116.81) rectangle ( 49.81,123.81);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,125.55) {Post-intervention};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,117.55) {Observed};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.08,170.34) {c)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.99,130.87) {0.25 mg/m$^3$};
 \end{scope}

### 2025-04-15 illustrate-intervention-distribution.R

@@ -1,6 +1,7 @@
 # Figures for illustrating intervention ####
 # May 25, 2023
 
+library(data.table)
 library(here)
 library(boxr); box_auth()
 
@@ -26,7 +27,8 @@ options(
 # dat <- box_read(1179471733155)
 # dat <- dat[yin.gm >= 1965]
 dat.reduced <- box_read(928445783979)
-N <- length(unique(dat.reduced[!is.na(I)]$studyno))
+setDT(dat.reduced)
+N <- length(unique(dat.reduced[!is.na(I), studyno]))
 message(sum(dat.reduced[!is.na(I)]$status))
 source(here("g-formula.R"))
 dat.reduced[,.(year1 = min(year), year2 = max(year)), I]
@@ -169,46 +171,46 @@ mytheme <- theme_bw() +
 				plot.margin = margin(t = 6, b = 6, l = 6, r = 6)
 	)
 
-tikz('reports/SER (2023)/resources/intervention-density.tex',
-		 width = 3.75, height = 2.7,
-		 documentDeclaration = "\\documentclass{beamer}",
-		 bareBones = T, standAlone = F)
-melt(soluble_distribution[Observed > 0, -'studyno'],
-		 measure.vars = names(soluble_distribution[,-'studyno'])) -> ggdat
-ggdat[grep("Post", variable), variable := "Post-intervention\\ \\ \\ \\ "]
-ggdat[,variable := factor(variable, levels = rev(unique(variable)))]
-print(
-	ggplot(ggdat,
-				 aes(x = value, col = variable, fill = variable,
-				 		alpha = variable, linewidth = variable)) +
-		# geom_density(fill = NA, bw = 0.1, linewidth = 8 / .pt) +
-		geom_histogram(position = 'identity',
-									 aes(y = after_stat(density)),
-									 breaks = exp(seq(log(1e-3), log(10), 0.5))
-		) +
-		geom_vline(aes(lty = '0.25 mg/m\\textsuperscript{3}', xintercept = a),
-							 linewidth = 4 / .pt) +
-		scale_linetype_manual(values = 2) +
-		labs(x = "Exposure to soluble MWF (mg/m\\textsuperscript{3})",
-				 y = "Density",
-				 col = "Distribution:\\ \\ \\ ",
-				 fill = "Distribution:\\ \\ \\ ",
-				 alpha = "Distribution:\\ \\ \\ ",
[…]

### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-a.tex
cannot figure out figure

--- 2023-08-05 reports/paper/resources/intervention-density-witnin-combos-a.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:49:59
+% Created by tikzDevice version 0.12.3.1 on 2025-04-15 00:28:30
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
+\path[clip] ( 38.23, 31.51) rectangle (246.94,165.67);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
+\path[fill=fillColor] ( 38.23, 31.51) rectangle (246.94,165.67);
 \definecolor{fillColor}{RGB}{211,211,211}
 
-\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,110.79);
+\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
 
-\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 46.99);
 
@@
 
-\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 62.00);
+\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.91, 46.99);
 
-\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[fill=fillColor] ( 76.91, 37.60) rectangle ( 84.20, 46.99);
 
@@
 
-\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 37.60);
+\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 46.99);
 
-\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);
+\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10,159.58);
 
-\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);
+\path[fill=fillColor] (106.10, 37.60) rectangle (113.40, 37.60);
 
-\path[fill=fillColor] (113.39, 37.60) rectangle (120.69,159.58);
+\path[fill=fillColor] (113.40, 37.60) rectangle (120.69, 37.60);
 
@@
 
-\path[fill=fillColor] (135.29, 37.60) rectangle (142.58, 37.60);
+\path[fill=fillColor] (135.29, 37.60) rectangle (142.59, 37.60);
 
-\path[fill=fillColor] (142.58, 37.60) rectangle (149.88, 37.60);
+\path[fill=fillColor] (142.59, 37.60) rectangle (149.88, 37.60);
 
@@
 
-\path[fill=fillColor] (171.78, 37.60) rectangle (179.07, 37.60);
+\path[fill=fillColor] (171.78, 37.60) rectangle (179.08, 37.60);
 
-\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[fill=fillColor] (179.08, 37.60) rectangle (186.37, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01,110.79);
+\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 46.99);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 62.00);
+\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.91, 46.99);
 
-\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 76.91, 37.60) rectangle ( 84.20, 46.99);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 46.99);
 
-\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 46.99);
 
-\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.40, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (113.40, 37.60) rectangle (120.69, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 46.99);
 
-\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.59, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (142.59, 37.60) rectangle (149.88, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 93.90);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 46.99);
 
-\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.08, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (179.08, 37.60) rectangle (186.37, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 46.99);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 56.37);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 62.00);
+\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 46.99);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.50) -- (120.69,165.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.51) -- (120.69,165.67);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.22, 31.50) rectangle (246.94,165.68);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.23, 31.51) rectangle (246.94,165.67);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 34.85) {0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 62.29) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 74.72) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 89.74) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,114.60) {20};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,117.18) {15};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,144.62) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,154.48) {30};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
-	( 38.22, 37.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 37.60) --
+	( 38.23, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 65.05) --
-	( 38.22, 65.05);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 77.48) --
+	( 38.23, 77.48);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 92.49) --
-	( 38.22, 92.49);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,117.36) --
+	( 38.23,117.36);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,119.93) --
-	( 38.22,119.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,147.38) --
-	( 38.22,147.38);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,157.23) --
+	( 38.23,157.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.75) --
-	( 47.71, 31.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.76) --
+	( 47.71, 31.51);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.75) --
-	(106.10, 31.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.76) --
+	(106.10, 31.51);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.75) --
-	(164.48, 31.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.76) --
+	(164.48, 31.51);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.75) --
-	(222.86, 31.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.76) --
+	(222.86, 31.51);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.58,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.59,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,143.84) rectangle (244.95,163.87);
+\path[fill=fillColor] (168.95,144.09) rectangle (244.95,164.62);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,157.35) {Target exposure limit:};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,158.10) {Target exposure limit:};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,146.34) rectangle (176.95,154.34);
+\path[fill=fillColor] (168.95,146.59) rectangle (176.95,154.59);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.34) -- (172.95,154.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.59) -- (172.95,154.59);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.59) {0.25 mg/m$^3$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.84) {0.25 mg/m$^3$};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,113.81) rectangle (240.85,141.84);
+\path[fill=fillColor] (168.95,113.06) rectangle (240.85,141.59);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.32) {Distribution:};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.07) {Distribution:};
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
+\path[fill=fillColor] (168.95,123.56) rectangle (176.95,131.56);
 \end{scope}
@@
 
-\path[fill=fillColor] (168.95,116.31) rectangle (176.95,124.31);
+\path[fill=fillColor] (168.95,115.56) rectangle (176.95,123.56);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt] (169.45,116.81) rectangle (176.45,123.81);
+\path[draw=drawColor,line width= 0.4pt] (169.45,116.06) rectangle (176.45,123.06);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,125.55) {Post-intervention};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,124.80) {Post-intervention};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.22,170.34) {a)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,116.80) {Observed};
 \end{scope}

### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-b.tex
cannot figure out figure

--- 2023-06-30 reports/paper/resources/intervention-density-witnin-combos-b.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:08
+% Created by tikzDevice version 0.12.3.1 on 2025-04-15 00:28:46
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
+\path[clip] ( 38.23, 31.51) rectangle (246.94,165.67);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
+\path[fill=fillColor] ( 38.23, 31.51) rectangle (246.94,165.67);
 \definecolor{fillColor}{RGB}{211,211,211}
 
-\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,159.58);
+\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
 
-\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31,159.58);
 
@@
 
-\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 37.60);
+\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.91, 37.60);
 
-\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[fill=fillColor] ( 76.91, 37.60) rectangle ( 84.20, 37.60);
 
@@
 
-\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);
+\path[fill=fillColor] (106.10, 37.60) rectangle (113.40, 37.60);
 
-\path[fill=fillColor] (113.39, 37.60) rectangle (120.69, 37.60);
+\path[fill=fillColor] (113.40, 37.60) rectangle (120.69, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 68.10);
+\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 98.59);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.91, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);
+\path[draw=drawColor,line width= 0.4pt] ( 76.91, 37.60) rectangle ( 84.20, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.40, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (113.40, 37.60) rectangle (120.69, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 98.59);
+\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 68.10);
+\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.59, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (142.59, 37.60) rectangle (149.88, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 98.59);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.08, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);
+\path[draw=drawColor,line width= 0.4pt] (179.08, 37.60) rectangle (186.37, 37.60);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 34.85) {0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 65.34) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 65.34) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 95.83) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 95.83) {20};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,126.33) {30};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,126.33) {30};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,156.82) {40};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,156.82) {40};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
-	( 38.22, 37.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 37.60) --
+	( 38.23, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 68.10) --
-	( 38.22, 68.10);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 68.10) --
+	( 38.23, 68.10);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 98.59) --
-	( 38.22, 98.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 98.59) --
+	( 38.23, 98.59);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,129.08) --
-	( 38.22,129.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,129.08) --
+	( 38.23,129.08);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,159.58) --
-	( 38.22,159.58);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,159.58) --
+	( 38.23,159.58);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.36,170.34) {b)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,116.80) {Observed};
 \end{scope}

### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-c.tex
cannot figure out figure

@@
-% Created by tikzDevice version 0.12.6 on 2025-04-14 23:49:06
+% Created by tikzDevice version 0.12.3.1 on 2025-04-15 00:28:48
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 25.28, 31.76) rectangle (246.94,165.67);
+\path[clip] ( 38.23, 31.51) rectangle (246.94,165.67);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 25.28, 31.76) rectangle (246.94,165.67);
+\path[fill=fillColor] ( 38.23, 31.51) rectangle (246.94,165.67);
+\definecolor{fillColor}{RGB}{211,211,211}
+
+\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
+
+\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+
+\path[fill=fillColor] ( 62.31, 37.60) rectangle ( 69.61, 68.10);
+
+\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.91, 37.60);
+
+\path[fill=fillColor] ( 76.91, 37.60) rectangle ( 84.20, 37.60);
+
+\path[fill=fillColor] ( 84.20, 37.60) rectangle ( 91.50, 68.10);
+
+\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80,159.58);
+
+\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);
+
+\path[fill=fillColor] (106.10, 37.60) rectangle (113.40, 37.60);
+
+\path[fill=fillColor] (113.40, 37.60) rectangle (120.69, 37.60);
+
+\path[fill=fillColor] (120.69, 37.60) rectangle (127.99, 37.60);
+
+\path[fill=fillColor] (127.99, 37.60) rectangle (135.29, 37.60);
+
+\path[fill=fillColor] (135.29, 37.60) rectangle (142.59, 37.60);
+
+\path[fill=fillColor] (142.59, 37.60) rectangle (149.88, 37.60);
+
+\path[fill=fillColor] (149.88, 37.60) rectangle (157.18, 37.60);
+
+\path[fill=fillColor] (157.18, 37.60) rectangle (164.48, 37.60);
+
+\path[fill=fillColor] (164.48, 37.60) rectangle (171.78, 37.60);
+
+\path[fill=fillColor] (171.78, 37.60) rectangle (179.08, 37.60);
+
+\path[fill=fillColor] (179.08, 37.60) rectangle (186.37, 37.60);
+
+\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);
+
+\path[fill=fillColor] (193.67, 37.60) rectangle (200.97, 37.60);
+
+\path[fill=fillColor] (200.97, 37.60) rectangle (208.27, 37.60);
+
+\path[fill=fillColor] (208.27, 37.60) rectangle (215.56, 37.60);
+
+\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);
+
+\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);
+
+\path[fill=fillColor] (230.16, 37.60) rectangle (237.46, 37.60);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (136.11, 31.76) -- (136.11,165.67);
+\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 25.28, 31.76) rectangle (246.94,165.67);
+\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] ( 62.31, 37.60) rectangle ( 69.61, 68.10);
+
+\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.91, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] ( 76.91, 37.60) rectangle ( 84.20, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] ( 84.20, 37.60) rectangle ( 91.50, 68.10);
+
+\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 68.10);
+
+\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.40, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (113.40, 37.60) rectangle (120.69, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.59, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (142.59, 37.60) rectangle (149.88, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (157.18, 37.60) rectangle (164.48, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.08, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (179.08, 37.60) rectangle (186.37, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (193.67, 37.60) rectangle (200.97, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (208.27, 37.60) rectangle (215.56, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16,129.08);
+
+\path[draw=drawColor,line width= 0.4pt] (230.16, 37.60) rectangle (237.46, 37.60);
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.51) -- (120.69,165.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.23, 31.51) rectangle (246.94,165.67);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 34.85) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 80.59) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,126.33) {20};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.28, 29.01) --
-	( 25.28, 31.76);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 37.60) --
+	( 38.23, 37.60);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 80.69, 29.01) --
-	( 80.69, 31.76);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 83.34) --
+	( 38.23, 83.34);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (136.11, 29.01) --
-	(136.11, 31.76);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,129.08) --
+	( 38.23,129.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (191.53, 29.01) --
-	(191.53, 31.76);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.76) --
+	( 47.71, 31.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.76) --
+	(106.10, 31.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.76) --
+	(164.48, 31.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.76) --
+	(222.86, 31.51);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 25.28, 21.30) {0.200};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 47.71, 21.04) {0.0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 80.69, 21.30) {0.225};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.10, 21.04) {0.2};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (136.11, 21.30) {0.250};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.48, 21.04) {0.4};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (191.53, 21.30) {0.275};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (222.86, 21.04) {0.6};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (136.11,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.59,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.72) {Density};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.59) {Density};
 \end{scope}
@@
 
-\path[fill=fillColor] ( 27.49,127.13) rectangle (103.49,150.66);
+\path[fill=fillColor] ( 42.31,144.09) rectangle (118.31,164.62);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 27.49,144.14) {Target exposure limit:};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 42.31,158.10) {Target exposure limit:};
 \end{scope}
@@
 
-\path[fill=fillColor] ( 27.49,129.63) rectangle ( 35.49,137.63);
+\path[fill=fillColor] ( 42.31,146.59) rectangle ( 50.31,154.59);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] ( 31.49,129.63) -- ( 31.49,137.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] ( 46.31,146.59) -- ( 46.31,154.59);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.99,130.87) {0.25 mg/m$^3$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,147.84) {0.25 mg/m$^3$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 42.31,113.06) rectangle (114.22,141.59);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 42.31,135.07) {Distribution:};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 42.31,123.56) rectangle ( 50.31,131.56);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{fillColor}{RGB}{211,211,211}
+
+\path[fill=fillColor] ( 42.31,123.56) rectangle ( 50.31,131.56);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 42.31,115.56) rectangle ( 50.31,123.56);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt] ( 42.81,116.06) rectangle ( 49.81,123.06);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,124.80) {Post-intervention};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,116.80) {Observed};
 \end{scope}

### 2025-04-15 illustrate-intervention-distribution.R

@@ -140,9 +140,9 @@ soluble_combos <- dta.wide[, c('studyno', dynamic.which), with = F][
 ]
 
 soluble_combo_distributions <- rbindlist(list(
-	soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][1,], on = dynamic.which],
-	soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][8,], on = dynamic.which],
-	soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][46,], on = dynamic.which]
+	soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][1,], on = eval(dynamic.which)],
+	soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][8,], on = eval(dynamic.which)],
+	soluble_combos[soluble_combos[,.N, dynamic.which][order(N, decreasing = T)][45,], on = eval(dynamic.which)]
 ), idcol = T)
 
 soluble_combo_distributions[,.id := factor(.id, labels = c(
